### 2024-12-15 tex/ECC25 /main.tex
first commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a content stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

% MY PAKEAGES ========================================
\usepackage{epsfig}
% \usepackage{lipsum}  
\usepackage{kotex}
% \usepackage{natbib}
\usepackage{cite}
\usepackage{amssymb}
\usepackage{xcolor}
% \usepackage{enumitem}
% \newlist{steps}{enumerate}{1}
% \setlist[steps, 1]{label = Step \arabic*: }

\usepackage{algorithm}
\usepackage{svg}

\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{subfig}
% \usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
% \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
 % T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
% \usepackage{balance}

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\newtheorem{remark}{Remark}
\newtheorem{assum}{Assumption}
\newtheorem{lem}{Lemma}
\newtheorem{theorem}{Theorem}

\makeatletter
\let\NAT@parse\undefined
\makeatother
\usepackage{hyperref}
\hypersetup{
    linkbordercolor=blue,
    filebordercolor=red,
    citebordercolor = green,      
    urlbordercolor=red,
    %
    % colorlinks=true,
    % linkcolor=blue,
    % filecolor=blue,
    % citecolor = blue,      
    % urlcolor=cyan,
}

% MY PAKEAGES ========================================

\title{\LARGE \bf
Imposing a Weight Norm Constraint for Neuro–Adaptive Control
}
% Constrained Optimization-Based neuro–Adaptive Control With Weight Constraint

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In this paper, a neuro–adaptive controller with weight norm constraints is proposed for uncertain Euler‒Lagrange systems. The boundedness of the weights in the neuro–adaptive controller design is important to prevent excessively large control inputs and system instability. To ensure the boundedness of the weights, the weight norm constraints are imposed as inequality constraints in the weight adaptation. The adaptation law is derived based on the constrained optimization method. The stability of the proposed controller is analyzed in the sense of Lyapunov, ensuring the boundedness of the tracking error and weight estimation. For the comparative study, two benchmark controllers and the proposed controller were evaluated through a numerical simulation of a two-link manipulator system and compared in terms of tracking performance and parameter dependency. The comparative study verified that the proposed controller has better tracking performance and lower parameter dependency.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  SECTION INTRODUCTION ===================================

\section{Introduction}

In various practical applications, Euler‒Lagrange systems generally have uncertainties due to their unknown and unmodeled dynamics.
These uncertainties degrade the control performance index.
Furthermore, if uncertainties dominate the system, they may lead to instability.
By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{RN26, RN30}.
Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.

More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{RN24}.
It uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{RN35}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{RN16, RN18}, radial basis function NN (RBFNN) \cite{RN17, RN31} and deep NN (DNN) \cite{RN36}.
The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.

% The corresponding issue in the adaptive control is the parameter drift.
% It refers to the weight divergence during the adaptation process, while the tracking error is bounded.

% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
One of the common issues in using NNs is that the outputs of NNs are not predictable.
This is because the input‒output relationships of the NNs are not interpretable (i.e., the NNs are usually called black boxes \cite{RN8, RN9}).
This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.

Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
In \cite{RN31, RN36}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
In addition, the $\sigma$-modification \cite{RN17} and the $\epsilon$-modification \cite{RN16, RN18} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights. 
The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
However, they lack theoretical analysis regarding the optimality of the adapted weights.

Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{RN1, RN13}.
Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
By regulating the magnitude of the weights, the stability of the adaptation process can be enhanced, and overfitting can be prevented.
However, $L_2$-regularization also involves a trade-off between adaptation stability and the optimality of the weights.

For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{RN29} can be utilized.
It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
To the best of the authors’ knowledge, no prior work has utilized the constrained optimization method for the real-time weight adaptation of neuro–adaptive control satisfying weight boundedness.
Therefore, the constrained optimization method could play a pivotal role in the neuro–adaptive control design addressing the weight boundedness.

The main contributions of this study are as follows:
\begin{itemize}
    \item The neuro–adaptive control problem is reformulated into a constrained optimization problem by treating the satisfaction of the weight boundedness as inequality constraints.
    \item The adaptation law is derived based on the constrained optimization method to minimize the objective function while satisfying the weight norm constraints.
    \item The stability of the adaptation laws is analyzed via Lyapunov stability analysis, which ensures the boundedness of the tracking error and weight estimation.
\end{itemize}

The remainder of this paper is organized as follows:
Section \ref{sec: Problem Formulation} presents the target-constrained system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the adaptation law. 
Section \ref{sec:stability} examines the stability of the proposed controller.
A comparative study of the three selected controllers, including the proposed controller through numerical simulation, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper by presenting future work.

%  SECTION PROBLEM FORMULATION ============================
\section{Problem Formulation}\label{sec: Problem Formulation}

\subsection{Notation}
In this study, the following notation is used.

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite{RN22}.
    \item $x_{(i)}$ denotes the $i\textsuperscript{th}$ element of vector $x$.    
    % \item $A_{(i,j)}$ is the $i\textsuperscript{th}$ row-$j\textsuperscript{th}$ column element of matrix $A$.
    \item $\text{row}_j(A)$ denotes the $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$. 
    % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$, respectively.
    \item $\text{vec}(A)\triangleq [\text{row}_1(A^T)  ,\cdots,\text{row}_m(A^T)  ]^T   $ for $A\in\mathbb{R}^{n\times m}$.
    % \item $\text{vec}(A)\triangleq [\text{col}_1(A)^T  ,\cdots,\text{col}_m(A)^T  ]^T   $ for $A\in\mathbb{R}^{n\times m}$.
    \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of $A\in\mathbb{R}^{n\times n}$.
\end{itemize}

\subsection{Model Dynamics and Control Objective}

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    M(q)\ddot q + C(q,\dot q)\dot q + G(q) + F(q) = \tau
    \label{eq. system dynamics 1}
\end{equation}
where $q\in \mathbb{R}^n$ and $\tau\in\mathbb R^n$ denote the generalized coordinate and the control input, respectively; $M(q)\in\mathbb{R}^{n\times n}$, $C(q,\dot q)\in\mathbb{R}^{n\times n}$, and $G(q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $F(q)\in\mathbb{R}^{n}$ denotes the external force.
Using the user-designed matrices $M_0>0,C_0$ and $G_0$, \eqref{eq. system dynamics 1} can be represented as 
\begin{equation}
    M_0\ddot q+C_0\dot q+G_0 = \tau + f(q,\dot q,\ddot q)
    \label{eq. system dynamics 2}
\end{equation}
where $f(q,\dot q,\ddot q) \triangleq -(M-M_0)\ddot q-(C-C_0)(q,\dot q)\dot q -(G-G_0) -F(q)$ denotes the residual unknown term.

Hence, the objective of the control design is to make $q$ track the continuously differentiable desired trajectory $q_d(t):\mathbb R\to \mathbb R^n$ under the unknown terms $f$.

%  SECTION CONTROLLER DESIGN ==============================
\section{Control Law Development}\label{sec:ctrl design}

In this section, the neuro–adaptive controller is developed.
Section \ref{sec:ctrl dev} presents the details of the neuro–adaptive controller and the NN model.
The adaptation law based on the constrained optimization method is derived in Section \ref{sec:adap_laws} by formulating a constrained optimization problem.

\subsection{Neuro–adaptive Control Design} \label{sec:ctrl dev}

The backstepping control-based approach is utilized to generate a reference signal $z^*\triangleq -{k_q}\tilde q+\dot q_d$ for ${z}\triangleq \dot q$, where $\tilde q\triangleq {q} - q_d$ and $k_q\in\mathbb R_{>0}$.
The desired stabilizing controller can be designed as follows:
\begin{equation}
    \tau^* = -M_0\cdot ({k_z}\tilde z)+ 
        ( 
            -M_0\tilde q+C_0{z}+G_0-f+M_0 \dot z^*
        )
    \label{eq. desired control}
\end{equation}
where $\tilde z\triangleq z-z^*$ and $k_z\in\mathbb R_{>0}$.
Note that the desired controller cannot be realized because $f$.

To approximate the desired controller, an NN is utilized.
The NN with a single hidden layer is represented as 
\begin{equation*}
    \Phi({q_{NN}};\theta)\triangleq V_1^T\phi(V_0^T{q_{NN}})
\end{equation*}
where ${q_{NN}}\in\mathbb R^{l_0+1}$ denotes the NN input vector, $V_i\in\mathbb R^{(l_i+1)\times l_{i+1}},\ i\in[0,1]$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\phi:\mathbb R^{l_1}\to\mathbb R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (i.e., $\phi(x) = [\sigma(x_{(1)}),\cdots, \sigma(x_{(l_1)}), 1]^T$).
For further simplicity, let $\theta\triangleq[\theta_1^T,\theta_0^T]^T\in\mathbb R^{\Xi}$ denote the total weight vector, where $\theta_i\triangleq \text{vec}(V_i)\in\mathbb R^{\Xi_i}$ denotes the vectorized weights.
$\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

Using this NN, the desired controller $\tau^*$ can be approximated by the ideal weight vector $\theta^*$ for a compact subset $\Omega_{NN}\in\mathbb R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{q_{NN}}\in\Omega_{NN}} \Vert\Phi({q_{NN}};\theta^*) - \tau^*\Vert=\epsilon<\infty$ \cite{RN35}.
% The boundedness of the norm of $\theta^*$  and approximation error $\epsilon$ are also claimed in \cite{RN35}.
The ideal weight vector $\theta^*$ is typically assumed to be bounded.
Then, using the estimated weight vector $\hat\theta=[\hat\theta_1^T,\hat\theta_0^T]^T$ of $\theta^*=[\theta_1^{*T},\theta_0^{*T}]^T$, the desired controller $\tau^*\approx -\Phi(q_{NN};\theta^*)-\epsilon$ can be approximated as follows:
\begin{equation}
    \tau \triangleq -\Phi({q_{NN}};\hat\theta).
    \label{eq. control law}
\end{equation}
For further sections, let $\Phi^*\triangleq\Phi({q_{NN}};\theta^*)$ and $\phi^* \triangleq\phi(V_0^{*T}{q_{NN}})$, and let $\hat\Phi\triangleq\Phi({q_{NN}};\hat\theta)$, $\hat\phi \triangleq\phi(\hat V_0^{T}{q_{NN}})$ and $\hat\phi' \triangleq \partial \hat\phi/\partial (\hat V_0^Tq_{NN})$.

Using \eqref{eq. system dynamics 2}, \eqref{eq. desired control}, and \eqref{eq. control law}, the error dynamics can be obtained as the first-order system of augmented error $\xi\triangleq[\tilde q^T,\tilde z^T]^T\in\mathbb R^{2n}$ as follows:
\begin{equation*}
    \dot\xi = A_\xi\xi+B_\xi(\Phi^*-\hat\Phi+\epsilon)
\end{equation*}
where 
\begin{equation*}
    A_\xi \triangleq 
    \begin{bmatrix}
        -{k_q} I_n &I_n\\-I_n& -{k_z} I_n
    \end{bmatrix}
    ,\ 
    B_\xi \triangleq 
    \begin{bmatrix}
        0_{n\times n}\\M_0^{-1}
    \end{bmatrix}.
\end{equation*}

\subsection{Adaptation Law Derivation}\label{sec:adap_laws}

Using the augmented error $\xi$, the quadratic objective function is defined as
\begin{equation*}
    J(\xi;\hat\theta)\triangleq
    {1\over 2}
    \xi^TW\xi
\end{equation*}
where $W=W^T>0$ denotes the weighting matrix.

For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\Vert\hat\theta_i\Vert^2-\bar\theta^2_i,\ i\in[0,1]$.
% Then the objective of the adaptation process can be reformulated into the constrained optimization problem as follows:
The control problem can be reformulated into a constrained optimization problem as follows:
\begin{equation*}
    \begin{matrix}
        \min_{\hat\theta} \ J(\xi;\hat\theta)
        \\ \\
        \begin{aligned}
        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal A = [\theta_0,\theta_1].
        \end{aligned}
    \end{matrix}
\end{equation*}
In this optimization problem, $\xi$ is considered a predefined parameter.
The corresponding Lagrangian function is defined as
\begin{equation}
    L(\xi,\hat\theta,[\lambda_j]_{j\in\mathcal A})\triangleq J(\xi;\hat\theta)+\sum_{j\in\mathcal A} \lambda_jc_j(\hat\theta)
    .
\end{equation}
% where $\mathcal A=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
To solve the dual problem $\min_{\hat\theta} \max_{[\lambda_j]_{j\in\mathcal A}}  L$, the adaptation law is derived as follows:
\begin{align}
        \dot {\hat\theta}&=-\alpha {\partial L\over\partial \hat\theta}
        =-\alpha 
        \bigg(
        {\partial J\over \partial \hat\theta}+\sum_{j\in\mathcal{A}}
        \lambda_j {\partial c_j\over \partial \hat\theta}
        \bigg),
    \label{eq. adaptation law th}
        \\
        \dot\lambda_j& = \beta_j{\partial L\over\partial \lambda_j} = \beta_j c_j ,
        \quad\quad\quad\quad      \      
        \forall j\in\mathcal A,
    \label{eq. adaptation law L}
        \\
        \lambda_j & = \max(\lambda_j,0) ,
        \quad\quad\quad\quad\ \ \ \ \ 
        \forall j\in\mathcal A,
    \label{eq. adaptation law L max}
\end{align}
where $\alpha\in\mathbb R_{>0}$ and $\beta_j\in\mathbb R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
\color{red}
% The Eq.~\eqref{eq. adaptation law L max} is analog to using an active set $\mathcal A=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
\color{black}

Using the chain rule, the gradient of the objective function with respect to the weights (i.e., $\partial J/\partial \hat\theta$) in \eqref{eq. adaptation law th} can be represented as
\begin{equation*}
    {\partial J\over\partial \hat\theta}
    =
    {\partial \xi\over\partial \hat\theta}^TW
    {\partial \xi\over\partial \hat\theta}
    .
\end{equation*}
The calculation of $\partial J/\partial \hat\theta$ is not straightforward because of the dynamics of $\xi$.
Using the forward sensitivity method presented in \cite{RN34}, the sensitivity equation can be obtained as follows:
\begin{equation}
    \dot \eta =A_\xi - B_\xi 
    % (\partial \hat\Phi/\partial \hat\theta)
    {\partial \hat\Phi\over\partial \hat\theta}
    \label{eq. sen eq}
\end{equation}
where $\eta\triangleq \partial \xi/\partial \hat\theta\in\mathbb R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
The initial value of $\eta$ is zero since the initial $\xi$ is independent of the weights.
By decomposing for each layer, the dynamics of $\eta_i\triangleq \partial \xi/\partial \hat\theta_i\in\mathbb R^{2n\times \Xi_i}$ can be represented as
\begin{equation*}
    \begin{aligned}
        \dot\eta =&
        \begin{bmatrix}
            \eta_1&\eta_0
        \end{bmatrix}'
        \\
        =&A_\xi
        \begin{bmatrix}
            \eta_1&\eta_0
        \end{bmatrix}
        -B_\xi
        \begin{bmatrix}
            (I_{l_2}\otimes \hat\phi^T)&\hat V_1^T\hat\phi'(I_{l_1}\otimes {q_{NN}}^T)
        \end{bmatrix}
        .
    \end{aligned}
\end{equation*}
The calculation of $\partial \hat\Phi/\partial\hat\theta$ is introduced in \cite{RN36}.
In conclusion, the gradient of the objective with respect to the weights can be obtained as ${\partial J/\partial \hat\theta} = \eta^TW\xi$ by simulating the sensitivity equation \eqref{eq. sen eq}.

On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
\begin{equation*}
    \frac{\partial c_{\theta_0}}{\partial\hat\theta}
    = 
    \begin{bmatrix}
        0_{\Xi_1\times 1} \\
        2\hat\theta_0 
    \end{bmatrix}
    ,\quad
    \frac{\partial c_{\theta_1}}{\partial\hat\theta}    
    = 
    \begin{bmatrix}
        2\hat\theta_1 \\
        0_{\Xi_0\times 1}
    \end{bmatrix}
    .
\end{equation*}

%  SECTION STABILITY ANALYSIS ==============================
\section{Stability Analysis}\label{sec:stability}

The following theorem proves the boundedness of the tracking error and the weight estimation of the weights.

\begin{theorem}
For the dynamical system in \eqref{eq. system dynamics 1}, the proposed controller \eqref{eq. control law} and the adaptation law \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max} ensure the boundedness of the tracking error $\xi$ and the weight estimation $\hat\theta$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq. ctrl stable condition}.
\end{theorem}

\begin{proof}

The boundedness is proven from the last layer to the first layer.

\subsection*{Step 1: Boundedness of $\hat\theta_1,\eta_1,\xi$}

% For convenience, assume that all the constraints are in the active set without loss of generality.
% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
\color{black}
Without loss of generality, assume that all the constraints. Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
\color{black}

The dynamics of $\xi$ can be represented as
\begin{equation*}    
    \dot \xi = A_\xi\xi +B_\xi
    (
        -\hat V_1^T \hat\phi+w(t)
    )
\end{equation*}
where $w(t)\triangleq V_1^{*T}\phi^*+\epsilon$ is a lumped residual term, which is bounded as $\Vert w(t)\Vert\le \bar w< 0$ since $\Vert\theta_1^*\Vert$ and $\Vert\phi^*\Vert$ are bounded.
The dynamics of $\eta_1$ and $\hat\theta_1$ are represented as
\begin{equation*}
    \begin{aligned}
        \dot\eta_1 =
        & 
        A_\xi \eta_1 -B_\xi (I_{l_{2}}\otimes \hat\phi^T)
        \\
        \dot{\hat\theta}_1 =
        & -\alpha 
        (
            \eta_1^TW\xi+2\lambda_{\theta_1} \hat\theta_1
        ).
    \end{aligned} 
\end{equation*}
According to \cite[Chap.~4 T.~1.9]{RN32}, the boundedness of $\eta_1$ can be obtained since $A_\xi$ is stable and the residual term $-B_\xi (I_{l_{2}}\otimes \hat\phi^T)$ is bounded.

Define the Lyapunov function $\mathcal V_1=(1/2)\xi^TP\xi+(1/2\alpha)\hat\theta_1^T\hat\theta_1$, with the Lyapunov equation $A_\xi^TP+PA_\xi=-Q$, where $A_\xi<0,P=P^T>0$, and $Q>0$.
Using a proposition $\hat V_1^T\hat\phi = \text{vec}(\hat V_1^T\hat\phi)=\text{vec}(\hat\phi^T\hat V_1) = (I_{l_2}\otimes \hat\theta^T)\text{vec}(\hat V_1)=(I_{l_2}\otimes \hat\phi^T)\hat\theta_1$ \cite[Proposition~(7.1.9)]{RN22}, the time derivative of $\mathcal V_1$ is
\begin{equation}
    \begin{aligned}
        \dot {\mathcal V}_1 =& {1\over 2}\xi^T(A_\xi^TP+PA_\xi)\xi+\xi ^TP ( -B_\xi\hat V_1^T\hat \phi   +B_\xi w(t) )\\
        &+\hat\theta_1^T
        (
            -\eta_1^TW \xi-2\lambda_{\theta_1} \hat\theta_1 
        )
        \\
        =& -{1\over 2}\xi^TQ\xi -\xi^TPB_\xi(I_{l_2}\otimes \hat\phi^T)\hat\theta_1 +\xi^T\Delta
        \\
        &
        -\hat\theta_1^T\eta_1^TW\xi
        -2\lambda_{\theta_1} \hat\theta_1^T\hat\theta_1
        \\
        \le& -(1/2)\lambda_\text{min}(Q)\Vert \xi\Vert ^2
        +\bar\Delta \Vert \xi\Vert  
        +\bar M\Vert \xi\Vert  \Vert \hat\theta_1\Vert
        -2\lambda_{\theta_1}
        \Vert\hat\theta_1\Vert ^2
        \\
        \le& 
        (
        -{\lambda_\text{min}(Q)/ 2} +{\bar M/ 2}
        )
        \Vert \xi\Vert ^2 +\bar\Delta \Vert \xi\Vert  
        \\
        &+ 
        (
        -2\lambda_{\theta_1} 
        +\bar M/ 2
        )
        \Vert \tilde\theta_1\Vert ^2 
        \end{aligned}
        \label{eq. lya 1}
\end{equation}
where $\Delta\triangleq PB_\xi w(t)$ and $M\triangleq  -PB_\xi(I_{l_2}\otimes \hat\phi^T)+W\eta_1$ are bounded such that $\Vert\Delta\Vert\le\bar\Delta<\infty$ and $\Vert M\Vert_F\le \bar M< \infty$, respectively.

By defining $P=I_n$, the eigenvalues of $Q=-A_\xi^T-A_\xi$ are $2k_q$ and $2k_z$, since $A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
\begin{equation}
    \text{min}(k_q,k_z)>\bar M/2
    ,
    \label{eq. ctrl stable condition}
\end{equation}
and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\bar M/2$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
\begin{equation*}
    \Theta_\xi = 
    \bigg\{
        \xi \ \bigg\vert\ \Vert\xi\Vert \le  
        {
            \bar \Delta \over \lambda _\text{min}(Q)-\bar M/2
        } 
    \bigg\}
    ,
\end{equation*}
and the weight estimation $\theta^*_1$ is bounded in
\begin{equation*}
    \Theta_{\hat\theta_1} = 
    \{ 
        \hat\theta 
        \ 
        \vert
        \ 
        \Vert\hat\theta\Vert \le  
        \bar\theta_1
    \}
    .
\end{equation*}
The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once $\hat\theta_1$ approaches the compact set $\Theta_{\hat\theta_1}$, satisfying the constraint $c_{\theta_1}$.

\subsection*{Step 2: Boundedness of $\hat\theta_0,\eta_0$}

The dynamics of $\eta_0$ and $\hat\theta_0$ are represented as
\begin{equation*}
    \begin{aligned}     
        \dot\eta_0 =& 
        A_\xi\eta_0 -B_\xi 
        \hat V_1^T\hat\phi'(I_1\otimes {q_{NN}}^T)
        \\
        \dot{\hat\theta}_0
        =&
        -\alpha 
        (
            \eta_0^TW\xi+2\lambda_{\theta_0} \hat\theta_0
        )
        .
    \end{aligned}
\end{equation*}
According to \cite[Chap.~4 T.~1.9]{RN32}, $\eta_0$ is bounded since $A_\xi$ is a stable matrix and $-B_\xi\hat V_1^T\hat\phi'(I_1\otimes {q_{NN}}^T)$ is bounded.
To obtain the invariance set of $\hat\theta_0$, taking the time derivative of the Lyapunov function $\mathcal V_0=(1/2\alpha)\hat\theta_0^T\hat\theta_0$ yields:
\begin{equation*}
    \begin{aligned}
        \dot {\mathcal V}_0 =& 
        \hat\theta_0^T (-\eta_0W\xi -2\lambda_{\theta_0}\hat\theta_0)
        \\
        \le &
        \Vert\hat\theta_0\Vert \Vert \eta_0W\xi\Vert -2\lambda_{\theta_0} \hat\theta_0^T\hat\theta_0
        \\
        \le &
        -2\lambda_{\theta_0} \Vert\hat\theta_0\Vert^2 + \Vert \eta_0W\xi\Vert \Vert \hat\theta_0\Vert 
        .
    \end{aligned}
\end{equation*}
Then, the invariance set can be represented as 
\begin{equation*}
    \Theta_{\hat\theta_0} =
    \{
        \hat\theta_0\ \vert \ \Vert\hat\theta_0\Vert \le \Vert\eta_0W\xi\Vert/\lambda_{\theta_0}
    \}
    .    
\end{equation*}
If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{\hat\theta_0}$ converges to $\{\hat\theta_0\ \vert \ \Vert\hat\theta_0\Vert \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.

\end{proof}

% \begin{remark}
%     In the constrained optimization method, the corresponding method of $L_2$-regularization method is the quadratic penalty method, which replaces the constrained optimization problem into an unconstrained optimization problem by adding the penalty term $(1/2\mu)\sum_{r\in\mathcal A} c_r^2$ in the objective function.
%     The penalty parameter $\mu\in\mathbb R_{>0}$ usually decreases over implementation for the convergence of the optimization process.
%     However, the decreased penalty term $\mu$ may alter the original objective function as the penalty term dominates the objective function.
%     Therefore, $L_2$-regularization inherently has the analogous drawback of the quadratic penalty method in the selection of the regularization coefficient $\lambda$.
% \end{remark}

% \subsection{Orthogoanl-regularization}

%  SECTION SIMULATION ======================================
\section{Simulations}\label{sec:sim}

\subsection{Setup}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.8\linewidth]{RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{|c||c|c|c|c|}
    \hline
    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline 
    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
    \hline
    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $\theta_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

The two-link manipulator model in \cite{RN33} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system parameters are given in Table~\ref{table: system parameters}.
The reference signal of $q=[q_1,q_2]^T$ is defined as follows:
\begin{equation*}
    q_d
    =
    \begin{bmatrix}
        {q_d}_1\\
        {q_d}_2
    \end{bmatrix}
    = 
    \begin{bmatrix}
        +\cos(\pi/2 t) + 1 \\
        -\cos(\pi/2 t) - 1 
    \end{bmatrix}
    .
\end{equation*}

For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod) and the proposed controller with constrained optimization (NAC-CO).
%%%%%%%%%%%%%%%%%%%%%
The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters $\lambda$, $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively.
The square root of the integrated squared error (ISE) (i.e., $\sqrt{\int_0^T\Vert\xi\Vert^2\,dt}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
The parameter dependencies of the controllers were examined via various values of the parameters. 
The values ranged from $0.001$ to $1$ across $10$ samples.
%%%%%%%%%%%%%%%%%%%%%

The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
The adaptation law of NAC-L2 is derived by adding the squared weight term $(1/2)\lambda\hat\theta^T\hat\theta$ to the objective function such that $J_{L_2} = J+(1/2)\lambda\hat\theta^T\hat\theta$, where $\lambda\in\mathbb R_{>0}$ denotes the $L_2$ coefficient.
The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda\hat\theta$ as follows:
\begin{equation*} 
    \dot{\hat\theta} = 
    {\partial J_{L_2}\over\partial \hat\theta}
    =-\alpha
    \bigg(
        {\partial J\over\partial \hat\theta}+\lambda\hat\theta
    \bigg)
    .
    \label{eq. adap L2}
\end{equation*}
Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma\hat\theta$, where $\sigma\in\mathbb R_{>0}$.
For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\Vert \tilde z \Vert\hat\theta$ is added to the adaptation law as follows:
\begin{equation*}
    \dot{\hat\theta} = -\alpha
    \bigg(
        {\partial J\over\partial \hat\theta}+\rho\Vert\tilde z\Vert\hat\theta
    \bigg)
    \label{eq. adap eMod}
\end{equation*}
where $\rho\in\mathbb R_{>0}$ denotes the $\epsilon$-modification coefficient.
By $\Vert\tilde z\Vert$, the stabilizing function proportionally increases as the tracking error $\tilde z$ increases.
Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
The adaptation law of NAC-CO is presented in \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L}, and \eqref{eq. adaptation law L max}.
Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.

All controllers had the same control parameters except their crucial parameters (i.e., $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $M_0=I_2$ and $W=\text{diag}([5,1,15,15])$.
The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
The NN input vector was set to the desired trajectory $q_d$, with the augmented 1 to incorporate the bias term in the weight matrix such that $q_{NN}=[q_d^T,1]^T$.
For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
The sampling time of the simulation and the simulation termination time were set to $T_s=10^{-4}$ and $T=10$, respectively.

\subsection{Results}

\begin{figure}[!t]      
    \centering
    {\includegraphics[width=.85\linewidth]{BoxWhisker.drawio.png}}
\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
    \label{fig: Box-beard plot}
\end{figure}

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Quantitative comparison of square root of tracking ISE.}
    \centering
    \begin{tabular}{|c||c|c|c|}
    \hline
     & \textbf{NAC-L2} & \textbf{NAC-eMod} & \textbf{NAC-CO} (proposed) 
     \\
    \hline 
    Maximum         & $11.1753$e-3 & $0.5603$e-3 & $0.3439$e-3 \\
    \hline
    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
    % \hline
    Median          & $0.5898$e-3 & $0.5519$e-3 & $0.3240$e-3 \\
    \hline
    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
    % \hline
    Minimum         & $0.5434$e-3 & $0.5434$e-3 & $0.3235$e-3 \\
    \hline
    \end{tabular}
    \label{table: error norm}
\end{table}

As shown in Fig.~\ref{fig: Box-beard plot}, the maximum square root of the tracking ISE of NAC-CO is smaller than the minimum square root of the tracking ISEs of NAC-L2 and NAC-eMod for all variations in the parameters.
This is because NAC-L2 and NAC-eMod bias the weights to the origin due to the presence of stabilizing functions.
A quantitative comparison of the square root of the tracking ISE is provided in Table~\ref{table: error norm}.

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig9.eps}%
        \label{fig: weight NAC-L2}}
    \vfill
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig10.eps}%
        \label{fig: weight NAC-eMod}}
    \vfill
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig8.eps}%
        \label{fig: weight NAC-CO}}
    \vfill
    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: weight}
\end{figure}

\begin{figure}[!t]      
    \centering
        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig6.eps}%
        \label{fig: error NAC-L2}}
    \vfill
        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig7.eps}%
        \label{fig: error NAC-eMod}}
    \vfill
        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig5.eps}%
        \label{fig: error NAC-CO}}
    \vfill
    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
    \label{fig: error}
\end{figure}

For the detailed analysis, three values of the parameters (i.e., $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda\hat\theta$.
Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
Since the weight norm is decreased, NAC-L2 cannot generate sufficient control inputs, resulting in a larger square root of tracking ISE, as shown in Fig.~\ref{fig: error NAC-L2}.

On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
This is because the stabilizing function $-\alpha\rho\Vert\tilde z\Vert\hat\theta$ can be decreased once the tracking error $\tilde z$ is sufficiently regulated.
However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (i.e., smaller weight norms are observed as $\rho$ increases. ).
Therefore, similar to NAC-L2, the biased weights produce insufficient control input, resulting in a relatively larger square root of tracking ISE than that of NAC-CO, as described in Table \ref{table: error norm}.

Finally, the weight norm of NAC-CO is smaller than those of NAC-L2 and NAC-eMod, as shown in Fig.~\ref{fig: weight NAC-CO}, with better tracking performance.
Even if a large $\beta_j$ is provided, NAC-CO can adjust the adaptation direction to satisfy the weight norm constraints faster, according to \eqref{eq. adaptation law L}.
Therefore, the lowest dependency on the update rate $\beta_j$ is observed in NAC-CO, as shown in Fig.~\ref{fig: weight NAC-CO} and Fig.~\ref{fig: error NAC-CO}.
Note that $\beta_j$ of NAC-CO is the update rate for the Lagrange multipliers, whereas $\lambda$ and $\rho$ are the coefficients of the stabilizing function that generates the biases of the weights.
However, considering the implementation using a digital computer, excessively large $\beta_j$ values should be avoided.

The details of the satisfaction of the weight norm constraints are shown in Fig.~\ref{fig: weight and multiplier} for NAC-CO with $\beta_j=0.001$.
As the weight norms of each layer reach the constraint boundary, the corresponding Lagrange multipliers are generated.
Using the Lagrange multipliers, the adaptation direction is adjusted toward the constraint satisfactory point.
The Lagrange multipliers disappear when the constraints are satisfied, and the weights are adapted to optimize the original objective function without weight bias.

\begin{figure}[!t]      
    \centering
    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig12.eps}%
    \label{fig: weight per layer NAC-CO}}
    \vfill
    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig11.eps}%
    \label{fig: multipliers NAC-CO}}
    \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
    \label{fig: weight and multiplier}
\end{figure}

Furthermore, it is important to note that NAC-CO shows enhanced tracking performance with smaller weights than NAC-L2 and NAC-eMod.
This implies that the weights in NAC-CO approach the different local optimal solution points from those of NAC-L2 and NAC-eMod.
Therefore, if the physical analysis of the system is available to predict the feasible maximum control inputs, NAC-CO can find the local optimal solution without unnecessarily large control inputs by imposing proper weight norm constraints.

%  SECTION CONCLUSION ======================================
\section{Conclusion}\label{sec:conclusion}

\color{black}
In this paper, a neuro–adaptive control method is proposed for uncertain Euler‒Lagrange systems, ensuring weight boundedness.
Adaptation laws are derived by formulating a constrained optimization problem with weight norm constraints.
The boundedness of the tracking error and the weight estimation are analyzed via Lyapunov analysis.
The simulation results demonstrate that the proposed controller outperforms the existing methods in terms of tracking performance and parameter dependency.
As further work, the state and output constraints for safety will be handled, ensuring stability.
\color{black}

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{APPENDIX}

% Appendixes should appear before the acknowledgment.

% \section*{ACKNOWLEDGMENT}

% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{ieeetr}
\bibliography{refs}

\end{document}

% \begin{figure}[!t]
%     \centering
%         \subfloat[ of Proposed]{\includegraphics[width=0.45\linewidth]{fig9.eps}%
%         \label{fig: weight_Proposed}}
%     \qquad
%         \subfloat[ of NAC-L2]{\includegraphics[width=0.45\linewidth]{fig10.eps}%
%         \label{fig: weight_NAC-L2}}
%     \vfill
%         \subfloat[ of NAC-eMod]{\includegraphics[width=0.45\linewidth]{fig11.eps}%
%         \label{fig: weight_NAC-eMod}}
%     \qquad
%         \subfloat[ of CM3]{\includegraphics[width=0.45\linewidth]{fig12.eps}%
%         \label{fig: weight_CM3}}
%     \caption{controls.}
%     \label{fig: weights}
% \end{figure}

### 2024-12-15 tex/TNNLS24/main.tex
first commit

\documentclass[lettersize,journal]{IEEEtran}
% code
% MY PACKAGES ===================================
\usepackage{epsfig}
\usepackage{lipsum}  
\usepackage{kotex}
% \usepackage{natbib}
\usepackage{cite}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{enumitem}
\newlist{steps}{enumerate}{1}
\setlist[steps, 1]{label = Step \arabic*: }
\usepackage{hyperref}
\hypersetup{
    linkbordercolor=blue,
    filebordercolor=red,
    citebordercolor = green,      
    urlbordercolor=red,
    %
    % colorlinks=true,
    % linkcolor=blue,
    % filecolor=blue,
    % citecolor = blue,      
    % urlcolor=cyan,
 }
 \usepackage{algorithm}
 \usepackage{svg}

% MY PACKAGES ===================================

\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{subfig}
\usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{multicol}

\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}
\usepackage{balance}

% MY PACKAGES ===================================
% \let\proof\relax
% \let\endproof\relax
\usepackage{amsthm}
\newtheorem{remark}{Remark}
\newtheorem{assum}{Assumption}
\newtheorem{lem}{Lemma}
\newtheorem{theorem}{Theorem}

% MY PACKAGES ===================================

\begin{document}
\title{
Constrained Optimization-Based Neuro‒Adaptive Control (CoNAC) for Uncertain Euler‒Lagrange Systems Under Weight and Input Constraints 
%Constrained Optimization-Based neuro‒Adaptive Control (CoNAC) for Uncertain Euler‒Lagrange Systems With Input Constraints/
}

\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
~Vol.~00, No.~0, Month~2024
}%
{How to Use the IEEEtran \LaTeX \ Templates}

\maketitle

\begin{abstract}
    This study presents a constrained optimization-based neuro‒adaptive controller (CoNAC) for uncertain Euler‒Lagrange systems subject to weight norm and input constraints. A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints. The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
\end{abstract}

\begin{IEEEkeywords}
Neuro‒adaptive control, constrained optimization, deep neural network, Euler‒Lagrange system, input constraint.
\end{IEEEkeywords}

%  SECTION INTRODUCTION ===================================
\section{Introduction}

\subsection{Background}

\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler‒Lagrange systems. These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. These uncertainties can significantly degrade control performance and, in some cases, lead to instability. To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{RN4}, \cite{RN2}.

More recently, neuro‒adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{RN1}. NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. Various types of NNs have been utilized in neuro‒adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{RN29}, \cite{RN44} and radial basis function (RBF) neural networks \cite{RN26}, \cite{RN10}, as well as more complex models like deep neural networks (DNNs) \cite{RN16} and their variations. SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{RN44, RN56, RN3, RN41}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{RN25}. Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{RN14} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{RN15}, have further extended the capabilities of neuro‒adaptive control systems.

A critical aspect of neuro‒adaptive control is the weight adaptation law, which governs how NN parameters are updated. Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.

However, two significant challenges persist in using NNs for adaptive control. First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs. When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{RN18}. Failing to address these constraints can degrade control performance or even destabilize the system.

Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro‒adaptive controllers. The following section will provide a detailed review of the existing solutions to these challenges.

\subsection{Literature Review}

\subsubsection{Ensuring Weight Norm Boundedness}

A common challenge in neuro‒adaptive control is maintaining the boundedness of the NN weights to ensure stability. In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly. For example, in \cite{RN16, RN14, RN11}, projection operators were used to constrain the weight norms to remain below predetermined constants. However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values. While this approach ensured that the NN remained stable, it did not necessarily result in optimal performance.

In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{RN10} and $\epsilon$-modification \cite{RN41, RN3}. These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.

\subsubsection{Satisfying Input Constraints}

The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. This problem is exacerbated in neuro‒adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.

To address input saturation, many studies introduced auxiliary systems. These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. For instance, in \cite{RN55, RN56, RN3}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly. This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.

Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{RN34, RN38, RN37}. In \cite{RN41}, the NN was used to approximate the desired control input, compensating for input saturation. However, these approaches typically handle input bound constraints on a per-input basis (i.e., applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.

\subsubsection{Limitations of Existing Approaches and Potential of Constrained Optimization}

Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations. Projection operators and modification techniques do not guarantee the optimality of the adapted weights. Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.

To overcome these limitations, constrained optimization offers a promising approach. By formulating the neuro‒adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (e.g., tracking error) subject to both weight norm and input constraints. Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{RN22}.

In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{RN60} and the Alternating Direction Method of Multipliers (ADMM) \cite{RN58, RN59}, have been used to train NNs offline. These methods impose constraints to address issues like gradient vanishing in backpropagation. However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation. This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro‒adaptive control.

\subsection{Contributions}

The main contributions of this study are listed as follows:
\begin{itemize}
    \item A constrained optimization-based neuro‒adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints. The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function.
    %, enabling more precise real-time adaptation.
\end{itemize}

\subsection{Organization}

The remainder of this paper is organized as follows. 
Section \ref{sec: Problem Formulation} presents the target system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
Candidates of the weight and input constraints are presented in Section \ref{sec:cstr candidates}.
Section \ref{sec:stability} analyzes the stability of the proposed controller.
A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
% The appendices provide the proof of the lemma used in the stability analysis.

%  SECTION PROBLEM FORMULATION ============================
\section{Problem Formulation}\label{sec: Problem Formulation}

\subsection{Notation}
In this study, the following notation is used:

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite{RN17}.
    \item $x_{(i)}$ denotes the $i\textsuperscript{th}$ element of the vector $x\in\mathbb R^n$.    
    % \item $A_{(i,j)}$ is the $i\textsuperscript{th}$ row-$j\textsuperscript{th}$ column element of matrix $A$.
    \item $\text{row}_i(A)$ denotes the $i\textsuperscript{th}$ row of the matrix $A\in\mathbb{R}^{n\times m}$. 
    % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$, respectively.
    \item $\text{vec}(A)\triangleq [\text{row}_1(A^T)  ,\cdots,\text{row}_m(A^T)  ]^T   $ for $A\in\mathbb{R}^{n\times m}$.
    % \item $\text{vec}(A)\triangleq [\text{col}_1(A)^T  ,\cdots,\text{col}_m(A)^T  ]^T   $ for $A\in\mathbb{R}^{n\times m}$.
    \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of the matrix $A\in\mathbb{R}^{n\times n}$.
\end{itemize}

\subsection{Model Dynamics and Control Objective}

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    M(q)\ddot q + C(q,\dot q)\dot q + G(q) + F(q) = h(\tau)
    \label{eq. system dynamics 1}
\end{equation}
where $q\in \mathbb{R}^n$ denotes the generalized coordinate, and $\tau\in\mathbb{R}^n$ denotes the control input. The terms $M(q)\in\mathbb{R}^{n\times n}$, $C(q,\dot q)\in\mathbb{R}^{n\times n}$, and $G(q)\in\mathbb{R}^{n}$ represent the unknown system function matrices, while $F(q)\in\mathbb{R}^{n}$ denotes the external force. The function $h(\cdot)\in \mathbb{R}^n$ is a control input saturation function, where each element represents the control input saturation for each element of $\tau$. The gradient of $h(\cdot)$ with respect to $\tau$ is continous and bounded, i.e., $\Vert\partial h/\partial \tau\Vert_F\in L_\infty$.

The control input saturation function represents the inherent physical limitations of the actuators. To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design. Section \ref{sec:cstr candidates} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

Using user-designed nominal system matrices $M_0 > 0$, $C_0$, and $G_0$, \eqref{eq. system dynamics 1} can be reformulated as
\begin{equation}
    M_0\ddot q+C_0\dot q+G_0 = h(\tau) + f(q,\dot q,\ddot q)
    \label{eq. system dynamics 2}
\end{equation}
where $f(q,\dot q,\ddot q) \triangleq -\Delta M(q)\ddot q-\Delta C(q,\dot q)\dot q -\Delta G(q) -F(q)\in\mathbb{R}^n$ is the lumped system uncertainty function. Here, $\Delta M(q)\triangleq M(q)-M_0$, $\Delta C(q,\dot q)\triangleq C(q,\dot q)-C_0$, and $\Delta G(q)\triangleq G(q)-G_0$.

The function $f$ acts like an external disturbance, leading to a poor performance index and potential instability. 
%Therefore, an adaptive control approach is required to improve the control performance. 
The control objective is to develop a neuro‒adaptive controller that enables $q$ to track a continuously differentiable desired trajectory ${q_d}(t): \mathbb{R} \to \mathbb{R}^n$, compensating for the external disturbance while addressing the imposed constraints.

%  SECTION CONTROLLER DESIGN ==============================
\section{Control Law Development}\label{sec:ctrl design}

The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig: controller}, consisting of: a reference generator, a DNN that functions as a neuro‒adaptive controller, and a weight optimizer for the DNN. 
The reference generator is designed based on backstepping control (BSC), similar to the approach in \cite{RN20}, to generate a tracking reference for both $q$ and $\dot q$.
% To break down the original system into lower dimension subsystems, the BSC approach is utilized to design the controller \cite{RN38}, since \eqref{eq. system dynamics 1} is a second-order system.
Section \ref{sec:NAC} presents the neuro‒adaptive controller along with the reference generator, and Section \ref{NN definition} defines the DNN model. The weight optimizer will be detailed in Section \ref{sec:adap_laws}.

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro‒adaptive controller (CoNAC).}
    \label{fig: controller}
\end{figure*}

\subsection{Neuro‒Adaptive Controller Design}\label{sec:NAC}

The system dynamics \eqref{eq. system dynamics 2} can be represented as
\begin{equation}
    \begin{aligned}
        \dot {q} &= {z},\\
        \dot {z} &= -M_0^{-1} C_0 {z}-M_0^{-1} G_0+M_0^{-1} h(\tau) + M_0^{-1} f,
    \end{aligned}
    \label{eq. x dynamics}
\end{equation}
where ${z}\triangleq \dot q$.

Consider the Lyapunov function ${\mathcal V}_{c1}\triangleq(1/2){\tilde q}^T  {\tilde q}$, where ${\tilde q}\triangleq {q}-{q_d}$ represents the tracking error between the actual trajectory ${q}$ and the desired trajectory $q_d$. 
The desired trajectory of ${z}$, ensuring $\dot {\mathcal V}_{c1}={\tilde q}^T  ({z}-\dot {q_d})<0$ is 
\begin{equation}
    {z^*} \triangleq -{k_q}{\tilde q} + \dot q_d,
\end{equation}
which functions as the reference generator with control gain ${k_q} \in\mathbb{R}_{>0}$. The tracking error of ${z}$ relative to the desired trajectory ${z^*}$ is defined as
\begin{equation}
    {\tilde z} \triangleq {z} - {z^*} = {z} - (-{k_q}{\tilde q} + \dot q_d).
    \label{eq. e2}
\end{equation}

Next, consider the Lyapunov function ${\mathcal V}_{c2}\triangleq {\mathcal V}_{c1} + (1/2) {\tilde z}^T  {\tilde z}$.
Its time derivative is
\begin{equation}
    \begin{aligned}
    \dot {\mathcal V}_{c2} &=
    {\tilde q}^T  (-{k_q}{\tilde q}+{\tilde z}) +{\tilde z}^T  (-M_0^{-1} C _0{z} -M_0^{-1} G_0\\
    &\quad
    +M_0^{-1}h(\tau)+M_0^{-1} f- \dot z^*)\\
    &= -{k_q}{\tilde q}^T  {\tilde q} -{k_z}{\tilde z}^T  {\tilde z} +{\tilde z}^T  ({k_z}{\tilde z}+{\tilde q}\\
    &\quad-M_0^{-1} C_0{z} -M_0^{-1} G_0+M_0^{-1} h(\tau)+M_0^{-1} f- \dot z^* )
    \end{aligned}
\end{equation}
with control gain ${k_z}\in\mathbb{R}_{>0}$. 
The stabilizing control law, which does not account for weight norm and input constraints, is defined as follows:
\begin{equation}
    \tau^* \triangleq-M_0\cdot ({k_z}{\tilde z})+ 
    ( 
        -M_0{\tilde q}+C_0{z}+G_0-f+M_0 \dot z^*
    ).
    \label{eq. desired control}
\end{equation}
This control law ensures that the time derivative of the Lyapunov function is negative definite, as $\dot {\mathcal V}_{c2} = -{k_q}{\tilde q}^T  {\tilde q}-{k_z}{\tilde z}^T  {\tilde z}<0$, in the absence of any constraints. However, the control law $\tau^*$ cannot be realized in practice because the lumped system uncertainty function $f$, which accounts for unmodeled dynamics and disturbances, is not available.

Let $\Phi\triangleq\Phi(q_{NN};\theta): \mathbb{R}^{l}\times\mathbb{R}^{\Xi}\to\mathbb{R}^{n}$ represent the DNN, where $q_{NN}\in\mathbb{R}^{l}$ is the DNN input vector, and $\theta\in\mathbb{R}^{\Xi}$ is the vector of trainable weights.
The architecture of $\Phi(q_{NN};\theta)$ will be defined in Section \ref{NN definition}.
According to the universal approximation theorem for DNNs \cite{RN33}, $\Phi(q_{NN};\theta)$ can approximate a nonlinear function $g(\cdot)$ with an ideal weight vector $\theta^*$ on a compact subset $\Omega_{NN}\in\mathbb{R}^{l}$ to $\epsilon$-accuracy, such that $\sup_{q_{NN}\in\Omega_{NN}}\Vert \Phi(q_{NN};\theta^*) - g(\cdot) \Vert = \epsilon < \infty$.
Furthermore, the theorem states that the norm of $\theta^*$ is bounded, i.e., $\Vert\theta^*\Vert\le \bar\theta<\infty$.
In this study, $\theta^*$ is defined as a local optimal point, rather than a global optimal point.
%within the compact subset $\Omega_\theta=\{\theta^* \ \vert\ \Vert\theta^*\Vert\le \bar\theta\}$, where $\bar\theta$ denotes the user-selected maximum norm of the weight, ensuring $\epsilon$-accuracy.

The stabilizing control law is expressed by the DNN approximation with the ideal weight vector $\Phi^*\triangleq\Phi(q_{NN};\theta^*)$ as follows:
\begin{align}
    \tau^*=& -(\Phi^*+\epsilon),
\end{align}
which is estimated online by
\begin{align}
    \tau =& -\hat\Phi,
    \label{eq. approximated control}
\end{align}
where $\hat\Phi\triangleq\Phi(q_{NN};\hat\theta)$, and  $\hat\theta$ is the estimated weight vector for $\theta^*$.

Using \eqref{eq. x dynamics}, \eqref{eq. e2}, \eqref{eq. desired control}, and \eqref{eq. approximated control}, the error dynamics can be derived as
\begin{equation}
    \begin{aligned}
        \dot {\tilde q} = & -{k_q} {\tilde q} + {\tilde z} \\
        \dot {\tilde z} = & -{\tilde q} -{k_z} {\tilde z} + M_0^{-1} (\Phi^*-h(\hat\Phi)+\epsilon).
    \end{aligned}
    \label{eq. error dynamics1}
\end{equation}
The error dynamics \eqref{eq. error dynamics1} can be represented as a first-order system: 
\begin{equation}
    \dot\xi = A_\xi \xi + B_\xi (\Phi^*-h(\hat\Phi)+\epsilon)
    \label{eq. xi dynamics}
\end{equation}
where 
$\xi\triangleq[{\tilde q}^T  , {\tilde z}^T  ]^T  \in\mathbb{R}^{2n}$ denotes the augmented error,
and
\begin{equation*}
    A_\xi \triangleq 
    \begin{bmatrix}
        -{k_q} I_n &I_n\\-I_n& -{k_z} I_n
    \end{bmatrix}
    ,\ 
    B_\xi \triangleq 
    \begin{bmatrix}
        0_{n\times n}\\M_0^{-1}
    \end{bmatrix}.
\end{equation*}
Note that $A_\xi$ is a stable matrix, and $\Vert B_\xi\Vert_F<\infty$.
% According to \eqref{eq. xi dynamics}, $\xi$ will be regulated as $\hat\theta \rightarrow \theta^*$.

\subsection{Deep Neural Network (DNN) Model}\label{NN definition}

The DNN architecture presented in \cite{RN16} is utilized in this study and is defined as follows:
\begin{equation}
    \Phi(q_{NN};\theta) \triangleq V_k^T  \phi_{k}(V_{k-1}^T   \cdots \phi_2(V_1^T   \phi_1(V_0^T   q_{NN}))\cdots ))
    \label{eq. DNN structure 1}
\end{equation}
where $V_i\in\mathbb{R}^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\phi_i: \mathbb{R}^{l_i}\to\mathbb{R}^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. The activation function is defined as $\phi_i(x)=[\sigma(x_{(1)}),\sigma(x_{(2)}),\cdots, \sigma(x_{(l_{i})}), 1]^T$, where $\sigma: \mathbb{R}\to\mathbb{R}$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. Notice that the output size of $\Phi(\cdot)$ is the same as that of the control input $\tau$ (i.e., $l_{k+1}=n$). For a better understanding, \eqref{eq. DNN structure 1} also can be represented recursively as 
\begin{equation*}
    \Phi_i \triangleq
    \begin{cases}
        V_i^T  \phi_i(\Phi_{i-1}), &i\in[1,\dots,k],\\
        V_0^T  q_{NN},&i=0,
    \end{cases}
    \label{eq. DNN structure 2}
\end{equation*}
where $\Phi_k = \Phi(q_{NN};\theta)$.

One of the widely used activation functions for large DNNs is from the ReLU family \cite{RN27}, which effectively avoids the gradient vanishing problem during error backpropagation. However, for control applications, where relatively shallow DNNs are typically sufficient and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function. These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\Vert \phi_i(\cdot)\Vert < \infty$ and  $\Vert \nabla\phi_i(\cdot)\Vert_F < \infty$. In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (i.e., $\sigma(\cdot) = \tanh(\cdot))$, which provides desirable boundedness with $\Vert\sigma(\cdot)\Vert<1$ and $\Vert\nabla\sigma(\cdot)\Vert< 1$.

For simplicity, each layer's weights are vectorized as $\theta_i\triangleq\text{vec}(V_i)\in\mathbb{R}^{\Xi_i}$, where $\Xi_i\triangleq (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. The total weight vector $\theta\in\mathbb{R}^{\Xi}$ is defined by augmentating $\theta_i$ for all $i\in \left[0,\cdots,k\right]$ as 
\begin{equation*}
    \theta \triangleq 
    \begin{bmatrix}
        \theta_k\\
        \theta_{k-1}\\
        \vdots\\
        \theta_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \text{vec}(V_k)\\
        \text{vec}(V_{k-1})\\
        \vdots\\
        \text{vec}(V_0)
    \end{bmatrix},
\end{equation*}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \Phi(q_{NN};\theta)$ with respect to $\theta$ is defined as
\begin{equation}
    {\partial\Phi\over\partial \theta}=
    \begin{bmatrix}
        \dfrac{\partial \Phi}{\partial \theta_k}&
        \dfrac{\partial \Phi}{\partial \theta_{k-1}}&
    \cdots &
        \dfrac{\partial \Phi}{\partial \theta_0}
    \end{bmatrix}
    \in\mathbb{R}^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation*}
    \frac{\partial \Phi}{\partial \theta_i} = 
    \begin{cases}
        (I_{l_{k+1}}\otimes \phi_{k}^T  ), & i=k \\
        V_k^T   \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^T  ), & i=k-1\\
        &\vdots \\
        V_k^T   \phi'_{k} \cdots V_1^T  \phi_1' (I_{l_1}\otimes q_{NN}^T  ), & i = 0
    \end{cases},
\end{equation*}
where $\phi_i\triangleq \phi_i(\Phi_{i-1})$ and $\phi_i'\triangleq \partial \phi_i/\partial \Phi_{i-1}$.

In the following sections, let $\Phi^*_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\theta^*$. Additionally, define $\phi^*_i\triangleq\phi_i(\Phi^*_{i-1})$ and $\phi^{*'}_i\triangleq \partial \phi^*_i/\partial \Phi^*_{i-1}$. Similarly, $\hat\Phi_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \theta$, and define $\hat\phi_i\triangleq\phi_i(\hat\Phi_{i-1})$ and $\hat\phi_i'\triangleq \partial \hat\phi_i/\partial \hat\Phi_{i-1}$, respectively.

%  SECTION ADAPTATION LAW DERIVATION =======================
\section{Weight Adaptation Laws}\label{sec:adap_laws}

% \subsection{Adaptation Law using Lagrangian Function}
\subsection{Weight Optimizer Design}

Consider a positive definite objective function defined as 
\begin{equation*}
    J(\xi;\hat\theta)\triangleq 
    % {1\over 2}
    % \begin{bmatrix}
    %     {\tilde q}\\{\tilde z}
    % \end{bmatrix}^T
    % W
    % \begin{bmatrix}
    %     {\tilde q}\\{\tilde z}
    % \end{bmatrix}
    % =
    {1\over 2} \xi^T   W\xi
\end{equation*}
where $W=W^T  >0$ is a weighting matrix.
%Note that $\xi$ is considered a function of $\hat\theta$.
% Equality constraints $c_i,\ i\in\mathcal{q}$ and 
Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints. The corresponding constrained optimization problem is formulated as
\begin{equation}
    \begin{matrix}
        \min_{\hat\theta} \ J(\xi;\hat\theta)
        \\ \\
        \begin{aligned}
        \text{s.t. }&c_{j}(\hat\theta) 
        \le0, \quad j\in\mathcal{I},
        % c_{\mathcal{q},i}(\hat\theta) =0, \quad i\in\mathcal{q},\\
        \end{aligned}
    \end{matrix}
    \label{eq. train obj}
\end{equation}
% where $q_a$ is an additional vector in the constraints.
Here, $\xi$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
\begin{equation*}
    L(\xi,\hat\theta,[\lambda_j]_{j\in\mathcal A}) \triangleq J(\xi;\hat\theta) + 
    \sum_{j\in\mathcal A}
    \lambda_{j}
    c_{j}(\hat\theta)
\end{equation*}
where $\lambda_j$ denotes the Lagrange multiplier for each constraint, and $\mathcal A \triangleq \{j\in\mathcal I\ |\ c_j\ge 0\}$ represents the active set.

The adaptation laws for $\hat\theta$ and $[\lambda]_{j\in\mathcal A}$ are derived to solve the dual problem of \eqref{eq. train obj} (i.e.,  $\min_{\hat\theta} \max_{[\lambda]_{j\in\mathcal A}}L(\xi,\hat\theta,[\lambda]_{j\in\mathcal A})$), as follows:
%\begin{equation}
    \begin{align}
            \dot {\hat\theta}&=-\alpha {\partial L\over\partial \hat\theta}
            =-\alpha 
            \bigg(
            {\partial J\over \partial \hat\theta}+\sum_{j\in\mathcal{A}}
            \lambda_j {\partial c_j\over\partial \hat\theta}
            \bigg),
        \label{eq. adaptation law th}
            \\
            \dot\lambda_j& = \beta_j{\partial L\over\partial \lambda_j} = \beta_j c_j ,
            \quad\quad\quad\quad      \      
            \forall j\in\mathcal A,
        \label{eq. adaptation law L}
            \\
            \lambda_j & = \max(\lambda_j,0) ,
            \quad\quad\quad\quad\ \ \ \ \ 
            \forall j\in\mathcal A,
        \label{eq. adaptation law L max}
    \end{align}
    % \label{eq. adaptation law}
% \end{equation}
where $\alpha\in\mathbb{R}_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\mathbb{R}_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal A$. 
The Lagrange multipliers associated with inequality constraints are non-negative, i.e., $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive. When a constraint $c_j$ becomes active (i.e., violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation. Once the violation is resolved and the constraint is no longer active (i.e., $c_j < 0$), the multiplier decreases gradually until it returns to zero. Note that this adaption law is similar to the ALM in \cite{RN22}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-c_j/\mu,0)$, with $\mu\in\mathbb{R}_{>0}$ being the penalty parameter.

At steady state, where $\dot{\hat\theta}=0$ and $\dot\lambda_j=0$, the KKT conditions are satisfied, i.e., $\partial L/\partial \hat\theta=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{RN22}.
In other words, the proposed optimizer updates the DNN weights and Lagrange multipliers in a way that satisfies the KKT conditions. These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
% The KKT condition is satisfied, when $\hat\theta$ converges to $\theta^*$, since $\partial L/\partial \hat\theta=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).

\subsection{Calculation of the Exact Gradient of Objective Function}

The adaptation law for $\hat\theta$ involves the gradient of the objective function with respect to $\hat\theta$ (i.e., ${\partial J/\partial \hat\theta}$); see \eqref{eq. adaptation law th}. Since the objective function depends on the state $\xi$ of a dynamic system, obtaining the gradient is not straightforward. Therefore, the forward sensitivity method from \cite{RN12} is employed to calculate the exact gradient of the objective function.

By partially differentiating \eqref{eq. xi dynamics}, the sensitivity equation of $\xi$ with respect to $\hat\theta$ is first obtained as
\begin{equation}
    \dot\eta = A_\xi\eta - B_\xi{\partial h\over\partial \tau}{\partial\hat\Phi\over\partial\hat\theta}
    \label{eq. eta dynamics 1}
\end{equation}
where $\eta \triangleq \partial \xi/\partial \hat\theta\in\mathbb R^{2n\times \Xi}$.
Since the initial value of $\xi$ is independent to $\hat\theta$, $\eta|_{t=0}$ is a zero matrix. The gradient of the objective function with respect to $\hat\theta$ is then obtained as 
\begin{equation}
   {\partial J\over\partial \hat\theta} =  {\partial \xi\over \partial \hat\theta}^T  W\xi=\eta^T  W\xi\in\mathbb{R}^\Xi.
   \label{eq. dJdth}
\end{equation}
Equations \eqref{eq. eta dynamics 1} and \eqref{eq. dJdth} can be decomposed for each layer as 
\begin{equation}
    \begin{aligned}
        \dot \eta&= 
        \begin{bmatrix}
            \eta_k&
            \eta_{k-1}&
            \cdots &
            \eta_0
        \end{bmatrix}'
        \\
        &=A_\xi
        \begin{bmatrix}
            \eta_k&
            \cdots &
            \eta_0
        \end{bmatrix}
        -B_\xi{\partial h\over\partial \tau}
        \begin{bmatrix}
            (I_{l_{k+1}}\otimes \hat\phi_{k}^T  )&
        \cdots&
        (\cdot)
        \end{bmatrix}
    \end{aligned}
    \label{eq. eta dynamics}
\end{equation}
and
\begin{equation*}\label{eq. grad_J}
    {\partial J\over\partial\hat\theta}
    =
    \begin{bmatrix}
        \partial J/\partial\hat\theta_k\\\vdots\\\partial J/\partial\hat\theta_0\\
    \end{bmatrix}    =
    \begin{bmatrix}
        \eta_k^T\\\vdots\\\eta_0^T\\
    \end{bmatrix}
    W
    \xi
\end{equation*}
where $\eta_i \triangleq \partial \xi/\partial \hat\theta_i\in\mathbb R^{2n\times \Xi_i}$. The exact gradient of the objective function is calculated based on \eqref{eq. dJdth}, with the value of $\eta$ obtained by simulating the sensitivity equation \eqref{eq. eta dynamics 1}.

The proposed controller is implemented using Algorithm \ref{alg: alg1}. For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$. If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{RN22} to ensure that the objective function decreases.

\begin{algorithm}[!t]
    \caption{Weight Optimizer Implementation.}\label{alg: alg1}
    \begin{algorithmic}[1]
        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
        \renewcommand{\algorithmicensure}{\textbf{Output:}}
        \REQUIRE $\xi$, $\hat\theta$, $\lambda_j$, $\eta$
        \ENSURE  $\hat\theta$, $\lambda_j$, $\eta$
        \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
        \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
        \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
        \STATE Determine update directions $\dot{\hat\theta}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
        \STATE Update weight vector $\hat\theta\leftarrow \hat\theta+\dot{\hat\theta}\cdot T_s$;
        \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
        \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
        \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
        \STATE \textbf{RETURN};
    \end{algorithmic}
    \label{alg1}
\end{algorithm}

 \section{Constraint Candidates}\label{sec:cstr candidates}

This section introduces potential weight and input constraints that can be used in the proposed neuro‒adaptive controller. The controller can handle any combination of the following constraints, provided they meet the specified assumptions.

\begin{assum}
    The constraint functions $c_j(\hat\theta),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\theta^*)\le 0$.
    \label{assum1}
\end{assum}

% \begin{assum}
%     The Frobenius norm of $\partial c_j/\partial\hat\theta_i$ is bounded. %when the norms of $\hat\theta_i,\ \forall i [k,\cdots,i+1]$ are bounded.
%     \label{assum2}
% \end{assum}

% The Assumption \ref{assum2} also means that the boundedness of $\Vert\hat\theta_k\Vert$ implies the boundedness of $\Vert\partial c_j/\partial \hat\theta\Vert_F$, since $\tau=-\hat V_k\hat\phi_k$ is bounded when $\Vert\hat\theta_k\Vert$ bounded i.e., $\Vert\phi(\cdot)\Vert$ is already bounded.

\begin{assum}
    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{RN22}.
    \label{assum2}
\end{assum}

\subsection{Weight Norm Constraint}\label{sec:cstr weight ball}

The weight norm constraint $\mathbf{c}_{\theta}\triangleq [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ limits the maximum norm of each layer's weight vector, where
\begin{equation}
    c_{\theta_i}=\Vert \hat\theta_i\Vert^2 -\bar\theta_i^2 \le 0
    \label{eq. cstr weight ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\hat\theta_i$. 
The gradient of $\mathbf{c}_\theta$ with respect to $\hat\theta$ is given by
\begin{equation}\label{eq weight norm cnst grad}
    {\partial \mathbf c_\theta \over \partial \hat\theta}
    \triangleq
    \begin{bmatrix}
        (\partial c_{\theta_0}/\partial \hat\theta)^T
        \\ 
        \vdots 
        \\
        (\partial c_{\theta_k}/\partial \hat\theta)^T
    \end{bmatrix}
    = 2\cdot 
    \begin{bmatrix}
        0&0&\cdots & \hat\theta_0^T\\
        \vdots&\vdots&\ddots&\vdots\\
        0&\hat\theta^T_{k-1}&\cdots &0\\
        \hat\theta^T_k&0&\cdots &0
    \end{bmatrix}
    \in\mathbb R^{(k+1)\times\Xi}
    .
\end{equation}
%As demonstrated in Section \ref{sec:stability}, the weight norm constraint should be imposed on the controller to ensure the boundedness of the tracking error and weight estimation.

%\begin{remark} Imposing the weight norm constraint is analogous to applying $L_2$-regularization, a common technique used in DNN training to prevent parameter drift or overfitting \cite{RN23}, by minimizing the $L_2$ norm of the estimated weight vector $\hat\theta$. Typically, $L_2$-regularization adds a term $\lambda\Vert\hat\theta\Vert_2^2$ to the objective function $J$, where $\lambda\in\mathbb R_{>0}$ is a constant $L_2$ coefficient. This term biases the trainable weights $\hat\theta$ toward the origin (i.e., $\hat\theta = 0$) in the adaptation law \eqref{eq. adaptation law th}. In contrast, within the proposed controller, the term associated with the maximum weight ball constraint in the adaptation law (i.e., $\sum_{j\in\mathcal{A}}\lambda_j (\partial c_j/\partial \hat\theta)$ in \eqref{eq. adaptation law th}) vanishes when the constraint is satisfied (i.e., $\lambda_j = 0$).
    % 1. 제약조건이 사라져 자유롭게 ball condition 내에서 optimal point로 접근할 수 있다.
%    As a result, $\hat\theta$ can still converge to $\theta^*$ without being restricted to the origin.
%    Moreover, $\lambda_{b_i}$ which corresponds to $\lambda$ varies as the constraint is violated, while $L_2$-regularization has a constant coefficient.
%    \label{remark: ball cstr}
%\end{remark}

\subsection{Input Bound Constraint}

Most physical systems have control input limits due to electrical and mechanical limitations. These are expressed as $\mathbf{c}_{\overline \tau}\triangleq [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\mathbf{c}_{\underline\tau}\triangleq [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
\begin{equation}
    \begin{aligned}
        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
        \\
        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
    \end{aligned}
    \label{eq. cstr input saturation}
\end{equation}
with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
The gradients of $\mathbf{c}_{\overline \tau}$ and $\mathbf{c}_{\underline\tau}$ with respect to $\hat\theta$ are given by
\begin{equation}
    \begin{aligned}
        {\partial \mathbf \mathbf c_{\overline \tau} \over \partial \hat\theta}
        & 
        \begin{bmatrix}
            (\partial c_{\overline \tau_1}/\partial \hat\theta)^T \\
            \vdots \\
            (\partial c_{\overline \tau_n}/\partial \hat\theta)^T
        \end{bmatrix}
         = -{\partial \hat\Phi\over\partial\hat\theta}
         \\
        =&
        -\begin{bmatrix}
            (I_{l_{k+1}}\otimes \hat\phi_{k}^T)&
            % V_k^T \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^T)&
            \cdots &
            (
            \cdot
            )
        \end{bmatrix} 
        &
        \in
        \mathbb R^{n\times \Xi}
        , 
        \\
        {\partial \mathbf \mathbf c_{\underline\tau} \over \partial \hat\theta}         
        \triangleq
        & 
        \begin{bmatrix}
            (\partial c_{\underline\tau_1}/\partial \hat\theta)^T \\
            \vdots \\
            (\partial c_{\underline\tau_n}/\partial \hat\theta)^T
        \end{bmatrix}
        = +{\partial \hat\Phi\over\partial\hat\theta}
        \\
        =&
        +\begin{bmatrix}
            (I_{l_{k+1}}\otimes \hat\phi_{k}^T)&
            % V_k^T \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^T)&
            \cdots &
            (
            \cdot
            )
        \end{bmatrix} 
        &
        \in
        \mathbb R^{n\times \Xi}
        .
    \end{aligned}
    \label{eq. nabla input sat}
\end{equation}

\subsection{Input Norm Constraint}\label{sec:input_norm_cnst}

Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate. Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations. This can be captured by the following inequality constraint: 
\begin{equation}
    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
    \label{eq. cstr input ball}
\end{equation}
with $\bar\tau\in\mathbb{R}_{>0}$ denoting the maximum allowable control input magnitude. This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{RN62}.
% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
The gradients of $c_{u}$ with respect to $\hat\theta$ are given by
\begin{equation}
    {\partial \mathbf \mathbf c_{u} \over \partial \hat\theta}
    = -\sum_{i=1}^n 2\tau_{(i)} 
    \bigg(
        \text{row}_i
        \bigg(
            -{\partial \hat\Phi\over\partial\hat\theta}
        \bigg)
    \bigg)^T  
    = \tau^T (I_{l_{k+1}}\otimes \hat\phi_k^T)
    \in \mathbb R^{\Xi}.
    \label{eq. nabla input ball}
\end{equation}
It should be noted that constraints \eqref{eq. cstr input saturation} and \eqref{eq. cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq. nabla input sat} and \eqref{eq. nabla input ball} are linearly dependent, violating the LICQ condition.

%  SECTION STABILITY ANALYSIS ==============================
\section{Stability Analysis}\label{sec:stability}

Before conducting the stability analysis, let $\tilde\theta\triangleq [\tilde\theta_i]_{i\in[0,\cdots,k]}$, where $\tilde\theta_i\triangleq\hat\theta_i-\theta^*_i$ represents the weight estimation error. The following Lemmas are introduced for the stability analysis. % of the last layer of the DNN.
\begin{lem}
    If Assumptions \ref{assum1} and \ref{assum2} are satisfied, the angle between $\partial c_j/\partial \hat\theta_k$ and $\hat\theta_k$ is positive when $c_j$ is active set, i.e., $(\partial c_j/\partial \hat\theta_k)^T\hat\theta_k>0$.
    \label{lem1}
\end{lem}

%\begin{figure}[!t]
%    \centering
%    \includegraphics[width=.99\linewidth]{spaces.drawio.png}
%    \caption{Convexity of input constraints.}
%    \label{fig: spaces}
%\end{figure}

\begin{proof}

Since $\tau = -\hat\Phi$, using \cite[Proposition 7.1.9]{RN17}, a linear map $T(\cdot):\hat\theta_k\to\tau$ can be derived: 
\begin{equation}\label{eq linear map}
    \begin{aligned}
    \tau = &-\hat\Phi = -\text{vec}(\hat\Phi)     = -\text{vec}(\hat V_k \hat\phi_k) 
    \\
    = & -(I_{l_{k+1}}\otimes \hat\phi_k^T)\text{vec}(\hat V_k)
    =-(I_{l_{k+1}}\otimes \hat\phi_k^T)\hat\theta_k = T(\hat\phi_k) \hat\theta_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in $\tau$-space (assumed in Assumption \ref{assum1}) holds in $\hat\theta_k$-space, implying
%, as depicted in Fig.~\ref{fig: spaces}. 
that $(\partial c_j/\partial \hat\theta_k)^T\hat\theta_k>0$.

\end{proof}

% \begin{assum}
%     The Frobenius norm of $\partial c_j/\partial\hat\theta_i$ is bounded. %when the norms of $\hat\theta_i,\ \forall i [k,\cdots,i+1]$ are bounded.
%     \label{assum2}
% \end{assum}

\begin{lem} 
    If $c_j(\hat\theta),\ \forall j\in\mathcal I \setminus \{\theta_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum1}, then $\Vert\partial c_j/\partial\hat\theta_i\Vert$, for all $i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\hat\theta_i$, for all $i\in[k,\cdots, i+1]$, remain bounded.
    % which can be verified using the boundedness of $\hat\theta_i,\ \forall i [k,\cdots,i+1]$ (as demonstrated in Section \ref{sec:stability}), and the boundedness of $\Vert\phi_i(\cdot)\Vert$ and $\Vert\nabla\phi_i(\cdot)\Vert$.
    \label{lem2}
\end{lem}

\begin{proof}

The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\theta_i\}_{i\in[0,\cdots,k]}$, with respect to $\hat\theta_i$ is represented as
\begin{equation*}
    {\partial c_j\over\partial \hat\theta_i} = {\partial c_j\over\partial \tau} {\partial \tau\over\partial \hat\Phi} {\partial \hat\Phi\over\partial \hat\theta_i}
\end{equation*}
where $\partial \tau/\partial \hat\Phi=-I_n$, which is bounded. From the linear mapping in \eqref{eq linear map}, $\tau$ is bounded as long as $\hat\theta_k$ is bounded (by the condition of the lemma), and $\Vert\phi_k(\cdot)\Vert$ is bounded due to the properties of the activation functions. By Assumption \ref{assum1}, the function $c_j$ is convex. The convex function has a bounded derivative with respect to $\tau$, since $\tau$ is a bounded variable (i.e., $\partial c_j/\partial\tau$ is bounded). Furthermore, $\partial \hat\Phi/\partial \hat\theta_i$ is bounded, provided that the norms of $\hat\theta_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. This can be verfied by using the definition of $\partial \hat\Phi/\partial\hat\theta_i$ given in \eqref{eq. nabla phi}.
Consequently, $\Vert\partial c_j/\partial \hat\theta_i\Vert,\ \forall j\in\mathcal I \setminus \{\theta_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\hat\theta_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.

\end{proof}

The following theorem shows that $\hat\theta$ and $\xi$ are bounded.

\begin{theorem}
    For the dynamical system in \eqref{eq. system dynamics 1}, the neuro‒adaptive controller \eqref{eq. approximated control} and weight adaptation laws \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L}, and \eqref{eq. adaptation law L max} ensure the boundedness of the augmented error $\xi$ and the weight estimate $\hat \theta$. This holds with the weight norm constraint \eqref{eq. cstr weight ball} and input constraints satisfying Assumption \ref{assum1} and \ref{assum2}, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq. ctrl stable condition}.
\end{theorem}

\begin{proof}

The boundednesses of $\hat\theta$, $\xi$, and $\eta$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\hat\Phi$. The step-by-step analysis is described as follows.

\subsection*{Step 1: Boundedness of $\hat\theta_k,\eta_k$, and $\xi$}
% \subsubsection*{Step 1: Boundedness of $\hat\theta_k,\eta_k,\xi$}

% Noting that $\Phi^* = V_k^{*T}\phi^*_k$ and $\hat\Phi = \hat V_k^{T}\hat \phi_k$, the error dynamics \eqref{eq. xi dynamics} can be rewritten by adding and substracting $V_k^{*T}\hat\phi_k$ on the right side as follows:
% \begin{equation}
%     \begin{aligned}
%         \dot \xi &= A_\xi\xi +B_\xi
%         \bigg( 
%             (V^*_k - \hat V_k)^T   \hat\phi_{k} + V^{*T} (\phi_{k}^*-\hat\phi_{k} ) +\epsilon
%         \bigg)\\
%         &=A_\xi\xi  + B_\xi
%         \bigg( 
%             (V^*_k - \hat V_k)^T   \hat\phi_{k} +w(t)
%         \bigg)
%     \end{aligned}
% \end{equation}
% where $w(t) \triangleq V_k^{*T} (\phi^*_{k} - \hat\phi_{k} ) + \epsilon$ is the bounded unknown term, given that $\phi_k(\cdot)$ , $V_k^*=\text{vec}^{-1}(\theta^*_k)$ and $\epsilon$ are bounded.

The boundedness of $\xi$ follows from \eqref{eq. xi dynamics}, using the result from \cite[Chap.~4 T.~1.9]{RN13}, since $A_\xi$ is a stable matrix and the term $B_\xi (\Phi^*-h(\hat\Phi)+\epsilon)$ is bounded due to $\Vert B_\xi\Vert_F$, $\Vert V_k^*\Vert_F$, $\Vert \phi(\cdot)\Vert$, $\Vert h(\cdot)\Vert$, and $\Vert\epsilon\Vert <\infty$.

%The weight norm constraint $\mathbf{c}_{b}\triangleq [c_{b_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ presented in Section \ref{sec:cstr candidates} is imposed on the controller.
%Additional constraints that satisfy Assumptions \ref{assum1}, \ref{assum2} and \ref{assum3} can be imposed and the constraint candidates are introduced in Section \ref{sec:cstr candidates}.

Assume that all constraints are actve in $\mathcal A$ without loss of generality. The dynamics of $\eta_k$ and $\hat\theta_k$ can be decomposed from \eqref{eq. adaptation law th} and \eqref{eq. eta dynamics} as 
\begin{equation*}
    \begin{aligned}
        \dot\eta_k =
        & 
        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}{\partial \hat\Phi\over \partial \hat\theta_k}
        =
        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}(I_{l_{k+1}}\otimes \hat\phi_k^T)\\
        \dot{\hat\theta}_k =
        & -\alpha 
        \bigg[
            \eta_k^TW\xi+
            \sum_{j\in\mathcal{A}}
            \lambda_j{\partial c_j\over\partial \hat\theta_k}
        \bigg]
    \end{aligned} 
\end{equation*}
According to \cite[Chap.~4 T.~1.9]{RN13}, $\Vert \eta_k\Vert_F$ is bounded, since $A_\xi$ is a stable matrix and the term $-B_\xi(\partial h/\partial \tau)(I_{l_{k+1}}\otimes\hat\phi_k^T)$ is also bounded.

Let $\mathcal{V}: \mathbb{R}^{2n} \times \mathbb{R}^{\Xi} \to \mathbb{R}_{>0}$ denote the Lyapunov function:
\begin{equation}
    \mathcal{V} = \frac{1}{2} \xi^T P \xi + \frac{1}{2 \alpha} \hat{\theta}_k^T \hat{\theta}_k,
    \label{eq. Lyapunov func}
\end{equation}
with the Lyapunov equation $A_\xi^T P + P A_\xi = -Q$, where $A_\xi < 0$, $P = P^T > 0$, and $Q > 0$.
Taking the time derivative of $\mathcal{V}$ yields:
\begin{equation}
    \begin{aligned}
        \dot{\mathcal{V}} 
        &= -\frac{1}{2} \xi^T Q \xi + \xi^T P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon) \\
        &\quad - \hat{\theta}_k^T \left( \eta_k W \xi + \sum_{j \in \mathcal{A}} \lambda_j \frac{\partial c_j}{\partial \hat{\theta}_k} \right)
    \end{aligned}
    \label{eq. Lyapunov dot}
\end{equation}
By applying the boundedness of $\Delta \triangleq P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon)$ and $M \triangleq \eta_k W$, where $\Vert \Delta \Vert \leq \bar{\Delta} < \infty$ and $\Vert M \Vert_F \leq \bar{M} < \infty$, this simplifies to:
\begin{equation}
    \begin{aligned}
        \dot{\mathcal{V}} 
        &\leq \left( -\frac{\lambda_{\text{min}}(Q)}{2} + \frac{\bar{M}}{2} \right) \Vert \xi \Vert^2 + \bar{\Delta} \Vert \xi \Vert \\
        &\quad + \frac{\bar{M}}{2} \Vert \hat{\theta}_k \Vert^2 - \sum_{j \in \mathcal{A}} \lambda_j \hat{\theta}_k^T \frac{\partial c_j}{\partial \hat{\theta}_k}.
    \end{aligned}
    \label{eq. dot Vk 1}
\end{equation}

By representing the term $\partial c_{\theta_k}/\partial \hat\theta_k$ in the last inequality as $\partial c_{\theta_k}/\partial \hat\theta_k=2\hat\theta_k$ using the result provided in \eqref{eq weight norm cnst grad}, $\dot {\mathcal V}$ can be rewritten as
\begin{equation}
    \begin{aligned}
        \dot {\mathcal V} \le&
        (\cdot) + 
        \bigg(
            -2\lambda _{\theta_k}+{\bar M}/{2}
        \bigg)
        \Vert\hat\theta_k\Vert^2 
        \\
        &- \underbrace{
        \sum_{j\in\mathcal{A}\setminus \{\theta_i\}_{i\in[0,\cdots,k]}}\lambda_j\hat\theta_k^T{\partial c_j\over\partial \hat\theta_k}
        }_{>0, \text{\;by Lemma} \ref{lem1} \text{\;and\;} \text{Assumption} \ref{assum2}}	
        \\
        \le&
        \bigg(
            -{\lambda_\text{min}(Q)}/{2}+{\bar M}/{2}
        \bigg)
        \Vert\xi\Vert^2
        +\bar \Delta \Vert \xi\Vert 
        \\&
        + 
        \bigg(
            -2\lambda _{\theta_k}+{\bar M}/{2}
        \bigg)
        \Vert\hat\theta_k\Vert^2 
    \end{aligned}
    \label{eq. dot Vk 2}
\end{equation}
%From \eqref{eq. dot Vk 2}, by defining $P=I_2$, if the control gains ${k_q}$ and ${k_z}$ are selected sufficiently large such that
Define $P=I_2$, leading to $Q = -A_{\xi}^T - A_{\xi}$. Consequently, the minimum eigenvalues ${\lambda_{\text{min}}(Q)}$ is determined by $2\min({k_q},{k_z})$, as follows from the structure of the matrix $A_{\xi}$. From \eqref{eq. dot Vk 2}, if the control gains ${k_q}$ and ${k_z}$ are chosen sufficiently large to satisfy the condition:
%is a function of $k_q$ and $k_z$, as per the definition of matrix $A_{\xi}$. From \eqref{eq. dot Vk 2}, if the control gains ${k_q}$ and ${k_z}$ are chosen sufficiently large such that
\begin{equation}
    % -\lambda_\text{min}(Q)/2+M/2<0
    \min({k_q},{k_z})>\bar M/2
    \label{eq. ctrl stable condition}
\end{equation}
and if the Lagrange multiplier $\lambda_{\theta_k}$ for the weight norm constraint of the $k\textsuperscript{th}$ layer is increased sufficiently, such that
\begin{equation}\label{eq: lambda bk}
    -2\lambda_{\theta_k} +{\bar M/ 2}<0,  
\end{equation}
(as dictated by \eqref{eq. adaptation law L} when the corresponding constraint is violated, i.e., $c_{\theta_k}=\Vert \hat\theta_k\Vert^2 -\bar\theta_k^2 > 0$), then both $\xi$ and $\hat\theta_k$ will remain bounded within the compact sets $\Theta_\xi$ and $\Theta_{\hat\theta_k}$, defined as
\begin{equation}
    \Theta_\xi = 
    \bigg\{ \xi \ \bigg\vert\ \Vert\xi\Vert \le  
    {2\bar \Delta\over \lambda _\text{min}(Q)-\bar M} 
    \bigg\}
\end{equation}
and
\begin{equation}\label{eq: hat theta k bnd}
    \Theta_{\hat\theta_k} = 
    \{
    \hat\theta_k 
    \ 
    \vert
    \ 
    \Vert
    \hat\theta_k\Vert \le  
    \bar\theta_k
    \}
    .
\end{equation}
The increase of the Lagrange multiplier $\lambda_{\theta_k}$ will halt once $\hat \theta_k$ reaches the compact set $\Theta_{\hat\theta_k}$. Thus, the Lagrange multiplier $\lambda_{\theta_k}$ is bounded.
% Note that the compact set $\Theta_{\hat\theta_k}$ implies that the input norm constraint for the last $k\textsuperscript{th}$ layer is satisfied because the condition \eqref{eq: lambda bk} is fulfilled in the case of constraint violation.

%Note that $\Theta_{\tilde\theta_k}$ converges to $\{\tilde\theta_k\  \vert \ \Vert\tilde\theta_k\Vert\le\bar\theta_k\}$, if $\lambda_{b,k}$ increases such that $4\lambda_{b,k} \gg  \bar M_k$.

% To analyze the boundedness of the Lagrange multipliers, let $\mathcal V_2$ be defined as

% \begin{figure}[!t]
%     \centering
%     \includegraphics[width=0.7\linewidth]{lyapunov.drawio.png}
%     \caption{caption.}
%     \label{fig: V space}
% \end{figure}

The boundedness of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal A\setminus\{\theta_i\}_{i\in[0,\cdots,k]}$, can be accessed by considering the convexity of the constraints in $\hat\theta_k$-space.
The boundedness of the remaining Lagrange multipliers associated with the weight norm constraints, $\lambda_{\theta_r},\ \forall r\in[0,\cdots,k-1]$, will be examined in Step $i$. Based on Assumption \ref{assum1} and Lemma \ref{lem1},  
%(i.e., the constraint is convex on $\tau$-space and $\hat\theta_k$-space, including the origin), 
the equality constraints $c_j \le 0, \ \forall j\in\mathcal A\setminus \{\theta_i\}_{i\in[0,\cdots,k]}$, formconvex sets $\Theta_{c_j}$ in $\hat\theta_k$-space.
Let $\Theta_c\triangleq \cap_{j\in\mathcal A\setminus \{\theta_i\}_{i\in[0,\cdots ,k]}} \Theta_{c_j}$ represent the intersection of these convex sets, which also contains the origin.
If $\lambda_j$ increases sufficiently such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal A\setminus \{\theta_i\}_{i\in[0,\cdots,k]}}\lambda_j\hat\theta_k^T(\partial c_j/\partial \hat\theta_k)<0$, then ${\mathcal V}$, and consequently $\Vert\hat\theta_k\Vert$, will decrease until $\hat\theta_k$ reaches $\Theta_\xi\cap\Theta_{\hat\theta_k}\cap\Theta_c$. Once $\hat\theta_k$ hits the boundary of $\Theta_c$, the Lagrange multipliers will cease to increase, thus ensuring their boundedness.

% To analyze the boundedness of the Lagrange multipliers, assume that $\lambda_j$ dominantly increased such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal{A}-\{\theta_k\}}\lambda_j\hat\theta_k^T(\partial c_j/\partial \hat\theta_k)<0$. Then $\hat\theta_k$ approaches into $\Theta_\xi\cap\Theta_{\hat\theta_k}\cap\Theta_\gamma$. It means that the Lagrange multipliers are bounded satisfying the constraints.

%  subset of $\hat\theta_k$ which satisfy the constraints in $\mathcal A$, can be represented as 
% \begin{equation*}
%    \Theta_\gamma=
%    \{
%        \hat\theta_k
%        \ \vert\ 
%        \Vert\hat\theta_k\Vert
%        \le \gamma
%    \}
% \end{equation*}
% where $\gamma \le \bar\theta_k$, since if $\gamma$ is greater than $\bar\theta_k$, the constraint can be handled by $c_{\theta_k}$. %, as shown in Fig~\ref{fig: V space}.

%To analyze the Lagrange multipliers, assume that the Lagrange multipliers are increased such that
% \begin{equation*}
%    \dot V \le - \underbrace{
%     \sum_{j\in\mathcal{A}-b_k}\lambda_j\tilde\theta_k^T\nabla c_{j,k}
%     }_{>0}	\le -\gamma_k <0
% \end{equation*}
%with $\gamma_k\in\mathbb R_{>0}$.
%It imples that there is a finite time $t_f$ for $\hat\theta_k$ to converge to the point that satisfies the every constraint, while approaching to the $\theta^*$.
%When the constraints are satisfied, the reminders of the multipliers in $\mathcal A$ converges.

\subsection*{Step i: Boundedness of $\hat\theta_i$ and $\eta_i, \ i\in[k-1,\cdots,0]$}
 % \subsubsection*{Step i: Boundedness of $\hat\theta_i,\eta_i,\ i\in[k-1,\cdots,0]$}

% Following facts
% \begin{equation}
%     {\partial \hat\Phi\over \partial \hat\theta_i} = V_k^T  \phi'_k \cdots V_{i+1}^T  \phi'_{i+1} (I_{l_{i+1}}\otimes \phi^T  _{i})
% \end{equation}

The boundedness of the Frobenius norm of the gradient $\partial\hat\Phi/\partial \hat\theta_i$ can be obtained from its definition in \eqref{eq. nabla phi}. This relies on the fact that the boundedness of $\Vert\hat\theta_i\Vert,\ \forall i\in[k,\cdots,i+1]$, was already shown in the previous step (i.e., Step 1 to Step $i+1$) and the activation functions $\hat\phi_i$ and their derivative $\hat\phi_i'$ are bounded.

The dynamics of $\eta_i$ and $\hat\theta_i$ for all $i\in [k-1,\cdots,0]$ are represented as
\begin{equation*}
    \dot\eta_i = 
    A_\xi\eta_i -B_\xi {\partial h\over\partial\tau}
    {\partial \hat\Phi\over \partial \hat\theta_i}
\end{equation*}
and
\begin{equation*}
    \begin{aligned}
        \dot{\hat\theta}_i 
        =&
        -\alpha 
        \bigg[
            \eta_i^TW\xi+2\lambda_{\theta_i} \hat\theta_i
            +
            \sum_{j\in\mathcal{A}\setminus \{\theta_i\}_{i\in[0,\cdots,k]}}\lambda_j{\partial c_j\over\partial \hat\theta_i}
        \bigg].
    \end{aligned}
\end{equation*}
According to \cite[Chap.~4 T.~1.9]{RN13}, $\Vert\eta_i\Vert_F$ is bounded because $A_\xi$ is a stable matrix and the terms $\Vert B_\xi\Vert, \Vert(\partial h/\partial \tau)\Vert_F$, and $\Vert\partial \hat\Phi/\partial\hat\theta_i\Vert_F$ are bounded.
When $\lambda_{\theta_i}$ is generated due to a violation of the weight norm constraint, $\hat\theta_i$ remains bounded because the term $-2\alpha\lambda_{\theta_i}$ is stable, and the residual terms $\Vert\eta_iW\xi\Vert$, $\lambda_j$, and $\Vert(\partial c_j/\partial \hat\theta_i)\Vert_F$ for all $j\in\mathcal{A}\setminus \{\theta_i\}_{i\in[0,\cdots,k]}$ are bounded, as demonstrated in Step 1 and by Lemma \ref{lem2}.
The boundedness of each $\lambda_{\theta_i}$ also can be obtained, assuming that $\lambda_{\theta_i}$ is sufficiently increased regulating $\Vert\theta_i\Vert$ into the origin until $c_{\theta_i}$ is satisfied.

Therefore, starting from the boundedness of $\xi$, $\hat\theta_k$, and $\eta_k$ in the $k\textsuperscript{th}$ layer, the boundednesses of $\hat\theta_i$ and $\eta_i$ for the remaining layers $i\in[0,\cdots,k-1]$ can be established recursively, down to the input layer ($i=0$). Thus, $\hat\theta$, $\xi$, and $\eta$ are bounded because $\hat\theta_i,\eta_i,\ \forall i\in[0,\cdots,k]$ and $\xi$ are bounded. Furthermore, since the estimated weight vector $\hat\theta$ is bounded, the weight estimation error $\tilde\theta$ is also bounded, as $\theta^*$ is bounded according to the universal approximation theorem.

\end{proof}

%  SECTION SIMULATION ======================================
\section{Simulation}\label{sec:sim}

\subsection{Setup}

The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{RN32}. 
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$, and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
%This model contains terms of gravity and friction in its mechanical system.
%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
%and can be considered as the disturbance of the system.
The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for ${q}=[q_1,q_2]^T$ was defined as
\begin{equation*}
    {q_d}(t) = 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    =
    \begin{bmatrix}
        +\cos(0.5\pi t) + 1 \\
        -\cos(0.5\pi t) - 1 
    \end{bmatrix}.
\end{equation*}
%\color{red}
%Considering the power limitation of the power source for the actuators [], 
The control input saturation function was defined as $h(\tau)\triangleq \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{RN28} and is given by
\begin{equation}
    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
    \label{eq. h func}
\end{equation}
with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.

In addition to this physically imposed control input saturation, the input norm constraint \eqref{eq. cstr input ball} was imposed to ensure that the control input $\tau$ stays within the unsaturation region of $h(\tau)$ and to prevent inefficient use of the input. With a sufficiently large value for $p$, the input norm constraint essentially matches the control input saturation function. Note that among the selected controllers given below, only the proposed CoNAC can rigorously handle this input norm constraint.

% **********************************************************
% SYSTEM FIGURE AND TABLE
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \label{table: error norm}
    \centering
    \begin{tabular}{|c||c|c|c|c|}
    \hline
    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline 
    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
    \hline
    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{fig13.eps}
    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
    \label{fig: h func}
\end{figure}

% SYSTEM FIGURE AND TABLE
% **********************************************************
Four controllers were examined for a comparative study. The first was the Backstepping Controller (BSC), used as the baseline. The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro‒adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC. While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints. The third was DNN-BSC augmented with an auxiliary system presented in \cite{RN55, RN56, RN3} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint. As a result, an approximation of the input norm constraint was used as an input bound constraint. Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework. The properties of these four controllers are summarized in Table \ref{table:controller}.
%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{|c||c|c|c|}
    \hline
    & \multicolumn{3}{c|}{Handling Capability}\\
    \hline
    & System & Weight Norm & Input Norm\\
    &  Uncertainty & Constraint & Constraint\\
    \hline 
    BSC     & X & X & X\\
    \hline
    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
         &  & (by projection) & \\
    \hline
    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
       &  & (by projection) &  (by aux. system)\\
       % &  & & linearized constraint)\\
    % \hline
    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
    %    &  & (by projection) &  system for \\
    %    &  & & linearized constraint)\\
    \hline
    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
         &  & (by optimization) & (by optimization)\\
    \hline
    \end{tabular}
\end{table}

% \begin{table}
% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
% \centering
% {\begin{tabular}{cc}\textcolor{black}ine
% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
% Rated power & 3 kW\\
% Rated speed & 4500 RPM\\
% Rated torque & 6.4 Nm\\
% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
% $I_{max}$ & 15 A \\
% $V_{dc}$ & 100 V\\
% $R_s$ & 0.34 $\Omega$\\
% $P$ & 3\\
% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
% \multirow{2}{*}{Controller} & TMS320F28377D\\
% & (Texas Instrument) \\
% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
%  & (Infineon Technologies)
% \\\textcolor{black}ine
% \end{tabular}}
% \end{table}

% \begin{table}[!t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Common Parameters of Selected Controllers.}
%     \label{table: error norm}
%     \centering
%     \begin{tabular}{|c||c|c|c|c|c|c|}
%     \hline
%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
%     \hline 
%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
%     \hline
%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
%     \hline
%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
%     \hline
%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
%     \hline
%     \end{tabular}
%     \label{table: control parameters}
% \end{table}

% **** CM1,2 control law *****
The BSC used the control law defined in \eqref{eq. desired control} with $\hat f=[0,0]^T$. Since BSC did not consider the unknown system dynamics, the approximation term $\hat f$ was set to zero.
%CM1 has the following control gains and design parameters: $k_s=5,{k_z}=5, M_0=I_2, C_0=I_2, G_0=[0,0]^T  $.
% Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^T$. 
The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN i.e., $\hat f\approx \hat\Phi$. The adaptation law for DNN-BSC, as presented in \cite{RN16}, was defined by 
\begin{equation}\label{eq:projection}
\dot {\hat\theta}= \text{Proj}_{\Omega}[\alpha  (\partial \hat\Phi/\partial \hat\theta)M_0^{-1}{\tilde z}],
\end{equation}
where $\text{Proj}_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{RN20}, which projects an input vector onto a convex set $\Omega$. The convex set was defined as ${\Omega}\triangleq \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i\triangleq \{\hat\theta_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq. cstr weight ball}.
% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\text{Proj}_\Omega(\cdot)$ projects to the convex set, (i.e., the constraints are generally non-convex on the $\hat\theta$-space.).
% **** CM3 control law *****

The control law for DNN-BSC-A was the same as DNN-BSC, but with an auxiliary system to compensate for control input violations. Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq. cstr input ball}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq. cstr input saturation} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$. The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
%considering $h(\cdot)$, saturated control input is defined as $s(\tau)\triangleq \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\mathbb{R}^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} = 
\tau_{(i)}-\text{sat}(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
% s(\tau)-\tau$.
The auxiliary state variables were used in the adaptation law \eqref{eq:projection} by substituting ${\tilde z}$ with ${\tilde z}+\zeta$.

% **** CoNAC control law *****
The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq. approximated control}. The update rates for the multipliers were set as $\beta_{j}=0.1$. The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.

For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, i.e., $q_{NN}=[{q_d}^T,1]^T$ with the augmented scalar 1 included to account for the bias term in the weight matrix. 
Each DNN architecture had two hidden layers with eight nodes (i.e., $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$. The constraint parameters were $\bar\theta_0=20, \bar\theta_1=30, \bar\theta_2=40$, and $\bar\tau = 50$ (from Eq. \eqref{eq. h func}). The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^T$.
The sampling time of the simulations was selected as $T_s=10^{-4}$.
% The same values were assigned across all the controllers for the common parameters for a fair comparison.
% The other parameters for CM1 to CoNAC were selected as listed in Table.~\ref{table: control parameters}. The same values were assigned across all the controllers for the common parameters for a fair comparison.

% **********************************************************
% SIMULATION FIGURES
\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig1.eps}%
        \label{fig: tracking_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig2.eps}%
        \label{fig: tracking_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig3.eps}%
        \label{fig: tracking_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig4.eps}%
        \label{fig: tracking_CoNAC}}
    \caption{Comparison of the tracking performance across the selected controllers.}
    \label{fig: tracking}
\end{figure*}

\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig5.eps}%
        \label{fig: control_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig6.eps}%
        \label{fig: control_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig7.eps}%
        \label{fig: control_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig8.eps}%
        \label{fig: control_CoNAC}}
    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
    \label{fig: control}
\end{figure*}

\begin{figure}[!t]
    \centering
    {\includegraphics[width=0.9\linewidth]{fig16.eps}
    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
    \label{fig: ball control}}
\end{figure}

\begin{figure*}[!t]
    \centering
        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig12.eps}%
        \label{fig: multiplier_CoNAC}}
    \hfill
        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig9.eps}%
        \label{fig: weight_CM2}}
    \vfill
        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig10.eps}%
        \label{fig: weight_CM3}}
    \hfill
        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig11.eps}%
        \label{fig: weight_CoNAC}}       
    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
    \label{fig: weight and multiplier}
\end{figure*}
% SIMULATION FIGURES
% **********************************************************

\subsection{System Uncertainty Handling}

The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties. As a result,
%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
%the parameters of CM1 are poorly tuned, 
BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.

By leveraging the DNN to compensate for the lumped system uncertainty within the BSC, DNN-BSC achieved improved tracking performance compared to BSC, as seen in Fig.~\ref{fig: tracking_CM2}. Fig.~\ref{fig: tracking_CM3} shows that DNN-BSC-A enhanced tracking performance for $q_2$, but tracking for $q_1$ remained unsatisfactory due to incomplete constraint handling, which will be discussed in detail in Section \ref{sec:sim_cnst}.
%By compensating the uncertain terms the control input of CM2 in Fig.~\ref{fig: control_CM2} is saturated.

Finally, CoNAC, which directly approximates the stabilizing control law along with the compensation term, demonstrated satisfactory tracking performance across both states, as illustrated in Fig.~\ref{fig: tracking_CoNAC}.

\subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}

The resulting control input $\tau$ and physically saturation control input $h(\tau)$ for the selected controllers are shown in Fig.~\ref{fig: control}. As illustrated in Fig.~\ref{fig: control_CM1}, BSC did not violate the input norm constraint (i.e., $\tau = h(\tau)$). However, in DNN-BSC, the added compensation term from the DNN caused violations of the input norm constraint (i.e., $\tau > h(\tau)$) at several points; see Fig.~\ref{fig: control_CM2}. This failure to account for the input norm constraint led to oscillations in the control input $\tau$. The DNN adaptation process attempted to increase the weights to reduce the residual errors that were not constrained by saturation, but after saturation ceased, the control input had to rapidly adjust back to realistic levels, leading to oscillatory behavior. Such high-frequency oscillations may induce instability in the control system or cause fatigue in the actuators.

On the other hand, both DNN-BSC-A and CoNAC successfully handled their imposed input constraints, as shown in Fig.~\ref{fig: control_CM3} and Fig.~\ref{fig: control_CoNAC}, respectively, without causing notable oscillations in the control input $\tau$ even after the input constraint was activated. However, the tracking performance of DNN-BSC-A was lower than that of DNN-BSC and CoNAC, as the auxiliary system used in DNN-BSC-A approximated the input norm constraint with an input bound constraint, creating a rectangular constraint in the $\tau$-space (see Fig.~\ref{fig: ball control}). In contrast, CoNAC satisfied the nonlinear input norm constraint and produced the physically maximum control input, resulting in improved tracking performance.

It is also important to note that the control input trajectory in DNN-BSC-A depends on the dynamics of the auxiliary system. The auxiliary system regulates the violated control input after sufficient auxiliary state $\zeta$ is generated to compensate for the violation. This can be observed in Fig.~\ref{fig: ball control}, where DNN-BSC-A exhibited minor violations of the input bound constraint. In contrast, CoNAC satisfied the constraint without being affected by such dynamics, as its Lagrange multiplier adjusted as soon as the constraint was violated.

%Meanwhile, CM2 and CM3 is based on BSC, and the desired controller $\tau^*$ of CoNAC is based on the BSC which may produce larger control input by canceling the stabilizing system dynamics.
%Therefore, CM2, CM3, and CoNAC produced the saturated control input.
%These control results show why the control saturation should be handled.

\subsection{Weight Norm Constraint Handling}

The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}. All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.

IN DNN-BSC, as shown in Fig.~\ref{fig: weight_CM2}, the weight norm of the last layer (i.e., $\Vert {{{\hat \theta }_2}} \Vert$) fluctuated significantly over time, proportional to the control input norm. This is because the last layer’s weights directly determine the control input. When the control input violated the input norm constraint, the last layer’s weight norm hit the boundary and stayed there due to the projection operator. However, the projection operator only responded to violations without considering optimality or behavior.
%In the case of CM2 which does not consider the control input constraint, the weight norm of the last layer reaches the maximum weight norm value, when the control is saturated.
%It is because the weights get increased to produce larger control input to reduce the tracking error of $q_2$. (i.e., the maximum magnitude of the control input depends on the weight norm of the last layer, since the activation function is bounded.)

In DNN-BSC-A, none of the weight norms reached their boundaries, as shown in Fig.~\ref{fig: weight_CM3}. This was due to the auxiliary system, where the auxiliary state $\zeta$ reduced the control input, ensuring it stayed within the input constraint.

In CoNAC, all weight norms complied with the imposed constraints through the constrained optimization approach, as illustrated in Fig.\ref{fig: weight_CoNAC}. When any weight norm approached its upper limit, the Lagrange multiplier was promptly activated to steer the weight adaptation direction towards a constraint-satisfactory point (see Fig.\ref{fig: multiplier_CoNAC}). Notably, the weight norms of the first and second layers ($\Vert {{{\hat \theta }_0}} \Vert$ and $\Vert {{{\hat \theta }_1}} \Vert$) remained nearly constant throughout the control period. The weight norm of the last layer $\Vert {{{\hat \theta }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint. This quasi-static behavior of the weight norm (i.e., $d{\hat\theta}/dt=-\alpha\partial L/\partial \hat\theta \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (i.e., $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC. However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds. This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
%(i.e., $\partial J/\partial\hat\theta = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\hat\theta} c_j)$.
%, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.

The overall weight norms of CoNAC were larger than those of DNN-BSC and DNN-BSC-A, since CoNAC approximated the entire stabilizing control law, whereas DNN-BSC and DNN-BSC-A only approximated the system uncertainty term within the BSC framework.

%Because the simulation is implemented in a digital computer, the multipliers repeat to disappear and be generated, since the constraints are satisfied and violated in the digital process.

%\subsection{Analysis of the Neural Network}

%Generally, the existing literature states that the maximum norms of the weights should be sufficiently large (i.e., $\bar\theta_i \gg 0$) since the designer does not know where the global optimal point of the weights is.
%However, using the physical prior knowledge of the system, one can guess the proper value of the maximum norm, since the magnitude of the control input depends on the last layer's weights due to the bounded activation function.
%Furthermore, the simulation study shows that the selected controllers have sufficiently good performances with the small maximum weight norms.
%It means that the local optimal point of the weights are more effective for the stability analysis and the limitating the control input's amplitude.

%Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
%However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}. (i.e., the weight updates are smaller as its layer is closer to the input layer.)
%To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.

%  SECTION CONCLUSION ======================================
\section{Conclusion}\label{sec:conclusion}

This paper presented a constrained optimization-based neuro‒adaptive controller (CoNAC) for the uncertain Euler‒Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework. The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.

The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds. By formulating these constraints as part of the optimization process, CoNAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.

Simulation results validated the superior performance of CoNAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A. CoNAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.

Future work may extend this approach to address constraints on both the system inputs and states, further enhancing the flexibility and robustness of neuro‒adaptive control systems using constrained optimization.

%  SECTION APPENDIX ======================================
%  \appendices

% \section{Proof of Lemma \ref{lem1}}\label{sec:proof lem1}

% Let $\omega^*\triangleq [\theta_k^{*T}; [\hat\theta_i]_{i\in[0,\cdots,k-1]}]$ and $\hat\omega\triangleq [\hat\theta_k^{T}; [\hat\theta_i]_{i\in[0,\cdots,k-1]}]$. 
% If the Assumption \ref{assum1} holds (i.e., $c(\omega^*)<0,c(\hat\omega)\ge 0$), then $\nabla c_{j,k}^T\hat\theta_k>0$ also implies $\nabla c_{j,k}^T\tilde\theta_k>0$, as demonstrated by the following analysis: 
% \begin{equation}
%     \begin{aligned}
%         -\nabla c_{j,k}^T \tilde\theta_k=&\nabla c_{j,k}^T(\theta_k^*-\hat\theta_k)
%         =
%         {d\over d\delta } c_j(\hat\omega +\delta (\omega^*-\hat\omega))\bigg\vert _{\delta=0} \\
%         =& \lim_{\delta\to 0} {c_j(\hat\theta-\delta(\omega^*-\hat\omega)) + c_j(\hat\omega)\over \delta}\\
%         \le& \lim_{\delta\to0} {\delta c_j(\omega^*) + (1-\delta) c_j(\hat\omega)-c_j(\hat\omega)\over \delta}
%         \\
%         =& c_j(\omega^*) - c_j(\hat\omega) < 0
%         \end{aligned}
% \end{equation}

% It follows that $\nabla c_{j,k}^T\hat\theta_k>0$ holds for all the constraints introduced in Section \ref{sec:cstr candidates}.

% \section{Details of CM3}\label{sec:detail CM3}

% As motivated by 
% \color{red}
% \cite{RN111}-\cite{RN110}
% \color{black}
% , the auxiliary system is introduced to compensate the control input saturation, as
% \begin{equation}
%     \dot \zeta  = 
%     \begin{cases}
%         -K_\zeta \zeta - 
%         \bigg({
%         \vert {\tilde z}^TM_0^{-1}k_\zeta\Delta\tau\vert +0.5k_\zeta^2\Delta \tau^T\Delta \tau
%         \over
%         \Vert\zeta\Vert^2
%         }\bigg)
%         \zeta
%         +
%         k_\zeta
%         \Delta \tau,
%         \\
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad\quad

%         \Vert \zeta\Vert \ge \mu
%         \\
%         -K_\zeta \zeta+ k_\zeta\Delta \tau, 
%         \quad\quad\quad
%         \quad\quad\quad
%         \quad\quad\quad\ 
%         \Vert\zeta\Vert < \mu
%     \end{cases}
%     \label{eq. aux system}
% \end{equation}
% where $\zeta$ denotes the auxiliary state variables, $\Delta\tau \triangleq h(\tau) - \tau$, $\mu\in\mathbb R_{>0}$ is a positive constant, and $K_\zeta=K_\zeta^T>0$.
% To scale the difference of the magnitude between ${\tilde z}$ and $\Delta\tau$, $k_\zeta\in\mathbb R_{>0}$ is used.

% Let the control law be defined as 
% \begin{equation}
%     \tau =-{k_z}M_0{\tilde z}-M_0K_p \zeta -M_0{\tilde q}+C_0{z}+G_0-\hat f+M_0 \dot {z^*}
%     \label{eq: control law CM3}
% \end{equation}
% where $K_p$ denotes the gain matrix.
% Then the system is bounded with the following criteria: ${k_q} > 0, {k_z} >1/2, k_\zeta>1, \mu>1, K_p > 0, K_\zeta >{1\over 2}(K_p^TK_p+I),\dot{\hat\theta } = \text{Proj}_{\Omega}[\alpha\nabla\hat\Phi^T{M^{-1}}^{T} {\tilde z}]$.
% The proof of the boundedness can be readily obtained using the Lyapunov function $V=(1/2){\tilde q}^T{\tilde q}+(1/2){\tilde z}^T{\tilde z}+(1/2\alpha)\tilde\theta^T\tilde\theta + (1/2)\zeta^T\zeta$.

%  BIBLIOGRAPHY ============================================
\bibliographystyle{ieeetr}
\bibliography{refs}

\end{document}

### 2024-12-15 src/H_main_plotter.m

@@ -1,0 +1,880 @@
+clear
+clc
+
+%%
+FIGURE_PLOT = 1;
+% SAVE_FLAG = 1;
+SAVE_FLAG = 1;
+POSITION_FLAG = 1; % it will plot fiugures in the same position
+
+addpath("InpSatFunc/")
+
+%% DATA LOAD
+% group1 = 1;
+% group2 = 2;
+% group3 = 3:7;
+% group4 = 8:12;
+
+for c_idx = 1:1:4
+    fprintf("[INFO] Loading CTRL%d\n", c_idx);
+    ctrl_results.("ctrl"+string(c_idx)) = load( ...
+        "sim_result/CTRL"+string(c_idx)+"/CTRL" + string(c_idx) + "_result.mat" ...
+    );
+end
+c_list = get(gca,'colororder');
+
+group = [1 2 3 4];
+quantitive_report(ctrl_results, group);
+
+if ~FIGURE_PLOT
+    return
+end
+
+%% FIGURE NAMES
+fig_names = [
+    "fig1" %  state vs ref; CTRL1
+    "fig2" %  state vs ref; CTRL2
+    "fig3" %  state vs ref; CTRL3
+    "fig4" %  state vs ref; CTRL4
+    "fig5" %  control input; CTRL1
+    "fig6" %  control input; CTRL2
+    "fig7" %  control input; CTRL3
+    "fig8" %  control input; CTRL4
+    "fig9" %  weight ball; CTRL2
+    "fig10" %  weight ball; CTRL3
+    "fig11" %  weight ball; CTRL4
+    "fig12" %  multipliers; CTRL4
+    "fig13" %  saturation function
+    "fig14" %  total controls
+    "fig15" %  total trajectories
+    "fig16" %  control ball (focus)
+];
+
+% REPRESENTIVE CONTROLLER
+ctrl1_rep = ctrl_results.("ctrl"+string(group(1)));
+ctrl2_rep = ctrl_results.("ctrl"+string(group(2)));
+ctrl3_rep = ctrl_results.("ctrl"+string(group(3)));
+ctrl4_rep = ctrl_results.("ctrl"+string(group(4)));
+
+%% FIGURE 1~4: STATE vs REFERENCE
+figure(1); clf; 
+plot_ref(ctrl1_rep, POSITION_FLAG); 
+figure(2); clf;
+plot_ref(ctrl2_rep, POSITION_FLAG); 
[…]

### 2024-12-15 src/Simulink version/InpSatFunc/dfdx_11.m

@@ -1,0 +1,14 @@
+function dfdx_11 = dfdx_11(x1,x2)
+%DFDX_11
+%    DFDX_11 = DFDX_11(X1,X2)
+
+%    This function was generated by the Symbolic Math Toolbox version 9.2.
+%    12-Sep-2024 10:14:56
+
+t2 = x1.^2;
+t3 = x2.^2;
+t4 = t2+t3;
+t5 = t4.^50;
+t6 = t5./7.888609052210118e+169;
+t7 = t6+1.0;
+dfdx_11 = 1.0./t7.^(1.0./1.0e+2)-(t2.*t4.^49.*1.0./t7.^(1.01e+2./1.0e+2))./7.888609052210118e+169;

### 2024-12-15 src/Simulink version/InpSatFunc/dfdx_12.m

@@ -1,0 +1,13 @@
+function dfdx_12 = dfdx_12(x1,x2)
+%DFDX_12
+%    DFDX_12 = DFDX_12(X1,X2)
+
+%    This function was generated by the Symbolic Math Toolbox version 9.2.
+%    12-Sep-2024 10:14:56
+
+t2 = x1.^2;
+t3 = x2.^2;
+t4 = t2+t3;
+et1 = t4.^49.*x1.*x2.*1.0./(t4.^50./7.888609052210118e+169+1.0).^(1.01e+2./1.0e+2);
+et2 = -1.267650600228229e-170;
+dfdx_12 = et1.*et2;

### 2024-12-15 src/Simulink version/InpSatFunc/dfdx_21.m

@@ -1,0 +1,13 @@
+function dfdx_21 = dfdx_21(x1,x2)
+%DFDX_21
+%    DFDX_21 = DFDX_21(X1,X2)
+
+%    This function was generated by the Symbolic Math Toolbox version 9.2.
+%    12-Sep-2024 10:14:56
+
+t2 = x1.^2;
+t3 = x2.^2;
+t4 = t2+t3;
+et1 = t4.^49.*x1.*x2.*1.0./(t4.^50./7.888609052210118e+169+1.0).^(1.01e+2./1.0e+2);
+et2 = -1.267650600228229e-170;
+dfdx_21 = et1.*et2;

### 2024-12-15 src/Simulink version/demo1_plot.m

@@ -1,0 +1,258 @@
+function [] = demo1_plot(sim_result, nnOpt)
+
+%% FIGURE SETTING
+fig_names = [
+    "fig1 state vs ref"
+    "fig2 dot state vs ref"
+    "fig3 control input"
+    "fig4 weight ball"
+    "fig5 input ball"
+    "fig6 multipliers"        
+    "fig7 zeta"        
+    "fig8 zeta ball"        
+];
+
+fig_len = length(fig_names);
+
+%% PREPARE
+font_size = 12;
+line_width = 2;
+lgd_size = 8;
+
+%% DATA EXTRACTION
+t = sim_result.tout;
+
+x1 = signal2data(sim_result.logsout, "x1"); x1 = x1.Data;
+x2 = signal2data(sim_result.logsout, "x2"); x2 = x2.Data;
+xd1 = signal2data(sim_result.logsout, "xd1"); xd1 = xd1.Data;
+xd2 = signal2data(sim_result.logsout, "xd2"); xd2 = xd2.Data;
+
+r1 = signal2data(sim_result.logsout, "r1"); r1 = r1.Data;
+r2 = signal2data(sim_result.logsout, "r2"); r2 = r2.Data;
+rd1 = signal2data(sim_result.logsout, "rd1"); rd1 = rd1.Data;
+rd2 = signal2data(sim_result.logsout, "rd2"); rd2 = rd2.Data;
+
+u1 = signal2data(sim_result.logsout, "u1"); u1 = u1.Data;     
+u2 = signal2data(sim_result.logsout, "u2"); u2 = u2.Data;
+
+th = signal2data(sim_result.weights, "Weights"); th = th.Data;
+L = signal2data(sim_result.multipliers, "Multipliers"); L = L.Data;
+
+dot_L = signal2data(sim_result.dot_L, "dot_L"); dot_L = dot_L.Data;
+
+z1 = signal2data(sim_result.logsout, "zeta1"); z1 = z1.Data;
+z2 = signal2data(sim_result.logsout, "zeta2"); z2 = z2.Data;
+
+cstr = nnOpt.cstr;
+
+%% FIG.1: STATE vs REFERENCE
+figure(1); clf
+tl = tiledlayout(2, 1);
+
+nexttile
+p1 = plot(t, r1, "Color", "green", "LineWidth", line_width, "LineStyle", "-"); hold on
[…]

### 2024-12-15 src/Simulink version/demo1_src.m

@@ -1,0 +1,167 @@
+clear
+
+%% SIMULATION SETTING
+sim_name = "demo1.slx";
+T = 5;
+
+addpath("dynamics_model/");
+
+%% SYSTEM DECLARE
+[~, IC] = model1_load();
+% [r_f, rd_f, rdd_f] = ref1_load(); % sin func
+
+x0 = IC.x;
+
+%% ALGORITHM SELECTION
+% ctrl_name = "CTRL1"; % BSC
+ctrl_name = "CTRL2"; % Dixon
+% ctrl_name = "CTRL3"; % Dixon + Aux.
+% ctrl_name = "CTRL4"; % Proposed
+
+%% NN STRUCTURE
+nnOpt.init_range = 1e-3; % weight init range
+nnOpt.e_tol = 0; % error tolerance
+nnOpt.W = diag([1 1 1 1]); % error weight matrix
+
+%% CONTROLLER PARAMETERS
+nnOpt.ctrl_param.k1 = 50;
+nnOpt.ctrl_param.k2 = 50;
+
+nnOpt.ctrl_param.mu = 1e-1;
+zeta = rand(2,1) / norm(rand(2,1)) * sqrt(nnOpt.ctrl_param.mu) * 1.5;
+
+nnOpt.ctrl_param.Kp    = eye(2) * 1e0 * 2;
+nnOpt.ctrl_param.Azeta = eye(2) * 1e1 *0;
+% nnOpt.ctrl_param.Kp    = diag([1 0.1]) * 1e1 * 1;
+% nnOpt.ctrl_param.Azeta = diag([1 0.1]) * 1e0 * 5;
+nnOpt.ctrl_param.Bzeta = diag([1 1]) * 1e0 * 1;
+
+assert(nnOpt.ctrl_param.k2 > 1/2)
+% assert( all( ...
+%     eig(2*nnOpt.ctrl_param.Kzeta -nnOpt.ctrl_param.Kp'*nnOpt.ctrl_param.Kp-eye(size(nnOpt.ctrl_param.Kzeta))) > 0 ...
+%     ))
+
+nnOpt.ctrl_param.M = eye(2) * 1;
+nnOpt.ctrl_param.C = eye(2) * 1;
+nnOpt.ctrl_param.G = zeros(2,1);
+nnOpt.ctrl_param.inv_M = inv(nnOpt.ctrl_param.M);
+
+%% ALGORITHM PARAMETERS
[…]

### 2024-12-15 src/Simulink version/nn_V_norm_cal.m

@@ -1,0 +1,13 @@
+function Vn = nn_V_norm_cal(V, nnOpt)
+
+    Vn = zeros(nnOpt.l_size-1,1);
+
+    cumsum_V = [0;cumsum(nnOpt.v_size_list)];
+    for l_idx = 1:1:nnOpt.l_size-1
+        start_pt = cumsum_V(l_idx)+1;
+        end_pt = cumsum_V(l_idx+1);   
+
+        Vn(l_idx) = norm(V(start_pt: end_pt));
+    end
+    
+end

### 2024-12-15 src/dynamics_model/model1_load.m

@@ -1,0 +1,63 @@
+function [grad_x, IC] = model1_load()
+% The Cartesian Coordinates are ignored
+% x = [q1 q2 \dot{q1} \dot{q2}]
+
+%% INITIAL CONDITION
+% ********************************************************
+% IC.x = [1;-1;0;0];  
+IC.x = [2;-2;0;0];  
+IC.u = [0; 0];
+
+%% SYSTEM DYNAMICS
+% ********************************************************
+grad_x = @(q, u, t) model_wrapper(q, u, t);
+
+end
+
+%% Local function
+% ********************************************************
+function f = model_wrapper(q, u, t)
+    [M, C, G, F ] = model1(q, t);
+    
+    del_M = zeros(2,2); 
+    % del_C = [
+    %     tanh(q(1))*100
+    %     -tanh(q(2))*100
+    % ]; 
+    del_C = zeros(2,2); 
+
+    % del_G = rand(2,1)*1e0;
+    del_G = zeros(2,1);
+
+    M = M + del_M;
+    C = C + del_C;
+    G = G + del_G;
+
+    % d = [
+    %     tanh(q(1))*20 + sin(5*t)*3e1
+    %     -tanh(q(2))*20 + cos(5*t)*3e1
+    % ];
+    d = zeros(2,1);
+
+    f1 = q(3:4);
+    f2 = M \ (-C*q(3:4) -G -F +u +d);
+    
+    f = [f1 ; f2];
+end
+
+% function x = forward_kinematics(q, L1, L2)
+
+%     J = calculate_jacobian(q(1), q(2), L1, L2);
+%     x = [L1*cos(q(1)) + L2*cos(q(1) + q(2));
+%          L1*sin(q(1)) + L2*sin(q(1) + q(2));
+%          J * q(3:4)];
+% end
+
+% function J = calculate_jacobian(q1, q2, L1, L2)
+
+%     J = [(-L1*sin(q1) - L2*sin(q1 + q2)), -L2*sin(q1 + q2);
+%           (L1*cos(q1) + L2*cos(q1 + q2)),  L2*cos(q1 + q2)];
+% end
+
+
+

### 2024-12-15 src/main_plotter.m

@@ -1,0 +1,878 @@
+clear
+clc
+
+%%
+FIGURE_PLOT = 1;
+% SAVE_FLAG = 1;
+SAVE_FLAG = 1;
+POSITION_FLAG = 1; % it will plot fiugures in the same position
+
+addpath("InpSatFunc/")
+
+%% DATA LOAD
+% group1 = 1;
+% group2 = 2;
+% group3 = 3:7;
+% group4 = 8:12;
+
+for c_idx = 1:1:4
+    fprintf("[INFO] Loading CTRL%d\n", c_idx);
+    ctrl_results.("ctrl"+string(c_idx)) = load( ...
+        "sim_result/CTRL"+string(c_idx)+"/CTRL" + string(c_idx) + "_result.mat" ...
+    );
+end
+c_list = get(gca,'colororder');
+
+group = [1 2 3 4];
+quantitive_report(ctrl_results, group);
+
+if ~FIGURE_PLOT
+    return
+end
+
+%% FIGURE NAMES
+fig_names = [
+    "fig1" %  state vs ref; CTRL1
+    "fig2" %  state vs ref; CTRL2
+    "fig3" %  state vs ref; CTRL3
+    "fig4" %  state vs ref; CTRL4
+    "fig5" %  control input; CTRL1
+    "fig6" %  control input; CTRL2
+    "fig7" %  control input; CTRL3
+    "fig8" %  control input; CTRL4
+    "fig9" %  weight ball; CTRL2
+    "fig10" %  weight ball; CTRL3
+    "fig11" %  weight ball; CTRL4
+    "fig12" %  multipliers; CTRL4
+    "fig13" %  saturation function
+    "fig14" %  total controls
+    "fig15" %  total trajectories
+    "fig16" %  control ball (focus)
+];
+
+% REPRESENTIVE CONTROLLER
+ctrl1_rep = ctrl_results.("ctrl"+string(group(1)));
+ctrl2_rep = ctrl_results.("ctrl"+string(group(2)));
+ctrl3_rep = ctrl_results.("ctrl"+string(group(3)));
+ctrl4_rep = ctrl_results.("ctrl"+string(group(4)));
+
+%% FIGURE 1~4: STATE vs REFERENCE
+figure(1); clf; 
+plot_ref(ctrl1_rep, POSITION_FLAG); 
+figure(2); clf;
+plot_ref(ctrl2_rep, POSITION_FLAG); 
[…]

### 2024-12-15 src/main_var.m

@@ -1,0 +1,89 @@
+
+% ********************************************************
+%    * Optimization based Neuro Adaptive Controller *
+%
+%   Crafted By - Ryu Myeongseok
+%   Version 0.1
+%   Date : 2024.08.-  
+%
+% ********************************************************
+
+%% INITIALIZATION
+clear  
+clc
+
+addpath("dynamics_model/");
+addpath("utils/");
+addpath("utils_NN/");
+addpath("InpSatFunc/");
+
+%% SIMULATION SETTING
+dt = 1e-4;
+% T = 5;
+T = 10;
+% T = 15;
+% T = 200;
+t = 0:dt:T;
+rpt_dt = 1;
+
+
+FIGURE_PLOT_FLAG    = 0;
+ANIMATION_FLAG      = 0;
+AINMATION_SAVE_FLAG = 0;
+FIGURE_SAVE_FLAG    = 0;
+RESULT_SAVE_FLAG    = 1;
+
+%% CONTROLLER SETTING
+opts = readtable("ctrlOpts.csv",'delimiter', ',', 'TextType', 'string','ReadVariableNames',1, 'ReadRowNames', 1);
+
+num_ctrl = size(opts, 2);
+
+% CoNAC
+c_idx = 5;
+% p_list = linspace(1e-3, 1, 10);
+p_list = [0.001 0.445 1];
+
+% L2
+% c_idx = 6;
+% p_list = linspace(1e-3, 1, 10);
+% p_list = [0.001 0.445 1];
+
+% e_mod
+% c_idx = 7;
+% p_list = linspace(1e-3, 1, 10);
+% p_list = [0.001 0.445 1];
+
+Pi_list = zeros(3, length(p_list));
+Pi_list(1, :) = p_list;  
+
+for p_idx = 1:1:length(p_list)
+    seed = 10; rng(seed);
+    % ctrl_name = opts.Properties.VariableNames{c_idx};
+    ctrl_name = "CTRL"+string(c_idx)+"_"+string(p_idx);
+    [ctrlOpt, nnOpt] = opt_load(c_idx, opts, dt);
+
+    if c_idx == 5
+        nnOpt.beta = p_list(p_idx) * [1;1;0;0;0;0;0];
+    elseif c_idx == 6
+        nnOpt.L2 = p_list(p_idx);  
+    elseif c_idx == 7
+        nnOpt.rho = p_list(p_idx);
+    end
+
+    simulate
[…]

### 2024-12-15 src/test/aux_sat_test.m

@@ -1,0 +1,193 @@
+% ********************************************************
+%    * Optimization based Neuro Adaptive Controller *
+%
+%   Crafted By - Ryu Myeongseok
+%   Version 0.1
+%   Date : 2024.08.-  
+%
+% ********************************************************
+ 
+%% INITIALIZATION
+% ********************************************************
+clear  
+clc
+
+addpath("../dynamics_model/")
+%% SIMULATION SETTING
+% ********************************************************
+dt = 1e-4;
+% T = 0.01;
+T = 10;
+% T = 15;
+% T = 200;
+t = 0:dt:T;
+rpt_dt = 1;
+
+[grad_x, IC] = model1_load();
+[r_f, rd_f, rdd_f] = ref1_load(); % sin func
+
+%% INITIAL CONDITION
+% ********************************************************
+x = IC.x;
+u = IC.u;
+
+%% RECORDER
+% ********************************************************
+num_x = length(x); num_u = length(u);
+num_t = length(t);
+
+x_hist = zeros(num_x, num_t); x_hist(:, 1) = x;
+r_hist = zeros(num_x/2, num_t); r_hist(:, 1) = r_f(x,0);
+u_hist = zeros(num_u, num_t); u_hist(:, 1) = u;
+uSat_hist = zeros(num_u, num_t); uSat_hist(:, 1) = u;
+aux_hist = zeros(2, num_t); 
+
+k1 = 10; 
+k2 = 10;
+
+delta = 1e2;
+zeta = rand(2,1)/norm(rand(2,1))* sqrt(delta);
+pre_zeta = zeta;
+aux_hist(:, 1) = zeta;
+
+for t_idx = 2:1:num_t
+    
+    r1 = r_f(x, t(t_idx));
+    r1d = rd_f(x, t(t_idx));
+    r1dd = rdd_f(x, t(t_idx));
+  
+    % e = x-[r;rd];
+    e1 = r1 - x(1:2);
+    r2 = k1*e1 + r1d;
+    e2 = r2 - x(3:4);
+    e = [e1;e2];
+    r2d = r1dd + k1*(x(3:4) + r1d);
+       
+    M = eye(2);
+    C = eye(2);
+    G = zeros(2,1);
+    % k2 = 1e1;
+    
[…]

### 2024-12-15 src/test/opt_read_test.m

@@ -1,0 +1,93 @@
+clear
+
+opts = readtable("ctrlOpts.csv",'delimiter', ',', 'TextType', 'string','ReadVariableNames',0, 'ReadRowNames', 1);
+
+type_idx = find(opts.Properties.RowNames == "type");
+alg_idx = find(opts.Properties.RowNames == "alg");
+e_tol_idx = find(opts.Properties.RowNames == "e_tol");
+init_range_idx = find(opts.Properties.RowNames == "init_range");
+k1_idx = find(opts.Properties.RowNames == "k1");
+k2_idx = find(opts.Properties.RowNames == "k2");
+M_idx = find(opts.Properties.RowNames == "M");
+C_idx = find(opts.Properties.RowNames == "C");
+G_idx = find(opts.Properties.RowNames == "G");
+NN_size_idx = find(opts.Properties.RowNames == "NN_size");
+alpha_idx = find(opts.Properties.RowNames == "alpha");
+rho_idx = find(opts.Properties.RowNames == "rho");
+beta_idx = find(opts.Properties.RowNames == "beta");
+V_max_idx = find(opts.Properties.RowNames == "V_max");
+U_max_idx = find(opts.Properties.RowNames == "U_max");
+U_min_idx = find(opts.Properties.RowNames == "U_min");
+u_ball_idx = find(opts.Properties.RowNames == "u_ball");
+Azeta_idx = find(opts.Properties.RowNames == "Azeta");
+Bzeta_idx = find(opts.Properties.RowNames == "Bzeta");
+
+c_idx = 1;
+
+type = opts{type_idx, c_idx};
+
+if strcmp(type, "CTRL1") % BSC
+    ctrlOpt.k1 = str2num(opts{k1_idx, c_idx});
+    ctrlOpt.k2 = str2num(opts{k2_idx, c_idx});
+
+    ctrlOpt.M = str2num(opts{M_idx, c_idx});
+    ctrlOpt.C = str2num(opts{C_idx, c_idx});
+    ctrlOpt.G = str2num(opts{G_idx, c_idx});
+
+elseif strcmp(type, "CTRL2") % BSC + Dixon
+    nnOpt.e_tol = str2num(opts{e_tol_idx, c_idx});
[…]

### 2024-12-15 src/utils/animate.m

@@ -1,0 +1,94 @@
+
+figure(7); clf
+
+L1 = .45;            
+L2 = .45;
+
+accel = 100;
+
+if AINMATION_SAVE_FLAG
+    v = VideoWriter("sim_result/"+ctrl_name, 'MPEG-4');
+    % v.Quality = 100;
+    v.FrameRate = 1/dt/accel; 
+    open(v);
+end
+
+for t_idx = 1:accel:num_t
+    clf
+
+    q1 = x_hist(1, t_idx); q2 = x_hist(2, t_idx);
+    r1 = r_hist(1, t_idx); r2 = r_hist(2, t_idx);
+
+    plot( ...
+        L1* [0 cos(r1), cos(r1)+cos(r1+r2)], ...
+        L1* [0 sin(r1), sin(r1)+sin(r1+r2)], ...
+        "Color", "red", ...
+        "LineStyle","-", ...
+        "Marker","o", ...
+        "LineWidth", line_width ...
+        ); hold on
+
+    plot( ...
+        L1* [0 cos(q1), cos(q1)+cos(q1+q2)], ...
+        L1* [0 sin(q1), sin(q1)+sin(q1+q2)], ...
+        "Color", "blue", ...
+        "LineStyle","-", ...
+        "Marker","o", ...
+        "LineWidth", line_width ...
+        ); hold on
+
+    % time 
+    text(-.95,+.8,0, ...
+        sprintf( ...
+            't [s]: %.2f\t/%.2f (%.1f%%) ', t(t_idx), T, round(t(t_idx)/T*100, 3) ...
+        ), ...
+        "FontSize", font_size, ...
+        "FontName", "Times New Roman" ...
+        );
+
+    xlabel("$x$", "Interpreter", "latex")
+    ylabel("$y$", "Interpreter","latex")
+    set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+
+    grid on
+    xlim([-1.2 1.2]);
+    ylim([-1.2 1.2]);
+    pbaspect([1 1 1])
+
+    % input ball
+    axes('Position',[.6 .22 .2 .2])
+    box on
+    ang = 0:0.01:2*pi;
+    shadow = max(1, t_idx-1e3:1:t_idx);
+    
+    plot(u_hist(1,shadow ), u_hist(2,shadow ), "color", 'red', "LineWidth", line_width, "LineStyle", "-"); hold on
[…]

### 2024-12-15 src/utils/plotter1.m

@@ -1,0 +1,197 @@
+
+%% FIGURE SETTING
+% ********************************************************
+fig_names = [
+    "fig1 state vs ref"
+    "fig2 dot state vs ref"
+    "fig3 control input"
+    "fig4 weight ball"
+    "fig5 input ball"
+    "fig6 multipliers & dot Lagrangian"        
+];
+
+fig_len = length(fig_names);
+
+%% FIG.1: STATE vs REFERENCE
+% ********************************************************
+figure(1); clf
+tl = tiledlayout(2, 1);
+
+nexttile
+p1 = plot(t, r1, "Color", "green", "LineWidth", line_width, "LineStyle", "-"); hold on
+p2 = plot(t, x1, "Color", "blue", "LineWidth", line_width, "LineStyle", "-."); hold on
+xlabel("Time $[\rm s]$", "Interpreter", "latex")
+ylabel("State 1 $[\rm rad]$", "Interpreter","latex")
+set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+grid on
+% ylim([min(r1) * 0.75, max(r1) * 1.25])
+% ylim([-0.5, 2.5])
+legend([p1, p2], ["$r_1$","$x_1$"], "Interpreter","latex", "FontSize", lgd_size, "FontWeight", "bold", "Location", "northwest")
+
+nexttile
+p1 = plot(t, r2, "Color", "green", "LineWidth", line_width, "LineStyle", "-"); hold on
+p2 = plot(t, x2, "Color", "blue", "LineWidth", line_width, "LineStyle", "-."); hold on
+xlabel("Time $[\rm s]$", "Interpreter", "latex")
+ylabel("State 2 $[\rm rad]$", "Interpreter","latex")
+set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+grid on
+% ylim([min(r2) * 1.25, max(r2) * 0.75])
+% ylim([-2.5, .5])
+legend([p1, p2], ["$r_2$","$x_2$"], "Interpreter","latex", "FontSize", lgd_size, "FontWeight", "bold", "Location", "northwest")
+
+%% FIG.2: DOT STATE vs REFERENCE
+% ********************************************************
+
+figure(2); clf
+tl = tiledlayout(2, 1);
+
+nexttile
[…]

### 2024-12-15 src/utils_NN/nn_init.m

@@ -1,0 +1,17 @@
+function nn = nn_init(nnOpt)
+
+    if strcmp(nnOpt.alg, "none")
+        nn.V = 0;
+        return
+    end
+
+    %% MATRICES PRE-ALLOCATION
+    nn.V = (rand(nnOpt.v_size,1)-1/2)*2*nnOpt.init_range;
+    nn.tape = zeros(nnOpt.t_size, 1);
+    
+    %% SENSITIVY INITIALIZATION (PROPOSED)
+    if strcmp(nnOpt.alg, "Proposed") || strcmp(nnOpt.alg, "L2") || strcmp(nnOpt.alg, "eMod")
+        nn.eta = zeros(nnOpt.NN_size(end)*2, nnOpt.v_size);
+    end
+
+end

### 2024-12-15 src/utils_NN/nn_nnGradient.m

@@ -1,0 +1,58 @@
+function total_grad = nn_nnGradient(nn, nnOpt)
+
+    %% PRE-ALLOCATION
+    total_grad = zeros(nnOpt.NN_size(end), nnOpt.v_size);
+    
+    %% 
+    pt_V = nnOpt.v_size;
+    pt_tape = nnOpt.t_size;
+
+    grad_to_back = 1;
+
+    %% BACKWARD (TOTAL NN GRDIENT CALCULATION)
+    for l_idx = flip(2:1:nnOpt.l_size)
+        l2 = nnOpt.NN_size(l_idx);        
+        l1 = nnOpt.NN_size(l_idx-1);        
+        
+        % pre_Phi
+        Phi = nn.tape(pt_tape-l1+1: pt_tape);
+        aug_phi = [tanh(Phi); 1];
+
+        % (I \otimes phi_k^T)
+        grad = kron(eye(l2), aug_phi');
+        if l_idx ~= nnOpt.l_size
+            n = l2+1; m = nnOpt.NN_size(l_idx+1);
+            % get phi_dot
+            phi_dot = tanh_dot(pre_Phi);
+            % get V weight
+            V = reshape(nn.V(pt_V-(n*m)+1: pt_V), n,m);
+            grad_to_back = grad_to_back * V'*phi_dot;
+
+            % pointer to next
+            pt_V = pt_V - (n*m);
+        end
+        grad = grad_to_back*grad;
+
+        % save to total grad
+        total_grad(:, pt_V-((l1+1)*l2)+1: pt_V) = grad;
+
+        % pointer to next
+        pt_tape = pt_tape - l1;
+
+        % for efficiency
+        pre_Phi = Phi;
+
+    end
+
+    %% ERROR CHECK
+    assert(pt_V == (nnOpt.NN_size(1)+1)*nnOpt.NN_size(2));
+    assert(pt_tape == 0);
+end
+
+%% LOCAL FUNCTIONS
+function phi_dot = tanh_dot(Phi)
+    phi_dot = zeros(length(Phi)+1, length(Phi));
+    for idx = 1:1:length(Phi)
+        phi_dot(idx,idx) = 1-tanh(Phi(idx))^2;
+    end
+end

### 2025-02-14 main.tex
Add public

--- 2024-12-15 tex/TNNLS24/main.tex
@@
 % code
-% MY PACKAGES ===================================
-\usepackage{epsfig}
-\usepackage{lipsum}  
-\usepackage{kotex}
-% \usepackage{natbib}
-\usepackage{cite}
-\usepackage{amssymb}
-\usepackage{xcolor}
-\usepackage{enumitem}
-\newlist{steps}{enumerate}{1}
-\setlist[steps, 1]{label = Step \arabic*: }
-\usepackage{hyperref}
-\hypersetup{
-    linkbordercolor=blue,
-    filebordercolor=red,
-    citebordercolor = green,      
-    urlbordercolor=red,
-    %
-    % colorlinks=true,
-    % linkcolor=blue,
-    % filecolor=blue,
-    % citecolor = blue,      
-    % urlcolor=cyan,
- }
- \usepackage{algorithm}
- \usepackage{svg}
-
-% MY PACKAGES ===================================
-
-\usepackage{amsmath,amsfonts}
-\usepackage{algorithmic}
-\usepackage{array}
-% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\usepackage{subfig}
-\usepackage{textcomp}
-\usepackage{stfloats}
-\usepackage{url}
-\usepackage{verbatim}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage{multicol}
+
+\input{dding_template/tex_packages/tex_packages_general.tex}
 
@@
     \centering
-    \includegraphics[width=0.7\linewidth]{Controller.drawio.png}
+    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
     \centering
-    \includegraphics[width=0.7\linewidth]{RobotModel.drawio.png}
+    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
     \centering
-    \includegraphics[width=0.9\linewidth]{fig13.eps}
+    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
     \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
@@
     \centering
-        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig1.eps}%
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
         \label{fig: tracking_CM1}}
     \hfill
-        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig2.eps}%
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
         \label{fig: tracking_CM2}}
     \vfill
-        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig3.eps}%
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
         \label{fig: tracking_CM3}}
     \hfill
-        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig4.eps}%
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
         \label{fig: tracking_CoNAC}}
@@
     \centering
-        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig5.eps}%
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
         \label{fig: control_CM1}}
     \hfill
-        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig6.eps}%
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
         \label{fig: control_CM2}}
     \vfill
-        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig7.eps}%
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
         \label{fig: control_CM3}}
     \hfill
-        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig8.eps}%
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
         \label{fig: control_CoNAC}}
@@
     \centering
-    {\includegraphics[width=0.9\linewidth]{fig16.eps}
+    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
     \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
@@
     \centering
-        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig12.eps}%
+        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
         \label{fig: multiplier_CoNAC}}
     \hfill
-        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig9.eps}%
+        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
         \label{fig: weight_CM2}}
     \vfill
-        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig10.eps}%
+        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
         \label{fig: weight_CM3}}
     \hfill
-        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig11.eps}%
+        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
         \label{fig: weight_CoNAC}}       
@@
 
-%  SECTION APPENDIX ======================================
-%  \appendices
-
-% \section{Proof of Lemma \ref{lem1}}\label{sec:proof lem1}
-
-% Let $\omega^*\triangleq [\theta_k^{*T}; [\hat\theta_i]_{i\in[0,\cdots,k-1]}]$ and $\hat\omega\triangleq [\hat\theta_k^{T}; [\hat\theta_i]_{i\in[0,\cdots,k-1]}]$. 
-% If the Assumption \ref{assum1} holds (i.e., $c(\omega^*)<0,c(\hat\omega)\ge 0$), then $\nabla c_{j,k}^T\hat\theta_k>0$ also implies $\nabla c_{j,k}^T\tilde\theta_k>0$, as demonstrated by the following analysis:
-% \begin{equation}
-%     \begin{aligned}
-%         -\nabla c_{j,k}^T \tilde\theta_k=&\nabla c_{j,k}^T(\theta_k^*-\hat\theta_k)
-%         =
-%         {d\over d\delta } c_j(\hat\omega +\delta (\omega^*-\hat\omega))\bigg\vert _{\delta=0} \\
-%         =& \lim_{\delta\to 0} {c_j(\hat\theta-\delta(\omega^*-\hat\omega)) + c_j(\hat\omega)\over \delta}\\
-%         \le& \lim_{\delta\to0} {\delta c_j(\omega^*) + (1-\delta) c_j(\hat\omega)-c_j(\hat\omega)\over \delta}
-%         \\
-%         =& c_j(\omega^*) - c_j(\hat\omega) < 0
-%         \end{aligned}
-% \end{equation}
-
-% It follows that $\nabla c_{j,k}^T\hat\theta_k>0$ holds for all the constraints introduced in Section \ref{sec:cstr candidates}.
-
-% \section{Details of CM3}\label{sec:detail CM3}
-
-% As motivated by 
-% \color{red}
-% \cite{RN111}-\cite{RN110}
-% \color{black}
-% , the auxiliary system is introduced to compensate the control input saturation, as
-% \begin{equation}
-%     \dot \zeta  = 
-%     \begin{cases}
-%         -K_\zeta \zeta - 
-%         \bigg({
-%         \vert {\tilde z}^TM_0^{-1}k_\zeta\Delta\tau\vert +0.5k_\zeta^2\Delta \tau^T\Delta \tau
-%         \over
-%         \Vert\zeta\Vert^2
-%         }\bigg)
-%         \zeta
-%         +
-%         k_\zeta
-%         \Delta \tau,
-%         \\
-%         \quad\quad\quad
-%         \quad\quad\quad
-%         \quad\quad\quad
-%         \quad\quad\quad
-%         \quad\quad\quad\quad
-
-%         \Vert \zeta\Vert \ge \mu
-%         \\
-%         -K_\zeta \zeta+ k_\zeta\Delta \tau, 
-%         \quad\quad\quad
-%         \quad\quad\quad
-%         \quad\quad\quad\ 
-%         \Vert\zeta\Vert < \mu
-%     \end{cases}
-%     \label{eq. aux system}
-% \end{equation}
-% where $\zeta$ denotes the auxiliary state variables, $\Delta\tau \triangleq h(\tau) - \tau$, $\mu\in\mathbb R_{>0}$ is a positive constant, and $K_\zeta=K_\zeta^T>0$.
-% To scale the difference of the magnitude between ${\tilde z}$ and $\Delta\tau$, $k_\zeta\in\mathbb R_{>0}$ is used.
-
-% Let the control law be defined as 
-% \begin{equation}
-%     \tau =-{k_z}M_0{\tilde z}-M_0K_p \zeta -M_0{\tilde q}+C_0{z}+G_0-\hat f+M_0 \dot {z^*}
-%     \label{eq: control law CM3}
-% \end{equation}
-% where $K_p$ denotes the gain matrix.
-% Then the system is bounded with the following criteria: ${k_q} > 0, {k_z} >1/2, k_\zeta>1, \mu>1, K_p > 0, K_\zeta >{1\over 2}(K_p^TK_p+I),\dot{\hat\theta } = \text{Proj}_{\Omega}[\alpha\nabla\hat\Phi^T{M^{-1}}^{T} {\tilde z}]$.
-% The proof of the boundedness can be readily obtained using the Lyapunov function $V=(1/2){\tilde q}^T{\tilde q}+(1/2){\tilde z}^T{\tilde z}+(1/2\alpha)\tilde\theta^T\tilde\theta + (1/2)\zeta^T\zeta$.
-
 %  BIBLIOGRAPHY ============================================

### 2025-03-11 manuscript.tex
first commit

--- 2024-12-15 tex/ECC25 /main.tex
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{RobotModel.drawio.png}
+    \includegraphics[width=0.8\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
     \centering
-    {\includegraphics[width=.85\linewidth]{BoxWhisker.drawio.png}}
+    {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
 \caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
@@
     \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig9.eps}%
+        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
         \label{fig: weight NAC-L2}}
     \vfill
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig10.eps}%
+        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
         \label{fig: weight NAC-eMod}}
     \vfill
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig8.eps}%
+        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
         \label{fig: weight NAC-CO}}
@@
     \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig6.eps}%
+        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
         \label{fig: error NAC-L2}}
     \vfill
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig7.eps}%
+        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
         \label{fig: error NAC-eMod}}
     \vfill
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig5.eps}%
+        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
         \label{fig: error NAC-CO}}
@@
     \centering
-    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig12.eps}%
+    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
     \label{fig: weight per layer NAC-CO}}
     \vfill
-    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig11.eps}%
+    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
     \label{fig: multipliers NAC-CO}}

### 2025-03-11 manuscript.tex
bold vec. and mat.

@@
 \usepackage{amsthm}
+
+\makeatletter
+\let\NAT@parse\undefined
+\makeatother
+\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}
+% \usepackage[]{hyperref}
+% \hypersetup{
+%     % bookmarksnumbered=true,
+%     %   linkbordercolor=blue,
+%     %   filebordercolor=red,
+%     %   citebordercolor = green,      
+%     %   urlbordercolor=red,
+%       %
+%       colorlinks=false
+%       % linkcolor=blue,
+%       % filecolor=blue,
+%       % citecolor = blue,      
+%       % urlcolor=cyan,
+% }
+
+\usepackage{cleveref, autonum}
+
 \newtheorem{remark}{Remark}
@@
 
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
-\usepackage{hyperref}
-\hypersetup{
-    linkbordercolor=blue,
-    filebordercolor=red,
-    citebordercolor = green,      
-    urlbordercolor=red,
-    %
-    % colorlinks=true,
-    % linkcolor=blue,
-    % filecolor=blue,
-    % citecolor = blue,      
-    % urlcolor=cyan,
+\newcommand{\etal}{\textit{et~al.\ }}
+\newcommand\eg{\textit{e.g.\ }}
+\newcommand\ie{\textrm{i.e.\ }}
+\newcommand\R{\mathbb{R}}
+
+\newcommand*{\mv}[1]{\boldsymbol{#1}}
+\newcommand*{\mm}[1]{\boldsymbol{#1}}
+\newcommand*{\norm}[1]{\lVert #1 \rVert}
+
+\newcommand\bx{\mv x}
+\newcommand\bu{\mv u}
+
+\newcommand\der{\mathrm d}
+\newcommand*{\ddfrac}[2]{
+    \frac{\der {#1}}{\der {#2}}
+}
+\newcommand*{\ddtfrac}[2]{
+    \tfrac{\der {#1}}{\der {#2}}
 }
@@
 One of the common issues in using NNs is that the outputs of NNs are not predictable.
-This is because the input‒output relationships of the NNs are not interpretable (i.e., the NNs are usually called black boxes \cite{RN8, RN9}).
+This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{RN8, RN9}).
 This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
@@
     \item $\otimes$ denotes the Kronecker product \cite{RN22}.
-    \item $x_{(i)}$ denotes the $i\textsuperscript{th}$ element of vector $x$.    
+    \item $\mv x_{(i)}$ denotes the $i\textsuperscript{th}$ element of vector $\mv x$.    
     % \item $A_{(i,j)}$ is the $i\textsuperscript{th}$ row-$j\textsuperscript{th}$ column element of matrix $A$.
-    \item $\text{row}_j(A)$ denotes the $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$. 
+    \item $\text{row}_j(\mm A)$ denotes the $j\textsuperscript{th}$ row of $\mm A\in\mathbb{R}^{n\times m}$. 
     % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$, respectively.
-    \item $\text{vec}(A)\triangleq [\text{row}_1(A^T)  ,\cdots,\text{row}_m(A^T)  ]^T   $ for $A\in\mathbb{R}^{n\times m}$.
-    % \item $\text{vec}(A)\triangleq [\text{col}_1(A)^T  ,\cdots,\text{col}_m(A)^T  ]^T   $ for $A\in\mathbb{R}^{n\times m}$.
+    \item $\text{vec}(\mm A)\triangleq [\text{row}_1(\mm A^\top )  ,\cdots,\text{row}_m(\mm A^\top )]^\top $ for $\mm A\in\mathbb{R}^{n\times m}$.
+    % \item $\text{vec}(A)\triangleq [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\mathbb{R}^{n\times m}$.
     \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of $A\in\mathbb{R}^{n\times n}$.
@@
 \begin{equation}
-    M(q)\ddot q + C(q,\dot q)\dot q + G(q) + F(q) = \tau
+    \mm M(\mv q)\ddot {\mv q} + \mm C(\mv q,\dot {\mv q})\dot {\mv q} + \mm G(\mv q) + \mm F(\mv q) = \mv \tau
     \label{eq. system dynamics 1}
 \end{equation}
-where $q\in \mathbb{R}^n$ and $\tau\in\mathbb R^n$ denote the generalized coordinate and the control input, respectively; $M(q)\in\mathbb{R}^{n\times n}$, $C(q,\dot q)\in\mathbb{R}^{n\times n}$, and $G(q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $F(q)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $M_0>0,C_0$ and $G_0$, \eqref{eq. system dynamics 1} can be represented as 
+where $\mv q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M(\mv q)\in\mathbb{R}^{n\times n}$, $\mm C(\mv q,\dot {\mv q})\in\mathbb{R}^{n\times n}$, and $\mm G(\mv q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F(\mv q)\in\mathbb{R}^{n}$ denotes the external force.
+Using the user-designed matrices $\mm M_0>0,\mm C_0$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
 \begin{equation}
-    M_0\ddot q+C_0\dot q+G_0 = \tau + f(q,\dot q,\ddot q)
+    \mm M_0\ddot {\mv q}+\mm C_0\dot {\mv q}+\mm G_0 = \mv \tau + \mv f(\mv q,\dot {\mv q},\ddot {\mv q})
     \label{eq. system dynamics 2}
 \end{equation}
-where $f(q,\dot q,\ddot q) \triangleq -(M-M_0)\ddot q-(C-C_0)(q,\dot q)\dot q -(G-G_0) -F(q)$ denotes the residual unknown term.
+where $\mv f(\mv q,\dot {\mv q},\ddot {\mv q}) \triangleq -(\mm M-\mm M_0)\ddot {\mv q}-(\mm C-\mm C_0)(\mv q,\dot {\mv q})\dot {\mv q} -(\mm G-\mm G_0) -\mm F(\mv q)$ denotes the residual unknown term.
 
-Hence, the objective of the control design is to make $q$ track the continuously differentiable desired trajectory $q_d(t):\mathbb R\to \mathbb R^n$ under the unknown terms $f$.
+Hence, the objective of the control design is to make $\mv q$ track the continuously differentiable desired trajectory $\mv q_d(t):\R\to \R^n$ under the unknown terms $\mv f$.
 
@@
 
-The backstepping control-based approach is utilized to generate a reference signal $z^*\triangleq -{k_q}\tilde q+\dot q_d$ for ${z}\triangleq \dot q$, where $\tilde q\triangleq {q} - q_d$ and $k_q\in\mathbb R_{>0}$.
+The backstepping control-based approach is utilized to generate a reference signal $\mv z^*\triangleq -{k_q}\tilde {\mv q}+\dot {\mv q}_d$ for $\mv {z}\triangleq \dot {\mv q}$, where $\tilde {\mv q}\triangleq \mv {q} - {\mv q}_d$ and $k_q\in\R_{>0}$.
 The desired stabilizing controller can be designed as follows:
 \begin{equation}
-    \tau^* = -M_0\cdot ({k_z}\tilde z)+ 
+    \mv \tau^* = 
+    -\mm M_0\cdot ({k_z}\tilde {\mv z})
+    + 
         ( 
-            -M_0\tilde q+C_0{z}+G_0-f+M_0 \dot z^*
+            -\mm M_0\tilde {\mv q}+\mm C_0{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
         )
@@
 \end{equation}
-where $\tilde z\triangleq z-z^*$ and $k_z\in\mathbb R_{>0}$.
-Note that the desired controller cannot be realized because $f$.
+where $\tilde {\mv z}\triangleq \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
+Note that the desired controller cannot be realized because of $\mv f$.
 
@@
 The NN with a single hidden layer is represented as 
-\begin{equation*}
-    \Phi({q_{NN}};\theta)\triangleq V_1^T\phi(V_0^T{q_{NN}})
-\end{equation*}
-where ${q_{NN}}\in\mathbb R^{l_0+1}$ denotes the NN input vector, $V_i\in\mathbb R^{(l_i+1)\times l_{i+1}},\ i\in[0,1]$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\phi:\mathbb R^{l_1}\to\mathbb R^{l_1+1}$ denotes the activation function layer.
-The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (i.e., $\phi(x) = [\sigma(x_{(1)}),\cdots, \sigma(x_{(l_1)}), 1]^T$).
-For further simplicity, let $\theta\triangleq[\theta_1^T,\theta_0^T]^T\in\mathbb R^{\Xi}$ denote the total weight vector, where $\theta_i\triangleq \text{vec}(V_i)\in\mathbb R^{\Xi_i}$ denotes the vectorized weights.
+\begin{equation}
+    \mv \Phi({\mv q_{NN}};\mv \theta)\triangleq \mm V_1^\top \mv \phi(\mm V_0^\top {\mv q_{NN}})
+\end{equation}
+where ${\mv q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\mm V_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in[0,1]$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\mv \phi:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
+The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\mv \phi(\mv x) = [\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1]^\top $).
+For further simplicity, let $\mv \theta\triangleq[\mv \theta_1^\top ,\mv \theta_0^\top ]^\top \in\R^{\Xi}$ denote the total weight vector, where $\mv \theta_i\triangleq \text{vec}(\mm V_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
 $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
 
-Using this NN, the desired controller $\tau^*$ can be approximated by the ideal weight vector $\theta^*$ for a compact subset $\Omega_{NN}\in\mathbb R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{q_{NN}}\in\Omega_{NN}} \Vert\Phi({q_{NN}};\theta^*) - \tau^*\Vert=\epsilon<\infty$ \cite{RN35}.
+Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\mv \theta^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\mv q_{NN}}\in\Omega_{NN}} \allowbreak \Vert\mv \Phi({\mv q_{NN}};\mv \theta^*) - \mv \tau^*\Vert=\epsilon<\infty$ \cite{RN35}.
 % The boundedness of the norm of $\theta^*$  and approximation error $\epsilon$ are also claimed in \cite{RN35}.
-The ideal weight vector $\theta^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\hat\theta=[\hat\theta_1^T,\hat\theta_0^T]^T$ of $\theta^*=[\theta_1^{*T},\theta_0^{*T}]^T$, the desired controller $\tau^*\approx -\Phi(q_{NN};\theta^*)-\epsilon$ can be approximated as follows:
+The ideal weight vector $\mv \theta^*$ is typically assumed to be bounded.
+Then, using the estimated weight vector $\hat{\mv \theta}=[\hat{\mv \theta}_1^\top ,\hat{\mv \theta}_0^\top ]^\top $ of $\mv \theta^*=[\mv \theta_1^{*\top},\mv \theta_0^{*\top}]^\top $, the desired controller $\mv \tau^*\approx -\mv \Phi(\mv q_{NN};\mv \theta^*)-\epsilon$ can be approximated as follows:
 \begin{equation}
-    \tau \triangleq -\Phi({q_{NN}};\hat\theta).
+    \mv \tau \triangleq -\mv \Phi({\mv q_{NN}};\hat{\mv \theta}).
     \label{eq. control law}
 \end{equation}
-For further sections, let $\Phi^*\triangleq\Phi({q_{NN}};\theta^*)$ and $\phi^* \triangleq\phi(V_0^{*T}{q_{NN}})$, and let $\hat\Phi\triangleq\Phi({q_{NN}};\hat\theta)$, $\hat\phi \triangleq\phi(\hat V_0^{T}{q_{NN}})$ and $\hat\phi' \triangleq \partial \hat\phi/\partial (\hat V_0^Tq_{NN})$.
+For further sections, let $\mv \Phi^*\triangleq\mv \Phi({\mv q_{NN}};\mv \theta^*)$ and $\mv \phi^* \triangleq\mv \phi(\mm V_0^{*\top}{\mv q_{NN}})$, and let $\hat{\mv \Phi}\triangleq{\mv \Phi}({\mv q_{NN}};\hat{\mv \theta})$, $\hat{\mv \phi} \triangleq\mv \phi(\hat {\mm V}_0^{\top}{\mv q_{NN}})$ and $\hat{\mv \phi}' \triangleq \partial \hat{\mv \phi}/\partial (\hat {\mm V}_0^\top \mv q_{NN})$.
 
@@
 desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\xi\triangleq[\tilde q^T,\tilde z^T]^T\in\mathbb R^{2n}$ as follows:
-\begin{equation*}
-    \dot\xi = A_\xi\xi+B_\xi(\Phi^*-\hat\Phi+\epsilon)
-\end{equation*}
+control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi\triangleq[\tilde {\mv q}^\top ,\tilde {\mv z}^\top ]^\top \in\R^{2n}$ as follows:
+\begin{equation}
+    \dot{\mv \xi} 
+    = 
+    \mm A_\xi{\mv \xi}+\mm B_\xi(\mv \Phi^*-\hat{\mv \Phi}+\epsilon)
+\end{equation}
 where 
-\begin{equation*}
-    A_\xi \triangleq 
+\begin{equation}
+    \mm A_\xi \triangleq 
     \begin{bmatrix}
-        -{k_q} I_n &I_n\\-I_n& -{k_z} I_n
+        -{k_q} \mm I_{n\times n} &\mm I_{n\times n}
+        \\
+        -\mm I_{n\times n}& -{k_z} \mm I_{n\times n}
     \end{bmatrix}
     ,\ 
-    B_\xi \triangleq 
+    \mm B_\xi \triangleq 
     \begin{bmatrix}
-        0_{n\times n}\\M_0^{-1}
+        \mm 0_{n\times n}\\\mm M_0^{-1}
     \end{bmatrix}.
-\end{equation*}
+\end{equation}
 
@@
 
-Using the augmented error $\xi$, the quadratic objective function is defined as
-\begin{equation*}
-    J(\xi;\hat\theta)\triangleq
+Using the augmented error $\mv \xi$, the quadratic objective function is defined as
+\begin{equation}
+    J(\mv \xi;\hat{\mv \theta})\triangleq
     {1\over 2}
-    \xi^TW\xi
-\end{equation*}
-where $W=W^T>0$ denotes the weighting matrix.
+    \mv \xi^\top \mm W\mv \xi
+\end{equation}
+where $\mm W=\mm W^\top >0$ denotes the weighting matrix.
 
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\Vert\hat\theta_i\Vert^2-\bar\theta^2_i,\ i\in[0,1]$.
+For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\Vert{\hat{\mv\theta}}_i\Vert^2-\bar\theta^2_i,\ i\in[0,1]$.
 % Then the objective of the adaptation process can be reformulated into the constrained optimization problem as follows:
 The control problem can be reformulated into a constrained optimization problem as follows:
-\begin{equation*}
+\begin{equation}
     \begin{matrix}
-        \min_{\hat\theta} \ J(\xi;\hat\theta)
+        \min_{{\hat{\mv\theta}}} \ J(\mv \xi;{\hat{\mv\theta}})
         \\ \\
         \begin{aligned}
-        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal A = [\theta_0,\theta_1].
+        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I = [\theta_0,\theta_1].
         \end{aligned}
     \end{matrix}
-\end{equation*}
+\end{equation}
 In this optimization problem, $\xi$ is considered a predefined parameter.
@@
 \begin{equation}
-    L(\xi,\hat\theta,[\lambda_j]_{j\in\mathcal A})\triangleq J(\xi;\hat\theta)+\sum_{j\in\mathcal A} \lambda_jc_j(\hat\theta)
+    L(
+        \mv \xi,
+        {\hat{\mv\theta}},
+        [\lambda_j]_{j\in\mathcal I}
+    )
+    \triangleq 
+    J(\mv \xi;{\hat{\mv\theta}})
+    +
+    \sum_{j\in\mathcal I} \lambda_jc_j({\hat{\mv\theta}})
     .
 \end{equation}
-% where $\mathcal A=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{\hat\theta} \max_{[\lambda_j]_{j\in\mathcal A}}  L$, the adaptation law is derived as follows:
+% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
+To solve the dual problem $\min_{{\hat{\mv\theta}}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
 \begin{align}
-        \dot {\hat\theta}&=-\alpha {\partial L\over\partial \hat\theta}
+        \dot {{\hat{\mv\theta}}}&=-\alpha {\partial L\over\partial {\hat{\mv\theta}}}
         =-\alpha 
         \bigg(
-        {\partial J\over \partial \hat\theta}+\sum_{j\in\mathcal{A}}
-        \lambda_j {\partial c_j\over \partial \hat\theta}
+        {\partial J\over \partial {\hat{\mv\theta}}}+\sum_{j\in\mathcal{A}}
+        \lambda_j {\partial c_j\over \partial {\hat{\mv\theta}}}
         \bigg),
@@
         \quad\quad\quad\quad      \      
-        \forall j\in\mathcal A,
+        \forall j\in\mathcal I,
     \label{eq. adaptation law L}
@@
         \quad\quad\quad\quad\ \ \ \ \ 
-        \forall j\in\mathcal A,
+        \forall j\in\mathcal I,
     \label{eq. adaptation law L max}
 \end{align}
-where $\alpha\in\mathbb R_{>0}$ and $\beta_j\in\mathbb R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
+where $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
 \color{red}
 % The Eq.~\eqref{eq.
-adaptation law L max} is analog to using an active set $\mathcal A=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
+adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
 \color{black}
 
-Using the chain rule, the gradient of the objective function with respect to the weights (i.e., $\partial J/\partial \hat\theta$) in \eqref{eq. adaptation law th} can be represented as
-\begin{equation*}
-    {\partial J\over\partial \hat\theta}
+Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\partial J/\partial {\hat{\mv\theta}}$) in \eqref{eq. adaptation law th} can be represented as
+\begin{equation}
+    {\partial J\over\partial {\hat{\mv\theta}}}
     =
-    {\partial \xi\over\partial \hat\theta}^TW
-    {\partial \xi\over\partial \hat\theta}
+    {\partial \mv\xi\over\partial {\hat{\mv\theta}}}^\top 
+    \mm W
+    {\partial \mv\xi\over\partial {\hat{\mv\theta}}}
     .
-\end{equation*}
-The calculation of $\partial J/\partial \hat\theta$ is not straightforward because of the dynamics of $\xi$.
+\end{equation}
+The calculation of $\partial J/\partial {\hat{\mv\theta}}$ is not straightforward because of the dynamics of $\xi$.
 Using the forward sensitivity method presented in \cite{RN34}, the sensitivity equation can be obtained as follows:
 \begin{equation}
-    \dot \eta =A_\xi - B_\xi 
-    % (\partial \hat\Phi/\partial \hat\theta)
-    {\partial \hat\Phi\over\partial \hat\theta}
+    \dot {\mm \eta} =
+    \mm A_\xi - \mm B_\xi 
+    % (\partial \hat{\mv\Phi}/\partial {\hat{\mv\theta}})
+    {\partial \hat{\mv\Phi}\over\partial {\hat{\mv\theta}}}
+    ,
     \label{eq. sen eq}
 \end{equation}
-where $\eta\triangleq \partial \xi/\partial \hat\theta\in\mathbb R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
-The initial value of $\eta$ is zero since the initial $\xi$ is independent of the weights.
-By decomposing for each layer, the dynamics of $\eta_i\triangleq \partial \xi/\partial \hat\theta_i\in\mathbb R^{2n\times \Xi_i}$ can be represented as
-\begin{equation*}
+where ${\mm \eta}\triangleq \partial \mv\xi/\partial {\hat{\mv\theta}}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
+The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
+By decomposing for each layer, the dynamics of ${\mm \eta}_i\triangleq \partial \mv\xi/\partial {\hat{\mv\theta}}_i\in\R^{2n\times \Xi_i}$ can be represented as
+\begin{equation}
     \begin{aligned}
-        \dot\eta =&
+        \dot{\mm \eta} =&
         \begin{bmatrix}
-            \eta_1&\eta_0
+            {\mm \eta}_1&{\mm \eta}_0
         \end{bmatrix}'
         \\
-        =&A_\xi
+        =&
+        \mm A_\xi
+        % \begin{bmatrix}
+        [
+            {\mm \eta}_1
+            \ \ 
+            {\mm \eta}_0
+        ]
+        % \end{bmatrix}
+        -\mm B_\xi
+        % \begin{bmatrix}
+        [
+            (\mm I_{l_2}\otimes \hat{\mv\phi}^\top )
+            \ \ 
+            \hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_{l_1}\otimes {\mv q_{NN}}^\top )
+        ]
+        % \end{bmatrix}
+        .
+    \end{aligned}
+\end{equation}
+The calculation of $\partial \hat{\mv\Phi}/\partial{\hat{\mv\theta}}$ is introduced in \cite{RN36}.
+In conclusion, the gradient of the objective with respect to the weights can be obtained as ${\partial J/\partial {\hat{\mv\theta}}} = {\mm \eta}^\top\mm W\mv\xi$ by simulating the sensitivity equation \eqref{eq.
+sen eq}.
+
+On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
+\begin{equation}
+    \frac{\partial c_{\theta_0}}{\partial{\hat{\mv\theta}}}
+    = 
     \begin{bmatrix}
-            \eta_1&\eta_0
+        \mm 0_{\Xi_1\times 1} \\
+        2{\hat{\mv\theta}}_0 
     \end{bmatrix}
-        -B_\xi
+    ,\quad
+    \frac{\partial c_{\theta_1}}{\partial{\hat{\mv\theta}}}    
+    = 
     \begin{bmatrix}
-            (I_{l_2}\otimes \hat\phi^T)&\hat V_1^T\hat\phi'(I_{l_1}\otimes {q_{NN}}^T)
+        2{\hat{\mv\theta}}_1 \\
+        \mm 0_{\Xi_0\times 1}
     \end{bmatrix}
     .
-    \end{aligned}
-\end{equation*}
-The calculation of $\partial \hat\Phi/\partial\hat\theta$ is introduced in \cite{RN36}.
-In conclusion, the gradient of the objective with respect to the weights can be obtained as ${\partial J/\partial \hat\theta} = \eta^TW\xi$ by simulating the sensitivity equation \eqref{eq. sen eq}.
-
-On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
-\begin{equation*}
-    \frac{\partial c_{\theta_0}}{\partial\hat\theta}
-    = 
-    \begin{bmatrix}
-        0_{\Xi_1\times 1} \\
-        2\hat\theta_0 
-    \end{bmatrix}
-    ,\quad
-    \frac{\partial c_{\theta_1}}{\partial\hat\theta}    
-    = 
-    \begin{bmatrix}
-        2\hat\theta_1 \\
-        0_{\Xi_0\times 1}
-    \end{bmatrix}
-    .
-\end{equation*}
+\end{equation}
 
@@
 adaptation law L} and \eqref{eq.
-adaptation law L max} ensure the boundedness of the tracking error $\xi$ and the weight estimation $\hat\theta$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
+adaptation law L max} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\hat{\mv\theta}}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
 ctrl stable condition}.
@@
 
-\subsection*{Step 1: Boundedness of $\hat\theta_1,\eta_1,\xi$}
+\subsection*{Step 1: Boundedness of ${\hat{\mv\theta}}_1,{\mm \eta}_1,\mv \xi$}
 
@@
 
-The dynamics of $\xi$ can be represented as
-\begin{equation*}    
-    \dot \xi = A_\xi\xi +B_\xi
+The dynamics of $\mv \xi$ can be represented as
+\begin{equation}    
+    \dot {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
     (
-        -\hat V_1^T \hat\phi+w(t)
+        -\hat {\mm V}_1^\top \hat{\mv\phi}+\mv w(t)
     )
-\end{equation*}
-where $w(t)\triangleq V_1^{*T}\phi^*+\epsilon$ is a lumped residual term, which is bounded as $\Vert w(t)\Vert\le \bar w< 0$ since $\Vert\theta_1^*\Vert$ and $\Vert\phi^*\Vert$ are bounded.
-The dynamics of $\eta_1$ and $\hat\theta_1$ are represented as
-\begin{equation*}
+\end{equation}
+where $\mv w(t)\triangleq {\mm V}_1^{*T}\mv\phi^*+\mv \epsilon$ is a lumped residual term, which is bounded as $\Vert\mv  w(t)\Vert\le \bar w< 0$ since $\Vert\mv\theta_1^*\Vert$ and $\Vert\mv\phi^*\Vert$ are bounded.
+The dynamics of ${\mm \eta}_1$ and ${\hat{\mv\theta}}_1$ are represented as
+\begin{equation}
     \begin{aligned}
-        \dot\eta_1 =
+        \dot{\mm \eta}_1 =
         & 
-        A_\xi \eta_1 -B_\xi (I_{l_{2}}\otimes \hat\phi^T)
+        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )
         \\
-        \dot{\hat\theta}_1 =
+        \dot{{\hat{\mv\theta}}}_1 =
         & -\alpha 
         (
-            \eta_1^TW\xi+2\lambda_{\theta_1} \hat\theta_1
+            {\mm \eta}_1^\top \mm W\mv\xi+2\lambda_{\theta_1} {\hat{\mv\theta}}_1
         ).
     \end{aligned} 
-\end{equation*}
-According to \cite[Chap.~4 T.~1.9]{RN32}, the boundedness of $\eta_1$ can be obtained since $A_\xi$ is stable and the residual term $-B_\xi (I_{l_{2}}\otimes \hat\phi^T)$ is bounded.
+\end{equation}
+According to \cite[Chap.~4 T.~1.9]{RN32}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )$ is bounded.
 
-Define the Lyapunov function $\mathcal V_1=(1/2)\xi^TP\xi+(1/2\alpha)\hat\theta_1^T\hat\theta_1$, with the Lyapunov equation $A_\xi^TP+PA_\xi=-Q$, where $A_\xi<0,P=P^T>0$, and $Q>0$.
-Using a proposition $\hat V_1^T\hat\phi = \text{vec}(\hat V_1^T\hat\phi)=\text{vec}(\hat\phi^T\hat V_1) = (I_{l_2}\otimes \hat\theta^T)\text{vec}(\hat V_1)=(I_{l_2}\otimes \hat\phi^T)\hat\theta_1$ \cite[Proposition~(7.1.9)]{RN22}, the time derivative of $\mathcal V_1$ is
+Define the Lyapunov function $\mathcal V_1=(1/2)\mv\xi^\top \mm P\mv\xi+(1/2\alpha){\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
+Using a proposition $\hat {\mm V}_1^\top \hat{\mv\phi} = \text{vec}(\hat {\mm V}_1^\top \hat{\mv\phi})=\text{vec}(\hat{\mv\phi}^\top \hat {\mm V}_1) = (\mm I_{l_2}\otimes {\hat{\mv\theta}}^\top )\text{vec}(\hat {\mm V}_1)=(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1$ \cite[Proposition~(7.1.9)]{RN22}, the time derivative of $\mathcal V_1$ is
 \begin{equation}
     \begin{aligned}
-        \dot {\mathcal V}_1 =& {1\over 2}\xi^T(A_\xi^TP+PA_\xi)\xi+\xi ^TP ( -B_\xi\hat V_1^T\hat \phi   +B_\xi w(t) )\\
-        &+\hat\theta_1^T
+        \dot {\mathcal V}_1 
+        =& 
+        {1\over 2}
+        \mv \xi^\top (\mm A_\xi^\top \mm P+\mm P\mm A_\xi)\mv \xi
+        +
+        \mv \xi^\top \mm P ( -\mm B_\xi\hat {\mm V}_1^\top \hat {\mv \phi} +\mm B_\xi \mv w(t) )\\
+        &
+        +{\hat{\mv\theta}}_1^\top 
         (
-            -\eta_1^TW \xi-2\lambda_{\theta_1} \hat\theta_1 
+            -{\mm \eta}_1^\top \mm W \xi-2\lambda_{\theta_1} {\hat{\mv\theta}}_1 
         )
         \\
-        =& -{1\over 2}\xi^TQ\xi -\xi^TPB_\xi(I_{l_2}\otimes \hat\phi^T)\hat\theta_1 +\xi^T\Delta
+        =& 
+        -{1\over 2}\mv \xi^\top \mm Q\mv \xi 
+        -
+        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1 
+        +\mv \xi^\top \mv \Delta
         \\
         &
-        -\hat\theta_1^T\eta_1^TW\xi
-        -2\lambda_{\theta_1} \hat\theta_1^T\hat\theta_1
+        -{\hat{\mv\theta}}_1^\top {\mm \eta}_1^\top \mm W\mv \xi
+        -2\lambda_{\theta_1} {\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1
         \\
-        \le& -(1/2)\lambda_\text{min}(Q)\Vert \xi\Vert ^2
-        +\bar\Delta \Vert \xi\Vert  
-        +\bar M\Vert \xi\Vert  \Vert \hat\theta_1\Vert
+        \le&
+        -(1/2)\lambda_\text{min}(\mm Q)\Vert \mv \xi\Vert ^2
+        +\bar\Delta \Vert \mv \xi\Vert  
+        +\bar M\Vert \mv \xi\Vert  \Vert {\hat{\mv\theta}}_1\Vert
+        \\
+        &
         -2\lambda_{\theta_1}
-        \Vert\hat\theta_1\Vert ^2
+        \Vert{\hat{\mv\theta}}_1\Vert ^2
         \\
@@
         (
-        -{\lambda_\text{min}(Q)/ 2} +{\bar M/ 2}
+        -{\lambda_\text{min}(\mm Q)/ 2} +{\bar M/ 2}
         )
-        \Vert \xi\Vert ^2 +\bar\Delta \Vert \xi\Vert  
+        \Vert \mv \xi\Vert ^2 +\bar\Delta \Vert \mv \xi\Vert  
         \\
@@
         )
-        \Vert \tilde\theta_1\Vert ^2 
+        \Vert \tilde{\mv \theta}_1\Vert ^2 
         \end{aligned}
@@
 \end{equation}
-where $\Delta\triangleq PB_\xi w(t)$ and $M\triangleq  -PB_\xi(I_{l_2}\otimes \hat\phi^T)+W\eta_1$ are bounded such that $\Vert\Delta\Vert\le\bar\Delta<\infty$ and $\Vert M\Vert_F\le \bar M< \infty$, respectively.
+where $\mv \Delta\triangleq \mm P\mm B_\xi \mv w(t)$ and $\mm M\triangleq -\mm P\mm B_\xi(\mm I_{l_2}\otimes \hat{\mv\phi}^\top )+\mm W{\mm \eta}_1$ are bounded such that $\Vert\mv \Delta\Vert\le\bar\Delta<\infty$ and $\Vert\mm M\Vert_F\le \bar M< \infty$, respectively.
 
-By defining $P=I_n$, the eigenvalues of $Q=-A_\xi^T-A_\xi$ are $2k_q$ and $2k_z$, since $A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
+By defining $\mm P=\mm I_n$, the eigenvalues of $\mm Q=-\mm A_\xi^\top -\mm A_\xi$ are $2k_q$ and $2k_z$, since $\mm A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
 According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
@@
 and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\bar M/2$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
-\begin{equation*}
+\begin{equation}
     \Theta_\xi = 
     \bigg\{
-        \xi \ \bigg\vert\ \Vert\xi\Vert \le  
+        \mv\xi\mid\Vert\mv\xi\Vert \le  
         {
-            \bar \Delta \over \lambda _\text{min}(Q)-\bar M/2
+            \bar \Delta \over \lambda _\text{min}(\mm Q)-\bar M/2
         } 
@@
     ,
-\end{equation*}
+\end{equation}
 and the weight estimation $\theta^*_1$ is bounded in
-\begin{equation*}
-    \Theta_{\hat\theta_1} = 
+\begin{equation}
+    \Theta_{{\hat{\mv\theta}}_1} = 
     \{ 
-        \hat\theta 
-        \ 
-        \vert
-        \ 
-        \Vert\hat\theta\Vert \le  
+        {\hat{\mv\theta}_1} 
+        \mid
+        \Vert{\hat{\mv\theta}_1}\Vert 
+        \le  
         \bar\theta_1
@@
     .
-\end{equation*}
-The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once $\hat\theta_1$ approaches the compact set $\Theta_{\hat\theta_1}$, satisfying the constraint $c_{\theta_1}$.
+\end{equation}
+The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\hat{\mv\theta}}_1$ approaches the compact set $\Theta_{{\hat{\mv\theta}}_1}$, satisfying the constraint $c_{\theta_1}$.
 
-\subsection*{Step 2: Boundedness of $\hat\theta_0,\eta_0$}
+\subsection*{Step 2: Boundedness of ${\hat{\mv\theta}}_0,{\mm \eta}_0$}
 
-The dynamics of $\eta_0$ and $\hat\theta_0$ are represented as
-\begin{equation*}
+The dynamics of ${\mm \eta}_0$ and ${\hat{\mv\theta}}_0$ are represented as
+\begin{equation}
     \begin{aligned}     
-        \dot\eta_0 =& 
-        A_\xi\eta_0 -B_\xi 
-        \hat V_1^T\hat\phi'(I_1\otimes {q_{NN}}^T)
+        \dot{\mm \eta}_0 =& 
+        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
+        \hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )
         \\
-        \dot{\hat\theta}_0
+        \dot{{\hat{\mv\theta}}}_0
         =&
@@
         (
-            \eta_0^TW\xi+2\lambda_{\theta_0} \hat\theta_0
+            {\mm \eta}_0^\top \mm W\mv \xi+2\lambda_{\theta_0} {\hat{\mv\theta}}_0
         )
@@
     \end{aligned}
-\end{equation*}
-According to \cite[Chap.~4 T.~1.9]{RN32}, $\eta_0$ is bounded since $A_\xi$ is a stable matrix and $-B_\xi\hat V_1^T\hat\phi'(I_1\otimes {q_{NN}}^T)$ is bounded.
-To obtain the invariance set of $\hat\theta_0$, taking the time derivative of the Lyapunov function $\mathcal V_0=(1/2\alpha)\hat\theta_0^T\hat\theta_0$ yields:
-\begin{equation*}
+\end{equation}
+According to \cite[Chap.~4 T.~1.9]{RN32}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )$ is bounded.
+To obtain the invariance set of ${\hat{\mv\theta}}_0$, taking the time derivative of the Lyapunov function $\mathcal V_0=(1/2\alpha){\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0$ yields:
+\begin{equation}
     \begin{aligned}
         \dot {\mathcal V}_0 =& 
-        \hat\theta_0^T (-\eta_0W\xi -2\lambda_{\theta_0}\hat\theta_0)
+        {\hat{\mv\theta}}_0^\top (-{\mm \eta}_0\mm W\mv \xi -2\lambda_{\theta_0}{\hat{\mv\theta}}_0)
         \\
         \le &
-        \Vert\hat\theta_0\Vert \Vert \eta_0W\xi\Vert -2\lambda_{\theta_0} \hat\theta_0^T\hat\theta_0
+        \Vert{\hat{\mv\theta}}_0\Vert \Vert {\mm \eta}_0\mm W\mv \xi\Vert -2\lambda_{\theta_0} {\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0
         \\
         \le &
-        -2\lambda_{\theta_0} \Vert\hat\theta_0\Vert^2 + \Vert \eta_0W\xi\Vert \Vert \hat\theta_0\Vert 
+        -2\lambda_{\theta_0} \Vert{\hat{\mv\theta}}_0\Vert^2 + \Vert {\mm \eta}_0\mm W\mv \xi\Vert \Vert {\hat{\mv\theta}}_0\Vert 
         .
     \end{aligned}
-\end{equation*}
+\end{equation}
 Then, the invariance set can be represented as 
-\begin{equation*}
-    \Theta_{\hat\theta_0} =
+\begin{equation}
+    \Theta_{{\hat{\mv\theta}}_0} =
     \{
-        \hat\theta_0\ \vert \ \Vert\hat\theta_0\Vert \le \Vert\eta_0W\xi\Vert/\lambda_{\theta_0}
+        {\hat{\mv\theta}}_0\mid\Vert{\hat{\mv\theta}}_0\Vert 
+        \le
+        \Vert{\mm \eta}_0\mm W\mv \xi\Vert/\lambda_{\theta_0}
     \}
     .    
-\end{equation*}
-If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{\hat\theta_0}$ converges to $\{\hat\theta_0\ \vert \ \Vert\hat\theta_0\Vert \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
+\end{equation}
+If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\hat{\mv\theta}}_0}$ converges to $\{{\hat{\mv\theta}}_0\ \vert \ \Vert{\hat{\mv\theta}}_0\Vert \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
 Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.
@@
 % \begin{remark}
-%     In the constrained optimization method, the corresponding method of $L_2$-regularization method is the quadratic penalty method, which replaces the constrained optimization problem into an unconstrained optimization problem by adding the penalty term $(1/2\mu)\sum_{r\in\mathcal A} c_r^2$ in the objective function.
-%     The penalty parameter $\mu\in\mathbb R_{>0}$ usually decreases over implementation for the convergence of the optimization process.
+%     In the constrained optimization method, the corresponding method of $L_2$-regularization method is the quadratic penalty method, which replaces the constrained optimization problem into an unconstrained optimization problem by adding the penalty term $(1/2\mu)\sum_{r\in\mathcal I} c_r^2$ in the objective function.
+%     The penalty parameter $\mu\in\R_{>0}$ usually decreases over implementation for the convergence of the optimization process.
 %     However, the decreased penalty term $\mu$ may alter the original objective function as the penalty term dominates the objective function.
@@
 The values of the system parameters are given in Table~\ref{table: system parameters}.
-The reference signal of $q=[q_1,q_2]^T$ is defined as follows:
-\begin{equation*}
-    q_d
+The reference signal of $\mv q=[q_1,q_2]^\top $ is defined as follows:
+\begin{equation}
+    \mv q_d
     =
@@
     .
-\end{equation*}
+\end{equation}
 
@@
 The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters $\lambda$, $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively.
-The square root of the integrated squared error (ISE) (i.e., $\sqrt{\int_0^T\Vert\xi\Vert^2\,dt}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
+The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \Vert\mv \xi\Vert^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
 The parameter dependencies of the controllers were examined via various values of the parameters. 
@@
 The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $(1/2)\lambda\hat\theta^T\hat\theta$ to the objective function such that $J_{L_2} = J+(1/2)\lambda\hat\theta^T\hat\theta$, where $\lambda\in\mathbb R_{>0}$ denotes the $L_2$ coefficient.
-The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda\hat\theta$ as follows:
-\begin{equation*} 
-    \dot{\hat\theta} = 
-    {\partial J_{L_2}\over\partial \hat\theta}
+The adaptation law of NAC-L2 is derived by adding the squared weight term $(1/2)\lambda{\hat{\mv\theta}}^\top {\hat{\mv\theta}}$ to the objective function such that $J_{L_2} = J+(1/2)\lambda{\hat{\mv\theta}}^\top {\hat{\mv\theta}}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
+The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\hat{\mv\theta}}$ as follows:
+\begin{equation} 
+    \dot{{\hat{\mv\theta}}} = 
+    {\partial J_{L_2}\over\partial {\hat{\mv\theta}}}
     =-\alpha
     \bigg(
-        {\partial J\over\partial \hat\theta}+\lambda\hat\theta
+        {\partial J\over\partial {\hat{\mv\theta}}}+\lambda{\hat{\mv\theta}}
     \bigg)
@@
     \label{eq. adap L2}
-\end{equation*}
-Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma\hat\theta$, where $\sigma\in\mathbb R_{>0}$.
-For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\Vert \tilde z \Vert\hat\theta$ is added to the adaptation law as follows:
-\begin{equation*}
-    \dot{\hat\theta} = -\alpha
+\end{equation}
+Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\hat{\mv\theta}}$, where $\sigma\in\R_{>0}$.
+For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\Vert \tilde{\mv z} \Vert{\hat{\mv\theta}}$ is added to the adaptation law as follows:
+\begin{equation}
+    \dot{{\hat{\mv\theta}}} = -\alpha
     \bigg(
-        {\partial J\over\partial \hat\theta}+\rho\Vert\tilde z\Vert\hat\theta
+        {\partial J\over\partial {\hat{\mv\theta}}}+\rho\Vert\tilde {\mv z}\Vert{\hat{\mv\theta}}
     \bigg)
     \label{eq. adap eMod}
-\end{equation*}
-where $\rho\in\mathbb R_{>0}$ denotes the $\epsilon$-modification coefficient.
-By $\Vert\tilde z\Vert$, the stabilizing function proportionally increases as the tracking error $\tilde z$ increases.
+\end{equation}
+where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
+By $\Vert\tilde {\mv z}\Vert$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
 Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
@@
 
-All controllers had the same control parameters except their crucial parameters (i.e., $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $M_0=I_2$ and $W=\text{diag}([5,1,15,15])$.
+All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\mm M_0=I_2$ and $\mm W=\text{diag}([5,1,15,15])$.
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The NN input vector was set to the desired trajectory $q_d$, with the augmented 1 to incorporate the bias term in the weight matrix such that $q_{NN}=[q_d^T,1]^T$.
+The NN input vector was set to the desired trajectory $\mv q_d$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\mv q_{NN}=[\mv q_d^\top ,1]^\top $.
 For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
@@
 
-For the detailed analysis, three values of the parameters (i.e., $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
-As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda\hat\theta$.
+For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
+As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\hat{\mv\theta}}$.
 Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
@@
 On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
-This is because the stabilizing function $-\alpha\rho\Vert\tilde z\Vert\hat\theta$ can be decreased once the tracking error $\tilde z$ is sufficiently regulated.
-However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (i.e., smaller weight norms are observed as $\rho$ increases. ).
+This is because the stabilizing function $-\alpha\rho\Vert\tilde {\mv z}\Vert{\hat{\mv\theta}}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
+However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (\ie smaller weight norms are observed as $\rho$ increases.).
 Therefore, similar to NAC-L2, the biased weights produce insufficient control input, resulting in a relatively larger square root of tracking ISE than that of NAC-CO, as described in Table \ref{table: error norm}.

### 2025-03-12 manuscript.tex
Move packages and macros to submodule

@@
 
-%In case you encounter the following error:
-%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
-%Error 1000 An error occurred while parsing a content stream. Unable to analyze the PDF file.
-%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
-%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
-%\pdfobjcompresslevel=0
-%\pdfminorversion=4
+% \makeatletter
+% \let\NAT@parse\undefined
+% \makeatother
 
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
-
-% MY PAKEAGES ========================================
-\usepackage{epsfig}
-% \usepackage{lipsum}  
-\usepackage{kotex}
-% \usepackage{natbib}
-\usepackage{cite}
-\usepackage{amssymb}
-\usepackage{xcolor}
-% \usepackage{enumitem}
-% \newlist{steps}{enumerate}{1}
-% \setlist[steps, 1]{label = Step \arabic*: }
-
-\usepackage{algorithm}
-\usepackage{svg}
-
-\usepackage{amsmath,amsfonts}
-\usepackage{algorithmic}
-\usepackage{array}
-% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-\usepackage{subfig}
-% \usepackage{textcomp}
-\usepackage{stfloats}
-\usepackage{url}
-\usepackage{verbatim}
-\usepackage{graphicx}
-% \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
-% \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
- % T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-% \usepackage{balance}
-
-\let\proof\relax
-\let\endproof\relax
-\usepackage{amsthm}
-
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
-\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}
-% \usepackage[]{hyperref}
-% \hypersetup{
-%     % bookmarksnumbered=true,
-%     %   linkbordercolor=blue,
-%     %   filebordercolor=red,
-%     %   citebordercolor = green,      
-%     %   urlbordercolor=red,
-%       %
-%       colorlinks=false
-%       % linkcolor=blue,
-%       % filecolor=blue,
-%       % citecolor = blue,      
-%       % urlcolor=cyan,
-% }
-
-\usepackage{cleveref, autonum}
-
-\newtheorem{remark}{Remark}
-\newtheorem{assum}{Assumption}
-\newtheorem{lem}{Lemma}
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\etal}{\textit{et~al.\ }}
-\newcommand\eg{\textit{e.g.\ }}
-\newcommand\ie{\textrm{i.e.\ }}
-\newcommand\R{\mathbb{R}}
-
-\newcommand*{\mv}[1]{\boldsymbol{#1}}
-\newcommand*{\mm}[1]{\boldsymbol{#1}}
-\newcommand*{\norm}[1]{\lVert #1 \rVert}
-
-\newcommand\bx{\mv x}
-\newcommand\bu{\mv u}
-
-\newcommand\der{\mathrm d}
-\newcommand*{\ddfrac}[2]{
-    \frac{\der {#1}}{\der {#2}}
-}
-\newcommand*{\ddtfrac}[2]{
-    \tfrac{\der {#1}}{\der {#2}}
-}
+\input{dding_template/tex_packages/tex_packages_general.tex}
+\input{dding_template/tex_macros/tex_macros_general.tex}
 
@@
 }
-% Constrained Optimization-Based neuro–Adaptive Control With Weight Constraint
 
@@
 \begin{proof}
-
 The boundedness is proven from the last layer to the first layer.

### 2025-03-15 manuscript.tex
modifying new control design (considering Lagragian system's properties)
and
added tikz prac.

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
-
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
-
-\IEEEoverridecommandlockouts                              % This command is only needed if 
-                                                          % you want to use the \thanks command
-
-\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% \makeatletter
-% \let\NAT@parse\undefined
-% \makeatother
-
+\documentclass[lettersize,journal]{IEEEtran}
+% code
+
+\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}
+% \usepackage{balance}
 \input{dding_template/tex_packages/tex_packages_general.tex}
@@
 
-% MY PAKEAGES ========================================
-
-\title{\LARGE \bf
-Imposing a Weight Norm Constraint for Neuro–Adaptive Control
+\newcommand*{\sat}{\mathcal{S}}
+\newcommand*{\fe}{\mv r}
+\newcommand*{\ptfrac}[2]{\tfrac{\partial #1}{\partial #2}}
+\newcommand*{\dtfrac}[2]{\tfrac{\der #1}{\der #2}}
+\newcommand*{\q}{\mv q}
+\newcommand*{\dq}{\dot{\mv q}}
+\newcommand*{\ddq}{\ddot{\mv q}}
+\newcommand*{\qd}{\mv q_d}
+\newcommand*{\dqd}{\dot{\mv q_d}}
+\newcommand*{\ddqd}{\ddot{\mv q_d}}
+
+\newcommand*{\NN}{\mv\Phi}
+\newcommand*{\act}{\mv\phi}
+\newcommand*{\wth}{\mv\theta}
+\newcommand*{\wV}{\mm V}
+
+\begin{document}
+\title{
+Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
+%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
 }
 
-\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
-\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
-\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
-\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
-        {\tt\small jiyun6606@gm.gist.ac.kr}}%
-}
-
-\begin{document}
+\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
+~Vol.~00, No.~0, Month~2024
+}%
+{How to Use the IEEEtran \LaTeX \ Templates}
 
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-
-In this paper, a neuro–adaptive controller with weight norm constraints is proposed for uncertain Euler‒Lagrange systems. 
-The boundedness of the weights in the neuro–adaptive controller design is important to prevent excessively large control inputs and system instability. 
-To ensure the boundedness of the weights, the weight norm constraints are imposed as inequality constraints in the weight adaptation. 
-The adaptation law is derived based on the constrained optimization method. 
-The stability of the proposed controller is analyzed in the sense of Lyapunov, ensuring the boundedness of the tracking error and weight estimation. 
-For the comparative study, two benchmark controllers and the proposed controller were evaluated through a numerical simulation of a two-link manipulator system and compared in terms of tracking performance and parameter dependency.
-The comparative study verified that the proposed controller has better tracking performance and lower parameter dependency.
-
+    This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints.
+A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints.
+The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state.
+The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights.
+Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{IEEEkeywords}
+Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
+\end{IEEEkeywords}
+
 %  SECTION INTRODUCTION ===================================
-
 \section{Introduction}
 
-In various practical applications, Euler‒Lagrange systems generally have uncertainties due to their unknown and unmodeled dynamics.
-These uncertainties degrade the control performance index.
-Furthermore, if uncertainties dominate the system, they may lead to instability.
-By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{RN26, RN30}.
-Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.
-
-More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{RN24}.
-It uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{RN35}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
-This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
-Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{RN16, RN18}, radial basis function NN (RBFNN) \cite{RN17, RN31} and deep NN (DNN) \cite{RN36}.
-The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.
-
-% The corresponding issue in the adaptive control is the parameter drift.
-% It refers to the weight divergence during the adaptation process, while the tracking error is bounded.
-
-% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs is that the outputs of NNs are not predictable.
-This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{RN8, RN9}).
-This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
-
-Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
-In \cite{RN31, RN36}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
-However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
-Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
-In addition, the $\sigma$-modification \cite{RN17} and the $\epsilon$-modification \cite{RN16, RN18} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
-The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
-However, they lack theoretical analysis regarding the optimality of the adapted weights.
-
-Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
-One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{RN1, RN13}.
-Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
-By regulating the magnitude of the weights, the stability of the adaptation process can be enhanced, and overfitting can be prevented.
-However, $L_2$-regularization also involves a trade-off between adaptation stability and the optimality of the weights.
-
-For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{RN29} can be utilized.
-It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
-To the best of the authors’ knowledge, no prior work has utilized the constrained optimization method for the real-time weight adaptation of neuro–adaptive control satisfying weight boundedness.
-Therefore, the constrained optimization method could play a pivotal role in the neuro–adaptive control design addressing the weight boundedness.
-
-The main contributions of this study are as follows:
+\subsection{Background}
+
+\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems.
+These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints.
+In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances.
+These uncertainties can significantly degrade control performance and, in some cases, lead to instability.
+To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{RN4}, \cite{RN2}.
+
+More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{RN1}.
+NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error.
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{RN29}, \cite{RN44} and radial basis function (RBF) neural networks \cite{RN26}, \cite{RN10}, as well as more complex models like deep neural networks (DNNs) \cite{RN16} and their variations.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{RN44, RN56, RN3, RN41}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{RN25}.
+Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{RN14} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{RN15}, have further extended the capabilities of neuro-adaptive control systems.
+
+A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated.
+Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
+
+However, two significant challenges persist in using NNs for adaptive control.
+First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs.
+When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints.
+Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{RN18}.
+Failing to address these constraints can degrade control performance or even destabilize the system.
+
+Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers.
+The following section will provide a detailed review of the existing solutions to these challenges.
+
+\subsection{Literature Review}
+
+\subsubsection{Ensuring Weight Norm Boundedness}
+
+A common challenge in neuro-adaptive control is maintaining the boundedness of the NN weights to ensure stability.
+In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly.
+For example, in \cite{RN16, RN14, RN11}, projection operators were used to constrain the weight norms to remain below predetermined constants.
+However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values.
+While this approach ensured that the NN remained stable, it did not necessarily result in optimal performance.
+
+In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{RN10} and $\epsilon$-modification \cite{RN41, RN3}.
+These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law.
+Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.
+
+\subsubsection{Satisfying Input Constraints}
+
+The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations.
+The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints.
+This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping.
+In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.
+
+To address input saturation, many studies introduced auxiliary systems.
+These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred.
+For instance, in \cite{RN55, RN56, RN3}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
+This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.
+
+Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{RN34, RN38, RN37}.
+In \cite{RN41}, the NN was used to approximate the desired control input, compensating for input saturation.
+However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+
+\subsubsection{Limitations of Existing Approaches and Potential of Constrained Optimization}
+
+Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations.
+Projection operators and modification techniques do not guarantee the optimality of the adapted weights.
+Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.
+
+To overcome these limitations, constrained optimization offers a promising approach.
+By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (e.g., tracking error) subject to both weight norm and input constraints.
+Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{RN22}.
+
+In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{RN60} and the Alternating Direction Method of Multipliers (ADMM) \cite{RN58, RN59}, have been used to train NNs offline.
+These methods impose constraints to address issues like gradient vanishing in backpropagation.
+However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation.
+This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.
+
+\subsection{Contributions}
+
+The main contributions of this study are listed as follows:
 \begin{itemize}
-    \item The neuro–adaptive control problem is reformulated into a constrained optimization problem by treating the satisfaction of the weight boundedness as inequality constraints.
-    \item The adaptation law is derived based on the constrained optimization method to minimize the objective function while satisfying the weight norm constraints.
-    \item The stability of the adaptation laws is analyzed via Lyapunov stability analysis, which ensures the boundedness of the tracking error and weight estimation.
+    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
+    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
+The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
+    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function.
+    %, enabling more precise real-time adaptation.
 \end{itemize}
 
-The remainder of this paper is organized as follows:
-Section \ref{sec: Problem Formulation} presents the target-constrained system and control objective.
-Section \ref{sec:ctrl design} introduces the proposed controller and the adaptation law. 
-Section \ref{sec:stability} examines the stability of the proposed controller.
-A comparative study of the three selected controllers, including the proposed controller through numerical simulation, is reported in Section \ref{sec:sim}.
-Finally, Section \ref{sec:conclusion} concludes the paper by presenting future work.
+\subsection{Organization}
+
+The remainder of this paper is organized as follows. 
+Section \ref{sec: Problem Formulation} presents the target system and control objective.
+Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
+In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
+Candidates of the weight and input constraints are presented in Section \ref{sec:cstr candidates}.
+Section \ref{sec:stability} analyzes the stability of the proposed controller.
+A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
+Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
+% The appendices provide the proof of the lemma used in the stability analysis.
 
@@
 \subsection{Notation}
-In this study, the following notation is used.
+In this study, the following notation is used:
 
 \begin{itemize}
-    \item $\otimes$ denotes the Kronecker product \cite{RN22}.
-    \item $\mv x_{(i)}$ denotes the $i\textsuperscript{th}$ element of vector $\mv x$.    
+    \item $\otimes$ denotes the Kronecker product \cite{RN17}.
+    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $\mm A\triangleq [a_{ij}]_{i\in[1,\cdots,n],j\in[1,\cdots ,]}\in\R^{n\times m}$ denotes a vector and a matrix.
+    % \item $x_{(i)}$ denotes the $i\textsuperscript{th}$ element of the vector $x\in\mathbb R^n$.    
     % \item $A_{(i,j)}$ is the $i\textsuperscript{th}$ row-$j\textsuperscript{th}$ column element of matrix $A$.
-    \item $\text{row}_j(\mm A)$ denotes the $j\textsuperscript{th}$ row of $\mm A\in\mathbb{R}^{n\times m}$. 
-    % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$, respectively.
-    \item $\text{vec}(\mm A)\triangleq [\text{row}_1(\mm A^\top )  ,\cdots,\text{row}_m(\mm A^\top )]^\top $ for $\mm A\in\mathbb{R}^{n\times m}$.
-    % \item $\text{vec}(A)\triangleq [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\mathbb{R}^{n\times m}$.
-    \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of $A\in\mathbb{R}^{n\times n}$.
+    \item $\text{row}_i(A)$ denotes the $i\textsuperscript{th}$ row of the matrix $A\in\R^{n\times m}$. 
+    % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
+    \item $\textit{vec}(A)\triangleq [\text{row}_1(A^\top)  ,\cdots,\text{row}_m(A^\top)  ]^\top   $ for $A\in\R^{n\times m}$.
+    % \item $\textit{vec}(A)\triangleq [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
+    \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of the matrix $A\in\R^{n\times n}$.
 \end{itemize}
@@
 
-Consider an uncertain Euler‒Lagrange system modeled as
-\begin{equation}
-    \mm M(\mv q)\ddot {\mv q} + \mm C(\mv q,\dot {\mv q})\dot {\mv q} + \mm G(\mv q) + \mm F(\mv q) = \mv \tau
-    \label{eq. system dynamics 1}
-\end{equation}
-where $\mv q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M(\mv q)\in\mathbb{R}^{n\times n}$, $\mm C(\mv q,\dot {\mv q})\in\mathbb{R}^{n\times n}$, and $\mm G(\mv q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F(\mv q)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\mm M_0>0,\mm C_0$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
-\begin{equation}
-    \mm M_0\ddot {\mv q}+\mm C_0\dot {\mv q}+\mm G_0 = \mv \tau + \mv f(\mv q,\dot {\mv q},\ddot {\mv q})
-    \label{eq. system dynamics 2}
-\end{equation}
-where $\mv f(\mv q,\dot {\mv q},\ddot {\mv q}) \triangleq -(\mm M-\mm M_0)\ddot {\mv q}-(\mm C-\mm C_0)(\mv q,\dot {\mv q})\dot {\mv q} -(\mm G-\mm G_0) -\mm F(\mv q)$ denotes the residual unknown term.
-
-Hence, the objective of the control design is to make $\mv q$ track the continuously differentiable desired trajectory $\mv q_d(t):\R\to \R^n$ under the unknown terms $\mv f$.
+Consider an uncertain Euler-Lagrange system modeled as
+\begin{equation}
+    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
+    =
+    \sat(\mv\tau)
+    \label{eq:sys1}
+\end{equation}
+where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
+The terms $\mm M\triangleq\mm M(\q)\in\R^{n\times n}$, $\mm V_m\triangleq\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F\triangleq\mm F(\dq)\in\R^{n}$ and $\mm G\triangleq\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+The function $\sat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
+\begin{equation}
+    \sat(\mv\tau)
+    \triangleq
+    \begin{cases}
+        \mv\tau, 
+        & 
+        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
+        \\
+        \bar\tau
+        \cdot
+        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
+        & 
+        \text{otherwise},
+    \end{cases}
+\end{equation}
+where $\bar\tau$ denotes the maximum norm of control input.
+To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
+Section \ref{sec:cstr candidates} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+
+The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
+We introduce the following properties:
+\begin{prop} \cite{Lewis:1998aa}
+    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
+    \label{prop:M}
+\end{prop}
+
+\begin{prop} \cite{Lewis:1998aa}
+    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $\dot{\mm M}-2\mm V_m$ is skew-symmetric.
+    \label{prop:skew}
+\end{prop}
+
+\begin{prop}
+    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
+\end{prop}
+
+In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
+Considering the control input saturation function, $\qd(t)$ is supposed to be available to design a feasible control input in the presence of the control input saturation.
 
@@
 
-In this section, the neuro–adaptive controller is developed.
-Section \ref{sec:ctrl dev} presents the details of the neuro–adaptive controller and the NN model.
-The adaptation law based on the constrained optimization method is derived in Section \ref{sec:adap_laws} by formulating a constrained optimization problem.
-
-\subsection{Neuro–adaptive Control Design} \label{sec:ctrl dev}
-
-The backstepping control-based approach is utilized to generate a reference signal $\mv z^*\triangleq -{k_q}\tilde {\mv q}+\dot {\mv q}_d$ for $\mv {z}\triangleq \dot {\mv q}$, where $\tilde {\mv q}\triangleq \mv {q} - {\mv q}_d$ and $k_q\in\R_{>0}$.
-The desired stabilizing controller can be designed as follows:
-\begin{equation}
-    \mv \tau^* = 
-    -\mm M_0\cdot ({k_z}\tilde {\mv z})
+The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig: controller}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
+Section \ref{sec:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{NN definition} defines the DNN model.
+The weight optimizer will be detailed in Section \ref{sec:adap_laws}.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
+    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
+    \label{fig: controller}
+\end{figure*}
+
+\subsection{Neuro-Adaptive Controller Design}\label{sec:NAC}
+
+First, let us define the filtered tracking error $\fe\in\R^n$ as 
+\begin{equation}
+    \fe \triangleq \dot{\mv e}-\mm\Lambda \mv e
+    ,
+    \label{eq:err:filtered}
+\end{equation}
+where $\mv e \triangleq \q - \qd$ denotes the tracking error, $\dot{\mv e} \triangleq \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
+Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
+
+Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
+\begin{equation}
+    \mm M \dot\fe
+    =
+    -\mm V_m \fe
+    -\mm K \fe
+    + \mv f
+    -\mv \tau_d + \sat(\mv\tau)
+    ,
+\end{equation}
+where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
+    \mv f\triangleq \mv f(\q,\dq,\dqd,\ddqd)
+    =
+    \mm K \fe
+    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
     +
-        ( 
-            -\mm M_0\tilde {\mv q}+\mm C_0{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
+    \mm V_m(-\dqd+\mm\Lambda\mv e)
+    -
+    \mm F
+    -
+    \mm G
+    \in\R^n
+$ denotes the lumped system uncertainty.
+
+Consider the Lyapunov function $\mathcal V_1\triangleq \tfrac{1}{2}\fe^\top \mm M\fe$. 
+Invoking Property \ref{prop:skew}, the time derivative of $\mathcal V_1$ is
+\begin{equation}
+    \begin{aligned}
+        \dot{\mathcal V}_1
+        =&
+        \fe^\top \mm M (
+            -\mm V_m \fe -\mm K \fe + \mv f
+            -\mv \tau_d + \sat(\mv\tau)
         )
-    \label{eq. desired control}
-\end{equation}
-where $\tilde {\mv z}\triangleq \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
-Note that the desired controller cannot be realized because of $\mv f$.
-
-To approximate the desired controller, an NN is utilized.
-The NN with a single hidden layer is represented as 
-\begin{equation}
-    \mv \Phi({\mv q_{NN}};\mv \theta)\triangleq \mm V_1^\top \mv \phi(\mm V_0^\top {\mv q_{NN}})
-\end{equation}
-where ${\mv q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\mm V_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in[0,1]$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\mv \phi:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
-The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\mv \phi(\mv x) = [\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1]^\top $).
-For further simplicity, let $\mv \theta\triangleq[\mv \theta_1^\top ,\mv \theta_0^\top ]^\top \in\R^{\Xi}$ denote the total weight vector, where $\mv \theta_i\triangleq \text{vec}(\mm V_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
-$\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
-
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\mv \theta^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\mv q_{NN}}\in\Omega_{NN}} \allowbreak \Vert\mv \Phi({\mv q_{NN}};\mv \theta^*) - \mv \tau^*\Vert=\epsilon<\infty$ \cite{RN35}.
-% The boundedness of the norm of $\theta^*$  and approximation error $\epsilon$ are also claimed in \cite{RN35}.
-The ideal weight vector $\mv \theta^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\hat{\mv \theta}=[\hat{\mv \theta}_1^\top ,\hat{\mv \theta}_0^\top ]^\top $ of $\mv \theta^*=[\mv \theta_1^{*\top},\mv \theta_0^{*\top}]^\top $, the desired controller $\mv \tau^*\approx -\mv \Phi(\mv q_{NN};\mv \theta^*)-\epsilon$ can be approximated as follows:
-\begin{equation}
-    \mv \tau \triangleq -\mv \Phi({\mv q_{NN}};\hat{\mv \theta}).
-    \label{eq. control law}
-\end{equation}
-For further sections, let $\mv \Phi^*\triangleq\mv \Phi({\mv q_{NN}};\mv \theta^*)$ and $\mv \phi^* \triangleq\mv \phi(\mm V_0^{*\top}{\mv q_{NN}})$, and let $\hat{\mv \Phi}\triangleq{\mv \Phi}({\mv q_{NN}};\hat{\mv \theta})$, $\hat{\mv \phi} \triangleq\mv \phi(\hat {\mm V}_0^{\top}{\mv q_{NN}})$ and $\hat{\mv \phi}' \triangleq \partial \hat{\mv \phi}/\partial (\hat {\mm V}_0^\top \mv q_{NN})$.
-
-Using \eqref{eq.
-system dynamics 2}, \eqref{eq.
-desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi\triangleq[\tilde {\mv q}^\top ,\tilde {\mv z}^\top ]^\top \in\R^{2n}$ as follows:
-\begin{equation}
-    \dot{\mv \xi} 
+        +
+        \tfrac{1}{2}
+        \fe^\top \dot{\mm M}\fe
+        \\
+        =&
+        -
+        \fe^\top \mm K \fe 
+        +
+        \fe^\top (
+            \mv f+\sat(\mv\tau)
+            -\mv \tau_d
+        )
+        +
+        \tfrac{1}{2}
+        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
+        \\
+        \le&
+        -\lambda_\text{min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mv f+\sat(\mv \tau))
+        \\
+        \le&
+        -\lambda_\text{min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\sat(\mv\tau)-\mv\tau^*)
+        ,
+    \end{aligned}
+    \label{eq:lya1:dot1}
+\end{equation}
+where $\mv\tau^*\triangleq -\mv f$ is the ideal control input. 
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
+However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.
+
+To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
+Let $\NN\triangleq\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{NN definition}.
+According to the universal approximation theorem for DNNs \cite{RN33}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\wth^*$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\wth^*) - \mv g(\cdot)} = \mv\epsilon < \infty$.
+Furthermore, the theorem states that the norm of $\wth^*$ is bounded, \ie $\norm{\wth^*}\le \bar\wth<\infty$.
+In this study, $\wth^*$ is defined as a local optimal point, rather than a global optimal point.
+
+In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\NN^*\triangleq\NN(\q_{NN};\wth^*)$ as follows:
+\begin{align}
+    \mv\tau^*=& -(\NN^*+\mv\epsilon),
+    \label{eq:control:ideal}
+\end{align}
+which is estimated online by
+\begin{align}
+    \mv\tau =& -\hat\NN,
+    \label{eq:control:est}
+\end{align}
+where $\hat\NN\triangleq\NN(\q_{NN};\hat\wth)$, and  $\hat\wth$ is the estimated weight vector for $\wth^*$.
+
+Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $\mathcal V_1$ can be rewritten as
+\begin{equation}
+    \dot{\mathcal V}_1
+    \le 
+    -\lambda_\text{min}(\mm K)\norm{\fe}^2
+    +
+    \bar\tau_d\norm{\fe}
+    +
+    \fe^\top (\sat(\hat\NN)-\NN^*-\mv\epsilon)
+    .
+    \label{eq:lya1:dot2}
+\end{equation}
+Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\hat\wth$ to $\wth^*$ (\ie $\hat\NN\to\NN^*$).
+
+\subsection{Deep Neural Network (DNN) Model}\label{NN definition}
+
+The DNN architecture $\NN_k = \NN(\q_{NN};\wth)$ can be recursively represented as follows:
+\begin{equation}
+    \NN_i \triangleq
+    \begin{cases}
+        \wV_i^\top \NN_i(\NN_{i-1}), 
+        &
+        i\in[1,\dots,k],
+        \\
+        \wV_0^\top \q_{NN},
+        &
+        i=0
+        ,
+    \end{cases}
+    \label{eq. DNN structure 2}
+\end{equation}
+where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
+The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).
+
+One of the widely used activation functions for large DNNs is from the ReLU family \cite{RN27}, which effectively avoids the gradient vanishing problem during error backpropagation. 
+However, for control applications, where relatively shallow DNNs are typically sufficient and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
+These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\dtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x)),\ \forall x\in\R$, which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\dtfrac{\sigma(x)}{x}}< 1$.
+
+For simplicity, each layer's weights are vectorized as $\wth_i\triangleq\textit{vec}(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i\triangleq (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer.
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmentating $\wth_i$ for all $i\in \left[0,\cdots,k\right]$ as 
+\begin{equation}
+    \wth \triangleq 
+    \begin{bmatrix}
+        \wth_k\\
+        \wth_{k-1}\\
+        \vdots\\
+        \wth_0
+    \end{bmatrix}
     =
-    \mm A_\xi{\mv \xi}+\mm B_\xi(\mv \Phi^*-\hat{\mv \Phi}+\epsilon)
+    \begin{bmatrix}
+        \textit{vec}(\wV_k)\\
+        \textit{vec}(\wV_{k-1})\\
+        \vdots\\
+        \textit{vec}(\wV_0)
+    \end{bmatrix},
+\end{equation}
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
+\begin{equation}
+    \ptfrac{\NN}{\wth}=
+    \begin{bmatrix}
+        \ptfrac{\NN}{\wth_k}&
+        \ptfrac{\NN}{\wth_{k-1}}&
+    \cdots &
+        \ptfrac{\NN}{\wth_0}
+    \end{bmatrix}
+    \in\R^{n \times \Xi}
+    \label{eq. nabla phi}
 \end{equation}
@@
 \begin{equation}
-    \mm A_\xi \triangleq 
-    \begin{bmatrix}
-        -{k_q} \mm I_{n\times n} &\mm I_{n\times n}
-        \\
-        -\mm I_{n\times n}& -{k_z} \mm I_{n\times n}
-    \end{bmatrix}
-    ,\ 
-    \mm B_\xi \triangleq 
-    \begin{bmatrix}
-        \mm 0_{n\times n}\\\mm M_0^{-1}
-    \end{bmatrix}.
-\end{equation}
-
-\subsection{Adaptation Law Derivation}\label{sec:adap_laws}
-
-Using the augmented error $\mv \xi$, the quadratic objective function is defined as
-\begin{equation}
-    J(\mv \xi;\hat{\mv \theta})\triangleq
-    {1\over 2}
-    \mv \xi^\top \mm W\mv \xi
-\end{equation}
-where $\mm W=\mm W^\top >0$ denotes the weighting matrix.
-
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\Vert{\hat{\mv\theta}}_i\Vert^2-\bar\theta^2_i,\ i\in[0,1]$.
-% Then the objective of the adaptation process can be reformulated into the constrained optimization problem as follows:
-The control problem can be reformulated into a constrained optimization problem as follows:
+    \ptfrac{\NN}{\wth_i} = 
+    \begin{cases}
+        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
+        &
+        i=k 
+        \\
+        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
+        & 
+        i=k-1
+        \\
+        &
+        \vdots 
+        \\
+        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
+        &
+        i = 0
+    \end{cases},
+\end{equation}
+where $\act_i\triangleq \act_i(\NN_{i-1})$ and $\act_i'\triangleq \ptfrac{\act_i}{\NN_{i-1}}$.
+
+In the following sections, let $\NN^*_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\wth^*$. 
+Additionally, define $\act^*_i\triangleq\act_i(\NN^*_{i-1})$ and $\act^{*'}_i\triangleq \ptfrac{\act^*_i}{\NN^*_{i-1}}$. 
+Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i\triangleq\act_i(\hat\NN_{i-1})$ and $\hat\act_i'\triangleq \ptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
+
+%  SECTION ADAPTATION LAW DERIVATION =======================
+\section{Weight Adaptation Laws}\label{sec:adap_laws}
+
+% \subsection{Adaptation Law using Lagrangian Function}
+\subsection{Weight Optimizer Design}
+
+Consider a positive definite objective function defined as 
+\begin{equation}
+    J(\fe;\hat\wth)\triangleq 
+    \tfrac{1}{2} \fe^\top  \mm W\fe
+\end{equation}
+where $\mm W\in\R^{n\times n}$ is symmetric positive weighting matrix.
+Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
+The corresponding constrained optimization problem is formulated as
 \begin{equation}
     \begin{matrix}
-        \min_{{\hat{\mv\theta}}} \ J(\mv \xi;{\hat{\mv\theta}})
+        \min_{\hat\wth} \ J(\fe;\hat\wth)
         \\ \\
         \begin{aligned}
-        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I = [\theta_0,\theta_1].
+        \text{s.t. }&c_{j}(\hat\wth) 
+        \le0, \quad j\in\mathcal{I},
         \end{aligned}
     \end{matrix}
-\end{equation}
-In this optimization problem, $\xi$ is considered a predefined parameter.
-The corresponding Lagrangian function is defined as
+    \label{eq. train obj}
+\end{equation}
+Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
 \begin{equation}
     L(
-        \mv \xi,
-        {\hat{\mv\theta}},
-        [\lambda_j]_{j\in\mathcal I}
+        \fe,\hat\wth,[\lambda_j]_{j\in\mathcal I}
     ) 
     \triangleq 
-    J(\mv \xi;{\hat{\mv\theta}})
+    J(\fe;\hat\wth) 
     + 
-    \sum_{j\in\mathcal I} \lambda_jc_j({\hat{\mv\theta}})
-    .
-\end{equation}
-% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{{\hat{\mv\theta}}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
+    \sum_{j\in\mathcal I}
+    \lambda_{j}
+    c_{j}(\hat\wth)
+\end{equation}
+where $\lambda_j$ denotes the Lagrange multiplier for each constraint.
+
+The adaptation laws for $\hat\wth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq.
+train obj} (\ie  $\min_{\hat\wth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\hat\wth,[\lambda]_{j\in\mathcal I})$), as follows:
+\begin{subequations}
     \begin{align}
-        \dot {{\hat{\mv\theta}}}&=-\alpha {\partial L\over\partial {\hat{\mv\theta}}}
+            \dot {\hat\wth}&=-\alpha {\partial L\over\partial \hat\wth}
             =-\alpha 
             \bigg(
-        {\partial J\over \partial {\hat{\mv\theta}}}+\sum_{j\in\mathcal{A}}
-        \lambda_j {\partial c_j\over \partial {\hat{\mv\theta}}}
+            {\partial J\over \partial \hat\wth}+\sum_{j\in\mathcal{I}}
+            \lambda_j {\partial c_j\over\partial \hat\wth}
             \bigg),
@@
             \lambda_j & = \max(\lambda_j,0) ,
-        \quad\quad\quad\quad\ \ \ \ \ 
-        \forall j\in\mathcal I,
         \label{eq. adaptation law L max}
     \end{align}
-where $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
-\color{red}
-% The Eq.~\eqref{eq.
-adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
-\color{black}
-
-Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\partial J/\partial {\hat{\mv\theta}}$) in \eqref{eq. adaptation law th} can be represented as
-\begin{equation}
-    {\partial J\over\partial {\hat{\mv\theta}}}
+    \label{eq. adaptation law}
+\end{subequations}
+where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
+When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation.
+Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
+Note that this adaption law is similar to the ALM in \cite{RN22}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-c_j/\mu,0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\dot{\hat\wth}=0$ and $\dot\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \hat\wth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{RN22}.
+In other words, the proposed optimizer updates $\hat\wth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
+These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
+% The KKT condition is satisfied, when $\hat\wth$ converges to $\wth^*$, since $\partial L/\partial \hat\wth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).
+
+\subsection{Calculation of the Exact Gradient of Objective Function}
+
+\MSRY{NEED TO BE REVISED}
+The adaptation law for $\hat\wth$ involves the gradient of the objective function with respect to $\hat\wth$ (\ie ${\partial J/\partial \hat\wth}$); see \eqref{eq.
+adaptation law th}.
+Since the objective function depends on the state $\xi$ of a dynamic system, obtaining the gradient is not straightforward.
+Therefore, the forward sensitivity method from \cite{RN12} is employed to calculate the exact gradient of the objective function.
+
+By partially differentiating \eqref{eq. xi dynamics}, the sensitivity equation of $\xi$ with respect to $\hat\wth$ is first obtained as
+\begin{equation}
+    \dot\eta = A_\xi\eta - B_\xi{\partial h\over\partial \tau}{\partial\hat\Phi\over\partial\hat\wth}
+    \label{eq. eta dynamics 1}
+\end{equation}
+where $\eta \triangleq \partial \xi/\partial \hat\wth\in\mathbb R^{2n\times \Xi}$.
+Since the initial value of $\xi$ is independent to $\hat\wth$, $\eta|_{t=0}$ is a zero matrix. The gradient of the objective function with respect to $\hat\wth$ is then obtained as 
+\begin{equation}
+   {\partial J\over\partial \hat\wth} =  {\partial \xi\over \partial \hat\wth}^\top  W\xi=\eta^\top  W\xi\in\R^\Xi.
+   \label{eq. dJdth}
+\end{equation}
+Equations \eqref{eq. eta dynamics 1} and \eqref{eq. dJdth} can be decomposed for each layer as 
+\begin{equation}
+    \begin{aligned}
+        \dot \eta&= 
+        \begin{bmatrix}
+            \eta_k&
+            \eta_{k-1}&
+            \cdots &
+            \eta_0
+        \end{bmatrix}'
+        \\
+        &=A_\xi
+        \begin{bmatrix}
+            \eta_k&
+            \cdots &
+            \eta_0
+        \end{bmatrix}
+        -B_\xi{\partial h\over\partial \tau}
+        \begin{bmatrix}
+            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top  )&
+        \cdots&
+        (\cdot)
+        \end{bmatrix}
+    \end{aligned}
+    \label{eq. eta dynamics}
+\end{equation}
+and
+\begin{equation}\label{eq. grad_J}
+    {\partial J\over\partial\hat\wth}
     =
-    {\partial \mv\xi\over\partial {\hat{\mv\theta}}}^\top 
-    \mm W
-    {\partial \mv\xi\over\partial {\hat{\mv\theta}}}
+    \begin{bmatrix}
+        \partial J/\partial\hat\wth_k\\\vdots\\\partial J/\partial\hat\wth_0\\
+    \end{bmatrix}    =
+    \begin{bmatrix}
+        \eta_k^\top\\\vdots\\\eta_0^\top\\
+    \end{bmatrix}
+    W
+    \xi
+\end{equation}
+where $\eta_i \triangleq \partial \xi/\partial \hat\wth_i\in\mathbb R^{2n\times \Xi_i}$.
+The exact gradient of the objective function is calculated based on \eqref{eq.
+dJdth}, with the value of $\eta$ obtained by simulating the sensitivity equation \eqref{eq.
+eta dynamics 1}.
+
+The proposed controller is implemented using Algorithm \ref{alg: alg1}.
+For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
+If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{RN22} to ensure that the objective function decreases.
+
+\begin{algorithm}[!t]
+    \caption{Weight Optimizer Implementation.}\label{alg: alg1}
+    \begin{algorithmic}[1]
+        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+        \renewcommand{\algorithmicensure}{\textbf{Output:}}
+        \REQUIRE $\xi$, $\hat\wth$, $\lambda_j$, $\eta$
+        \ENSURE  $\hat\wth$, $\lambda_j$, $\eta$
+        \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
+        \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
+        \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
+        \STATE Determine update directions $\dot{\hat\wth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
+        \STATE Update weight vector $\hat\wth\leftarrow \hat\wth+\dot{\hat\wth}\cdot T_s$;
+        \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
+        \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
+        \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
+        \STATE \textbf{RETURN};
+    \end{algorithmic}
+    \label{alg1}
+\end{algorithm}
+
+ \section{Constraint Candidates}\label{sec:cstr candidates}
+
+This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller. 
+The controller can handle any combination of the following constraints, provided they meet the specified assumptions.
+
+\begin{assum}
+    The constraint functions $c_j(\hat\wth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\wth^*)\le 0$.
+    \label{assum1}
+\end{assum}
+
+% \begin{assum}
+%     The Frobenius norm of $\partial c_j/\partial\hat\wth_i$ is bounded. %when the norms of $\hat\wth_i,\ \forall i [k,\cdots,i+1]$ are bounded.
+%     \label{assum2}
+% \end{assum}
+
+% The Assumption \ref{assum2} also means that the boundedness of $\Vert\hat\wth_k\Vert$ implies the boundedness of $\Vert\partial c_j/\partial \hat\wth\Vert_F$, since $\tau=-\hat V_k\hat\phi_k$ is bounded when $\Vert\hat\wth_k\Vert$ bounded \ie $\Vert\phi(\cdot)\Vert$ is already bounded.
+
+\begin{assum}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{RN22}.
+    \label{assum2}
+\end{assum}
+
+\subsection{Weight Norm Constraint}\label{sec:cstr weight ball}
+
+The weight norm constraint $\mathbf{c}_{\theta}\triangleq [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ limits the maximum norm of each layer's weight vector, where
+\begin{equation}
+    c_{\theta_i}
+    =
+    \Vert \hat\wth_i\Vert^2 
+    -
+    \bar\theta_i^2 \le 0
+    \label{eq. cstr weight ball}
+\end{equation}
+with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\hat\wth_i$. 
+The gradient of $\mathbf{c}_\theta$ with respect to $\hat\wth$ is given by
+\begin{equation}\label{eq weight norm cnst grad}
+    {\partial \mathbf c_\theta \over \partial \hat\wth}
+    \triangleq
+    \begin{bmatrix}
+        (\partial c_{\theta_0}/\partial \hat\wth)^\top
+        \\ 
+        \vdots 
+        \\
+        (\partial c_{\theta_k}/\partial \hat\wth)^\top
+    \end{bmatrix}
+    = 2\cdot 
+    \begin{bmatrix}
+        0&0&\cdots & \hat\wth_0^\top\\
+        \vdots&\vdots&\ddots&\vdots\\
+        0&\hat\wth^\top_{k-1}&\cdots &0\\
+        \hat\wth^\top_k&0&\cdots &0
+    \end{bmatrix}
+    \in\mathbb R^{(k+1)\times\Xi}
     .
 \end{equation}
-The calculation of $\partial J/\partial {\hat{\mv\theta}}$ is not straightforward because of the dynamics of $\xi$.
-Using the forward sensitivity method presented in \cite{RN34}, the sensitivity equation can be obtained as follows:
-\begin{equation}
-    \dot {\mm \eta} =
-    \mm A_\xi - \mm B_\xi 
-    % (\partial \hat{\mv\Phi}/\partial {\hat{\mv\theta}})
-    {\partial \hat{\mv\Phi}\over\partial {\hat{\mv\theta}}}
+%As demonstrated in Section \ref{sec:stability}, the weight norm constraint should be imposed on the controller to ensure the boundedness of the tracking error and weight estimation.
+
+%\begin{remark} Imposing the weight norm constraint is analogous to applying $L_2$-regularization, a common technique used in DNN training to prevent parameter drift or overfitting \cite{RN23}, by minimizing the $L_2$ norm of the estimated weight vector $\hat\wth$.
+Typically, $L_2$-regularization adds a term $\lambda\Vert\hat\wth\Vert_2^2$ to the objective function $J$, where $\lambda\in\mathbb R_{>0}$ is a constant $L_2$ coefficient.
+This term biases the trainable weights $\hat\wth$ toward the origin (\ie $\hat\wth = 0$) in the adaptation law \eqref{eq.
+adaptation law th}.
+In contrast, within the proposed controller, the term associated with the maximum weight ball constraint in the adaptation law (\ie $\sum_{j\in\mathcal{A}}\lambda_j (\partial c_j/\partial \hat\wth)$ in \eqref{eq.
+adaptation law th}) vanishes when the constraint is satisfied (\ie $\lambda_j = 0$).
+    % 1. 제약조건이 사라져 자유롭게 ball condition 내에서 optimal point로 접근할 수 있다.
+%    As a result, $\hat\wth$ can still converge to $\wth^*$ without being restricted to the origin.
+%    Moreover, $\lambda_{b_i}$ which corresponds to $\lambda$ varies as the constraint is violated, while $L_2$-regularization has a constant coefficient.
+%    \label{remark: ball cstr}
+%\end{remark}
+
+\subsection{Input Bound Constraint}
+
+Most physical systems have control input limits due to electrical and mechanical limitations.
+These are expressed as $\mathbf{c}_{\overline \tau}\triangleq [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\mathbf{c}_{\underline\tau}\triangleq [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+\begin{equation}
+    \begin{aligned}
+        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
+        \\
+        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+    \end{aligned}
+    \label{eq. cstr input saturation}
+\end{equation}
+with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
+% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
+The gradients of $\mathbf{c}_{\overline \tau}$ and $\mathbf{c}_{\underline\tau}$ with respect to $\hat\wth$ are given by
+\begin{equation}
+    \begin{aligned}
+        {\partial \mathbf \mathbf c_{\overline \tau} \over \partial \hat\wth}
+        & 
+        \begin{bmatrix}
+            (\partial c_{\overline \tau_1}/\partial \hat\wth)^\top \\
+            \vdots \\
+            (\partial c_{\overline \tau_n}/\partial \hat\wth)^\top
+        \end{bmatrix}
+         = -{\partial \hat\Phi\over\partial\hat\wth}
+         \\
+        =&
+        -\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
         , 
-    \label{eq. sen eq}
-\end{equation}
-where ${\mm \eta}\triangleq \partial \mv\xi/\partial {\hat{\mv\theta}}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
-The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
-By decomposing for each layer, the dynamics of ${\mm \eta}_i\triangleq \partial \mv\xi/\partial {\hat{\mv\theta}}_i\in\R^{2n\times \Xi_i}$ can be represented as
-\begin{equation}
-    \begin{aligned}
-        \dot{\mm \eta} =&
+        \\
+        {\partial \mathbf \mathbf c_{\underline\tau} \over \partial \hat\wth}         
+        \triangleq
+        & 
         \begin{bmatrix}
-            {\mm \eta}_1&{\mm \eta}_0
-        \end{bmatrix}'
+            (\partial c_{\underline\tau_1}/\partial \hat\wth)^\top \\
+            \vdots \\
+            (\partial c_{\underline\tau_n}/\partial \hat\wth)^\top
+        \end{bmatrix}
+        = +{\partial \hat\Phi\over\partial\hat\wth}
         \\
         =&
-        \mm A_\xi
-        % \begin{bmatrix}
-        [
-            {\mm \eta}_1
-            \ \ 
-            {\mm \eta}_0
-        ]
-        % \end{bmatrix}
-        -\mm B_\xi
-        % \begin{bmatrix}
-        [
-            (\mm I_{l_2}\otimes \hat{\mv\phi}^\top )
-            \ \ 
-            \hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_{l_1}\otimes {\mv q_{NN}}^\top )
-        ]
-        % \end{bmatrix}
+        +\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
         .
     \end{aligned}
-\end{equation}
-The calculation of $\partial \hat{\mv\Phi}/\partial{\hat{\mv\theta}}$ is introduced in \cite{RN36}.
-In conclusion, the gradient of the objective with respect to the weights can be obtained as ${\partial J/\partial {\hat{\mv\theta}}} = {\mm \eta}^\top\mm W\mv\xi$ by simulating the sensitivity equation \eqref{eq.
-sen eq}.
-
-On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
-\begin{equation}
-    \frac{\partial c_{\theta_0}}{\partial{\hat{\mv\theta}}}
+    \label{eq. nabla input sat}
+\end{equation}
+
+\subsection{Input Norm Constraint}\label{sec:input_norm_cnst}
+
+Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
+Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
+This can be captured by the following inequality constraint:
+\begin{equation}
+    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
+    \label{eq. cstr input ball}
+\end{equation}
+with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
+This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{RN62}.
+% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
+The gradients of $c_{u}$ with respect to $\hat\wth$ are given by
+\begin{equation}
+    {\partial \mathbf \mathbf c_{u} \over \partial \hat\wth}
+    = -\sum_{i=1}^n 2\tau_{(i)} 
+    \bigg(
+        \text{row}_i
+        \bigg(
+            -{\partial \hat\Phi\over\partial\hat\wth}
+        \bigg)
+    \bigg)^\top  
+    = \tau^\top (I_{l_{k+1}}\otimes \hat\phi_k^\top)
+    \in \mathbb R^{\Xi}.
+    \label{eq. nabla input ball}
+\end{equation}
+It should be noted that constraints \eqref{eq.
+cstr input saturation} and \eqref{eq.
+cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
+nabla input sat} and \eqref{eq.
+nabla input ball} are linearly dependent, violating the LICQ condition.
+
+%  SECTION STABILITY ANALYSIS ==============================
+\section{Stability Analysis}\label{sec:stability}
+
+Before conducting the stability analysis, let $\tilde\wth\triangleq [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i\triangleq\hat\wth_i-\wth^*_i$ represents the weight estimation error.
+The following Lemmas are introduced for the stability analysis.
+% of the last layer of the DNN.
+\begin{lem}
+    If Assumptions \ref{assum1} and \ref{assum2} are satisfied, the angle between $\partial c_j/\partial \hat\wth_k$ and $\hat\wth_k$ is positive when $c_j$ is active set, \ie $(\partial c_j/\partial \hat\wth_k)^\top\hat\wth_k>0$.
+    \label{lem1}
+\end{lem}
+
+%\begin{figure}[!t]
+%    \centering
+%    \includegraphics[width=.99\linewidth]{spaces.drawio.png}
+%    \caption{Convexity of input constraints.}
+%    \label{fig: spaces}
+%\end{figure}
+
+\begin{proof}
+
+Since $\tau = -\hat\Phi$, using \cite[Proposition 7.1.9]{RN17}, a linear map $T(\cdot):\hat\wth_k\to\tau$ can be derived: 
+\begin{equation}\label{eq linear map}
+    \begin{aligned}
+    \tau = &-\hat\Phi = -\textit{vec}(\hat\Phi)     = -\textit{vec}(\hat V_k \hat\phi_k) 
+    \\
+    = & -(I_{l_{k+1}}\otimes \hat\phi_k^\top)\textit{vec}(\hat V_k)
+    =-(I_{l_{k+1}}\otimes \hat\phi_k^\top)\hat\wth_k = T(\hat\phi_k) \hat\wth_k.
+    \end{aligned}
+\end{equation}
+Therefore, the convexity of the input constraints in $\tau$-space (assumed in Assumption \ref{assum1}) holds in $\hat\wth_k$-space, implying
+%, as depicted in Fig.~\ref{fig: spaces}. 
+that $(\partial c_j/\partial \hat\wth_k)^\top\hat\wth_k>0$.
+
+\end{proof}
+
+% \begin{assum}
+%     The Frobenius norm of $\partial c_j/\partial\hat\wth_i$ is bounded. %when the norms of $\hat\wth_i,\ \forall i [k,\cdots,i+1]$ are bounded.
+%     \label{assum2}
+% \end{assum}
+
+\begin{lem} 
+    If $c_j(\hat\wth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum1}, then $\Vert\partial c_j/\partial\hat\wth_i\Vert$, for all $i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\hat\wth_i$, for all $i\in[k,\cdots, i+1]$, remain bounded.
+    % which can be verified using the boundedness of $\hat\wth_i,\ \forall i [k,\cdots,i+1]$ (as demonstrated in Section \ref{sec:stability}), and the boundedness of $\Vert\phi_i(\cdot)\Vert$ and $\Vert\nabla\phi_i(\cdot)\Vert$.
+    \label{lem2}
+\end{lem}
+
+\begin{proof}
+
+The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\hat\wth_i$ is represented as
+\begin{equation}
+    {\partial c_j\over\partial \hat\wth_i} = {\partial c_j\over\partial \tau} {\partial \tau\over\partial \hat\Phi} {\partial \hat\Phi\over\partial \hat\wth_i}
+\end{equation}
+where $\partial \tau/\partial \hat\Phi=-I_n$, which is bounded.
+From the linear mapping in \eqref{eq linear map}, $\tau$ is bounded as long as $\hat\wth_k$ is bounded (by the condition of the lemma), and $\Vert\phi_k(\cdot)\Vert$ is bounded due to the properties of the activation functions.
+By Assumption \ref{assum1}, the function $c_j$ is convex.
+The convex function has a bounded derivative with respect to $\tau$, since $\tau$ is a bounded variable (\ie $\partial c_j/\partial\tau$ is bounded).
+Furthermore, $\partial \hat\Phi/\partial \hat\wth_i$ is bounded, provided that the norms of $\hat\wth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded.
+This can be verfied by using the definition of $\partial \hat\Phi/\partial\hat\wth_i$ given in \eqref{eq.
+nabla phi}.
+Consequently, $\Vert\partial c_j/\partial \hat\wth_i\Vert,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\hat\wth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+
+\end{proof}
+
+The following theorem shows that $\hat\wth$ and $\xi$ are bounded.
+
+\begin{theorem}
+    For the dynamical system in \eqref{eq.
+system dynamics 1}, the neuro-adaptive controller \eqref{eq.
+approximated control} and weight adaptation laws \eqref{eq.
+adaptation law th}, \eqref{eq.
+adaptation law L}, and \eqref{eq.
+adaptation law L max} ensure the boundedness of the augmented error $\xi$ and the weight estimate $\hat \wth$.
+This holds with the weight norm constraint \eqref{eq.
+cstr weight ball} and input constraints satisfying Assumption \ref{assum1} and \ref{assum2}, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
+ctrl stable condition}.
+\end{theorem}
+
+\begin{proof}
+
+The boundednesses of $\hat\wth$, $\xi$, and $\eta$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\hat\Phi$.
+The step-by-step analysis is described as follows.
+
+\subsection*{Step 1: Boundedness of $\hat\wth_k,\eta_k$, and $\xi$}
+% \subsubsection*{Step 1: Boundedness of $\hat\wth_k,\eta_k,\xi$}
+
+% Noting that $\Phi^* = V_k^{*T}\phi^*_k$ and $\hat\Phi = \hat V_k^{T}\hat \phi_k$, the error dynamics \eqref{eq.
+xi dynamics} can be rewritten by adding and substracting $V_k^{*T}\hat\phi_k$ on the right side as follows:
+% \begin{equation}
+%     \begin{aligned}
+%         \dot \xi &= A_\xi\xi +B_\xi
+%         \bigg( 
+%             (V^*_k - \hat V_k)^\top   \hat\phi_{k} + V^{*T} (\phi_{k}^*-\hat\phi_{k} ) +\epsilon
+%         \bigg)\\
+%         &=A_\xi\xi  + B_\xi
+%         \bigg( 
+%             (V^*_k - \hat V_k)^\top   \hat\phi_{k} +w(t)
+%         \bigg)
+%     \end{aligned}
+% \end{equation}
+% where $w(t) \triangleq V_k^{*T} (\phi^*_{k} - \hat\phi_{k} ) + \epsilon$ is the bounded unknown term, given that $\phi_k(\cdot)$ , $V_k^*=\textit{vec}^{-1}(\wth^*_k)$ and $\epsilon$ are bounded.
+
+The boundedness of $\xi$ follows from \eqref{eq.
+xi dynamics}, using the result from \cite[Chap.~4 T.~1.9]{RN13}, since $A_\xi$ is a stable matrix and the term $B_\xi (\Phi^*-h(\hat\Phi)+\epsilon)$ is bounded due to $\Vert B_\xi\Vert_F$, $\Vert V_k^*\Vert_F$, $\Vert \phi(\cdot)\Vert$, $\Vert h(\cdot)\Vert$, and $\Vert\epsilon\Vert <\infty$.
+
+%The weight norm constraint $\mathbf{c}_{b}\triangleq [c_{b_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ presented in Section \ref{sec:cstr candidates} is imposed on the controller.
+%Additional constraints that satisfy Assumptions \ref{assum1}, \ref{assum2} and \ref{assum3} can be imposed and the constraint candidates are introduced in Section \ref{sec:cstr candidates}.
+
+Assume that all constraints are actve in $\mathcal A$ without loss of generality.
+The dynamics of $\eta_k$ and $\hat\wth_k$ can be decomposed from \eqref{eq.
+adaptation law th} and \eqref{eq.
+eta dynamics} as
+\begin{equation}
+    \begin{aligned}
+        \dot\eta_k =
+        & 
+        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}{\partial \hat\Phi\over \partial \hat\wth_k}
+        =
+        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}(I_{l_{k+1}}\otimes \hat\phi_k^\top)\\
+        \dot{\hat\wth}_k =
+        & -\alpha 
+        \bigg[
+            \eta_k^\top W\xi+
+            \sum_{j\in\mathcal{A}}
+            \lambda_j{\partial c_j\over\partial \hat\wth_k}
+        \bigg]
+    \end{aligned} 
+\end{equation}
+According to \cite[Chap.~4 T.~1.9]{RN13}, $\Vert \eta_k\Vert_F$ is bounded, since $A_\xi$ is a stable matrix and the term $-B_\xi(\partial h/\partial \tau)(I_{l_{k+1}}\otimes\hat\phi_k^\top)$ is also bounded.
+
+Let $\mathcal{V}: \R^{2n} \times \R^{\Xi} \to \R_{>0}$ denote the Lyapunov function:
+\begin{equation}
+    \mathcal{V} = \frac{1}{2} \xi^\top P \xi + \frac{1}{2 \alpha} \hat{\wth}_k^\top \hat{\wth}_k,
+    \label{eq. Lyapunov func}
+\end{equation}
+with the Lyapunov equation $A_\xi^\top P + P A_\xi = -Q$, where $A_\xi < 0$, $P = P^\top > 0$, and $Q > 0$.
+Taking the time derivative of $\mathcal{V}$ yields:
+\begin{equation}
+    \begin{aligned}
+        \dot{\mathcal{V}} 
+        &= -\frac{1}{2} \xi^\top Q \xi + \xi^\top P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon) \\
+        &\quad - \hat{\wth}_k^\top \left( \eta_k W \xi + \sum_{j \in \mathcal{A}} \lambda_j \frac{\partial c_j}{\partial \hat{\wth}_k} \right)
+    \end{aligned}
+    \label{eq. Lyapunov dot}
+\end{equation}
+By applying the boundedness of $\Delta \triangleq P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon)$ and $M \triangleq \eta_k W$, where $\Vert \Delta \Vert \leq \bar{\Delta} < \infty$ and $\Vert M \Vert_F \leq \bar{M} < \infty$, this simplifies to:
+\begin{equation}
+    \begin{aligned}
+        \dot{\mathcal{V}} 
+        &\leq \left( -\frac{\lambda_{\text{min}}(Q)}{2} + \frac{\bar{M}}{2} \right) \Vert \xi \Vert^2 + \bar{\Delta} \Vert \xi \Vert \\
+        &\quad + \frac{\bar{M}}{2} \Vert \hat{\wth}_k \Vert^2 - \sum_{j \in \mathcal{A}} \lambda_j \hat{\wth}_k^\top \frac{\partial c_j}{\partial \hat{\wth}_k}.
+    \end{aligned}
+    \label{eq. dot Vk 1}
+\end{equation}
+
+By representing the term $\partial c_{\wth_k}/\partial \hat\wth_k$ in the last inequality as $\partial c_{\wth_k}/\partial \hat\wth_k=2\hat\wth_k$ using the result provided in \eqref{eq weight norm cnst grad}, $\dot {\mathcal V}$ can be rewritten as
+\begin{equation}
+    \begin{aligned}
+        \dot {\mathcal V} \le&
+        (\cdot) + 
+        \bigg(
+            -2\lambda _{\wth_k}+{\bar M}/{2}
+        \bigg)
+        \Vert\hat\wth_k\Vert^2 
+        \\
+        &- \underbrace{
+        \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\hat\wth_k^\top{\partial c_j\over\partial \hat\wth_k}
+        }_{>0, \text{\;by Lemma} \ref{lem1} \text{\;and\;} \text{Assumption} \ref{assum2}}	
+        \\
+        \le&
+        \bigg(
+            -{\lambda_\text{min}(Q)}/{2}+{\bar M}/{2}
+        \bigg)
+        \Vert\xi\Vert^2
+        +\bar \Delta \Vert \xi\Vert 
+        \\&
+        + 
+        \bigg(
+            -2\lambda _{\wth_k}+{\bar M}/{2}
+        \bigg)
+        \Vert\hat\wth_k\Vert^2 
+    \end{aligned}
+    \label{eq. dot Vk 2}
+\end{equation}
+%From \eqref{eq. dot Vk 2}, by defining $P=I_2$, if the control gains ${k_q}$ and ${k_z}$ are selected sufficiently large such that
+Define $P=I_2$, leading to $Q = -A_{\xi}^\top - A_{\xi}$.
+Consequently, the minimum eigenvalues ${\lambda_{\text{min}}(Q)}$ is determined by $2\min({k_q},{k_z})$, as follows from the structure of the matrix $A_{\xi}$.
+From \eqref{eq.
+dot Vk 2}, if the control gains ${k_q}$ and ${k_z}$ are chosen sufficiently large to satisfy the condition:
+%is a function of $k_q$ and $k_z$, as per the definition of matrix $A_{\xi}$. From \eqref{eq. dot Vk 2}, if the control gains ${k_q}$ and ${k_z}$ are chosen sufficiently large such that
+\begin{equation}
+    % -\lambda_\text{min}(Q)/2+M/2<0
+    \min({k_q},{k_z})>\bar M/2
+    \label{eq. ctrl stable condition}
+\end{equation}
+and if the Lagrange multiplier $\lambda_{\wth_k}$ for the weight norm constraint of the $k\textsuperscript{th}$ layer is increased sufficiently, such that
+\begin{equation}\label{eq: lambda bk}
+    -2\lambda_{\wth_k} +{\bar M/ 2}<0,  
+\end{equation}
+(as dictated by \eqref{eq.
+adaptation law L} when the corresponding constraint is violated, \ie $c_{\wth_k}=\Vert \hat\wth_k\Vert^2 -\bar\wth_k^2 > 0$), then both $\xi$ and $\hat\wth_k$ will remain bounded within the compact sets $\wth_\xi$ and $\wth_{\hat\wth_k}$, defined as
+\begin{equation}
+    \wth_\xi = 
+    \bigg\{ \xi \ \bigg\vert\ \Vert\xi\Vert \le  
+    {2\bar \Delta\over \lambda _\text{min}(Q)-\bar M} 
+    \bigg\}
+\end{equation}
+and
+\begin{equation}\label{eq: hat wth k bnd}
+    \wth_{\hat\wth_k} = 
+    \{
+    \hat\wth_k 
+    \ 
+    \vert
+    \ 
+    \Vert
+    \hat\wth_k\Vert \le  
+    \bar\wth_k
+    \}
+    .
+\end{equation}
+The increase of the Lagrange multiplier $\lambda_{\wth_k}$ will halt once $\hat \wth_k$ reaches the compact set $\wth_{\hat\wth_k}$. Thus, the Lagrange multiplier $\lambda_{\wth_k}$ is bounded.
+% Note that the compact set $\wth_{\hat\wth_k}$ implies that the input norm constraint for the last $k\textsuperscript{th}$ layer is satisfied because the condition \eqref{eq: lambda bk} is fulfilled in the case of constraint violation.
+
+%Note that $\wth_{\tilde\wth_k}$ converges to $\{\tilde\wth_k\  \vert \ \Vert\tilde\wth_k\Vert\le\bar\wth_k\}$, if $\lambda_{b,k}$ increases such that $4\lambda_{b,k} \gg  \bar M_k$.
+
+% To analyze the boundedness of the Lagrange multipliers, let $\mathcal V_2$ be defined as
+
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=0.7\linewidth]{lyapunov.drawio.png}
+%     \caption{caption.}
+%     \label{fig: V space}
+% \end{figure}
+
+The boundedness of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal A\setminus\{\wth_i\}_{i\in[0,\cdots,k]}$, can be accessed by considering the convexity of the constraints in $\hat\wth_k$-space.
+The boundedness of the remaining Lagrange multipliers associated with the weight norm constraints, $\lambda_{\wth_r},\ \forall r\in[0,\cdots,k-1]$, will be examined in Step $i$.
+Based on Assumption \ref{assum1} and Lemma \ref{lem1},
+%(\ie the constraint is convex on $\tau$-space and $\hat\wth_k$-space, including the origin), 
+the equality constraints $c_j \le 0, \ \forall j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, formconvex sets $\wth_{c_j}$ in $\hat\wth_k$-space.
+Let $\wth_c\triangleq \cap_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots ,k]}} \wth_{c_j}$ represent the intersection of these convex sets, which also contains the origin.
+If $\lambda_j$ increases sufficiently such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\hat\wth_k^\top(\partial c_j/\partial \hat\wth_k)<0$, then ${\mathcal V}$, and consequently $\Vert\hat\wth_k\Vert$, will decrease until $\hat\wth_k$ reaches $\wth_\xi\cap\wth_{\hat\wth_k}\cap\wth_c$.
+Once $\hat\wth_k$ hits the boundary of $\wth_c$, the Lagrange multipliers will cease to increase, thus ensuring their boundedness.
+
+% To analyze the boundedness of the Lagrange multipliers, assume that $\lambda_j$ dominantly increased such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal{A}-\{\wth_k\}}\lambda_j\hat\wth_k^\top(\partial c_j/\partial \hat\wth_k)<0$.
+Then $\hat\wth_k$ approaches into $\wth_\xi\cap\wth_{\hat\wth_k}\cap\wth_\gamma$.
+It means that the Lagrange multipliers are bounded satisfying the constraints.
+
+%  subset of $\hat\wth_k$ which satisfy the constraints in $\mathcal A$, can be represented as 
+% \begin{equation}
+%    \wth_\gamma=
+%    \{
+%        \hat\wth_k
+%        \ \vert\ 
+%        \Vert\hat\wth_k\Vert
+%        \le \gamma
+%    \}
+% \end{equation}
+% where $\gamma \le \bar\wth_k$, since if $\gamma$ is greater than $\bar\wth_k$, the constraint can be handled by $c_{\wth_k}$. %, as shown in Fig~\ref{fig: V space}.
+
+%To analyze the Lagrange multipliers, assume that the Lagrange multipliers are increased such that
+% \begin{equation}
+%    \dot V \le - \underbrace{
+%     \sum_{j\in\mathcal{A}-b_k}\lambda_j\tilde\wth_k^\top\nabla c_{j,k}
+%     }_{>0}	\le -\gamma_k <0
+% \end{equation}
+%with $\gamma_k\in\mathbb R_{>0}$.
+%It imples that there is a finite time $t_f$ for $\hat\wth_k$ to converge to the point that satisfies the every constraint, while approaching to the $\wth^*$.
+%When the constraints are satisfied, the reminders of the multipliers in $\mathcal A$ converges.
+
+\subsection*{Step i: Boundedness of $\hat\wth_i$ and $\eta_i, \ i\in[k-1,\cdots,0]$}
+ % \subsubsection*{Step i: Boundedness of $\hat\wth_i,\eta_i,\ i\in[k-1,\cdots,0]$}
+
+% Following facts
+% \begin{equation}
+%     {\partial \hat\Phi\over \partial \hat\wth_i} = V_k^\top  \phi'_k \cdots V_{i+1}^\top  \phi'_{i+1} (I_{l_{i+1}}\otimes \phi^\top  _{i})
+% \end{equation}
+
+The boundedness of the Frobenius norm of the gradient $\partial\hat\Phi/\partial \hat\wth_i$ can be obtained from its definition in \eqref{eq.
+nabla phi}.
+This relies on the fact that the boundedness of $\Vert\hat\wth_i\Vert,\ \forall i\in[k,\cdots,i+1]$, was already shown in the previous step (\ie Step 1 to Step $i+1$) and the activation functions $\hat\phi_i$ and their derivative $\hat\phi_i'$ are bounded.
+
+The dynamics of $\eta_i$ and $\hat\wth_i$ for all $i\in [k-1,\cdots,0]$ are represented as
+\begin{equation}
+    \dot\eta_i = 
+    A_\xi\eta_i -B_\xi {\partial h\over\partial\tau}
+    {\partial \hat\Phi\over \partial \hat\wth_i}
+\end{equation}
+and
+\begin{equation}
+    \begin{aligned}
+        \dot{\hat\wth}_i 
+        =&
+        -\alpha 
+        \bigg[
+            \eta_i^\top W\xi+2\lambda_{\wth_i} \hat\wth_i
+            +
+            \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j{\partial c_j\over\partial \hat\wth_i}
+        \bigg].
+    \end{aligned}
+\end{equation}
+According to \cite[Chap.~4 T.~1.9]{RN13}, $\Vert\eta_i\Vert_F$ is bounded because $A_\xi$ is a stable matrix and the terms $\Vert B_\xi\Vert, \Vert(\partial h/\partial \tau)\Vert_F$, and $\Vert\partial \hat\Phi/\partial\hat\wth_i\Vert_F$ are bounded.
+When $\lambda_{\wth_i}$ is generated due to a violation of the weight norm constraint, $\hat\wth_i$ remains bounded because the term $-2\alpha\lambda_{\wth_i}$ is stable, and the residual terms $\Vert\eta_iW\xi\Vert$, $\lambda_j$, and $\Vert(\partial c_j/\partial \hat\wth_i)\Vert_F$ for all $j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ are bounded, as demonstrated in Step 1 and by Lemma \ref{lem2}.
+The boundedness of each $\lambda_{\wth_i}$ also can be obtained, assuming that $\lambda_{\wth_i}$ is sufficiently increased regulating $\Vert\wth_i\Vert$ into the origin until $c_{\wth_i}$ is satisfied.
+
+Therefore, starting from the boundedness of $\xi$, $\hat\wth_k$, and $\eta_k$ in the $k\textsuperscript{th}$ layer, the boundednesses of $\hat\wth_i$ and $\eta_i$ for the remaining layers $i\in[0,\cdots,k-1]$ can be established recursively, down to the input layer ($i=0$).
+Thus, $\hat\wth$, $\xi$, and $\eta$ are bounded because $\hat\wth_i,\eta_i,\ \forall i\in[0,\cdots,k]$ and $\xi$ are bounded.
+Furthermore, since the estimated weight vector $\hat\wth$ is bounded, the weight estimation error $\tilde\wth$ is also bounded, as $\wth^*$ is bounded according to the universal approximation theorem.
+
+\end{proof}
+
+%  SECTION SIMULATION ======================================
+\section{Simulation}\label{sec:sim}
+
+\subsection{Setup}
+
+The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{RN32}. 
+The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$, and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+%This model contains terms of gravity and friction in its mechanical system.
+%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
+%and can be considered as the disturbance of the system.
+The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for ${q}=[q_1,q_2]^\top$ was defined as
+\begin{equation}
+    {q_d}(t) = 
+    \begin{bmatrix}
+        {q_d}_1\\{q_d}_2
+    \end{bmatrix}
     =
     \begin{bmatrix}
-        \mm 0_{\Xi_1\times 1} \\
-        2{\hat{\mv\theta}}_0 
-    \end{bmatrix}
-    ,\quad
-    \frac{\partial c_{\theta_1}}{\partial{\hat{\mv\theta}}}    
-    = 
-    \begin{bmatrix}
-        2{\hat{\mv\theta}}_1 \\
-        \mm 0_{\Xi_0\times 1}
-    \end{bmatrix}
-    .
-\end{equation}
-
-%  SECTION STABILITY ANALYSIS ==============================
-\section{Stability Analysis}\label{sec:stability}
-
-The following theorem proves the boundedness of the tracking error and the weight estimation of the weights.
-
-\begin{theorem}
-For the dynamical system in \eqref{eq.
-system dynamics 1}, the proposed controller \eqref{eq.
-control law} and the adaptation law \eqref{eq.
-adaptation law th}, \eqref{eq.
-adaptation law L} and \eqref{eq.
-adaptation law L max} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\hat{\mv\theta}}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
-ctrl stable condition}.
-\end{theorem}
-
-\begin{proof}
-The boundedness is proven from the last layer to the first layer.
-
-\subsection*{Step 1: Boundedness of ${\hat{\mv\theta}}_1,{\mm \eta}_1,\mv \xi$}
-
-% For convenience, assume that all the constraints are in the active set without loss of generality.
-% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
-\color{black}
-Without loss of generality, assume that all the constraints. Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
-%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
-\color{black}
-
-The dynamics of $\mv \xi$ can be represented as
-\begin{equation}    
-    \dot {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
-    (
-        -\hat {\mm V}_1^\top \hat{\mv\phi}+\mv w(t)
-    )
-\end{equation}
-where $\mv w(t)\triangleq {\mm V}_1^{*T}\mv\phi^*+\mv \epsilon$ is a lumped residual term, which is bounded as $\Vert\mv  w(t)\Vert\le \bar w< 0$ since $\Vert\mv\theta_1^*\Vert$ and $\Vert\mv\phi^*\Vert$ are bounded.
-The dynamics of ${\mm \eta}_1$ and ${\hat{\mv\theta}}_1$ are represented as
-\begin{equation}
-    \begin{aligned}
-        \dot{\mm \eta}_1 =
-        & 
-        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )
-        \\
-        \dot{{\hat{\mv\theta}}}_1 =
-        & -\alpha 
-        (
-            {\mm \eta}_1^\top \mm W\mv\xi+2\lambda_{\theta_1} {\hat{\mv\theta}}_1
-        ).
-    \end{aligned} 
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{RN32}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )$ is bounded.
-
-Define the Lyapunov function $\mathcal V_1=(1/2)\mv\xi^\top \mm P\mv\xi+(1/2\alpha){\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
-Using a proposition $\hat {\mm V}_1^\top \hat{\mv\phi} = \text{vec}(\hat {\mm V}_1^\top \hat{\mv\phi})=\text{vec}(\hat{\mv\phi}^\top \hat {\mm V}_1) = (\mm I_{l_2}\otimes {\hat{\mv\theta}}^\top )\text{vec}(\hat {\mm V}_1)=(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1$ \cite[Proposition~(7.1.9)]{RN22}, the time derivative of $\mathcal V_1$ is
-\begin{equation}
-    \begin{aligned}
-        \dot {\mathcal V}_1 
-        =& 
-        {1\over 2}
-        \mv \xi^\top (\mm A_\xi^\top \mm P+\mm P\mm A_\xi)\mv \xi
-        +
-        \mv \xi^\top \mm P ( -\mm B_\xi\hat {\mm V}_1^\top \hat {\mv \phi} +\mm B_\xi \mv w(t) )\\
-        &
-        +{\hat{\mv\theta}}_1^\top 
-        (
-            -{\mm \eta}_1^\top \mm W \xi-2\lambda_{\theta_1} {\hat{\mv\theta}}_1 
-        )
-        \\
-        =& 
-        -{1\over 2}\mv \xi^\top \mm Q\mv \xi 
-        -
-        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1 
-        +\mv \xi^\top \mv \Delta
-        \\
-        &
-        -{\hat{\mv\theta}}_1^\top {\mm \eta}_1^\top \mm W\mv \xi
-        -2\lambda_{\theta_1} {\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1
-        \\
-        \le&
-        -(1/2)\lambda_\text{min}(\mm Q)\Vert \mv \xi\Vert ^2
-        +\bar\Delta \Vert \mv \xi\Vert  
-        +\bar M\Vert \mv \xi\Vert  \Vert {\hat{\mv\theta}}_1\Vert
-        \\
-        &
-        -2\lambda_{\theta_1}
-        \Vert{\hat{\mv\theta}}_1\Vert ^2
-        \\
-        \le& 
-        (
-        -{\lambda_\text{min}(\mm Q)/ 2} +{\bar M/ 2}
-        )
-        \Vert \mv \xi\Vert ^2 +\bar\Delta \Vert \mv \xi\Vert  
-        \\
-        &+ 
-        (
-        -2\lambda_{\theta_1} 
-        +\bar M/ 2
-        )
-        \Vert \tilde{\mv \theta}_1\Vert ^2 
-        \end{aligned}
-        \label{eq. lya 1}
-\end{equation}
-where $\mv \Delta\triangleq \mm P\mm B_\xi \mv w(t)$ and $\mm M\triangleq -\mm P\mm B_\xi(\mm I_{l_2}\otimes \hat{\mv\phi}^\top )+\mm W{\mm \eta}_1$ are bounded such that $\Vert\mv \Delta\Vert\le\bar\Delta<\infty$ and $\Vert\mm M\Vert_F\le \bar M< \infty$, respectively.
-
-By defining $\mm P=\mm I_n$, the eigenvalues of $\mm Q=-\mm A_\xi^\top -\mm A_\xi$ are $2k_q$ and $2k_z$, since $\mm A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
-According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
-\begin{equation}
-    \text{min}(k_q,k_z)>\bar M/2
-    ,
-    \label{eq. ctrl stable condition}
-\end{equation}
-and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\bar M/2$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
-\begin{equation}
-    \Theta_\xi = 
-    \bigg\{
-        \mv\xi\mid\Vert\mv\xi\Vert \le  
-        {
-            \bar \Delta \over \lambda _\text{min}(\mm Q)-\bar M/2
-        } 
-    \bigg\}
-    ,
-\end{equation}
-and the weight estimation $\theta^*_1$ is bounded in
-\begin{equation}
-    \Theta_{{\hat{\mv\theta}}_1} = 
-    \{ 
-        {\hat{\mv\theta}_1} 
-        \mid
-        \Vert{\hat{\mv\theta}_1}\Vert 
-        \le  
-        \bar\theta_1
-    \}
-    .
-\end{equation}
-The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\hat{\mv\theta}}_1$ approaches the compact set $\Theta_{{\hat{\mv\theta}}_1}$, satisfying the constraint $c_{\theta_1}$.
-
-\subsection*{Step 2: Boundedness of ${\hat{\mv\theta}}_0,{\mm \eta}_0$}
-
-The dynamics of ${\mm \eta}_0$ and ${\hat{\mv\theta}}_0$ are represented as
-\begin{equation}
-    \begin{aligned}     
-        \dot{\mm \eta}_0 =& 
-        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )
-        \\
-        \dot{{\hat{\mv\theta}}}_0
-        =&
-        -\alpha 
-        (
-            {\mm \eta}_0^\top \mm W\mv \xi+2\lambda_{\theta_0} {\hat{\mv\theta}}_0
-        )
-        .
-    \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{RN32}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )$ is bounded.
-To obtain the invariance set of ${\hat{\mv\theta}}_0$, taking the time derivative of the Lyapunov function $\mathcal V_0=(1/2\alpha){\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0$ yields:
-\begin{equation}
-    \begin{aligned}
-        \dot {\mathcal V}_0 =& 
-        {\hat{\mv\theta}}_0^\top (-{\mm \eta}_0\mm W\mv \xi -2\lambda_{\theta_0}{\hat{\mv\theta}}_0)
-        \\
-        \le &
-        \Vert{\hat{\mv\theta}}_0\Vert \Vert {\mm \eta}_0\mm W\mv \xi\Vert -2\lambda_{\theta_0} {\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0
-        \\
-        \le &
-        -2\lambda_{\theta_0} \Vert{\hat{\mv\theta}}_0\Vert^2 + \Vert {\mm \eta}_0\mm W\mv \xi\Vert \Vert {\hat{\mv\theta}}_0\Vert 
-        .
-    \end{aligned}
-\end{equation}
-Then, the invariance set can be represented as 
-\begin{equation}
-    \Theta_{{\hat{\mv\theta}}_0} =
-    \{
-        {\hat{\mv\theta}}_0\mid\Vert{\hat{\mv\theta}}_0\Vert 
-        \le
-        \Vert{\mm \eta}_0\mm W\mv \xi\Vert/\lambda_{\theta_0}
-    \}
-    .    
-\end{equation}
-If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\hat{\mv\theta}}_0}$ converges to $\{{\hat{\mv\theta}}_0\ \vert \ \Vert{\hat{\mv\theta}}_0\Vert \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
-Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.
-
-\end{proof}
-
-% \begin{remark}
-%     In the constrained optimization method, the corresponding method of $L_2$-regularization method is the quadratic penalty method, which replaces the constrained optimization problem into an unconstrained optimization problem by adding the penalty term $(1/2\mu)\sum_{r\in\mathcal I} c_r^2$ in the objective function.
-%     The penalty parameter $\mu\in\R_{>0}$ usually decreases over implementation for the convergence of the optimization process.
-%     However, the decreased penalty term $\mu$ may alter the original objective function as the penalty term dominates the objective function.
-%     Therefore, $L_2$-regularization inherently has the analogous drawback of the quadratic penalty method in the selection of the regularization coefficient $\lambda$.
-% \end{remark}
-
-% \subsection{Orthogoanl-regularization}
-
-%  SECTION SIMULATION ======================================
-\section{Simulations}\label{sec:sim}
-
-\subsection{Setup}
-
+        +\cos(0.5\pi t) + 1 \\
+        -\cos(0.5\pi t) - 1 
+    \end{bmatrix}.
+\end{equation}
+%\color{red}
+%Considering the power limitation of the power source for the actuators [], 
+The control input saturation function was defined as $h(\tau)\triangleq \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{RN28} and is given by
+\begin{equation}
+    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
+    \label{eq. h func}
+\end{equation}
+with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
+The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.
+
+In addition to this physically imposed control input saturation, the input norm constraint \eqref{eq.
+cstr input ball} was imposed to ensure that the control input $\tau$ stays within the unsaturation region of $h(\tau)$ and to prevent inefficient use of the input.
+With a sufficiently large value for $p$, the input norm constraint essentially matches the control input saturation function.
+Note that among the selected controllers given below, only the proposed CoNAC can rigorously handle this input norm constraint.
+
+% **********************************************************
+% SYSTEM FIGURE AND TABLE
 \begin{figure}[!t]
     \centering
-    \includegraphics[width=0.8\linewidth]{fig/RobotModel.drawio.png}
+    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
     \caption{System model parameters.}
+    \label{table: error norm}
     \centering
@@
     \hline
-    $\theta_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
+    $b_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
     \hline
@@
 
-The two-link manipulator model in \cite{RN33} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
-In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
-The values of the system parameters are given in Table~\ref{table: system parameters}.
-The reference signal of $\mv q=[q_1,q_2]^\top $ is defined as follows:
-\begin{equation}
-    \mv q_d
-    =
-    \begin{bmatrix}
-        {q_d}_1\\
-        {q_d}_2
-    \end{bmatrix}
-    = 
-    \begin{bmatrix}
-        +\cos(\pi/2 t) + 1 \\
-        -\cos(\pi/2 t) - 1 
-    \end{bmatrix}
-    .
-\end{equation}
-
-For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod) and the proposed controller with constrained optimization (NAC-CO).
-%%%%%%%%%%%%%%%%%%%%%
-The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters $\lambda$, $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively.
-The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \Vert\mv \xi\Vert^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
-The parameter dependencies of the controllers were examined via various values of the parameters. 
-The values ranged from $0.001$ to $1$ across $10$ samples.
-%%%%%%%%%%%%%%%%%%%%%
-
-The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $(1/2)\lambda{\hat{\mv\theta}}^\top {\hat{\mv\theta}}$ to the objective function such that $J_{L_2} = J+(1/2)\lambda{\hat{\mv\theta}}^\top {\hat{\mv\theta}}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
-The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\hat{\mv\theta}}$ as follows:
-\begin{equation} 
-    \dot{{\hat{\mv\theta}}} = 
-    {\partial J_{L_2}\over\partial {\hat{\mv\theta}}}
-    =-\alpha
-    \bigg(
-        {\partial J\over\partial {\hat{\mv\theta}}}+\lambda{\hat{\mv\theta}}
-    \bigg)
-    .
-    \label{eq. adap L2}
-\end{equation}
-Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\hat{\mv\theta}}$, where $\sigma\in\R_{>0}$.
-For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\Vert \tilde{\mv z} \Vert{\hat{\mv\theta}}$ is added to the adaptation law as follows:
-\begin{equation}
-    \dot{{\hat{\mv\theta}}} = -\alpha
-    \bigg(
-        {\partial J\over\partial {\hat{\mv\theta}}}+\rho\Vert\tilde {\mv z}\Vert{\hat{\mv\theta}}
-    \bigg)
-    \label{eq. adap eMod}
-\end{equation}
-where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
-By $\Vert\tilde {\mv z}\Vert$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
-Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
-The adaptation law of NAC-CO is presented in \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L}, and \eqref{eq. adaptation law L max}.
-Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.
-
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\mm M_0=I_2$ and $\mm W=\text{diag}([5,1,15,15])$.
-The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The NN input vector was set to the desired trajectory $\mv q_d$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\mv q_{NN}=[\mv q_d^\top ,1]^\top $.
-For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
-The sampling time of the simulation and the simulation termination time were set to $T_s=10^{-4}$ and $T=10$, respectively.
-
-\subsection{Results}
-
 \begin{figure}[!t]
     \centering
-    {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
-\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
-    \label{fig: Box-beard plot}
+    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
+    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
+    \label{fig: h func}
 \end{figure}
+
+% SYSTEM FIGURE AND TABLE
+% **********************************************************
+Four controllers were examined for a comparative study.
+The first was the Backstepping Controller (BSC), used as the baseline.
+The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro-adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC.
+While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints.
+The third was DNN-BSC augmented with an auxiliary system presented in \cite{RN55, RN56, RN3} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
+As a result, an approximation of the input norm constraint was used as an input bound constraint.
+Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework.
+The properties of these four controllers are summarized in Table \ref{table:controller}.
+%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).
 
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Quantitative comparison of square root of tracking ISE.}
+    \caption{Properties of the controllers used in simulation}
+    \label{table:controller}
     \centering
@@
     \hline
-     & \textbf{NAC-L2} & \textbf{NAC-eMod} & \textbf{NAC-CO} (proposed) 
-     \\
+    & \multicolumn{3}{c|}{Handling Capability}\\
     \hline
-    Maximum         & $11.1753$e-3 & $0.5603$e-3 & $0.3439$e-3 \\
+    & System & Weight Norm & Input Norm\\
+    &  Uncertainty & Constraint & Constraint\\
     \hline 
-    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
+    BSC     & X & X & X\\
+    \hline
+    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
+         &  & (by projection) & \\
+    \hline
+    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
+       &  & (by projection) &  (by aux. system)\\
+       % &  & & linearized constraint)\\
     % \hline
-    Median          & $0.5898$e-3 & $0.5519$e-3 & $0.3240$e-3 \\
+    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
+    %    &  & (by projection) &  system for \\
+    %    &  & & linearized constraint)\\
     \hline
-    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
-    % \hline
-    Minimum         & $0.5434$e-3 & $0.5434$e-3 & $0.3235$e-3 \\
+    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
+         &  & (by optimization) & (by optimization)\\
     \hline
     \end{tabular}
-    \label{table: error norm}
 \end{table}
 
-As shown in Fig.~\ref{fig: Box-beard plot}, the maximum square root of the tracking ISE of NAC-CO is smaller than the minimum square root of the tracking ISEs of NAC-L2 and NAC-eMod for all variations in the parameters.
-This is because NAC-L2 and NAC-eMod bias the weights to the origin due to the presence of stabilizing functions.
-A quantitative comparison of the square root of the tracking ISE is provided in Table~\ref{table: error norm}.
+% \begin{table}
+% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
+% \centering
+% {\begin{tabular}{cc}\textcolor{black}ine
+% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
+% Rated power & 3 kW\\
+% Rated speed & 4500 RPM\\
+% Rated torque & 6.4 Nm\\
+% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
+% $I_{max}$ & 15 A \\
+% $V_{dc}$ & 100 V\\
+% $R_s$ & 0.34 $\Omega$\\
+% $P$ & 3\\
+% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
+% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
+% \multirow{2}{*}{Controller} & TMS320F28377D\\
+% & (Texas Instrument) \\
+% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
+%  & (Infineon Technologies)
+% \\\textcolor{black}ine
+% \end{tabular}}
+% \end{table}
+
+% \begin{table}[!t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Common Parameters of Selected Controllers.}
+%     \label{table: error norm}
+%     \centering
+%     \begin{tabular}{|c||c|c|c|c|c|c|}
+%     \hline
+%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
+%     \hline 
+%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
+%     \hline
+%     \end{tabular}
+%     \label{table: control parameters}
+% \end{table}
+
+% **** CM1,2 control law *****
+The BSC used the control law defined in \eqref{eq. desired control} with $\hat f=[0,0]^\top$. Since BSC did not consider the unknown system dynamics, the approximation term $\hat f$ was set to zero.
+%CM1 has the following control gains and design parameters: $k_s=5,{k_z}=5, M_0=I_2, C_0=I_2, G_0=[0,0]^\top  $.
+% Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^\top$. 
+The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \hat\Phi$.
+The adaptation law for DNN-BSC, as presented in \cite{RN16}, was defined by
+\begin{equation}\label{eq:projection}
+\dot {\hat\wth}= \text{Proj}_{\Omega}[\alpha  (\partial \hat\Phi/\partial \hat\wth)M_0^{-1}{\tilde z}],
+\end{equation}
+where $\text{Proj}_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{RN20}, which projects an input vector onto a convex set $\Omega$.
+The convex set was defined as ${\Omega}\triangleq \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i\triangleq \{\hat\wth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
+cstr weight ball}.
+% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\text{Proj}_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\hat\wth$-space.).
+% **** CM3 control law *****
+
+The control law for DNN-BSC-A was the same as DNN-BSC, but with an auxiliary system to compensate for control input violations.
+Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq.
+cstr input ball}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq.
+cstr input saturation} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
+The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
+%considering $h(\cdot)$, saturated control input is defined as $s(\tau)\triangleq \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
+The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\R^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} =
+\tau_{(i)}-\text{sat}(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
+% s(\tau)-\tau$.
+The auxiliary state variables were used in the adaptation law \eqref{eq:projection} by substituting ${\tilde z}$ with ${\tilde z}+\zeta$.
+
+% **** CoNAC control law *****
+The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq.
+approximated control}.
+The update rates for the multipliers were set as $\beta_{j}=0.1$.
+The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
+
+For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
+Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
+The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ (from Eq.
+\eqref{eq.
+h func}).
+The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
+The sampling time of the simulations was selected as $T_s=10^{-4}$.
+% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+% The other parameters for CM1 to CoNAC were selected as listed in Table.~\ref{table: control parameters}.
+The same values were assigned across all the controllers for the common parameters for a fair comparison.
+
+% **********************************************************
+% SIMULATION FIGURES
+\begin{figure*}[!t]
+    \centering
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
+        \label{fig: tracking_CM1}}
+    \hfill
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
+        \label{fig: tracking_CM2}}
+    \vfill
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
+        \label{fig: tracking_CM3}}
+    \hfill
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
+        \label{fig: tracking_CoNAC}}
+    \caption{Comparison of the tracking performance across the selected controllers.}
+    \label{fig: tracking}
+\end{figure*}
+
+\begin{figure*}[!t]
+    \centering
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
+        \label{fig: control_CM1}}
+    \hfill
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
+        \label{fig: control_CM2}}
+    \vfill
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
+        \label{fig: control_CM3}}
+    \hfill
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
+        \label{fig: control_CoNAC}}
+    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
+    \label{fig: control}
+\end{figure*}
 
@@
     \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
-        \label{fig: weight NAC-L2}}
+    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
+    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
+    \label{fig: ball control}}
+\end{figure}
+
+\begin{figure*}[!t]
+    \centering
+        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
+        \label{fig: multiplier_CoNAC}}
+    \hfill
+        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
+        \label{fig: weight_CM2}}
     \vfill
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
-        \label{fig: weight NAC-eMod}}
-    \vfill
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
-        \label{fig: weight NAC-CO}}
-    \vfill
-    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: weight}
-\end{figure}
-
-\begin{figure}[!t]      
-    \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
-        \label{fig: error NAC-L2}}
-    \vfill
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
-        \label{fig: error NAC-eMod}}
-    \vfill
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
-        \label{fig: error NAC-CO}}
-    \vfill
-    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: error}
-\end{figure}
-
-For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
-As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\hat{\mv\theta}}$.
-Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
-Since the weight norm is decreased, NAC-L2 cannot generate sufficient control inputs, resulting in a larger square root of tracking ISE, as shown in Fig.~\ref{fig: error NAC-L2}.
-
-On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
-This is because the stabilizing function $-\alpha\rho\Vert\tilde {\mv z}\Vert{\hat{\mv\theta}}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
-However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (\ie smaller weight norms are observed as $\rho$ increases.).
-Therefore, similar to NAC-L2, the biased weights produce insufficient control input, resulting in a relatively larger square root of tracking ISE than that of NAC-CO, as described in Table \ref{table: error norm}.
-
-Finally, the weight norm of NAC-CO is smaller than those of NAC-L2 and NAC-eMod, as shown in Fig.~\ref{fig: weight NAC-CO}, with better tracking performance.
-Even if a large $\beta_j$ is provided, NAC-CO can adjust the adaptation direction to satisfy the weight norm constraints faster, according to \eqref{eq. adaptation law L}.
-Therefore, the lowest dependency on the update rate $\beta_j$ is observed in NAC-CO, as shown in Fig.~\ref{fig: weight NAC-CO} and Fig.~\ref{fig: error NAC-CO}.
-Note that $\beta_j$ of NAC-CO is the update rate for the Lagrange multipliers, whereas $\lambda$ and $\rho$ are the coefficients of the stabilizing function that generates the biases of the weights.
-However, considering the implementation using a digital computer, excessively large $\beta_j$ values should be avoided.
-
-The details of the satisfaction of the weight norm constraints are shown in Fig.~\ref{fig: weight and multiplier} for NAC-CO with $\beta_j=0.001$.
-As the weight norms of each layer reach the constraint boundary, the corresponding Lagrange multipliers are generated.
-Using the Lagrange multipliers, the adaptation direction is adjusted toward the constraint satisfactory point.
-The Lagrange multipliers disappear when the constraints are satisfied, and the weights are adapted to optimize the original objective function without weight bias.
-
-\begin{figure}[!t]      
-    \centering
-    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
-    \label{fig: weight per layer NAC-CO}}
-    \vfill
-    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
-    \label{fig: multipliers NAC-CO}}
-    \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
+        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
+        \label{fig: weight_CM3}}
+    \hfill
+        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
+        \label{fig: weight_CoNAC}}       
+    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
     \label{fig: weight and multiplier}
-\end{figure}
-
-Furthermore, it is important to note that NAC-CO shows enhanced tracking performance with smaller weights than NAC-L2 and NAC-eMod.
-This implies that the weights in NAC-CO approach the different local optimal solution points from those of NAC-L2 and NAC-eMod.
-Therefore, if the physical analysis of the system is available to predict the feasible maximum control inputs, NAC-CO can find the local optimal solution without unnecessarily large control inputs by imposing proper weight norm constraints.
+\end{figure*}
+% SIMULATION FIGURES
+% **********************************************************
+
+\subsection{System Uncertainty Handling}
+
+The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
+To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties.
+As a result,
+%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
+%the parameters of CM1 are poorly tuned, 
+BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.
+
+By leveraging the DNN to compensate for the lumped system uncertainty within the BSC, DNN-BSC achieved improved tracking performance compared to BSC, as seen in Fig.~\ref{fig: tracking_CM2}.
+Fig.~\ref{fig: tracking_CM3} shows that DNN-BSC-A enhanced tracking performance for $q_2$, but tracking for $q_1$ remained unsatisfactory due to incomplete constraint handling, which will be discussed in detail in Section \ref{sec:sim_cnst}.
+%By compensating the uncertain terms the control input of CM2 in Fig.~\ref{fig: control_CM2} is saturated.
+
+Finally, CoNAC, which directly approximates the stabilizing control law along with the compensation term, demonstrated satisfactory tracking performance across both states, as illustrated in Fig.~\ref{fig: tracking_CoNAC}.
+
+\subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}
+
+The resulting control input $\tau$ and physically saturation control input $h(\tau)$ for the selected controllers are shown in Fig.~\ref{fig: control}.
+As illustrated in Fig.~\ref{fig: control_CM1}, BSC did not violate the input norm constraint (\ie $\tau = h(\tau)$).
+However, in DNN-BSC, the added compensation term from the DNN caused violations of the input norm constraint (\ie $\tau > h(\tau)$) at several points; see Fig.~\ref{fig: control_CM2}.
+This failure to account for the input norm constraint led to oscillations in the control input $\tau$.
+The DNN adaptation process attempted to increase the weights to reduce the residual errors that were not constrained by saturation, but after saturation ceased, the control input had to rapidly adjust back to realistic levels, leading to oscillatory behavior.
+Such high-frequency oscillations may induce instability in the control system or cause fatigue in the actuators.
+
+On the other hand, both DNN-BSC-A and CoNAC successfully handled their imposed input constraints, as shown in Fig.~\ref{fig: control_CM3} and Fig.~\ref{fig: control_CoNAC}, respectively, without causing notable oscillations in the control input $\tau$ even after the input constraint was activated.
+However, the tracking performance of DNN-BSC-A was lower than that of DNN-BSC and CoNAC, as the auxiliary system used in DNN-BSC-A approximated the input norm constraint with an input bound constraint, creating a rectangular constraint in the $\tau$-space (see Fig.~\ref{fig: ball control}).
+In contrast, CoNAC satisfied the nonlinear input norm constraint and produced the physically maximum control input, resulting in improved tracking performance.
+
+It is also important to note that the control input trajectory in DNN-BSC-A depends on the dynamics of the auxiliary system.
+The auxiliary system regulates the violated control input after sufficient auxiliary state $\zeta$ is generated to compensate for the violation.
+This can be observed in Fig.~\ref{fig: ball control}, where DNN-BSC-A exhibited minor violations of the input bound constraint.
+In contrast, CoNAC satisfied the constraint without being affected by such dynamics, as its Lagrange multiplier adjusted as soon as the constraint was violated.
+
+%Meanwhile, CM2 and CM3 is based on BSC, and the desired controller $\tau^*$ of CoNAC is based on the BSC which may produce larger control input by canceling the stabilizing system dynamics.
+%Therefore, CM2, CM3, and CoNAC produced the saturated control input.
+%These control results show why the control saturation should be handled.
+
+\subsection{Weight Norm Constraint Handling}
+
+The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}.
+All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.
+
+IN DNN-BSC, as shown in Fig.~\ref{fig: weight_CM2}, the weight norm of the last layer (\ie $\Vert {{{\hat \wth }_2}} \Vert$) fluctuated significantly over time, proportional to the control input norm.
+This is because the last layer’s weights directly determine the control input.
+When the control input violated the input norm constraint, the last layer’s weight norm hit the boundary and stayed there due to the projection operator.
+However, the projection operator only responded to violations without considering optimality or behavior.
+%In the case of CM2 which does not consider the control input constraint, the weight norm of the last layer reaches the maximum weight norm value, when the control is saturated.
+%It is because the weights get increased to produce larger control input to reduce the tracking error of $q_2$.
+(\ie the maximum magnitude of the control input depends on the weight norm of the last layer, since the activation function is bounded.)
+
+In DNN-BSC-A, none of the weight norms reached their boundaries, as shown in Fig.~\ref{fig: weight_CM3}.
+This was due to the auxiliary system, where the auxiliary state $\zeta$ reduced the control input, ensuring it stayed within the input constraint.
+
+In CoNAC, all weight norms complied with the imposed constraints through the constrained optimization approach, as illustrated in Fig.\ref{fig: weight_CoNAC}.
+When any weight norm approached its upper limit, the Lagrange multiplier was promptly activated to steer the weight adaptation direction towards a constraint-satisfactory point (see Fig.\ref{fig: multiplier_CoNAC}).
+Notably, the weight norms of the first and second layers ($\Vert {{{\hat \wth }_0}} \Vert$ and $\Vert {{{\hat \wth }_1}} \Vert$) remained nearly constant throughout the control period.
+The weight norm of the last layer $\Vert {{{\hat \wth }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint.
+This quasi-static behavior of the weight norm (\ie $d{\hat\wth}/dt=-\alpha\partial L/\partial \hat\wth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
+However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds.
+This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
+%(\ie $\partial J/\partial\hat\wth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\hat\wth} c_j)$.
+%, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.
+
+The overall weight norms of CoNAC were larger than those of DNN-BSC and DNN-BSC-A, since CoNAC approximated the entire stabilizing control law, whereas DNN-BSC and DNN-BSC-A only approximated the system uncertainty term within the BSC framework.
+
+%Because the simulation is implemented in a digital computer, the multipliers repeat to disappear and be generated, since the constraints are satisfied and violated in the digital process.
+
+%\subsection{Analysis of the Neural Network}
+
+%Generally, the existing literature states that the maximum norms of the weights should be sufficiently large (\ie $\bar\wth_i \gg 0$) since the designer does not know where the global optimal point of the weights is.
+%However, using the physical prior knowledge of the system, one can guess the proper value of the maximum norm, since the magnitude of the control input depends on the last layer's weights due to the bounded activation function.
+%Furthermore, the simulation study shows that the selected controllers have sufficiently good performances with the small maximum weight norms.
+%It means that the local optimal point of the weights are more effective for the stability analysis and the limitating the control input's amplitude.
+
+%Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
+%However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}.
+(\ie the weight updates are smaller as its layer is closer to the input layer.)
+%To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
 
@@
 
-\color{black}
-In this paper, a neuro–adaptive control method is proposed for uncertain Euler‒Lagrange systems, ensuring weight boundedness.
-Adaptation laws are derived by formulating a constrained optimization problem with weight norm constraints.
-The boundedness of the tracking error and the weight estimation are analyzed via Lyapunov analysis.
-The simulation results demonstrate that the proposed controller outperforms the existing methods in terms of tracking performance and parameter dependency.
-As further work, the state and output constraints for safety will be handled, ensuring stability.
-\color{black}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{APPENDIX}
-
-% Appendixes should appear before the acknowledgment.
-
-% \section*{ACKNOWLEDGMENT}
-
-% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ.
-Avoid the stilted expression, ÒOne of us (R.
-B.
-G.) thanks .
-.
-.Ó  Instead, try ÒR.
-B.
-G.
-thanksÓ.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
+
+The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds.
+By formulating these constraints as part of the optimization process, CoNAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
+
+Simulation results validated the superior performance of CoNAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+CoNAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
+
+Future work may extend this approach to address constraints on both the system inputs and states, further enhancing the flexibility and robustness of neuro-adaptive control systems using constrained optimization.
+
+%  BIBLIOGRAPHY ============================================
 \bibliographystyle{ieeetr}
@@
 \end{document}
-
-% \begin{figure}[!t]
-%     \centering
-%         \subfloat[ of Proposed]{\includegraphics[width=0.45\linewidth]{fig9.eps}%
-%         \label{fig: weight_Proposed}}
-%     \qquad
-%         \subfloat[ of NAC-L2]{\includegraphics[width=0.45\linewidth]{fig10.eps}%
-%         \label{fig: weight_NAC-L2}}
-%     \vfill
-%         \subfloat[ of NAC-eMod]{\includegraphics[width=0.45\linewidth]{fig11.eps}%
-%         \label{fig: weight_NAC-eMod}}
-%     \qquad
-%         \subfloat[ of CM3]{\includegraphics[width=0.45\linewidth]{fig12.eps}%
-%         \label{fig: weight_CM3}}
-%     \caption{controls.}
-%     \label{fig: weights}
-% \end{figure}

### 2025-03-15 src/script_simulation/controllers/CoNAC/loadOpts.m

@@ -6,16 +6,16 @@ function opt = loadOpts(dt)
     
     opt.Gamma = diag([1 1]);
 
-    opt.alpha = 1e-0;
+    opt.alpha = 1e+1;
     opt.rho = opt.alpha*0e-0;
-    opt.NN_size = [6,8,2];
+    opt.NN_size = [6,8,8,2];
     opt.W = 1;
     opt.e_size = 2;
 
     % opt.beta = [1 1 1] * 1e-1;
-    opt.beta(1:2) = [1 1] * 1e0;
-    opt.beta(3) = 5e1; % control ipnut
-    opt.cstr.V_max = [10;40] * 1e0;
+    opt.beta(1:3) = [1 1 1] * 1e0;
+    opt.beta(4) = 5e1; % control ipnut
+    opt.cstr.V_max = [10;10;40] * 1e0;
     opt.cstr.u_ball = 50;
 
     c_num = length(opt.beta);

### 2025-03-15 src/script_simulation/main_TNNLS.m

@@ -13,27 +13,28 @@ FIGURE_PLOT_FLAG    = 1;
 ANIMATION_FLAG      = 0;
 AINMATION_SAVE_FLAG = 0;
 FIGURE_SAVE_FLAG    = 0;
-RESULT_SAVE_FLAG    = 0;
+RESULT_SAVE_FLAG    = 1;
 
 %% SIMULATION SETTING
-dt = 1e-4;
-T = 15;
+ctrl_dt = 1e-4;
+dt = ctrl_dt * 1/1;
+T = 30;
 t = 0:dt:T;
 rpt_dt = 1;
 
 %% SYSTEM DECLARE
 grad_x = model1_load();
-[xd1_f, xd2_f] = ref1_load(); % sin func
-% [r_f, rd_f, rdd_f] = ref2_load(); % step func
+% [xd1_f, xd2_f] = ref1_load(); % sin func
+[xd1_f, xd2_f] = ref3_load(); 
 
-x1 = [2;-2];  
+x1 = [-deg2rad(90);0];  
 x2 = [0;0];
 u = [0;0];
 
 %% CONTROLLER LOAD
 addpath("controllers/CoNAC");
 addpath(genpath('controllers/CoNAC'))
-opt = loadOpts(dt);
+opt = loadOpts(ctrl_dt);
 initControl;
 
 %% RECORDER INITIALIZATION
@@ -53,11 +54,13 @@ for t_idx = 2:1:num_t
 
     r = e2 + opt.Gamma * e1;
 
-    x_in = [x1;x2;r];
+    if t_idx==2 || rem(t(t_idx)/dt, ctrl_dt/dt) == 0
+        x_in = [x1;x2;r];
 
-    [nn, u_NN] = nnForward(nn, opt, x_in);
-    [nn, opt] = nnBackward(nn, opt, r, u_NN);
-    u = u_NN;
+        [nn, u_NN] = nnForward(nn, opt, x_in);
+        [nn, opt] = nnBackward(nn, opt, r, u_NN);
+        u = u_NN;
+    end
 
     % control input saturation
     if norm(u) > opt.cstr.u_ball
@@ -89,4 +92,45 @@ fprintf("\n");
 if FIGURE_PLOT_FLAG
     addpath("utils");
     plot_wrapper;
+end
+
+if RESULT_SAVE_FLAG
+    data_name = [
+        "$t$";
+        "$q_1$";
+        "$q_2$";
[…]

### 2025-03-16 manuscript.tex
modifying

@@
 
-\newcommand*{\sat}{\mathcal{S}}
+\DeclareMathOperator{\myvec}{vec}
+\DeclareMathOperator{\sat}{sat}
+\DeclareMathOperator{\myrow}{row}
+
 \newcommand*{\fe}{\mv r}
-\newcommand*{\ptfrac}[2]{\tfrac{\partial #1}{\partial #2}}
-\newcommand*{\dtfrac}[2]{\tfrac{\der #1}{\der #2}}
+
 \newcommand*{\q}{\mv q}
@@
 \newcommand*{\wth}{\mv\theta}
-\newcommand*{\wV}{\mm V}
+\newcommand*{\wV}{\mm W}
+
+\newcommand*{\estwth}{\widehat\wth}
+\newcommand*{\estNN}{\widehat\NN}
+\newcommand*{\estact}{\widehat\act}
+\newcommand*{\estwV}{\widehat\wV}
+
+\newcommand*{\idealwth}{\wth^*}
+\newcommand*{\idealNN}{\NN^*}
+\newcommand*{\idealact}{\act^*}
+\newcommand*{\idealwV}{\wV^*}
 
@@
 
+\section*{Notation}
+In this study, the following notation is used:
+
+\begin{itemize}
+    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
+    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
+        \mm A
+        := 
+        [a_{ij}]
+        _{
+            i\in[1,\cdots,n],j\in[1,\cdots ,]
+        }\allowbreak\in\R^{n\times m}
+        $ denotes a vector and a matrix.
+    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
+    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
+    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
+    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
+    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
+    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
+\end{itemize}
+
 %  SECTION INTRODUCTION ===================================
@@
 These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
-To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{RN4}, \cite{RN2}.
-
-More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{RN1}.
+To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.
+
+More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
 NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
-Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{RN29}, \cite{RN44} and radial basis function (RBF) neural networks \cite{RN26}, \cite{RN10}, as well as more complex models like deep neural networks (DNNs) \cite{RN16} and their variations.
-SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{RN44, RN56, RN3, RN41}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{RN25}.
-Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{RN14} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{RN15}, have further extended the capabilities of neuro-adaptive control systems.
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}.
+Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
 
@@
 When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. 
-Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{RN18}.
+Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{Esfandiari:2021aa}. 
 Failing to address these constraints can degrade control performance or even destabilize the system.
@@
 Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
-The following section will provide a detailed review of the existing solutions to these challenges.
+he following section will provide a detailed review of the existing solutions to these challenges.
 
@@
 In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly. 
-For example, in \cite{RN16, RN14, RN11}, projection operators were used to constrain the weight norms to remain below predetermined constants.
+For example, in \cite{Zhou:2023aa,Griffis:2023aa,Patil:2022aa}, projection operators were used to constrain the weight norms to remain below predetermined constants. 
 However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values. 
@@
 
-In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{RN10} and $\epsilon$-modification \cite{RN41, RN3}.
+In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{Ge:2002aa} and $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa}. 
 These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. 
@@
 These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
-For instance, in \cite{RN55, RN56, RN3}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
+For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
 This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.
 
-Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{RN34, RN38, RN37}.
-In \cite{RN41}, the NN was used to approximate the desired control input, compensating for input saturation.
+Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}.
+In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
 However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
@@
 To overcome these limitations, constrained optimization offers a promising approach. 
-By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (e.g., tracking error) subject to both weight norm and input constraints.
-Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{RN22}.
-
-In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{RN60} and the Alternating Direction Method of Multipliers (ADMM) \cite{RN58, RN59}, have been used to train NNs offline.
+By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (\eg tracking error) subject to both weight norm and input constraints.
+Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.
+
+In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{Evens:2021aa} and the Alternating Direction Method of Multipliers (ADMM) \cite{Wang:2019aa,Taylor:2016aa}, have been used to train NNs offline.
 These methods impose constraints to address issues like gradient vanishing in backpropagation. 
@@
 The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
-    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function.
+    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
     %, enabling more precise real-time adaptation.
@@
 The remainder of this paper is organized as follows. 
-Section \ref{sec: Problem Formulation} presents the target system and control objective.
+Section \ref{sec:Problem Formulation} presents the target system and control objective.
 Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
 In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
-Candidates of the weight and input constraints are presented in Section \ref{sec:cstr candidates}.
+Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
 Section \ref{sec:stability} analyzes the stability of the proposed controller.
@@
 %  SECTION PROBLEM FORMULATION ============================
-\section{Problem Formulation}\label{sec: Problem Formulation}
-
-\subsection{Notation}
-In this study, the following notation is used:
-
-\begin{itemize}
-    \item $\otimes$ denotes the Kronecker product \cite{RN17}.
-    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $\mm A\triangleq [a_{ij}]_{i\in[1,\cdots,n],j\in[1,\cdots ,]}\in\R^{n\times m}$ denotes a vector and a matrix.
-    % \item $x_{(i)}$ denotes the $i\textsuperscript{th}$ element of the vector $x\in\mathbb R^n$.    
-    % \item $A_{(i,j)}$ is the $i\textsuperscript{th}$ row-$j\textsuperscript{th}$ column element of matrix $A$.
-    \item $\text{row}_i(A)$ denotes the $i\textsuperscript{th}$ row of the matrix $A\in\R^{n\times m}$. 
-    % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
-    \item $\textit{vec}(A)\triangleq [\text{row}_1(A^\top)  ,\cdots,\text{row}_m(A^\top)  ]^\top   $ for $A\in\R^{n\times m}$.
-    % \item $\textit{vec}(A)\triangleq [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
-    \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of the matrix $A\in\R^{n\times n}$.
-\end{itemize}
+\section{Problem Formulation}\label{sec:Problem Formulation}
 
@@
 where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
-The terms $\mm M\triangleq\mm M(\q)\in\R^{n\times n}$, $\mm V_m\triangleq\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F\triangleq\mm F(\dq)\in\R^{n}$ and $\mm G\triangleq\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
 The function $\sat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
@@
     \sat(\mv\tau)
-    \triangleq
+    :=
     \begin{cases}
@@
     \end{cases}
+    \label{eq:sat}
 \end{equation}
@@
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
-Section \ref{sec:cstr candidates} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
 
@@
 \begin{prop} \cite{Lewis:1998aa}
-    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $\dot{\mm M}-2\mm V_m$ is skew-symmetric.
+    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
     \label{prop:skew}
@@
     The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
+    \label{prop:dis_bound}
 \end{prop}
@@
 
-The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig: controller}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
-Section \ref{sec:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{NN definition} defines the DNN model.
-The weight optimizer will be detailed in Section \ref{sec:adap_laws}.
+The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
+Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model.
+The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.
 
@@
     \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
-    \label{fig: controller}
+    \label{fig:ctrl:diagram}
 \end{figure*}
 
-\subsection{Neuro-Adaptive Controller Design}\label{sec:NAC}
+\subsection{Neuro-Adaptive Controller Design}\label{sec:sub:NAC}
 
@@
 \begin{equation}
-    \fe \triangleq \dot{\mv e}-\mm\Lambda \mv e
+    \fe := \dot{\mv e}-\mm\Lambda \mv e
     ,
@@
 \end{equation}
-where $\mv e \triangleq \q - \qd$ denotes the tracking error, $\dot{\mv e} \triangleq \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
+where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
 Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
@@
     ,
+    \label{eq:sys:filtered}
 \end{equation}
 where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
-    \mv f\triangleq \mv f(\q,\dq,\dqd,\ddqd)
+    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
     =
@@
 
-Consider the Lyapunov function $\mathcal V_1\triangleq \tfrac{1}{2}\fe^\top \mm M\fe$. 
-Invoking Property \ref{prop:skew}, the time derivative of $\mathcal V_1$ is
+Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
+Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
 \begin{equation}
     \begin{aligned}
-        \dot{\mathcal V}_1
+        \dot{V}_1
         =&
@@
         )
+        \\
+        &
         +
@@
 \end{equation}
-where $\mv\tau^*\triangleq -\mv f$ is the ideal control input. 
+where $\mv\tau^*:= -\mv f$ is the ideal control input. 
 Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
@@
 To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
-Let $\NN\triangleq\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
-The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{NN definition}.
-According to the universal approximation theorem for DNNs \cite{RN33}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\wth^*$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\wth^*) - \mv g(\cdot)} = \mv\epsilon < \infty$.
-Furthermore, the theorem states that the norm of $\wth^*$ is bounded, \ie $\norm{\wth^*}\le \bar\wth<\infty$.
-In this study, $\wth^*$ is defined as a local optimal point, rather than a global optimal point.
-
-In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\NN^*\triangleq\NN(\q_{NN};\wth^*)$ as follows:
+Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
+Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
+In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
+
+In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
 \begin{align}
-    \mv\tau^*=& -(\NN^*+\mv\epsilon),
+    \mv\tau^*=& \idealNN+\mv\epsilon,
     \label{eq:control:ideal}
@@
 \begin{align}
-    \mv\tau =& -\hat\NN,
+    \mv\tau =& \estNN,
     \label{eq:control:est}
 \end{align}
-where $\hat\NN\triangleq\NN(\q_{NN};\hat\wth)$, and  $\hat\wth$ is the estimated weight vector for $\wth^*$.
+where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
 
@@
     +
-    \fe^\top (\sat(\hat\NN)-\NN^*-\mv\epsilon)
+    \fe^\top (\sat(\hat\NN)-\idealNN-\mv\epsilon)
     .
@@
 \end{equation}
-Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\hat\wth$ to $\wth^*$ (\ie $\hat\NN\to\NN^*$).
-
-\subsection{Deep Neural Network (DNN) Model}\label{NN definition}
+Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).
+
+\subsection{Deep Neural Network (DNN) Model}\label{sec:sub:NN definition}
 
@@
 \begin{equation}
-    \NN_i \triangleq
+    \NN_i :=
     \begin{cases}
@@
     \end{cases}
-    \label{eq. DNN structure 2}
+    \label{eq:DNN:architecture}
 \end{equation}
@@
 
-One of the widely used activation functions for large DNNs is from the ReLU family \cite{RN27}, which effectively avoids the gradient vanishing problem during error backpropagation. 
-However, for control applications, where relatively shallow DNNs are typically sufficient and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
-These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\dtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
-In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x)),\ \forall x\in\R$, which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\dtfrac{\sigma(x)}{x}}< 1$.
-
-For simplicity, each layer's weights are vectorized as $\wth_i\triangleq\textit{vec}(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i\triangleq (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer.
-The total weight vector $\wth\in\R^{\Xi}$ is defined by augmentating $\wth_i$ for all $i\in \left[0,\cdots,k\right]$ as 
-\begin{equation}
-    \wth \triangleq 
+One of the widely used activation functions for large DNNs is from the ReLU family \cite{Maas:2013aa}, which effectively avoids the gradient vanishing problem during error backpropagation. 
+However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
+These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\ddtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}< 1$.
+
+For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
+\begin{equation}
+    \wth := 
     \begin{bmatrix}
@@
     \begin{bmatrix}
-        \textit{vec}(\wV_k)\\
-        \textit{vec}(\wV_{k-1})\\
+        \myvec(\wV_k)\\
+        \myvec(\wV_{k-1})\\
         \vdots\\
-        \textit{vec}(\wV_0)
+        \myvec(\wV_0)
     \end{bmatrix},
@@
 \begin{equation}
-    \ptfrac{\NN}{\wth}=
+    \pptfrac{\NN}{\wth}=
     \begin{bmatrix}
-        \ptfrac{\NN}{\wth_k}&
-        \ptfrac{\NN}{\wth_{k-1}}&
+        \pptfrac{\NN}{\wth_k}&
+        \pptfrac{\NN}{\wth_{k-1}}&
     \cdots &
-        \ptfrac{\NN}{\wth_0}
+        \pptfrac{\NN}{\wth_0}
     \end{bmatrix}
@@
 \begin{equation}
-    \ptfrac{\NN}{\wth_i} = 
+    \pptfrac{\NN}{\wth_i} = 
     \begin{cases}
@@
 \end{equation}
-where $\act_i\triangleq \act_i(\NN_{i-1})$ and $\act_i'\triangleq \ptfrac{\act_i}{\NN_{i-1}}$.
-
-In the following sections, let $\NN^*_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\wth^*$. 
-Additionally, define $\act^*_i\triangleq\act_i(\NN^*_{i-1})$ and $\act^{*'}_i\triangleq \ptfrac{\act^*_i}{\NN^*_{i-1}}$. 
-Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i\triangleq\act_i(\hat\NN_{i-1})$ and $\hat\act_i'\triangleq \ptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
+where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
+
+In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
+Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and $\act^{*'}_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i:=\act_i(\hat\NN_{i-1})$ and $\hat\act_i':= \pptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
 
@@
 % \subsection{Adaptation Law using Lagrangian Function}
-\subsection{Weight Optimizer Design}
-
-Consider a positive definite objective function defined as 
-\begin{equation}
-    J(\fe;\hat\wth)\triangleq 
+\subsection{Weight Optimizer Design}\label{sec:sub:weight optimizer}
+
+The control objective can be represented as follows:
+\begin{equation}
+    \begin{matrix}
+        \min_{\estwth} \ J(\fe;\estwth):= 
         \tfrac{1}{2} \fe^\top  \mm W\fe
-\end{equation}
-where $\mm W\in\R^{n\times n}$ is symmetric positive weighting matrix.
-Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
-The corresponding constrained optimization problem is formulated as
-\begin{equation}
-    \begin{matrix}
-        \min_{\hat\wth} \ J(\fe;\hat\wth)
         \\ \\
         \begin{aligned}
-        \text{s.t. }&c_{j}(\hat\wth) 
+        \text{s.t. }&c_{j}(\estwth) 
         \le0, \quad j\in\mathcal{I},
@@
     \end{matrix}
-    \label{eq. train obj}
-\end{equation}
+    \label{eq:opt:problem1}
+\end{equation}
+where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top  \mm W\fe$ is the objective function, and $\mm W\in\R^{n\times n}$ is a symmetric positive weighting matrix.
+Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
 Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
@@
     L(
-        \fe,\hat\wth,[\lambda_j]_{j\in\mathcal I}
+        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
     ) 
-    \triangleq 
-    J(\fe;\hat\wth) 
+    := 
+    J(\fe;\estwth) 
     + 
@@
     \lambda_{j}
-    c_{j}(\hat\wth)
+    c_{j}(\estwth)
+    \label{eq:lagrangian}
 \end{equation}
@@
 
-The adaptation laws for $\hat\wth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq.
-train obj} (\ie  $\min_{\hat\wth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\hat\wth,[\lambda]_{j\in\mathcal I})$), as follows:
+The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
 \begin{subequations}
     \begin{align}
-            \dot {\hat\wth}&=-\alpha {\partial L\over\partial \hat\wth}
-            =-\alpha 
-            \bigg(
-            {\partial J\over \partial \hat\wth}+\sum_{j\in\mathcal{I}}
-            \lambda_j {\partial c_j\over\partial \hat\wth}
-            \bigg),
-        \label{eq. adaptation law th}
-            \\
-            \dot\lambda_j& = \beta_j{\partial L\over\partial \lambda_j} = \beta_j c_j ,
-            \quad\quad\quad\quad      \      
-            \forall j\in\mathcal I,
-        \label{eq. adaptation law L}
+            \ddtt{\estwth}
+            &
+            =
+            -\alpha \pptfrac{L}{\estwth}
+            =
+            -\alpha 
+            \left(
+                \pptfrac{J}{\estwth}
+                +
+                \textstyle\sum_{j\in\mathcal{I}}
+                \lambda_j 
+                \pptfrac{c_j}{\estwth}
+            \right),
+        \label{eq:adap:th}
+            \\
+            \ddtt\lambda_j
+            & 
+            = 
+            \beta_j\pptfrac{L}{\lambda_j} 
+            = 
+            \beta_j c_j ,
+            \quad \forall j\in\mathcal I,
+        \label{eq:adap:lbd}
             \\
             \lambda_j & = \max(\lambda_j,0) ,
-        \label{eq. adaptation law L max}
+        \label{eq:adap:lbd:max}
     \end{align}
-    \label{eq. adaptation law}
+    \label{eq:adaptation law}
 \end{subequations}
@@
 Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
-Note that this adaption law is similar to the ALM in \cite{RN22}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-c_j/\mu,0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
-
-At steady state, where $\dot{\hat\wth}=0$ and $\dot\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \hat\wth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{RN22}.
-In other words, the proposed optimizer updates $\hat\wth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \estwth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
+In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
 These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
-% The KKT condition is satisfied, when $\hat\wth$ converges to $\wth^*$, since $\partial L/\partial \hat\wth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).
-
-\subsection{Calculation of the Exact Gradient of Objective Function}
-
-\MSRY{NEED TO BE REVISED}
-The adaptation law for $\hat\wth$ involves the gradient of the objective function with respect to $\hat\wth$ (\ie ${\partial J/\partial \hat\wth}$); see \eqref{eq.
-adaptation law th}.
-Since the objective function depends on the state $\xi$ of a dynamic system, obtaining the gradient is not straightforward.
-Therefore, the forward sensitivity method from \cite{RN12} is employed to calculate the exact gradient of the objective function.
-
-By partially differentiating \eqref{eq. xi dynamics}, the sensitivity equation of $\xi$ with respect to $\hat\wth$ is first obtained as
-\begin{equation}
-    \dot\eta = A_\xi\eta - B_\xi{\partial h\over\partial \tau}{\partial\hat\Phi\over\partial\hat\wth}
-    \label{eq. eta dynamics 1}
-\end{equation}
-where $\eta \triangleq \partial \xi/\partial \hat\wth\in\mathbb R^{2n\times \Xi}$.
-Since the initial value of $\xi$ is independent to $\hat\wth$, $\eta|_{t=0}$ is a zero matrix. The gradient of the objective function with respect to $\hat\wth$ is then obtained as 
-\begin{equation}
-   {\partial J\over\partial \hat\wth} =  {\partial \xi\over \partial \hat\wth}^\top  W\xi=\eta^\top  W\xi\in\R^\Xi.
-   \label{eq. dJdth}
-\end{equation}
-Equations \eqref{eq. eta dynamics 1} and \eqref{eq. dJdth} can be decomposed for each layer as 
-\begin{equation}
+% The KKT condition is satisfied, when $\estwth$ converges to $\idealwth$, since $\partial L/\partial \estwth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).
+
+\subsection{Approximation of the Gradient of Objective Function}
+
+The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\mv\tau}$ (\ie 
+$
+    \pptfrac{J}{\mv \tau}
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\mv \tau}{\estwth}))^\top \fe
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\estNN}{\estwth}))^\top \fe
+$). 
+Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
+The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
+\begin{equation}
+    \ddtt (
+        \pptfrac{\fe}{\mv\tau}
+    )
+    =
+    \pptfrac{}{
+        \mv\tau
+    }
+    \left[
+        \mm M^{-1}(
+            -\mm V_m \fe
+            -\mm K \fe
+            + \mv f
+            -\mv \tau_d + \sat(\mv\tau)
+        )
+    \right]
+    .
+\end{equation}
+However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\mm M,\mm V_m, \mm F$ and $ \mm G$).
+Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
+
+In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\mv\tau}$ as $
+    \pptfrac{\fe}{\mv\tau}
+    \approx
+    [
+        \mathrm{sign}(\pptfrac{r_i}{\tau_j})
+    ]_{i,j\in[1,\cdots,m]}
+$ using the sign of each entry (\ie control direction).
+However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\mm M^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
+Therefore, we propose to approximate $\pptfrac{\fe}{\mv\tau}$ as $\pptfrac{\fe}{\mv\tau}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
+\begin{equation}
+    \ddtt{\estwth}
+    \approx
+    -\alpha 
+    \left(
+        \pptfrac{\estNN}{\estwth}^\top
+        \fe
+        +
+        \textstyle\sum_{j\in\mathcal{I}}
+        \lambda_j 
+        \pptfrac{c_j}{\estwth}
+    \right)
+    .
+    \label{eq:adap:th:approx}
+\end{equation}
+
+%% ALGORITHM PART; Now omitted!
+% The proposed controller is implemented using Algorithm \ref{alg: alg1}.
+For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
+If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
+
+% \begin{algorithm}[!t]
+%     \caption{Weight Optimizer Implementation.}\label{alg: alg1}
+%     \begin{algorithmic}[1]
+%         \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+%         \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%         \REQUIRE $\xi$, $\estwth$, $\lambda_j$, $\eta$
+%         \ENSURE  $\estwth$, $\lambda_j$, $\eta$
+%         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
+%         \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
+%         \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
+%         \STATE Determine update directions $\dot{\estwth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
+%         \STATE Update weight vector $\estwth\leftarrow \estwth+\dot{\estwth}\cdot T_s$;
+%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
+%         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
+%         \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
+%         \STATE \textbf{RETURN};
+%     \end{algorithmic}
+%     \label{alg1}
+% \end{algorithm}
+
+\subsection{Constraint Candidates}\label{sec:sub:cstr}
+
+This section introduces conditions which imposed constraints must satisfy and the weight constraints.
+The potential control input constraints are presented in Appendix \ref{sec:appen:cstr}.
+First, we introduce the following assumptions for the constraints.
+
+\begin{assum}
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
+    \label{assum:convex}
+\end{assum}
+
+\begin{assum}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
+    \label{assum:LICQ}
+\end{assum}
+
+\begin{remark}
+    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in pracice including the origin.
+    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
+    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
+\end{remark}
+
+The following Lemma is introduced for the stability analysis. % of the last layer of the DNN.
+\begin{lem}
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    \label{lem:convex:angle}
+\end{lem}
+
+\begin{proof}
+
+Since $\mv\tau = -\estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
+\begin{equation}\label{eq:linear:map}
     \begin{aligned}
-        \dot \eta&= 
-        \begin{bmatrix}
-            \eta_k&
-            \eta_{k-1}&
-            \cdots &
-            \eta_0
-        \end{bmatrix}'
-        \\
-        &=A_\xi
-        \begin{bmatrix}
-            \eta_k&
-            \cdots &
-            \eta_0
-        \end{bmatrix}
-        -B_\xi{\partial h\over\partial \tau}
-        \begin{bmatrix}
-            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top  )&
-        \cdots&
-        (\cdot)
-        \end{bmatrix}
+    \mv\tau 
+    = 
+    &
+    -\estNN 
+    % = 
+    % -\myvec(\estNN)
+    =
+    -\myvec(
+        \estwV_k^\top \estact_k
+    ) 
+    = 
+    -(
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top
+    \myvec(\estwV_k)
+    \\
+    = &
+    -\underbrace{
+        (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top}_{:=\mm T(\estact_k)}
+    \estwth_k 
+    =
+    \mm T(\estact_k) \estwth_k.
     \end{aligned}
-    \label{eq. eta dynamics}
-\end{equation}
-and
-\begin{equation}\label{eq. grad_J}
-    {\partial J\over\partial\hat\wth}
-    =
-    \begin{bmatrix}
-        \partial J/\partial\hat\wth_k\\\vdots\\\partial J/\partial\hat\wth_0\\
-    \end{bmatrix}    =
-    \begin{bmatrix}
-        \eta_k^\top\\\vdots\\\eta_0^\top\\
-    \end{bmatrix}
-    W
-    \xi
-\end{equation}
-where $\eta_i \triangleq \partial \xi/\partial \hat\wth_i\in\mathbb R^{2n\times \Xi_i}$.
-The exact gradient of the objective function is calculated based on \eqref{eq.
-dJdth}, with the value of $\eta$ obtained by simulating the sensitivity equation \eqref{eq.
-eta dynamics 1}.
-
-The proposed controller is implemented using Algorithm \ref{alg: alg1}.
-For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
-If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{RN22} to ensure that the objective function decreases.
-
-\begin{algorithm}[!t]
-    \caption{Weight Optimizer Implementation.}\label{alg: alg1}
-    \begin{algorithmic}[1]
-        \renewcommand{\algorithmicrequire}{\textbf{Input:}}
-        \renewcommand{\algorithmicensure}{\textbf{Output:}}
-        \REQUIRE $\xi$, $\hat\wth$, $\lambda_j$, $\eta$
-        \ENSURE  $\hat\wth$, $\lambda_j$, $\eta$
-        \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
-        \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
-        \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
-        \STATE Determine update directions $\dot{\hat\wth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
-        \STATE Update weight vector $\hat\wth\leftarrow \hat\wth+\dot{\hat\wth}\cdot T_s$;
-        \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
-        \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
-        \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
-        \STATE \textbf{RETURN};
-    \end{algorithmic}
-    \label{alg1}
-\end{algorithm}
-
- \section{Constraint Candidates}\label{sec:cstr candidates}
-
-This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller. 
-The controller can handle any combination of the following constraints, provided they meet the specified assumptions.
-
-\begin{assum}
-    The constraint functions $c_j(\hat\wth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\wth^*)\le 0$.
-    \label{assum1}
-\end{assum}
-
-% \begin{assum}
-%     The Frobenius norm of $\partial c_j/\partial\hat\wth_i$ is bounded. %when the norms of $\hat\wth_i,\ \forall i [k,\cdots,i+1]$ are bounded.
-%     \label{assum2}
-% \end{assum}
-
-% The Assumption \ref{assum2} also means that the boundedness of $\Vert\hat\wth_k\Vert$ implies the boundedness of $\Vert\partial c_j/\partial \hat\wth\Vert_F$, since $\tau=-\hat V_k\hat\phi_k$ is bounded when $\Vert\hat\wth_k\Vert$ bounded \ie $\Vert\phi(\cdot)\Vert$ is already bounded.
-
-\begin{assum}
-    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{RN22}.
-    \label{assum2}
-\end{assum}
-
-\subsection{Weight Norm Constraint}\label{sec:cstr weight ball}
-
-The weight norm constraint $\mathbf{c}_{\theta}\triangleq [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ limits the maximum norm of each layer's weight vector, where
+\end{equation}
+Therefore, the convexity of the input constraints in $\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+
+\end{proof}
+
+The weight constraints are essential to prevent the weights from diverging during the adaptation process.
+The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
 \begin{equation}
@@
     =
-    \Vert \hat\wth_i\Vert^2 
+    \Vert \estwth_i\Vert^2 
     -
     \bar\theta_i^2 \le 0
-    \label{eq. cstr weight ball}
-\end{equation}
-with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\hat\wth_i$. 
-The gradient of $\mathbf{c}_\theta$ with respect to $\hat\wth$ is given by
-\begin{equation}\label{eq weight norm cnst grad}
-    {\partial \mathbf c_\theta \over \partial \hat\wth}
-    \triangleq
-    \begin{bmatrix}
-        (\partial c_{\theta_0}/\partial \hat\wth)^\top
-        \\ 
-        \vdots 
-        \\
-        (\partial c_{\theta_k}/\partial \hat\wth)^\top
-    \end{bmatrix}
-    = 2\cdot 
-    \begin{bmatrix}
-        0&0&\cdots & \hat\wth_0^\top\\
-        \vdots&\vdots&\ddots&\vdots\\
-        0&\hat\wth^\top_{k-1}&\cdots &0\\
-        \hat\wth^\top_k&0&\cdots &0
-    \end{bmatrix}
-    \in\mathbb R^{(k+1)\times\Xi}
+    \label{eq:cstr:weight_ball}
+\end{equation}
+with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
+The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
+\begin{equation}
+    \pptfrac{c_{\theta_i}}{\estwth_j} 
+    =
+    \begin{cases}
+        2\estwth_i,
+        &
+        \text{if } i=j
+        \\
+        0,
+        &
+        \text{if } i\ne j
         .
-\end{equation}
-%As demonstrated in Section \ref{sec:stability}, the weight norm constraint should be imposed on the controller to ensure the boundedness of the tracking error and weight estimation.
-
-%\begin{remark} Imposing the weight norm constraint is analogous to applying $L_2$-regularization, a common technique used in DNN training to prevent parameter drift or overfitting \cite{RN23}, by minimizing the $L_2$ norm of the estimated weight vector $\hat\wth$.
-Typically, $L_2$-regularization adds a term $\lambda\Vert\hat\wth\Vert_2^2$ to the objective function $J$, where $\lambda\in\mathbb R_{>0}$ is a constant $L_2$ coefficient.
-This term biases the trainable weights $\hat\wth$ toward the origin (\ie $\hat\wth = 0$) in the adaptation law \eqref{eq.
-adaptation law th}.
-In contrast, within the proposed controller, the term associated with the maximum weight ball constraint in the adaptation law (\ie $\sum_{j\in\mathcal{A}}\lambda_j (\partial c_j/\partial \hat\wth)$ in \eqref{eq.
-adaptation law th}) vanishes when the constraint is satisfied (\ie $\lambda_j = 0$).
-    % 1. 제약조건이 사라져 자유롭게 ball condition 내에서 optimal point로 접근할 수 있다.
-%    As a result, $\hat\wth$ can still converge to $\wth^*$ without being restricted to the origin.
-%    Moreover, $\lambda_{b_i}$ which corresponds to $\lambda$ varies as the constraint is violated, while $L_2$-regularization has a constant coefficient.
-%    \label{remark: ball cstr}
-%\end{remark}
-
-\subsection{Input Bound Constraint}
-
-Most physical systems have control input limits due to electrical and mechanical limitations.
-These are expressed as $\mathbf{c}_{\overline \tau}\triangleq [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\mathbf{c}_{\underline\tau}\triangleq [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
-\begin{equation}
-    \begin{aligned}
-        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
-        \\
-        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
-    \end{aligned}
-    \label{eq. cstr input saturation}
-\end{equation}
-with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
-% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
-The gradients of $\mathbf{c}_{\overline \tau}$ and $\mathbf{c}_{\underline\tau}$ with respect to $\hat\wth$ are given by
-\begin{equation}
-    \begin{aligned}
-        {\partial \mathbf \mathbf c_{\overline \tau} \over \partial \hat\wth}
-        & 
-        \begin{bmatrix}
-            (\partial c_{\overline \tau_1}/\partial \hat\wth)^\top \\
-            \vdots \\
-            (\partial c_{\overline \tau_n}/\partial \hat\wth)^\top
-        \end{bmatrix}
-         = -{\partial \hat\Phi\over\partial\hat\wth}
-         \\
-        =&
-        -\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
-            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
-            \cdots &
-            (
-            \cdot
-            )
-        \end{bmatrix} 
-        &
-        \in
-        \mathbb R^{n\times \Xi}
-        , 
-        \\
-        {\partial \mathbf \mathbf c_{\underline\tau} \over \partial \hat\wth}         
-        \triangleq
-        & 
-        \begin{bmatrix}
-            (\partial c_{\underline\tau_1}/\partial \hat\wth)^\top \\
-            \vdots \\
-            (\partial c_{\underline\tau_n}/\partial \hat\wth)^\top
-        \end{bmatrix}
-        = +{\partial \hat\Phi\over\partial\hat\wth}
-        \\
-        =&
-        +\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
-            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
-            \cdots &
-            (
-            \cdot
-            )
-        \end{bmatrix} 
-        &
-        \in
-        \mathbb R^{n\times \Xi}
-        .
-    \end{aligned}
-    \label{eq. nabla input sat}
-\end{equation}
-
-\subsection{Input Norm Constraint}\label{sec:input_norm_cnst}
-
-Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
-Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
-This can be captured by the following inequality constraint:
-\begin{equation}
-    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
-    \label{eq. cstr input ball}
-\end{equation}
-with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
-This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{RN62}.
-% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
-The gradients of $c_{u}$ with respect to $\hat\wth$ are given by
-\begin{equation}
-    {\partial \mathbf \mathbf c_{u} \over \partial \hat\wth}
-    = -\sum_{i=1}^n 2\tau_{(i)} 
-    \bigg(
-        \text{row}_i
-        \bigg(
-            -{\partial \hat\Phi\over\partial\hat\wth}
-        \bigg)
-    \bigg)^\top  
-    = \tau^\top (I_{l_{k+1}}\otimes \hat\phi_k^\top)
-    \in \mathbb R^{\Xi}.
-    \label{eq. nabla input ball}
-\end{equation}
-It should be noted that constraints \eqref{eq.
-cstr input saturation} and \eqref{eq.
-cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
-nabla input sat} and \eqref{eq.
-nabla input ball} are linearly dependent, violating the LICQ condition.
+    \end{cases} 
+    \label{eq:cstr:weight_ball:grad}
+\end{equation}
+Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.
 
@@
 
-Before conducting the stability analysis, let $\tilde\wth\triangleq [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i\triangleq\hat\wth_i-\wth^*_i$ represents the weight estimation error.
-The following Lemmas are introduced for the stability analysis.
-% of the last layer of the DNN.
-\begin{lem}
-    If Assumptions \ref{assum1} and \ref{assum2} are satisfied, the angle between $\partial c_j/\partial \hat\wth_k$ and $\hat\wth_k$ is positive when $c_j$ is active set, \ie $(\partial c_j/\partial \hat\wth_k)^\top\hat\wth_k>0$.
-    \label{lem1}
-\end{lem}
-
-%\begin{figure}[!t]
-%    \centering
-%    \includegraphics[width=.99\linewidth]{spaces.drawio.png}
-%    \caption{Convexity of input constraints.}
-%    \label{fig: spaces}
-%\end{figure}
-
-\begin{proof}
-
-Since $\tau = -\hat\Phi$, using \cite[Proposition 7.1.9]{RN17}, a linear map $T(\cdot):\hat\wth_k\to\tau$ can be derived: 
-\begin{equation}\label{eq linear map}
-    \begin{aligned}
-    \tau = &-\hat\Phi = -\textit{vec}(\hat\Phi)     = -\textit{vec}(\hat V_k \hat\phi_k) 
-    \\
-    = & -(I_{l_{k+1}}\otimes \hat\phi_k^\top)\textit{vec}(\hat V_k)
-    =-(I_{l_{k+1}}\otimes \hat\phi_k^\top)\hat\wth_k = T(\hat\phi_k) \hat\wth_k.
-    \end{aligned}
-\end{equation}
-Therefore, the convexity of the input constraints in $\tau$-space (assumed in Assumption \ref{assum1}) holds in $\hat\wth_k$-space, implying
-%, as depicted in Fig.~\ref{fig: spaces}. 
-that $(\partial c_j/\partial \hat\wth_k)^\top\hat\wth_k>0$.
-
-\end{proof}
-
-% \begin{assum}
-%     The Frobenius norm of $\partial c_j/\partial\hat\wth_i$ is bounded. %when the norms of $\hat\wth_i,\ \forall i [k,\cdots,i+1]$ are bounded.
-%     \label{assum2}
-% \end{assum}
-
-\begin{lem} 
-    If $c_j(\hat\wth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum1}, then $\Vert\partial c_j/\partial\hat\wth_i\Vert$, for all $i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\hat\wth_i$, for all $i\in[k,\cdots, i+1]$, remain bounded.
-    % which can be verified using the boundedness of $\hat\wth_i,\ \forall i [k,\cdots,i+1]$ (as demonstrated in Section \ref{sec:stability}), and the boundedness of $\Vert\phi_i(\cdot)\Vert$ and $\Vert\nabla\phi_i(\cdot)\Vert$.
-    \label{lem2}
-\end{lem}
-
-\begin{proof}
-
-The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\hat\wth_i$ is represented as
-\begin{equation}
-    {\partial c_j\over\partial \hat\wth_i} = {\partial c_j\over\partial \tau} {\partial \tau\over\partial \hat\Phi} {\partial \hat\Phi\over\partial \hat\wth_i}
-\end{equation}
-where $\partial \tau/\partial \hat\Phi=-I_n$, which is bounded.
-From the linear mapping in \eqref{eq linear map}, $\tau$ is bounded as long as $\hat\wth_k$ is bounded (by the condition of the lemma), and $\Vert\phi_k(\cdot)\Vert$ is bounded due to the properties of the activation functions.
+% \begin{lem} 
+%     If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum1}, then $\Vert\partial c_j/\partial\estwth_i\Vert$, for all $i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i$, for all $i\in[k,\cdots, i+1]$, remain bounded.
+%     % which can be verified using the boundedness of $\estwth_i,\ \forall i [k,\cdots,i+1]$ (as demonstrated in Section \ref{sec:stability}), and the boundedness of $\Vert\phi_i(\cdot)\Vert$ and $\Vert\nabla\phi_i(\cdot)\Vert$.
+%     \label{lem2}
+% \end{lem}
+
+% \begin{proof}
+
+% The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
+% \begin{equation}
+%     {\partial c_j\over\partial \estwth_i} = {\partial c_j\over\partial \tau} {\partial \tau\over\partial \hat\Phi} {\partial \hat\Phi\over\partial \estwth_i}
+% \end{equation}
+% where $\partial \tau/\partial \hat\Phi=-I_n$, which is bounded.
+From the linear mapping in \eqref{eq linear map}, $\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\Vert\phi_k(\cdot)\Vert$ is bounded due to the properties of the activation functions.
 By Assumption \ref{assum1}, the function $c_j$ is convex.
 The convex function has a bounded derivative with respect to $\tau$, since $\tau$ is a bounded variable (\ie $\partial c_j/\partial\tau$ is bounded).
-Furthermore, $\partial \hat\Phi/\partial \hat\wth_i$ is bounded, provided that the norms of $\hat\wth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded.
-This can be verfied by using the definition of $\partial \hat\Phi/\partial\hat\wth_i$ given in \eqref{eq.
+Furthermore, $\partial \hat\Phi/\partial \estwth_i$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded.
+This can be verfied by using the definition of $\partial \hat\Phi/\partial\estwth_i$ given in \eqref{eq.
 nabla phi}.
-Consequently, $\Vert\partial c_j/\partial \hat\wth_i\Vert,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\hat\wth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
-
-\end{proof}
-
-The following theorem shows that $\hat\wth$ and $\xi$ are bounded.
+% Consequently, $\Vert\partial c_j/\partial \estwth_i\Vert,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+
+% \end{proof}
+
+Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+The following theorem shows that $\estwth$ and $\fe$ are bounded.
 
 \begin{theorem}
-    For the dynamical system in \eqref{eq.
-system dynamics 1}, the neuro-adaptive controller \eqref{eq.
-approximated control} and weight adaptation laws \eqref{eq.
-adaptation law th}, \eqref{eq.
-adaptation law L}, and \eqref{eq.
-adaptation law L max} ensure the boundedness of the augmented error $\xi$ and the weight estimate $\hat \wth$.
-This holds with the weight norm constraint \eqref{eq.
-cstr weight ball} and input constraints satisfying Assumption \ref{assum1} and \ref{assum2}, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
-ctrl stable condition}.
+    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$.
+    This holds with the weight norm constraint \eqref{eq:cstr:weight_ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
 \end{theorem}
@@
 
-The boundednesses of $\hat\wth$, $\xi$, and $\eta$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\hat\Phi$.
+The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
+Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
+This assumption is reasonable, since even if the constraint is inactive \MSRY{Add the reason why it is reasonable.}
 The step-by-step analysis is described as follows.
-
-\subsection*{Step 1: Boundedness of $\hat\wth_k,\eta_k$, and $\xi$}
-% \subsubsection*{Step 1: Boundedness of $\hat\wth_k,\eta_k,\xi$}
-
-% Noting that $\Phi^* = V_k^{*T}\phi^*_k$ and $\hat\Phi = \hat V_k^{T}\hat \phi_k$, the error dynamics \eqref{eq.
-xi dynamics} can be rewritten by adding and substracting $V_k^{*T}\hat\phi_k$ on the right side as follows:
-% \begin{equation}
-%     \begin{aligned}
-%         \dot \xi &= A_\xi\xi +B_\xi
-%         \bigg( 
-%             (V^*_k - \hat V_k)^\top   \hat\phi_{k} + V^{*T} (\phi_{k}^*-\hat\phi_{k} ) +\epsilon
-%         \bigg)\\
-%         &=A_\xi\xi  + B_\xi
-%         \bigg( 
-%             (V^*_k - \hat V_k)^\top   \hat\phi_{k} +w(t)
-%         \bigg)
-%     \end{aligned}
-% \end{equation}
-% where $w(t) \triangleq V_k^{*T} (\phi^*_{k} - \hat\phi_{k} ) + \epsilon$ is the bounded unknown term, given that $\phi_k(\cdot)$ , $V_k^*=\textit{vec}^{-1}(\wth^*_k)$ and $\epsilon$ are bounded.
-
-The boundedness of $\xi$ follows from \eqref{eq.
-xi dynamics}, using the result from \cite[Chap.~4 T.~1.9]{RN13}, since $A_\xi$ is a stable matrix and the term $B_\xi (\Phi^*-h(\hat\Phi)+\epsilon)$ is bounded due to $\Vert B_\xi\Vert_F$, $\Vert V_k^*\Vert_F$, $\Vert \phi(\cdot)\Vert$, $\Vert h(\cdot)\Vert$, and $\Vert\epsilon\Vert <\infty$.
-
-%The weight norm constraint $\mathbf{c}_{b}\triangleq [c_{b_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ presented in Section \ref{sec:cstr candidates} is imposed on the controller.
-%Additional constraints that satisfy Assumptions \ref{assum1}, \ref{assum2} and \ref{assum3} can be imposed and the constraint candidates are introduced in Section \ref{sec:cstr candidates}.
+\MSRY{start from here plz}
+\subsection*{Step 1: Boundedness of $\estwth_k$, and $\fe$}
+
+% As the result of the time derivative of $V_1$, the radius of invariant set $\Theta_\fe^{c_1}$ of $\fe$ can be obtained as
 
 Assume that all constraints are actve in $\mathcal A$ without loss of generality.
-The dynamics of $\eta_k$ and $\hat\wth_k$ can be decomposed from \eqref{eq.
+The dynamics of $\eta_k$ and $\estwth_k$ can be decomposed from \eqref{eq.
 adaptation law th} and \eqref{eq.
@@
         & 
-        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}{\partial \hat\Phi\over \partial \hat\wth_k}
+        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}{\partial \hat\Phi\over \partial \estwth_k}
         =
         A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}(I_{l_{k+1}}\otimes \hat\phi_k^\top)\\
-        \dot{\hat\wth}_k =
+        \dot{\estwth}_k =
         & -\alpha 
@@
             \sum_{j\in\mathcal{A}}
-            \lambda_j{\partial c_j\over\partial \hat\wth_k}
+            \lambda_j{\partial c_j\over\partial \estwth_k}
         \bigg]
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{RN13}, $\Vert \eta_k\Vert_F$ is bounded, since $A_\xi$ is a stable matrix and the term $-B_\xi(\partial h/\partial \tau)(I_{l_{k+1}}\otimes\hat\phi_k^\top)$ is also bounded.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, $\Vert \eta_k\Vert_F$ is bounded, since $A_\xi$ is a stable matrix and the term $-B_\xi(\partial h/\partial \tau)(I_{l_{k+1}}\otimes\hat\phi_k^\top)$ is also bounded.
 
@@
 \end{equation}
-By applying the boundedness of $\Delta \triangleq P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon)$ and $M \triangleq \eta_k W$, where $\Vert \Delta \Vert \leq \bar{\Delta} < \infty$ and $\Vert M \Vert_F \leq \bar{M} < \infty$, this simplifies to:
+By applying the boundedness of $\Delta := P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon)$ and $M := \eta_k W$, where $\Vert \Delta \Vert \leq \bar{\Delta} < \infty$ and $\Vert M \Vert_F \leq \bar{M} < \infty$, this simplifies to:
 \begin{equation}
@@
 
-By representing the term $\partial c_{\wth_k}/\partial \hat\wth_k$ in the last inequality as $\partial c_{\wth_k}/\partial \hat\wth_k=2\hat\wth_k$ using the result provided in \eqref{eq weight norm cnst grad}, $\dot {\mathcal V}$ can be rewritten as
+By representing the term $\partial c_{\wth_k}/\partial \estwth_k$ in the last inequality as $\partial c_{\wth_k}/\partial \estwth_k=2\estwth_k$ using the result provided in \eqref{eq weight norm cnst grad}, $\dot {\mathcal V}$ can be rewritten as
 \begin{equation}
@@
         \bigg)
-        \Vert\hat\wth_k\Vert^2 
+        \Vert\estwth_k\Vert^2 
         \\
         &- \underbrace{
-        \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\hat\wth_k^\top{\partial c_j\over\partial \hat\wth_k}
+        \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\estwth_k^\top{\partial c_j\over\partial \estwth_k}
         }_{>0, \text{\;by Lemma} \ref{lem1} \text{\;and\;} \text{Assumption} \ref{assum2}}	
@@
         \bigg)
-        \Vert\hat\wth_k\Vert^2 
+        \Vert\estwth_k\Vert^2 
     \end{aligned}
@@
 (as dictated by \eqref{eq.
-adaptation law L} when the corresponding constraint is violated, \ie $c_{\wth_k}=\Vert \hat\wth_k\Vert^2 -\bar\wth_k^2 > 0$), then both $\xi$ and $\hat\wth_k$ will remain bounded within the compact sets $\wth_\xi$ and $\wth_{\hat\wth_k}$, defined as
+adaptation law L} when the corresponding constraint is violated, \ie $c_{\wth_k}=\Vert \estwth_k\Vert^2 -\bar\wth_k^2 > 0$), then both $\xi$ and $\estwth_k$ will remain bounded within the compact sets $\wth_\xi$ and $\wth_{\estwth_k}$, defined as
 \begin{equation}
@@
 \begin{equation}\label{eq: hat wth k bnd}
-    \wth_{\hat\wth_k} = 
+    \wth_{\estwth_k} = 
     \{
-    \hat\wth_k 
+    \estwth_k 
     \ 
@@
     \Vert
-    \hat\wth_k\Vert \le  
+    \estwth_k\Vert \le  
     \bar\wth_k
@@
 \end{equation}
-The increase of the Lagrange multiplier $\lambda_{\wth_k}$ will halt once $\hat \wth_k$ reaches the compact set $\wth_{\hat\wth_k}$. Thus, the Lagrange multiplier $\lambda_{\wth_k}$ is bounded.
-% Note that the compact set $\wth_{\hat\wth_k}$ implies that the input norm constraint for the last $k\textsuperscript{th}$ layer is satisfied because the condition \eqref{eq: lambda bk} is fulfilled in the case of constraint violation.
+The increase of the Lagrange multiplier $\lambda_{\wth_k}$ will halt once $\hat \wth_k$ reaches the compact set $\wth_{\estwth_k}$. Thus, the Lagrange multiplier $\lambda_{\wth_k}$ is bounded.
+% Note that the compact set $\wth_{\estwth_k}$ implies that the input norm constraint for the last $k\textsuperscript{th}$ layer is satisfied because the condition \eqref{eq: lambda bk} is fulfilled in the case of constraint violation.
 
@@
 
-The boundedness of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal A\setminus\{\wth_i\}_{i\in[0,\cdots,k]}$, can be accessed by considering the convexity of the constraints in $\hat\wth_k$-space.
+The boundedness of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal A\setminus\{\wth_i\}_{i\in[0,\cdots,k]}$, can be accessed by considering the convexity of the constraints in $\estwth_k$-space.
 The boundedness of the remaining Lagrange multipliers associated with the weight norm constraints, $\lambda_{\wth_r},\ \forall r\in[0,\cdots,k-1]$, will be examined in Step $i$.
 Based on Assumption \ref{assum1} and Lemma \ref{lem1},
-%(\ie the constraint is convex on $\tau$-space and $\hat\wth_k$-space, including the origin), 
-the equality constraints $c_j \le 0, \ \forall j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, formconvex sets $\wth_{c_j}$ in $\hat\wth_k$-space.
-Let $\wth_c\triangleq \cap_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots ,k]}} \wth_{c_j}$ represent the intersection of these convex sets, which also contains the origin.
-If $\lambda_j$ increases sufficiently such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\hat\wth_k^\top(\partial c_j/\partial \hat\wth_k)<0$, then ${\mathcal V}$, and consequently $\Vert\hat\wth_k\Vert$, will decrease until $\hat\wth_k$ reaches $\wth_\xi\cap\wth_{\hat\wth_k}\cap\wth_c$.
-Once $\hat\wth_k$ hits the boundary of $\wth_c$, the Lagrange multipliers will cease to increase, thus ensuring their boundedness.
-
-% To analyze the boundedness of the Lagrange multipliers, assume that $\lambda_j$ dominantly increased such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal{A}-\{\wth_k\}}\lambda_j\hat\wth_k^\top(\partial c_j/\partial \hat\wth_k)<0$.
-Then $\hat\wth_k$ approaches into $\wth_\xi\cap\wth_{\hat\wth_k}\cap\wth_\gamma$.
+%(\ie the constraint is convex on $\tau$-space and $\estwth_k$-space, including the origin), 
+\MSRY{CHECK BELOW LINE}
+the equality constraints $c_j \le 0, \ \forall j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, formconvex sets $\wth_{c_j}$ in $\estwth_k$-space.
+Let $\wth_c:= \cap_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots ,k]}} \wth_{c_j}$ represent the intersection of these convex sets, which also contains the origin.
+If $\lambda_j$ increases sufficiently such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\estwth_k^\top(\partial c_j/\partial \estwth_k)<0$, then ${\mathcal V}$, and consequently $\Vert\estwth_k\Vert$, will decrease until $\estwth_k$ reaches $\wth_\xi\cap\wth_{\estwth_k}\cap\wth_c$.
+Once $\estwth_k$ hits the boundary of $\wth_c$, the Lagrange multipliers will cease to increase, thus ensuring their boundedness.
+
+% To analyze the boundedness of the Lagrange multipliers, assume that $\lambda_j$ dominantly increased such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal{A}-\{\wth_k\}}\lambda_j\estwth_k^\top(\partial c_j/\partial \estwth_k)<0$.
+Then $\estwth_k$ approaches into $\wth_\xi\cap\wth_{\estwth_k}\cap\wth_\gamma$.
 It means that the Lagrange multipliers are bounded satisfying the constraints.
 
-%  subset of $\hat\wth_k$ which satisfy the constraints in $\mathcal A$, can be represented as 
+%  subset of $\estwth_k$ which satisfy the constraints in $\mathcal A$, can be represented as 
 % \begin{equation}
@@
 %    \{
-%        \hat\wth_k
+%        \estwth_k
 %        \ \vert\ 
-%        \Vert\hat\wth_k\Vert
+%        \Vert\estwth_k\Vert
 %        \le \gamma
@@
 %with $\gamma_k\in\mathbb R_{>0}$.
-%It imples that there is a finite time $t_f$ for $\hat\wth_k$ to converge to the point that satisfies the every constraint, while approaching to the $\wth^*$.
+%It imples that there is a finite time $t_f$ for $\estwth_k$ to converge to the point that satisfies the every constraint, while approaching to the $\idealwth$.
 %When the constraints are satisfied, the reminders of the multipliers in $\mathcal A$ converges.
 
-\subsection*{Step i: Boundedness of $\hat\wth_i$ and $\eta_i, \ i\in[k-1,\cdots,0]$}
- % \subsubsection*{Step i: Boundedness of $\hat\wth_i,\eta_i,\ i\in[k-1,\cdots,0]$}
+\subsection*{Step i: Boundedness of $\estwth_i$ and $\eta_i, \ i\in[k-1,\cdots,0]$}
+ % \subsubsection*{Step i: Boundedness of $\estwth_i,\eta_i,\ i\in[k-1,\cdots,0]$}
 
@@
 % \begin{equation}
-%     {\partial \hat\Phi\over \partial \hat\wth_i} = V_k^\top  \phi'_k \cdots V_{i+1}^\top  \phi'_{i+1} (I_{l_{i+1}}\otimes \phi^\top  _{i})
+%     {\partial \hat\Phi\over \partial \estwth_i} = V_k^\top  \phi'_k \cdots V_{i+1}^\top  \phi'_{i+1} (I_{l_{i+1}}\otimes \phi^\top  _{i})
 % \end{equation}
 
-The boundedness of the Frobenius norm of the gradient $\partial\hat\Phi/\partial \hat\wth_i$ can be obtained from its definition in \eqref{eq.
+The boundedness of the Frobenius norm of the gradient $\partial\hat\Phi/\partial \estwth_i$ can be obtained from its definition in \eqref{eq.
 nabla phi}.
-This relies on the fact that the boundedness of $\Vert\hat\wth_i\Vert,\ \forall i\in[k,\cdots,i+1]$, was already shown in the previous step (\ie Step 1 to Step $i+1$) and the activation functions $\hat\phi_i$ and their derivative $\hat\phi_i'$ are bounded.
-
-The dynamics of $\eta_i$ and $\hat\wth_i$ for all $i\in [k-1,\cdots,0]$ are represented as
+This relies on the fact that the boundedness of $\Vert\estwth_i\Vert,\ \forall i\in[k,\cdots,i+1]$, was already shown in the previous step (\ie Step 1 to Step $i+1$) and the activation functions $\hat\phi_i$ and their derivative $\hat\phi_i'$ are bounded.
+
+The dynamics of $\eta_i$ and $\estwth_i$ for all $i\in [k-1,\cdots,0]$ are represented as
 \begin{equation}
@@
     A_\xi\eta_i -B_\xi {\partial h\over\partial\tau}
-    {\partial \hat\Phi\over \partial \hat\wth_i}
+    {\partial \hat\Phi\over \partial \estwth_i}
 \end{equation}
@@
     \begin{aligned}
-        \dot{\hat\wth}_i 
+        \dot{\estwth}_i 
         =&
@@
         \bigg[
-            \eta_i^\top W\xi+2\lambda_{\wth_i} \hat\wth_i
+            \eta_i^\top W\xi+2\lambda_{\wth_i} \estwth_i
             +
-            \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j{\partial c_j\over\partial \hat\wth_i}
+            \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j{\partial c_j\over\partial \estwth_i}
         \bigg].
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{RN13}, $\Vert\eta_i\Vert_F$ is bounded because $A_\xi$ is a stable matrix and the terms $\Vert B_\xi\Vert, \Vert(\partial h/\partial \tau)\Vert_F$, and $\Vert\partial \hat\Phi/\partial\hat\wth_i\Vert_F$ are bounded.
-When $\lambda_{\wth_i}$ is generated due to a violation of the weight norm constraint, $\hat\wth_i$ remains bounded because the term $-2\alpha\lambda_{\wth_i}$ is stable, and the residual terms $\Vert\eta_iW\xi\Vert$, $\lambda_j$, and $\Vert(\partial c_j/\partial \hat\wth_i)\Vert_F$ for all $j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ are bounded, as demonstrated in Step 1 and by Lemma \ref{lem2}.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, $\Vert\eta_i\Vert_F$ is bounded because $A_\xi$ is a stable matrix and the terms $\Vert B_\xi\Vert, \Vert(\partial h/\partial \tau)\Vert_F$, and $\Vert\partial \hat\Phi/\partial\estwth_i\Vert_F$ are bounded.
+When $\lambda_{\wth_i}$ is generated due to a violation of the weight norm constraint, $\estwth_i$ remains bounded because the term $-2\alpha\lambda_{\wth_i}$ is stable, and the residual terms $\Vert\eta_iW\xi\Vert$, $\lambda_j$, and $\Vert(\partial c_j/\partial \estwth_i)\Vert_F$ for all $j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ are bounded, as demonstrated in Step 1 and by Lemma \ref{lem2}.
 The boundedness of each $\lambda_{\wth_i}$ also can be obtained, assuming that $\lambda_{\wth_i}$ is sufficiently increased regulating $\Vert\wth_i\Vert$ into the origin until $c_{\wth_i}$ is satisfied.
 
-Therefore, starting from the boundedness of $\xi$, $\hat\wth_k$, and $\eta_k$ in the $k\textsuperscript{th}$ layer, the boundednesses of $\hat\wth_i$ and $\eta_i$ for the remaining layers $i\in[0,\cdots,k-1]$ can be established recursively, down to the input layer ($i=0$).
-Thus, $\hat\wth$, $\xi$, and $\eta$ are bounded because $\hat\wth_i,\eta_i,\ \forall i\in[0,\cdots,k]$ and $\xi$ are bounded.
-Furthermore, since the estimated weight vector $\hat\wth$ is bounded, the weight estimation error $\tilde\wth$ is also bounded, as $\wth^*$ is bounded according to the universal approximation theorem.
+Therefore, starting from the boundedness of $\xi$, $\estwth_k$, and $\eta_k$ in the $k\textsuperscript{th}$ layer, the boundednesses of $\estwth_i$ and $\eta_i$ for the remaining layers $i\in[0,\cdots,k-1]$ can be established recursively, down to the input layer ($i=0$).
+Thus, $\estwth$, $\xi$, and $\eta$ are bounded because $\estwth_i,\eta_i,\ \forall i\in[0,\cdots,k]$ and $\xi$ are bounded.
+Furthermore, since the estimated weight vector $\estwth$ is bounded, the weight estimation error $\tilde\wth$ is also bounded, as $\idealwth$ is bounded according to the universal approximation theorem.
 
@@
 
-The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{RN32}. 
+The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
 The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$, and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
@@
 %Considering the power limitation of the power source for the actuators [], 
-The control input saturation function was defined as $h(\tau)\triangleq \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{RN28} and is given by
+The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
 \begin{equation}
@@
 While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints.
-The third was DNN-BSC augmented with an auxiliary system presented in \cite{RN55, RN56, RN3} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
+The third was DNN-BSC augmented with an auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
 As a result, an approximation of the input norm constraint was used as an input bound constraint.
@@
 The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \hat\Phi$.
-The adaptation law for DNN-BSC, as presented in \cite{RN16}, was defined by
+The adaptation law for DNN-BSC, as presented in \cite{Patil:2022aa}, was defined by
 \begin{equation}\label{eq:projection}
-\dot {\hat\wth}= \text{Proj}_{\Omega}[\alpha  (\partial \hat\Phi/\partial \hat\wth)M_0^{-1}{\tilde z}],
-\end{equation}
-where $\text{Proj}_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{RN20}, which projects an input vector onto a convex set $\Omega$.
-The convex set was defined as ${\Omega}\triangleq \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i\triangleq \{\hat\wth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
+\dot {\estwth}= \text{Proj}_{\Omega}[\alpha  (\partial \hat\Phi/\partial \estwth)M_0^{-1}{\tilde z}],
+\end{equation}
+where $\text{Proj}_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{Krstic:1995aa}, which projects an input vector onto a convex set $\Omega$.
+The convex set was defined as ${\Omega}:= \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i:= \{\estwth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
 cstr weight ball}.
-% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\text{Proj}_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\hat\wth$-space.).
+% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\text{Proj}_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\estwth$-space.).
 % **** CM3 control law *****
@@
 The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
-%considering $h(\cdot)$, saturated control input is defined as $s(\tau)\triangleq \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
+%considering $h(\cdot)$, saturated control input is defined as $s(\tau):= \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
 The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\R^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} =
@@
 The weight norm of the last layer $\Vert {{{\hat \wth }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint.
-This quasi-static behavior of the weight norm (\ie $d{\hat\wth}/dt=-\alpha\partial L/\partial \hat\wth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
+This quasi-static behavior of the weight norm (\ie $d{\estwth}/dt=-\alpha\partial L/\partial \estwth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
 However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds.
 This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
-%(\ie $\partial J/\partial\hat\wth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\hat\wth} c_j)$.
+%(\ie $\partial J/\partial\estwth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\estwth} c_j)$.
 %, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.
@@
 
+\begin{appendices}
+
+\section{Constraint Candidates}\label{sec:appen:cstr}
+
+This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller.
+
+\subsection{Input Bound Constraint}\label{sec:appen:input_bound_cstr}
+
+Most physical systems have control input limits due to electrical and mechanical limitations.
+These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+\begin{equation}
+    \begin{aligned}
+        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
+        \\
+        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+    \end{aligned}
+    \label{eq. cstr input saturation}
+\end{equation}
+with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
+% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
+The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
+\begin{equation}
+    \begin{aligned}
+        {\partial \boldsymbol c_{\overline \tau} \over \partial \estwth}
+        =& 
+        \begin{bmatrix}
+            (\partial c_{\overline \tau_1}/\partial \estwth)^\top \\
+            \vdots \\
+            (\partial c_{\overline \tau_n}/\partial \estwth)^\top
+        \end{bmatrix}
+            = -{\partial \hat\Phi\over\partial\estwth}
+            \\
+        =&
+        -\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
+        , 
+        \\
+        {\partial \boldsymbol c_{\underline\tau} \over \partial \estwth}         
+        :=
+        & 
+        \begin{bmatrix}
+            (\partial c_{\underline\tau_1}/\partial \estwth)^\top \\
+            \vdots \\
+            (\partial c_{\underline\tau_n}/\partial \estwth)^\top
+        \end{bmatrix}
+        = +{\partial \hat\Phi\over\partial\estwth}
+        \\
+        =&
+        +\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
+        .
+    \end{aligned}
+    \label{eq. nabla input sat}
+\end{equation}
+
+\subsection{Input Norm Constraint}\label{sec:appen:input_norm_cstr}
+
+Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
+Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
+This can be captured by the following inequality constraint:
+\begin{equation}
+    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
+    \label{eq. cstr input ball}
+\end{equation}
+with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
+This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
+% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
+The gradients of $c_{u}$ with respect to $\estwth$ are given by
+\begin{equation}
+    {\partial \boldsymbol c_{u} \over \partial \estwth}
+    = -\sum_{i=1}^n 2\tau_{(i)} 
+    \bigg(
+        \myrow_i
+        \bigg(
+            -{\partial \hat\Phi\over\partial\estwth}
+        \bigg)
+    \bigg)^\top  
+    = \tau^\top (I_{l_{k+1}}\otimes \hat\phi_k^\top)
+    \in \mathbb R^{\Xi}.
+    \label{eq. nabla input ball}
+\end{equation}
+It should be noted that constraints \eqref{eq.
+cstr input saturation} and \eqref{eq.
+cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
+nabla input sat} and \eqref{eq.
+nabla input ball} are linearly dependent, violating the LICQ condition.
+
+\end{appendices}
+
 %  BIBLIOGRAPHY ============================================
+{\footnotesize
 \bibliographystyle{ieeetr}
-\bibliography{refs}
+% \bibliography{}
+\bibliography{dding_template/refs}}
 

### 2025-03-16 manuscript.tex
integrated bib with template

--- 2025-03-12 manuscript.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%2345678901234567890123456789012345678901234567890123456789012345678901234567890
-%        1         2         3         4         5         6         7         8
-
 \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
@@
 \input{dding_template/tex_macros/tex_macros_general.tex}
-
 % MY PAKEAGES ========================================
@@
 Furthermore, if uncertainties dominate the system, they may lead to instability.
-By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{RN26, RN30}.
+By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{Tao:2003aa,Ioannou:2006aa}.
 Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.
 
-More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{RN24}.
-It uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{RN35}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
+More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{Farrell:2006aa}.
+It uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
 This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
-Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{RN16, RN18}, radial basis function NN (RBFNN) \cite{RN17, RN31} and deep NN (DNN) \cite{RN36}.
+Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa} and deep NN (DNN) \cite{Patil:2022aa}.
 The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.
@@
 One of the common issues in using NNs is that the outputs of NNs are not predictable.
-This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{RN8, RN9}).
+This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
 This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
@@
 Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
-In \cite{RN31, RN36}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
+In \cite{Zhou:2023aa,Patil:2022aa}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
 However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
 Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
-In addition, the $\sigma$-modification \cite{RN17} and the $\epsilon$-modification \cite{RN16, RN18} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
+In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
 The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
@@
 Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
-One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{RN1, RN13}.
+One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{Wu:2020aa,Lewkowycz:2020aa}.
 Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
@@
 
-For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{RN29} can be utilized.
+For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{Nocedal:2006aa} can be utilized.
 It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
@@
 \begin{itemize}
-    \item $\otimes$ denotes the Kronecker product \cite{RN22}.
+    \item $\otimes$ denotes the Kronecker product \cite{Bernstein:2009aa}.
     \item $\mv x_{(i)}$ denotes the $i\textsuperscript{th}$ element of vector $\mv x$.    
@@
 
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\mv \theta^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\mv q_{NN}}\in\Omega_{NN}} \allowbreak \Vert\mv \Phi({\mv q_{NN}};\mv \theta^*) - \mv \tau^*\Vert=\epsilon<\infty$ \cite{RN35}.
-% The boundedness of the norm of $\theta^*$  and approximation error $\epsilon$ are also claimed in \cite{RN35}.
+Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\mv \theta^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\mv q_{NN}}\in\Omega_{NN}} \allowbreak \Vert\mv \Phi({\mv q_{NN}};\mv \theta^*) - \mv \tau^*\Vert=\epsilon<\infty$ \cite{Cybenko:1989aa}.
 The ideal weight vector $\mv \theta^*$ is typically assumed to be bounded.
@@
 The calculation of $\partial J/\partial {\hat{\mv\theta}}$ is not straightforward because of the dynamics of $\xi$.
-Using the forward sensitivity method presented in \cite{RN34}, the sensitivity equation can be obtained as follows:
+Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
 \begin{equation}
@@
 \end{equation}
-The calculation of $\partial \hat{\mv\Phi}/\partial{\hat{\mv\theta}}$ is introduced in \cite{RN36}.
+The calculation of $\partial \hat{\mv\Phi}/\partial{\hat{\mv\theta}}$ is introduced in \cite{Patil:2022aa}.
 In conclusion, the gradient of the objective with respect to the weights can be obtained as ${\partial J/\partial {\hat{\mv\theta}}} = {\mm \eta}^\top\mm W\mv\xi$ by simulating the sensitivity equation \eqref{eq.
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{RN32}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )$ is bounded.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )$ is bounded.
 
 Define the Lyapunov function $\mathcal V_1=(1/2)\mv\xi^\top \mm P\mv\xi+(1/2\alpha){\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
-Using a proposition $\hat {\mm V}_1^\top \hat{\mv\phi} = \text{vec}(\hat {\mm V}_1^\top \hat{\mv\phi})=\text{vec}(\hat{\mv\phi}^\top \hat {\mm V}_1) = (\mm I_{l_2}\otimes {\hat{\mv\theta}}^\top )\text{vec}(\hat {\mm V}_1)=(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1$ \cite[Proposition~(7.1.9)]{RN22}, the time derivative of $\mathcal V_1$ is
+Using a proposition $\hat {\mm V}_1^\top \hat{\mv\phi} = \text{vec}(\hat {\mm V}_1^\top \hat{\mv\phi})=\text{vec}(\hat{\mv\phi}^\top \hat {\mm V}_1) = (\mm I_{l_2}\otimes {\hat{\mv\theta}}^\top )\text{vec}(\hat {\mm V}_1)=(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $\mathcal V_1$ is
 \begin{equation}
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{RN32}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )$ is bounded.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )$ is bounded.
 To obtain the invariance set of ${\hat{\mv\theta}}_0$, taking the time derivative of the Lyapunov function $\mathcal V_0=(1/2\alpha){\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0$ yields:
@@
 
-The two-link manipulator model in \cite{RN33} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
+The two-link manipulator model in \cite{Markus:2013aa} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
 In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+{\footnotesize
 \bibliographystyle{ieeetr}
-\bibliography{refs}
+\bibliography{dding_template/refs}}
 
 \end{document}
-
-% \begin{figure}[!t]
-%     \centering
-%         \subfloat[ of Proposed]{\includegraphics[width=0.45\linewidth]{fig9.eps}%
-%         \label{fig: weight_Proposed}}
-%     \qquad
-%         \subfloat[ of NAC-L2]{\includegraphics[width=0.45\linewidth]{fig10.eps}%
-%         \label{fig: weight_NAC-L2}}
-%     \vfill
-%         \subfloat[ of NAC-eMod]{\includegraphics[width=0.45\linewidth]{fig11.eps}%
-%         \label{fig: weight_NAC-eMod}}
-%     \qquad
-%         \subfloat[ of CM3]{\includegraphics[width=0.45\linewidth]{fig12.eps}%
-%         \label{fig: weight_CM3}}
-%     \caption{controls.}
-%     \label{fig: weights}
-% \end{figure}

### 2025-03-17 manuscript.tex
modifying
to stability analysis
now, numerical and real-system implementation validations are desired.

--- 2025-03-16 manuscript.tex
@@
 
-\newcommand*{\fe}{\mv r}
-
-\newcommand*{\q}{\mv q}
+\newcommand*{\fe}{\mv{r}}
+
+\newcommand*{\q}{\mv{q}}
 \newcommand*{\dq}{\dot{\mv q}}
 \newcommand*{\ddq}{\ddot{\mv q}}
-\newcommand*{\qd}{\mv q_d}
+\newcommand*{\qd}{\mv{q_d}}
 \newcommand*{\dqd}{\dot{\mv q_d}}
@@
 
-\newcommand*{\NN}{\mv\Phi}
-\newcommand*{\act}{\mv\phi}
-\newcommand*{\wth}{\mv\theta}
-\newcommand*{\wV}{\mm W}
-
-\newcommand*{\estwth}{\widehat\wth}
-\newcommand*{\estNN}{\widehat\NN}
-\newcommand*{\estact}{\widehat\act}
-\newcommand*{\estwV}{\widehat\wV}
-
-\newcommand*{\idealwth}{\wth^*}
-\newcommand*{\idealNN}{\NN^*}
-\newcommand*{\idealact}{\act^*}
-\newcommand*{\idealwV}{\wV^*}
+\newcommand*{\NN}{\mv{\Phi}}
+\newcommand*{\act}{\mv{\phi}}
+\newcommand*{\wth}{\mv{\theta}}
+\newcommand*{\wV}{\mm{W}}
+
+\newcommand*{\estwth}{\widehat{\wth}}
+\newcommand*{\estNN}{\widehat{\NN}}
+\newcommand*{\estact}{\widehat{\act}}
+\newcommand*{\estwV}{\widehat{\wV}}
+
+\newcommand*{\idealwth}{{\wth}^*}
+\newcommand*{\idealNN}{{\NN}^*}
+\newcommand*{\idealact}{{\act}^*}
+\newcommand*{\idealwV}{{\wV}^*}
 
@@
 
-In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
-Considering the control input saturation function, $\qd(t)$ is supposed to be available to design a feasible control input in the presence of the control input saturation.
+In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
+Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
+\begin{assum}
+    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
+    \label{assum:feasible}
+\end{assum}
 
@@
     \begin{aligned}
-        \dot{V}_1
+        \ddtt{V}_1
         =&
@@
 \end{equation}
-where $\mv\tau^*:= -\mv f$ is the ideal control input. 
+where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
 Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
@@
     \end{cases},
+    \label{eq:NN:grad}
 \end{equation}
@@
 \begin{remark}
-    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in pracice including the origin.
+    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in practice including the origin.
     Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
@@
 
-The following Lemma is introduced for the stability analysis. % of the last layer of the DNN.
+The following Lemma is introduced for the stability analysis.
 \begin{lem}
@@
 
-Since $\mv\tau = -\estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
+Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
 \begin{equation}\label{eq:linear:map}
@@
     &
-    -\estNN 
+    \estNN 
     % = 
-    % -\myvec(\estNN)
-    =
-    -\myvec(
+    % \myvec(\estNN)
+    =
+    \myvec(
         \estwV_k^\top \estact_k
@@
     = 
-    -(
+    (
         \mm I_{l_{k+1}}
@@
     = &
-    -\underbrace{
+    \underbrace{
         (
@@
 \end{equation}
-Therefore, the convexity of the input constraints in $\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
 that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
@@
     =
+    \tfrac{1}{2}
+    (
         \Vert \estwth_i\Vert^2 
         -
-    \bar\theta_i^2 \le 0
+        \bar\theta_i^2 
+    )    
+    \le 0
     \label{eq:cstr:weight_ball}
@@
     \begin{cases}
-        2\estwth_i,
+        \estwth_i,
         &
@@
 
-% \begin{lem} 
-%     If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum1}, then $\Vert\partial c_j/\partial\estwth_i\Vert$, for all $i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i$, for all $i\in[k,\cdots, i+1]$, remain bounded.
-%     % which can be verified using the boundedness of $\estwth_i,\ \forall i [k,\cdots,i+1]$ (as demonstrated in Section \ref{sec:stability}), and the boundedness of $\Vert\phi_i(\cdot)\Vert$ and $\Vert\nabla\phi_i(\cdot)\Vert$.
-%     \label{lem2}
-% \end{lem}
-
-% \begin{proof}
-
-% The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
-% \begin{equation}
-%     {\partial c_j\over\partial \estwth_i} = {\partial c_j\over\partial \tau} {\partial \tau\over\partial \hat\Phi} {\partial \hat\Phi\over\partial \estwth_i}
-% \end{equation}
-% where $\partial \tau/\partial \hat\Phi=-I_n$, which is bounded.
-From the linear mapping in \eqref{eq linear map}, $\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\Vert\phi_k(\cdot)\Vert$ is bounded due to the properties of the activation functions.
-By Assumption \ref{assum1}, the function $c_j$ is convex.
-The convex function has a bounded derivative with respect to $\tau$, since $\tau$ is a bounded variable (\ie $\partial c_j/\partial\tau$ is bounded).
-Furthermore, $\partial \hat\Phi/\partial \estwth_i$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded.
-This can be verfied by using the definition of $\partial \hat\Phi/\partial\estwth_i$ given in \eqref{eq.
-nabla phi}.
-% Consequently, $\Vert\partial c_j/\partial \estwth_i\Vert,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
-
-% \end{proof}
-
 Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+The following lemma is introduced for the stability analysis.
+
+\begin{lem} 
+    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i,\ \forall i\in[k,\cdots, i+1]$, remain bounded.
+    \label{lem:cstr:grad:bound}
+\end{lem}
+
+\begin{proof}
+
+The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
+\begin{equation}
+    \pptfrac{c_j}{\estwth_i} 
+    = 
+    \pptfrac{c_j}{\mv\tau} 
+    \pptfrac{\mv\tau}{\estNN} 
+    \pptfrac{\estNN}{\estwth_i}
+\end{equation}
+where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
+From the linear mapping in \eqref{eq:linear:map}, $\mv\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
+By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
+The convex function has a bounded derivative with respect to $\mv\tau$, since $\mv\tau$ is a bounded variable (\ie $\pptfrac{c_j}{\mv\tau}$ is bounded). 
+Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
+This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
+Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+
+\end{proof}
+
 The following theorem shows that $\estwth$ and $\fe$ are bounded.
@@
 Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
-This assumption is reasonable, since even if the constraint is inactive \MSRY{Add the reason why it is reasonable.}
-The step-by-step analysis is described as follows.
-\MSRY{start from here plz}
-\subsection*{Step 1: Boundedness of $\estwth_k$, and $\fe$}
-
-% As the result of the time derivative of $V_1$, the radius of invariant set $\Theta_\fe^{c_1}$ of $\fe$ can be obtained as
-
-Assume that all constraints are actve in $\mathcal A$ without loss of generality.
-The dynamics of $\eta_k$ and $\estwth_k$ can be decomposed from \eqref{eq.
-adaptation law th} and \eqref{eq.
-eta dynamics} as
+This assumption is reasonable, since even if the constraint is inactive 
+\MSRY{Add the reason why it is reasonable.}
+We consider two cases: (C$_1$) control input constraints are active, and (C$_2$) control input constraints are inactive.
+Using the fact that amplitude of the control input is only depends on $\estwth_k$ (\ie see \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$), the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
+
+\subsection*{Case (C$_1$): Control input constraints are active.}
+
+As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
+\begin{equation}
+    \Theta_{\fe}^{c_1} 
+    = 
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\text{min}}(\mm K)}
+    \right\}
+    .
+    \label{eq:invariant:c1:fe}
+\end{equation}
+
+To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
+Taking the time derivative of $V_2$ yields:
 \begin{equation}
     \begin{aligned}
-        \dot\eta_k =
-        & 
-        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}{\partial \hat\Phi\over \partial \estwth_k}
-        =
-        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}(I_{l_{k+1}}\otimes \hat\phi_k^\top)\\
-        \dot{\estwth}_k =
-        & -\alpha 
-        \bigg[
-            \eta_k^\top W\xi+
-            \sum_{j\in\mathcal{A}}
-            \lambda_j{\partial c_j\over\partial \estwth_k}
-        \bigg]
+        \ddtt  V_2 
+        =& 
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \textstyle\sum_{j\in\mathcal{I}}
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        =&
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        \\
+        &
+            +
+            \textstyle\sum_{
+                j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+            }
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        \underbrace{
+            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
+        }_{:=c_1\in\R_{>0}}
+        \norm{\fe}
+        \norm{\estwth_k}
+        \\
+        &
+        -
+        \underbrace{
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j 
+        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
+        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        c_1     
+        \norm{\fe}
+        \norm{\estwth_k}
+        .
     \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, $\Vert \eta_k\Vert_F$ is bounded, since $A_\xi$ is a stable matrix and the term $-B_\xi(\partial h/\partial \tau)(I_{l_{k+1}}\otimes\hat\phi_k^\top)$ is also bounded.
-
-Let $\mathcal{V}: \R^{2n} \times \R^{\Xi} \to \R_{>0}$ denote the Lyapunov function:
-\begin{equation}
-    \mathcal{V} = \frac{1}{2} \xi^\top P \xi + \frac{1}{2 \alpha} \hat{\wth}_k^\top \hat{\wth}_k,
-    \label{eq. Lyapunov func}
-\end{equation}
-with the Lyapunov equation $A_\xi^\top P + P A_\xi = -Q$, where $A_\xi < 0$, $P = P^\top > 0$, and $Q > 0$.
-Taking the time derivative of $\mathcal{V}$ yields:
+    \label{eq:lya2:dot}
+\end{equation}
+According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
+\begin{equation}
+    \Theta_{\theta_k}^{c_1} 
+    = 
+    \left\{ 
+        \estwth_k \in \R^{\Xi_{k}} 
+        \mid 
+        \norm{\estwth_k} 
+        \le 
+        \tfrac{
+            c_1(2\bar\tau+\bar\tau_d)
+        }{
+            \lambda_{\theta_k}\lambda_\text{min}(\mm K)
+        }
+    \right\}
+    .
+    \label{eq:invariant:c1:wth}
+\end{equation}
+
+The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
+For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{c_1}$ is squeezed to a point.
+The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
+It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
+This drives $\estwth_k$ to the origin until the constraint is satisfied (\ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space).
+
+Therefore, the boundedness of $\estwth$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{c_1}$ and $\Theta_{\theta_k}^{c_1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
+
+\subsection*{Case (C$_2$): Control input constraints are inactive.}
+
+Since, here, the control input constraints are inactive, $\sat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
+Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
 \begin{equation}
     \begin{aligned}
-        \dot{\mathcal{V}} 
-        &= -\frac{1}{2} \xi^\top Q \xi + \xi^\top P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon) \\
-        &\quad - \hat{\wth}_k^\top \left( \eta_k W \xi + \sum_{j \in \mathcal{A}} \lambda_j \frac{\partial c_j}{\partial \hat{\wth}_k} \right)
+        \ddtt V_3
+        =&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\bar\tau_d\norm{\fe}
+        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
+        \\
+        &
+        -\estwth_k^\top (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        )
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(
+            \bar\tau_d+\norm{
+                \underbrace{
+                    \idealNN+\mv\epsilon
+                }_{=\mv\tau^*}
+            }
+        )
+        \norm{\fe}
+        \\
+        &
+        -\estNN^\top\fe 
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(\bar\tau_d+\bar\tau)
+        \norm{\fe}
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        .
     \end{aligned}
-    \label{eq. Lyapunov dot}
-\end{equation}
-By applying the boundedness of $\Delta := P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon)$ and $M := \eta_k W$, where $\Vert \Delta \Vert \leq \bar{\Delta} < \infty$ and $\Vert M \Vert_F \leq \bar{M} < \infty$, this simplifies to:
-\begin{equation}
-    \begin{aligned}
-        \dot{\mathcal{V}} 
-        &\leq \left( -\frac{\lambda_{\text{min}}(Q)}{2} + \frac{\bar{M}}{2} \right) \Vert \xi \Vert^2 + \bar{\Delta} \Vert \xi \Vert \\
-        &\quad + \frac{\bar{M}}{2} \Vert \hat{\wth}_k \Vert^2 - \sum_{j \in \mathcal{A}} \lambda_j \hat{\wth}_k^\top \frac{\partial c_j}{\partial \hat{\wth}_k}.
-    \end{aligned}
-    \label{eq. dot Vk 1}
-\end{equation}
-
-By representing the term $\partial c_{\wth_k}/\partial \estwth_k$ in the last inequality as $\partial c_{\wth_k}/\partial \estwth_k=2\estwth_k$ using the result provided in \eqref{eq weight norm cnst grad}, $\dot {\mathcal V}$ can be rewritten as
-\begin{equation}
-    \begin{aligned}
-        \dot {\mathcal V} \le&
-        (\cdot) + 
-        \bigg(
-            -2\lambda _{\wth_k}+{\bar M}/{2}
-        \bigg)
-        \Vert\estwth_k\Vert^2 
-        \\
-        &- \underbrace{
-        \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\estwth_k^\top{\partial c_j\over\partial \estwth_k}
-        }_{>0, \text{\;by Lemma} \ref{lem1} \text{\;and\;} \text{Assumption} \ref{assum2}}	
-        \\
-        \le&
-        \bigg(
-            -{\lambda_\text{min}(Q)}/{2}+{\bar M}/{2}
-        \bigg)
-        \Vert\xi\Vert^2
-        +\bar \Delta \Vert \xi\Vert 
-        \\&
-        + 
-        \bigg(
-            -2\lambda _{\wth_k}+{\bar M}/{2}
-        \bigg)
-        \Vert\estwth_k\Vert^2 
-    \end{aligned}
-    \label{eq. dot Vk 2}
-\end{equation}
-%From \eqref{eq. dot Vk 2}, by defining $P=I_2$, if the control gains ${k_q}$ and ${k_z}$ are selected sufficiently large such that
-Define $P=I_2$, leading to $Q = -A_{\xi}^\top - A_{\xi}$.
-Consequently, the minimum eigenvalues ${\lambda_{\text{min}}(Q)}$ is determined by $2\min({k_q},{k_z})$, as follows from the structure of the matrix $A_{\xi}$.
-From \eqref{eq.
-dot Vk 2}, if the control gains ${k_q}$ and ${k_z}$ are chosen sufficiently large to satisfy the condition:
-%is a function of $k_q$ and $k_z$, as per the definition of matrix $A_{\xi}$. From \eqref{eq. dot Vk 2}, if the control gains ${k_q}$ and ${k_z}$ are chosen sufficiently large such that
-\begin{equation}
-    % -\lambda_\text{min}(Q)/2+M/2<0
-    \min({k_q},{k_z})>\bar M/2
-    \label{eq. ctrl stable condition}
-\end{equation}
-and if the Lagrange multiplier $\lambda_{\wth_k}$ for the weight norm constraint of the $k\textsuperscript{th}$ layer is increased sufficiently, such that
-\begin{equation}\label{eq: lambda bk}
-    -2\lambda_{\wth_k} +{\bar M/ 2}<0,  
-\end{equation}
-(as dictated by \eqref{eq.
-adaptation law L} when the corresponding constraint is violated, \ie $c_{\wth_k}=\Vert \estwth_k\Vert^2 -\bar\wth_k^2 > 0$), then both $\xi$ and $\estwth_k$ will remain bounded within the compact sets $\wth_\xi$ and $\wth_{\estwth_k}$, defined as
-\begin{equation}
-    \wth_\xi = 
-    \bigg\{ \xi \ \bigg\vert\ \Vert\xi\Vert \le  
-    {2\bar \Delta\over \lambda _\text{min}(Q)-\bar M} 
-    \bigg\}
-\end{equation}
-and
-\begin{equation}\label{eq: hat wth k bnd}
-    \wth_{\estwth_k} = 
-    \{
-    \estwth_k 
-    \ 
-    \vert
-    \ 
-    \Vert
-    \estwth_k\Vert \le  
-    \bar\wth_k
-    \}
+    \label{eq:lya3:dot}
+\end{equation}
+Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
+\begin{equation}
+    \Theta_{\fe}^{c_2}
+    =
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{
+            \bar\tau_d+\bar\tau
+        }{
+            \lambda_{\text{min}}(\mm K)
+        }
+    \right\}
     .
 \end{equation}
-The increase of the Lagrange multiplier $\lambda_{\wth_k}$ will halt once $\hat \wth_k$ reaches the compact set $\wth_{\estwth_k}$. Thus, the Lagrange multiplier $\lambda_{\wth_k}$ is bounded.
-% Note that the compact set $\wth_{\estwth_k}$ implies that the input norm constraint for the last $k\textsuperscript{th}$ layer is satisfied because the condition \eqref{eq: lambda bk} is fulfilled in the case of constraint violation.
-
-%Note that $\wth_{\tilde\wth_k}$ converges to $\{\tilde\wth_k\  \vert \ \Vert\tilde\wth_k\Vert\le\bar\wth_k\}$, if $\lambda_{b,k}$ increases such that $4\lambda_{b,k} \gg  \bar M_k$.
-
-% To analyze the boundedness of the Lagrange multipliers, let $\mathcal V_2$ be defined as
-
-% \begin{figure}[!t]
-%     \centering
-%     \includegraphics[width=0.7\linewidth]{lyapunov.drawio.png}
-%     \caption{caption.}
-%     \label{fig: V space}
-% \end{figure}
-
-The boundedness of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal A\setminus\{\wth_i\}_{i\in[0,\cdots,k]}$, can be accessed by considering the convexity of the constraints in $\estwth_k$-space.
-The boundedness of the remaining Lagrange multipliers associated with the weight norm constraints, $\lambda_{\wth_r},\ \forall r\in[0,\cdots,k-1]$, will be examined in Step $i$.
-Based on Assumption \ref{assum1} and Lemma \ref{lem1},
-%(\ie the constraint is convex on $\tau$-space and $\estwth_k$-space, including the origin), 
-\MSRY{CHECK BELOW LINE}
-the equality constraints $c_j \le 0, \ \forall j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, formconvex sets $\wth_{c_j}$ in $\estwth_k$-space.
-Let $\wth_c:= \cap_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots ,k]}} \wth_{c_j}$ represent the intersection of these convex sets, which also contains the origin.
-If $\lambda_j$ increases sufficiently such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal A\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j\estwth_k^\top(\partial c_j/\partial \estwth_k)<0$, then ${\mathcal V}$, and consequently $\Vert\estwth_k\Vert$, will decrease until $\estwth_k$ reaches $\wth_\xi\cap\wth_{\estwth_k}\cap\wth_c$.
-Once $\estwth_k$ hits the boundary of $\wth_c$, the Lagrange multipliers will cease to increase, thus ensuring their boundedness.
-
-% To analyze the boundedness of the Lagrange multipliers, assume that $\lambda_j$ dominantly increased such that $\dot{\mathcal V} \approx -\sum_{j\in\mathcal{A}-\{\wth_k\}}\lambda_j\estwth_k^\top(\partial c_j/\partial \estwth_k)<0$.
-Then $\estwth_k$ approaches into $\wth_\xi\cap\wth_{\estwth_k}\cap\wth_\gamma$.
-It means that the Lagrange multipliers are bounded satisfying the constraints.
-
-%  subset of $\estwth_k$ which satisfy the constraints in $\mathcal A$, can be represented as 
-% \begin{equation}
-%    \wth_\gamma=
-%    \{
-%        \estwth_k
-%        \ \vert\ 
-%        \Vert\estwth_k\Vert
-%        \le \gamma
-%    \}
-% \end{equation}
-% where $\gamma \le \bar\wth_k$, since if $\gamma$ is greater than $\bar\wth_k$, the constraint can be handled by $c_{\wth_k}$. %, as shown in Fig~\ref{fig: V space}.
-
-%To analyze the Lagrange multipliers, assume that the Lagrange multipliers are increased such that
-% \begin{equation}
-%    \dot V \le - \underbrace{
-%     \sum_{j\in\mathcal{A}-b_k}\lambda_j\tilde\wth_k^\top\nabla c_{j,k}
-%     }_{>0}	\le -\gamma_k <0
-% \end{equation}
-%with $\gamma_k\in\mathbb R_{>0}$.
-%It imples that there is a finite time $t_f$ for $\estwth_k$ to converge to the point that satisfies the every constraint, while approaching to the $\idealwth$.
-%When the constraints are satisfied, the reminders of the multipliers in $\mathcal A$ converges.
-
-\subsection*{Step i: Boundedness of $\estwth_i$ and $\eta_i, \ i\in[k-1,\cdots,0]$}
- % \subsubsection*{Step i: Boundedness of $\estwth_i,\eta_i,\ i\in[k-1,\cdots,0]$}
-
-% Following facts
-% \begin{equation}
-%     {\partial \hat\Phi\over \partial \estwth_i} = V_k^\top  \phi'_k \cdots V_{i+1}^\top  \phi'_{i+1} (I_{l_{i+1}}\otimes \phi^\top  _{i})
-% \end{equation}
-
-The boundedness of the Frobenius norm of the gradient $\partial\hat\Phi/\partial \estwth_i$ can be obtained from its definition in \eqref{eq.
-nabla phi}.
-This relies on the fact that the boundedness of $\Vert\estwth_i\Vert,\ \forall i\in[k,\cdots,i+1]$, was already shown in the previous step (\ie Step 1 to Step $i+1$) and the activation functions $\hat\phi_i$ and their derivative $\hat\phi_i'$ are bounded.
-
-The dynamics of $\eta_i$ and $\estwth_i$ for all $i\in [k-1,\cdots,0]$ are represented as
-\begin{equation}
-    \dot\eta_i = 
-    A_\xi\eta_i -B_\xi {\partial h\over\partial\tau}
-    {\partial \hat\Phi\over \partial \estwth_i}
-\end{equation}
-and
-\begin{equation}
-    \begin{aligned}
-        \dot{\estwth}_i 
-        =&
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
+
+\hfill
+
+The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
+The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
+\begin{equation}
+    \ddtt \estwth_i 
+    =
     -\alpha
-        \bigg[
-            \eta_i^\top W\xi+2\lambda_{\wth_i} \estwth_i
-            +
-            \sum_{j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}}\lambda_j{\partial c_j\over\partial \estwth_i}
-        \bigg].
-    \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, $\Vert\eta_i\Vert_F$ is bounded because $A_\xi$ is a stable matrix and the terms $\Vert B_\xi\Vert, \Vert(\partial h/\partial \tau)\Vert_F$, and $\Vert\partial \hat\Phi/\partial\estwth_i\Vert_F$ are bounded.
-When $\lambda_{\wth_i}$ is generated due to a violation of the weight norm constraint, $\estwth_i$ remains bounded because the term $-2\alpha\lambda_{\wth_i}$ is stable, and the residual terms $\Vert\eta_iW\xi\Vert$, $\lambda_j$, and $\Vert(\partial c_j/\partial \estwth_i)\Vert_F$ for all $j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ are bounded, as demonstrated in Step 1 and by Lemma \ref{lem2}.
-The boundedness of each $\lambda_{\wth_i}$ also can be obtained, assuming that $\lambda_{\wth_i}$ is sufficiently increased regulating $\Vert\wth_i\Vert$ into the origin until $c_{\wth_i}$ is satisfied.
-
-Therefore, starting from the boundedness of $\xi$, $\estwth_k$, and $\eta_k$ in the $k\textsuperscript{th}$ layer, the boundednesses of $\estwth_i$ and $\eta_i$ for the remaining layers $i\in[0,\cdots,k-1]$ can be established recursively, down to the input layer ($i=0$).
-Thus, $\estwth$, $\xi$, and $\eta$ are bounded because $\estwth_i,\eta_i,\ \forall i\in[0,\cdots,k]$ and $\xi$ are bounded.
-Furthermore, since the estimated weight vector $\estwth$ is bounded, the weight estimation error $\tilde\wth$ is also bounded, as $\idealwth$ is bounded according to the universal approximation theorem.
+    (
+        \pptfrac{\estNN}{\estwth_i}^\top
+        \fe
+        +
+        \lambda_{\theta_i}\estwth_i
+        +
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j
+        \pptfrac{c_j}{\estwth_i}
+    )
+    .
+\end{equation}
+Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
+
+\hfill
+
+Finally, the filtered error $\fe$ and the estimated weights $\estwth$ are bounded and the imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
 
@@
 % Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^\top$. 
-The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \hat\Phi$.
+The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \estNN$.
 The adaptation law for DNN-BSC, as presented in \cite{Patil:2022aa}, was defined by
 \begin{equation}\label{eq:projection}
-\dot {\estwth}= \text{Proj}_{\Omega}[\alpha  (\partial \hat\Phi/\partial \estwth)M_0^{-1}{\tilde z}],
+\dot {\estwth}= \text{Proj}_{\Omega}[\alpha  (\partial \estNN/\partial \estwth)M_0^{-1}{\tilde z}],
 \end{equation}
@@
         \end{bmatrix}
-            = -{\partial \hat\Phi\over\partial\estwth}
+            = -{\partial \estNN\over\partial\estwth}
             \\
@@
         -\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
             % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
@@
         \end{bmatrix}
-        = +{\partial \hat\Phi\over\partial\estwth}
+        = +{\partial \estNN\over\partial\estwth}
         \\
@@
         +\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \hat\phi_{k}^\top)&
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
             % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
@@
         \bigg(
-            -{\partial \hat\Phi\over\partial\estwth}
+            -{\partial \estNN\over\partial\estwth}
         \bigg)
     \bigg)^\top  
-    = \tau^\top (I_{l_{k+1}}\otimes \hat\phi_k^\top)
+    = \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
     \in \mathbb R^{\Xi}.

### 2025-03-17 src/script_simulation/controllers/CoNAC/loadOpts.m

@@ -6,7 +6,7 @@ function opt = loadOpts(dt)
     
     opt.Gamma = diag([1 1]);
 
-    opt.alpha = 1e+1;
+    opt.alpha = 1e0;
     opt.rho = opt.alpha*0e-0;
     opt.NN_size = [6,8,8,2];
     opt.W = 1;

### 2025-03-17 src/script_simulation/main_TNNLS.m

@@ -13,12 +13,12 @@ FIGURE_PLOT_FLAG    = 1;
 ANIMATION_FLAG      = 0;
 AINMATION_SAVE_FLAG = 0;
 FIGURE_SAVE_FLAG    = 0;
-RESULT_SAVE_FLAG    = 1;
+RESULT_SAVE_FLAG    = 0;
 
 %% SIMULATION SETTING
-ctrl_dt = 1e-4;
-dt = ctrl_dt * 1/1;
-T = 30;
+ctrl_dt = 1/500;
+dt = ctrl_dt * 1/10;
+T = 50;
 t = 0:dt:T;
 rpt_dt = 1;
 

### 2025-03-19 manuscript.tex
subtitute notations using template

--- 2025-03-16 manuscript.tex
@@
 % MY PAKEAGES ========================================
+
+\newcommand*{\q}{\mv{q}}
+\newcommand*{\dq}{\dot{\q}}
+\newcommand*{\ddq}{\ddot{\q}}
+\newcommand*{\qd}{\mv{q_d}}
+\newcommand*{\dqd}{\dot{\qd}}
+\newcommand*{\ddqd}{\ddot{\qd}}
 
@@
 %  SECTION INTRODUCTION ===================================
+
+\section*{Notation}
+In this study, the following notation is used:
+
+\begin{itemize}
+    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
+    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ denotes a vector.
+    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
+    %     \mm A
+    %     := 
+    %     [a_{ij}]
+    %     _{
+    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
+    %     }\allowbreak\in\R^{n\times m}
+    %     $ denotes a vector and a matrix.
+    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
+    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
+    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
+    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
+    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
+    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
+\end{itemize}
 
@@
 
-\subsection{Notation}
-In this study, the following notation is used.
-
-\begin{itemize}
-    \item $\otimes$ denotes the Kronecker product \cite{Bernstein:2009aa}.
-    \item $\mv x_{(i)}$ denotes the $i\textsuperscript{th}$ element of vector $\mv x$.    
-    % \item $A_{(i,j)}$ is the $i\textsuperscript{th}$ row-$j\textsuperscript{th}$ column element of matrix $A$.
-    \item $\text{row}_j(\mm A)$ denotes the $j\textsuperscript{th}$ row of $\mm A\in\mathbb{R}^{n\times m}$. 
-    % \item $\text{col}_i(A)$ and $\text{row}_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\mathbb{R}^{n\times m}$, respectively.
-    \item $\text{vec}(\mm A)\triangleq [\text{row}_1(\mm A^\top )  ,\cdots,\text{row}_m(\mm A^\top )]^\top $ for $\mm A\in\mathbb{R}^{n\times m}$.
-    % \item $\text{vec}(A)\triangleq [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\mathbb{R}^{n\times m}$.
-    \item $\lambda_\text{min}(A)$ denotes the minimum eigenvalue of $A\in\mathbb{R}^{n\times n}$.
-\end{itemize}
-
 \subsection{Model Dynamics and Control Objective}
@@
 \begin{equation}
-    \mm M(\mv q)\ddot {\mv q} + \mm C(\mv q,\dot {\mv q})\dot {\mv q} + \mm G(\mv q) + \mm F(\mv q) = \mv \tau
+    \mm M\ddq + \mm V_m\dq + \mm F + \mm G + \mv\tau_d
+    =
+    \mv\tau 
     \label{eq. system dynamics 1}
 \end{equation}
-where $\mv q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M(\mv q)\in\mathbb{R}^{n\times n}$, $\mm C(\mv q,\dot {\mv q})\in\mathbb{R}^{n\times n}$, and $\mm G(\mv q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F(\mv q)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\mm M_0>0,\mm C_0$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
+where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
+Using the user-designed matrices $\mm M_0>0,\mm V_{m0}$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
 \begin{equation}
-    \mm M_0\ddot {\mv q}+\mm C_0\dot {\mv q}+\mm G_0 = \mv \tau + \mv f(\mv q,\dot {\mv q},\ddot {\mv q})
+    \mm M_0\ddq+\mm V_{m0}\dq+\mm G_0 = \mv \tau + \mv f(\q,\dq,\ddq)
     \label{eq. system dynamics 2}
 \end{equation}
-where $\mv f(\mv q,\dot {\mv q},\ddot {\mv q}) \triangleq -(\mm M-\mm M_0)\ddot {\mv q}-(\mm C-\mm C_0)(\mv q,\dot {\mv q})\dot {\mv q} -(\mm G-\mm G_0) -\mm F(\mv q)$ denotes the residual unknown term.
+where $\mv f(\q,\dq,\ddq) := -(\mm M-\mm M_0)\ddq-(\mm V_m-\mm V_{m0})\dq -(\mm G-\mm G_0) -\mm F$ denotes the residual unknown term.
 
-Hence, the objective of the control design is to make $\mv q$ track the continuously differentiable desired trajectory $\mv q_d(t):\R\to \R^n$ under the unknown terms $\mv f$.
+Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd(t):\R\to \R^n$ under the unknown terms $\mv f$.
 
@@
 
-The backstepping control-based approach is utilized to generate a reference signal $\mv z^*\triangleq -{k_q}\tilde {\mv q}+\dot {\mv q}_d$ for $\mv {z}\triangleq \dot {\mv q}$, where $\tilde {\mv q}\triangleq \mv {q} - {\mv q}_d$ and $k_q\in\R_{>0}$.
+The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
 The desired stabilizing controller can be designed as follows:
@@
         ( 
-            -\mm M_0\tilde {\mv q}+\mm C_0{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
+            -\mm M_0\tilde {\q}+\mm V_{m0}{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
         )
@@
 \end{equation}
-where $\tilde {\mv z}\triangleq \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
+where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
 Note that the desired controller cannot be realized because of $\mv f$.
@@
 \begin{equation}
-    \mv \Phi({\mv q_{NN}};\mv \theta)\triangleq \mm V_1^\top \mv \phi(\mm V_0^\top {\mv q_{NN}})
+    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
 \end{equation}
-where ${\mv q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\mm V_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in[0,1]$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\mv \phi:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
-The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\mv \phi(\mv x) = [\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1]^\top $).
-For further simplicity, let $\mv \theta\triangleq[\mv \theta_1^\top ,\mv \theta_0^\top ]^\top \in\R^{\Xi}$ denote the total weight vector, where $\mv \theta_i\triangleq \text{vec}(\mm V_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
+where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
+The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
+For further simplicity, let $\wth:=\left(\wth_1^\top ,\wth_0^\top \right)^\top \in\R^{\Xi}$ denote the total weight vector, where $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
 $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
 
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\mv \theta^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\mv q_{NN}}\in\Omega_{NN}} \allowbreak \Vert\mv \Phi({\mv q_{NN}};\mv \theta^*) - \mv \tau^*\Vert=\epsilon<\infty$ \cite{Cybenko:1989aa}.
-The ideal weight vector $\mv \theta^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\hat{\mv \theta}=[\hat{\mv \theta}_1^\top ,\hat{\mv \theta}_0^\top ]^\top $ of $\mv \theta^*=[\mv \theta_1^{*\top},\mv \theta_0^{*\top}]^\top $, the desired controller $\mv \tau^*\approx -\mv \Phi(\mv q_{NN};\mv \theta^*)-\epsilon$ can be approximated as follows:
+Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
+The ideal weight vector $\wth^*$ is typically assumed to be bounded.
+Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\epsilon$ can be approximated as follows:
 \begin{equation}
-    \mv \tau \triangleq -\mv \Phi({\mv q_{NN}};\hat{\mv \theta}).
+    \mv \tau := -\NN({\q_{NN}};\estwth)
+    .
     \label{eq. control law}
 \end{equation}
-For further sections, let $\mv \Phi^*\triangleq\mv \Phi({\mv q_{NN}};\mv \theta^*)$ and $\mv \phi^* \triangleq\mv \phi(\mm V_0^{*\top}{\mv q_{NN}})$, and let $\hat{\mv \Phi}\triangleq{\mv \Phi}({\mv q_{NN}};\hat{\mv \theta})$, $\hat{\mv \phi} \triangleq\mv \phi(\hat {\mm V}_0^{\top}{\mv q_{NN}})$ and $\hat{\mv \phi}' \triangleq \partial \hat{\mv \phi}/\partial (\hat {\mm V}_0^\top \mv q_{NN})$.
+For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\NN^* :=\NN({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estNN :=\NN(\estwV_0^{\top}{\q_{NN}})$ and $\estNN' := \pptfrac{\estNN}{\estwV_0^\top \q_{NN}}$.
 
@@
 desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi\triangleq[\tilde {\mv q}^\top ,\tilde {\mv z}^\top ]^\top \in\R^{2n}$ as follows:
+control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=\left(\tilde {\q}^\top ,\tilde {\mv z}^\top\right)^\top \in\R^{2n}$ as follows:
 \begin{equation}
@@
     = 
-    \mm A_\xi{\mv \xi}+\mm B_\xi(\mv \Phi^*-\hat{\mv \Phi}+\epsilon)
+    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
 \end{equation}
-where 
+where $\mv \epsilon\in\R^2$ is bounded approximation error and 
 \begin{equation}
-    \mm A_\xi \triangleq 
+    \mm A_\xi := 
     \begin{bmatrix}
-        -{k_q} \mm I_{n\times n} &\mm I_{n\times n}
+        -{k_q} \mm I_{n} &\mm I_{n}
         \\
-        -\mm I_{n\times n}& -{k_z} \mm I_{n\times n}
+        -\mm I_{n}& -{k_z} \mm I_{n}
     \end{bmatrix}
     ,\ 
-    \mm B_\xi \triangleq 
+    \mm B_\xi := 
     \begin{bmatrix}
@@
 
-Using the augmented error $\mv \xi$, the quadratic objective function is defined as
-\begin{equation}
-    J(\mv \xi;\hat{\mv \theta})\triangleq
-    {1\over 2}
-    \mv \xi^\top \mm W\mv \xi
-\end{equation}
-where $\mm W=\mm W^\top >0$ denotes the weighting matrix.
-
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\Vert{\hat{\mv\theta}}_i\Vert^2-\bar\theta^2_i,\ i\in[0,1]$.
-% Then the objective of the adaptation process can be reformulated into the constrained optimization problem as follows:
+For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in[0,1]$.
 The control problem can be reformulated into a constrained optimization problem as follows:
@@
     \begin{matrix}
-        \min_{{\hat{\mv\theta}}} \ J(\mv \xi;{\hat{\mv\theta}})
+        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
+        :=
+        {1\over 2}
+        \mv \xi^\top \mm \Lambda \mv \xi
         \\ \\
         \begin{aligned}
-        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I = [\theta_0,\theta_1].
+        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
+        = 
+        \{\theta_0,\theta_1\}
+        ,
         \end{aligned}
@@
 \end{equation}
-In this optimization problem, $\xi$ is considered a predefined parameter.
+where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
+In this optimization problem, $\mv \xi$ is considered a predefined parameter.
 The corresponding Lagrangian function is defined as
@@
         \mv \xi,
-        {\hat{\mv\theta}},
+        {\estwth},
         [\lambda_j]_{j\in\mathcal I}
     )
-    \triangleq 
-    J(\mv \xi;{\hat{\mv\theta}})
+    := 
+    J(\mv \xi;{\estwth})
     +
-    \sum_{j\in\mathcal I} \lambda_jc_j({\hat{\mv\theta}})
+    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
     .
@@
 % where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{{\hat{\mv\theta}}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
+To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
+\begin{subequations}
     \begin{align}
-        \dot {{\hat{\mv\theta}}}&=-\alpha {\partial L\over\partial {\hat{\mv\theta}}}
+            \ddtt {{\estwth}}
+            &
+            =
+            -\alpha 
+            \pptfrac{L}{{\estwth}}
             =-\alpha 
-        \bigg(
-        {\partial J\over \partial {\hat{\mv\theta}}}+\sum_{j\in\mathcal{A}}
-        \lambda_j {\partial c_j\over \partial {\hat{\mv\theta}}}
-        \bigg),
+            \left(
+                \pptfrac{J}{{\estwth}}
+                +
+                \textstyle\sum_{j\in\mathcal{I}}
+                \lambda_j 
+                \pptfrac{c_j}{\estwth}
+            \right),
         \label{eq. adaptation law th}
             \\
-        \dot\lambda_j& = \beta_j{\partial L\over\partial \lambda_j} = \beta_j c_j ,
+            \ddtt\lambda_j
+            & 
+            = 
+            \beta_j
+            \pptfrac{L}{\lambda_j} 
+            = 
+            \beta_j c_j ,
             \quad\quad\quad\quad      \      
@@
             \\
-        \lambda_j & = \max(\lambda_j,0) ,
+            \lambda_j 
+            & 
+            = 
+            \max(\lambda_j,0) ,
             \quad\quad\quad\quad\ \ \ \ \ 
@@
     \end{align}
+    \label{eq. adaptation laws}
+\end{subequations}
 where $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
@@
 
-Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\partial J/\partial {\hat{\mv\theta}}$) in \eqref{eq. adaptation law th} can be represented as
+Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
 \begin{equation}
-    {\partial J\over\partial {\hat{\mv\theta}}}
+    \pptfrac{J}{\estwth}
     =
-    {\partial \mv\xi\over\partial {\hat{\mv\theta}}}^\top 
-    \mm W
-    {\partial \mv\xi\over\partial {\hat{\mv\theta}}}
+    \pptfrac{\mv\xi}{\estwth}^\top 
+    \mm \Lambda
+    \pptfrac{\mv\xi}{\estwth}
     .
 \end{equation}
-The calculation of $\partial J/\partial {\hat{\mv\theta}}$ is not straightforward because of the dynamics of $\xi$.
+The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
 Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
 \begin{equation}
-    \dot {\mm \eta} =
+    \ddtt{\mm \eta} =
     \mm A_\xi - \mm B_\xi 
-    % (\partial \hat{\mv\Phi}/\partial {\hat{\mv\theta}})
-    {\partial \hat{\mv\Phi}\over\partial {\hat{\mv\theta}}}
+    % (\partial \estNN/\partial {\estwth})
+    \pptfrac{\estNN}{\estwth}
     ,
@@
 \end{equation}
-where ${\mm \eta}\triangleq \partial \mv\xi/\partial {\hat{\mv\theta}}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
+where ${\mm \eta}:= \pptfrac{\mv\xi}{\estwth}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
 The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
-By decomposing for each layer, the dynamics of ${\mm \eta}_i\triangleq \partial \mv\xi/\partial {\hat{\mv\theta}}_i\in\R^{2n\times \Xi_i}$ can be represented as
+By decomposing for each layer, the dynamics of ${\mm \eta}_i:= \pptfrac{\mv\xi}{\estwth}_i\in\R^{2n\times \Xi_i}$ can be represented as
 \begin{equation}
     \begin{aligned}
-        \dot{\mm \eta} =&
+        \ddtt{\mm \eta} 
+        \!=\!&
         \begin{bmatrix}
@@
         \\
-        =&
+        \!=\!&
         \mm A_\xi
@@
         % \end{bmatrix}
-        -\mm B_\xi
+        \!-\!
+        \mm B_\xi
         % \begin{bmatrix}
         [
-            (\mm I_{l_2}\otimes \hat{\mv\phi}^\top )
+            (\mm I_{l_2}\!\otimes\!\estact^\top )
             \ \ 
-            \hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_{l_1}\otimes {\mv q_{NN}}^\top )
+            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
         ]
@@
 \end{equation}
-The calculation of $\partial \hat{\mv\Phi}/\partial{\hat{\mv\theta}}$ is introduced in \cite{Patil:2022aa}.
-In conclusion, the gradient of the objective with respect to the weights can be obtained as ${\partial J/\partial {\hat{\mv\theta}}} = {\mm \eta}^\top\mm W\mv\xi$ by simulating the sensitivity equation \eqref{eq.
+The calculation of $\pptfrac{\estNN}{\estwth}$ is introduced in \cite{Patil:2022aa}.
+In conclusion, the gradient of the objective with respect to the weights can be obtained as $\pptfrac{J}{\estwth} = {\mm \eta}^\top\mm \Lambda\mv\xi$ by simulating the sensitivity equation \eqref{eq.
 sen eq}.
@@
 \begin{equation}
-    \frac{\partial c_{\theta_0}}{\partial{\hat{\mv\theta}}}
+    \pptfrac{c_{\theta_0}}{{\estwth}}
     = 
@@
         \mm 0_{\Xi_1\times 1} \\
-        2{\hat{\mv\theta}}_0 
+        2{\estwth}_0 
     \end{bmatrix}
     ,\quad
-    \frac{\partial c_{\theta_1}}{\partial{\hat{\mv\theta}}}    
+    \pptfrac{c_{\theta_1}}{{\estwth}}    
     = 
     \begin{bmatrix}
-        2{\hat{\mv\theta}}_1 \\
+        2{\estwth}_1 \\
         \mm 0_{\Xi_0\times 1}
@@
 control law} and the adaptation law \eqref{eq.
-adaptation law th}, \eqref{eq.
-adaptation law L} and \eqref{eq.
-adaptation law L max} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\hat{\mv\theta}}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
+adaptation laws} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\estwth}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
 ctrl stable condition}.
@@
 
-\subsection*{Step 1: Boundedness of ${\hat{\mv\theta}}_1,{\mm \eta}_1,\mv \xi$}
+\subsection*{Step 1: Boundedness of ${\estwth}_1,{\mm \eta}_1,\mv \xi$}
 
@@
 \begin{equation}    
-    \dot {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
+    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
     (
-        -\hat {\mm V}_1^\top \hat{\mv\phi}+\mv w(t)
+        -\estwV_1^\top \estact+\mv w(t)
     )
 \end{equation}
-where $\mv w(t)\triangleq {\mm V}_1^{*T}\mv\phi^*+\mv \epsilon$ is a lumped residual term, which is bounded as $\Vert\mv  w(t)\Vert\le \bar w< 0$ since $\Vert\mv\theta_1^*\Vert$ and $\Vert\mv\phi^*\Vert$ are bounded.
-The dynamics of ${\mm \eta}_1$ and ${\hat{\mv\theta}}_1$ are represented as
+where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1}$ and $\norm{\idealact}$ are bounded.
+The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
 \begin{equation}
     \begin{aligned}
-        \dot{\mm \eta}_1 =
+        \ddtt{\mm \eta}_1 =
         & 
-        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )
+        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
+        ,
         \\
-        \dot{{\hat{\mv\theta}}}_1 =
+        \ddtt{{\estwth}}_1 =
         & -\alpha 
         (
-            {\mm \eta}_1^\top \mm W\mv\xi+2\lambda_{\theta_1} {\hat{\mv\theta}}_1
-        ).
+            {\mm \eta}_1^\top 
+            \mm \Lambda
+            \mv\xi
+            +
+            2\lambda_{\theta_1} {\estwth}_1
+        )
+        .
     \end{aligned} 
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \hat{\mv\phi}^\top )$ is bounded.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.
 
-Define the Lyapunov function $\mathcal V_1=(1/2)\mv\xi^\top \mm P\mv\xi+(1/2\alpha){\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
-Using a proposition $\hat {\mm V}_1^\top \hat{\mv\phi} = \text{vec}(\hat {\mm V}_1^\top \hat{\mv\phi})=\text{vec}(\hat{\mv\phi}^\top \hat {\mm V}_1) = (\mm I_{l_2}\otimes {\hat{\mv\theta}}^\top )\text{vec}(\hat {\mm V}_1)=(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $\mathcal V_1$ is
+Define the Lyapunov function $V_1=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
+Using a proposition $\estwV_1^\top \estact = \myvec(\estwV_1^\top \estact)=\myvec(\estact^\top \estwV_1) = (\mm I_{l_2}\otimes {\estact}^\top )\myvec(\estwV_1)=(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $V_1$ is
 \begin{equation}
     \begin{aligned}
-        \dot {\mathcal V}_1 
-        =& 
-        {1\over 2}
-        \mv \xi^\top (\mm A_\xi^\top \mm P+\mm P\mm A_\xi)\mv \xi
-        +
-        \mv \xi^\top \mm P ( -\mm B_\xi\hat {\mm V}_1^\top \hat {\mv \phi} +\mm B_\xi \mv w(t) )\\
+        \ddtt \! {V}_1 
+        \!=\!& 
+        \tfrac{1}{2}
+        \mv \xi^\top 
+            (
+                \mm A_\xi^\top \mm P+\mm P\mm A_\xi
+            )
+        \mv \xi
+        \!+\!
+        \mv \xi^\top \mm P (
+            \!-\!\mm B_\xi\estwV_1^\top \estact +\mm B_\xi \mv w(t) 
+        )\\
         &
-        +{\hat{\mv\theta}}_1^\top 
-        (
-            -{\mm \eta}_1^\top \mm W \xi-2\lambda_{\theta_1} {\hat{\mv\theta}}_1 
-        )
+        +{\estwth}_1^\top 
+        \!
+        (\!
+            -{\mm \eta}_1^\top \mm \Lambda \xi-2\lambda_{\theta_1} {\estwth}_1 
+        \!)
         \\
         =& 
-        -{1\over 2}\mv \xi^\top \mm Q\mv \xi 
+        -\tfrac{1}{2}
+        \mv \xi^\top \mm Q\mv \xi 
         -
-        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \hat{\mv\phi}^\top ){\hat{\mv\theta}}_1 
+        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1 
         +\mv \xi^\top \mv \Delta
@@
         &
-        -{\hat{\mv\theta}}_1^\top {\mm \eta}_1^\top \mm W\mv \xi
-        -2\lambda_{\theta_1} {\hat{\mv\theta}}_1^\top {\hat{\mv\theta}}_1
+        -{\estwth}_1^\top {\mm \eta}_1^\top \mm \Lambda\mv \xi
+        -2\lambda_{\theta_1} {\estwth}_1^\top {\estwth}_1
         \\
         \le&
-        -(1/2)\lambda_\text{min}(\mm Q)\Vert \mv \xi\Vert ^2
-        +\bar\Delta \Vert \mv \xi\Vert  
-        +\bar M\Vert \mv \xi\Vert  \Vert {\hat{\mv\theta}}_1\Vert
+        -
+        \tfrac{1}{2}
+        \lambda_\text{min}(\mm Q)\norm{\mv \xi} ^2
+        +\bar\Delta \norm{\mv \xi}
+        +\bar M\norm{\mv \xi} \norm{{\estwth}_1}
         \\
@@
         -2\lambda_{\theta_1}
-        \Vert{\hat{\mv\theta}}_1\Vert ^2
+        \norm{{\estwth}_1}^2
         \\
@@
         (
-        -{\lambda_\text{min}(\mm Q)/ 2} +{\bar M/ 2}
+        -{\lambda_\text{min}(\mm Q)/ 2} +{\tfrac{\bar M}{2}}
         )
-        \Vert \mv \xi\Vert ^2 +\bar\Delta \Vert \mv \xi\Vert  
+        \norm{\mv \xi}^2 +\bar\Delta \norm{\mv \xi}
         \\
@@
         -2\lambda_{\theta_1} 
-        +\bar M/ 2
+        +\tfrac{\bar M}{2}
         )
-        \Vert \tilde{\mv \theta}_1\Vert ^2 
+        \norm{\tilde{\wth}_1}^2 
         \end{aligned}
@@
 \end{equation}
-where $\mv \Delta\triangleq \mm P\mm B_\xi \mv w(t)$ and $\mm M\triangleq -\mm P\mm B_\xi(\mm I_{l_2}\otimes \hat{\mv\phi}^\top )+\mm W{\mm \eta}_1$ are bounded such that $\Vert\mv \Delta\Vert\le\bar\Delta<\infty$ and $\Vert\mm M\Vert_F\le \bar M< \infty$, respectively.
+where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estNN^\top )+\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.
 
@@
 \begin{equation}
-    \text{min}(k_q,k_z)>\bar M/2
+    \text{min}(k_q,k_z)>\tfrac{\bar M}{2}
     ,
@@
 \end{equation}
-and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\bar M/2$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
+and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\tfrac{\bar M}{2}$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
 \begin{equation}
     \Theta_\xi = 
-    \bigg\{
-        \mv\xi\mid\Vert\mv\xi\Vert \le  
-        {
-            \bar \Delta \over \lambda _\text{min}(\mm Q)-\bar M/2
+    \left\{
+        \mv\xi\mid
+        \norm{\mv\xi}
+        \le  
+        \tfrac{
+            \bar \Delta
+        }{
+            \lambda _\text{min}(\mm Q)-{\bar M}/{2}
         } 
-    \bigg\}
+    \right\}
     ,
 \end{equation}
-and the weight estimation $\theta^*_1$ is bounded in
+and the weight estimation $\estwth_1$ is bounded in
 \begin{equation}
-    \Theta_{{\hat{\mv\theta}}_1} = 
+    \Theta_{{\theta}_1} = 
     \{ 
-        {\hat{\mv\theta}_1} 
+        {\estwth_1} 
         \mid
-        \Vert{\hat{\mv\theta}_1}\Vert 
+        \norm{\estwth_1}
         \le  
@@
 \end{equation}
-The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\hat{\mv\theta}}_1$ approaches the compact set $\Theta_{{\hat{\mv\theta}}_1}$, satisfying the constraint $c_{\theta_1}$.
+The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\estwth}_1$ approaches the compact set $\Theta_{{\theta}_1}$, satisfying the constraint $c_{\theta_1}$.
 
-\subsection*{Step 2: Boundedness of ${\hat{\mv\theta}}_0,{\mm \eta}_0$}
+\subsection*{Step 2: Boundedness of ${\estwth}_0,{\mm \eta}_0$}
 
-The dynamics of ${\mm \eta}_0$ and ${\hat{\mv\theta}}_0$ are represented as
+The dynamics of ${\mm \eta}_0$ and ${\estwth}_0$ are represented as
 \begin{equation}
     \begin{aligned}     
-        \dot{\mm \eta}_0 =& 
+        \ddtt{\mm \eta}_0 =& 
         \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )
+        \estwV_1^\top \estact'(\mm I_1\otimes {\q_{NN}}^\top )
         \\
-        \dot{{\hat{\mv\theta}}}_0
+        \ddtt{{\estwth}}_0
         =&
@@
         (
-            {\mm \eta}_0^\top \mm W\mv \xi+2\lambda_{\theta_0} {\hat{\mv\theta}}_0
+            {\mm \eta}_0^\top \mm \Lambda\mv \xi+2\lambda_{\theta_0} {\estwth}_0
         )
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\hat {\mm V}_1^\top \hat{\mv\phi}'(\mm I_1\otimes {\mv q_{NN}}^\top )$ is bounded.
-To obtain the invariance set of ${\hat{\mv\theta}}_0$, taking the time derivative of the Lyapunov function $\mathcal V_0=(1/2\alpha){\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0$ yields:
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\estwV_1^\top \estact'(\mm I_1\otimes {\q_{NN}}^\top )$ is bounded.
+To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=(1/2\alpha){\estwth}_0^\top {\estwth}_0$ yields:
 \begin{equation}
     \begin{aligned}
-        \dot {\mathcal V}_0 =& 
-        {\hat{\mv\theta}}_0^\top (-{\mm \eta}_0\mm W\mv \xi -2\lambda_{\theta_0}{\hat{\mv\theta}}_0)
+        \ddtt {V}_0 =& 
+        {\estwth}_0^\top (-{\mm \eta}_0\mm \Lambda\mv \xi -2\lambda_{\theta_0}{\estwth}_0)
         \\
         \le &
-        \Vert{\hat{\mv\theta}}_0\Vert \Vert {\mm \eta}_0\mm W\mv \xi\Vert -2\lambda_{\theta_0} {\hat{\mv\theta}}_0^\top {\hat{\mv\theta}}_0
+        \norm{{\estwth}_0} \norm{{\mm \eta}_0\mm \Lambda\mv \xi} 
+        -
+        2\lambda_{\theta_0} {\estwth}_0^\top {\estwth}_0
+        ,
         \\
         \le &
-        -2\lambda_{\theta_0} \Vert{\hat{\mv\theta}}_0\Vert^2 + \Vert {\mm \eta}_0\mm W\mv \xi\Vert \Vert {\hat{\mv\theta}}_0\Vert 
+        -2\lambda_{\theta_0} 
+        \norm{{\estwth}_0}^2 
+        + 
+        \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
+        \norm{{\estwth}_0}
         .
@@
 \begin{equation}
-    \Theta_{{\hat{\mv\theta}}_0} =
+    \Theta_{{\theta}_0} =
     \{
-        {\hat{\mv\theta}}_0\mid\Vert{\hat{\mv\theta}}_0\Vert 
+        {\estwth}_0\mid\norm{\estwth_0}
         \le
-        \Vert{\mm \eta}_0\mm W\mv \xi\Vert/\lambda_{\theta_0}
+        \tfrac{
+            \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
+        }{
+            \lambda_{\theta_0}
+        }
     \}
@@
 \end{equation}
-If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\hat{\mv\theta}}_0}$ converges to $\{{\hat{\mv\theta}}_0\ \vert \ \Vert{\hat{\mv\theta}}_0\Vert \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
+If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
 Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.
@@
 The values of the system parameters are given in Table~\ref{table: system parameters}.
-The reference signal of $\mv q=[q_1,q_2]^\top $ is defined as follows:
+The reference signal of $\q=[q_1,q_2]^\top $ is defined as follows:
 \begin{equation}
-    \mv q_d
+    \qd
     =
@@
     \begin{bmatrix}
-        +\cos(\pi/2 t) + 1 \\
-        -\cos(\pi/2 t) - 1 
+        +\cos(
+            \tfrac{\pi}{2}t
+        ) + 1 \\
+        -\cos(
+            \tfrac{\pi}{2}t
+        ) - 1 
     \end{bmatrix}
@@
 The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters $\lambda$, $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively.
-The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \Vert\mv \xi\Vert^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
+The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \norm{\mv \xi}^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
 The parameter dependencies of the controllers were examined via various values of the parameters. 
@@
 The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $(1/2)\lambda{\hat{\mv\theta}}^\top {\hat{\mv\theta}}$ to the objective function such that $J_{L_2} = J+(1/2)\lambda{\hat{\mv\theta}}^\top {\hat{\mv\theta}}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
-The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\hat{\mv\theta}}$ as follows:
+The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2} = J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
+The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
 \begin{equation} 
-    \dot{{\hat{\mv\theta}}} = 
-    {\partial J_{L_2}\over\partial {\hat{\mv\theta}}}
+    \ddtt{{\estwth}} = 
+    \pptfrac{J_{L_2}}{\estwth}
     =-\alpha
-    \bigg(
-        {\partial J\over\partial {\hat{\mv\theta}}}+\lambda{\hat{\mv\theta}}
-    \bigg)
+    \left(
+        \pptfrac{J}{\estwth}
+        +
+        \lambda{\estwth}
+    \right)
     .
@@
 \end{equation}
-Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\hat{\mv\theta}}$, where $\sigma\in\R_{>0}$.
-For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\Vert \tilde{\mv z} \Vert{\hat{\mv\theta}}$ is added to the adaptation law as follows:
+Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\estwth}$, where $\sigma\in\R_{>0}$.
+For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\norm{\tilde{\mv z}}{\estwth}$ is added to the adaptation law as follows:
 \begin{equation}
-    \dot{{\hat{\mv\theta}}} = -\alpha
-    \bigg(
-        {\partial J\over\partial {\hat{\mv\theta}}}+\rho\Vert\tilde {\mv z}\Vert{\hat{\mv\theta}}
-    \bigg)
+    \ddtt{{\estwth}} = -\alpha
+    \left(
+        \pptfrac{J}{\estwth}
+        +
+        \rho\norm{\tilde {\mv z}}{\estwth}
+    \right)
     \label{eq. adap eMod}
@@
 where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
-By $\Vert\tilde {\mv z}\Vert$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
+By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
 Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
-The adaptation law of NAC-CO is presented in \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L}, and \eqref{eq. adaptation law L max}.
+The adaptation law of NAC-CO is presented in \eqref{eq. adaptation laws}.
 Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.
 
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\mm M_0=I_2$ and $\mm W=\text{diag}([5,1,15,15])$.
+All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\mm M_0=I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The NN input vector was set to the desired trajectory $\mv q_d$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\mv q_{NN}=[\mv q_d^\top ,1]^\top $.
+The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.
 For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
-The sampling time of the simulation and the simulation termination time were set to $T_s=10^{-4}$ and $T=10$, respectively.
+The sampling time of the simulation and the simulation termination time were set to $T_s=100\ \mu\mathrm{s}$ and $T=10\ \mathrm{s}$, respectively.
 
@@
 For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
-As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\hat{\mv\theta}}$.
+As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\estwth}$.
 Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
@@
 On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
-This is because the stabilizing function $-\alpha\rho\Vert\tilde {\mv z}\Vert{\hat{\mv\theta}}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
+This is because the stabilizing function $-\alpha\rho\norm{\tilde {\mv z}}{\estwth}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
 However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (\ie smaller weight norms are observed as $\rho$ increases.).

### 2025-03-21 manuscript.tex
move macros to template
add more explanation; need to review again to fix typo

@@
     \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
-    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ denotes a vector.
+    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ denotes a vector.
     % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
@@
 
-\section{Introduction}
+\section{Introduction} \label{sec:intro}
 
@@
 \end{equation}
-where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\mm M_0>0,\mm V_{m0}$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
+where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
+Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V_m}$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
 \begin{equation}
-    \mm M_0\ddq+\mm V_{m0}\dq+\mm G_0 = \mv \tau + \mv f(\q,\dq,\ddq)
+    \widehat{\mm M}\ddq+\widehat{\mm V_m}\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
     \label{eq. system dynamics 2}
 \end{equation}
-where $\mv f(\q,\dq,\ddq) := -(\mm M-\mm M_0)\ddq-(\mm V_m-\mm V_{m0})\dq -(\mm G-\mm G_0) -\mm F$ denotes the residual unknown term.
+where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V_m})\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.
 
-Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd(t):\R\to \R^n$ under the unknown terms $\mv f$.
+Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd:=\qd(t):\R\to \R^n$ under the unknown terms $\mv f:=\mv f(\q,\dq,\ddq)$.
 
@@
     \mv \tau^* = 
-    -\mm M_0\cdot ({k_z}\tilde {\mv z})
+    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
     + 
         ( 
-            -\mm M_0\tilde {\q}+\mm V_{m0}{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
+            -\widehat{\mm M}\tilde {\q}
+            +
+            \widehat{\mm V_m}{\mv z}
+            +
+            \widehat{\mm G}
+            -
+            \mv f
+            +
+            \widehat{\mm M} \dot {\mv z}^*
         )
@@
 To approximate the desired controller, an NN is utilized.
+\MSRY{
+    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
+}
 The NN with a single hidden layer is represented as 
@@
 The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
-For further simplicity, let $\wth:=\left(\wth_1^\top ,\wth_0^\top \right)^\top \in\R^{\Xi}$ denote the total weight vector, where $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
-$\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
+For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
 
@@
 The ideal weight vector $\wth^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\epsilon$ can be approximated as follows:
+Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\mv\epsilon$ with bounded approximation error $\mv \epsilon\in\R^2$, can be approximated as follows:
 \begin{equation}
@@
 \end{equation}
-For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\NN^* :=\NN({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estNN :=\NN(\estwV_0^{\top}{\q_{NN}})$ and $\estNN' := \pptfrac{\estNN}{\estwV_0^\top \q_{NN}}$.
+For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{\estwV_0^\top \q_{NN}}$.
 
@@
 desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=\left(\tilde {\q}^\top ,\tilde {\mv z}^\top\right)^\top \in\R^{2n}$ as follows:
+control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=(\tilde {\q}^\top ,\tilde {\mv z}^\top)^\top \in\R^{2n}$ as follows:
 \begin{equation}
@@
 \end{equation}
-where $\mv \epsilon\in\R^2$ is bounded approximation error and 
+and 
 \begin{equation}
@@
     \begin{bmatrix}
-        \mm 0_{n\times n}\\\mm M_0^{-1}
+        \mm 0_{n\times n}\\\widehat{\mm M}^{-1}
     \end{bmatrix}.
@@
 
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in[0,1]$.
+\MSRY{
+    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be addressed to prevent excessively large control inputs and system instability.
+}
+For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in\{0,1\}$.
 The control problem can be reformulated into a constrained optimization problem as follows:
@@
         :=
-        {1\over 2}
+        \tfrac{1}{2}
         \mv \xi^\top \mm \Lambda \mv \xi
@@
             \max(\lambda_j,0) ,
-            \quad\quad\quad\quad\ \ \ \ \ 
-            \forall j\in\mathcal I,
         \label{eq. adaptation law L max}
@@
 \end{subequations}
-where $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
+where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
 \color{red}
@@
     \mm \Lambda
-    \pptfrac{\mv\xi}{\estwth}
+    \mv\xi
     .
@@
     \ddtt{\mm \eta} =
-    \mm A_\xi - \mm B_\xi 
+    \mm A_\xi \mm\eta
+    - \mm B_\xi 
     % (\partial \estNN/\partial {\estwth})
@@
 \color{black}
-Without loss of generality, assume that all the constraints. Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
+Without loss of generality, assume that all the constraints are violated. 
+Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
 %If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
@@
 \end{equation}
-where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1}$ and $\norm{\idealact}$ are bounded.
+where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
 The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
@@
 
-Define the Lyapunov function $V_1=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
+Define the Lyapunov function $V_1:=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
 Using a proposition $\estwV_1^\top \estact = \myvec(\estwV_1^\top \estact)=\myvec(\estact^\top \estwV_1) = (\mm I_{l_2}\otimes {\estact}^\top )\myvec(\estwV_1)=(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $V_1$ is
@@
         &
-        +{\estwth}_1^\top 
+        -{\estwth}_1^\top 
         \!
-        (\!
-            -{\mm \eta}_1^\top \mm \Lambda \xi-2\lambda_{\theta_1} {\estwth}_1 
-        \!)
+        (
+            {\mm \eta}_1^\top \mm \Lambda \xi+2\lambda_{\theta_1} {\estwth}_1 
+        )
         \\
@@
         (
-        -{\lambda_\text{min}(\mm Q)/ 2} +{\tfrac{\bar M}{2}}
+            -\tfrac{1}{2}\lambda_\text{min}(\mm Q)
+            +{\tfrac{\bar M}{2}}
         )
@@
         \norm{\tilde{\wth}_1}^2 
+        ,
         \end{aligned}
@@
 \end{equation}
-where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estNN^\top )+\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.
+where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top )-\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.
 
@@
 \begin{equation}
-    \Theta_\xi = 
+    \Theta_\xi := 
     \left\{
@@
         \tfrac{
-            \bar \Delta
+            2\bar \Delta
         }{
-            \lambda _\text{min}(\mm Q)-{\bar M}/{2}
+            \lambda _\text{min}(\mm Q)-{\bar M}
         } 
@@
 \begin{equation}
-    \Theta_{{\theta}_1} = 
-    \{ 
+    \Theta_{{\theta}_1} := 
+    \left\{ 
         {\estwth_1} 
@@
         \bar\theta_1
-    \}
+    \right\}
     .
@@
         \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \estwV_1^\top \estact'(\mm I_1\otimes {\q_{NN}}^\top )
+        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
         \\
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\estwV_1^\top \estact'(\mm I_1\otimes {\q_{NN}}^\top )$ is bounded.
-To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=(1/2\alpha){\estwth}_0^\top {\estwth}_0$ yields:
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )$ is bounded.
+To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=\tfrac{1}{2\alpha}{\estwth}_0^\top {\estwth}_0$ yields:
 \begin{equation}
@@
         \ddtt {V}_0 =& 
-        {\estwth}_0^\top (-{\mm \eta}_0\mm \Lambda\mv \xi -2\lambda_{\theta_0}{\estwth}_0)
+        -{\estwth}_0^\top (
+            {\mm \eta}_0\mm \Lambda\mv \xi 
+            +2\lambda_{\theta_0}{\estwth}_0
+        )
         \\
@@
 \begin{equation}
-    \Theta_{{\theta}_0} =
-    \{
+    \Theta_{{\theta}_0} :=
+    \left\{
         {\estwth}_0\mid\norm{\estwth_0}
@@
         }{
-            \lambda_{\theta_0}
+            2\lambda_{\theta_0}
         }
-    \}
+    \right\}
     .    
@@
 
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\mm M_0=I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
+All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
+\MSRY{
+    The validity of the selected number of nodes were demonstrated through experiments 
+}
 The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.

### 2025-03-22 manuscript.tex
fix regarding revision comments and new table style

@@
 \begin{equation}
-    \mm M\ddq + \mm V_m\dq + \mm F + \mm G + \mv\tau_d
+    \mm M\ddq + \mm V_m\dq+ \mm G + \mm F 
     =
     \mv\tau 
+    ,
     \label{eq. system dynamics 1}
@@
     \widehat{\mm M}\ddq+\widehat{\mm V_m}\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
+    ,
     \label{eq. system dynamics 2}
@@
     ) 
+    ,
     \label{eq. desired control}
@@
 To approximate the desired controller, an NN is utilized.
-\MSRY{
-    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
-}
+\color{red}
+    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2018aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
+\color{black}
 The NN with a single hidden layer is represented as 
@@
     \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
+    ,
 \end{equation}
@@
 \end{equation}
-For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{\estwV_0^\top \q_{NN}}$.
+For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{NN})}$.
 
@@
     \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
+    ,
 \end{equation}
@@
 
-\MSRY{
-    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be addressed to prevent excessively large control inputs and system instability.
-}
+\color{red}
+    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
+\color{black}
 For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in\{0,1\}$.
@@
     )
+    ,
 \end{equation}
@@
     \centering
-    \begin{tabular}{|c||c|c|c|c|}
+    \begin{tabular}{c c c c c }
     \hline
-    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+    \hline
     \hline 
@@
         \rho\norm{\tilde {\mv z}}{\estwth}
+        ,
     \right)
@@
 
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
+All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-\MSRY{
+\color{red}    
     The validity of the selected number of nodes were demonstrated through experiments 
-}
+\color{black}
 The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.
@@
     \centering
-    \begin{tabular}{|c||c|c|c|}
+    \begin{tabular}{c c c c }
     \hline
-     & \textbf{NAC-L2} & \textbf{NAC-eMod} & \textbf{NAC-CO} (proposed) 
+     & \textbf{NAC-L2}\!&\!\textbf{NAC-eMod}\!&\!\textbf{NAC-CO} (proposed) 
      \\
      \hline
-    Maximum         & $11.1753$e-3 & $0.5603$e-3 & $0.3439$e-3 \\
+    \hline 
+    Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
     \hline
@@
     % \hline
-    Median          & $0.5898$e-3 & $0.5519$e-3 & $0.3240$e-3 \\
+    Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
     \hline
@@
     % \hline
-    Minimum         & $0.5434$e-3 & $0.5434$e-3 & $0.3235$e-3 \\
+    Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
     \hline

### 2025-03-22 src/main_ECC_plotter.m

@@ -129,8 +129,8 @@ plot(t, e2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ..
     "DisplayName", "$\beta=0.45$"); hold on
 plot(t, e3, "color", c_list(3,:), "LineWidth", line_width, "LineStyle", "--", ...
     "DisplayName", "$\beta=1$"); hold on
-xlabel("$t\ (\rm s)$", "Interpreter", "latex")
-ylabel("$\Vert\xi\Vert\ (\rm rad)$", "Interpreter","latex")
+xlabel("Time / S", "Interpreter", "latex")
+ylabel("$\Vert\mathbf{\xi}\Vert$ / rad", "Interpreter","latex")
 set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
 grid on
 ylim([-.005, .03])
@@ -167,8 +167,8 @@ plot(t, e2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ..
     "DisplayName", "$\lambda=0.45$"); hold on
 plot(t, e3, "color", c_list(3,:), "LineWidth", line_width, "LineStyle", "--", ...
     "DisplayName", "$\lambda=1$"); hold on
-xlabel("$t\ (\rm s)$", "Interpreter", "latex")
-ylabel("$\Vert\xi\Vert\ (\rm rad)$", "Interpreter","latex")
+xlabel("Time / S", "Interpreter", "latex")
+ylabel("$\Vert\mathbf{\xi}\Vert$ / rad", "Interpreter","latex")
 set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
 grid on
 ylim([-.005, .03])
@@ -206,8 +206,8 @@ plot(t, e2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ..
     "DisplayName", "$\rho=0.45$"); hold on
 plot(t, e3, "color", c_list(3,:), "LineWidth", line_width, "LineStyle", "--", ...
     "DisplayName", "$\rho=1$"); hold on
-xlabel("$t\ (\rm s)$", "Interpreter", "latex")
-ylabel("$\Vert\xi\Vert\ (\rm rad)$", "Interpreter","latex")
+xlabel("Time / S", "Interpreter", "latex")
+ylabel("$\Vert\mathbf{\xi}\Vert$ / rad", "Interpreter","latex")
[…]

### 2025-03-22 manuscript.tex
use new macros

--- 2025-03-19 manuscript.tex
@@
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
-
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
-
-\IEEEoverridecommandlockouts                              % This command is only needed if 
-                                                          % you want to use the \thanks command
-
-\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-% \makeatletter
-% \let\NAT@parse\undefined
-% \makeatother
-
+\documentclass[lettersize,journal]{IEEEtran}
+% code
+
+\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}
+% \usepackage{balance}
 \input{dding_template/tex_packages/tex_packages_general.tex}
 \input{dding_template/tex_macros/tex_macros_general.tex}
-% MY PAKEAGES ========================================
+
+\newcommand*{\fe}{\mv{r}}
 
 \newcommand*{\q}{\mv{q}}
-\newcommand*{\dq}{\dot{\q}}
-\newcommand*{\ddq}{\ddot{\q}}
+\newcommand*{\dq}{\dot{\mv q}}
+\newcommand*{\ddq}{\ddot{\mv q}}
 \newcommand*{\qd}{\mv{q_d}}
-\newcommand*{\dqd}{\dot{\qd}}
-\newcommand*{\ddqd}{\ddot{\qd}}
-
-\title{\LARGE \bf
-Imposing a Weight Norm Constraint for Neuro–Adaptive Control
+\newcommand*{\dqd}{\dot{\mv q_d}}
+\newcommand*{\ddqd}{\ddot{\mv q_d}}
+
+\begin{document}
+\title{
+Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
+%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
 }
 
-\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
-\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
-\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
-\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
-        {\tt\small jiyun6606@gm.gist.ac.kr}}%
-}
-
-\begin{document}
+\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
+~Vol.~00, No.~0, Month~2024
+}%
+{How to Use the IEEEtran \LaTeX \ Templates}
 
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-
-In this paper, a neuro–adaptive controller with weight norm constraints is proposed for uncertain Euler‒Lagrange systems. 
-The boundedness of the weights in the neuro–adaptive controller design is important to prevent excessively large control inputs and system instability. 
-To ensure the boundedness of the weights, the weight norm constraints are imposed as inequality constraints in the weight adaptation. 
-The adaptation law is derived based on the constrained optimization method. 
-The stability of the proposed controller is analyzed in the sense of Lyapunov, ensuring the boundedness of the tracking error and weight estimation. 
-For the comparative study, two benchmark controllers and the proposed controller were evaluated through a numerical simulation of a two-link manipulator system and compared in terms of tracking performance and parameter dependency.
-The comparative study verified that the proposed controller has better tracking performance and lower parameter dependency.
-
+    This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints.
+A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints.
+The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state.
+The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights.
+Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  SECTION INTRODUCTION ===================================
+\begin{IEEEkeywords}
+Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
+\end{IEEEkeywords}
 
@@
     \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
-    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ denotes a vector.
-    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
-    %     \mm A
-    %     := 
-    %     [a_{ij}]
-    %     _{
-    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
-    %     }\allowbreak\in\R^{n\times m}
-    %     $ denotes a vector and a matrix.
+    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
+        \mm A
+        := 
+        [a_{ij}]
+        _{
+            i\in[1,\cdots,n],j\in[1,\cdots ,]
+        }\allowbreak\in\R^{n\times m}
+        $ denote a vector and a matrix.
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
@@
     \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
-    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
+    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
 \end{itemize}
 
+%  SECTION INTRODUCTION ===================================
 \section{Introduction}
 
-In various practical applications, Euler‒Lagrange systems generally have uncertainties due to their unknown and unmodeled dynamics.
-These uncertainties degrade the control performance index.
-Furthermore, if uncertainties dominate the system, they may lead to instability.
-By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{Tao:2003aa,Ioannou:2006aa}.
-Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.
-
-More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{Farrell:2006aa}.
-It uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
-This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
-Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa} and deep NN (DNN) \cite{Patil:2022aa}.
-The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.
-
-% The corresponding issue in the adaptive control is the parameter drift.
-% It refers to the weight divergence during the adaptation process, while the tracking error is bounded.
-
-% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs is that the outputs of NNs are not predictable.
-This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
-This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
-
-Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
-In \cite{Zhou:2023aa,Patil:2022aa}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
-However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
-Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
-In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
-The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
-However, they lack theoretical analysis regarding the optimality of the adapted weights.
-
-Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
-One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{Wu:2020aa,Lewkowycz:2020aa}.
-Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
-By regulating the magnitude of the weights, the stability of the adaptation process can be enhanced, and overfitting can be prevented.
-However, $L_2$-regularization also involves a trade-off between adaptation stability and the optimality of the weights.
-
-For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{Nocedal:2006aa} can be utilized.
-It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
-To the best of the authors’ knowledge, no prior work has utilized the constrained optimization method for the real-time weight adaptation of neuro–adaptive control satisfying weight boundedness.
-Therefore, the constrained optimization method could play a pivotal role in the neuro–adaptive control design addressing the weight boundedness.
-
-The main contributions of this study are as follows:
+\subsection{Background}
+
+\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
+These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
+In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
+These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
+To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.
+
+More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
+NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}.
+Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
+
+A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated. 
+Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
+
+However, two significant challenges persist in using NNs for adaptive control. 
+First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs. 
+When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. 
+Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{Esfandiari:2021aa}. 
+Failing to address these constraints can degrade control performance or even destabilize the system.
+
+Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
+he following section will provide a detailed review of the existing solutions to these challenges.
+
+\subsection{Literature Review}
+
+\subsubsection{Ensuring Weight Norm Boundedness}
+
+A common challenge in neuro-adaptive control is maintaining the boundedness of the NN weights to ensure stability. 
+In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly. 
+For example, in \cite{Zhou:2023aa,Griffis:2023aa,Patil:2022aa}, projection operators were used to constrain the weight norms to remain below predetermined constants. 
+However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values. 
+While this approach ensured that the NN remained stable, it did not necessarily result in optimal performance.
+
+In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{Ge:2002aa} and $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa}. 
+These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. 
+Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.
+
+\subsubsection{Satisfying Input Constraints}
+
+The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
+The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
+This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
+In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.
+
+To address input saturation, many studies introduced auxiliary systems. 
+These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
+For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
+This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.
+
+Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}.
+In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
+However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+
+\subsubsection{Limitations of Existing Approaches and Potential of Constrained Optimization}
+
+Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations. 
+Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
+Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.
+
+To overcome these limitations, constrained optimization offers a promising approach. 
+By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (\eg tracking error) subject to both weight norm and input constraints.
+Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.
+
+In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{Evens:2021aa} and the Alternating Direction Method of Multipliers (ADMM) \cite{Wang:2019aa,Taylor:2016aa}, have been used to train NNs offline.
+These methods impose constraints to address issues like gradient vanishing in backpropagation. 
+However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation. 
+This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.
+
+\subsection{Contributions}
+
+The main contributions of this study are listed as follows:
 \begin{itemize}
-    \item The neuro–adaptive control problem is reformulated into a constrained optimization problem by treating the satisfaction of the weight boundedness as inequality constraints.
-    \item The adaptation law is derived based on the constrained optimization method to minimize the objective function while satisfying the weight norm constraints.
-    \item The stability of the adaptation laws is analyzed via Lyapunov stability analysis, which ensures the boundedness of the tracking error and weight estimation.
+    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
+    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
+The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
+    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
+    %, enabling more precise real-time adaptation.
 \end{itemize}
 
-The remainder of this paper is organized as follows:
-Section \ref{sec: Problem Formulation} presents the target-constrained system and control objective.
-Section \ref{sec:ctrl design} introduces the proposed controller and the adaptation law. 
-Section \ref{sec:stability} examines the stability of the proposed controller.
-A comparative study of the three selected controllers, including the proposed controller through numerical simulation, is reported in Section \ref{sec:sim}.
-Finally, Section \ref{sec:conclusion} concludes the paper by presenting future work.
+\subsection{Organization}
+
+The remainder of this paper is organized as follows. 
+Section \ref{sec:Problem Formulation} presents the target system and control objective.
+Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
+In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
+Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
+Section \ref{sec:stability} analyzes the stability of the proposed controller.
+A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
+Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
+% The appendices provide the proof of the lemma used in the stability analysis.
 
 %  SECTION PROBLEM FORMULATION ============================
-\section{Problem Formulation}\label{sec: Problem Formulation}
+\section{Problem Formulation}\label{sec:Problem Formulation}
 
@@
 
-Consider an uncertain Euler‒Lagrange system modeled as
-\begin{equation}
-    \mm M\ddq + \mm V_m\dq + \mm F + \mm G + \mv\tau_d
-    =
-    \mv\tau 
-    \label{eq. system dynamics 1}
-\end{equation}
-where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\mm M_0>0,\mm V_{m0}$ and $\mm G_0$, \eqref{eq. system dynamics 1} can be represented as 
-\begin{equation}
-    \mm M_0\ddq+\mm V_{m0}\dq+\mm G_0 = \mv \tau + \mv f(\q,\dq,\ddq)
-    \label{eq. system dynamics 2}
-\end{equation}
-where $\mv f(\q,\dq,\ddq) := -(\mm M-\mm M_0)\ddq-(\mm V_m-\mm V_{m0})\dq -(\mm G-\mm G_0) -\mm F$ denotes the residual unknown term.
-
-Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd(t):\R\to \R^n$ under the unknown terms $\mv f$.
+Consider an uncertain Euler-Lagrange system modeled as
+\begin{equation}
+    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
+    =
+    \mysat(\mv\tau)
+    \label{eq:sys1}
+\end{equation}
+where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
+The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
+\begin{equation}
+    \mysat(\mv\tau)
+    :=
+    \begin{cases}
+        \mv\tau, 
+        & 
+        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
+        \\
+        \bar\tau
+        \cdot
+        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
+        & 
+        \text{otherwise},
+    \end{cases}
+    \label{eq:sat}
+\end{equation}
+where $\bar\tau$ denotes the maximum norm of control input.
+To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
+Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+
+The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
+We introduce the following properties:
+\begin{prop} \cite{Lewis:1998aa}
+    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
+    \label{prop:M}
+\end{prop}
+
+\begin{prop} \cite{Lewis:1998aa}
+    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
+    \label{prop:skew}
+\end{prop}
+
+\begin{prop}
+    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
+    \label{prop:dis_bound}
+\end{prop}
+
+In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
+Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
+\begin{assum}
+    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
+    \label{assum:feasible}
+\end{assum}
 
@@
 
-In this section, the neuro–adaptive controller is developed.
-Section \ref{sec:ctrl dev} presents the details of the neuro–adaptive controller and the NN model.
-The adaptation law based on the constrained optimization method is derived in Section \ref{sec:adap_laws} by formulating a constrained optimization problem.
-
-\subsection{Neuro–adaptive Control Design} \label{sec:ctrl dev}
-
-The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
-The desired stabilizing controller can be designed as follows:
-\begin{equation}
-    \mv \tau^* = 
-    -\mm M_0\cdot ({k_z}\tilde {\mv z})
-    + 
-        ( 
-            -\mm M_0\tilde {\q}+\mm V_{m0}{\mv z}+\mm G_0-\mv f+\mm M_0 \dot {\mv z}^*
+The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
+Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model.
+The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
+    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
+    \label{fig:ctrl:diagram}
+\end{figure*}
+
+\subsection{Neuro-Adaptive Controller Design}\label{sec:sub:NAC}
+
+First, let us define the filtered tracking error $\fe\in\R^n$ as 
+\begin{equation}
+    \fe := \dot{\mv e}-\mm\Lambda \mv e
+    ,
+    \label{eq:err:filtered}
+\end{equation}
+where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
+Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
+
+Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
+\begin{equation}
+    \mm M \dot\fe
+    =
+    -\mm V_m \fe
+    -\mm K \fe
+    + \mv f
+    -\mv \tau_d + \mysat(\mv\tau)
+    ,
+    \label{eq:sys:filtered}
+\end{equation}
+where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
+    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
+    =
+    \mm K \fe
+    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
+    +
+    \mm V_m(-\dqd+\mm\Lambda\mv e)
+    -
+    \mm F
+    -
+    \mm G
+    \in\R^n
+$ denotes the lumped system uncertainty.
+
+Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
+Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
+\begin{equation}
+    \begin{aligned}
+        \ddtt{V}_1
+        =&
+        \fe^\top \mm M (
+            -\mm V_m \fe -\mm K \fe + \mv f
+            -\mv \tau_d + \mysat(\mv\tau)
         )
-    \label{eq. desired control}
-\end{equation}
-where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
-Note that the desired controller cannot be realized because of $\mv f$.
-
-To approximate the desired controller, an NN is utilized.
-The NN with a single hidden layer is represented as 
-\begin{equation}
-    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
-\end{equation}
-where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
-The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
-For further simplicity, let $\wth:=\left(\wth_1^\top ,\wth_0^\top \right)^\top \in\R^{\Xi}$ denote the total weight vector, where $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights.
-$\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
-
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
-The ideal weight vector $\wth^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\epsilon$ can be approximated as follows:
-\begin{equation}
-    \mv \tau := -\NN({\q_{NN}};\estwth)
+        \\
+        &
+        +
+        \tfrac{1}{2}
+        \fe^\top \dot{\mm M}\fe
+        \\
+        =&
+        -
+        \fe^\top \mm K \fe 
+        +
+        \fe^\top (
+            \mv f+\mysat(\mv\tau)
+            -\mv \tau_d
+        )
+        \\
+        &
+        +
+        \tfrac{1}{2}
+        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
+        \\
+        \le&
+        -\lambda_\text{min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mv f+\mysat(\mv \tau))
+        \\
+        \le&
+        -\lambda_\text{min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
+        ,
+    \end{aligned}
+    \label{eq:lya1:dot1}
+\end{equation}
+where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
+However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.
+
+To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
+Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
+Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
+In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
+
+In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
+\begin{align}
+    \mv\tau^*=& \idealNN+\mv\epsilon,
+    \label{eq:control:ideal}
+\end{align}
+which is estimated online by
+\begin{align}
+    \mv\tau =& \estNN,
+    \label{eq:control:est}
+\end{align}
+where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
+
+Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $\mathcal V_1$ can be rewritten as
+\begin{equation}
+    \dot{\mathcal V}_1
+    \le 
+    -\lambda_\text{min}(\mm K)\norm{\fe}^2
+    +
+    \bar\tau_d\norm{\fe}
+    +
+    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
     .
-    \label{eq. control law}
-\end{equation}
-For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\NN^* :=\NN({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estNN :=\NN(\estwV_0^{\top}{\q_{NN}})$ and $\estNN' := \pptfrac{\estNN}{\estwV_0^\top \q_{NN}}$.
-
-Using \eqref{eq.
-system dynamics 2}, \eqref{eq.
-desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=\left(\tilde {\q}^\top ,\tilde {\mv z}^\top\right)^\top \in\R^{2n}$ as follows:
-\begin{equation}
-    \dot{\mv \xi} 
-    = 
-    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
-\end{equation}
-where $\mv \epsilon\in\R^2$ is bounded approximation error and 
-\begin{equation}
-    \mm A_\xi := 
+    \label{eq:lya1:dot2}
+\end{equation}
+Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).
+
+\subsection{Deep Neural Network (DNN) Model}\label{sec:sub:NN definition}
+
+The DNN architecture $\NN_k = \NN(\q_{NN};\wth)$ can be recursively represented as follows:
+\begin{equation}
+    \NN_i :=
+    \begin{cases}
+        \wV_i^\top \NN_i(\NN_{i-1}), 
+        &
+        i\in[1,\dots,k],
+        \\
+        \wV_0^\top \q_{NN},
+        &
+        i=0
+        ,
+    \end{cases}
+    \label{eq:DNN:architecture}
+\end{equation}
+where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
+The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).
+
+One of the widely used activation functions for large DNNs is from the ReLU family \cite{Maas:2013aa}, which effectively avoids the gradient vanishing problem during error backpropagation. 
+However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
+These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\ddtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}< 1$.
+
+For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
+\begin{equation}
+    \wth := 
     \begin{bmatrix}
-        -{k_q} \mm I_{n} &\mm I_{n}
-        \\
-        -\mm I_{n}& -{k_z} \mm I_{n}
+        \wth_k\\
+        \wth_{k-1}\\
+        \vdots\\
+        \wth_0
     \end{bmatrix}
-    ,\ 
-    \mm B_\xi := 
+    =
     \begin{bmatrix}
-        \mm 0_{n\times n}\\\mm M_0^{-1}
-    \end{bmatrix}.
-\end{equation}
-
-\subsection{Adaptation Law Derivation}\label{sec:adap_laws}
-
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in[0,1]$.
-The control problem can be reformulated into a constrained optimization problem as follows:
+        \myvec(\wV_k)\\
+        \myvec(\wV_{k-1})\\
+        \vdots\\
+        \myvec(\wV_0)
+    \end{bmatrix},
+\end{equation}
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
+\begin{equation}
+    \pptfrac{\NN}{\wth}=
+    \begin{bmatrix}
+        \pptfrac{\NN}{\wth_k}&
+        \pptfrac{\NN}{\wth_{k-1}}&
+    \cdots &
+        \pptfrac{\NN}{\wth_0}
+    \end{bmatrix}
+    \in\R^{n \times \Xi}
+    \label{eq. nabla phi}
+\end{equation}
+where
+\begin{equation}
+    \pptfrac{\NN}{\wth_i} = 
+    \begin{cases}
+        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
+        &
+        i=k 
+        \\
+        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
+        & 
+        i=k-1
+        \\
+        &
+        \vdots 
+        \\
+        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
+        &
+        i = 0
+    \end{cases},
+    \label{eq:NN:grad}
+\end{equation}
+where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
+
+In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
+Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and $\act^{*'}_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i:=\act_i(\hat\NN_{i-1})$ and $\hat\act_i':= \pptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
+
+%  SECTION ADAPTATION LAW DERIVATION =======================
+\section{Weight Adaptation Laws}\label{sec:adap_laws}
+
+% \subsection{Adaptation Law using Lagrangian Function}
+\subsection{Weight Optimizer Design}\label{sec:sub:weight optimizer}
+
+The control objective can be represented as follows:
 \begin{equation}
     \begin{matrix}
-        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
-        :=
-        {1\over 2}
-        \mv \xi^\top \mm \Lambda \mv \xi
+        \min_{\estwth} \ J(\fe;\estwth):= 
+        \tfrac{1}{2} \fe^\top  \mm W\fe
         \\ \\
         \begin{aligned}
-        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
-        = 
-        \{\theta_0,\theta_1\}
-        ,
+        \text{s.t. }&c_{j}(\estwth) 
+        \le0, \quad j\in\mathcal{I},
         \end{aligned}
     \end{matrix}
-\end{equation}
-where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
-In this optimization problem, $\mv \xi$ is considered a predefined parameter.
-The corresponding Lagrangian function is defined as
+    \label{eq:opt:problem1}
+\end{equation}
+where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top  \mm W\fe$ is the objective function, and $\mm W\in\R^{n\times n}$ is a symmetric positive weighting matrix.
+Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
+Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
 \begin{equation}
     L(
-        \mv \xi,
-        {\estwth},
-        [\lambda_j]_{j\in\mathcal I}
+        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
     ) 
     := 
-    J(\mv \xi;{\estwth})
-    +
-    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
-    .
-\end{equation}
-% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
+    J(\fe;\estwth) 
+    + 
+    \sum_{j\in\mathcal I}
+    \lambda_{j}
+    c_{j}(\estwth)
+    \label{eq:lagrangian}
+\end{equation}
+where $\lambda_j$ denotes the Lagrange multiplier for each constraint.
+
+The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
 \begin{subequations}
     \begin{align}
-            \ddtt {{\estwth}}
-            &
+            \ddtt{\estwth}
+            &
+            =
+            -\alpha \pptfrac{L}{\estwth}
             =
             -\alpha 
-            \pptfrac{L}{{\estwth}}
-            =-\alpha 
             \left(
-                \pptfrac{J}{{\estwth}}
+                \pptfrac{J}{\estwth}
                 +
@@
             \right),
-        \label{eq. adaptation law th}
+        \label{eq:adap:th}
             \\
@@
             = 
-            \beta_j
-            \pptfrac{L}{\lambda_j} 
+            \beta_j\pptfrac{L}{\lambda_j} 
             = 
             \beta_j c_j ,
-            \quad\quad\quad\quad      \      
-            \forall j\in\mathcal I,
-        \label{eq. adaptation law L}
-            \\
+            \quad \forall j\in\mathcal I,
+        \label{eq:adap:lbd}
+            \\
+            \lambda_j & = \max(\lambda_j,0) ,
+        \label{eq:adap:lbd:max}
+    \end{align}
+    \label{eq:adaptation law}
+\end{subequations}
+where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
+When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation.
+Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \estwth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
+In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
+These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
+% The KKT condition is satisfied, when $\estwth$ converges to $\idealwth$, since $\partial L/\partial \estwth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).
+
+\subsection{Approximation of the Gradient of Objective Function}
+
+The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\mv\tau}$ (\ie 
+$
+    \pptfrac{J}{\mv \tau}
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\mv \tau}{\estwth}))^\top \fe
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\estNN}{\estwth}))^\top \fe
+$). 
+Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
+The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
+\begin{equation}
+    \ddtt (
+        \pptfrac{\fe}{\mv\tau}
+    )
+    =
+    \pptfrac{}{
+        \mv\tau
+    }
+    \left[
+        \mm M^{-1}(
+            -\mm V_m \fe
+            -\mm K \fe
+            + \mv f
+            -\mv \tau_d + \mysat(\mv\tau)
+        )
+    \right]
+    .
+\end{equation}
+However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\mm M,\mm V_m, \mm F$ and $ \mm G$).
+Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
+
+In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\mv\tau}$ as $
+    \pptfrac{\fe}{\mv\tau}
+    \approx
+    [
+        \mathrm{sign}(\pptfrac{r_i}{\tau_j})
+    ]_{i,j\in[1,\cdots,m]}
+$ using the sign of each entry (\ie control direction).
+However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\mm M^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
+Therefore, we propose to approximate $\pptfrac{\fe}{\mv\tau}$ as $\pptfrac{\fe}{\mv\tau}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
+\begin{equation}
+    \ddtt{\estwth}
+    \approx
+    -\alpha 
+    \left(
+        \pptfrac{\estNN}{\estwth}^\top
+        \fe
+        +
+        \textstyle\sum_{j\in\mathcal{I}}
         \lambda_j 
-            & 
-            = 
-            \max(\lambda_j,0) ,
-            \quad\quad\quad\quad\ \ \ \ \ 
-            \forall j\in\mathcal I,
-        \label{eq. adaptation law L max}
-    \end{align}
-    \label{eq. adaptation laws}
-\end{subequations}
-where $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
-\color{red}
-% The Eq.~\eqref{eq.
-adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
-\color{black}
-
-Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
-\begin{equation}
-    \pptfrac{J}{\estwth}
-    =
-    \pptfrac{\mv\xi}{\estwth}^\top 
-    \mm \Lambda
-    \pptfrac{\mv\xi}{\estwth}
+        \pptfrac{c_j}{\estwth}
+    \right)
     .
-\end{equation}
-The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
-Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
-\begin{equation}
-    \ddtt{\mm \eta} =
-    \mm A_\xi - \mm B_\xi 
-    % (\partial \estNN/\partial {\estwth})
-    \pptfrac{\estNN}{\estwth}
-    ,
-    \label{eq. sen eq}
-\end{equation}
-where ${\mm \eta}:= \pptfrac{\mv\xi}{\estwth}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
-The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
-By decomposing for each layer, the dynamics of ${\mm \eta}_i:= \pptfrac{\mv\xi}{\estwth}_i\in\R^{2n\times \Xi_i}$ can be represented as
-\begin{equation}
+    \label{eq:adap:th:approx}
+\end{equation}
+
+%% ALGORITHM PART; Now omitted!
+% The proposed controller is implemented using Algorithm \ref{alg: alg1}.
+For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
+If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
+
+% \begin{algorithm}[!t]
+%     \caption{Weight Optimizer Implementation.}\label{alg: alg1}
+%     \begin{algorithmic}[1]
+%         \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+%         \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%         \REQUIRE $\xi$, $\estwth$, $\lambda_j$, $\eta$
+%         \ENSURE  $\estwth$, $\lambda_j$, $\eta$
+%         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
+%         \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
+%         \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
+%         \STATE Determine update directions $\dot{\estwth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
+%         \STATE Update weight vector $\estwth\leftarrow \estwth+\dot{\estwth}\cdot T_s$;
+%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
+%         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
+%         \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
+%         \STATE \textbf{RETURN};
+%     \end{algorithmic}
+%     \label{alg1}
+% \end{algorithm}
+
+\subsection{Constraint Candidates}\label{sec:sub:cstr}
+
+This section introduces conditions which imposed constraints must satisfy and the weight constraints.
+The potential control input constraints are presented in Appendix \ref{sec:appen:cstr}.
+First, we introduce the following assumptions for the constraints.
+
+\begin{assum}
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
+    \label{assum:convex}
+\end{assum}
+
+\begin{assum}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
+    \label{assum:LICQ}
+\end{assum}
+
+\begin{remark}
+    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in practice including the origin.
+    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
+    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
+\end{remark}
+
+The following Lemma is introduced for the stability analysis.
+\begin{lem}
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    \label{lem:convex:angle}
+\end{lem}
+
+\begin{proof}
+
+Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
+\begin{equation}\label{eq:linear:map}
     \begin{aligned}
-        \ddtt{\mm \eta} 
-        \!=\!&
-        \begin{bmatrix}
-            {\mm \eta}_1&{\mm \eta}_0
-        \end{bmatrix}'
-        \\
-        \!=\!&
-        \mm A_\xi
-        % \begin{bmatrix}
-        [
-            {\mm \eta}_1
-            \ \ 
-            {\mm \eta}_0
-        ]
-        % \end{bmatrix}
-        \!-\!
-        \mm B_\xi
-        % \begin{bmatrix}
-        [
-            (\mm I_{l_2}\!\otimes\!\estact^\top )
-            \ \ 
-            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
-        ]
-        % \end{bmatrix}
+    \mv\tau 
+    = 
+    &
+    \estNN 
+    % = 
+    % \myvec(\estNN)
+    =
+    \myvec(
+        \estwV_k^\top \estact_k
+    ) 
+    = 
+    (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top
+    \myvec(\estwV_k)
+    \\
+    = &
+    \underbrace{
+        (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top}_{:=\mm T(\estact_k)}
+    \estwth_k 
+    =
+    \mm T(\estact_k) \estwth_k.
+    \end{aligned}
+\end{equation}
+Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+
+\end{proof}
+
+The weight constraints are essential to prevent the weights from diverging during the adaptation process.
+The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+\begin{equation}
+    c_{\theta_i}
+    =
+    \tfrac{1}{2}
+    (
+        \Vert \estwth_i\Vert^2 
+        -
+        \bar\theta_i^2 
+    )    
+    \le 0
+    \label{eq:cstr:weight_ball}
+\end{equation}
+with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
+The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
+\begin{equation}
+    \pptfrac{c_{\theta_i}}{\estwth_j} 
+    =
+    \begin{cases}
+        \estwth_i,
+        &
+        \text{if } i=j
+        \\
+        0,
+        &
+        \text{if } i\ne j
+        .
+    \end{cases} 
+    \label{eq:cstr:weight_ball:grad}
+\end{equation}
+Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.
+
+%  SECTION STABILITY ANALYSIS ==============================
+\section{Stability Analysis}\label{sec:stability}
+
+Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+The following lemma is introduced for the stability analysis.
+
+\begin{lem} 
+    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i,\ \forall i\in[k,\cdots, i+1]$, remain bounded.
+    \label{lem:cstr:grad:bound}
+\end{lem}
+
+\begin{proof}
+
+The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
+\begin{equation}
+    \pptfrac{c_j}{\estwth_i} 
+    = 
+    \pptfrac{c_j}{\mv\tau} 
+    \pptfrac{\mv\tau}{\estNN} 
+    \pptfrac{\estNN}{\estwth_i}
+\end{equation}
+where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
+From the linear mapping in \eqref{eq:linear:map}, $\mv\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
+By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
+The convex function has a bounded derivative with respect to $\mv\tau$, since $\mv\tau$ is a bounded variable (\ie $\pptfrac{c_j}{\mv\tau}$ is bounded). 
+Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
+This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
+Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+
+\end{proof}
+
+The following theorem shows that $\estwth$ and $\fe$ are bounded.
+
+\begin{theorem}
+    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$.
+    This holds with the weight norm constraint \eqref{eq:cstr:weight_ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
+\end{theorem}
+
+\begin{proof}
+
+The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
+Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
+This assumption is reasonable, since even if the constraint is inactive 
+\MSRY{Add the reason why it is reasonable.}
+We consider two cases: (C$_1$) control input constraints are active, and (C$_2$) control input constraints are inactive.
+Using the fact that amplitude of the control input is only depends on $\estwth_k$ (\ie see \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$), the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
+
+\subsection*{Case (C$_1$): Control input constraints are active.}
+
+As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
+\begin{equation}
+    \Theta_{\fe}^{c_1} 
+    = 
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\text{min}}(\mm K)}
+    \right\}
+    .
+    \label{eq:invariant:c1:fe}
+\end{equation}
+
+To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
+Taking the time derivative of $V_2$ yields:
+\begin{equation}
+    \begin{aligned}
+        \ddtt  V_2 
+        =& 
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \textstyle\sum_{j\in\mathcal{I}}
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        =&
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        \\
+        &
+            +
+            \textstyle\sum_{
+                j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+            }
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        \underbrace{
+            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
+        }_{:=c_1\in\R_{>0}}
+        \norm{\fe}
+        \norm{\estwth_k}
+        \\
+        &
+        -
+        \underbrace{
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j 
+        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
+        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        c_1     
+        \norm{\fe}
+        \norm{\estwth_k}
         .
     \end{aligned}
-\end{equation}
-The calculation of $\pptfrac{\estNN}{\estwth}$ is introduced in \cite{Patil:2022aa}.
-In conclusion, the gradient of the objective with respect to the weights can be obtained as $\pptfrac{J}{\estwth} = {\mm \eta}^\top\mm \Lambda\mv\xi$ by simulating the sensitivity equation \eqref{eq.
-sen eq}.
-
-On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
-\begin{equation}
-    \pptfrac{c_{\theta_0}}{{\estwth}}
-    = 
-    \begin{bmatrix}
-        \mm 0_{\Xi_1\times 1} \\
-        2{\estwth}_0 
-    \end{bmatrix}
-    ,\quad
-    \pptfrac{c_{\theta_1}}{{\estwth}}    
-    = 
-    \begin{bmatrix}
-        2{\estwth}_1 \\
-        \mm 0_{\Xi_0\times 1}
-    \end{bmatrix}
+    \label{eq:lya2:dot}
+\end{equation}
+According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
+\begin{equation}
+    \Theta_{\theta_k}^{c_1} 
+    = 
+    \left\{ 
+        \estwth_k \in \R^{\Xi_{k}} 
+        \mid 
+        \norm{\estwth_k} 
+        \le 
+        \tfrac{
+            c_1(2\bar\tau+\bar\tau_d)
+        }{
+            \lambda_{\theta_k}\lambda_\text{min}(\mm K)
+        }
+    \right\}
     .
-\end{equation}
-
-%  SECTION STABILITY ANALYSIS ==============================
-\section{Stability Analysis}\label{sec:stability}
-
-The following theorem proves the boundedness of the tracking error and the weight estimation of the weights.
-
-\begin{theorem}
-For the dynamical system in \eqref{eq.
-system dynamics 1}, the proposed controller \eqref{eq.
-control law} and the adaptation law \eqref{eq.
-adaptation laws} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\estwth}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
-ctrl stable condition}.
-\end{theorem}
-
-\begin{proof}
-The boundedness is proven from the last layer to the first layer.
-
-\subsection*{Step 1: Boundedness of ${\estwth}_1,{\mm \eta}_1,\mv \xi$}
-
-% For convenience, assume that all the constraints are in the active set without loss of generality.
-% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
-\color{black}
-Without loss of generality, assume that all the constraints. Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
-%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
-\color{black}
-
-The dynamics of $\mv \xi$ can be represented as
-\begin{equation}    
-    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
+    \label{eq:invariant:c1:wth}
+\end{equation}
+
+The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
+For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{c_1}$ is squeezed to a point.
+The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
+It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
+This drives $\estwth_k$ to the origin until the constraint is satisfied (\ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space).
+
+Therefore, the boundedness of $\estwth$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{c_1}$ and $\Theta_{\theta_k}^{c_1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
+
+\subsection*{Case (C$_2$): Control input constraints are inactive.}
+
+Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
+Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
+\begin{equation}
+    \begin{aligned}
+        \ddtt V_3
+        =&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\bar\tau_d\norm{\fe}
+        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
+        \\
+        &
+        -\estwth_k^\top (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        )
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(
+            \bar\tau_d+\norm{
+                \underbrace{
+                    \idealNN+\mv\epsilon
+                }_{=\mv\tau^*}
+            }
+        )
+        \norm{\fe}
+        \\
+        &
+        -\estNN^\top\fe 
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(\bar\tau_d+\bar\tau)
+        \norm{\fe}
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        .
+    \end{aligned}
+    \label{eq:lya3:dot}
+\end{equation}
+Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
+\begin{equation}
+    \Theta_{\fe}^{c_2}
+    =
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{
+            \bar\tau_d+\bar\tau
+        }{
+            \lambda_{\text{min}}(\mm K)
+        }
+    \right\}
+    .
+\end{equation}
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
+
+\hfill
+
+The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
+The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
+\begin{equation}
+    \ddtt \estwth_i 
+    =
+    -\alpha
     (
-        -\estwV_1^\top \estact+\mv w(t)
-    )
-\end{equation}
-where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1}$ and $\norm{\idealact}$ are bounded.
-The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
-\begin{equation}
-    \begin{aligned}
-        \ddtt{\mm \eta}_1 =
-        & 
-        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
-        ,
-        \\
-        \ddtt{{\estwth}}_1 =
-        & -\alpha 
-        (
-            {\mm \eta}_1^\top 
-            \mm \Lambda
-            \mv\xi
-            +
-            2\lambda_{\theta_1} {\estwth}_1
+        \pptfrac{\estNN}{\estwth_i}^\top
+        \fe
+        +
+        \lambda_{\theta_i}\estwth_i
+        +
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j
+        \pptfrac{c_j}{\estwth_i}
     )
     .
-    \end{aligned} 
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.
-
-Define the Lyapunov function $V_1=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
-Using a proposition $\estwV_1^\top \estact = \myvec(\estwV_1^\top \estact)=\myvec(\estact^\top \estwV_1) = (\mm I_{l_2}\otimes {\estact}^\top )\myvec(\estwV_1)=(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $V_1$ is
-\begin{equation}
-    \begin{aligned}
-        \ddtt \! {V}_1 
-        \!=\!& 
-        \tfrac{1}{2}
-        \mv \xi^\top 
-            (
-                \mm A_\xi^\top \mm P+\mm P\mm A_\xi
-            )
-        \mv \xi
-        \!+\!
-        \mv \xi^\top \mm P (
-            \!-\!\mm B_\xi\estwV_1^\top \estact +\mm B_\xi \mv w(t) 
-        )\\
-        &
-        +{\estwth}_1^\top 
-        \!
-        (\!
-            -{\mm \eta}_1^\top \mm \Lambda \xi-2\lambda_{\theta_1} {\estwth}_1 
-        \!)
-        \\
-        =& 
-        -\tfrac{1}{2}
-        \mv \xi^\top \mm Q\mv \xi 
-        -
-        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1 
-        +\mv \xi^\top \mv \Delta
-        \\
-        &
-        -{\estwth}_1^\top {\mm \eta}_1^\top \mm \Lambda\mv \xi
-        -2\lambda_{\theta_1} {\estwth}_1^\top {\estwth}_1
-        \\
-        \le&
-        -
-        \tfrac{1}{2}
-        \lambda_\text{min}(\mm Q)\norm{\mv \xi} ^2
-        +\bar\Delta \norm{\mv \xi}
-        +\bar M\norm{\mv \xi} \norm{{\estwth}_1}
-        \\
-        &
-        -2\lambda_{\theta_1}
-        \norm{{\estwth}_1}^2
-        \\
-        \le& 
-        (
-        -{\lambda_\text{min}(\mm Q)/ 2} +{\tfrac{\bar M}{2}}
-        )
-        \norm{\mv \xi}^2 +\bar\Delta \norm{\mv \xi}
-        \\
-        &+ 
-        (
-        -2\lambda_{\theta_1} 
-        +\tfrac{\bar M}{2}
-        )
-        \norm{\tilde{\wth}_1}^2 
-        \end{aligned}
-        \label{eq. lya 1}
-\end{equation}
-where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estNN^\top )+\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.
-
-By defining $\mm P=\mm I_n$, the eigenvalues of $\mm Q=-\mm A_\xi^\top -\mm A_\xi$ are $2k_q$ and $2k_z$, since $\mm A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
-According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
-\begin{equation}
-    \text{min}(k_q,k_z)>\tfrac{\bar M}{2}
-    ,
-    \label{eq. ctrl stable condition}
-\end{equation}
-and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\tfrac{\bar M}{2}$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
-\begin{equation}
-    \Theta_\xi = 
-    \left\{
-        \mv\xi\mid
-        \norm{\mv\xi}
-        \le  
-        \tfrac{
-            \bar \Delta
-        }{
-            \lambda _\text{min}(\mm Q)-{\bar M}/{2}
-        } 
-    \right\}
-    ,
-\end{equation}
-and the weight estimation $\estwth_1$ is bounded in
-\begin{equation}
-    \Theta_{{\theta}_1} = 
-    \{ 
-        {\estwth_1} 
-        \mid
-        \norm{\estwth_1}
-        \le  
-        \bar\theta_1
-    \}
-    .
-\end{equation}
-The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\estwth}_1$ approaches the compact set $\Theta_{{\theta}_1}$, satisfying the constraint $c_{\theta_1}$.
-
-\subsection*{Step 2: Boundedness of ${\estwth}_0,{\mm \eta}_0$}
-
-The dynamics of ${\mm \eta}_0$ and ${\estwth}_0$ are represented as
-\begin{equation}
-    \begin{aligned}     
-        \ddtt{\mm \eta}_0 =& 
-        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \estwV_1^\top \estact'(\mm I_1\otimes {\q_{NN}}^\top )
-        \\
-        \ddtt{{\estwth}}_0
-        =&
-        -\alpha 
-        (
-            {\mm \eta}_0^\top \mm \Lambda\mv \xi+2\lambda_{\theta_0} {\estwth}_0
-        )
-        .
-    \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\estwV_1^\top \estact'(\mm I_1\otimes {\q_{NN}}^\top )$ is bounded.
-To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=(1/2\alpha){\estwth}_0^\top {\estwth}_0$ yields:
-\begin{equation}
-    \begin{aligned}
-        \ddtt {V}_0 =& 
-        {\estwth}_0^\top (-{\mm \eta}_0\mm \Lambda\mv \xi -2\lambda_{\theta_0}{\estwth}_0)
-        \\
-        \le &
-        \norm{{\estwth}_0} \norm{{\mm \eta}_0\mm \Lambda\mv \xi} 
-        -
-        2\lambda_{\theta_0} {\estwth}_0^\top {\estwth}_0
-        ,
-        \\
-        \le &
-        -2\lambda_{\theta_0} 
-        \norm{{\estwth}_0}^2 
-        + 
-        \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
-        \norm{{\estwth}_0}
-        .
-    \end{aligned}
-\end{equation}
-Then, the invariance set can be represented as 
-\begin{equation}
-    \Theta_{{\theta}_0} =
-    \{
-        {\estwth}_0\mid\norm{\estwth_0}
-        \le
-        \tfrac{
-            \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
-        }{
-            \lambda_{\theta_0}
-        }
-    \}
-    .    
-\end{equation}
-If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
-Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.
+\end{equation}
+Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
+
+\hfill
+
+Finally, the filtered error $\fe$ and the estimated weights $\estwth$ are bounded and the imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
 
@@
 
-% \begin{remark}
-%     In the constrained optimization method, the corresponding method of $L_2$-regularization method is the quadratic penalty method, which replaces the constrained optimization problem into an unconstrained optimization problem by adding the penalty term $(1/2\mu)\sum_{r\in\mathcal I} c_r^2$ in the objective function.
-%     The penalty parameter $\mu\in\R_{>0}$ usually decreases over implementation for the convergence of the optimization process.
-%     However, the decreased penalty term $\mu$ may alter the original objective function as the penalty term dominates the objective function.
-%     Therefore, $L_2$-regularization inherently has the analogous drawback of the quadratic penalty method in the selection of the regularization coefficient $\lambda$.
-% \end{remark}
-
-% \subsection{Orthogoanl-regularization}
-
 %  SECTION SIMULATION ======================================
-\section{Simulations}\label{sec:sim}
+\section{Simulation}\label{sec:sim}
 
@@
 
+The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
+The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$, and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+%This model contains terms of gravity and friction in its mechanical system.
+%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
+%and can be considered as the disturbance of the system.
+The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for ${q}=[q_1,q_2]^\top$ was defined as
+\begin{equation}
+    {q_d}(t) = 
+    \begin{bmatrix}
+        {q_d}_1\\{q_d}_2
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        +\cos(0.5\pi t) + 1 \\
+        -\cos(0.5\pi t) - 1 
+    \end{bmatrix}.
+\end{equation}
+%\color{red}
+%Considering the power limitation of the power source for the actuators [], 
+The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
+\begin{equation}
+    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
+    \label{eq. h func}
+\end{equation}
+with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
+The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.
+
+In addition to this physically imposed control input saturation, the input norm constraint \eqref{eq.
+cstr input ball} was imposed to ensure that the control input $\tau$ stays within the unsaturation region of $h(\tau)$ and to prevent inefficient use of the input.
+With a sufficiently large value for $p$, the input norm constraint essentially matches the control input saturation function.
+Note that among the selected controllers given below, only the proposed CoNAC can rigorously handle this input norm constraint.
+
+% **********************************************************
+% SYSTEM FIGURE AND TABLE
 \begin{figure}[!t]
     \centering
-    \includegraphics[width=0.8\linewidth]{fig/RobotModel.drawio.png}
+    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
 
-The two-link manipulator model in \cite{Markus:2013aa} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
-In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
-The values of the system parameters are given in Table~\ref{table: system parameters}.
-The reference signal of $\q=[q_1,q_2]^\top $ is defined as follows:
-\begin{equation}
-    \qd
-    =
-    \begin{bmatrix}
-        {q_d}_1\\
-        {q_d}_2
-    \end{bmatrix}
-    = 
-    \begin{bmatrix}
-        +\cos(
-            \tfrac{\pi}{2}t
-        ) + 1 \\
-        -\cos(
-            \tfrac{\pi}{2}t
-        ) - 1 
-    \end{bmatrix}
-    .
-\end{equation}
-
-For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod) and the proposed controller with constrained optimization (NAC-CO).
-%%%%%%%%%%%%%%%%%%%%%
-The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters $\lambda$, $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively.
-The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \norm{\mv \xi}^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
-The parameter dependencies of the controllers were examined via various values of the parameters. 
-The values ranged from $0.001$ to $1$ across $10$ samples.
-%%%%%%%%%%%%%%%%%%%%%
-
-The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2} = J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
-The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
-\begin{equation} 
-    \ddtt{{\estwth}} = 
-    \pptfrac{J_{L_2}}{\estwth}
-    =-\alpha
-    \left(
-        \pptfrac{J}{\estwth}
-        +
-        \lambda{\estwth}
-    \right)
-    .
-    \label{eq. adap L2}
-\end{equation}
-Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\estwth}$, where $\sigma\in\R_{>0}$.
-For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\norm{\tilde{\mv z}}{\estwth}$ is added to the adaptation law as follows:
-\begin{equation}
-    \ddtt{{\estwth}} = -\alpha
-    \left(
-        \pptfrac{J}{\estwth}
-        +
-        \rho\norm{\tilde {\mv z}}{\estwth}
-    \right)
-    \label{eq. adap eMod}
-\end{equation}
-where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
-By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
-Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
-The adaptation law of NAC-CO is presented in \eqref{eq. adaptation laws}.
-Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.
-
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\mm M_0=I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
-The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.
-For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
-The sampling time of the simulation and the simulation termination time were set to $T_s=100\ \mu\mathrm{s}$ and $T=10\ \mathrm{s}$, respectively.
-
-\subsection{Results}
-
 \begin{figure}[!t]
     \centering
-    {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
-\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
-    \label{fig: Box-beard plot}
+    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
+    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
+    \label{fig: h func}
 \end{figure}
+
+% SYSTEM FIGURE AND TABLE
+% **********************************************************
+Four controllers were examined for a comparative study.
+The first was the Backstepping Controller (BSC), used as the baseline.
+The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro-adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC.
+While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints.
+The third was DNN-BSC augmented with an auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
+As a result, an approximation of the input norm constraint was used as an input bound constraint.
+Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework.
+The properties of these four controllers are summarized in Table \ref{table:controller}.
+%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).
 
@@
     \hline
-     & \textbf{NAC-L2} & \textbf{NAC-eMod} & \textbf{NAC-CO} (proposed) 
-     \\
+    & \multicolumn{3}{c|}{Handling Capability}\\
     \hline
-    Maximum         & $11.1753$e-3 & $0.5603$e-3 & $0.3439$e-3 \\
+    & System & Weight Norm & Input Norm\\
+    &  Uncertainty & Constraint & Constraint\\
     \hline 
-    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
+    BSC     & X & X & X\\
+    \hline
+    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
+         &  & (by projection) & \\
+    \hline
+    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
+       &  & (by projection) &  (by aux. system)\\
+       % &  & & linearized constraint)\\
     % \hline
-    Median          & $0.5898$e-3 & $0.5519$e-3 & $0.3240$e-3 \\
+    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
+    %    &  & (by projection) &  system for \\
+    %    &  & & linearized constraint)\\
     \hline
-    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
-    % \hline
-    Minimum         & $0.5434$e-3 & $0.5434$e-3 & $0.3235$e-3 \\
+    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
+         &  & (by optimization) & (by optimization)\\
     \hline
     \end{tabular}
-    \label{table: error norm}
 \end{table}
 
-As shown in Fig.~\ref{fig: Box-beard plot}, the maximum square root of the tracking ISE of NAC-CO is smaller than the minimum square root of the tracking ISEs of NAC-L2 and NAC-eMod for all variations in the parameters.
-This is because NAC-L2 and NAC-eMod bias the weights to the origin due to the presence of stabilizing functions.
-A quantitative comparison of the square root of the tracking ISE is provided in Table~\ref{table: error norm}.
+% \begin{table}
+% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
+% \centering
+% {\begin{tabular}{cc}\textcolor{black}ine
+% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
+% Rated power & 3 kW\\
+% Rated speed & 4500 RPM\\
+% Rated torque & 6.4 Nm\\
+% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
+% $I_{max}$ & 15 A \\
+% $V_{dc}$ & 100 V\\
+% $R_s$ & 0.34 $\Omega$\\
+% $P$ & 3\\
+% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
+% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
+% \multirow{2}{*}{Controller} & TMS320F28377D\\
+% & (Texas Instrument) \\
+% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
+%  & (Infineon Technologies)
+% \\\textcolor{black}ine
+% \end{tabular}}
+% \end{table}
+
+% \begin{table}[!t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Common Parameters of Selected Controllers.}
+%     \label{table: error norm}
+%     \centering
+%     \begin{tabular}{|c||c|c|c|c|c|c|}
+%     \hline
+%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
+%     \hline 
+%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
+%     \hline
+%     \end{tabular}
+%     \label{table: control parameters}
+% \end{table}
+
+% **** CM1,2 control law *****
+The BSC used the control law defined in \eqref{eq. desired control} with $\hat f=[0,0]^\top$. Since BSC did not consider the unknown system dynamics, the approximation term $\hat f$ was set to zero.
+%CM1 has the following control gains and design parameters: $k_s=5,{k_z}=5, M_0=I_2, C_0=I_2, G_0=[0,0]^\top  $.
+% Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^\top$. 
+The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \estNN$.
+The adaptation law for DNN-BSC, as presented in \cite{Patil:2022aa}, was defined by
+\begin{equation}\label{eq:projection}
+\dot {\estwth}= \myproj_{\Omega}[\alpha  (\partial \estNN/\partial \estwth)M_0^{-1}{\tilde z}],
+\end{equation}
+where $\myproj_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{Krstic:1995aa}, which projects an input vector onto a convex set $\Omega$.
+The convex set was defined as ${\Omega}:= \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i:= \{\estwth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
+cstr weight ball}.
+% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\myproj_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\estwth$-space.).
+% **** CM3 control law *****
+
+The control law for DNN-BSC-A was the same as DNN-BSC, but with an auxiliary system to compensate for control input violations.
+Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq.
+cstr input ball}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq.
+cstr input saturation} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
+The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
+%considering $h(\cdot)$, saturated control input is defined as $s(\tau):= \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
+The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\R^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} =
+\tau_{(i)}-\text{sat}(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
+% s(\tau)-\tau$.
+The auxiliary state variables were used in the adaptation law \eqref{eq:projection} by substituting ${\tilde z}$ with ${\tilde z}+\zeta$.
+
+% **** CoNAC control law *****
+The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq.
+approximated control}.
+The update rates for the multipliers were set as $\beta_{j}=0.1$.
+The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
+
+For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
+Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
+The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ (from Eq.
+\eqref{eq.
+h func}).
+The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
+The sampling time of the simulations was selected as $T_s=10^{-4}$.
+% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+% The other parameters for CM1 to CoNAC were selected as listed in Table.~\ref{table: control parameters}.
+The same values were assigned across all the controllers for the common parameters for a fair comparison.
+
+% **********************************************************
+% SIMULATION FIGURES
+\begin{figure*}[!t]
+    \centering
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
+        \label{fig: tracking_CM1}}
+    \hfill
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
+        \label{fig: tracking_CM2}}
+    \vfill
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
+        \label{fig: tracking_CM3}}
+    \hfill
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
+        \label{fig: tracking_CoNAC}}
+    \caption{Comparison of the tracking performance across the selected controllers.}
+    \label{fig: tracking}
+\end{figure*}
+
+\begin{figure*}[!t]
+    \centering
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
+        \label{fig: control_CM1}}
+    \hfill
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
+        \label{fig: control_CM2}}
+    \vfill
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
+        \label{fig: control_CM3}}
+    \hfill
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
+        \label{fig: control_CoNAC}}
+    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
+    \label{fig: control}
+\end{figure*}
 
@@
     \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
-        \label{fig: weight NAC-L2}}
+    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
+    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
+    \label{fig: ball control}}
+\end{figure}
+
+\begin{figure*}[!t]
+    \centering
+        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
+        \label{fig: multiplier_CoNAC}}
+    \hfill
+        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
+        \label{fig: weight_CM2}}
     \vfill
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
-        \label{fig: weight NAC-eMod}}
-    \vfill
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
-        \label{fig: weight NAC-CO}}
-    \vfill
-    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: weight}
-\end{figure}
-
-\begin{figure}[!t]      
-    \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
-        \label{fig: error NAC-L2}}
-    \vfill
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
-        \label{fig: error NAC-eMod}}
-    \vfill
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
-        \label{fig: error NAC-CO}}
-    \vfill
-    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: error}
-\end{figure}
-
-For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
-As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\estwth}$.
-Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
-Since the weight norm is decreased, NAC-L2 cannot generate sufficient control inputs, resulting in a larger square root of tracking ISE, as shown in Fig.~\ref{fig: error NAC-L2}.
-
-On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
-This is because the stabilizing function $-\alpha\rho\norm{\tilde {\mv z}}{\estwth}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
-However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (\ie smaller weight norms are observed as $\rho$ increases.).
-Therefore, similar to NAC-L2, the biased weights produce insufficient control input, resulting in a relatively larger square root of tracking ISE than that of NAC-CO, as described in Table \ref{table: error norm}.
-
-Finally, the weight norm of NAC-CO is smaller than those of NAC-L2 and NAC-eMod, as shown in Fig.~\ref{fig: weight NAC-CO}, with better tracking performance.
-Even if a large $\beta_j$ is provided, NAC-CO can adjust the adaptation direction to satisfy the weight norm constraints faster, according to \eqref{eq. adaptation law L}.
-Therefore, the lowest dependency on the update rate $\beta_j$ is observed in NAC-CO, as shown in Fig.~\ref{fig: weight NAC-CO} and Fig.~\ref{fig: error NAC-CO}.
-Note that $\beta_j$ of NAC-CO is the update rate for the Lagrange multipliers, whereas $\lambda$ and $\rho$ are the coefficients of the stabilizing function that generates the biases of the weights.
-However, considering the implementation using a digital computer, excessively large $\beta_j$ values should be avoided.
-
-The details of the satisfaction of the weight norm constraints are shown in Fig.~\ref{fig: weight and multiplier} for NAC-CO with $\beta_j=0.001$.
-As the weight norms of each layer reach the constraint boundary, the corresponding Lagrange multipliers are generated.
-Using the Lagrange multipliers, the adaptation direction is adjusted toward the constraint satisfactory point.
-The Lagrange multipliers disappear when the constraints are satisfied, and the weights are adapted to optimize the original objective function without weight bias.
-
-\begin{figure}[!t]      
-    \centering
-    \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
-    \label{fig: weight per layer NAC-CO}}
-    \vfill
-    \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
-    \label{fig: multipliers NAC-CO}}
-    \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
+        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
+        \label{fig: weight_CM3}}
+    \hfill
+        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
+        \label{fig: weight_CoNAC}}       
+    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
     \label{fig: weight and multiplier}
-\end{figure}
-
-Furthermore, it is important to note that NAC-CO shows enhanced tracking performance with smaller weights than NAC-L2 and NAC-eMod.
-This implies that the weights in NAC-CO approach the different local optimal solution points from those of NAC-L2 and NAC-eMod.
-Therefore, if the physical analysis of the system is available to predict the feasible maximum control inputs, NAC-CO can find the local optimal solution without unnecessarily large control inputs by imposing proper weight norm constraints.
+\end{figure*}
+% SIMULATION FIGURES
+% **********************************************************
+
+\subsection{System Uncertainty Handling}
+
+The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
+To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties.
+As a result,
+%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
+%the parameters of CM1 are poorly tuned, 
+BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.
+
+By leveraging the DNN to compensate for the lumped system uncertainty within the BSC, DNN-BSC achieved improved tracking performance compared to BSC, as seen in Fig.~\ref{fig: tracking_CM2}.
+Fig.~\ref{fig: tracking_CM3} shows that DNN-BSC-A enhanced tracking performance for $q_2$, but tracking for $q_1$ remained unsatisfactory due to incomplete constraint handling, which will be discussed in detail in Section \ref{sec:sim_cnst}.
+%By compensating the uncertain terms the control input of CM2 in Fig.~\ref{fig: control_CM2} is saturated.
+
+Finally, CoNAC, which directly approximates the stabilizing control law along with the compensation term, demonstrated satisfactory tracking performance across both states, as illustrated in Fig.~\ref{fig: tracking_CoNAC}.
+
+\subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}
+
+The resulting control input $\tau$ and physically saturation control input $h(\tau)$ for the selected controllers are shown in Fig.~\ref{fig: control}.
+As illustrated in Fig.~\ref{fig: control_CM1}, BSC did not violate the input norm constraint (\ie $\tau = h(\tau)$).
+However, in DNN-BSC, the added compensation term from the DNN caused violations of the input norm constraint (\ie $\tau > h(\tau)$) at several points; see Fig.~\ref{fig: control_CM2}.
+This failure to account for the input norm constraint led to oscillations in the control input $\tau$.
+The DNN adaptation process attempted to increase the weights to reduce the residual errors that were not constrained by saturation, but after saturation ceased, the control input had to rapidly adjust back to realistic levels, leading to oscillatory behavior.
+Such high-frequency oscillations may induce instability in the control system or cause fatigue in the actuators.
+
+On the other hand, both DNN-BSC-A and CoNAC successfully handled their imposed input constraints, as shown in Fig.~\ref{fig: control_CM3} and Fig.~\ref{fig: control_CoNAC}, respectively, without causing notable oscillations in the control input $\tau$ even after the input constraint was activated.
+However, the tracking performance of DNN-BSC-A was lower than that of DNN-BSC and CoNAC, as the auxiliary system used in DNN-BSC-A approximated the input norm constraint with an input bound constraint, creating a rectangular constraint in the $\tau$-space (see Fig.~\ref{fig: ball control}).
+In contrast, CoNAC satisfied the nonlinear input norm constraint and produced the physically maximum control input, resulting in improved tracking performance.
+
+It is also important to note that the control input trajectory in DNN-BSC-A depends on the dynamics of the auxiliary system.
+The auxiliary system regulates the violated control input after sufficient auxiliary state $\zeta$ is generated to compensate for the violation.
+This can be observed in Fig.~\ref{fig: ball control}, where DNN-BSC-A exhibited minor violations of the input bound constraint.
+In contrast, CoNAC satisfied the constraint without being affected by such dynamics, as its Lagrange multiplier adjusted as soon as the constraint was violated.
+
+%Meanwhile, CM2 and CM3 is based on BSC, and the desired controller $\tau^*$ of CoNAC is based on the BSC which may produce larger control input by canceling the stabilizing system dynamics.
+%Therefore, CM2, CM3, and CoNAC produced the saturated control input.
+%These control results show why the control saturation should be handled.
+
+\subsection{Weight Norm Constraint Handling}
+
+The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}.
+All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.
+
+IN DNN-BSC, as shown in Fig.~\ref{fig: weight_CM2}, the weight norm of the last layer (\ie $\Vert {{{\hat \wth }_2}} \Vert$) fluctuated significantly over time, proportional to the control input norm.
+This is because the last layer’s weights directly determine the control input.
+When the control input violated the input norm constraint, the last layer’s weight norm hit the boundary and stayed there due to the projection operator.
+However, the projection operator only responded to violations without considering optimality or behavior.
+%In the case of CM2 which does not consider the control input constraint, the weight norm of the last layer reaches the maximum weight norm value, when the control is saturated.
+%It is because the weights get increased to produce larger control input to reduce the tracking error of $q_2$.
+(\ie the maximum magnitude of the control input depends on the weight norm of the last layer, since the activation function is bounded.)
+
+In DNN-BSC-A, none of the weight norms reached their boundaries, as shown in Fig.~\ref{fig: weight_CM3}.
+This was due to the auxiliary system, where the auxiliary state $\zeta$ reduced the control input, ensuring it stayed within the input constraint.
+
+In CoNAC, all weight norms complied with the imposed constraints through the constrained optimization approach, as illustrated in Fig.\ref{fig: weight_CoNAC}.
+When any weight norm approached its upper limit, the Lagrange multiplier was promptly activated to steer the weight adaptation direction towards a constraint-satisfactory point (see Fig.\ref{fig: multiplier_CoNAC}).
+Notably, the weight norms of the first and second layers ($\Vert {{{\hat \wth }_0}} \Vert$ and $\Vert {{{\hat \wth }_1}} \Vert$) remained nearly constant throughout the control period.
+The weight norm of the last layer $\Vert {{{\hat \wth }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint.
+This quasi-static behavior of the weight norm (\ie $d{\estwth}/dt=-\alpha\partial L/\partial \estwth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
+However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds.
+This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
+%(\ie $\partial J/\partial\estwth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\estwth} c_j)$.
+%, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.
+
+The overall weight norms of CoNAC were larger than those of DNN-BSC and DNN-BSC-A, since CoNAC approximated the entire stabilizing control law, whereas DNN-BSC and DNN-BSC-A only approximated the system uncertainty term within the BSC framework.
+
+%Because the simulation is implemented in a digital computer, the multipliers repeat to disappear and be generated, since the constraints are satisfied and violated in the digital process.
+
+%\subsection{Analysis of the Neural Network}
+
+%Generally, the existing literature states that the maximum norms of the weights should be sufficiently large (\ie $\bar\wth_i \gg 0$) since the designer does not know where the global optimal point of the weights is.
+%However, using the physical prior knowledge of the system, one can guess the proper value of the maximum norm, since the magnitude of the control input depends on the last layer's weights due to the bounded activation function.
+%Furthermore, the simulation study shows that the selected controllers have sufficiently good performances with the small maximum weight norms.
+%It means that the local optimal point of the weights are more effective for the stability analysis and the limitating the control input's amplitude.
+
+%Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
+%However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}.
+(\ie the weight updates are smaller as its layer is closer to the input layer.)
+%To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
 
@@
 
-\color{black}
-In this paper, a neuro–adaptive control method is proposed for uncertain Euler‒Lagrange systems, ensuring weight boundedness.
-Adaptation laws are derived by formulating a constrained optimization problem with weight norm constraints.
-The boundedness of the tracking error and the weight estimation are analyzed via Lyapunov analysis.
-The simulation results demonstrate that the proposed controller outperforms the existing methods in terms of tracking performance and parameter dependency.
-As further work, the state and output constraints for safety will be handled, ensuring stability.
-\color{black}
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{APPENDIX}
-
-% Appendixes should appear before the acknowledgment.
-
-% \section*{ACKNOWLEDGMENT}
-
-% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ.
-Avoid the stilted expression, ÒOne of us (R.
-B.
-G.) thanks .
+This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
+
+The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds.
+By formulating these constraints as part of the optimization process, CoNAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
+
+Simulation results validated the superior performance of CoNAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+CoNAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
+
+Future work may extend this approach to address constraints on both the system inputs and states, further enhancing the flexibility and robustness of neuro-adaptive control systems using constrained optimization.
+
+\begin{appendices}
+
+\section{Constraint Candidates}\label{sec:appen:cstr}
+
+This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller.
+
+\subsection{Input Bound Constraint}\label{sec:appen:input_bound_cstr}
+
+Most physical systems have control input limits due to electrical and mechanical limitations.
+These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+\begin{equation}
+    \begin{aligned}
+        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
+        \\
+        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+    \end{aligned}
+    \label{eq. cstr input saturation}
+\end{equation}
+with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
+% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
+The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
+\begin{equation}
+    \begin{aligned}
+        {\partial \boldsymbol c_{\overline \tau} \over \partial \estwth}
+        =& 
+        \begin{bmatrix}
+            (\partial c_{\overline \tau_1}/\partial \estwth)^\top \\
+            \vdots \\
+            (\partial c_{\overline \tau_n}/\partial \estwth)^\top
+        \end{bmatrix}
+            = -{\partial \estNN\over\partial\estwth}
+            \\
+        =&
+        -\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
+        , 
+        \\
+        {\partial \boldsymbol c_{\underline\tau} \over \partial \estwth}         
+        :=
+        & 
+        \begin{bmatrix}
+            (\partial c_{\underline\tau_1}/\partial \estwth)^\top \\
+            \vdots \\
+            (\partial c_{\underline\tau_n}/\partial \estwth)^\top
+        \end{bmatrix}
+        = +{\partial \estNN\over\partial\estwth}
+        \\
+        =&
+        +\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
         .
-.Ó  Instead, try ÒR.
-B.
-G.
-thanksÓ.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \end{aligned}
+    \label{eq. nabla input sat}
+\end{equation}
+
+\subsection{Input Norm Constraint}\label{sec:appen:input_norm_cstr}
+
+Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
+Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
+This can be captured by the following inequality constraint:
+\begin{equation}
+    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
+    \label{eq. cstr input ball}
+\end{equation}
+with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
+This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
+% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
+The gradients of $c_{u}$ with respect to $\estwth$ are given by
+\begin{equation}
+    {\partial \boldsymbol c_{u} \over \partial \estwth}
+    = -\sum_{i=1}^n 2\tau_{(i)} 
+    \bigg(
+        \myrow_i
+        \bigg(
+            -{\partial \estNN\over\partial\estwth}
+        \bigg)
+    \bigg)^\top  
+    = \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
+    \in \mathbb R^{\Xi}.
+    \label{eq. nabla input ball}
+\end{equation}
+It should be noted that constraints \eqref{eq.
+cstr input saturation} and \eqref{eq.
+cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
+nabla input sat} and \eqref{eq.
+nabla input ball} are linearly dependent, violating the LICQ condition.
+
+\end{appendices}
+
+%  BIBLIOGRAPHY ============================================
 {\footnotesize
 \bibliographystyle{ieeetr}
+% \bibliography{}
 \bibliography{dding_template/refs}}

### 2025-03-23 manuscript.tex
final touch before report to Prof.

--- 2025-03-22 manuscript.tex
@@
 
-% \makeatletter
-% \let\NAT@parse\undefined
-% \makeatother
+\makeatletter
+\let\NAT@parse\undefined
+\makeatother
 
-\input{dding_template/tex_packages/tex_packages_general.tex}
-\input{dding_template/tex_macros/tex_macros_general.tex}
-% MY PAKEAGES ========================================
-
-\newcommand*{\q}{\mv{q}}
-\newcommand*{\dq}{\dot{\q}}
-\newcommand*{\ddq}{\ddot{\q}}
-\newcommand*{\qd}{\mv{q_d}}
-\newcommand*{\dqd}{\dot{\qd}}
-\newcommand*{\ddqd}{\ddot{\qd}}
+\def\pub{false} % true for publication, false for draft
+\newcommand*{\template}{dding_template}
+\input{\template/preamble/preamble_conf.tex}
 
@@
 More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{Farrell:2006aa}.
-It uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
+It generally uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
 This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
@@
 % One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs is that the outputs of NNs are not predictable.
+One of the common issues in using NNs 
+\color{red}
+for control compontnets
+\color{black}
+is that the outputs of NNs are not predictable.
 This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
+\color{red}
+This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.
+\color{black}
+\st{
     This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
+}
 
@@
 where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V_m}$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
+Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V}_m$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
 \begin{equation}
-    \widehat{\mm M}\ddq+\widehat{\mm V_m}\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
+    \widehat{\mm M}\ddq+\widehat{\mm V}_m\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
     ,
@@
 \end{equation}
-where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V_m})\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.
+where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V}_m)\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.
 
@@
         +
-        \widehat{\mm V_m}{\mv z}
+        \widehat{\mm V}_m{\mv z}
         +
@@
 \color{red}
-    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2018aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
+    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
 \color{black}
@@
 \begin{equation}
-    \NN({\q_{NN}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{NN}})
+    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
     ,
 \end{equation}
-where ${\q_{NN}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
+where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
 The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
-For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i=(l_i+1)\cdot l_{i+1}$ and $\Xi=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
+For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
 
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{NN}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{NN}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
+Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{n}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{n}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
 The ideal weight vector $\wth^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\estwth=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\wth^*=(\wth_1^{*\top},\wth_0^{*\top})^\top $, the desired controller $\mv \tau^*\approx -\NN(\q_{NN};\wth^*)-\mv\epsilon$ with bounded approximation error $\mv \epsilon\in\R^2$, can be approximated as follows:
+Then, using the estimated weight vector $\estwth:=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\idealwth:=({\idealwth_{1}}^{\top},{\idealwth_{0}}^{\top})^\top $ and bounded approximation error $\mv \epsilon\in\R^2$, the approximated desired controller $\mv \tau^*\approx -\NN(\q_{n};\idealwth)-\mv\epsilon$ can be estimated as follows:
 \begin{equation}
-    \mv \tau := -\NN({\q_{NN}};\estwth)
+    \mv \tau := -\NN({\q_{n}};\estwth)
     .
@@
 \end{equation}
-For further sections, let $\idealNN:=\NN({\q_{NN}};\idealwth)$ and $\idealact :=\act({\idealwV}_0^{\top}{\q_{NN}})$, and let $\estNN:={\NN}({\q_{NN}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{NN}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{NN})}$.
+For further sections, let $\idealNN:=\NN({\q_{n}};\idealwth)$ and $\idealact :=\act({\idealwV_0}^{\top}{\q_{n}})$, and let $\estNN:={\NN}({\q_{n}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{n}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{n})}$.
 
@@
 desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=(\tilde {\q}^\top ,\tilde {\mv z}^\top)^\top \in\R^{2n}$ as follows:
+control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=({\tilde {\q}}^\top ,{\tilde {\mv z}}^\top)^\top \in\R^{2n}$ as follows:
 \begin{equation}
-    \dot{\mv \xi} 
+    \ddtt{\mv \xi} 
     = 
@@
 \color{black}
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ i\in\{0,1\}$.
+For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}:=c_{\theta_i}(\estwth_i)=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ \forall i\in\{0,1\}$.
 The control problem can be reformulated into a constrained optimization problem as follows:
@@
         \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
-        = 
+        := 
         \{\theta_0,\theta_1\}
@@
 % where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L$, the adaptation law is derived as follows:
+To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L(\mv \xi,{\estwth},[\lambda_j]_{j\in\mathcal I}$, the adaptation law is derived as follows:
 \begin{subequations}
@@
 Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
-\begin{equation}
+% \begin{equation}
+$
     \pptfrac{J}{\estwth}
@@
     .
-\end{equation}
+% \end{equation}
+$
 The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
@@
             \ \ 
-            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
+            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
         ]
@@
 \end{equation}
-where $\mv w(t):= {\idealwV}_1^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
+where $\mv w(t):= {\idealwV_1}^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
 The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )$ is bounded.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $\norm{-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )}$ is bounded.
 
@@
         \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )
+        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
         \\
@@
 \end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{NN}}^\top )$ is bounded.
+According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $\norm{-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )}$ is bounded.
 To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=\tfrac{1}{2\alpha}{\estwth}_0^\top {\estwth}_0$ yields:
@@
     \hline 
-    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
+    $m_p$ & Mass of $p\textsubscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
     \hline
-    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
+    $l_p$  & Length of $p\textsubscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
     \hline
-    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
+    ${l_c}_p$ & COM of $p\textsubscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
     \hline
-    $\theta_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
+    $b_p$   & Viscous coef. of $p\textsubscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
     \hline
-    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
+    ${f_c}_p$  & Friction coef. of $p\textsubscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
     \hline
@@
 The two-link manipulator model in \cite{Markus:2013aa} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
-In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in\{1,2\}$.
 The values of the system parameters are given in Table~\ref{table: system parameters}.
@@
 %%%%%%%%%%%%%%%%%%%%%
-The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters $\lambda$, $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively.
+The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters (\ie $L_2$ coefficient $\lambda$, $\epsilon$-modification coefficient $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively).
 The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \norm{\mv \xi}^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
@@
 The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2} = J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$ denotes the $L_2$ coefficient.
+The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2}:= J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$.
 The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
@@
         \rho\norm{\tilde {\mv z}}{\estwth}
+    \right)
     ,
-    \right)
     \label{eq. adap eMod}
 \end{equation}
-where $\rho\in\R_{>0}$ denotes the $\epsilon$-modification coefficient.
+where $\rho\in\R_{>0}$.
 By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
@@
 
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\text{diag}([5,1,15,15])$.
+All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
@@
 \color{black}
-The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{NN}=[\qd^\top ,1]^\top $.
+The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
 For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
-The sampling time of the simulation and the simulation termination time were set to $T_s=100\ \mu\mathrm{s}$ and $T=10\ \mathrm{s}$, respectively.
+The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.
 
@@
         \label{fig: weight NAC-L2}}
-    \vfill
+    \vspace{.1mm}
         \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
         \label{fig: weight NAC-eMod}}
-    \vfill
+    \vspace{.1mm}
         \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
         \label{fig: weight NAC-CO}}
-    \vfill
     \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
@@
         \label{fig: error NAC-L2}}
-    \vfill
+    \vspace{.1mm}
         \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
         \label{fig: error NAC-eMod}}
-    \vfill
+    \vspace{.1mm}
         \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
         \label{fig: error NAC-CO}}
-    \vfill
     \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
@@
 
-For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in[0.001,0.45,1]$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
+For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in\{0.001,0.45,1\}$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
 As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\estwth}$.
@@
         \label{fig: weight per layer NAC-CO}}
-    \vfill
+    \vspace{.1mm}
         \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
@@
 
-\color{black}
+%
 In this paper, a neuro–adaptive control method is proposed for uncertain Euler‒Lagrange systems, ensuring weight boundedness.
@@
 The simulation results demonstrate that the proposed controller outperforms the existing methods in terms of tracking performance and parameter dependency.
-As further work, the state and output constraints for safety will be handled, ensuring stability.
-\color{black}
+As further work, the state constraints for safety will be handled, ensuring stability.
+%
 
@@
     \bibliographystyle{ieeetr}
-\bibliography{dding_template/refs}}
+    \bibliography{dding_template/refs}
+}
 

### 2025-03-23 src/main_ECC_plotter.m

@@ -124,13 +124,13 @@ e3 = sqrt(sum(e3.^2, 1));
 plot(t, zeros(size(t)), "color",  'black', "LineWidth", line_width, "LineStyle", "-", ...
     'HandleVisibility','off'); hold on
 plot(t, e1, "color",  c_list(1,:), "LineWidth", line_width, "LineStyle", "-", ...
-    "DisplayName", "$\beta=0.001$"); hold on
+    "DisplayName", "$\beta_j=0.001$"); hold on
 plot(t, e2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ...
-    "DisplayName", "$\beta=0.45$"); hold on
+    "DisplayName", "$\beta_j=0.45$"); hold on
 plot(t, e3, "color", c_list(3,:), "LineWidth", line_width, "LineStyle", "--", ...
-    "DisplayName", "$\beta=1$"); hold on
-xlabel("Time / S", "Interpreter", "latex")
-ylabel("$\Vert\mathbf{\xi}\Vert$ / rad", "Interpreter","latex")
+    "DisplayName", "$\beta_j=1$"); hold on
+xlabel("Time / s", "Interpreter", "latex")
+ylabel("$\Vert {\xi}\Vert$ / rad", "Interpreter","latex")
 set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
 grid on
 ylim([-.005, .03])
@@ -167,8 +167,8 @@ plot(t, e2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ..
     "DisplayName", "$\lambda=0.45$"); hold on
 plot(t, e3, "color", c_list(3,:), "LineWidth", line_width, "LineStyle", "--", ...
     "DisplayName", "$\lambda=1$"); hold on
-xlabel("Time / S", "Interpreter", "latex")
-ylabel("$\Vert\mathbf{\xi}\Vert$ / rad", "Interpreter","latex")
+xlabel("Time / s", "Interpreter", "latex")
+ylabel("$\Vert {\xi}\Vert$ / rad", "Interpreter","latex")
 set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
 grid on
 ylim([-.005, .03])
@@ -206,8 +206,8 @@ plot(t, e2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ..
[…]

### 2025-03-24 manuscript.tex
table left align
school to department

@@
 \thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
-\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
+\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
 \thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
@@
     \centering
-    \begin{tabular}{c c c c c }
+    \begin{tabular}{c m{11em} c c c }
     \hline

### 2025-03-25 manuscript.tex
fix; prof. comments

@@
 
-\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
-\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
-\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
-\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
-        {\tt\small jiyun6606@gm.gist.ac.kr}}%
+\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{3}$% <-this % stops a space
+\thanks{
+    *This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No.
+KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}
+}% <-this % stops a space
+\thanks{
+    $^{1}$Myeongseok Ryu is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr}
+}%
+\thanks{
+    $^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
+        {\tt\small jiyun6606@gm.gist.ac.kr}
+}%
+\thanks{
+    $^{3}$Kyunghwan Choi was with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, Republic of Korea.
+He is currently with the Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small kyunghwan.choi90@gmail.com}
+}%
 }
@@
 % One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs 
-\color{red}
-for control compontnets
-\color{black}
-is that the outputs of NNs are not predictable.
+One of the common issues in using NNs as control compontnets is that the outputs of NNs are not predictable.
 This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
-\color{red}
 This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.
-\color{black}
-\st{
-    This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
-}
 
@@
 To approximate the desired controller, an NN is utilized.
-\color{red}
-    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
-\color{black}
+Even though DNNs have a higher approximation capability than SHLNNs \cite{Rolnick:2018aa}, here, an SHLNN is utilized for simplicity and low computational complexity.
 The NN with a single hidden layer is represented as 
@@
 
-\color{red}
 As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
-\color{black}
 For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}:=c_{\theta_i}(\estwth_i)=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ \forall i\in\{0,1\}$.
@@
         \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
+        ,
         \\
@@
 Then, the invariance set can be represented as 
-\begin{equation}
+% \begin{equation}
+$
     \Theta_{{\theta}_0} :=
-    \left\{
+    % \left\{
+    \{
         {\estwth}_0\mid\norm{\estwth_0}
@@
         }
-    \right\}
+    % \right\}
+    \}
     .    
-\end{equation}
+$
+% \end{equation}
 If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
@@
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-\color{red}    
 The validity of the selected number of nodes were demonstrated through experiments 
-\color{black}
 The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
@@
         \label{fig: weight NAC-L2}}
-    \vspace{.1mm}
+    \vspace{-2mm}
         \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
         \label{fig: weight NAC-eMod}}
-    \vspace{.1mm}
+    \vspace{-2mm}
         \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
@@
         \label{fig: error NAC-L2}}
-    \vspace{.1mm}
+    \vspace{-2mm}
         \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
         \label{fig: error NAC-eMod}}
-    \vspace{.1mm}
+    \vspace{-2mm}
         \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
@@
         \label{fig: weight per layer NAC-CO}}
-    \vspace{.1mm}
+    \vspace{-1mm}
         \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
@@
         \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
+    \vspace{-2mm}
         \label{fig: weight and multiplier}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-{\footnotesize
+% {\footnotesize
     \bibliographystyle{ieeetr}
     \bibliography{dding_template/refs}
-}
+% }
 

### 2025-03-26 manuscript.tex
first commit to GitHub

--- 2025-03-23 manuscript.tex
@@
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
-
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
-
-\IEEEoverridecommandlockouts                              % This command is only needed if 
-                                                          % you want to use the \thanks command
-
-\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
-
+\documentclass[lettersize,journal]{IEEEtran}
+% code
+
+\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}
+
+% \usepackage{balance}
 \def\pub{false} % true for publication, false for draft
-\newcommand*{\template}{dding_template}
+\newcommand*{\template}{template}
 \input{\template/preamble/preamble_conf.tex}
 
-\title{\LARGE \bf
-Imposing a Weight Norm Constraint for Neuro–Adaptive Control
+\newcommand*{\fe}{\mv{r}}
+
+\begin{document}
+\title{
+Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
+%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
 }
 
-\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
-\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
-\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
-\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
-        {\tt\small jiyun6606@gm.gist.ac.kr}}%
-}
-
-\begin{document}
+\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
+~Vol.~00, No.~0, Month~2024
+}%
+{How to Use the IEEEtran \LaTeX \ Templates}
 
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-
-In this paper, a neuro–adaptive controller with weight norm constraints is proposed for uncertain Euler‒Lagrange systems. 
-The boundedness of the weights in the neuro–adaptive controller design is important to prevent excessively large control inputs and system instability. 
-To ensure the boundedness of the weights, the weight norm constraints are imposed as inequality constraints in the weight adaptation. 
-The adaptation law is derived based on the constrained optimization method. 
-The stability of the proposed controller is analyzed in the sense of Lyapunov, ensuring the boundedness of the tracking error and weight estimation. 
-For the comparative study, two benchmark controllers and the proposed controller were evaluated through a numerical simulation of a two-link manipulator system and compared in terms of tracking performance and parameter dependency.
-The comparative study verified that the proposed controller has better tracking performance and lower parameter dependency.
-
+    This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints.
+A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints.
+The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state.
+The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights.
+Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  SECTION INTRODUCTION ===================================
+\begin{IEEEkeywords}
+Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
+\end{IEEEkeywords}
 
@@
     \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
-    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ denotes a vector.
-    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
-    %     \mm A
-    %     := 
-    %     [a_{ij}]
-    %     _{
-    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
-    %     }\allowbreak\in\R^{n\times m}
-    %     $ denotes a vector and a matrix.
+    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
+        \mm A
+        := 
+        [a_{ij}]
+        _{
+            i\in[1,\cdots,n],j\in[1,\cdots ,]
+        }\allowbreak\in\R^{n\times m}
+        $ denote a vector and a matrix.
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
@@
     \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
-    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
+    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
 \end{itemize}
 
-\section{Introduction} \label{sec:intro}
-
-In various practical applications, Euler‒Lagrange systems generally have uncertainties due to their unknown and unmodeled dynamics.
-These uncertainties degrade the control performance index.
-Furthermore, if uncertainties dominate the system, they may lead to instability.
-By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{Tao:2003aa,Ioannou:2006aa}.
-Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.
-
-More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{Farrell:2006aa}.
-It generally uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
-This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
-Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa} and deep NN (DNN) \cite{Patil:2022aa}.
-The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.
-
-% The corresponding issue in the adaptive control is the parameter drift.
-% It refers to the weight divergence during the adaptation process, while the tracking error is bounded.
-
-% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs 
-\color{red}
-for control compontnets
-\color{black}
-is that the outputs of NNs are not predictable.
-This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
-\color{red}
-This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.
-\color{black}
-\st{
-    This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
-}
-
-Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
-In \cite{Zhou:2023aa,Patil:2022aa}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
-However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
-Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
-In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
-The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
-However, they lack theoretical analysis regarding the optimality of the adapted weights.
-
-Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
-One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{Wu:2020aa,Lewkowycz:2020aa}.
-Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
-By regulating the magnitude of the weights, the stability of the adaptation process can be enhanced, and overfitting can be prevented.
-However, $L_2$-regularization also involves a trade-off between adaptation stability and the optimality of the weights.
-
-For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{Nocedal:2006aa} can be utilized.
-It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
-To the best of the authors’ knowledge, no prior work has utilized the constrained optimization method for the real-time weight adaptation of neuro–adaptive control satisfying weight boundedness.
-Therefore, the constrained optimization method could play a pivotal role in the neuro–adaptive control design addressing the weight boundedness.
-
-The main contributions of this study are as follows:
+%  SECTION INTRODUCTION ===================================
+\section{Introduction}
+
+\subsection{Background}
+
+\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
+These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
+In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
+These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
+To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.
+
+More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
+NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}.
+Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
+
+A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated. 
+Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
+
+However, two significant challenges persist in using NNs for adaptive control. 
+First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs. 
+When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. 
+Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{Esfandiari:2021aa}. 
+Failing to address these constraints can degrade control performance or even destabilize the system.
+
+Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
+he following section will provide a detailed review of the existing solutions to these challenges.
+
+\subsection{Literature Review}
+
+\subsubsection{Ensuring Weight Norm Boundedness}
+
+A common challenge in neuro-adaptive control is maintaining the boundedness of the NN weights to ensure stability. 
+In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly. 
+For example, in \cite{Zhou:2023aa,Griffis:2023aa,Patil:2022aa}, projection operators were used to constrain the weight norms to remain below predetermined constants. 
+However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values. 
+While this approach ensured that the NN remained stable, it did not necessarily result in optimal performance.
+
+In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{Ge:2002aa} and $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa}. 
+These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. 
+Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.
+
+\subsubsection{Satisfying Input Constraints}
+
+The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
+The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
+This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
+In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.
+
+To address input saturation, many studies introduced auxiliary systems. 
+These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
+For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
+This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.
+
+Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}.
+In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
+However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+
+\subsubsection{Limitations of Existing Approaches and Potential of Constrained Optimization}
+
+Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations. 
+Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
+Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.
+
+To overcome these limitations, constrained optimization offers a promising approach. 
+By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (\eg tracking error) subject to both weight norm and input constraints.
+Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.
+
+In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{Evens:2021aa} and the Alternating Direction Method of Multipliers (ADMM) \cite{Wang:2019aa,Taylor:2016aa}, have been used to train NNs offline.
+These methods impose constraints to address issues like gradient vanishing in backpropagation. 
+However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation. 
+This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.
+
+\subsection{Contributions}
+
+The main contributions of this study are listed as follows:
 \begin{itemize}
-    \item The neuro–adaptive control problem is reformulated into a constrained optimization problem by treating the satisfaction of the weight boundedness as inequality constraints.
-    \item The adaptation law is derived based on the constrained optimization method to minimize the objective function while satisfying the weight norm constraints.
-    \item The stability of the adaptation laws is analyzed via Lyapunov stability analysis, which ensures the boundedness of the tracking error and weight estimation.
+    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
+    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
+The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
+    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
+    %, enabling more precise real-time adaptation.
 \end{itemize}
 
-The remainder of this paper is organized as follows:
-Section \ref{sec: Problem Formulation} presents the target-constrained system and control objective.
-Section \ref{sec:ctrl design} introduces the proposed controller and the adaptation law. 
-Section \ref{sec:stability} examines the stability of the proposed controller.
-A comparative study of the three selected controllers, including the proposed controller through numerical simulation, is reported in Section \ref{sec:sim}.
-Finally, Section \ref{sec:conclusion} concludes the paper by presenting future work.
+\subsection{Organization}
+
+The remainder of this paper is organized as follows. 
+Section \ref{sec:Problem Formulation} presents the target system and control objective.
+Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
+In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
+Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
+Section \ref{sec:stability} analyzes the stability of the proposed controller.
+A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
+Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
+% The appendices provide the proof of the lemma used in the stability analysis.
 
 %  SECTION PROBLEM FORMULATION ============================
-\section{Problem Formulation}\label{sec: Problem Formulation}
+\section{Problem Formulation}\label{sec:Problem Formulation}
 
@@
 
-Consider an uncertain Euler‒Lagrange system modeled as
-\begin{equation}
-    \mm M\ddq + \mm V_m\dq+ \mm G + \mm F 
-    =
-    \mv\tau 
-    ,
-    \label{eq. system dynamics 1}
-\end{equation}
-where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V}_m$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
-\begin{equation}
-    \widehat{\mm M}\ddq+\widehat{\mm V}_m\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
-    ,
-    \label{eq. system dynamics 2}
-\end{equation}
-where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V}_m)\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.
-
-Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd:=\qd(t):\R\to \R^n$ under the unknown terms $\mv f:=\mv f(\q,\dq,\ddq)$.
+Consider an uncertain Euler-Lagrange system modeled as
+\begin{equation}
+    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
+    =
+    \mysat(\mv\tau)
+    \label{eq:sys1}
+\end{equation}
+where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
+The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
+\begin{equation}
+    \mysat(\mv\tau)
+    :=
+    \begin{cases}
+        \mv\tau, 
+        & 
+        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
+        \\
+        \bar\tau
+        \cdot
+        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
+        & 
+        \text{otherwise},
+    \end{cases}
+    \label{eq:sat}
+\end{equation}
+where $\bar\tau$ denotes the maximum norm of control input.
+To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
+Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+
+The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
+We introduce the following properties:
+\begin{prop} \cite{Lewis:1998aa}
+    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
+    \label{prop:M}
+\end{prop}
+
+\begin{prop} \cite{Lewis:1998aa}
+    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
+    \label{prop:skew}
+\end{prop}
+
+\begin{prop}
+    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
+    \label{prop:dis_bound}
+\end{prop}
+
+In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
+Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
+\begin{assum}
+    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
+    \label{assum:feasible}
+\end{assum}
 
@@
 
-In this section, the neuro–adaptive controller is developed.
-Section \ref{sec:ctrl dev} presents the details of the neuro–adaptive controller and the NN model.
-The adaptation law based on the constrained optimization method is derived in Section \ref{sec:adap_laws} by formulating a constrained optimization problem.
-
-\subsection{Neuro–adaptive Control Design} \label{sec:ctrl dev}
-
-The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
-The desired stabilizing controller can be designed as follows:
-\begin{equation}
-    \mv \tau^* = 
-    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
-    + 
-    ( 
-        -\widehat{\mm M}\tilde {\q}
-        +
-        \widehat{\mm V}_m{\mv z}
-        +
-        \widehat{\mm G}
+The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
+Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model.
+The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
+    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
+    \label{fig:ctrl:diagram}
+\end{figure*}
+
+\subsection{Neuro-Adaptive Controller Design}\label{sec:sub:NAC}
+
+First, let us define the filtered tracking error $\fe\in\R^n$ as 
+\begin{equation}
+    \fe := \dot{\mv e}-\mm\Lambda \mv e
+    ,
+    \label{eq:err:filtered}
+\end{equation}
+where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
+Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
+
+Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
+\begin{equation}
+    \mm M \dot\fe
+    =
+    -\mm V_m \fe
+    -\mm K \fe
+    + \mv f
+    -\mv \tau_d + \mysat(\mv\tau)
+    ,
+    \label{eq:sys:filtered}
+\end{equation}
+where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
+    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
+    =
+    \mm K \fe
+    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
+    +
+    \mm V_m(-\dqd+\mm\Lambda\mv e)
     -
-        \mv f
-        +
-        \widehat{\mm M} \dot {\mv z}^*
+    \mm F
+    -
+    \mm G
+    \in\R^n
+$ denotes the lumped system uncertainty.
+
+Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
+Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
+\begin{equation}
+    \begin{aligned}
+        \ddtt{V}_1
+        =&
+        \fe^\top \mm M (
+            -\mm V_m \fe -\mm K \fe + \mv f
+            -\mv \tau_d + \mysat(\mv\tau)
         )
+        \\
+        &
+        +
+        \tfrac{1}{2}
+        \fe^\top \dot{\mm M}\fe
+        \\
+        =&
+        -
+        \fe^\top \mm K \fe 
+        +
+        \fe^\top (
+            \mv f+\mysat(\mv\tau)
+            -\mv \tau_d
+        )
+        \\
+        &
+        +
+        \tfrac{1}{2}
+        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
+        \\
+        \le&
+        -\lambda_\text{min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mv f+\mysat(\mv \tau))
+        \\
+        \le&
+        -\lambda_\text{min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
         ,
-    \label{eq. desired control}
-\end{equation}
-where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
-Note that the desired controller cannot be realized because of $\mv f$.
-
-To approximate the desired controller, an NN is utilized.
-\color{red}
-    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
-\color{black}
-The NN with a single hidden layer is represented as 
-\begin{equation}
-    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
+    \end{aligned}
+    \label{eq:lya1:dot1}
+\end{equation}
+where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
+However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.
+
+To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
+Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
+Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
+In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
+
+In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
+\begin{align}
+    \mv\tau^*=& \idealNN+\mv\epsilon,
+    \label{eq:control:ideal}
+\end{align}
+which is estimated online by
+\begin{align}
+    \mv\tau =& \estNN,
+    \label{eq:control:est}
+\end{align}
+where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
+
+Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $\mathcal V_1$ can be rewritten as
+\begin{equation}
+    \dot{\mathcal V}_1
+    \le 
+    -\lambda_\text{min}(\mm K)\norm{\fe}^2
+    +
+    \bar\tau_d\norm{\fe}
+    +
+    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
+    .
+    \label{eq:lya1:dot2}
+\end{equation}
+Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).
+
+\subsection{Deep Neural Network (DNN) Model}\label{sec:sub:NN definition}
+
+The DNN architecture $\NN_k = \NN(\q_{NN};\wth)$ can be recursively represented as follows:
+\begin{equation}
+    \NN_i :=
+    \begin{cases}
+        \wV_i^\top \NN_i(\NN_{i-1}), 
+        &
+        i\in[1,\dots,k],
+        \\
+        \wV_0^\top \q_{NN},
+        &
+        i=0
         ,
-\end{equation}
-where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
-The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
-For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
-
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{n}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{n}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
-The ideal weight vector $\wth^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\estwth:=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\idealwth:=({\idealwth_{1}}^{\top},{\idealwth_{0}}^{\top})^\top $ and bounded approximation error $\mv \epsilon\in\R^2$, the approximated desired controller $\mv \tau^*\approx -\NN(\q_{n};\idealwth)-\mv\epsilon$ can be estimated as follows:
-\begin{equation}
-    \mv \tau := -\NN({\q_{n}};\estwth)
-    .
-    \label{eq. control law}
-\end{equation}
-For further sections, let $\idealNN:=\NN({\q_{n}};\idealwth)$ and $\idealact :=\act({\idealwV_0}^{\top}{\q_{n}})$, and let $\estNN:={\NN}({\q_{n}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{n}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{n})}$.
-
-Using \eqref{eq.
-system dynamics 2}, \eqref{eq.
-desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=({\tilde {\q}}^\top ,{\tilde {\mv z}}^\top)^\top \in\R^{2n}$ as follows:
-\begin{equation}
-    \ddtt{\mv \xi} 
-    = 
-    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
-    ,
-\end{equation}
-and 
-\begin{equation}
-    \mm A_\xi := 
+    \end{cases}
+    \label{eq:DNN:architecture}
+\end{equation}
+where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
+The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).
+
+One of the widely used activation functions for large DNNs is from the ReLU family \cite{Maas:2013aa}, which effectively avoids the gradient vanishing problem during error backpropagation. 
+However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
+These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\ddtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}< 1$.
+
+For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
+\begin{equation}
+    \wth := 
     \begin{bmatrix}
-        -{k_q} \mm I_{n} &\mm I_{n}
-        \\
-        -\mm I_{n}& -{k_z} \mm I_{n}
+        \wth_k\\
+        \wth_{k-1}\\
+        \vdots\\
+        \wth_0
     \end{bmatrix}
-    ,\ 
-    \mm B_\xi := 
+    =
     \begin{bmatrix}
-        \mm 0_{n\times n}\\\widehat{\mm M}^{-1}
-    \end{bmatrix}.
-\end{equation}
-
-\subsection{Adaptation Law Derivation}\label{sec:adap_laws}
-
-\color{red}
-    As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
-\color{black}
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}:=c_{\theta_i}(\estwth_i)=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ \forall i\in\{0,1\}$.
-The control problem can be reformulated into a constrained optimization problem as follows:
+        \myvec(\wV_k)\\
+        \myvec(\wV_{k-1})\\
+        \vdots\\
+        \myvec(\wV_0)
+    \end{bmatrix},
+\end{equation}
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
+\begin{equation}
+    \pptfrac{\NN}{\wth}=
+    \begin{bmatrix}
+        \pptfrac{\NN}{\wth_k}&
+        \pptfrac{\NN}{\wth_{k-1}}&
+    \cdots &
+        \pptfrac{\NN}{\wth_0}
+    \end{bmatrix}
+    \in\R^{n \times \Xi}
+    \label{eq. nabla phi}
+\end{equation}
+where
+\begin{equation}
+    \pptfrac{\NN}{\wth_i} = 
+    \begin{cases}
+        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
+        &
+        i=k 
+        \\
+        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
+        & 
+        i=k-1
+        \\
+        &
+        \vdots 
+        \\
+        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
+        &
+        i = 0
+    \end{cases},
+    \label{eq:NN:grad}
+\end{equation}
+where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
+
+In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
+Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and $\act^{*'}_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i:=\act_i(\hat\NN_{i-1})$ and $\hat\act_i':= \pptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
+
+%  SECTION ADAPTATION LAW DERIVATION =======================
+\section{Weight Adaptation Laws}\label{sec:adap_laws}
+
+% \subsection{Adaptation Law using Lagrangian Function}
+\subsection{Weight Optimizer Design}\label{sec:sub:weight optimizer}
+
+The control objective can be represented as follows:
 \begin{equation}
     \begin{matrix}
-        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
-        :=
-        \tfrac{1}{2}
-        \mv \xi^\top \mm \Lambda \mv \xi
+        \min_{\estwth} \ J(\fe;\estwth):= 
+        \tfrac{1}{2} \fe^\top  \mm W\fe
         \\ \\
         \begin{aligned}
-        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
-        := 
-        \{\theta_0,\theta_1\}
-        ,
+        \text{s.t. }&c_{j}(\estwth) 
+        \le0, \quad j\in\mathcal{I},
         \end{aligned}
     \end{matrix}
-\end{equation}
-where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
-In this optimization problem, $\mv \xi$ is considered a predefined parameter.
-The corresponding Lagrangian function is defined as
+    \label{eq:opt:problem1}
+\end{equation}
+where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top  \mm W\fe$ is the objective function, and $\mm W\in\R^{n\times n}$ is a symmetric positive weighting matrix.
+Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
+Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
 \begin{equation}
     L(
-        \mv \xi,
-        {\estwth},
-        [\lambda_j]_{j\in\mathcal I}
+        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
     ) 
     := 
-    J(\mv \xi;{\estwth})
-    +
-    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
-    .
-\end{equation}
-% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L(\mv \xi,{\estwth},[\lambda_j]_{j\in\mathcal I}$, the adaptation law is derived as follows:
+    J(\fe;\estwth) 
+    + 
+    \sum_{j\in\mathcal I}
+    \lambda_{j}
+    c_{j}(\estwth)
+    \label{eq:lagrangian}
+\end{equation}
+where $\lambda_j$ denotes the Lagrange multiplier for each constraint.
+
+The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
 \begin{subequations}
     \begin{align}
-            \ddtt {{\estwth}}
-            &
+            \ddtt{\estwth}
+            &
+            =
+            -\alpha \pptfrac{L}{\estwth}
             =
             -\alpha 
-            \pptfrac{L}{{\estwth}}
-            =-\alpha 
             \left(
-                \pptfrac{J}{{\estwth}}
+                \pptfrac{J}{\estwth}
                 +
@@
             = 
-            \beta_j
-            \pptfrac{L}{\lambda_j} 
+            \beta_j\pptfrac{L}{\lambda_j} 
             = 
             \beta_j c_j ,
-            \quad\quad\quad\quad      \      
-            \forall j\in\mathcal I,
-        \label{eq. adaptation law L}
-            \\
+            \quad \forall j\in\mathcal I,
+        \label{eq:adap:lbd}
+            \\
+            \lambda_j & = \max(\lambda_j,0) ,
+        \label{eq:adap:lbd:max}
+    \end{align}
+    \label{eq:adaptation law}
+\end{subequations}
+where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
+When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation.
+Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \estwth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
+In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
+These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
+% The KKT condition is satisfied, when $\estwth$ converges to $\idealwth$, since $\partial L/\partial \estwth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).
+
+\subsection{Approximation of the Gradient of Objective Function}
+
+The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\mv\tau}$ (\ie 
+$
+    \pptfrac{J}{\mv \tau}
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\mv \tau}{\estwth}))^\top \fe
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\estNN}{\estwth}))^\top \fe
+$). 
+Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
+The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
+\begin{equation}
+    \ddtt (
+        \pptfrac{\fe}{\mv\tau}
+    )
+    =
+    \pptfrac{}{
+        \mv\tau
+    }
+    \left[
+        \mm M^{-1}(
+            -\mm V_m \fe
+            -\mm K \fe
+            + \mv f
+            -\mv \tau_d + \mysat(\mv\tau)
+        )
+    \right]
+    .
+\end{equation}
+However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\mm M,\mm V_m, \mm F$ and $ \mm G$).
+Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
+
+In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\mv\tau}$ as $
+    \pptfrac{\fe}{\mv\tau}
+    \approx
+    [
+        \mathrm{sign}(\pptfrac{r_i}{\tau_j})
+    ]_{i,j\in[1,\cdots,m]}
+$ using the sign of each entry (\ie control direction).
+However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\mm M^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
+Therefore, we propose to approximate $\pptfrac{\fe}{\mv\tau}$ as $\pptfrac{\fe}{\mv\tau}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
+\begin{equation}
+    \ddtt{\estwth}
+    \approx
+    -\alpha 
+    \left(
+        \pptfrac{\estNN}{\estwth}^\top
+        \fe
+        +
+        \textstyle\sum_{j\in\mathcal{I}}
         \lambda_j 
-            & 
-            = 
-            \max(\lambda_j,0) ,
-        \label{eq. adaptation law L max}
-    \end{align}
-    \label{eq. adaptation laws}
-\end{subequations}
-where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
-\color{red}
-% The Eq.~\eqref{eq.
-adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
-\color{black}
-
-Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
-% \begin{equation}
-$
-    \pptfrac{J}{\estwth}
-    =
-    \pptfrac{\mv\xi}{\estwth}^\top 
-    \mm \Lambda
-    \mv\xi
+        \pptfrac{c_j}{\estwth}
+    \right)
     .
-% \end{equation}
-$
-The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
-Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
-\begin{equation}
-    \ddtt{\mm \eta} =
-    \mm A_\xi \mm\eta
-    - \mm B_\xi 
-    % (\partial \estNN/\partial {\estwth})
-    \pptfrac{\estNN}{\estwth}
-    ,
-    \label{eq. sen eq}
-\end{equation}
-where ${\mm \eta}:= \pptfrac{\mv\xi}{\estwth}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
-The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
-By decomposing for each layer, the dynamics of ${\mm \eta}_i:= \pptfrac{\mv\xi}{\estwth}_i\in\R^{2n\times \Xi_i}$ can be represented as
-\begin{equation}
+    \label{eq:adap:th:approx}
+\end{equation}
+
+%% ALGORITHM PART; Now omitted!
+% The proposed controller is implemented using Algorithm \ref{alg: alg1}.
+For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
+If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
+
+% \begin{algorithm}[!t]
+%     \caption{Weight Optimizer Implementation.}\label{alg: alg1}
+%     \begin{algorithmic}[1]
+%         \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+%         \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%         \REQUIRE $\xi$, $\estwth$, $\lambda_j$, $\eta$
+%         \ENSURE  $\estwth$, $\lambda_j$, $\eta$
+%         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
+%         \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
+%         \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
+%         \STATE Determine update directions $\dot{\estwth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
+%         \STATE Update weight vector $\estwth\leftarrow \estwth+\dot{\estwth}\cdot T_s$;
+%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
+%         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
+%         \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
+%         \STATE \textbf{RETURN};
+%     \end{algorithmic}
+%     \label{alg1}
+% \end{algorithm}
+
+\subsection{Constraint Candidates}\label{sec:sub:cstr}
+
+This section introduces conditions which imposed constraints must satisfy and the weight constraints.
+The potential control input constraints are presented in Appendix \ref{sec:appen:cstr}.
+First, we introduce the following assumptions for the constraints.
+
+\begin{assum}
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
+    \label{assum:convex}
+\end{assum}
+
+\begin{assum}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
+    \label{assum:LICQ}
+\end{assum}
+
+\begin{remark}
+    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in practice including the origin.
+    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
+    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
+\end{remark}
+
+The following Lemma is introduced for the stability analysis.
+\begin{lem}
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    \label{lem:convex:angle}
+\end{lem}
+
+\begin{proof}
+
+Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
+\begin{equation}\label{eq:linear:map}
     \begin{aligned}
-        \ddtt{\mm \eta} 
-        \!=\!&
-        \begin{bmatrix}
-            {\mm \eta}_1&{\mm \eta}_0
-        \end{bmatrix}'
-        \\
-        \!=\!&
-        \mm A_\xi
-        % \begin{bmatrix}
-        [
-            {\mm \eta}_1
-            \ \ 
-            {\mm \eta}_0
-        ]
-        % \end{bmatrix}
-        \!-\!
-        \mm B_\xi
-        % \begin{bmatrix}
-        [
-            (\mm I_{l_2}\!\otimes\!\estact^\top )
-            \ \ 
-            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
-        ]
-        % \end{bmatrix}
+    \mv\tau 
+    = 
+    &
+    \estNN 
+    % = 
+    % \myvec(\estNN)
+    =
+    \myvec(
+        \estwV_k^\top \estact_k
+    ) 
+    = 
+    (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top
+    \myvec(\estwV_k)
+    \\
+    = &
+    \underbrace{
+        (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top}_{:=\mm T(\estact_k)}
+    \estwth_k 
+    =
+    \mm T(\estact_k) \estwth_k.
+    \end{aligned}
+\end{equation}
+Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+
+\end{proof}
+
+The weight constraints are essential to prevent the weights from diverging during the adaptation process.
+The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+\begin{equation}
+    c_{\theta_i}
+    =
+    \tfrac{1}{2}
+    (
+        \Vert \estwth_i\Vert^2 
+        -
+        \bar\theta_i^2 
+    )    
+    \le 0
+    \label{eq:cstr:weight_ball}
+\end{equation}
+with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
+The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
+\begin{equation}
+    \pptfrac{c_{\theta_i}}{\estwth_j} 
+    =
+    \begin{cases}
+        \estwth_i,
+        &
+        \text{if } i=j
+        \\
+        0,
+        &
+        \text{if } i\ne j
+        .
+    \end{cases} 
+    \label{eq:cstr:weight_ball:grad}
+\end{equation}
+Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.
+
+%  SECTION STABILITY ANALYSIS ==============================
+\section{Stability Analysis}\label{sec:stability}
+
+Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+The following lemma is introduced for the stability analysis.
+
+\begin{lem} 
+    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i,\ \forall i\in[k,\cdots, i+1]$, remain bounded.
+    \label{lem:cstr:grad:bound}
+\end{lem}
+
+\begin{proof}
+
+The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
+\begin{equation}
+    \pptfrac{c_j}{\estwth_i} 
+    = 
+    \pptfrac{c_j}{\mv\tau} 
+    \pptfrac{\mv\tau}{\estNN} 
+    \pptfrac{\estNN}{\estwth_i}
+\end{equation}
+where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
+From the linear mapping in \eqref{eq:linear:map}, $\mv\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
+By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
+The convex function has a bounded derivative with respect to $\mv\tau$, since $\mv\tau$ is a bounded variable (\ie $\pptfrac{c_j}{\mv\tau}$ is bounded). 
+Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
+This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
+Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+
+\end{proof}
+
+The following theorem shows that $\estwth$ and $\fe$ are bounded.
+
+\begin{theorem}
+    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$.
+    This holds with the weight norm constraint \eqref{eq:cstr:weight_ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
+\end{theorem}
+
+\begin{proof}
+
+The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
+Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
+This assumption is reasonable, since even if the constraint is inactive 
+\MSRY{Add the reason why it is reasonable.}
+We consider two cases: (C$_1$) control input constraints are active, and (C$_2$) control input constraints are inactive.
+Using the fact that amplitude of the control input is only depends on $\estwth_k$ (\ie see \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$), the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
+
+\subsection*{Case (C$_1$): Control input constraints are active.}
+
+As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
+\begin{equation}
+    \Theta_{\fe}^{c_1} 
+    = 
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\text{min}}(\mm K)}
+    \right\}
+    .
+    \label{eq:invariant:c1:fe}
+\end{equation}
+
+To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
+Taking the time derivative of $V_2$ yields:
+\begin{equation}
+    \begin{aligned}
+        \ddtt  V_2 
+        =& 
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \textstyle\sum_{j\in\mathcal{I}}
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        =&
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        \\
+        &
+            +
+            \textstyle\sum_{
+                j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+            }
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        \underbrace{
+            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
+        }_{:=c_1\in\R_{>0}}
+        \norm{\fe}
+        \norm{\estwth_k}
+        \\
+        &
+        -
+        \underbrace{
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j 
+        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
+        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        c_1     
+        \norm{\fe}
+        \norm{\estwth_k}
         .
     \end{aligned}
-\end{equation}
-The calculation of $\pptfrac{\estNN}{\estwth}$ is introduced in \cite{Patil:2022aa}.
-In conclusion, the gradient of the objective with respect to the weights can be obtained as $\pptfrac{J}{\estwth} = {\mm \eta}^\top\mm \Lambda\mv\xi$ by simulating the sensitivity equation \eqref{eq.
-sen eq}.
-
-On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
-\begin{equation}
-    \pptfrac{c_{\theta_0}}{{\estwth}}
-    = 
-    \begin{bmatrix}
-        \mm 0_{\Xi_1\times 1} \\
-        2{\estwth}_0 
-    \end{bmatrix}
-    ,\quad
-    \pptfrac{c_{\theta_1}}{{\estwth}}    
-    = 
-    \begin{bmatrix}
-        2{\estwth}_1 \\
-        \mm 0_{\Xi_0\times 1}
-    \end{bmatrix}
-    .
-\end{equation}
-
-%  SECTION STABILITY ANALYSIS ==============================
-\section{Stability Analysis}\label{sec:stability}
-
-The following theorem proves the boundedness of the tracking error and the weight estimation of the weights.
-
-\begin{theorem}
-For the dynamical system in \eqref{eq.
-system dynamics 1}, the proposed controller \eqref{eq.
-control law} and the adaptation law \eqref{eq.
-adaptation laws} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\estwth}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
-ctrl stable condition}.
-\end{theorem}
-
-\begin{proof}
-The boundedness is proven from the last layer to the first layer.
-
-\subsection*{Step 1: Boundedness of ${\estwth}_1,{\mm \eta}_1,\mv \xi$}
-
-% For convenience, assume that all the constraints are in the active set without loss of generality.
-% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
-\color{black}
-Without loss of generality, assume that all the constraints are violated. 
-Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
-%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
-\color{black}
-
-The dynamics of $\mv \xi$ can be represented as
-\begin{equation}    
-    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
-    (
-        -\estwV_1^\top \estact+\mv w(t)
-    )
-    ,
-\end{equation}
-where $\mv w(t):= {\idealwV_1}^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
-The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
-\begin{equation}
-    \begin{aligned}
-        \ddtt{\mm \eta}_1 =
-        & 
-        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
-        ,
-        \\
-        \ddtt{{\estwth}}_1 =
-        & -\alpha 
-        (
-            {\mm \eta}_1^\top 
-            \mm \Lambda
-            \mv\xi
-            +
-            2\lambda_{\theta_1} {\estwth}_1
-        )
-        .
-    \end{aligned} 
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $\norm{-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )}$ is bounded.
-
-Define the Lyapunov function $V_1:=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
-Using a proposition $\estwV_1^\top \estact = \myvec(\estwV_1^\top \estact)=\myvec(\estact^\top \estwV_1) = (\mm I_{l_2}\otimes {\estact}^\top )\myvec(\estwV_1)=(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $V_1$ is
-\begin{equation}
-    \begin{aligned}
-        \ddtt \! {V}_1 
-        \!=\!& 
-        \tfrac{1}{2}
-        \mv \xi^\top 
-            (
-                \mm A_\xi^\top \mm P+\mm P\mm A_\xi
-            )
-        \mv \xi
-        \!+\!
-        \mv \xi^\top \mm P (
-            \!-\!\mm B_\xi\estwV_1^\top \estact +\mm B_\xi \mv w(t) 
-        )\\
-        &
-        -{\estwth}_1^\top 
-        \!
-        (
-            {\mm \eta}_1^\top \mm \Lambda \xi+2\lambda_{\theta_1} {\estwth}_1 
-        )
-        \\
-        =& 
-        -\tfrac{1}{2}
-        \mv \xi^\top \mm Q\mv \xi 
-        -
-        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1 
-        +\mv \xi^\top \mv \Delta
-        \\
-        &
-        -{\estwth}_1^\top {\mm \eta}_1^\top \mm \Lambda\mv \xi
-        -2\lambda_{\theta_1} {\estwth}_1^\top {\estwth}_1
-        \\
-        \le&
-        -
-        \tfrac{1}{2}
-        \lambda_\text{min}(\mm Q)\norm{\mv \xi} ^2
-        +\bar\Delta \norm{\mv \xi}
-        +\bar M\norm{\mv \xi} \norm{{\estwth}_1}
-        \\
-        &
-        -2\lambda_{\theta_1}
-        \norm{{\estwth}_1}^2
-        \\
-        \le& 
-        (
-            -\tfrac{1}{2}\lambda_\text{min}(\mm Q)
-            +{\tfrac{\bar M}{2}}
-        )
-        \norm{\mv \xi}^2 +\bar\Delta \norm{\mv \xi}
-        \\
-        &+ 
-        (
-        -2\lambda_{\theta_1} 
-        +\tfrac{\bar M}{2}
-        )
-        \norm{\tilde{\wth}_1}^2 
-        ,
-        \end{aligned}
-        \label{eq. lya 1}
-\end{equation}
-where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top )-\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.
-
-By defining $\mm P=\mm I_n$, the eigenvalues of $\mm Q=-\mm A_\xi^\top -\mm A_\xi$ are $2k_q$ and $2k_z$, since $\mm A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
-According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
-\begin{equation}
-    \text{min}(k_q,k_z)>\tfrac{\bar M}{2}
-    ,
-    \label{eq. ctrl stable condition}
-\end{equation}
-and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\tfrac{\bar M}{2}$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
-\begin{equation}
-    \Theta_\xi := 
+    \label{eq:lya2:dot}
+\end{equation}
+According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
+\begin{equation}
+    \Theta_{\theta_k}^{c_1} 
+    = 
     \left\{ 
-        \mv\xi\mid
-        \norm{\mv\xi}
+        \estwth_k \in \R^{\Xi_{k}} 
+        \mid 
+        \norm{\estwth_k} 
         \le 
         \tfrac{
-            2\bar \Delta
+            c_1(2\bar\tau+\bar\tau_d)
         }{
-            \lambda _\text{min}(\mm Q)-{\bar M}
-        } 
-    \right\}
-    ,
-\end{equation}
-and the weight estimation $\estwth_1$ is bounded in
-\begin{equation}
-    \Theta_{{\theta}_1} := 
-    \left\{ 
-        {\estwth_1} 
-        \mid
-        \norm{\estwth_1}
-        \le  
-        \bar\theta_1
-    \right\}
-    .
-\end{equation}
-The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\estwth}_1$ approaches the compact set $\Theta_{{\theta}_1}$, satisfying the constraint $c_{\theta_1}$.
-
-\subsection*{Step 2: Boundedness of ${\estwth}_0,{\mm \eta}_0$}
-
-The dynamics of ${\mm \eta}_0$ and ${\estwth}_0$ are represented as
-\begin{equation}
-    \begin{aligned}     
-        \ddtt{\mm \eta}_0 =& 
-        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
-        \\
-        \ddtt{{\estwth}}_0
-        =&
-        -\alpha 
-        (
-            {\mm \eta}_0^\top \mm \Lambda\mv \xi+2\lambda_{\theta_0} {\estwth}_0
-        )
-        .
-    \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $\norm{-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )}$ is bounded.
-To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=\tfrac{1}{2\alpha}{\estwth}_0^\top {\estwth}_0$ yields:
-\begin{equation}
-    \begin{aligned}
-        \ddtt {V}_0 =& 
-        -{\estwth}_0^\top (
-            {\mm \eta}_0\mm \Lambda\mv \xi 
-            +2\lambda_{\theta_0}{\estwth}_0
-        )
-        \\
-        \le &
-        \norm{{\estwth}_0} \norm{{\mm \eta}_0\mm \Lambda\mv \xi} 
-        -
-        2\lambda_{\theta_0} {\estwth}_0^\top {\estwth}_0
-        ,
-        \\
-        \le &
-        -2\lambda_{\theta_0} 
-        \norm{{\estwth}_0}^2 
-        + 
-        \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
-        \norm{{\estwth}_0}
-        .
-    \end{aligned}
-\end{equation}
-Then, the invariance set can be represented as 
-\begin{equation}
-    \Theta_{{\theta}_0} :=
-    \left\{
-        {\estwth}_0\mid\norm{\estwth_0}
-        \le
-        \tfrac{
-            \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
-        }{
-            2\lambda_{\theta_0}
+            \lambda_{\theta_k}\lambda_\text{min}(\mm K)
         }
@@
     .
-\end{equation}
-If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
-Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.
+    \label{eq:invariant:c1:wth}
+\end{equation}
+
+The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
+For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{c_1}$ is squeezed to a point.
+The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
+It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
+This drives $\estwth_k$ to the origin until the constraint is satisfied (\ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space).
+
+Therefore, the boundedness of $\estwth$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{c_1}$ and $\Theta_{\theta_k}^{c_1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
+
+\subsection*{Case (C$_2$): Control input constraints are inactive.}
+
+Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
+Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
+\begin{equation}
+    \begin{aligned}
+        \ddtt V_3
+        =&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\bar\tau_d\norm{\fe}
+        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
+        \\
+        &
+        -\estwth_k^\top (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        )
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(
+            \bar\tau_d+\norm{
+                \underbrace{
+                    \idealNN+\mv\epsilon
+                }_{=\mv\tau^*}
+            }
+        )
+        \norm{\fe}
+        \\
+        &
+        -\estNN^\top\fe 
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(\bar\tau_d+\bar\tau)
+        \norm{\fe}
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        .
+    \end{aligned}
+    \label{eq:lya3:dot}
+\end{equation}
+Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
+\begin{equation}
+    \Theta_{\fe}^{c_2}
+    =
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{
+            \bar\tau_d+\bar\tau
+        }{
+            \lambda_{\text{min}}(\mm K)
+        }
+    \right\}
+    .
+\end{equation}
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
+
+\hfill
+
+The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
+The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
+\begin{equation}
+    \ddtt \estwth_i 
+    =
+    -\alpha
+    (
+        \pptfrac{\estNN}{\estwth_i}^\top
+        \fe
+        +
+        \lambda_{\theta_i}\estwth_i
+        +
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j
+        \pptfrac{c_j}{\estwth_i}
+    )
+    .
+\end{equation}
+Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
+
+\hfill
+
+Finally, the filtered error $\fe$ and the estimated weights $\estwth$ are bounded and the imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
 
@@
     \caption{System model parameters.}
+    \label{table: error norm}
     \centering
-    \begin{tabular}{c c c c c }
+    \begin{tabular}{|c||c|c|c|c|}
     \hline
-    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
     \hline 
+    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
     \hline
-    $m_p$ & Mass of $p\textsubscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
+    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
     \hline
-    $l_p$  & Length of $p\textsubscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
+    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
     \hline
-    ${l_c}_p$ & COM of $p\textsubscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
+    $b_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
     \hline
-    $b_p$   & Viscous coef. of $p\textsubscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
-    \hline
-    ${f_c}_p$  & Friction coef. of $p\textsubscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
+    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
     \hline
@@
 
-The two-link manipulator model in \cite{Markus:2013aa} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
-In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in\{1,2\}$.
-The values of the system parameters are given in Table~\ref{table: system parameters}.
-The reference signal of $\q=[q_1,q_2]^\top $ is defined as follows:
-\begin{equation}
-    \qd
-    =
-    \begin{bmatrix}
-        {q_d}_1\\
-        {q_d}_2
-    \end{bmatrix}
-    = 
-    \begin{bmatrix}
-        +\cos(
-            \tfrac{\pi}{2}t
-        ) + 1 \\
-        -\cos(
-            \tfrac{\pi}{2}t
-        ) - 1 
-    \end{bmatrix}
-    .
-\end{equation}
-
-For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod) and the proposed controller with constrained optimization (NAC-CO).
-%%%%%%%%%%%%%%%%%%%%%
-The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters (\ie $L_2$ coefficient $\lambda$, $\epsilon$-modification coefficient $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively).
-The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \norm{\mv \xi}^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
-The parameter dependencies of the controllers were examined via various values of the parameters. 
-The values ranged from $0.001$ to $1$ across $10$ samples.
-%%%%%%%%%%%%%%%%%%%%%
-
-The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2}:= J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$.
-The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
-\begin{equation} 
-    \ddtt{{\estwth}} = 
-    \pptfrac{J_{L_2}}{\estwth}
-    =-\alpha
-    \left(
-        \pptfrac{J}{\estwth}
-        +
-        \lambda{\estwth}
-    \right)
-    .
-    \label{eq. adap L2}
-\end{equation}
-Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\estwth}$, where $\sigma\in\R_{>0}$.
-For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\norm{\tilde{\mv z}}{\estwth}$ is added to the adaptation law as follows:
-\begin{equation}
-    \ddtt{{\estwth}} = -\alpha
-    \left(
-        \pptfrac{J}{\estwth}
-        +
-        \rho\norm{\tilde {\mv z}}{\estwth}
-    \right)
-    ,
-    \label{eq. adap eMod}
-\end{equation}
-where $\rho\in\R_{>0}$.
-By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
-Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
-The adaptation law of NAC-CO is presented in \eqref{eq. adaptation laws}.
-Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.
-
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
-The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-\color{red}    
-    The validity of the selected number of nodes were demonstrated through experiments 
-\color{black}
-The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
-For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
-The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.
-
-\subsection{Results}
-
 \begin{figure}[!t]
     \centering
-    {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
-\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
-    \label{fig: Box-beard plot}
+    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
+    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
+    \label{fig: h func}
 \end{figure}
+
+% SYSTEM FIGURE AND TABLE
+% **********************************************************
+Four controllers were examined for a comparative study.
+The first was the Backstepping Controller (BSC), used as the baseline.
+The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro-adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC.
+While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints.
+The third was DNN-BSC augmented with an auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
+As a result, an approximation of the input norm constraint was used as an input bound constraint.
+Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework.
+The properties of these four controllers are summarized in Table \ref{table:controller}.
+%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).
 
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Quantitative comparison of square root of tracking ISE.}
+    \caption{Properties of the controllers used in simulation}
+    \label{table:controller}
     \centering
-    \begin{tabular}{c c c c }
+    \begin{tabular}{|c||c|c|c|}
     \hline
-     & \textbf{NAC-L2}\!&\!\textbf{NAC-eMod}\!&\!\textbf{NAC-CO} (proposed) 
-     \\
+    & \multicolumn{3}{c|}{Handling Capability}\\
     \hline
+    & System & Weight Norm & Input Norm\\
+    &  Uncertainty & Constraint & Constraint\\
     \hline 
-    Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
+    BSC     & X & X & X\\
     \hline
-    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
+    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
+         &  & (by projection) & \\
+    \hline
+    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
+       &  & (by projection) &  (by aux. system)\\
+       % &  & & linearized constraint)\\
     % \hline
-    Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
+    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
+    %    &  & (by projection) &  system for \\
+    %    &  & & linearized constraint)\\
     \hline
-    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
-    % \hline
-    Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
+    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
+         &  & (by optimization) & (by optimization)\\
     \hline
     \end{tabular}
-    \label{table: error norm}
 \end{table}
 
-As shown in Fig.~\ref{fig: Box-beard plot}, the maximum square root of the tracking ISE of NAC-CO is smaller than the minimum square root of the tracking ISEs of NAC-L2 and NAC-eMod for all variations in the parameters.
-This is because NAC-L2 and NAC-eMod bias the weights to the origin due to the presence of stabilizing functions.
-A quantitative comparison of the square root of the tracking ISE is provided in Table~\ref{table: error norm}.
+% \begin{table}
+% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
+% \centering
+% {\begin{tabular}{cc}\textcolor{black}ine
+% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
+% Rated power & 3 kW\\
+% Rated speed & 4500 RPM\\
+% Rated torque & 6.4 Nm\\
+% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
+% $I_{max}$ & 15 A \\
+% $V_{dc}$ & 100 V\\
+% $R_s$ & 0.34 $\Omega$\\
+% $P$ & 3\\
+% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
+% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
+% \multirow{2}{*}{Controller} & TMS320F28377D\\
+% & (Texas Instrument) \\
+% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
+%  & (Infineon Technologies)
+% \\\textcolor{black}ine
+% \end{tabular}}
+% \end{table}
+
+% \begin{table}[!t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Common Parameters of Selected Controllers.}
+%     \label{table: error norm}
+%     \centering
+%     \begin{tabular}{|c||c|c|c|c|c|c|}
+%     \hline
+%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
+%     \hline 
+%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
+%     \hline
+%     \end{tabular}
+%     \label{table: control parameters}
+% \end{table}
+
+% **** CM1,2 control law *****
+The BSC used the control law defined in \eqref{eq. desired control} with $\hat f=[0,0]^\top$. Since BSC did not consider the unknown system dynamics, the approximation term $\hat f$ was set to zero.
+%CM1 has the following control gains and design parameters: $k_s=5,{k_z}=5, M_0=I_2, C_0=I_2, G_0=[0,0]^\top  $.
+% Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^\top$. 
+The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \estNN$.
+The adaptation law for DNN-BSC, as presented in \cite{Patil:2022aa}, was defined by
+\begin{equation}\label{eq:projection}
+\dot {\estwth}= \myproj_{\Omega}[\alpha  (\partial \estNN/\partial \estwth)M_0^{-1}{\tilde z}],
+\end{equation}
+where $\myproj_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{Krstic:1995aa}, which projects an input vector onto a convex set $\Omega$.
+The convex set was defined as ${\Omega}:= \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i:= \{\estwth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
+cstr weight ball}.
+% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\myproj_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\estwth$-space.).
+% **** CM3 control law *****
+
+The control law for DNN-BSC-A was the same as DNN-BSC, but with an auxiliary system to compensate for control input violations.
+Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq.
+cstr input ball}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq.
+cstr input saturation} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
+The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
+%considering $h(\cdot)$, saturated control input is defined as $s(\tau):= \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
+The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\R^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} =
+\tau_{(i)}-\text{sat}(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
+% s(\tau)-\tau$.
+The auxiliary state variables were used in the adaptation law \eqref{eq:projection} by substituting ${\tilde z}$ with ${\tilde z}+\zeta$.
+
+% **** CoNAC control law *****
+The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq.
+approximated control}.
+The update rates for the multipliers were set as $\beta_{j}=0.1$.
+The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
+
+For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
+Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
+The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ (from Eq.
+\eqref{eq.
+h func}).
+The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
+The sampling time of the simulations was selected as $T_s=10^{-4}$.
+% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+% The other parameters for CM1 to CoNAC were selected as listed in Table.~\ref{table: control parameters}.
+The same values were assigned across all the controllers for the common parameters for a fair comparison.
+
+% **********************************************************
+% SIMULATION FIGURES
+\begin{figure*}[!t]
+    \centering
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
+        \label{fig: tracking_CM1}}
+    \hfill
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
+        \label{fig: tracking_CM2}}
+    \vfill
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
+        \label{fig: tracking_CM3}}
+    \hfill
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
+        \label{fig: tracking_CoNAC}}
+    \caption{Comparison of the tracking performance across the selected controllers.}
+    \label{fig: tracking}
+\end{figure*}
+
+\begin{figure*}[!t]
+    \centering
+        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
+        \label{fig: control_CM1}}
+    \hfill
+        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
+        \label{fig: control_CM2}}
+    \vfill
+        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
+        \label{fig: control_CM3}}
+    \hfill
+        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
+        \label{fig: control_CoNAC}}
+    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
+    \label{fig: control}
+\end{figure*}
 
@@
     \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
-        \label{fig: weight NAC-L2}}
-    \vspace{.1mm}
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
-        \label{fig: weight NAC-eMod}}
-    \vspace{.1mm}
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
-        \label{fig: weight NAC-CO}}
-    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: weight}
+    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
+    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
+    \label{fig: ball control}}
 \end{figure}
 
-\begin{figure}[!t]      
+\begin{figure*}[!t]
     \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
-        \label{fig: error NAC-L2}}
-    \vspace{.1mm}
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
-        \label{fig: error NAC-eMod}}
-    \vspace{.1mm}
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
-        \label{fig: error NAC-CO}}
-    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: error}
-\end{figure}
-
-For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in\{0.001,0.45,1\}$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
-As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\estwth}$.
-Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
-Since the weight norm is decreased, NAC-L2 cannot generate sufficient control inputs, resulting in a larger square root of tracking ISE, as shown in Fig.~\ref{fig: error NAC-L2}.
-
-On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
-This is because the stabilizing function $-\alpha\rho\norm{\tilde {\mv z}}{\estwth}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
-However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (\ie smaller weight norms are observed as $\rho$ increases.).
-Therefore, similar to NAC-L2, the biased weights produce insufficient control input, resulting in a relatively larger square root of tracking ISE than that of NAC-CO, as described in Table \ref{table: error norm}.
-
-Finally, the weight norm of NAC-CO is smaller than those of NAC-L2 and NAC-eMod, as shown in Fig.~\ref{fig: weight NAC-CO}, with better tracking performance.
-Even if a large $\beta_j$ is provided, NAC-CO can adjust the adaptation direction to satisfy the weight norm constraints faster, according to \eqref{eq. adaptation law L}.
-Therefore, the lowest dependency on the update rate $\beta_j$ is observed in NAC-CO, as shown in Fig.~\ref{fig: weight NAC-CO} and Fig.~\ref{fig: error NAC-CO}.
-Note that $\beta_j$ of NAC-CO is the update rate for the Lagrange multipliers, whereas $\lambda$ and $\rho$ are the coefficients of the stabilizing function that generates the biases of the weights.
-However, considering the implementation using a digital computer, excessively large $\beta_j$ values should be avoided.
-
-The details of the satisfaction of the weight norm constraints are shown in Fig.~\ref{fig: weight and multiplier} for NAC-CO with $\beta_j=0.001$.
-As the weight norms of each layer reach the constraint boundary, the corresponding Lagrange multipliers are generated.
-Using the Lagrange multipliers, the adaptation direction is adjusted toward the constraint satisfactory point.
-The Lagrange multipliers disappear when the constraints are satisfied, and the weights are adapted to optimize the original objective function without weight bias.
-
-\begin{figure}[!t]      
-    \centering
-        \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
-        \label{fig: weight per layer NAC-CO}}
-    \vspace{.1mm}
-        \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
-        \label{fig: multipliers NAC-CO}}
-        \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
+        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
+        \label{fig: multiplier_CoNAC}}
+    \hfill
+        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
+        \label{fig: weight_CM2}}
+    \vfill
+        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
+        \label{fig: weight_CM3}}
+    \hfill
+        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
+        \label{fig: weight_CoNAC}}       
+    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
     \label{fig: weight and multiplier}
-\end{figure}
-
-Furthermore, it is important to note that NAC-CO shows enhanced tracking performance with smaller weights than NAC-L2 and NAC-eMod.
-This implies that the weights in NAC-CO approach the different local optimal solution points from those of NAC-L2 and NAC-eMod.
-Therefore, if the physical analysis of the system is available to predict the feasible maximum control inputs, NAC-CO can find the local optimal solution without unnecessarily large control inputs by imposing proper weight norm constraints.
+\end{figure*}
+% SIMULATION FIGURES
+% **********************************************************
+
+\subsection{System Uncertainty Handling}
+
+The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
+To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties.
+As a result,
+%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
+%the parameters of CM1 are poorly tuned, 
+BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.
+
+By leveraging the DNN to compensate for the lumped system uncertainty within the BSC, DNN-BSC achieved improved tracking performance compared to BSC, as seen in Fig.~\ref{fig: tracking_CM2}.
+Fig.~\ref{fig: tracking_CM3} shows that DNN-BSC-A enhanced tracking performance for $q_2$, but tracking for $q_1$ remained unsatisfactory due to incomplete constraint handling, which will be discussed in detail in Section \ref{sec:sim_cnst}.
+%By compensating the uncertain terms the control input of CM2 in Fig.~\ref{fig: control_CM2} is saturated.
+
+Finally, CoNAC, which directly approximates the stabilizing control law along with the compensation term, demonstrated satisfactory tracking performance across both states, as illustrated in Fig.~\ref{fig: tracking_CoNAC}.
+
+\subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}
+
+The resulting control input $\tau$ and physically saturation control input $h(\tau)$ for the selected controllers are shown in Fig.~\ref{fig: control}.
+As illustrated in Fig.~\ref{fig: control_CM1}, BSC did not violate the input norm constraint (\ie $\tau = h(\tau)$).
+However, in DNN-BSC, the added compensation term from the DNN caused violations of the input norm constraint (\ie $\tau > h(\tau)$) at several points; see Fig.~\ref{fig: control_CM2}.
+This failure to account for the input norm constraint led to oscillations in the control input $\tau$.
+The DNN adaptation process attempted to increase the weights to reduce the residual errors that were not constrained by saturation, but after saturation ceased, the control input had to rapidly adjust back to realistic levels, leading to oscillatory behavior.
+Such high-frequency oscillations may induce instability in the control system or cause fatigue in the actuators.
+
+On the other hand, both DNN-BSC-A and CoNAC successfully handled their imposed input constraints, as shown in Fig.~\ref{fig: control_CM3} and Fig.~\ref{fig: control_CoNAC}, respectively, without causing notable oscillations in the control input $\tau$ even after the input constraint was activated.
+However, the tracking performance of DNN-BSC-A was lower than that of DNN-BSC and CoNAC, as the auxiliary system used in DNN-BSC-A approximated the input norm constraint with an input bound constraint, creating a rectangular constraint in the $\tau$-space (see Fig.~\ref{fig: ball control}).
+In contrast, CoNAC satisfied the nonlinear input norm constraint and produced the physically maximum control input, resulting in improved tracking performance.
+
+It is also important to note that the control input trajectory in DNN-BSC-A depends on the dynamics of the auxiliary system.
+The auxiliary system regulates the violated control input after sufficient auxiliary state $\zeta$ is generated to compensate for the violation.
+This can be observed in Fig.~\ref{fig: ball control}, where DNN-BSC-A exhibited minor violations of the input bound constraint.
+In contrast, CoNAC satisfied the constraint without being affected by such dynamics, as its Lagrange multiplier adjusted as soon as the constraint was violated.
+
+%Meanwhile, CM2 and CM3 is based on BSC, and the desired controller $\tau^*$ of CoNAC is based on the BSC which may produce larger control input by canceling the stabilizing system dynamics.
+%Therefore, CM2, CM3, and CoNAC produced the saturated control input.
+%These control results show why the control saturation should be handled.
+
+\subsection{Weight Norm Constraint Handling}
+
+The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}.
+All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.
+
+IN DNN-BSC, as shown in Fig.~\ref{fig: weight_CM2}, the weight norm of the last layer (\ie $\Vert {{{\hat \wth }_2}} \Vert$) fluctuated significantly over time, proportional to the control input norm.
+This is because the last layer’s weights directly determine the control input.
+When the control input violated the input norm constraint, the last layer’s weight norm hit the boundary and stayed there due to the projection operator.
+However, the projection operator only responded to violations without considering optimality or behavior.
+%In the case of CM2 which does not consider the control input constraint, the weight norm of the last layer reaches the maximum weight norm value, when the control is saturated.
+%It is because the weights get increased to produce larger control input to reduce the tracking error of $q_2$.
+(\ie the maximum magnitude of the control input depends on the weight norm of the last layer, since the activation function is bounded.)
+
+In DNN-BSC-A, none of the weight norms reached their boundaries, as shown in Fig.~\ref{fig: weight_CM3}.
+This was due to the auxiliary system, where the auxiliary state $\zeta$ reduced the control input, ensuring it stayed within the input constraint.
+
+In CoNAC, all weight norms complied with the imposed constraints through the constrained optimization approach, as illustrated in Fig.\ref{fig: weight_CoNAC}.
+When any weight norm approached its upper limit, the Lagrange multiplier was promptly activated to steer the weight adaptation direction towards a constraint-satisfactory point (see Fig.\ref{fig: multiplier_CoNAC}).
+Notably, the weight norms of the first and second layers ($\Vert {{{\hat \wth }_0}} \Vert$ and $\Vert {{{\hat \wth }_1}} \Vert$) remained nearly constant throughout the control period.
+The weight norm of the last layer $\Vert {{{\hat \wth }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint.
+This quasi-static behavior of the weight norm (\ie $d{\estwth}/dt=-\alpha\partial L/\partial \estwth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
+However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds.
+This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
+%(\ie $\partial J/\partial\estwth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\estwth} c_j)$.
+%, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.
+
+The overall weight norms of CoNAC were larger than those of DNN-BSC and DNN-BSC-A, since CoNAC approximated the entire stabilizing control law, whereas DNN-BSC and DNN-BSC-A only approximated the system uncertainty term within the BSC framework.
+
+%Because the simulation is implemented in a digital computer, the multipliers repeat to disappear and be generated, since the constraints are satisfied and violated in the digital process.
+
+%\subsection{Analysis of the Neural Network}
+
+%Generally, the existing literature states that the maximum norms of the weights should be sufficiently large (\ie $\bar\wth_i \gg 0$) since the designer does not know where the global optimal point of the weights is.
+%However, using the physical prior knowledge of the system, one can guess the proper value of the maximum norm, since the magnitude of the control input depends on the last layer's weights due to the bounded activation function.
+%Furthermore, the simulation study shows that the selected controllers have sufficiently good performances with the small maximum weight norms.
+%It means that the local optimal point of the weights are more effective for the stability analysis and the limitating the control input's amplitude.
+
+%Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
+%However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}.
+(\ie the weight updates are smaller as its layer is closer to the input layer.)
+%To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
 
@@
 
-%
-In this paper, a neuro–adaptive control method is proposed for uncertain Euler‒Lagrange systems, ensuring weight boundedness.
-Adaptation laws are derived by formulating a constrained optimization problem with weight norm constraints.
-The boundedness of the tracking error and the weight estimation are analyzed via Lyapunov analysis.
-The simulation results demonstrate that the proposed controller outperforms the existing methods in terms of tracking performance and parameter dependency.
-As further work, the state constraints for safety will be handled, ensuring stability.
-%
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{APPENDIX}
-
-% Appendixes should appear before the acknowledgment.
-
-% \section*{ACKNOWLEDGMENT}
-
-% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ.
-Avoid the stilted expression, ÒOne of us (R.
-B.
-G.) thanks .
+This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
+
+The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds.
+By formulating these constraints as part of the optimization process, CoNAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
+
+Simulation results validated the superior performance of CoNAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+CoNAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
+
+Future work may extend this approach to address constraints on both the system inputs and states, further enhancing the flexibility and robustness of neuro-adaptive control systems using constrained optimization.
+
+\begin{appendices}
+
+\section{Constraint Candidates}\label{sec:appen:cstr}
+
+This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller.
+
+\subsection{Input Bound Constraint}\label{sec:appen:input_bound_cstr}
+
+Most physical systems have control input limits due to electrical and mechanical limitations.
+These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+\begin{equation}
+    \begin{aligned}
+        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
+        \\
+        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+    \end{aligned}
+    \label{eq. cstr input saturation}
+\end{equation}
+with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
+% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
+The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
+\begin{equation}
+    \begin{aligned}
+        {\partial \boldsymbol c_{\overline \tau} \over \partial \estwth}
+        =& 
+        \begin{bmatrix}
+            (\partial c_{\overline \tau_1}/\partial \estwth)^\top \\
+            \vdots \\
+            (\partial c_{\overline \tau_n}/\partial \estwth)^\top
+        \end{bmatrix}
+            = -{\partial \estNN\over\partial\estwth}
+            \\
+        =&
+        -\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
+        , 
+        \\
+        {\partial \boldsymbol c_{\underline\tau} \over \partial \estwth}         
+        :=
+        & 
+        \begin{bmatrix}
+            (\partial c_{\underline\tau_1}/\partial \estwth)^\top \\
+            \vdots \\
+            (\partial c_{\underline\tau_n}/\partial \estwth)^\top
+        \end{bmatrix}
+        = +{\partial \estNN\over\partial\estwth}
+        \\
+        =&
+        +\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \cdots &
+            (
+            \cdot
+            )
+        \end{bmatrix} 
+        &
+        \in
+        \mathbb R^{n\times \Xi}
         .
-.Ó  Instead, try ÒR.
-B.
-G.
-thanksÓ.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \end{aligned}
+    \label{eq. nabla input sat}
+\end{equation}
+
+\subsection{Input Norm Constraint}\label{sec:appen:input_norm_cstr}
+
+Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
+Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
+This can be captured by the following inequality constraint:
+\begin{equation}
+    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
+    \label{eq. cstr input ball}
+\end{equation}
+with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
+This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
+% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
+The gradients of $c_{u}$ with respect to $\estwth$ are given by
+\begin{equation}
+    {\partial \boldsymbol c_{u} \over \partial \estwth}
+    = -\sum_{i=1}^n 2\tau_{(i)} 
+    \bigg(
+        \myrow_i
+        \bigg(
+            -{\partial \estNN\over\partial\estwth}
+        \bigg)
+    \bigg)^\top  
+    = \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
+    \in \mathbb R^{\Xi}.
+    \label{eq. nabla input ball}
+\end{equation}
+It should be noted that constraints \eqref{eq.
+cstr input saturation} and \eqref{eq.
+cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
+nabla input sat} and \eqref{eq.
+nabla input ball} are linearly dependent, violating the LICQ condition.
+
+\end{appendices}
+
+%  BIBLIOGRAPHY ============================================
 {\footnotesize
 \bibliographystyle{ieeetr}
-    \bibliography{dding_template/refs}
-}
+% \bibliography{}
+\bibliography{\template/refs}}
 

### 2025-03-26 manuscript.tex
first commit to GitHub
final touch; submit to ECC

--- 2025-03-25 manuscript.tex
@@
 \def\pub{false} % true for publication, false for draft
-\newcommand*{\template}{dding_template}
+\newcommand*{\template}{template}
 \input{\template/preamble/preamble_conf.tex}
@@
 % One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs as control compontnets is that the outputs of NNs are not predictable.
+One of the common issues in using NNs as control components is that the outputs of NNs are not predictable.
 This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
-This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.
+This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control components from NNs.
 
@@
 The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
-For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
+For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denotes the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
 
@@
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The validity of the selected number of nodes were demonstrated through experiments 
+The validity of the selected number of nodes were demonstrated through experiments.
 The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
@@
     \bibliographystyle{ieeetr}
-    \bibliography{dding_template/refs}
+    \bibliography{\template/refs}
 % }

### 2025-03-29 manuscript.tex
table change
new table

--- 2025-03-26 manuscript.tex
@@
 We introduce the following properties:
-\begin{prop} \cite{Lewis:1998aa}
+\begin{prop} 
     The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
@@
 
-\begin{prop} \cite{Lewis:1998aa}
+\begin{prop} 
     The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
@@
 
-The DNN architecture $\NN_k = \NN(\q_{NN};\wth)$ can be recursively represented as follows:
+The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
 \begin{equation}
@@
 \begin{remark}
-    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in practice including the origin.
+    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex in practice including the origin.
     Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
@@
         \\
-        0,
+        \mv{0},
         &
@@
         -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
-        +\fe^\top \estNN
         +(\bar\tau_d+\bar\tau)
@@
 The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
-The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$, and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
 %This model contains terms of gravity and friction in its mechanical system.
@@
 %and can be considered as the disturbance of the system.
-The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for ${q}=[q_1,q_2]^\top$ was defined as
+The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for $\q=[q_1,q_2]^\top $ was defined as
 \begin{equation}
@@
     \caption{System model parameters.}
-    \label{table: error norm}
     \centering
-    \begin{tabular}{|c||c|c|c|c|}
-    \hline
-    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
-    \hline 
-    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
-    \hline
-    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
-    \hline
-    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
-    \hline
-    $b_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
-    \hline
-    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
+    \begin{tabular}{c m{11em} c c c }
+    \hline
+    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+    \hline
+    \hline 
+    $m_p$ & Mass of $p\textsuperscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
+    \hline
+    $l_p$  & Length of $p\textsuperscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
+    \hline
+    ${l_c}_p$ & COM of $p\textsuperscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
+    \hline
+    $b_p$   & Viscous coef. of $p\textsuperscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
+    \hline
+    ${f_c}_p$  & Friction coef. of $p\textsuperscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
     \hline
@@
 
-% **********************************************************
-% SIMULATION FIGURES
-\begin{figure*}[!t]
-    \centering
-        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
-        \label{fig: tracking_CM1}}
-    \hfill
-        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
-        \label{fig: tracking_CM2}}
-    \vfill
-        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
-        \label{fig: tracking_CM3}}
-    \hfill
-        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
-        \label{fig: tracking_CoNAC}}
-    \caption{Comparison of the tracking performance across the selected controllers.}
-    \label{fig: tracking}
-\end{figure*}
-
-\begin{figure*}[!t]
-    \centering
-        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
-        \label{fig: control_CM1}}
-    \hfill
-        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
-        \label{fig: control_CM2}}
-    \vfill
-        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
-        \label{fig: control_CM3}}
-    \hfill
-        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
-        \label{fig: control_CoNAC}}
-    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
-    \label{fig: control}
-\end{figure*}
-
-\begin{figure}[!t]
-    \centering
-    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
-    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
-    \label{fig: ball control}}
-\end{figure}
-
-\begin{figure*}[!t]
-    \centering
-        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
-        \label{fig: multiplier_CoNAC}}
-    \hfill
-        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
-        \label{fig: weight_CM2}}
-    \vfill
-        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
-        \label{fig: weight_CM3}}
-    \hfill
-        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
-        \label{fig: weight_CoNAC}}       
-    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
-    \label{fig: weight and multiplier}
-\end{figure*}
-% SIMULATION FIGURES
-% **********************************************************
-
 \subsection{System Uncertainty Handling}
 
+\begin{comment}
     The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
@@
     %To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
+\end{comment}
 
@@
     \begin{aligned}
-        {\partial \boldsymbol c_{\overline \tau} \over \partial \estwth}
+        \pptfrac{\boldsymbol c_{\overline \tau}}{\estwth}
         =& 
-        \begin{bmatrix}
-            (\partial c_{\overline \tau_1}/\partial \estwth)^\top \\
-            \vdots \\
-            (\partial c_{\overline \tau_n}/\partial \estwth)^\top
-        \end{bmatrix}
-            = -{\partial \estNN\over\partial\estwth}
-            \\
-        =&
+        % \begin{bmatrix}
+        %     \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
+        %     \vdots \\
+        %     \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
+        % \end{bmatrix}
+        = 
+            -\pptfrac{\estNN}{\estwth}
+        %     \\
+        % =&
+        =
         -\begin{bmatrix}
             (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
-            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
-            \cdots &
+            \!\cdots\! &
             (
@@
         \end{bmatrix} 
-        &
         \in
@@
         \\
-        {\partial \boldsymbol c_{\underline\tau} \over \partial \estwth}         
+        \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
         :=
         & 
-        \begin{bmatrix}
-            (\partial c_{\underline\tau_1}/\partial \estwth)^\top \\
-            \vdots \\
-            (\partial c_{\underline\tau_n}/\partial \estwth)^\top
-        \end{bmatrix}
-        = +{\partial \estNN\over\partial\estwth}
-        \\
-        =&
+        % \begin{bmatrix}
+        %     \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
+        %     \vdots \\
+        %     \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
+        % \end{bmatrix}
+        = 
+        +\pptfrac{\estNN}{\estwth}
+        % \\
+        % =&
+        =
         +\begin{bmatrix}
@@
             % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
-            \cdots &
+            \!\cdots\! &
             (
@@
 \begin{equation}
-    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
+    c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
     \label{eq. cstr input ball}
@@
 \begin{equation}
-    {\partial \boldsymbol c_{u} \over \partial \estwth}
-    = -\sum_{i=1}^n 2\tau_{(i)} 
-    \bigg(
+    \pptfrac{\boldsymbol c_{u}}{\estwth}
+    \!=\! 
+    -\textstyle\sum_{i=1}^n 2\tau_{(i)} 
+    \left(
         \myrow_i
-        \bigg(
-            -{\partial \estNN\over\partial\estwth}
-        \bigg)
-    \bigg)^\top  
-    = \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
+        (
+            -\pptfrac{\estNN}{\estwth}
+        )
+    \right)^\top  
+    \!=\! 
+    \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
     \in \mathbb R^{\Xi}.

### 2025-03-31 manuscript.tex
minor changes

--- 2025-03-26 manuscript.tex
@@
     *This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No.
-KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}
+KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (RS-2025-
+00554087). \it{(Corresponding author: Kyunghwan Choi)}
 }% <-this % stops a space
@@
 \thanks{
-    $^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
+    $^{2}$Jiyun Kim is with the Department of AI Convergence, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
         {\tt\small jiyun6606@gm.gist.ac.kr}
@@
     \hline 
-    $m_p$ & Mass of $p\textsubscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
+    $m_p$ & Mass of $p\textsuperscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
     \hline
-    $l_p$  & Length of $p\textsubscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
+    $l_p$  & Length of $p\textsuperscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
     \hline
-    ${l_c}_p$ & COM of $p\textsubscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
+    ${l_c}_p$ & COM of $p\textsuperscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
     \hline
-    $b_p$   & Viscous coef. of $p\textsubscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
+    $b_p$   & Viscous coef. of $p\textsuperscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
     \hline
-    ${f_c}_p$  & Friction coef. of $p\textsubscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
+    ${f_c}_p$  & Friction coef. of $p\textsuperscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
     \hline

### 2025-03-31 manuscript.tex
minor update for jiyun

@@
 \thanks{
-    $^{2}$Jiyun Kim is with the Department of AI Convergence, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
-        {\tt\small jiyun6606@gm.gist.ac.kr}
+    $^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small jiyun6606@gm.gist.ac.kr}
 }%

### 2025-04-02 manuscript.tex
real FINAL

@@
 
-\def\pub{false} % true for publication, false for draft
+\def\pub{true} % true for publication, false for draft
 \newcommand*{\template}{template}
@@
     % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
-    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
+    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of $\mm A\in\R^{n\times n}$.
     \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
@@
 This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
-Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa} and deep NN (DNN) \cite{Patil:2022aa}.
+Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa}, and deep NN (DNN) \cite{Patil:2022aa}.
 The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.
@@
 Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
-In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
+In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, thereby making the invariance set of the estimation error of the weights.
 The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
@@
         \tfrac{1}{2}
-        \mv \xi^\top \mm \Lambda \mv \xi
+        \mv \xi^\top \mm \Lambda \mv \xi,
         \\ \\
@@
         \tfrac{1}{2}
-        \lambda_\text{min}(\mm Q)\norm{\mv \xi} ^2
+        \lambda_{\min}(\mm Q)\norm{\mv \xi} ^2
         +\bar\Delta \norm{\mv \xi}
@@
         (
-            -\tfrac{1}{2}\lambda_\text{min}(\mm Q)
+            -\tfrac{1}{2}\lambda_{\min}(\mm Q)
             +{\tfrac{\bar M}{2}}
@@
 \begin{equation}
-    \text{min}(k_q,k_z)>\tfrac{\bar M}{2}
+    \min(k_q,k_z)>\tfrac{\bar M}{2}
     ,
@@
         }{
-            \lambda _\text{min}(\mm Q)-{\bar M}
+            \lambda _{\min}(\mm Q)-{\bar M}
         } 
@@
     \centering
-    \includegraphics[width=0.8\linewidth]{fig/RobotModel.drawio.png}
+    \includegraphics[width=0.9\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
     \label{fig: manipulator}
+    \vspace{-4mm}
 \end{figure}
@@
 
-For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod) and the proposed controller with constrained optimization (NAC-CO).
+For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod), and the proposed controller with constrained optimization (NAC-CO).
 %%%%%%%%%%%%%%%%%%%%%
@@
 The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The validity of the selected number of nodes were demonstrated through experiments.
+The validity of the selected number of nodes was demonstrated through experiments.
 The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
@@
     {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
-\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
+\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod, and NAC-CO across various parameter values.}
     \label{fig: Box-beard plot}

### 2025-04-03 manuscript.tex
add comparative study

--- 2025-03-31 manuscript.tex
@@
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
-
-%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper
-
-\IEEEoverridecommandlockouts                              % This command is only needed if 
-                                                          % you want to use the \thanks command
-
-\overrideIEEEmargins                                      % Needed to meet printer requirements.
-
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
-
+\documentclass[lettersize,journal]{IEEEtran}
+% code
+
+\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}
+
+% \usepackage{balance}
 \def\pub{false} % true for publication, false for draft
@@
 
-\title{\LARGE \bf
-Imposing a Weight Norm Constraint for Neuro–Adaptive Control
+\newcommand*{\fe}{\mv{r}}
+
+\begin{document}
+\title{
+Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
+%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
 }
 
-\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{3}$% <-this % stops a space
-\thanks{
-    *This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No.
-KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (RS-2025-
-00554087). \it{(Corresponding author: Kyunghwan Choi)}
-}% <-this % stops a space
-\thanks{
-    $^{1}$Myeongseok Ryu is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr}
+\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
+~Vol.~00, No.~0, Month~2024
 }%
-\thanks{
-    $^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small jiyun6606@gm.gist.ac.kr}
-}%
-\thanks{
-    $^{3}$Kyunghwan Choi was with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, Republic of Korea.
-He is currently with the Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small kyunghwan.choi90@gmail.com}
-}%
-}
-
-\begin{document}
+{How to Use the IEEEtran \LaTeX \ Templates}
 
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{abstract}
-
-In this paper, a neuro–adaptive controller with weight norm constraints is proposed for uncertain Euler‒Lagrange systems. 
-The boundedness of the weights in the neuro–adaptive controller design is important to prevent excessively large control inputs and system instability. 
-To ensure the boundedness of the weights, the weight norm constraints are imposed as inequality constraints in the weight adaptation. 
-The adaptation law is derived based on the constrained optimization method. 
-The stability of the proposed controller is analyzed in the sense of Lyapunov, ensuring the boundedness of the tracking error and weight estimation. 
-For the comparative study, two benchmark controllers and the proposed controller were evaluated through a numerical simulation of a two-link manipulator system and compared in terms of tracking performance and parameter dependency.
-The comparative study verified that the proposed controller has better tracking performance and lower parameter dependency.
-
+    This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints.
+A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints.
+The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state.
+The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights.
+Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  SECTION INTRODUCTION ===================================
+\begin{IEEEkeywords}
+Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
+\end{IEEEkeywords}
 
@@
     \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
-    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ denotes a vector.
-    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
-    %     \mm A
-    %     := 
-    %     [a_{ij}]
-    %     _{
-    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
-    %     }\allowbreak\in\R^{n\times m}
-    %     $ denotes a vector and a matrix.
+    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
+        \mm A
+        := 
+        [a_{ij}]
+        _{
+            i\in[1,\cdots,n],j\in[1,\cdots ,m]
+        }\allowbreak\in\R^{n\times m}
+        $ denote a vector and a matrix.
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
@@
     % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
-    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
-    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
+    \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
+    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
 \end{itemize}
 
-\section{Introduction} \label{sec:intro}
-
-In various practical applications, Euler‒Lagrange systems generally have uncertainties due to their unknown and unmodeled dynamics.
-These uncertainties degrade the control performance index.
-Furthermore, if uncertainties dominate the system, they may lead to instability.
-By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{Tao:2003aa,Ioannou:2006aa}.
-Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.
-
-More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{Farrell:2006aa}.
-It generally uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
-This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
-Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa} and deep NN (DNN) \cite{Patil:2022aa}.
-The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.
-
-% The corresponding issue in the adaptive control is the parameter drift.
-% It refers to the weight divergence during the adaptation process, while the tracking error is bounded.
-
-% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
-One of the common issues in using NNs as control components is that the outputs of NNs are not predictable.
-This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
-This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control components from NNs.
-
-Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
-In \cite{Zhou:2023aa,Patil:2022aa}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
-However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
-Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
-In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights.
-The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
-However, they lack theoretical analysis regarding the optimality of the adapted weights.
-
-Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
-One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{Wu:2020aa,Lewkowycz:2020aa}.
-Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
-By regulating the magnitude of the weights, the stability of the adaptation process can be enhanced, and overfitting can be prevented.
-However, $L_2$-regularization also involves a trade-off between adaptation stability and the optimality of the weights.
-
-For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{Nocedal:2006aa} can be utilized.
-It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
-To the best of the authors’ knowledge, no prior work has utilized the constrained optimization method for the real-time weight adaptation of neuro–adaptive control satisfying weight boundedness.
-Therefore, the constrained optimization method could play a pivotal role in the neuro–adaptive control design addressing the weight boundedness.
-
-The main contributions of this study are as follows:
+%  SECTION INTRODUCTION ===================================
+\section{Introduction}
+
+\subsection{Background}
+
+\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
+These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
+In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
+These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
+To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.
+
+More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
+NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}.
+Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
+
+A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated. 
+Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
+
+However, two significant challenges persist in using NNs for adaptive control. 
+First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs. 
+When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. 
+Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{Esfandiari:2021aa}. 
+Failing to address these constraints can degrade control performance or even destabilize the system.
+
+Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
+he following section will provide a detailed review of the existing solutions to these challenges.
+
+\subsection{Literature Review}
+
+\subsubsection{Ensuring Weight Norm Boundedness}
+
+A common challenge in neuro-adaptive control is maintaining the boundedness of the NN weights to ensure stability. 
+In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly. 
+For example, in \cite{Zhou:2023aa,Griffis:2023aa,Patil:2022aa}, projection operators were used to constrain the weight norms to remain below predetermined constants. 
+However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values. 
+While this approach ensured that the NN remained stable, it did not necessarily result in optimal performance.
+
+In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{Ge:2002aa} and $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa}. 
+These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. 
+Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.
+
+\subsubsection{Satisfying Input Constraints}
+
+The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
+The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
+This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
+In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.
+
+To address input saturation, many studies introduced auxiliary systems. 
+These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
+For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
+This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.
+
+Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}.
+In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
+However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+
+\subsubsection{Limitations of Existing Approaches and Potential of Constrained Optimization}
+
+Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations. 
+Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
+Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.
+
+To overcome these limitations, constrained optimization offers a promising approach. 
+By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (\eg tracking error) subject to both weight norm and input constraints.
+Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.
+
+In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{Evens:2021aa} and the Alternating Direction Method of Multipliers (ADMM) \cite{Wang:2019aa,Taylor:2016aa}, have been used to train NNs offline.
+These methods impose constraints to address issues like gradient vanishing in backpropagation. 
+However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation. 
+This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.
+
+\subsection{Contributions}
+
+The main contributions of this study are listed as follows:
 \begin{itemize}
-    \item The neuro–adaptive control problem is reformulated into a constrained optimization problem by treating the satisfaction of the weight boundedness as inequality constraints.
-    \item The adaptation law is derived based on the constrained optimization method to minimize the objective function while satisfying the weight norm constraints.
-    \item The stability of the adaptation laws is analyzed via Lyapunov stability analysis, which ensures the boundedness of the tracking error and weight estimation.
+    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
+    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
+The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
+    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
+    %, enabling more precise real-time adaptation.
 \end{itemize}
 
-The remainder of this paper is organized as follows:
-Section \ref{sec: Problem Formulation} presents the target-constrained system and control objective.
-Section \ref{sec:ctrl design} introduces the proposed controller and the adaptation law. 
-Section \ref{sec:stability} examines the stability of the proposed controller.
-A comparative study of the three selected controllers, including the proposed controller through numerical simulation, is reported in Section \ref{sec:sim}.
-Finally, Section \ref{sec:conclusion} concludes the paper by presenting future work.
+\subsection{Organization}
+
+The remainder of this paper is organized as follows. 
+Section \ref{sec:Problem Formulation} presents the target system and control objective.
+Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
+In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
+Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
+Section \ref{sec:stability} analyzes the stability of the proposed controller.
+A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
+Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
+% The appendices provide the proof of the lemma used in the stability analysis.
 
 %  SECTION PROBLEM FORMULATION ============================
-\section{Problem Formulation}\label{sec: Problem Formulation}
+\section{Problem Formulation}\label{sec:Problem Formulation}
 
@@
 
-Consider an uncertain Euler‒Lagrange system modeled as
-\begin{equation}
-    \mm M\ddq + \mm V_m\dq+ \mm G + \mm F 
-    =
-    \mv\tau 
-    ,
-    \label{eq. system dynamics 1}
-\end{equation}
-where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
-Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V}_m$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
-\begin{equation}
-    \widehat{\mm M}\ddq+\widehat{\mm V}_m\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
-    ,
-    \label{eq. system dynamics 2}
-\end{equation}
-where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V}_m)\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.
-
-Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd:=\qd(t):\R\to \R^n$ under the unknown terms $\mv f:=\mv f(\q,\dq,\ddq)$.
+Consider an uncertain Euler-Lagrange system modeled as
+\begin{equation}
+    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
+    =
+    \mysat(\mv\tau)
+    \label{eq:sys1}
+\end{equation}
+where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
+The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
+\begin{equation}
+    \mysat(\mv\tau)
+    :=
+    \begin{cases}
+        \mv\tau, 
+        & 
+        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
+        \\
+        \bar\tau
+        \cdot
+        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
+        & 
+        \text{otherwise},
+    \end{cases}
+    \label{eq:sat}
+\end{equation}
+where $\bar\tau$ denotes the maximum norm of control input.
+To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
+Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+
+The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
+We introduce the following properties:
+\begin{prop} 
+    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
+    \label{prop:M}
+\end{prop}
+
+\begin{prop} 
+    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
+    \label{prop:skew}
+\end{prop}
+
+\begin{prop}
+    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
+    \label{prop:dis_bound}
+\end{prop}
+
+In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
+Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
+\begin{assum}
+    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
+    \label{assum:feasible}
+\end{assum}
 
@@
 
-In this section, the neuro–adaptive controller is developed.
-Section \ref{sec:ctrl dev} presents the details of the neuro–adaptive controller and the NN model.
-The adaptation law based on the constrained optimization method is derived in Section \ref{sec:adap_laws} by formulating a constrained optimization problem.
-
-\subsection{Neuro–adaptive Control Design} \label{sec:ctrl dev}
-
-The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
-The desired stabilizing controller can be designed as follows:
-\begin{equation}
-    \mv \tau^* = 
-    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
-    + 
-    ( 
-        -\widehat{\mm M}\tilde {\q}
-        +
-        \widehat{\mm V}_m{\mv z}
-        +
-        \widehat{\mm G}
+The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
+Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model.
+The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
+    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
+    \label{fig:ctrl:diagram}
+\end{figure*}
+
+\subsection{Neuro-Adaptive Controller Design}\label{sec:sub:NAC}
+
+First, let us define the filtered tracking error $\fe\in\R^n$ as 
+\begin{equation}
+    \fe := \dot{\mv e}-\mm\Lambda \mv e
+    ,
+    \label{eq:err:filtered}
+\end{equation}
+where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
+Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
+
+Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
+\begin{equation}
+    \mm M \dot\fe
+    =
+    -\mm V_m \fe
+    -\mm K \fe
+    + \mv f
+    -\mv \tau_d + \mysat(\mv\tau)
+    ,
+    \label{eq:sys:filtered}
+\end{equation}
+where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
+    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
+    =
+    \mm K \fe
+    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
+    +
+    \mm V_m(-\dqd+\mm\Lambda\mv e)
     -
-        \mv f
-        +
-        \widehat{\mm M} \dot {\mv z}^*
-    ) 
+    \mm F
+    -
+    \mm G
+    \in\R^n
+$ denotes the lumped system uncertainty.
+
+Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
+Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
+\begin{equation}
+    \begin{aligned}
+        \ddtt{V}_1
+        =&
+        \fe^\top \mm M (
+            -\mm V_m \fe -\mm K \fe + \mv f
+            -\mv \tau_d + \mysat(\mv\tau)
+        )
+        \\
+        &
+        +
+        \tfrac{1}{2}
+        \fe^\top \dot{\mm M}\fe
+        \\
+        =&
+        -
+        \fe^\top \mm K \fe 
+        +
+        \fe^\top (
+            \mv f+\mysat(\mv\tau)
+            -\mv \tau_d
+        )
+        \\
+        &
+        +
+        \tfrac{1}{2}
+        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
+        \\
+        \le&
+        -\lambda_{\min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mv f+\mysat(\mv \tau))
+        \\
+        \le&
+        -\lambda_{\min}(\mm K)\norm{\fe}^2
+        +
+        \bar\tau_d\norm{\fe}
+        +
+        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
         ,
-    \label{eq. desired control}
-\end{equation}
-where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
-Note that the desired controller cannot be realized because of $\mv f$.
-
-To approximate the desired controller, an NN is utilized.
-Even though DNNs have a higher approximation capability than SHLNNs \cite{Rolnick:2018aa}, here, an SHLNN is utilized for simplicity and low computational complexity.
-The NN with a single hidden layer is represented as 
-\begin{equation}
-    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
+    \end{aligned}
+    \label{eq:lya1:dot1}
+\end{equation}
+where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
+However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.
+
+To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
+Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
+Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
+In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
+
+In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
+\begin{align}
+    \mv\tau^*=& \idealNN+\mv\epsilon,
+    \label{eq:control:ideal}
+\end{align}
+which is estimated online by
+\begin{align}
+    \mv\tau =& \estNN,
+    \label{eq:control:est}
+\end{align}
+where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
+
+Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $\mathcal V_1$ can be rewritten as
+\begin{equation}
+    \dot{\mathcal V}_1
+    \le 
+    -\lambda_{\min}(\mm K)\norm{\fe}^2
+    +
+    \bar\tau_d\norm{\fe}
+    +
+    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
+    .
+    \label{eq:lya1:dot2}
+\end{equation}
+Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).
+
+\subsection{Deep Neural Network (DNN) Model}\label{sec:sub:NN definition}
+
+The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
+\begin{equation}
+    \NN_i :=
+    \begin{cases}
+        \wV_i^\top \NN_i(\NN_{i-1}), 
+        &
+        i\in[1,\dots,k],
+        \\
+        \wV_0^\top \q_{NN},
+        &
+        i=0
         ,
-\end{equation}
-where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
-The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
-For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denotes the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.
-
-Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{n}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{n}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
-The ideal weight vector $\wth^*$ is typically assumed to be bounded.
-Then, using the estimated weight vector $\estwth:=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\idealwth:=({\idealwth_{1}}^{\top},{\idealwth_{0}}^{\top})^\top $ and bounded approximation error $\mv \epsilon\in\R^2$, the approximated desired controller $\mv \tau^*\approx -\NN(\q_{n};\idealwth)-\mv\epsilon$ can be estimated as follows:
-\begin{equation}
-    \mv \tau := -\NN({\q_{n}};\estwth)
-    .
-    \label{eq. control law}
-\end{equation}
-For further sections, let $\idealNN:=\NN({\q_{n}};\idealwth)$ and $\idealact :=\act({\idealwV_0}^{\top}{\q_{n}})$, and let $\estNN:={\NN}({\q_{n}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{n}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{n})}$.
-
-Using \eqref{eq.
-system dynamics 2}, \eqref{eq.
-desired control}, and \eqref{eq.
-control law}, the error dynamics can be obtained as the first-order system of augmented error $\mv \xi:=({\tilde {\q}}^\top ,{\tilde {\mv z}}^\top)^\top \in\R^{2n}$ as follows:
-\begin{equation}
-    \ddtt{\mv \xi} 
-    = 
-    \mm A_\xi{\mv \xi}+\mm B_\xi(\NN^*-\estNN+\mv\epsilon)
-    ,
-\end{equation}
-and 
-\begin{equation}
-    \mm A_\xi := 
+    \end{cases}
+    \label{eq:DNN:architecture}
+\end{equation}
+where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
+The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).
+
+One of the widely used activation functions for large DNNs is from the ReLU family \cite{Maas:2013aa}, which effectively avoids the gradient vanishing problem during error backpropagation. 
+However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
+These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\ddtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}< 1$.
+
+For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
+\begin{equation}
+    \wth := 
     \begin{bmatrix}
-        -{k_q} \mm I_{n} &\mm I_{n}
-        \\
-        -\mm I_{n}& -{k_z} \mm I_{n}
+        \wth_k\\
+        \wth_{k-1}\\
+        \vdots\\
+        \wth_0
     \end{bmatrix}
-    ,\ 
-    \mm B_\xi := 
+    =
     \begin{bmatrix}
-        \mm 0_{n\times n}\\\widehat{\mm M}^{-1}
-    \end{bmatrix}.
-\end{equation}
-
-\subsection{Adaptation Law Derivation}\label{sec:adap_laws}
-
-As discussed in Section \ref{sec:intro}, the boundedness of the weights should be considered to prevent excessively large control inputs and system instability.
-For the boundedness of the weights, weight norm constraints are imposed on the adaptation process such that $c_{\theta_i}:=c_{\theta_i}(\estwth_i)=\norm{{\estwth}_i}^2-\bar\theta^2_i,\ \forall i\in\{0,1\}$.
-The control problem can be reformulated into a constrained optimization problem as follows:
+        \myvec(\wV_k)\\
+        \myvec(\wV_{k-1})\\
+        \vdots\\
+        \myvec(\wV_0)
+    \end{bmatrix},
+\end{equation}
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
+\begin{equation}
+    \pptfrac{\NN}{\wth}=
+    \begin{bmatrix}
+        \pptfrac{\NN}{\wth_k}&
+        \pptfrac{\NN}{\wth_{k-1}}&
+    \cdots &
+        \pptfrac{\NN}{\wth_0}
+    \end{bmatrix}
+    \in\R^{n \times \Xi}
+    \label{eq. nabla phi}
+\end{equation}
+where
+\begin{equation}
+    \pptfrac{\NN}{\wth_i} = 
+    \begin{cases}
+        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
+        &
+        i=k 
+        \\
+        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
+        & 
+        i=k-1
+        \\
+        &
+        \vdots 
+        \\
+        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
+        &
+        i = 0
+    \end{cases},
+    \label{eq:NN:grad}
+\end{equation}
+where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
+
+In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
+Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and $\act^{*'}_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i:=\act_i(\hat\NN_{i-1})$ and $\hat\act_i':= \pptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
+
+%  SECTION ADAPTATION LAW DERIVATION =======================
+\section{Weight Adaptation Laws}\label{sec:adap_laws}
+
+% \subsection{Adaptation Law using Lagrangian Function}
+\subsection{Weight Optimizer Design}\label{sec:sub:weight optimizer}
+
+The control objective can be represented as follows:
 \begin{equation}
     \begin{matrix}
-        \min_{{\estwth}} \ J(\mv \xi;{\estwth})
-        :=
-        \tfrac{1}{2}
-        \mv \xi^\top \mm \Lambda \mv \xi
+        \min_{\estwth} \ J(\fe;\estwth):= 
+        \tfrac{1}{2} \fe^\top  \mm W\fe
         \\ \\
         \begin{aligned}
-        \text{subject to\;}&c_{j}\le0, \quad j\in\mathcal I 
-        := 
-        \{\theta_0,\theta_1\}
-        ,
+        \text{s.t. }&c_{j}(\estwth) 
+        \le0, \quad j\in\mathcal{I},
         \end{aligned}
     \end{matrix}
-\end{equation}
-where $\mm \Lambda=\mm \Lambda^\top >0$ denotes the weighting matrix.
-In this optimization problem, $\mv \xi$ is considered a predefined parameter.
-The corresponding Lagrangian function is defined as
+    \label{eq:opt:problem1}
+\end{equation}
+where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top  \mm W\fe$ is the objective function, and $\mm W\in\R^{n\times n}$ is a symmetric positive weighting matrix.
+Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
+Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
 \begin{equation}
     L(
-        \mv \xi,
-        {\estwth},
-        [\lambda_j]_{j\in\mathcal I}
+        \fe,\estwth,[\lambda_j]_{j\in\mathcal I}
     ) 
     := 
-    J(\mv \xi;{\estwth})
-    +
-    \textstyle\sum_{j\in\mathcal I} \lambda_jc_j({\estwth})
-    .
-\end{equation}
-% where $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ denotes the active set.
-To solve the dual problem $\min_{{\estwth}} \max_{[\lambda_j]_{j\in\mathcal I}}  L(\mv \xi,{\estwth},[\lambda_j]_{j\in\mathcal I}$, the adaptation law is derived as follows:
+    J(\fe;\estwth) 
+    + 
+    \sum_{j\in\mathcal I}
+    \lambda_{j}
+    c_{j}(\estwth)
+    \label{eq:lagrangian}
+\end{equation}
+where $\lambda_j$ denotes the Lagrange multiplier for each constraint.
+
+The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
 \begin{subequations}
     \begin{align}
-            \ddtt {{\estwth}}
-            &
+            \ddtt{\estwth}
+            &
+            =
+            -\alpha \pptfrac{L}{\estwth}
             =
             -\alpha 
-            \pptfrac{L}{{\estwth}}
-            =-\alpha 
             \left(
-                \pptfrac{J}{{\estwth}}
+                \pptfrac{J}{\estwth}
                 +
@@
             = 
-            \beta_j
-            \pptfrac{L}{\lambda_j} 
+            \beta_j\pptfrac{L}{\lambda_j} 
             = 
             \beta_j c_j ,
-            \quad\quad\quad\quad      \      
-            \forall j\in\mathcal I,
-        \label{eq. adaptation law L}
-            \\
+            \quad \forall j\in\mathcal I,
+        \label{eq:adap:lbd}
+            \\
+            \lambda_j & = \max(\lambda_j,0) ,
+        \label{eq:adap:lbd:max}
+    \end{align}
+    \label{eq:adaptation law}
+\end{subequations}
+where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
+When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation.
+Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \estwth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
+In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
+These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
+% The KKT condition is satisfied, when $\estwth$ converges to $\idealwth$, since $\partial L/\partial \estwth=0$ (i.e. the first-order necessary condition of the optimality is satisfied.).
+
+\subsection{Approximation of the Gradient of Objective Function}
+
+The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\mv\tau}$ (\ie 
+$
+    \pptfrac{J}{\mv \tau}
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\mv \tau}{\estwth}))^\top \fe
+    =
+    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\estNN}{\estwth}))^\top \fe
+$). 
+Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
+The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
+\begin{equation}
+    \ddtt (
+        \pptfrac{\fe}{\mv\tau}
+    )
+    =
+    \pptfrac{}{
+        \mv\tau
+    }
+    \left[
+        \mm M^{-1}(
+            -\mm V_m \fe
+            -\mm K \fe
+            + \mv f
+            -\mv \tau_d + \mysat(\mv\tau)
+        )
+    \right]
+    .
+\end{equation}
+However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\mm M,\mm V_m, \mm F$ and $ \mm G$).
+Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
+
+In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\mv\tau}$ as $
+    \pptfrac{\fe}{\mv\tau}
+    \approx
+    [
+        \mathrm{sign}(\pptfrac{r_i}{\tau_j})
+    ]_{i,j\in[1,\cdots,m]}
+$ using the sign of each entry (\ie control direction).
+However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\mm M^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
+Therefore, we propose to approximate $\pptfrac{\fe}{\mv\tau}$ as $\pptfrac{\fe}{\mv\tau}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
+\begin{equation}
+    \ddtt{\estwth}
+    \approx
+    -\alpha 
+    \left(
+        \pptfrac{\estNN}{\estwth}^\top
+        \fe
+        +
+        \textstyle\sum_{j\in\mathcal{I}}
         \lambda_j 
-            & 
-            = 
-            \max(\lambda_j,0) ,
-        \label{eq. adaptation law L max}
-    \end{align}
-    \label{eq. adaptation laws}
-\end{subequations}
-where arguments of $L$ are suppressed for brevity, and $\alpha\in\R_{>0}$ and $\beta_j\in\R_{>0}$ denote the adaptation gain and the update rate for each Lagrange multiplier, respectively.
-\color{red}
-% The Eq.~\eqref{eq.
-adaptation law L max} is analog to using an active set $\mathcal I=\{j\ \vert \ c_j\ge 0\}$ in constrained optimization theory which excludes terms of satisfied constraints in adaptation law.
-\color{black}
-
-Using the chain rule, the gradient of the objective function with respect to the weights (\ie $\pptfrac{J}{\estwth}$) in \eqref{eq. adaptation law th} can be represented as
-% \begin{equation}
-$
-    \pptfrac{J}{\estwth}
-    =
-    \pptfrac{\mv\xi}{\estwth}^\top 
-    \mm \Lambda
-    \mv\xi
+        \pptfrac{c_j}{\estwth}
+    \right)
     .
-% \end{equation}
-$
-The calculation of $\pptfrac{J}{\estwth}$ is not straightforward because of the dynamics of $\mv\xi$.
-Using the forward sensitivity method presented in \cite{Sengupta:2014aa}, the sensitivity equation can be obtained as follows:
-\begin{equation}
-    \ddtt{\mm \eta} =
-    \mm A_\xi \mm\eta
-    - \mm B_\xi 
-    % (\partial \estNN/\partial {\estwth})
-    \pptfrac{\estNN}{\estwth}
-    ,
-    \label{eq. sen eq}
-\end{equation}
-where ${\mm \eta}:= \pptfrac{\mv\xi}{\estwth}\in\R^{2n\times \Xi}$ denotes the sensitivity of the weights to the augmented error.
-The initial value of ${\mm \eta}$ is zero since the initial $\mv\xi$ is independent of the weights.
-By decomposing for each layer, the dynamics of ${\mm \eta}_i:= \pptfrac{\mv\xi}{\estwth}_i\in\R^{2n\times \Xi_i}$ can be represented as
-\begin{equation}
+    \label{eq:adap:th:approx}
+\end{equation}
+
+%% ALGORITHM PART; Now omitted!
+% The proposed controller is implemented using Algorithm \ref{alg: alg1}.
+For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
+If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
+
+% \begin{algorithm}[!t]
+%     \caption{Weight Optimizer Implementation.}\label{alg: alg1}
+%     \begin{algorithmic}[1]
+%         \renewcommand{\algorithmicrequire}{\textbf{Input:}}
+%         \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%         \REQUIRE $\xi$, $\estwth$, $\lambda_j$, $\eta$
+%         \ENSURE  $\estwth$, $\lambda_j$, $\eta$
+%         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
+%         \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
+%         \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
+%         \STATE Determine update directions $\dot{\estwth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
+%         \STATE Update weight vector $\estwth\leftarrow \estwth+\dot{\estwth}\cdot T_s$;
+%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
+%         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
+%         \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
+%         \STATE \textbf{RETURN};
+%     \end{algorithmic}
+%     \label{alg1}
+% \end{algorithm}
+
+\subsection{Constraint Candidates}\label{sec:sub:cstr}
+
+This section introduces conditions which imposed constraints must satisfy and the weight constraints.
+The potential control input constraints are presented in Appendix \ref{sec:appen:cstr}.
+First, we introduce the following assumptions for the constraints.
+
+\begin{assum}
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
+    \label{assum:convex}
+\end{assum}
+
+\begin{assum}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
+    \label{assum:LICQ}
+\end{assum}
+
+\begin{remark}
+    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex in practice including the origin.
+    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
+    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
+\end{remark}
+
+The following Lemma is introduced for the stability analysis.
+\begin{lem}
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    \label{lem:convex:angle}
+\end{lem}
+
+\begin{proof}
+
+Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
+\begin{equation}\label{eq:linear:map}
     \begin{aligned}
-        \ddtt{\mm \eta} 
-        \!=\!&
-        \begin{bmatrix}
-            {\mm \eta}_1&{\mm \eta}_0
-        \end{bmatrix}'
-        \\
-        \!=\!&
-        \mm A_\xi
-        % \begin{bmatrix}
-        [
-            {\mm \eta}_1
-            \ \ 
-            {\mm \eta}_0
-        ]
-        % \end{bmatrix}
-        \!-\!
-        \mm B_\xi
-        % \begin{bmatrix}
-        [
-            (\mm I_{l_2}\!\otimes\!\estact^\top )
-            \ \ 
-            \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
-        ]
-        % \end{bmatrix}
+    \mv\tau 
+    = 
+    &
+    \estNN 
+    % = 
+    % \myvec(\estNN)
+    =
+    \myvec(
+        \estwV_k^\top \estact_k
+    ) 
+    = 
+    (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top
+    \myvec(\estwV_k)
+    \\
+    = &
+    \underbrace{
+        (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top}_{:=\mm T(\estact_k)}
+    \estwth_k 
+    =
+    \mm T(\estact_k) \estwth_k.
+    \end{aligned}
+\end{equation}
+Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+
+\end{proof}
+
+The weight constraints are essential to prevent the weights from diverging during the adaptation process.
+The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+\begin{equation}
+    c_{\theta_i}
+    =
+    \tfrac{1}{2}
+    (
+        \Vert \estwth_i\Vert^2 
+        -
+        \bar\theta_i^2 
+    )    
+    \le 0
+    \label{eq:cstr:weight_ball}
+\end{equation}
+with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
+The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
+\begin{equation}
+    \pptfrac{c_{\theta_i}}{\estwth_j} 
+    =
+    \begin{cases}
+        \estwth_i,
+        &
+        \text{if } i=j
+        \\
+        \mv{0},
+        &
+        \text{if } i\ne j
+        .
+    \end{cases} 
+    \label{eq:cstr:weight_ball:grad}
+\end{equation}
+Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.
+
+%  SECTION STABILITY ANALYSIS ==============================
+\section{Stability Analysis}\label{sec:stability}
+
+Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+The following lemma is introduced for the stability analysis.
+
+\begin{lem} 
+    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i,\ \forall i\in[k,\cdots, i+1]$, remain bounded.
+    \label{lem:cstr:grad:bound}
+\end{lem}
+
+\begin{proof}
+
+The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
+\begin{equation}
+    \pptfrac{c_j}{\estwth_i} 
+    = 
+    \pptfrac{c_j}{\mv\tau} 
+    \pptfrac{\mv\tau}{\estNN} 
+    \pptfrac{\estNN}{\estwth_i}
+\end{equation}
+where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
+From the linear mapping in \eqref{eq:linear:map}, $\mv\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
+By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
+The convex function has a bounded derivative with respect to $\mv\tau$, since $\mv\tau$ is a bounded variable (\ie $\pptfrac{c_j}{\mv\tau}$ is bounded). 
+Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
+This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
+Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+
+\end{proof}
+
+The following theorem shows that $\estwth$ and $\fe$ are bounded.
+
+\begin{theorem}
+    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$.
+    This holds with the weight norm constraint \eqref{eq:cstr:weight_ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
+\end{theorem}
+
+\begin{proof}
+
+The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
+Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
+This assumption is reasonable, since even if the constraint is inactive 
+\MSRY{Add the reason why it is reasonable.}
+We consider two cases: (C$_1$) control input constraints are active, and (C$_2$) control input constraints are inactive.
+Using the fact that amplitude of the control input is only depends on $\estwth_k$ (\ie see \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$), the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
+
+\subsection*{Case (C$_1$): Control input constraints are active.}
+
+As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
+\begin{equation}
+    \Theta_{\fe}^{c_1} 
+    = 
+    \left\{ 
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
+        \le 
+        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\text{min}}(\mm K)}
+    \right\}
+    .
+    \label{eq:invariant:c1:fe}
+\end{equation}
+
+To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
+Taking the time derivative of $V_2$ yields:
+\begin{equation}
+    \begin{aligned}
+        \ddtt  V_2 
+        =& 
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \textstyle\sum_{j\in\mathcal{I}}
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        =&
+        -\estwth_k^\top 
+        (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        \\
+        &
+            +
+            \textstyle\sum_{
+                j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+            }
+            \lambda_j 
+            \pptfrac{c_j}{\estwth_k}
+        )
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        \underbrace{
+            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
+        }_{:=c_1\in\R_{>0}}
+        \norm{\fe}
+        \norm{\estwth_k}
+        \\
+        &
+        -
+        \underbrace{
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j 
+        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
+        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        \\
+        \le&
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
+        +
+        c_1     
+        \norm{\fe}
+        \norm{\estwth_k}
         .
     \end{aligned}
-\end{equation}
-The calculation of $\pptfrac{\estNN}{\estwth}$ is introduced in \cite{Patil:2022aa}.
-In conclusion, the gradient of the objective with respect to the weights can be obtained as $\pptfrac{J}{\estwth} = {\mm \eta}^\top\mm \Lambda\mv\xi$ by simulating the sensitivity equation \eqref{eq.
-sen eq}.
-
-On the other hand, the gradient of the constraints with respect to the weights can be represented as follows:
-\begin{equation}
-    \pptfrac{c_{\theta_0}}{{\estwth}}
-    = 
-    \begin{bmatrix}
-        \mm 0_{\Xi_1\times 1} \\
-        2{\estwth}_0 
-    \end{bmatrix}
-    ,\quad
-    \pptfrac{c_{\theta_1}}{{\estwth}}    
-    = 
-    \begin{bmatrix}
-        2{\estwth}_1 \\
-        \mm 0_{\Xi_0\times 1}
-    \end{bmatrix}
+    \label{eq:lya2:dot}
+\end{equation}
+According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
+\begin{equation}
+    \Theta_{\theta_k}^{c_1} 
+    = 
+    \left\{ 
+        \estwth_k \in \R^{\Xi_{k}} 
+        \mid 
+        \norm{\estwth_k} 
+        \le 
+        \tfrac{
+            c_1(2\bar\tau+\bar\tau_d)
+        }{
+            \lambda_{\theta_k}\lambda_{\min}(\mm K)
+        }
+    \right\}
     .
-\end{equation}
-
-%  SECTION STABILITY ANALYSIS ==============================
-\section{Stability Analysis}\label{sec:stability}
-
-The following theorem proves the boundedness of the tracking error and the weight estimation of the weights.
-
-\begin{theorem}
-For the dynamical system in \eqref{eq.
-system dynamics 1}, the proposed controller \eqref{eq.
-control law} and the adaptation law \eqref{eq.
-adaptation laws} ensure the boundedness of the tracking error $\mv \xi$ and the weight estimation ${\estwth}$, provided that the control gains ${k_q}$ and ${k_z}$ satisfy \eqref{eq.
-ctrl stable condition}.
-\end{theorem}
-
-\begin{proof}
-The boundedness is proven from the last layer to the first layer.
-
-\subsection*{Step 1: Boundedness of ${\estwth}_1,{\mm \eta}_1,\mv \xi$}
-
-% For convenience, assume that all the constraints are in the active set without loss of generality.
-% If the constraints are not in the active set, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraints are violated.
-\color{black}
-Without loss of generality, assume that all the constraints are violated. 
-Then, according to \eqref{eq. adaptation law L} and \eqref{eq. adaptation law L max}, all Lagrange multipliers are nonzero.
-%If the Lagrange multipliers are not sufficiently generated, the boundedness cannot be guaranteed, but weights will be adapted to reduce the objective function until the constraint violations.
-\color{black}
-
-The dynamics of $\mv \xi$ can be represented as
-\begin{equation}    
-    \ddtt {\mv\xi} = \mm A_\xi\mv \xi +\mm B_\xi
-    (
-        -\estwV_1^\top \estact+\mv w(t)
-    )
-    ,
-\end{equation}
-where $\mv w(t):= {\idealwV_1}^{\top}\idealact+\mv \epsilon$ is a lumped residual term, which is bounded as $\norm{\mv  w(t)}\le \bar w< 0$ since $\norm{\idealwth_1},\norm{\idealact}$ and $\norm{\mv\epsilon}$ are bounded.
-The dynamics of ${\mm \eta}_1$ and ${\estwth}_1$ are represented as
+    \label{eq:invariant:c1:wth}
+\end{equation}
+
+The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
+For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{c_1}$ is squeezed to a point.
+The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
+It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
+This drives $\estwth_k$ to the origin until the constraint is satisfied (\ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space).
+
+Therefore, the boundedness of $\estwth$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{c_1}$ and $\Theta_{\theta_k}^{c_1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
+
+\subsection*{Case (C$_2$): Control input constraints are inactive.}
+
+Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
+Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
 \begin{equation}
     \begin{aligned}
-        \ddtt{\mm \eta}_1 =
-        & 
-        \mm A_\xi {\mm \eta}_1 -\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )
-        ,
-        \\
-        \ddtt{{\estwth}}_1 =
-        & -\alpha 
-        (
-            {\mm \eta}_1^\top 
-            \mm \Lambda
-            \mv\xi
-            +
-            2\lambda_{\theta_1} {\estwth}_1
-        )
+        \ddtt V_3
+        =&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\bar\tau_d\norm{\fe}
+        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
+        \\
+        &
+        -\estwth_k^\top (
+            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            \fe
+            +
+            \lambda_{\theta_k}\estwth_k
+        )
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +\fe^\top \estNN
+        +(
+            \bar\tau_d+\norm{
+                \underbrace{
+                    \idealNN+\mv\epsilon
+                }_{=\mv\tau^*}
+            }
+        )
+        \norm{\fe}
+        \\
+        &
+        -\estNN^\top\fe 
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        \\
+        \le&
+        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        +(\bar\tau_d+\bar\tau)
+        \norm{\fe}
+        -\lambda_{\theta_k}\norm{\estwth_k}^2
         .
     \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, the boundedness of ${\mm \eta}_1$ can be obtained since $\mm A_\xi$ is stable and the residual term $\norm{-\mm B_\xi (\mm I_{l_{2}}\otimes \estact^\top )}$ is bounded.
-
-Define the Lyapunov function $V_1:=\tfrac{1}{2}\mv\xi^\top \mm P\mv\xi+\tfrac{1}{2\alpha}{\estwth}_1^\top {\estwth}_1$, with the Lyapunov equation $\mm A_\xi^\top \mm P+\mm P\mm A_\xi=-\mm Q$, where $\mm A_\xi<0,\mm P=\mm P^\top >0$, and $\mm Q>0$.
-Using a proposition $\estwV_1^\top \estact = \myvec(\estwV_1^\top \estact)=\myvec(\estact^\top \estwV_1) = (\mm I_{l_2}\otimes {\estact}^\top )\myvec(\estwV_1)=(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1$ \cite[Proposition~(7.1.9)]{Bernstein:2009aa}, the time derivative of $V_1$ is
-\begin{equation}
-    \begin{aligned}
-        \ddtt \! {V}_1 
-        \!=\!& 
-        \tfrac{1}{2}
-        \mv \xi^\top 
-            (
-                \mm A_\xi^\top \mm P+\mm P\mm A_\xi
-            )
-        \mv \xi
-        \!+\!
-        \mv \xi^\top \mm P (
-            \!-\!\mm B_\xi\estwV_1^\top \estact +\mm B_\xi \mv w(t) 
-        )\\
-        &
-        -{\estwth}_1^\top 
-        \!
-        (
-            {\mm \eta}_1^\top \mm \Lambda \xi+2\lambda_{\theta_1} {\estwth}_1 
-        )
-        \\
-        =& 
-        -\tfrac{1}{2}
-        \mv \xi^\top \mm Q\mv \xi 
-        -
-        \mv \xi^\top \mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top ){\estwth}_1 
-        +\mv \xi^\top \mv \Delta
-        \\
-        &
-        -{\estwth}_1^\top {\mm \eta}_1^\top \mm \Lambda\mv \xi
-        -2\lambda_{\theta_1} {\estwth}_1^\top {\estwth}_1
-        \\
-        \le&
-        -
-        \tfrac{1}{2}
-        \lambda_\text{min}(\mm Q)\norm{\mv \xi} ^2
-        +\bar\Delta \norm{\mv \xi}
-        +\bar M\norm{\mv \xi} \norm{{\estwth}_1}
-        \\
-        &
-        -2\lambda_{\theta_1}
-        \norm{{\estwth}_1}^2
-        \\
-        \le& 
-        (
-            -\tfrac{1}{2}\lambda_\text{min}(\mm Q)
-            +{\tfrac{\bar M}{2}}
-        )
-        \norm{\mv \xi}^2 +\bar\Delta \norm{\mv \xi}
-        \\
-        &+ 
-        (
-        -2\lambda_{\theta_1} 
-        +\tfrac{\bar M}{2}
-        )
-        \norm{\tilde{\wth}_1}^2 
-        ,
-        \end{aligned}
-        \label{eq. lya 1}
-\end{equation}
-where $\mv \Delta:= \mm P\mm B_\xi \mv w(t)$ and $\mm M:= -\mm P\mm B_\xi(\mm I_{l_2}\otimes \estact^\top )-\mm \Lambda{\mm \eta}_1$ are bounded such that $\norm{\mv \Delta}\le\bar\Delta<\infty$ and $\norm{\mm M}_F\le \bar M< \infty$, respectively.
-
-By defining $\mm P=\mm I_n$, the eigenvalues of $\mm Q=-\mm A_\xi^\top -\mm A_\xi$ are $2k_q$ and $2k_z$, since $\mm A_\xi$ is a skew-symmetric matrix except for the diagonal entries.
-According to \eqref{eq. lya 1}, if $k_q$ and $k_z$ are provided that
-\begin{equation}
-    \text{min}(k_q,k_z)>\tfrac{\bar M}{2}
-    ,
-    \label{eq. ctrl stable condition}
-\end{equation}
-and if $\lambda_{\theta_1}$ is increased sufficiently large such that $2\lambda_{\theta_1}>\tfrac{\bar M}{2}$, due to the violation of $c_{\theta_1}$, the tracking error is bounded in
-\begin{equation}
-    \Theta_\xi := 
+    \label{eq:lya3:dot}
+\end{equation}
+Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
+\begin{equation}
+    \Theta_{\fe}^{c_2}
+    =
     \left\{ 
-        \mv\xi\mid
-        \norm{\mv\xi}
+        \fe \in \R^n 
+        \mid 
+        \norm{\fe} 
         \le 
         \tfrac{
-            2\bar \Delta
+            \bar\tau_d+\bar\tau
         }{
-            \lambda _\text{min}(\mm Q)-{\bar M}
+            \lambda_{\text{min}}(\mm K)
         }
     \right\}
-    ,
-\end{equation}
-and the weight estimation $\estwth_1$ is bounded in
-\begin{equation}
-    \Theta_{{\theta}_1} := 
-    \left\{ 
-        {\estwth_1} 
-        \mid
-        \norm{\estwth_1}
-        \le  
-        \bar\theta_1
-    \right\}
     .
 \end{equation}
-The Lagrange multiplier $\lambda_{\theta_1}$ is also bounded since the $\lambda_{\theta_1}$ update stops once ${\estwth}_1$ approaches the compact set $\Theta_{{\theta}_1}$, satisfying the constraint $c_{\theta_1}$.
-
-\subsection*{Step 2: Boundedness of ${\estwth}_0,{\mm \eta}_0$}
-
-The dynamics of ${\mm \eta}_0$ and ${\estwth}_0$ are represented as
-\begin{equation}
-    \begin{aligned}     
-        \ddtt{\mm \eta}_0 =& 
-        \mm A_\xi{\mm \eta}_0 -\mm B_\xi 
-        \estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )
-        ,
-        \\
-        \ddtt{{\estwth}}_0
-        =&
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
+
+\hfill
+
+The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
+The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
+\begin{equation}
+    \ddtt \estwth_i 
+    =
     -\alpha
     (
-            {\mm \eta}_0^\top \mm \Lambda\mv \xi+2\lambda_{\theta_0} {\estwth}_0
+        \pptfrac{\estNN}{\estwth_i}^\top
+        \fe
+        +
+        \lambda_{\theta_i}\estwth_i
+        +
+        \textstyle\sum_{
+            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+        }
+        \lambda_j
+        \pptfrac{c_j}{\estwth_i}
     )
     .
-    \end{aligned}
-\end{equation}
-According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, ${\mm \eta}_0$ is bounded since $\mm A_\xi$ is a stable matrix and $\norm{-\mm B_\xi\estwV_1^\top \estact'(\mm I_{l_1}\otimes {\q_{n}}^\top )}$ is bounded.
-To obtain the invariance set of ${\estwth}_0$, taking the time derivative of the Lyapunov function $V_0=\tfrac{1}{2\alpha}{\estwth}_0^\top {\estwth}_0$ yields:
-\begin{equation}
-    \begin{aligned}
-        \ddtt {V}_0 =& 
-        -{\estwth}_0^\top (
-            {\mm \eta}_0\mm \Lambda\mv \xi 
-            +2\lambda_{\theta_0}{\estwth}_0
-        )
-        \\
-        \le &
-        \norm{{\estwth}_0} \norm{{\mm \eta}_0\mm \Lambda\mv \xi} 
-        -
-        2\lambda_{\theta_0} {\estwth}_0^\top {\estwth}_0
-        ,
-        \\
-        \le &
-        -2\lambda_{\theta_0} 
-        \norm{{\estwth}_0}^2 
-        + 
-        \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
-        \norm{{\estwth}_0}
-        .
-    \end{aligned}
-\end{equation}
-Then, the invariance set can be represented as 
-% \begin{equation}
-$
-    \Theta_{{\theta}_0} :=
-    % \left\{
-    \{
-        {\estwth}_0\mid\norm{\estwth_0}
-        \le
-        \tfrac{
-            \norm{{\mm \eta}_0\mm \Lambda\mv \xi}
-        }{
-            2\lambda_{\theta_0}
-        }
-    % \right\}
-    \}
-    .    
-$
-% \end{equation}
-If $\lambda_{\theta_0}$ is increased sufficiently large due to the violation of $c_{\theta_0}$, the invariance set $\Theta_{{\theta}_0}$ converges to $\{{\estwth}_0 \mid \norm{{\estwth}_0} \le \bar\theta_0\}$ until the constraint $c_{\theta_0}$ is satisfied.
-Therefore, the Lagrange multiplier $\lambda_{\theta_0}$ is also bounded.
+\end{equation}
+Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
+
+\hfill
+
+Finally, the filtered error $\fe$ and the estimated weights $\estwth$ are bounded and the imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
 
@@
 
+The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
+The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+%This model contains terms of gravity and friction in its mechanical system.
+%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
+%and can be considered as the disturbance of the system.
+The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for $\q=[q_1,q_2]^\top $ was defined as
+\begin{equation}
+    {q_d}(t) = 
+    \begin{bmatrix}
+        {q_d}_1\\{q_d}_2
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        +\cos(0.5\pi t) + 1 \\
+        -\cos(0.5\pi t) - 1 
+    \end{bmatrix}.
+\end{equation}
+%\color{red}
+%Considering the power limitation of the power source for the actuators [], 
+The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
+\begin{equation}
+    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
+    \label{eq. h func}
+\end{equation}
+with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
+The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.
+
+In addition to this physically imposed control input saturation, the input norm constraint \eqref{eq.
+cstr input ball} was imposed to ensure that the control input $\tau$ stays within the unsaturation region of $h(\tau)$ and to prevent inefficient use of the input.
+With a sufficiently large value for $p$, the input norm constraint essentially matches the control input saturation function.
+Note that among the selected controllers given below, only the proposed CoNAC can rigorously handle this input norm constraint.
+
+% **********************************************************
+% SYSTEM FIGURE AND TABLE
 \begin{figure}[!t]
     \centering
-    \includegraphics[width=0.8\linewidth]{fig/RobotModel.drawio.png}
+    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
 
-The two-link manipulator model in \cite{Markus:2013aa} is employed for the simulation demonstration as described in Fig.~\ref{fig: manipulator}.
-In the system, the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in\{1,2\}$.
-The values of the system parameters are given in Table~\ref{table: system parameters}.
-The reference signal of $\q=[q_1,q_2]^\top $ is defined as follows:
-\begin{equation}
-    \qd
-    =
-    \begin{bmatrix}
-        {q_d}_1\\
-        {q_d}_2
-    \end{bmatrix}
-    = 
-    \begin{bmatrix}
-        +\cos(
-            \tfrac{\pi}{2}t
-        ) + 1 \\
-        -\cos(
-            \tfrac{\pi}{2}t
-        ) - 1 
-    \end{bmatrix}
-    .
-\end{equation}
-
-For the comparative study, three controllers were selected: the neuro–adaptive controller with $L_2$-regularization (NAC-L2) and with $\epsilon$-modification (NAC-eMod) and the proposed controller with constrained optimization (NAC-CO).
-%%%%%%%%%%%%%%%%%%%%%
-The performances of the selected controllers are compared based on the tracking performances and the dependencies of the parameters (\ie $L_2$ coefficient $\lambda$, $\epsilon$-modification coefficient $\rho$, and $\beta_j$ of NAC-L2, NAC-eMod, and NAC-CO, respectively).
-The square root of the integrated squared error (ISE) (\ie $\sqrt{\int_0^T \norm{\mv \xi}^2\,\der t}$, where $T$ denotes a simulation termination time) is utilized to evaluate the tracking performance.
-The parameter dependencies of the controllers were examined via various values of the parameters. 
-The values ranged from $0.001$ to $1$ across $10$ samples.
-%%%%%%%%%%%%%%%%%%%%%
-
-The control laws of all three controllers were the same as those defined in \eqref{eq. control law}.
-The adaptation law of NAC-L2 is derived by adding the squared weight term $\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$ to the objective function such that $J_{L_2}:= J+\tfrac{1}{2}\lambda{\estwth}^\top {\estwth}$, where $\lambda\in\R_{>0}$.
-The adaptation law obtained via the gradient descent method is subsequently adjusted by adding a stabilizing term $-\alpha\lambda{\estwth}$ as follows:
-\begin{equation} 
-    \ddtt{{\estwth}} = 
-    \pptfrac{J_{L_2}}{\estwth}
-    =-\alpha
-    \left(
-        \pptfrac{J}{\estwth}
-        +
-        \lambda{\estwth}
-    \right)
-    .
-    \label{eq. adap L2}
-\end{equation}
-Note that this adaptation law derived based on $L_2$-regularization method in deep learning is inherently the same as the $\sigma$-modification in adaptive control theory, which adds the term $-\alpha\sigma{\estwth}$, where $\sigma\in\R_{>0}$.
-For NAC-eMod, similar to the $\sigma$-modification, the stabilizing function $-\alpha\rho\norm{\tilde{\mv z}}{\estwth}$ is added to the adaptation law as follows:
-\begin{equation}
-    \ddtt{{\estwth}} = -\alpha
-    \left(
-        \pptfrac{J}{\estwth}
-        +
-        \rho\norm{\tilde {\mv z}}{\estwth}
-    \right)
-    ,
-    \label{eq. adap eMod}
-\end{equation}
-where $\rho\in\R_{>0}$.
-By $\norm{\tilde {\mv z}}$, the stabilizing function proportionally increases as the tracking error $\tilde {\mv z}$ increases.
-Therefore, the adaptation attempts to reduce the tracking error mainly without the effect of the stabilizing function if the tracking error is sufficiently regulated.
-The adaptation law of NAC-CO is presented in \eqref{eq. adaptation laws}.
-Owing to the stabilizing functions, the weights of NAC-L2 and NAC-eMod are biased since the stabilizing functions drive the weights toward the origin.
-
-All controllers had the same control parameters except their crucial parameters (\ie $\lambda$, $\rho$ and $\beta_j$) as $k_q=1.1$, $k_z=10$, $\widehat{\mm M}=\mm I_2$ and $\mm \Lambda=\mydiag([5,1,15,15])$.
-The parameters of the NNs were set to $l_0=2$, $l_1=16$, $l_2=2$, and $\alpha=10^3$, and the same random seed was applied for weight initialization.
-The validity of the selected number of nodes were demonstrated through experiments.
-The NN input vector was set to the desired trajectory $\qd$, with the augmented 1 to incorporate the bias term in the weight matrix such that $\q_{n}=(\qd^\top ,1)^\top $.
-For NAC-CO, the parameters of the weight norm constraints were set as $\bar\theta_0=10$ and $\bar\theta_1=20$.
-The sampling time of the simulation and the simulation termination time were set to $T_s=100\,\mu\mathrm{s}$ and $T=10\,\mathrm{s}$, respectively.
-
-\subsection{Results}
-
 \begin{figure}[!t]
     \centering
-    {\includegraphics[width=.85\linewidth]{fig/BoxWhisker.drawio.png}}
-\caption{Box-and-Whisker plot of the square root of the tracking ISEs of NAC-L2, NAC-eMod and NAC-CO across various parameter values.}
-    \label{fig: Box-beard plot}
+    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
+    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
+    \label{fig: h func}
 \end{figure}
+
+% SYSTEM FIGURE AND TABLE
+% **********************************************************
+Four controllers were examined for a comparative study.
+The first was the Backstepping Controller (BSC), used as the baseline.
+The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro-adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC.
+While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints.
+The third was DNN-BSC augmented with an auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
+As a result, an approximation of the input norm constraint was used as an input bound constraint.
+Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework.
+The properties of these four controllers are summarized in Table \ref{table:controller}.
+%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).
 
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Quantitative comparison of square root of tracking ISE.}
+    \caption{Properties of the controllers used in simulation}
+    \label{table:controller}
     \centering
-    \begin{tabular}{c c c c }
-    \hline
-     & \textbf{NAC-L2}\!&\!\textbf{NAC-eMod}\!&\!\textbf{NAC-CO} (proposed) 
-     \\
-     \hline
-    \hline 
-    Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
-    \hline
-    % Upper quartile  & $1.7284$e-3 & $0.5566$e-3 & $0.3261$e-3 \\
+    \begin{tabular}{|c||c|c|c|}
+    \hline
+    & \multicolumn{3}{c|}{Handling Capability}\\
+    \hline
+    & System & Weight Norm & Input Norm\\
+    &  Uncertainty & Constraint & Constraint\\
+    \hline 
+    BSC     & X & X & X\\
+    \hline
+    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
+         &  & (by projection) & \\
+    \hline
+    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
+       &  & (by projection) &  (by aux. system)\\
+       % &  & & linearized constraint)\\
     % \hline
-    Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
-    \hline
-    % Lower quartile  & $0.5533$e-3 & $0.5470$e-3 & $0.3238$e-3 \\
+    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
+    %    &  & (by projection) &  system for \\
+    %    &  & & linearized constraint)\\
+    \hline
+    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
+         &  & (by optimization) & (by optimization)\\
+    \hline
+    \end{tabular}
+\end{table}
+
+% \begin{table}
+% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
+% \centering
+% {\begin{tabular}{cc}\textcolor{black}ine
+% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
+% Rated power & 3 kW\\
+% Rated speed & 4500 RPM\\
+% Rated torque & 6.4 Nm\\
+% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
+% $I_{max}$ & 15 A \\
+% $V_{dc}$ & 100 V\\
+% $R_s$ & 0.34 $\Omega$\\
+% $P$ & 3\\
+% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
+% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
+% \multirow{2}{*}{Controller} & TMS320F28377D\\
+% & (Texas Instrument) \\
+% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
+%  & (Infineon Technologies)
+% \\\textcolor{black}ine
+% \end{tabular}}
+% \end{table}
+
+% \begin{table}[!t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Common Parameters of Selected Controllers.}
+%     \label{table: error norm}
+%     \centering
+%     \begin{tabular}{|c||c|c|c|c|c|c|}
 %     \hline
-    Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
-    \hline
-    \end{tabular}
-    \label{table: error norm}
-\end{table}
-
-As shown in Fig.~\ref{fig: Box-beard plot}, the maximum square root of the tracking ISE of NAC-CO is smaller than the minimum square root of the tracking ISEs of NAC-L2 and NAC-eMod for all variations in the parameters.
-This is because NAC-L2 and NAC-eMod bias the weights to the origin due to the presence of stabilizing functions.
-A quantitative comparison of the square root of the tracking ISE is provided in Table~\ref{table: error norm}.
-
-\begin{figure}[!t]      
-    \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig9.eps}%
-        \label{fig: weight NAC-L2}}
-    \vspace{-2mm}
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig10.eps}%
-        \label{fig: weight NAC-eMod}}
-    \vspace{-2mm}
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig8.eps}%
-        \label{fig: weight NAC-CO}}
-    \caption{Weight norms of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: weight}
-\end{figure}
-
-\begin{figure}[!t]      
-    \centering
-        \subfloat[NAC-L2]{\includegraphics[width=.85\linewidth]{fig/fig6.eps}%
-        \label{fig: error NAC-L2}}
-    \vspace{-2mm}
-        \subfloat[NAC-eMod]{\includegraphics[width=.85\linewidth]{fig/fig7.eps}%
-        \label{fig: error NAC-eMod}}
-    \vspace{-2mm}
-        \subfloat[NAC-CO]{\includegraphics[width=.85\linewidth]{fig/fig5.eps}%
-        \label{fig: error NAC-CO}}
-    \caption{Tracking errors of NAC-L2, NAC-eMod, and NAC-CO.}
-    \label{fig: error}
-\end{figure}
-
-For the detailed analysis, three values of the parameters (\ie $\lambda,\rho,\beta_j\in\{0.001,0.45,1\}$) were selected as described in Fig.~\ref{fig: weight} and Fig.~\ref{fig: error}.
-As shown in Fig.~\ref{fig: weight NAC-L2}, increasing $\lambda$ reduces the weight norm of NAC-L2 via the stabilizing function $-\alpha\lambda{\estwth}$.
-Moreover, the high dependency of NAC-L2 on the $L_2$-regularization coefficient $\lambda$ can also be observed.
-Since the weight norm is decreased, NAC-L2 cannot generate sufficient control inputs, resulting in a larger square root of tracking ISE, as shown in Fig.~\ref{fig: error NAC-L2}.
-
-On the other hand, NAC-eMod has a lower dependency on the $\epsilon$-modification coefficient $\rho$, as shown in Fig.~\ref{fig: weight NAC-eMod} and Fig.~\ref{fig: error NAC-eMod}.
-This is because the stabilizing function $-\alpha\rho\norm{\tilde {\mv z}}{\estwth}$ can be decreased once the tracking error $\tilde {\mv z}$ is sufficiently regulated.
-However, the bias of the weights to the origin still exists, as described in Fig.~\ref{fig: weight NAC-eMod} (\ie smaller weight norms are observed as $\rho$ increases.).
-Therefore, similar to NAC-L2, the biased weights produce insufficient control input, resulting in a relatively larger square root of tracking ISE than that of NAC-CO, as described in Table \ref{table: error norm}.
-
-Finally, the weight norm of NAC-CO is smaller than those of NAC-L2 and NAC-eMod, as shown in Fig.~\ref{fig: weight NAC-CO}, with better tracking performance.
-Even if a large $\beta_j$ is provided, NAC-CO can adjust the adaptation direction to satisfy the weight norm constraints faster, according to \eqref{eq. adaptation law L}.
-Therefore, the lowest dependency on the update rate $\beta_j$ is observed in NAC-CO, as shown in Fig.~\ref{fig: weight NAC-CO} and Fig.~\ref{fig: error NAC-CO}.
-Note that $\beta_j$ of NAC-CO is the update rate for the Lagrange multipliers, whereas $\lambda$ and $\rho$ are the coefficients of the stabilizing function that generates the biases of the weights.
-However, considering the implementation using a digital computer, excessively large $\beta_j$ values should be avoided.
-
-The details of the satisfaction of the weight norm constraints are shown in Fig.~\ref{fig: weight and multiplier} for NAC-CO with $\beta_j=0.001$.
-As the weight norms of each layer reach the constraint boundary, the corresponding Lagrange multipliers are generated.
-Using the Lagrange multipliers, the adaptation direction is adjusted toward the constraint satisfactory point.
-The Lagrange multipliers disappear when the constraints are satisfied, and the weights are adapted to optimize the original objective function without weight bias.
-
-\begin{figure}[!t]      
-    \centering
-        \subfloat[Weight norm]{\includegraphics[width=.8 \linewidth]{fig/fig12.eps}%
-        \label{fig: weight per layer NAC-CO}}
-    \vspace{-1mm}
-        \subfloat[Lagrange multipliers]{\includegraphics[width=.8 \linewidth]{fig/fig11.eps}%
-        \label{fig: multipliers NAC-CO}}
-        \caption{Weight norms and Lagrange multipliers of NAC-CO ($\beta=0.001$).}
-    \vspace{-2mm}
-        \label{fig: weight and multiplier}
-\end{figure}
-
-Furthermore, it is important to note that NAC-CO shows enhanced tracking performance with smaller weights than NAC-L2 and NAC-eMod.
-This implies that the weights in NAC-CO approach the different local optimal solution points from those of NAC-L2 and NAC-eMod.
-Therefore, if the physical analysis of the system is available to predict the feasible maximum control inputs, NAC-CO can find the local optimal solution without unnecessarily large control inputs by imposing proper weight norm constraints.
+%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
+%     \hline 
+%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
+%     \hline
+%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
+%     \hline
+%     \end{tabular}
+%     \label{table: control parameters}
+% \end{table}
+
+% **** CM1,2 control law *****
+The BSC used the control law defined in \eqref{eq. desired control} with $\hat f=[0,0]^\top$. Since BSC did not consider the unknown system dynamics, the approximation term $\hat f$ was set to zero.
+%CM1 has the following control gains and design parameters: $k_s=5,{k_z}=5, M_0=I_2, C_0=I_2, G_0=[0,0]^\top  $.
+% Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^\top$. 
+The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \estNN$.
+The adaptation law for DNN-BSC, as presented in \cite{Patil:2022aa}, was defined by
+\begin{equation}\label{eq:projection}
+\dot {\estwth}= \myproj_{\Omega}[\alpha  (\partial \estNN/\partial \estwth)M_0^{-1}{\tilde z}],
+\end{equation}
+where $\myproj_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{Krstic:1995aa}, which projects an input vector onto a convex set $\Omega$.
+The convex set was defined as ${\Omega}:= \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i:= \{\estwth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
+cstr weight ball}.
+% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\myproj_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\estwth$-space.).
+% **** CM3 control law *****
+
+The control law for DNN-BSC-A was the same as DNN-BSC, but with an auxiliary system to compensate for control input violations.
+Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq.
+cstr input ball}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq.
+cstr input saturation} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
+The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
+%considering $h(\cdot)$, saturated control input is defined as $s(\tau):= \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
+The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\R^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} =
+\tau_{(i)}-\text{sat}(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
+% s(\tau)-\tau$.
+The auxiliary state variables were used in the adaptation law \eqref{eq:projection} by substituting ${\tilde z}$ with ${\tilde z}+\zeta$.
+
+% **** CoNAC control law *****
+The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq.
+approximated control}.
+The update rates for the multipliers were set as $\beta_{j}=0.1$.
+The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
+
+For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
+Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
+The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ (from Eq.
+\eqref{eq.
+h func}).
+The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
+The sampling time of the simulations was selected as $T_s=10^{-4}$.
+% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+% The other parameters for CM1 to CoNAC were selected as listed in Table.~\ref{table: control parameters}.
+The same values were assigned across all the controllers for the common parameters for a fair comparison.
+
+\subsection{System Uncertainty Handling}
+
+\begin{comment}
+    The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
+    To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties.
+As a result,
+    %poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
+    %the parameters of CM1 are poorly tuned, 
+    BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.
+
+    By leveraging the DNN to compensate for the lumped system uncertainty within the BSC, DNN-BSC achieved improved tracking performance compared to BSC, as seen in Fig.~\ref{fig: tracking_CM2}.
+Fig.~\ref{fig: tracking_CM3} shows that DNN-BSC-A enhanced tracking performance for $q_2$, but tracking for $q_1$ remained unsatisfactory due to incomplete constraint handling, which will be discussed in detail in Section \ref{sec:sim_cnst}.
+    %By compensating the uncertain terms the control input of CM2 in Fig.~\ref{fig: control_CM2} is saturated.
+
+    Finally, CoNAC, which directly approximates the stabilizing control law along with the compensation term, demonstrated satisfactory tracking performance across both states, as illustrated in Fig.~\ref{fig: tracking_CoNAC}.
+
+    \subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}
+
+    The resulting control input $\tau$ and physically saturation control input $h(\tau)$ for the selected controllers are shown in Fig.~\ref{fig: control}.
+As illustrated in Fig.~\ref{fig: control_CM1}, BSC did not violate the input norm constraint (\ie $\tau = h(\tau)$).
+However, in DNN-BSC, the added compensation term from the DNN caused violations of the input norm constraint (\ie $\tau > h(\tau)$) at several points; see Fig.~\ref{fig: control_CM2}.
+This failure to account for the input norm constraint led to oscillations in the control input $\tau$.
+The DNN adaptation process attempted to increase the weights to reduce the residual errors that were not constrained by saturation, but after saturation ceased, the control input had to rapidly adjust back to realistic levels, leading to oscillatory behavior.
+Such high-frequency oscillations may induce instability in the control system or cause fatigue in the actuators.
+
+    On the other hand, both DNN-BSC-A and CoNAC successfully handled their imposed input constraints, as shown in Fig.~\ref{fig: control_CM3} and Fig.~\ref{fig: control_CoNAC}, respectively, without causing notable oscillations in the control input $\tau$ even after the input constraint was activated.
+However, the tracking performance of DNN-BSC-A was lower than that of DNN-BSC and CoNAC, as the auxiliary system used in DNN-BSC-A approximated the input norm constraint with an input bound constraint, creating a rectangular constraint in the $\tau$-space (see Fig.~\ref{fig: ball control}).
+In contrast, CoNAC satisfied the nonlinear input norm constraint and produced the physically maximum control input, resulting in improved tracking performance.
+
+    It is also important to note that the control input trajectory in DNN-BSC-A depends on the dynamics of the auxiliary system.
+The auxiliary system regulates the violated control input after sufficient auxiliary state $\zeta$ is generated to compensate for the violation.
+This can be observed in Fig.~\ref{fig: ball control}, where DNN-BSC-A exhibited minor violations of the input bound constraint.
+In contrast, CoNAC satisfied the constraint without being affected by such dynamics, as its Lagrange multiplier adjusted as soon as the constraint was violated.
+
+    %Meanwhile, CM2 and CM3 is based on BSC, and the desired controller $\tau^*$ of CoNAC is based on the BSC which may produce larger control input by canceling the stabilizing system dynamics.
+    %Therefore, CM2, CM3, and CoNAC produced the saturated control input.
+    %These control results show why the control saturation should be handled.
+
+    \subsection{Weight Norm Constraint Handling}
+
+    The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}.
+All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.
+
+    IN DNN-BSC, as shown in Fig.~\ref{fig: weight_CM2}, the weight norm of the last layer (\ie $\Vert {{{\hat \wth }_2}} \Vert$) fluctuated significantly over time, proportional to the control input norm.
+This is because the last layer’s weights directly determine the control input.
+When the control input violated the input norm constraint, the last layer’s weight norm hit the boundary and stayed there due to the projection operator.
+However, the projection operator only responded to violations without considering optimality or behavior.
+    %In the case of CM2 which does not consider the control input constraint, the weight norm of the last layer reaches the maximum weight norm value, when the control is saturated.
+    %It is because the weights get increased to produce larger control input to reduce the tracking error of $q_2$.
+(\ie the maximum magnitude of the control input depends on the weight norm of the last layer, since the activation function is bounded.)
+
+    In DNN-BSC-A, none of the weight norms reached their boundaries, as shown in Fig.~\ref{fig: weight_CM3}.
+This was due to the auxiliary system, where the auxiliary state $\zeta$ reduced the control input, ensuring it stayed within the input constraint.
+
+    In CoNAC, all weight norms complied with the imposed constraints through the constrained optimization approach, as illustrated in Fig.\ref{fig: weight_CoNAC}.
+When any weight norm approached its upper limit, the Lagrange multiplier was promptly activated to steer the weight adaptation direction towards a constraint-satisfactory point (see Fig.\ref{fig: multiplier_CoNAC}).
+Notably, the weight norms of the first and second layers ($\Vert {{{\hat \wth }_0}} \Vert$ and $\Vert {{{\hat \wth }_1}} \Vert$) remained nearly constant throughout the control period.
+The weight norm of the last layer $\Vert {{{\hat \wth }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint.
+This quasi-static behavior of the weight norm (\ie $d{\estwth}/dt=-\alpha\partial L/\partial \estwth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
+However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds.
+This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
+    %(\ie $\partial J/\partial\estwth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\estwth} c_j)$.
+    %, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.
+
+    The overall weight norms of CoNAC were larger than those of DNN-BSC and DNN-BSC-A, since CoNAC approximated the entire stabilizing control law, whereas DNN-BSC and DNN-BSC-A only approximated the system uncertainty term within the BSC framework.
+
+    %Because the simulation is implemented in a digital computer, the multipliers repeat to disappear and be generated, since the constraints are satisfied and violated in the digital process.
+
+    %\subsection{Analysis of the Neural Network}
+
+    %Generally, the existing literature states that the maximum norms of the weights should be sufficiently large (\ie $\bar\wth_i \gg 0$) since the designer does not know where the global optimal point of the weights is.
+    %However, using the physical prior knowledge of the system, one can guess the proper value of the maximum norm, since the magnitude of the control input depends on the last layer's weights due to the bounded activation function.
+    %Furthermore, the simulation study shows that the selected controllers have sufficiently good performances with the small maximum weight norms.
+    %It means that the local optimal point of the weights are more effective for the stability analysis and the limitating the control input's amplitude.
+
+    %Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
+    %However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}.
+(\ie the weight updates are smaller as its layer is closer to the input layer.)
+    %To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
+\end{comment}
 
@@
 
-%
-In this paper, a neuro–adaptive control method is proposed for uncertain Euler‒Lagrange systems, ensuring weight boundedness.
-Adaptation laws are derived by formulating a constrained optimization problem with weight norm constraints.
-The boundedness of the tracking error and the weight estimation are analyzed via Lyapunov analysis.
-The simulation results demonstrate that the proposed controller outperforms the existing methods in terms of tracking performance and parameter dependency.
-As further work, the state constraints for safety will be handled, ensuring stability.
-%
-
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{APPENDIX}
-
-% Appendixes should appear before the acknowledgment.
-
-% \section*{ACKNOWLEDGMENT}
-
-% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ.
-Avoid the stilted expression, ÒOne of us (R.
-B.
-G.) thanks .
+This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
+
+The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds.
+By formulating these constraints as part of the optimization process, CoNAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
+
+Simulation results validated the superior performance of CoNAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+CoNAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
+
+Future work may extend this approach to address constraints on both the system inputs and states, further enhancing the flexibility and robustness of neuro-adaptive control systems using constrained optimization.
+
+\begin{appendices}
+
+\section{Constraint Candidates}\label{sec:appen:cstr}
+
+This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller.
+
+\subsection{Input Bound Constraint}\label{sec:appen:input_bound_cstr}
+
+Most physical systems have control input limits due to electrical and mechanical limitations.
+These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+\begin{equation}
+    \begin{aligned}
+        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
+        \\
+        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+    \end{aligned}
+    \label{eq. cstr input saturation}
+\end{equation}
+with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
+% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
+The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
+\begin{equation}
+    \begin{aligned}
+        \pptfrac{\boldsymbol c_{\overline \tau}}{\estwth}
+        =& 
+        % \begin{bmatrix}
+        %     \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
+        %     \vdots \\
+        %     \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
+        % \end{bmatrix}
+        = 
+            -\pptfrac{\estNN}{\estwth}
+        %     \\
+        % =&
+        =
+        -\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+            \!\cdots\! &
+            (
+                \cdot
+            )
+        \end{bmatrix} 
+        \in
+        \mathbb R^{n\times \Xi}
+        , 
+        \\
+        \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
+        :=
+        & 
+        % \begin{bmatrix}
+        %     \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
+        %     \vdots \\
+        %     \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
+        % \end{bmatrix}
+        = 
+        +\pptfrac{\estNN}{\estwth}
+        % \\
+        % =&
+        =
+        +\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
+            \!\cdots\! &
+            (
+                \cdot
+            )
+        \end{bmatrix} 
+        \in
+        \mathbb R^{n\times \Xi}
         .
-.Ó  Instead, try ÒR.
-B.
-G.
-thanksÓ.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% {\footnotesize
+    \end{aligned}
+    \label{eq. nabla input sat}
+\end{equation}
+
+\subsection{Input Norm Constraint}\label{sec:appen:input_norm_cstr}
+
+Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
+Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
+This can be captured by the following inequality constraint:
+\begin{equation}
+    c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
+    \label{eq. cstr input ball}
+\end{equation}
+with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
+This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
+% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
+The gradients of $c_{u}$ with respect to $\estwth$ are given by
+\begin{equation}
+    \pptfrac{\boldsymbol c_{u}}{\estwth}
+    \!=\! 
+    -\textstyle\sum_{i=1}^n 2\tau_{(i)} 
+    \left(
+        \myrow_i
+        (
+            -\pptfrac{\estNN}{\estwth}
+        )
+    \right)^\top  
+    \!=\! 
+    \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
+    \in \mathbb R^{\Xi}.
+    \label{eq. nabla input ball}
+\end{equation}
+It should be noted that constraints \eqref{eq.
+cstr input saturation} and \eqref{eq.
+cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
+nabla input sat} and \eqref{eq.
+nabla input ball} are linearly dependent, violating the LICQ condition.
+
+\end{appendices}
+
+%  BIBLIOGRAPHY ============================================
+{\footnotesize
 \bibliographystyle{ieeetr}
-    \bibliography{\template/refs}
-% }
+% \bibliography{}
+\bibliography{\template/refs}}
 

### 2025-04-03 src/script_simulation/controllers/Aux/loadOpts.m

@@ -8,7 +8,7 @@ function opt = loadOpts(dt)
 
     opt.alpha = 8e-1;
     opt.rho = opt.alpha*0e-2;
-    opt.NN_size = [6,4,4,2];
+    opt.NN_size = [6,8,8,2];
     opt.W = 1;
     opt.e_size = 2;
 

### 2025-04-03 src/script_simulation/controllers/Aux/utils/nnForward.m

@@ -1,0 +1,46 @@
+function [nn, out] = nnForward(nn, opt, in)
+    
+    %% POINTER TO START POINT
+    pt_V = 1;
+    pt_tape = 1;
+
+    %% FORWARD
+    % save to gradient tape
+    nn.tape(1: 1+opt.NN_size(1)-1) = in;
+    pt_tape = pt_tape + opt.NN_size(1);
+
+    for l_idx = 1:1:opt.l_size-1
+        n = opt.NN_size(l_idx)+1;
+        m = opt.NN_size(l_idx+1);
+
+        % get V weight
+        V = reshape(nn.th(pt_V: pt_V+(n*m)-1), n,m);
+    
+        % phi_k = tanh(nn_out); 1]
+        if l_idx == 1
+            in = [in; 1]; % only one augmentation for 1st layer
+        else
+            in = [tanh(in); 1];
+        end
+
+        % forward
+        in = V'*in;
+        
+        % save to gradient tape
+        if l_idx~=opt.l_size-1
+            nn.tape(pt_tape: pt_tape+m-1) = in;
+        end
+
+        % pointer to next
+        pt_V = pt_V + (n*m);
+        pt_tape = pt_tape + m;
+    end
+
+    %% ERROR CHECK
+    assert(pt_V-1 == opt.th_size);
+%     assert(pt_tape-1 == opt.t_size);
+
+    %% TERMINATION
+    out = in;    
+
+end

### 2025-04-03 src/script_simulation/controllers/Aux/utils/nnWeightNorm.m

@@ -1,0 +1,13 @@
+function Vn = nnWeightNorm(th, nnOpt)
+
+    Vn = zeros(nnOpt.l_size-1,1);
+
+    cumsum_V = [0;cumsum(nnOpt.th_size_list)];
+    for l_idx = 1:1:nnOpt.l_size-1
+        start_pt = cumsum_V(l_idx)+1;
+        end_pt = cumsum_V(l_idx+1);   
+
+        Vn(l_idx) = norm(th(start_pt: end_pt));
+    end
+    
+end

### 2025-04-03 src/script_simulation/controllers/CoNAC/utils/nnCstr.m

@@ -2,6 +2,8 @@ function [c, cd] = nnCstr(nn, opt, u_NN, nnGrad)
     %% CONSTRAINTS PARAMETERS
     th_max = opt.cstr.th_max;
     u_ball = opt.cstr.u_ball;
+    uMax1 = opt.cstr.uMax1;
+    uMax2 = opt.cstr.uMax2;
     
     %% ERROR CHECK
     assert(length(th_max) == opt.l_size-1)
@@ -15,28 +17,40 @@ function [c, cd] = nnCstr(nn, opt, u_NN, nnGrad)
         start_pt = cumsum_th(l_idx)+1;
         end_pt = cumsum_th(l_idx+1);   
 
-        c_b(l_idx) = norm(nn.th(start_pt: end_pt))^2 ...
-            - th_max(l_idx)^2;
+        c_b(l_idx) = .5*(norm(nn.th(start_pt: end_pt))^2 ...
+            - th_max(l_idx)^2);
     end
     
     % input saturation 
     u = u_NN;
     
     % input ball
-    c_ub = norm(u)^2 - u_ball^2;
+    c_ub = .5*(norm(u)^2 - u_ball^2);
+
+    % input 1
+    c_uM1 = u(1) - uMax1;
+    c_uM2 = u(2) - uMax2;
+    c_um1 = -uMax1 - u(1);
+    c_um2 = -uMax2 - u(2);
 
     % summary
-    c = [c_b; c_ub];
+    c = [c_b; c_ub; c_uM1; c_uM2; c_um1; c_um2];
     
     %% ACTIVE SET CONSTRAINT GRADIENT CALC
     cd = zeros(length(c), opt.th_size);
     for l_idx = 1:1:length(th_max)
         start_pt = cumsum_th(l_idx)+1;
         end_pt = cumsum_th(l_idx+1);
-        cd(l_idx, start_pt:end_pt) = 2 * nn.th(start_pt:end_pt,1);
+        cd(l_idx, start_pt:end_pt) = nn.th(start_pt:end_pt,1);
     end
     
-    cd(l_idx+1:end, :) = 2*u(1)*nnGrad(1,:) + 2*u(2)*nnGrad(2,:);
+    cd(l_idx+1:end, :) = [
+        u(1)*nnGrad(1,:) + u(2)*nnGrad(2,:);
+        nnGrad(1,:);
+        nnGrad(2,:);
+        -nnGrad(1,:);
+        -nnGrad(2,:);
+    ];
 end
 
 

### 2025-04-03 src/script_simulation/controllers/loadGlobalOpts.m

@@ -1,0 +1,51 @@
+function opt = loadGlobalOpts(dt, CONTROL_NUM)
+    opt.dt = dt;
+
+    opt.e_tol = 0e-3;
+    opt.init_range = 1e-3;
+    
+    opt.Lambda = diag([1 1]) * 5e0;
+
+    opt.alpha = 7.5e-1;
+    opt.rho = opt.alpha*0e-2;
+    opt.NN_size = [6,4,4,2];
+    opt.W = 1;
+    opt.e_size = 2;
+
+    opt.cstr.th_max = [11;12;13] * 1e0;
+    opt.cstr.u_ball = 6.5;
+    opt.cstr.uMax1 = 6;
+    opt.cstr.uMax2 = 2.5;
+
+    if CONTROL_NUM == 1
+        % opt.beta = [1 1 1] * 1e-1;
+        opt.beta(1:3) = [1 1 1] * 0e-3;
+        opt.beta(4) = 1e3; % control ipnut ball
+        opt.beta(5) = 1e3; % control ipnut 1 Max
+        opt.beta(6) = 0e4; % control ipnut 2 Max
+        opt.beta(7) = opt.beta(5); % control ipnut 1 Min
+        opt.beta(8) = opt.beta(6); % control ipnut 2 Min
+        opt.beta = opt.beta/opt.alpha;
+
+        c_num = length(opt.beta);
+        opt.lbd = zeros(c_num,1);
+
+    elseif CONTROL_NUM == 2
+        opt.A_zeta = -10 * eye(2);
+        opt.B_zeta = 1000 * eye(2);
+    end
+    
+%% PASSIVE NUMBER
+    % layer number
+    opt.l_size = length(opt.NN_size);
+    % total tape number
+    opt.tp_size = sum(opt.NN_size(1:end-1));
+    % total weight number (will be calc-ed)
+    opt.th_size_list = zeros(opt.l_size-1 ,1);    
+    for idx = 1:1:opt.l_size-1
+        opt.th_size_list(idx) = (opt.NN_size(idx)+1) * opt.NN_size(idx+1);
+    end
+
+    opt.th_size = sum(opt.th_size_list);    
+
+end

### 2025-04-03 src/script_simulation/main_TNNLS.m

@@ -14,6 +14,9 @@ ANIMATION_FLAG      = 0;
 AINMATION_SAVE_FLAG = 0;
 FIGURE_SAVE_FLAG    = 0;
 RESULT_SAVE_FLAG    = 0;
+CONTROL_NUM = 1;    % 1: CoNAC, 2: Aux.
+
+seed = 18; rng(seed);
 
 %% SIMULATION SETTING
 ctrl_dt = 1/250;
@@ -34,9 +37,20 @@ x2 = [0;0];
 u = [0;0];
 
 %% CONTROLLER LOAD
-addpath("controllers/CoNAC");
-addpath(genpath('controllers/CoNAC'))
-opt = loadOpts(ctrl_dt);
+%  TODO: design more controllers
+if CONTROL_NUM == 1    % CoNAC
+    ctrl_path = "CoNAC";
+elseif CONTROL_NUM == 2 % Aux.
+    ctrl_path = "Aux";
+end
+
+addpath("controllers/"+ctrl_path);
+addpath(genpath('controllers/'+ctrl_path));
+
+% opt = loadOpts(ctrl_dt);
+addpath("controllers");
+opt = loadGlobalOpts(ctrl_dt, CONTROL_NUM);
+
 initControl;
 
 %% RECORDER INITIALIZATION
@@ -56,21 +70,12 @@ for t_idx = 2:1:num_t
     r = e2 + opt.Lambda * e1;
 
     if t_idx==2 || rem(t(t_idx)/dt, ctrl_dt/dt) == 0
-        x_in = [x1;x2;r];
-
-        [nn, u_NN] = nnForward(nn, opt, x_in);
-        [nn, opt] = nnBackward(nn, opt, r, u_NN);
-        u = u_NN;
-        % u = zeros(size(u));
+        preControl
+        postControl
     end
 
     % control input saturation
-    if norm(u) > opt.cstr.u_ball
-        u_bar = opt.cstr.u_ball;
-        u_sat = u / norm(u) * u_bar;
-    else
-        u_sat = u;
-    end 
+    u_sat = sat(u, opt, CONTROL_NUM);
 
     % error check
     assert(~isnan(norm(u)));
@@ -97,42 +102,64 @@ if FIGURE_PLOT_FLAG
 end
 
 if RESULT_SAVE_FLAG
-    data_name = [
-        "$t$";
-        "$q_1$";
-        "$q_2$";
-        "$\dot{q}_1$";
[…]

### 2025-04-03 src/script_simulation/main_plotter.m

@@ -1,0 +1,353 @@
+clear
+
+%%
+SAVE_FLAG = 0;
+POSITION_FLAG = 1; % it will plot fiugures in the same position
+gray = "#808080";
+
+more_blue = "#0072BD";
+more_red = "#A2142F";
+
+%% 
+ctrl1_name = "3-Apr-2025_17-38-31"; % CoNAC
+ctrl2_name = "3-Apr-2025_17-38-57"; % Aux.
+
+%%
+ctrl1_log = load("sim_result/"+ctrl1_name+".mat");
+ctrl2_log = load("sim_result/"+ctrl2_name+".mat");
+
+%% RESULT PLOTTER
+T = ctrl1_log.T;
+t = ctrl1_log.t;
+obs_t = 1:length(t);
+opt1 = ctrl1_log.opt;
+opt2 = ctrl2_log.opt;
+
+c1_x1 = ctrl1_log.x1_hist;
+c1_x2 = ctrl1_log.x2_hist;
+c1_xd1 = ctrl1_log.xd1_hist;
+c1_xd2 = ctrl1_log.xd2_hist;
+c1_u = ctrl1_log.u_hist;
+c1_uSat = ctrl1_log.uSat_hist;
+c1_lbd = ctrl1_log.lbd_hist;
+c1_th = ctrl1_log.th_hist;
+
+c2_x1 = ctrl2_log.x1_hist;
+c2_x2 = ctrl2_log.x2_hist;
+c2_xd1 = ctrl2_log.xd1_hist;
+c2_xd2 = ctrl2_log.xd2_hist;
+c2_u = ctrl2_log.u_hist;
+c2_uSat = ctrl2_log.uSat_hist;
+c2_lbd = ctrl2_log.lbd_hist;
+c2_zeta = ctrl2_log.zeta_hist;
+c2_th = ctrl2_log.th_hist;
+
+u_max1 = opt1.cstr.uMax1;
+u_max2 = opt1.cstr.uMax2;
+u_ball = opt1.cstr.u_ball;
+th_max = opt1.cstr.th_max;
+
+%%
+font_size = 16;
+line_width = 2;
+lgd_size = 12;
+    
+fig_height = 210 * 1; 
+fig_width = 450 * 1;
+
+% font_size = 20;
+% line_width = 2;
+% lgd_size = 16;
+    
+% fig_height = 230 * 1; 
+% fig_width = 800 * 1;
+
+% ctrl_start = .75;
[…]

### 2025-04-03 src/script_simulation/models/model1_load.m

@@ -9,6 +9,8 @@ grad_x = @(q, u, t) model_wrapper(q, u, t);
 end
 
 %% Local function
+
+
 % ********************************************************
 function f = model_wrapper(q, u, t)
     [M, C, G, F ] = model1(q, t);

### 2025-04-03 src/script_simulation/models/ref4_load.m

@@ -5,16 +5,19 @@ r_func = @(t) ref_gen(t);
 end
 
 function [r1,r2] = ref_gen(t)
-    x0 = [deg2rad(-90);0];  
-    xd = [0;deg2rad(10)];
-    T = 3;    
+    x0 = deg2rad([-90;0]);  
+    xd1 = deg2rad([-45;135]);
+    xd2 = deg2rad([45;-45]);
+    T = 2;    
 
-    t = mod(t, 2*T);
+    t = mod(t, 3*T);
 
     if t < T
-        [r1,r2] = poly_filter(x0, xd, T, t);
+        [r1,r2] = poly_filter(x0, xd1, T, t);
+    elseif t < 2*T
+        [r1,r2] = poly_filter(xd1, xd2, T, (t-T));
     else
-        [r1,r2] = poly_filter(xd, x0, T, (t-T));
+        [r1,r2] = poly_filter(xd2, x0, T, (t-2*T));
     end
 end
 

### 2025-04-03 src/script_simulation/models/sat.m

@@ -1,0 +1,20 @@
+function u = sat(u, opt, CONTROL_NUM)
+    u_ball = opt.cstr.u_ball;
+    uMax1 = opt.cstr.uMax1;
+    uMax2 = opt.cstr.uMax2;
+
+    if norm(u) > u_ball
+        u = u/norm(u)*u_ball;
+    end
+
+    % if CONTROL_NUM == 1 && (u(2) > uMax2 || u(2) < -uMax2)
+    %     uMax2 = uMax2*sign(u(2));
+    %     u(1) = uMax2*u(1)/u(2);
+    %     u(2) = uMax2;
+    % end
+    if u(1) > uMax1 || u(1) < -uMax1
+        uMax1 = uMax1*sign(u(1));
+        u(2) = uMax1*u(2)/u(1);
+        u(1) = uMax1;
+    end
+end

### 2025-04-03 src/script_simulation/recorder/recInit.m

@@ -1,5 +1,4 @@
 
-fprintf("                                 \n");
 fprintf("\n");
 fprintf(" FLAGs\n");
 fprintf("     animation      : "+string(ANIMATION_FLAG)+"\n");
@@ -26,7 +25,14 @@ u_hist = zeros(num_u, num_t); u_hist(:, 1) = u;
 uSat_hist = zeros(num_u, num_t); uSat_hist(:, 1) = u;
 
 %% 
-lbd_hist = zeros(length(opt.beta), num_t); lbd_hist(:,1) = zeros(length(opt.beta),1);
-th_hist = zeros(opt.l_size-1, num_t); th_hist(:, 1) = nnWeightNorm(nn.th, opt);
+if CONTROL_NUM == 1
+    % CoNAC
+    lbd_hist = zeros(length(opt.beta), num_t); lbd_hist(:,1) = zeros(length(opt.beta),1);
+    th_hist = zeros(opt.l_size-1, num_t); th_hist(:, 1) = nnWeightNorm(nn.th, opt);
+elseif CONTROL_NUM == 2
+    % Aux.
+    th_hist = zeros(opt.l_size-1, num_t); th_hist(:, 1) = nnWeightNorm(nn.th, opt);
+    zeta_hist = zeros(num_u, num_t); zeta_hist(:, 1) = z;
+end
 
 % aux_hist = zeros(num_x/2, num_t);

### 2025-04-03 src/script_simulation/recorder/recRecord.m

@@ -5,7 +5,12 @@ xd2_hist(:, t_idx) = xd2;
 
 u_hist(:, t_idx) = u;
 uSat_hist(:, t_idx) = u_sat;
-lbd_hist(:, t_idx) = opt.lbd;
 th_hist(:, t_idx) = nnWeightNorm(nn.th, opt);
 
-% aux_hist(:, t_idx) = zeta;
+if CONTROL_NUM == 1
+    % CoNAC
+    lbd_hist(:, t_idx) = opt.lbd;
+elseif CONTROL_NUM == 2
+    % Aux.
+    zeta_hist(:, t_idx) = z;
+end

### 2025-04-03 src/script_simulation/utils/plot_wrapper.m

@@ -24,9 +24,19 @@ u1_sat = uSat_hist(1,:);
 u2_sat = uSat_hist(2,:);
 
 th = th_hist;
-L = lbd_hist;
 
-% dot_L = dot_L_hist;
+if CONTROL_NUM == 1
+    % CoNAC
+    L = lbd_hist;
+elseif CONTROL_NUM == 2
+    % Aux.
+    z1 = zeta_hist(1,:);
+    z2 = zeta_hist(2,:);
+end
 
 %% 
-plotter1
+if CONTROL_NUM == 1
+    plotter1
+elseif CONTROL_NUM == 2
+    plotter2
+end

### 2025-04-03 src/script_simulation/utils/plotter2.m

@@ -155,21 +155,16 @@ hF = gcf;
 hF.Position(3:4) = [fig_width, fig_height];
 tl = tiledlayout(2, 1);
 
-
-for l_idx = 1:1:size(L, 1)
-    c = rand(1,3);
-
-    % plot(t, L(l_idx, :), 'color', c, 'DisplayName',"$\lambda_"+string(l_idx)+"$" ...
-    % , "LineWidth", line_width, "LineStyle", "-"); hold on
-    semilogy(t, L(l_idx, :), 'color', c, 'DisplayName',"$\lambda_"+string(l_idx)+"$" ...
-    , "LineWidth", line_width, "LineStyle", "-"); hold on
-end
-grid on
+nexttile(1);
+p2 = plot(t, z1, "Color", "blue", "LineWidth", line_width, "LineStyle", "-."); hold on
 xlabel("Time $[\rm s]$", "Interpreter", "latex")
-ylabel("$\lambda_i$ (log scale)", "Interpreter", "latex")
+ylabel("Zeta 1 $[\rm rad]$", "Interpreter","latex")
 set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
-lgd = legend;
-lgd.Orientation = 'horizontal';
-lgd.Location = 'northoutside';
-lgd.Interpreter = 'latex';
-lgd.FontSize = lgd_size;
+grid on
+
+nexttile(2);
+p2 = plot(t, z2, "Color", "blue", "LineWidth", line_width, "LineStyle", "-."); hold on
+xlabel("Time $[\rm s]$", "Interpreter", "latex")
+ylabel("Zeta 2 $[\rm rad]$", "Interpreter","latex")
+set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+grid on

### 2025-04-05 manuscript.tex
move to Elsevier

@@
-\documentclass[lettersize,journal]{IEEEtran}
-% code
-
-\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}
+%% 
+%% Copyright 2007-2025 Elsevier Ltd
+%% 
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.3 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.3 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%% 
+%% Template article for Elsevier's document class `elsarticle'
+%% with harvard style bibliographic references
+
+% \documentclass[preprint,12pt,authoryear]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times,authoryear]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
+\documentclass[final,3p,times,authoryear]{elsarticle}
+% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
+%% \documentclass[final,5p,times,authoryear]{elsarticle}
+% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
 
@@
 \newcommand*{\template}{template}
-\input{\template/preamble/preamble_conf.tex}
+\input{\template/preamble/preamble_Elsevier.tex}
 
 \newcommand*{\fe}{\mv{r}}
+\DeclareMathOperator{\mypoly}{Poly} % filtered error
+
+\newcommand*{\figSize}{.99}
+
+% %% The amssymb package provides various useful mathematical symbols
+% \usepackage{amssymb}
+% %% The amsmath package provides various useful equation environments.
+% \usepackage{amsmath}
+% %% The amsthm package provides extended theorem environments
+% %% \usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
+
+\journal{Nuclear Physics B}
 
 \begin{document}
+
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for theassociated footnote;
+%% use the fnref command within \author or \affiliation for footnotes;
+%% use the fntext command for theassociated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for theassociated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \affiliation{organization={},
+%%            addressline={}, 
+%%            city={},
+%%            postcode={}, 
+%%            state={},
+%%            country={}}
+%% \fntext[label3]{}
+
 \title{
   Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
-%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
-}
-
-\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
-~Vol.~00, No.~0, Month~2024
-}%
-{How to Use the IEEEtran \LaTeX \ Templates}
-
-\maketitle
-
+} %% Article title
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{}
+%% \affiliation[label1]{organization={},
+%%             addressline={},
+%%             city={},
+%%             postcode={},
+%%             state={},
+%%             country={}}
+%%
+%% \affiliation[label2]{organization={},
+%%             addressline={},
+%%             city={},
+%%             postcode={},
+%%             state={},
+%%             country={}}
+
+\author{
+  Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
+} %% Author name
+
+%% Author affiliation
+\affiliation{organization={
+  Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST)
+},%Department and Organization
+            addressline={123 Cheomdangwagi-ro, Buk-gu}, 
+            city={Gwangju},
+            postcode={61005}, 
+            state={},
+            country={Korea}}
+
+%% Abstract
 \begin{abstract}
@@
 
-\begin{IEEEkeywords}
-Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
-\end{IEEEkeywords}
+%%Graphical abstract
+\begin{graphicalabstract}
+%\includegraphics{grabs}
+\end{graphicalabstract}
+
+%%Research highlights
+\begin{highlights}
+\item Research highlight 1
+\item Research highlight 2
+\end{highlights}
+
+%% Keywords
+\begin{keyword}
+Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep Euler-Lagrange system \sep input constraint
+
+%% keywords here, in the form: keyword \sep keyword
+%% PACS codes here, in the form: \PACS code \sep code
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+
+\end{keyword}
+
+\end{frontmatter}
+
+%% Add \usepackage{lineno} before \begin{document} and uncomment 
+%% following line to enable line numbers
+%% \linenumbers
+
+%% main text
+%%
 
@@
 
-\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
+Many engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
 These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
@@
 Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
-SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}.
 Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
@@
 In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
-Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
+Candidates of input constraints are presented in \ref{sec:appen:cstr}.
 Section \ref{sec:stability} analyzes the stability of the proposed controller.
@@
     \le 0
-    \label{eq:cstr:weight_ball}
+    \label{eq:cstr:weight:ball}
 \end{equation}
@@
     \end{cases} 
-    \label{eq:cstr:weight_ball:grad}
-\end{equation}
-Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.
+    \label{eq:cstr:weight:ball:grad}
+\end{equation}
+Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.
 
@@
     For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$.
-    This holds with the weight norm constraint \eqref{eq:cstr:weight_ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
+    This holds with the weight norm constraint \eqref{eq:cstr:weight:ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
 \end{theorem}
@@
 %  SECTION SIMULATION ======================================
-\section{Simulation}\label{sec:sim}
-
-\subsection{Setup}
-
+\section{Implementation and Validation}\label{sec:sim}
+
+The proposed CoNAC was validated via numerical simulations and real-time experiments on a two-link manipulator.
+
+\subsection{Numerical Simulation Validation}
+
+% ------------------------------------
+% Robot Model and Reference Trajectory
+% ------------------------------------
 The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
-The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
-%This model contains terms of gravity and friction in its mechanical system.
-%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
-%and can be considered as the disturbance of the system.
-The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for $\q=[q_1,q_2]^\top $ was defined as
+The system dynamics of the two-link manipulator is described by the following equations:
+\MSRY{ADD MORE DETAIL; Following Eqn is just example}
+\begin{equation}
+    \begin{aligned}
+        \mm M(\q) \ddtt{\q} + \mm V_m(\q,\dot\q) + \mm F(\q,\dot\q) + \mm G(\q) = \mv\tau,
+        \\
+        \mv\tau = \estNN(\q,\dot\q),
+    \end{aligned}
+    \label{eq:robot_dynamics}
+\end{equation}
+The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ \MSRY{more parameters} denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+The values of the system model parameters are provided in Table~\ref{table:system:params}. 
+The desired trajectory for $\q=[q_1,q_2]^\top $ was defined with \MSRY{5th Poly functions} as
 \begin{equation}
@@
   =
-    \begin{bmatrix}
-        +\cos(0.5\pi t) + 1 \\
-        -\cos(0.5\pi t) - 1 
-    \end{bmatrix}.
-\end{equation}
-%\color{red}
-%Considering the power limitation of the power source for the actuators [], 
-The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
-\begin{equation}
-    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
-    \label{eq. h func}
-\end{equation}
-with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
-The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.
-
-In addition to this physically imposed control input saturation, the input norm constraint \eqref{eq.
-cstr input ball} was imposed to ensure that the control input $\tau$ stays within the unsaturation region of $h(\tau)$ and to prevent inefficient use of the input.
-With a sufficiently large value for $p$, the input norm constraint essentially matches the control input saturation function.
-Note that among the selected controllers given below, only the proposed CoNAC can rigorously handle this input norm constraint.
-
-% **********************************************************
-% SYSTEM FIGURE AND TABLE
-\begin{figure}[!t]
+  \begin{cases}
+    \mypoly(\q_0,\q_1,t_f,t)
+      & \text{if } 0\le t < t_f \\
+    \mypoly(\q_1,\q_2,t_f,t-t_f)
+      & \text{if } t_f\le t < 2t_f \\
+    \mypoly(\q_2,\q_3,t_f,t-2t_f)
+      & \text{if } 2t_f\le t < 3t_f \\
+    \mypoly(\q_3,\q_0,t_f,t-3t_f)
+      & \text{if } 3t_f\le t < 4t_f \\
+  \end{cases}
+  ,
+  \label{eq:desired trajectory}
+\end{equation}
+where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, $\q_3=[0,\pi/2]^\top$, and $t_f=5$ s.
+\MSRY{VIDEO IS PROVIDED; IF WE CAN PROVIDE}
+
+% ------------------------------------
+% Control Input Saturation
+% ------------------------------------
+To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the following control input saturations were imposed:
+\begin{equation}
+  \mysat(\mv\tau) 
+  =
+  ,
+  \label{eq:control input saturation}
+\end{equation}
+where $\bar\tau=50, \bar\tau_1$ and $\bar\tau_2$ are the saturation limit values for the norm of the control input and the first and second links, respectively.
+
+% ------------------------------------
+% Robot Model Figure and Table
+% ------------------------------------
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
+    \includegraphics[width=0.5\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
 
-\begin{table}[!t]
+\begin{table}[t]
     \renewcommand{\arraystretch}{1.3}
@@
     \hline
+    ${f_s}_p$  & ?? $p\textsuperscript{th}$ link &   (Nm) &  (Nm) \\
+    \hline
     \end{tabular}
-    \label{table: system parameters}
+    \label{table:system:params}
 \end{table}
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
-    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
-    \label{fig: h func}
-\end{figure}
-
-% SYSTEM FIGURE AND TABLE
-% **********************************************************
-Four controllers were examined for a comparative study.
-The first was the Backstepping Controller (BSC), used as the baseline.
-The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro-adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC.
-While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints.
-The third was DNN-BSC augmented with an auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint.
+% ------------------------------------
+% Controllers
+% ------------------------------------
+For a comparative study, NAC with the auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (NAC-AUX) was implemented, which only considered the input bound constraint introcuded in \ref{sec:appen:cstr:input:norm} and not the nonlinear input norm constraint \eqref{eq:cstr:input:norm}.
 As a result, an approximation of the input norm constraint was used as an input bound constraint. 
-Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework.
+Besides, the proposed controller, CoNAC, rigorously considered the weight norm constraint, and input bound and norm constraints within a constrained optimization framework. 
 The properties of these four controllers are summarized in Table \ref{table:controller}.
-%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).
-
-\begin{table}[!t]
+
+% ------------------------------------
+% NAC-AUX
+% ------------------------------------
+The control law for NAC-AUX was the same CoNAC, but with an auxiliary system to compensate for control input violations. 
+Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq:cstr:input:norm}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq:cstr:input:bound} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
+The comparison between the original input norm constraint and its approximation is shown in Fig.~\MSRY{ADD FIGURE}.
+The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\mv{\tau},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta=-[20,0;0;20],\mm{B}_\zeta=[10,0;0,10]$\MSRY{SEE HERE}, and $\Delta\tau_{(i)} =
+\tau_{(i)}-\mysat(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
+The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
+
+% ------------------------------------
+% CoNAC
+% ------------------------------------
+The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq:control:est}. 
+The update rates for the multipliers were set as \MSRY{SEE HERE}$\beta_{j}=0.1$. The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
+
+% ------------------------------------
+% Controller Parameters
+% ------------------------------------
+For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
+Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
+The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ \MSRY{SEE HERE}.
+The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
+The sampling time of the simulations was selected as $T_s=10^{-4}$.
+% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+The parameters for CoNAC to NAC-AUX were listed in Table.~\ref{table:controller:params}. 
+% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+
+% ------------------------------------
+% Controller Table
+% ------------------------------------
+\begin{table}[t]
   \renewcommand{\arraystretch}{1.3}
@@
   \centering
-    \begin{tabular}{|c||c|c|c|}
-    \hline
-    & \multicolumn{3}{c|}{Handling Capability}\\
-    \hline
-    & System & Weight Norm & Input Norm\\
-    &  Uncertainty & Constraint & Constraint\\
-    \hline 
-    BSC     & X & X & X\\
-    \hline
-    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
-         &  & (by projection) & \\
-    \hline
-    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
-       &  & (by projection) &  (by aux. system)\\
-       % &  & & linearized constraint)\\
-    % \hline
-    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
-    %    &  & (by projection) &  system for \\
-    %    &  & & linearized constraint)\\
-    \hline
-    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
-         &  & (by optimization) & (by optimization)\\
+  \begin{tabular}{c c c}
+  \hline
+  & \multicolumn{2}{c}{\bf{Handling Capability}}\\
+  \hline
+  \hline
+  & Weight Norm Constraint & Input Norm Constraint\\
+  \hline
+  \hline
+  \multirow{2}{*}{\bf{CoNAC}} & O & $\triangle$ \\
+     & (by projection) &  (by aux. system)\\
+  \hline
+  \multirow{2}{*}{\bf{NAC-AUX}} & O & O\\
+     & (by optimization) & (by optimization)\\
   \hline
@@
 
-% \begin{table}
-% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
-% \centering
-% {\begin{tabular}{cc}\textcolor{black}ine
-% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
-% Rated power & 3 kW\\
-% Rated speed & 4500 RPM\\
-% Rated torque & 6.4 Nm\\
-% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
-% $I_{max}$ & 15 A \\
-% $V_{dc}$ & 100 V\\
-% $R_s$ & 0.34 $\Omega$\\
-% $P$ & 3\\
-% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
-% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
-% \multirow{2}{*}{Controller} & TMS320F28377D\\
-% & (Texas Instrument) \\
-% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
-%  & (Infineon Technologies)
-% \\\textcolor{black}ine
-% \end{tabular}}
-% \end{table}
-
-% \begin{table}[!t]
-%     \renewcommand{\arraystretch}{1.3}
-%     \caption{Common Parameters of Selected Controllers.}
-%     \label{table: error norm}
-%     \centering
-%     \begin{tabular}{|c||c|c|c|c|c|c|}
+% ------------------------------------
+% Controller Parameters
+% ------------------------------------
+\begin{table}[t]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Parameters of the controllers used in simulation}
+  \label{table:controller:params}
+  \centering
+  \begin{tabular}{c | c c c c c c c c c c c c c c}
+  \hline
+  & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\bar\theta_0$ & $\bar\theta_1$ & $\bar\theta_2$ & $\bar\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
+  \hline
+  \hline
+    \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
   % \hline
-%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
-%     \hline 
-%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
-%     \hline
-%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
-%     \hline
-%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
-%     \hline
-%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
-%     \hline
-%     \end{tabular}
-%     \label{table: control parameters}
-% \end{table}
-
-% **** CM1,2 control law *****
-The BSC used the control law defined in \eqref{eq. desired control} with $\hat f=[0,0]^\top$. Since BSC did not consider the unknown system dynamics, the approximation term $\hat f$ was set to zero.
-%CM1 has the following control gains and design parameters: $k_s=5,{k_z}=5, M_0=I_2, C_0=I_2, G_0=[0,0]^\top  $.
-% Since CM1 does not consider the unknown term, $\hat f$ was set to $[0,0]^\top$. 
-The control law for DNN-BSC was the same as BSC, but the unknown system dynamics were approximated by a DNN \ie $\hat f\approx \estNN$.
-The adaptation law for DNN-BSC, as presented in \cite{Patil:2022aa}, was defined by
-\begin{equation}\label{eq:projection}
-\dot {\estwth}= \myproj_{\Omega}[\alpha  (\partial \estNN/\partial \estwth)M_0^{-1}{\tilde z}],
-\end{equation}
-where $\myproj_{\Omega}(\cdot)$ is the projection operator \cite[Appendix E, eq.~(E.4)]{Krstic:1995aa}, which projects an input vector onto a convex set $\Omega$.
-The convex set was defined as ${\Omega}:= \{\Omega_0\,\cap\,\cdots\,\cap\, \Omega_k\}$, where $\Omega_i:= \{\estwth_i\ \vert \ c_{b_i}\le 0\}, \ \forall i\in[0,\cdots, k]$, representing the weight norm constraint \eqref{eq.
-cstr weight ball}.
-% The maximum control input ball constraint is not addressed since the stability analysis of \cite{RN16} uses the property that  $\myproj_\Omega(\cdot)$ projects to the convex set, (\ie the constraints are generally non-convex on the $\estwth$-space.).
-% **** CM3 control law *****
-
-The control law for DNN-BSC-A was the same as DNN-BSC, but with an auxiliary system to compensate for control input violations.
-Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq.
-cstr input ball}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq.
-cstr input saturation} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
-The comparison between the original input norm constraint and its approximation is shown in Fig.~\ref{fig: ball control}.
-%considering $h(\cdot)$, saturated control input is defined as $s(\tau):= \min(\max(\tau,-\bar\tau_s),\bar\tau_s)$, where $\bar\tau_s$ is $(\bar\tau/\sqrt{2}+\bar\tau)/2$;
-The auxiliary system is defined as $\dot\zeta = A_\zeta \zeta + B_\zeta \Delta\tau,\quad \zeta\vert_{t=0} = 0$, where $\zeta\in\R^n$ denotes the auxiliary state, $A_\zeta=-[20,0;0;20],B_\zeta=[10,0;0,10]$, and $\Delta\tau_{(i)} =
-\tau_{(i)}-\text{sat}(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
-% s(\tau)-\tau$.
-The auxiliary state variables were used in the adaptation law \eqref{eq:projection} by substituting ${\tilde z}$ with ${\tilde z}+\zeta$.
-
-% **** CoNAC control law *****
-The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq.
-approximated control}.
-The update rates for the multipliers were set as $\beta_{j}=0.1$.
-The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
-
-For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
-Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
-The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ (from Eq.
-\eqref{eq.
-h func}).
-The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
-The sampling time of the simulations was selected as $T_s=10^{-4}$.
-% The same values were assigned across all the controllers for the common parameters for a fair comparison.
-% The other parameters for CM1 to CoNAC were selected as listed in Table.~\ref{table: control parameters}.
-The same values were assigned across all the controllers for the common parameters for a fair comparison.
-
-\subsection{System Uncertainty Handling}
-
-\begin{comment}
+    \bf{NAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
+  \hline
+  \end{tabular}
+\end{table}
+
+\begin{figure}[t]
+  \centering
+    \subfloat[Tracking result of $d$-axis stator current .]{
+      \includegraphics[width=\figSize\linewidth]
+      {
+        src/mearsurement/figures/Fig1.eps
+      }%
+      \label{fig:ctrl:result:q1}}
+    \vspace{2mm}
+    \subfloat[Tracking result of $d$-axis stator current .]{
+      \includegraphics[width=\figSize\linewidth]
+      {
+        src/mearsurement/figures/Fig2.eps
+      }%
+      \label{fig:ctrl:result:q2}}
+    \vspace{2mm}
+      \subfloat[Control input.]{
+        \includegraphics[width=\figSize\linewidth]
+        {
+          src/mearsurement/figures/Fig3.eps
+        }%
+        \label{fig:ctrl:result:tau:1}}
+    \vspace{2mm}
+      \subfloat[Control input.]{
+        \includegraphics[width=\figSize\linewidth]
+        {
+          src/mearsurement/figures/Fig4.eps
+        }%
+        \label{fig:ctrl:result:tau:2}}
+  \caption{
+  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
+  }
+\label{fig:ctrl:result}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+    \subfloat[Tracking result of $d$-axis stator current .]{
+      \includegraphics[width=\figSize\linewidth]
+      {
+        src/mearsurement/figures/Fig5.eps
+      }%
+      \label{fig:ctrl:result:opt:norm}}
+    \vspace{2mm}
+    \subfloat[Tracking result of $d$-axis stator current .]{
+      \includegraphics[width=\figSize\linewidth]
+      {
+        src/mearsurement/figures/Fig6.eps
+      }%
+      \label{fig:ctrl:result:opt:multiplier}}
+    \vspace{2mm}
+      \subfloat[Control input.]{
+        \includegraphics[width=\figSize\linewidth]
+        {
+          src/mearsurement/figures/Fig8.eps
+        }%
+        \label{fig:ctrl:result:opt:zeta}}
+  \caption{
+  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
+  }
+  \label{fig:ctrl:result:opt}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+      \includegraphics[width=.3\linewidth]
+      {
+        src/mearsurement/figures/Fig9.eps
+      }%
+  \caption{
+  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line.
+  }
+  \label{fig:ctrl:result:conrol}
+\end{figure}
+
+\subsubsection{System Uncertainty Handling}
+
 The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
@@
 %To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
-\end{comment}
 
@@
 
-\begin{appendices}
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+\appendix
 
@@
 
-\subsection{Input Bound Constraint}\label{sec:appen:input_bound_cstr}
+\subsection{Input Bound Constraint}\label{sec:appen:cstr:input:bound}
 
@@
     \end{aligned}
-    \label{eq. cstr input saturation}
+    \label{eq:cstr:input:bound}
 \end{equation}
@@
     \end{aligned}
-    \label{eq. nabla input sat}
-\end{equation}
-
-\subsection{Input Norm Constraint}\label{sec:appen:input_norm_cstr}
+    \label{eq:cstr:input:bound:grad}
+\end{equation}
+
+\subsection{Input Norm Constraint}\label{sec:appen:cstr:input:norm}
 
@@
     c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
-    \label{eq. cstr input ball}
+    \label{eq:cstr:input:norm}
 \end{equation}
@@
     \in \mathbb R^{\Xi}.
-    \label{eq. nabla input ball}
+    \label{eq:cstr:input:norm:grad}
 \end{equation}
@@
 
-\end{appendices}
-
-%  BIBLIOGRAPHY ============================================
-{\footnotesize
-\bibliographystyle{ieeetr}
-% \bibliography{}
-\bibliography{\template/refs}}
+%% If you have bib database file and want bibtex to generate the
+%% bibitems, please use
+%%
+\bibliographystyle{elsarticle-harv} 
+\bibliography{refs}
+
+%% else use the following coding to input the bibitems directly in the
+%% TeX file.
+
+%% Refer following link for more details about bibliography and citations.
+%% https://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
+
+% \bibliographystyle{elsarticle-harv}
+% % \bibliography{}
+% \bibliography{\template/refs}
 
 \end{document}
+
+\endinput
+%%
+%% End of file `elsarticle-template-harv.tex'.

### 2025-04-05 manuscript_bck.tex
move to Elsevier

--- 2025-04-03 manuscript.tex
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
-    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
-    \label{fig: h func}
-\end{figure}
-
 % SYSTEM FIGURE AND TABLE
@@
     \centering
-    \begin{tabular}{|c||c|c|c|}
-    \hline
-    & \multicolumn{3}{c|}{Handling Capability}\\
-    \hline
-    & System & Weight Norm & Input Norm\\
-    &  Uncertainty & Constraint & Constraint\\
-    \hline 
-    BSC     & X & X & X\\
-    \hline
-    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
-         &  & (by projection) & \\
-    \hline
-    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
-       &  & (by projection) &  (by aux. system)\\
-       % &  & & linearized constraint)\\
-    % \hline
-    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
-    %    &  & (by projection) &  system for \\
-    %    &  & & linearized constraint)\\
-    \hline
-    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
-         &  & (by optimization) & (by optimization)\\
+    \begin{tabular}{c c c}
+    \hline
+    & \multicolumn{2}{c}{\bf{Handling Capability}}\\
+    \hline
+    \hline
+    & Weight Norm Constraint & Input Norm Constraint\\
+    \hline
+    \hline
+    \multirow{2}{*}{\bf{CoNAC}} & O & $\triangle$ \\
+       & (by projection) &  (by aux. system)\\
+    \hline
+    \multirow{2}{*}{\bf{NAC-AUX}} & O & O\\
+       & (by optimization) & (by optimization)\\
     \hline

### 2025-04-05 src/mearsurement/main_plotter.m

@@ -2,69 +2,79 @@ clear
 
 ANITMATE = 0;
 AINMATION_SAVE_FLAG = 0;
+SAVE_FLAG = 1;
+POSITION_FLAG = 1; % it will plot fiugures in the same position
 
 %%
-SAVE_FLAG = 0;
-POSITION_FLAG = 1; % it will plot fiugures in the same position
 gray = "#808080";
 
 more_blue = "#0072BD";
 more_red = "#A2142F";
 
+% font_size = 16;
+% line_width = 2;
+% lgd_size = 12;
+    
+% fig_height = 210 * 1; 
+% fig_width = 450 * 1;
+
+font_size = 20;
+line_width = 2;
+lgd_size = 16;
+    
+fig_height = 230 * 1; 
+fig_width = 800 * 2;
 %% 
-ctrl1_name = "data 1"; % CoNAC
-ctrl2_name = "data 1"; % Aux.
+ctrl1_name = "c1"; % CoNAC
+ctrl2_name = "c2"; % Aux.
 
 %%
-ctrl1_log = readmatrix("sim_result/"+ctrl1_name+".csv");
-ctrl2_log = readmatrix("sim_result/"+ctrl2_name+".csv");
+% ctrl1_log = readmatrix("sim_result/"+ctrl1_name+".csv");
+% ctrl2_log = readmatrix("sim_result/"+ctrl2_name+".csv");
+
+ctrl1_log = post_procc("sim_result/"+ctrl1_name+".csv");
+ctrl2_log = post_procc("sim_result/"+ctrl2_name+".csv");
 
 %% RESULT PLOTTER
 % T = ctrl1_log.T;
-t = ctrl1_log(:,1);
-t = t-t(1);
-T = t(end);
-obs_t = 1:length(t);
+t1 = ctrl1_log(:,1);
+t1 = t1-t1(1);
+t2 = ctrl2_log(:,1);
+t2 = t2-t2(1);
+T = t1(end);
+obs_t1 = 1:length(t1);
+obs_t2 = 1:length(t2);
 % opt1 = ctrl1_log.opt;
 % opt2 = ctrl2_log.opt;
 
-c1_x1 =     transpose(ctrl1_log(:,[3,7]));
-c1_x2 =     transpose(ctrl1_log(:,[4,8]));
-c1_xd1 =    transpose(ctrl1_log(:,[10,12]));
[…]

### 2025-04-05 src/mearsurement/post_procc.m

@@ -1,0 +1,58 @@
+function data = post_procc(path)
+
+    data = readtable(path);
+    data = data{1:end-1, 1:28};
+
+    del_ts = [0.001, 0.004];
+    pt = [];
+
+    for idx = 1:length(del_ts)
+        del_t = del_ts(idx);
+        tmp_pt = find((data(2:end,1) - data(1:end-1,1) - del_t).^2 < 1e-6);
+        
+        pt = union(pt, tmp_pt);
+    end
+
+    tmp_pt = find((data(2:end,7) - data(1:end-1,7)).^2 > 1e-2);
+    pt = setdiff(pt, tmp_pt);
+
+    pt = setdiff(pt, find(data(:,2).^2 < 1e-6));
+
+    data = data(pt, :);
+
+end
+
+
+% elapsedTime,
+% CONTROL_FLAG,
+% q(0),
+% q(1),
+% qdot(0),
+
+% qdot(1),
+% r(0),
+% r(1),
+% rdot(0),
+% rdot(1),
+
+% u(0),
+% u(1),
+% u_sat(0),
+% u_sat(1),
+% lbd(0), // th0 **** NUM LAMBDA: 8
+
+% lbd(1), // th1
+% lbd(2), // th2
+% lbd(3), // u_ball
+% lbd(4), // u_1 M
+% lbd(5), // u_2 M
+
+% lbd(6), // u_1 m
+% lbd(7), // u_2 m
+% Vn(0),
+% Vn(1),
+% Vn(2), // 잊지마잉
+
+% zeta_arr[0],
+% zeta_arr[1],
+% avgCtrlTimeSec // Add average ctrl_wrapper execution time

### 2025-04-06 manuscript.tex
update; figures and notations

@@
 The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
-The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
-\begin{equation}
-    \mysat(\mv\tau)
-    :=
-    \begin{cases}
-        \mv\tau, 
-        & 
-        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
-        \\
-        \bar\tau
-        \cdot
-        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
-        & 
-        \text{otherwise},
-    \end{cases}
-    \label{eq:sat}
-\end{equation}
-where $\bar\tau$ denotes the maximum norm of control input.
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\mv\tau)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
@@
 \end{equation}
-where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
+where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
 Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
@@
 \begin{equation}
-  {q_d}(t) = 
+    \qd(t) = 
     \begin{bmatrix}
@@
     \begin{cases}
-    \mypoly(\q_0,\q_1,t_f,t)
+    \mypoly({\qd}_0,{\qd}_1,t_f,t)
         & \text{if } 0\le t < t_f \\
-    \mypoly(\q_1,\q_2,t_f,t-t_f)
+    \mypoly({\qd}_1,{\qd}_2,t_f,t-t_f)
         & \text{if } t_f\le t < 2t_f \\
-    \mypoly(\q_2,\q_3,t_f,t-2t_f)
+    \mypoly({\qd}_2,{\qd}_1,t_f,t-2t_f)
         & \text{if } 2t_f\le t < 3t_f \\
-    \mypoly(\q_3,\q_0,t_f,t-3t_f)
+    \mypoly({\qd}_1,{\qd}_0,t_f,t-3t_f)
         & \text{if } 3t_f\le t < 4t_f \\
@@
 \end{equation}
-where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, $\q_3=[0,\pi/2]^\top$, and $t_f=5$ s.
+where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, and $t_f=5$ s.
 \MSRY{VIDEO IS PROVIDED; IF WE CAN PROVIDE}
@@
     \mysat(\mv\tau)
-  =
-  ,
-  \label{eq:control input saturation}
+    :=
+    \begin{cases}
+        \mv\tau, 
+        & 
+        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
+        \\
+        \bar\tau
+        \cdot
+        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
+        & 
+        \text{otherwise},
+    \end{cases}
+    \label{eq:sat}
 \end{equation}
@@
         & \multicolumn{2}{c}{\bf{Handling Capability}}\\
-  \hline
-  \hline
         & Weight Norm Constraint & Input Norm Constraint\\
@@
     \hline
-  \multirow{2}{*}{\bf{CoNAC}} & O & $\triangle$ \\
-     & (by projection) &  (by aux. system)\\
-  \hline
-  \multirow{2}{*}{\bf{NAC-AUX}} & O & O\\
+    \multirow{2}{*}{\bf{CoNAC}} & O & O \\
         & (by optimization) &  (by optimization)\\
+    \hline
+    \multirow{2}{*}{\bf{NAC-AUX}} & O & $\triangle$ \\
+        & (by optimization) & (by aux. system)\\
     \hline
@@
   \centering
-    \subfloat[Tracking result of $d$-axis stator current .]{
+    \subfloat[Tracking result of $q_1$.]{
       \includegraphics[width=\figSize\linewidth]
       {
-        src/mearsurement/figures/Fig1.eps
+        src/measurement/figures/Fig1.eps
       }%
@@
     \vspace{2mm}
-    \subfloat[Tracking result of $d$-axis stator current .]{
+    \subfloat[Tracking result of $q_2$.]{
       \includegraphics[width=\figSize\linewidth]
       {
-        src/mearsurement/figures/Fig2.eps
+        src/measurement/figures/Fig2.eps
       }%
@@
     \vspace{2mm}
-      \subfloat[Control input.]{
+      \subfloat[Control input $\tau_1$.]{
         \includegraphics[width=\figSize\linewidth]
         {
-          src/mearsurement/figures/Fig3.eps
+          src/measurement/figures/Fig3.eps
         }%
@@
     \vspace{2mm}
-      \subfloat[Control input.]{
+      \subfloat[Control input $\tau_2$.]{
         \includegraphics[width=\figSize\linewidth]
         {
-          src/mearsurement/figures/Fig4.eps
+          src/measurement/figures/Fig4.eps
         }%
@@
   \caption{
-  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
+  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
   }
@@
   \centering
-    \subfloat[Tracking result of $d$-axis stator current .]{
+    \subfloat[Norm of weights $\hat\theta_i$.]{
       \includegraphics[width=\figSize\linewidth]
       {
-        src/mearsurement/figures/Fig5.eps
+        src/measurement/figures/Fig5.eps
       }%
@@
     \vspace{2mm}
-    \subfloat[Tracking result of $d$-axis stator current .]{
+    \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
       \includegraphics[width=\figSize\linewidth]
       {
-        src/mearsurement/figures/Fig6.eps
+        src/measurement/figures/Fig6.eps
       }%
@@
     \vspace{2mm}
-      \subfloat[Control input.]{
+      \subfloat[Auxiliary states $\mv{\zeta}$ of NAC-AUX.]{
         \includegraphics[width=\figSize\linewidth]
         {
-          src/mearsurement/figures/Fig8.eps
+          src/measurement/figures/Fig8.eps
         }%
@@
   \caption{
-  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
+  ...
   }
@@
   \centering
-      \includegraphics[width=.3\linewidth]
+      \includegraphics[width=\figSize\linewidth]
       {
-        src/mearsurement/figures/Fig9.eps
+        src/measurement/figures/Fig9.eps
       }%
   \caption{
-  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line.
+Control input $\tau$ in time interval $[??, ??]$ s (bird's eye view).
   }
@@
 
-\subsubsection{System Uncertainty Handling}
-
-The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
+% ------------------------------------
+% Tracking Performance
+% ------------------------------------
+\subsubsection{Learning Capability of Neural Network}
+
+The tracking results of CoNAC and NAC-AUX are shown in Fig.~\ref{fig:ctrl:result}.
 To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties.
 As a result,
-%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
-%the parameters of CM1 are poorly tuned, 
 BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.
@@
 
-\subsection{Input Norm Constraint Handling}\label{sec:sim_cnst}
+% ------------------------------------
+% Control Input Saturation
+% ------------------------------------
+\subsubsection{Input Constraint Handling}
 
@@
 
-\subsection{Weight Norm Constraint Handling}
-
+% ------------------------------------
+% Weight Norm Constraint Handling
+% ------------------------------------
 The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}.
@@
 
-\section{Constraint Candidates}\label{sec:appen:cstr}
+\section{Input Constraint Candidates}\label{sec:appen:cstr}
 
@@
         =& 
-        % \begin{bmatrix}
-        %     \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
-        %     \vdots \\
-        %     \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
-        % \end{bmatrix}
-        = 
-            -\pptfrac{\estNN}{\estwth}
+        \begin{bmatrix}
+            \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
+            \vdots \\
+            \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
+        \end{bmatrix}
+        = 
+            +\pptfrac{\estNN}{\estwth}
         %     \\
@@
         =
-        -\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+        +
+        \begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estact_{k}^\top)&
             \!\cdots\! &
@@
         \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
-        :=
-        & 
-        % \begin{bmatrix}
-        %     \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
-        %     \vdots \\
-        %     \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
-        % \end{bmatrix}
-        = 
-        +\pptfrac{\estNN}{\estwth}
+        =
+        & 
+        \begin{bmatrix}
+            \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
+            \vdots \\
+            \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
+        \end{bmatrix}
+        = 
+        -\pptfrac{\estNN}{\estwth}
         % \\
@@
         =
-        +\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
+        -\begin{bmatrix}
+            (I_{l_{k+1}}\otimes \estact_{k}^\top)&
             % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
@@
 This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
-% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
+% The corresponding Lagrangian multiplier is $\lambda_{u_b}$. 
 The gradients of $c_{u}$ with respect to $\estwth$ are given by
@@
     \!=\! 
-    -\textstyle\sum_{i=1}^n 2\tau_{(i)} 
+    \textstyle\sum_{i=1}^n 2\tau_{(i)} 
     \left(
@@
         (
-            -\pptfrac{\estNN}{\estwth}
+            \pptfrac{\estNN}{\estwth}
         )
@@
     \!=\! 
-    \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
+    {\pptfrac{\estNN}{\estwth}}^\top
+    \mv{\tau}
+    % \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
     \in \mathbb R^{\Xi}.
@@
 \end{equation}
-It should be noted that constraints \eqref{eq.
-cstr input saturation} and \eqref{eq.
-cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq.
-nabla input sat} and \eqref{eq.
-nabla input ball} are linearly dependent, violating the LICQ condition.
+It should be noted that constraints \eqref{eq:cstr:input:bound} and \eqref{eq:cstr:input:norm} can be imposed simultaneously, as their gradients \eqref{eq:cstr:input:bound:grad} and \eqref{eq:cstr:input:norm:grad} are linearly independent, satisfying the LICQ condition.
 

### 2025-04-06 manuscript.tex
add more figures and replace with macros

@@
 %% \documentclass[final,1p,times,authoryear]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
-\documentclass[final,3p,times,authoryear]{elsarticle}
+% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
+% \documentclass[final,3p,times,authoryear]{elsarticle}
 % \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
-%% \documentclass[final,5p,times,authoryear]{elsarticle}
-% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
+% \documentclass[final,5p,times,authoryear]{elsarticle}
+\documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
 
@@
 
-\newcommand*{\fe}{\mv{r}}
-\DeclareMathOperator{\mypoly}{Poly} % filtered error
-
-\newcommand*{\figSize}{.99}
+\newcommand*{\figSizeTwoCol}{.49}
+\newcommand*{\figSizeOneCol}{0.98}
 
@@
             postcode={61005}, 
-            state={},
+            % state={},
             country={Korea}}
@@
     \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
-    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
-    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
+    % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
+    % \item $\myvec(A):= [\mycol_1(A)^\top  ,\cdots,\mycol_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
     \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
@@
 \begin{equation}
-    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
-    =
-    \mysat(\mv\tau)
+    \rbM\ddq + \rbVm + \rbF + \rbG + \rbd
+    =
+    \mysat(\rbu)
     \label{eq:sys1}
 \end{equation}
-where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
-The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
-The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\mv\tau)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
+where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the control input. 
+The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
@@
 \begin{prop} 
-    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
+    The inertia matrix $\rbM$ is symmetric, positive definite and bounded.
     \label{prop:M}
@@
 \begin{prop} 
-    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
+    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $(\dot{\rbM}-2\rbVm)$ is skew-symmetric.
     \label{prop:skew}
@@
 \begin{prop}
-    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
+    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \bar\tau_d$.
     \label{prop:dis_bound}
@@
 \begin{equation}
-    \mm M \dot\fe
-    =
-    -\mm V_m \fe
+    \rbM \dot\fe
+    =
+    -\rbVm \fe
     -\mm K \fe
     + \mv f
-    -\mv \tau_d + \mysat(\mv\tau)
+    -\rbd + \mysat(\rbu)
     ,
@@
     \mm K \fe
-    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
-    +
-    \mm V_m(-\dqd+\mm\Lambda\mv e)
+    +\rbM(-\ddqd+\mm\Lambda\dot{\mv e})
+    +
+    \rbVm(-\dqd+\mm\Lambda\mv e)
     -
-    \mm F
+    \rbF
     -
-    \mm G
+    \rbG
     \in\R^n
@@
 
-Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
+Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
 Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
@@
         =&
-        \fe^\top \mm M (
-            -\mm V_m \fe -\mm K \fe + \mv f
-            -\mv \tau_d + \mysat(\mv\tau)
+        \fe^\top \rbM (
+            -\rbVm \fe -\mm K \fe + \mv f
+            -\rbd + \mysat(\rbu)
         )
@@
         \tfrac{1}{2}
-        \fe^\top \dot{\mm M}\fe
+        \fe^\top \dot{\rbM}\fe
         \\
@@
         \fe^\top (
-            \mv f+\mysat(\mv\tau)
-            -\mv \tau_d
+            \mv f+\mysat(\rbu)
+            -\rbd
         )
@@
         \tfrac{1}{2}
-        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
+        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
         \\
@@
         +
-        \fe^\top (\mv f+\mysat(\mv \tau))
+        \fe^\top (\mv f+\mysat(\rbu))
         \\
@@
         +
-        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
+        \fe^\top (\mysat(\rbu)-\rbu^*)
         ,
@@
 \end{equation}
-where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
-Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
-However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.
-
-To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
+where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
+However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
+
+To overcome this issue, a DNN is employed to approximate $\rbu^*$.
 Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
@@
 
-In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
+In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
 \begin{align}
-    \mv\tau^*=& \idealNN+\mv\epsilon,
+    \rbu^*=& \idealNN+\mv\epsilon,
     \label{eq:control:ideal}
@@
 \begin{align}
-    \mv\tau =& \estNN,
+    \rbu =& \estNN,
     \label{eq:control:est}
@@
 
-Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $\mathcal V_1$ can be rewritten as
-\begin{equation}
-    \dot{\mathcal V}_1
+Substituting \eqref{eq:control:ideal} and \eqref{eq:control:est} into \eqref{eq:lya1:dot1}, the time derivative of $V_1$ can be rewritten as
+\begin{equation}
+    \ddtt{V}_1
     \le 
@@
 The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
-Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).
 
@@
         &
-        i=k 
+        i=k,
         \\
@@
         & 
-        i=k-1
+        i=k-1,
         \\
@@
         &
-        i = 0
-    \end{cases},
+        i = 0,
+    \end{cases}
     \label{eq:NN:grad}
@@
         \min_{\estwth} \ J(\fe;\estwth):= 
-        \tfrac{1}{2} \fe^\top  \mm W\fe
+        \tfrac{1}{2} \fe^\top \fe
         \\ \\
@@
 \end{equation}
-where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top  \mm W\fe$ is the objective function, and $\mm W\in\R^{n\times n}$ is a symmetric positive weighting matrix.
+where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
 Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
@@
     c_{j}(\estwth)
+    ,
     \label{eq:lagrangian}
@@
 Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
-Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \text{max}(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
-
-At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\partial L/\partial \estwth=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\pptfrac{L}{\estwth}=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
 In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
@@
 
-The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\mv\tau}$ (\ie 
+The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\rbu}$ (\ie 
 $
-    \pptfrac{J}{\mv \tau}
-    =
-    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\mv \tau}{\estwth}))^\top \fe
-    =
-    ((\pptfrac{\fe}{\mv\tau})(\pptfrac{\estNN}{\estwth}))^\top \fe
+    \pptfrac{J}{\rbu}
+    =
+    ((\pptfrac{\fe}{\rbu})(\pptfrac{\rbu}{\estwth}))^\top \fe
+    =
+    ((\pptfrac{\fe}{\rbu})(\pptfrac{\estNN}{\estwth}))^\top \fe
 $). 
@@
     \ddtt (
-        \pptfrac{\fe}{\mv\tau}
+        \pptfrac{\fe}{\rbu}
     )
@@
     \pptfrac{}{
-        \mv\tau
+        \rbu
     }
     \left[
-        \mm M^{-1}(
-            -\mm V_m \fe
+        \rbM^{-1}(
+            -\rbVm \fe
             -\mm K \fe
             + \mv f
-            -\mv \tau_d + \mysat(\mv\tau)
+            -\rbd + \mysat(\rbu)
         )
@@
 \end{equation}
-However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\mm M,\mm V_m, \mm F$ and $ \mm G$).
+However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\rbM,\rbVm, \rbF$ and $ \rbG$).
 Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
 
-In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\mv\tau}$ as $
-    \pptfrac{\fe}{\mv\tau}
+In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ as $
+    \pptfrac{\fe}{\rbu}
     \approx
     [
-        \mathrm{sign}(\pptfrac{r_i}{\tau_j})
+        \mysign(\pptfrac{r_i}{\tau_j})
     ]_{i,j\in[1,\cdots,m]}
 $ using the sign of each entry (\ie control direction).
-However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\mm M^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
-Therefore, we propose to approximate $\pptfrac{\fe}{\mv\tau}$ as $\pptfrac{\fe}{\mv\tau}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
+However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
+Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
 \begin{equation}
@@
     \left(
-        \pptfrac{\estNN}{\estwth}^\top
+        \pptfrac{\estNN}
+        {\estwth}^\top
         \fe
@@
 
-Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
+Since $\rbu = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\rbu$ can be derived: 
 \begin{equation}\label{eq:linear:map}
     \begin{aligned}
-    \mv\tau 
+    \rbu 
     = 
@@
 \end{equation}
-Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+Therefore, the convexity of the input constraints in $\rbu$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
 that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
@@
         &
-        \text{if } i=j
+        \text{if } i=j,
         \\
@@
     = 
-    \pptfrac{c_j}{\mv\tau} 
-    \pptfrac{\mv\tau}{\estNN} 
+    \pptfrac{c_j}{\rbu} 
+    \pptfrac{\rbu}{\estNN} 
     \pptfrac{\estNN}{\estwth_i}
@@
 where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
-From the linear mapping in \eqref{eq:linear:map}, $\mv\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
+From the linear mapping in \eqref{eq:linear:map}, $\rbu$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
 By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
-The convex function has a bounded derivative with respect to $\mv\tau$, since $\mv\tau$ is a bounded variable (\ie $\pptfrac{c_j}{\mv\tau}$ is bounded). 
+The convex function has a bounded derivative with respect to $\rbu$, since $\rbu$ is a bounded variable (\ie $\pptfrac{c_j}{\rbu}$ is bounded). 
 Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
@@
         \le 
-        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\text{min}}(\mm K)}
+        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\min}(\mm K)}
     \right\}
@@
             \textstyle\sum_{
-                j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
             }
@@
         \textstyle\sum_{
-            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
         }
@@
 The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
-Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
 It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
@@
         =&
-        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        -\lambda_{\min}(\mm K)\norm{\fe}^2
         +\bar\tau_d\norm{\fe}
@@
         \le&
-        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        -\lambda_{\min}(\mm K)\norm{\fe}^2
         +\fe^\top \estNN
@@
                     \idealNN+\mv\epsilon
-                }_{=\mv\tau^*}
+                }_{=\rbu^*}
             }
@@
         \le&
-        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
+        -\lambda_{\min}(\mm K)\norm{\fe}^2
         +(\bar\tau_d+\bar\tau)
@@
         }{
-            \lambda_{\text{min}}(\mm K)
+            \lambda_{\min}(\mm K)
         }
@@
     -\alpha
-    (
+    \left(
         \pptfrac{\estNN}{\estwth_i}^\top
@@
         \pptfrac{c_j}{\estwth_i}
-    )
+    \right)
     .
@@
     \begin{aligned}
-        \mm M(\q) \ddtt{\q} + \mm V_m(\q,\dot\q) + \mm F(\q,\dot\q) + \mm G(\q) = \mv\tau,
-        \\
-        \mv\tau = \estNN(\q,\dot\q),
+        \rbM(\q) \ddtt{\q} + \rbVm(\q,\dot\q) + \rbF(\q,\dot\q) + \rbG(\q) = \rbu,
+        \\
+        \rbu = \estNN(\q,\dot\q),
     \end{aligned}
@@
 \begin{equation}
-    \qd(t) = 
+    \qd(t) 
+    \!=\! 
     \begin{bmatrix}
@@
     \end{bmatrix}
-    =
+    \!=\!
     \begin{cases}
-    \mypoly({\qd}_0,{\qd}_1,t_f,t)
-        & \text{if } 0\le t < t_f \\
-    \mypoly({\qd}_1,{\qd}_2,t_f,t-t_f)
-        & \text{if } t_f\le t < 2t_f \\
-    \mypoly({\qd}_2,{\qd}_1,t_f,t-2t_f)
-        & \text{if } 2t_f\le t < 3t_f \\
-    \mypoly({\qd}_1,{\qd}_0,t_f,t-3t_f)
-        & \text{if } 3t_f\le t < 4t_f \\
+    \mypoly({\qd}_0,{\qd}_1,t_f,t),
+        & \text{if } 0\le t < t_f 
+        ,
+        \\
+    \mypoly({\qd}_1,{\qd}_2,t_f,t-t_f),
+        & \text{if } t_f\le t < 2t_f 
+        ,
+        \\
+    \mypoly({\qd}_2,{\qd}_1,t_f,t-2t_f),
+        & \text{if } 2t_f\le t < 3t_f 
+        .
+        \\
+    \mypoly({\qd}_1,{\qd}_0,t_f,t-3t_f),
+        & \text{if } 3t_f\le t < 4t_f 
+        ,
+        \\
     \end{cases}
-    ,
     \label{eq:desired trajectory}
@@
 \begin{equation}
-    \mysat(\mv\tau)
+    \mysat(\rbu)
     :=
     \begin{cases}
-        \mv\tau, 
-        & 
-        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
-        \\
-        \bar\tau
+        \rbu, 
+        & 
+        \text{if } \norm{\rbu}\le \bar\tau,
+        \\
+        \rbu
         \cdot
-        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
+        \tfrac{\bar\tau}{\norm{\rbu}}, 
         & 
@@
     \centering
-    \includegraphics[width=0.5\linewidth]{fig/RobotModel.drawio.png}
+    \includegraphics[width=0.75\linewidth]{fig/RobotModel.drawio.png}
     \caption{Two-link manipulator model.}
@@
     \centering
-    \begin{tabular}{c m{11em} c c c }
+    \begin{tabular}{c m{7em} c c c }
+        % \begin{tabular}{c c c c c}
     \hline
@@
 The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq:control:est}. 
-The update rates for the multipliers were set as \MSRY{SEE HERE}$\beta_{j}=0.1$. The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.
+The update rates for the multipliers were set as \MSRY{SEE HERE}$\beta_{j}=0.1$. The weight matrix $W$ was selected as $W=\mydiag([5,1,15,15])]$.
 
@@
 The sampling time of the simulations was selected as $T_s=10^{-4}$.
-% The same values were assigned across all the controllers for the common parameters for a fair comparison.
-The parameters for CoNAC to NAC-AUX were listed in Table.~\ref{table:controller:params}. 
+% The parameters for CoNAC to NAC-AUX were listed in Table.~\ref{table:controller:params}. 
 % The same values were assigned across all the controllers for the common parameters for a fair comparison.
@@
     \centering
-    \begin{tabular}{c c c}
+    \begin{tabular}{l c c}
     \hline
         & \multicolumn{2}{c}{\bf{Handling Capability}}\\
-        & Weight Norm Constraint & Input Norm Constraint\\
+        & Weight Constraint & Input Constraint\\
     \hline
@@
 % ------------------------------------
-\begin{table}[t]
-    \renewcommand{\arraystretch}{1.3}
-    \caption{Parameters of the controllers used in simulation}
-    \label{table:controller:params}
-    \centering
-    \begin{tabular}{c | c c c c c c c c c c c c c c}
-    \hline
-        & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\bar\theta_0$ & $\bar\theta_1$ & $\bar\theta_2$ & $\bar\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
-    \hline
-    \hline
-        \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
+% \begin{table}[t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Parameters of the controllers used in simulation}
+%     \label{table:controller:params}
+%     \centering
+%     \begin{tabular}{c | c c c c c c c c c c c c c c}
 %     \hline
-        \bf{NAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
-    \hline
-    \end{tabular}
-\end{table}
-
-\begin{figure}[t]
+%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\bar\theta_0$ & $\bar\theta_1$ & $\bar\theta_2$ & $\bar\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
+%     \hline
+%     \hline
+%         \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
+%     % \hline
+%         \bf{NAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
+%     \hline
+%     \end{tabular}
+% \end{table}
+
+\begin{figure*}[t]
   \centering
     \subfloat[Tracking result of $q_1$.]{
-      \includegraphics[width=\figSize\linewidth]
+      \includegraphics[width=\figSizeTwoCol\linewidth]
       {
@@
       \label{fig:ctrl:result:q1}}
-    \vspace{2mm}
+    % \vfill
     \subfloat[Tracking result of $q_2$.]{
-      \includegraphics[width=\figSize\linewidth]
+      \includegraphics[width=\figSizeTwoCol\linewidth]
       {
@@
       \label{fig:ctrl:result:q2}}
-    \vspace{2mm}
+    \vfill
       \subfloat[Control input $\tau_1$.]{
-        \includegraphics[width=\figSize\linewidth]
+        \includegraphics[width=\figSizeTwoCol\linewidth]
         {
@@
         \label{fig:ctrl:result:tau:1}}
-    \vspace{2mm}
+    % \vfill
       \subfloat[Control input $\tau_2$.]{
-        \includegraphics[width=\figSize\linewidth]
+        \includegraphics[width=\figSizeTwoCol\linewidth]
         {
@@
 \label{fig:ctrl:result}
-\end{figure}
+\end{figure*}
 
@@
     \subfloat[Norm of weights $\hat\theta_i$.]{
-      \includegraphics[width=\figSize\linewidth]
+      \includegraphics[width=\figSizeOneCol\linewidth]
       {
@@
     \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
-      \includegraphics[width=\figSize\linewidth]
+      \includegraphics[width=\figSizeOneCol\linewidth]
       {
@@
       \subfloat[Auxiliary states $\mv{\zeta}$ of NAC-AUX.]{
-        \includegraphics[width=\figSize\linewidth]
+        \includegraphics[width=\figSizeOneCol\linewidth]
         {
@@
   \centering
-      \includegraphics[width=\figSize\linewidth]
+      \includegraphics[width=\figSizeOneCol\linewidth]
       {
@@
   \label{fig:ctrl:result:conrol}
+\end{figure}
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.6\linewidth]{
+		src/figures/lambda_effect.drawio.pdf
+		}
+	\caption{
+		The effect of Lagrange multiplier $\lambda_{\theta_i}$ on the adaptation direction of $\widehat{ \mv{\theta}}_i$.
+		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively (i.e., $\lambda_{\theta_1}' > \lambda_{\theta_1}''$).
+	}
+	% \vspace{1mm}
+	\label{fig:lambda_effect}
 \end{figure}
@@
         c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
-        \\
+        ,
+        \quad
         c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+        ,
     \end{aligned}
@@
     c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
+    ,
     \label{eq:cstr:input:norm}

### 2025-04-06 src/measurement/main_plotter.m

@@ -23,7 +23,7 @@ line_width = 2;
 lgd_size = 16;
     
 fig_height = 230 * 1; 
-fig_width = 800 * 2;
+fig_width = 800 * 1;
 %% 
 ctrl1_name = "c1"; % CoNAC
 ctrl2_name = "c2"; % Aux.

### 2025-04-06 src/measurement/main_plotter.m
new figures

@@ -2,7 +2,7 @@ clear
 
 ANITMATE = 0;
 AINMATION_SAVE_FLAG = 0;
-SAVE_FLAG = 1;
+SAVE_FLAG = 0;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
 
 %%
@@ -29,11 +29,8 @@ ctrl1_name = "c1"; % CoNAC
 ctrl2_name = "c2"; % Aux.
 
 %%
-% ctrl1_log = readmatrix("sim_result/"+ctrl1_name+".csv");
-% ctrl2_log = readmatrix("sim_result/"+ctrl2_name+".csv");
-
-ctrl1_log = post_procc("sim_result/"+ctrl1_name+".csv");
-ctrl2_log = post_procc("sim_result/"+ctrl2_name+".csv");
+ctrl1_log = post_procc(ctrl1_name);
+ctrl2_log = post_procc(ctrl2_name);
 
 %% RESULT PLOTTER
 % T = ctrl1_log.T;
@@ -339,13 +336,30 @@ ylim([-u_max2*1.25, u_max2*1.25])
 % pbaspect([1 1 1])
 % legend([p1, p2], ["$\tau$", "Saturated $\tau$"], "Interpreter","latex", "FontSize", lgd_size, "FontWeight", "bold", "Location", "northwest")
 
+% =============================================
+%    Fig. 10: Computational Time
+% =============================================
+figure(10); clf;
+hF = gcf; 
+hF.Position(3:4) = [fig_width, fig_height];
+
+plot(t2(obs_t2), c2_cmp(1,obs_t2)*1e3, "color", 'cyan', "LineWidth", 2, "LineStyle", "-"); hold on
+plot(t1(obs_t1), c1_cmp(1,obs_t1)*1e3, "color", 'blue', "LineWidth", 2, "LineStyle", "-"); hold on
+xlabel("Time / s", "Interpreter", "latex")
+ylabel("Cmp. Time / ms", "Interpreter", "latex")
+set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+grid on 
+xlim([0 T])
+% ylim([-u_max2*1.25, u_max2*1.25])
+% legend([p1, p2], ["$\tau$", "Saturated $\tau$"], "Interpreter","latex", "FontSize", lgd_size, "FontWeight", "bold", "Location", "northwest")
+
 
 %% ============================================
 %% SAVE FIGURES
[…]

### 2025-04-06 src/measurement/post_procc.m

@@ -1,11 +1,16 @@
-function data = post_procc(path)
+function [data, loss_ratio] = post_procc(ctrl_name)
 
-    data = readtable(path);
+    data = readtable("sim_result/"+ctrl_name+".csv");
     data = data{1:end-1, 1:28};
 
     del_ts = [0.001, 0.004];
-    pt = [];
 
+    pt = find(data(:,2).^2 > 1e-6);
+    data = data(pt, :);
+    ori_num = length(data);
+
+    pt = [];
+    % sampling time check
     for idx = 1:length(del_ts)
         del_t = del_ts(idx);
         tmp_pt = find((data(2:end,1) - data(1:end-1,1) - del_t).^2 < 1e-6);
@@ -13,13 +18,18 @@ function data = post_procc(path)
         pt = union(pt, tmp_pt);
     end
 
-    tmp_pt = find((data(2:end,7) - data(1:end-1,7)).^2 > 1e-2);
-    pt = setdiff(pt, tmp_pt);
-
-    pt = setdiff(pt, find(data(:,2).^2 < 1e-6));
+    % remove the data with large change
+    thr = 1e0;
+    for idx = 3:28
+        tmp_pt = find((data(2:end,idx) - data(1:end-1,idx)).^2 > thr);
+        pt = setdiff(pt, tmp_pt);
+    end
 
     data = data(pt, :);
+    mod_num = length(data);
 
+    loss_ratio = (ori_num - mod_num) / ori_num;
+    fprintf('loss ratio: %.3f%%\n', loss_ratio*1e2);
 end
 
 

### 2025-04-08 manuscript.tex
new figures
add simulation plotter for variations

@@
 The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
-The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \bar\tau$, where $\bar\tau$ denotes the maximum norm of control input.
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
@@
 \begin{prop}
-    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \bar\tau_d$.
+    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \overline\tau_d$.
     \label{prop:dis_bound}
@@
 \begin{assum}
-    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
+    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \overline{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
     \label{assum:feasible}
@@
     \centering
-    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
+    \includegraphics[width=0.9\linewidth]{src/figures/Controller.drawio.png}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
         +
-        \bar\tau_d\norm{\fe}
+        \overline\tau_d\norm{\fe}
         +
@@
 \end{equation}
-where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
-Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
+where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
 However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
@@
 To overcome this issue, a DNN is employed to approximate $\rbu^*$.
-Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
-The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
-According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
-Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
+Let $\NN:=\NN({\q}_n;\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+The architecture of $\NN({\q}_n;\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
+Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
 In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
 
-In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
+In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN({\q}_n;\idealwth)$ as follows:
 \begin{align}
@@
 \end{align}
-where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
+where $\hat\NN:=\NN({\q}_n;\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
 
@@
     +
-    \bar\tau_d\norm{\fe}
+    \overline\tau_d\norm{\fe}
     +
@@
 
-The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
+The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
 \begin{equation}
@@
         \\
-        \wV_0^\top \q_{NN},
+        \wV_0^\top {\q}_n,
         &
@@
 \end{equation}
-where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
 \begin{equation}
@@
         \\
-        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
+        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes {\q}_n^\top  ), 
         &
@@
             =
-            -\alpha \pptfrac{L}{\estwth}
-            =
-            -\alpha 
+            -\Gamma \pptfrac{L}{\estwth}
+            =
+            -\Gamma 
             \left(
@@
 \end{subequations}
-where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+where $\Gamma=\Gamma^\top:=\mydiag([\gamma_1,\cdots,\gamma_n])\in\R^{n\times n}_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+By selecting $\gamma_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
 The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
@@
     \approx
-    -\alpha 
+    -\Gamma 
     \left(
@@
 For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
-If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
+If a large $T_s$ is used, $\Gamma$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
 
@@
         -
-        \bar\theta_i^2 
+        \overline\theta_i^2 
     )    
@@
 \end{equation}
-with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
+with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
 The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
@@
 
-As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
+As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as w
 \begin{equation}
@@
         \le 
-        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\min}(\mm K)}
+        \tfrac{2\overline\tau+\overline\tau_d}{\lambda_{\min}(\mm K)}
     \right\}
@@
 
-To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
+To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2}\estwth_k^\top\Gamma^{-1} \estwth_k$.
 Taking the time derivative of $V_2$ yields:
@@
         -\estwth_k^\top 
+        \Gamma^{-1}\Gamma
         (
@@
         \tfrac{
-            c_1(2\bar\tau+\bar\tau_d)
+            c_1(2\overline\tau+\overline\tau_d)
         }{
@@
         -\lambda_{\min}(\mm K)\norm{\fe}^2
-        +\bar\tau_d\norm{\fe}
+        +\overline\tau_d\norm{\fe}
         +\fe^\top (\estNN - \idealNN - \mv\epsilon)
@@
         +(
-            \bar\tau_d+\norm{
+            \overline\tau_d+\norm{
                 \underbrace{
@@
         -\lambda_{\min}(\mm K)\norm{\fe}^2
-        +(\bar\tau_d+\bar\tau)
+        +(\overline\tau_d+\overline\tau)
         \norm{\fe}
@@
         \tfrac{
-            \bar\tau_d+\bar\tau
+            \overline\tau_d+\overline\tau
         }{
@@
 \end{equation}
-The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
 
@@
     =
-    -\alpha
+    -\Gamma
     \left(
@@
 % ------------------------------------
-% Robot Model and Reference Trajectory
-% ------------------------------------
-The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
-The system dynamics of the two-link manipulator is described by the following equations:
-\MSRY{ADD MORE DETAIL; Following Eqn is just example}
-\begin{equation}
-    \begin{aligned}
-        \rbM(\q) \ddtt{\q} + \rbVm(\q,\dot\q) + \rbF(\q,\dot\q) + \rbG(\q) = \rbu,
-        \\
-        \rbu = \estNN(\q,\dot\q),
-    \end{aligned}
-    \label{eq:robot_dynamics}
-\end{equation}
-The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ \MSRY{more parameters} denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
+% MCU & Robot Model and Ref. Trajectory
+% ------------------------------------
+The proposed CoNAC was implemented using the OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency.
+The two-link manipulator model is depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
+\MSRY{CORRECT HERE}
+The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
+where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
 The values of the system model parameters are provided in Table~\ref{table:system:params}.
-The desired trajectory for $\q=[q_1,q_2]^\top $ was defined with \MSRY{5th Poly functions} as
+
+% ------------------------------------
+% Reference Trajectory
+% ------------------------------------
+The desired trajectory for $\q=[q_1,q_2]^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
+The desired trajectory is defined as follows:
 \begin{equation}
@@
     \begin{cases}
-    \mypoly({\qd}_0,{\qd}_1,t_f,t),
-        & \text{if } 0\le t < t_f 
+    \mypoly^5({\qd}_0,{\qd}_1,t_f,t),
+        \!&\!
+        \text{if } 0\le t < t_f 
         ,
         \\
-    \mypoly({\qd}_1,{\qd}_2,t_f,t-t_f),
-        & \text{if } t_f\le t < 2t_f 
+    \mypoly^5({\qd}_1,{\qd}_2,t_f,t-t_f),
+        \!&\!
+        \text{if } t_f\le t < 2t_f 
         ,
         \\
-    \mypoly({\qd}_2,{\qd}_1,t_f,t-2t_f),
-        & \text{if } 2t_f\le t < 3t_f 
+    \mypoly^5({\qd}_2,{\qd}_1,t_f,t-2t_f),
+        \!&\! 
+        \text{if } 2t_f\le t < 3t_f 
         .
         \\
-    \mypoly({\qd}_1,{\qd}_0,t_f,t-3t_f),
-        & \text{if } 3t_f\le t < 4t_f 
+    \mypoly^5({\qd}_1,{\qd}_0,t_f,t-3t_f),
+        \!&\!    
+        \text{if } 3t_f\le t < 4t_f 
         ,
@@
 \end{equation}
-where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, and $t_f=5$ s.
-\MSRY{VIDEO IS PROVIDED; IF WE CAN PROVIDE}
+where ${\qd}_0=[0,0]^\top$, ${\qd}_1=[\tfrac{5}{8}\pi,-\tfrac{3}{8}\pi]^\top$, ${\qd}_2=[\tfrac{5}{4}\pi/2,-\tfrac{3}{4}\pi]^\top$, and $t_f=4$ s.
+
+However, since the NN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
+Hence, the reference trajectory was applied 3 times by proportionally increasing the amplitude of the desired trajectory to the original ${\qd}_i,\ \forall i\in\{1,2\}$.
+Let us call the $i\textsuperscript{th}$ iteration of the reference trajectory as Episode $i,\ \forall i\in[1,2,3]$.
 
@@
 % ------------------------------------
-To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the following control input saturations were imposed:
-\begin{equation}
-    \mysat(\rbu)
-    :=
-    \begin{cases}
-        \rbu, 
-        & 
-        \text{if } \norm{\rbu}\le \bar\tau,
-        \\
+To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_1}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
+%
+\begin{subequations}
+    \begin{align}
+        \Theta_{\mysat, {\rbu}}
+        :=&
+        \left\{
             \rbu
-        \cdot
-        \tfrac{\bar\tau}{\norm{\rbu}}, 
-        & 
-        \text{otherwise},
-    \end{cases}
+            \mid
+            \norm{\rbu} \le \overline\tau
+        \right\}
+        \label{eq:sat:norm}
+        ,
+        \\
+        \Theta_{\mysat, {\tau_1}}
+        :=&
+        \left\{
+            \tau_1
+            \mid
+            \vert{\tau_1}\vert \le \overline\tau_1
+        \right\}
+        ,
+        \label{eq:sat:tau1}
+    \end{align}
     \label{eq:sat}
-\end{equation}
-where $\bar\tau=50, \bar\tau_1$ and $\bar\tau_2$ are the saturation limit values for the norm of the control input and the first and second links, respectively.
+\end{subequations}
+%
+\MSRY{CORRECT HERE}
+with $\overline\tau=10$ and $\overline\tau_1=9$ are the saturation limit values for the norm of the control input norm and the first links, respectively. 
+These domains \ref{eq:sat:norm} and \ref{eq:sat:tau1} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the first link actuator.
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.45\linewidth]{
+        src/figures/saturation.drawio.pdf
+    }
+    \caption{Saturation function.}
+    \label{fig:sat}
+\end{figure}
 
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{System model parameters.}
+    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
     \centering
-    \begin{tabular}{c m{7em} c c c }
+    \begin{tabular}{c m{6.5em} c c c }
     % \begin{tabular}{c c c c c}
@@
     \hline 
-    $m_p$ & Mass of $p\textsuperscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
-    \hline
-    $l_p$  & Length of $p\textsuperscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
-    \hline
-    ${l_c}_p$ & COM of $p\textsuperscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
-    \hline
-    $b_p$   & Viscous coef. of $p\textsuperscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
-    \hline
-    ${f_c}_p$  & Friction coef. of $p\textsuperscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
-    \hline
-    ${f_s}_p$  & ?? $p\textsuperscript{th}$ link &   (Nm) &  (Nm) \\
+    $m_p$ & Mass & 2.465 (kg) & 1.093 (kg) \\
+    \hline
+    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
+    \hline
+    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
+    \hline
+    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
+    \hline
+    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.16 (Nm) \\
+    \hline
+    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
+    \hline
+    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
     \hline
@@
 % ------------------------------------
-For a comparative study, NAC with the auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (NAC-AUX) was implemented, which only considered the input bound constraint introcuded in \ref{sec:appen:cstr:input:norm} and not the nonlinear input norm constraint \eqref{eq:cstr:input:norm}.
-As a result, an approximation of the input norm constraint was used as an input bound constraint. 
-Besides, the proposed controller, CoNAC, rigorously considered the weight norm constraint, and input bound and norm constraints within a constrained optimization framework. 
-The properties of these four controllers are summarized in Table \ref{table:controller}.
-
-% ------------------------------------
-% NAC-AUX
-% ------------------------------------
-The control law for NAC-AUX was the same CoNAC, but with an auxiliary system to compensate for control input violations. 
-Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq:cstr:input:norm}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq:cstr:input:bound} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$.
-The comparison between the original input norm constraint and its approximation is shown in Fig.~\MSRY{ADD FIGURE}.
-The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\mv{\tau},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta=-[20,0;0;20],\mm{B}_\zeta=[10,0;0,10]$\MSRY{SEE HERE}, and $\Delta\tau_{(i)} =
-\tau_{(i)}-\mysat(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
+For a comparative study, CoNAC with the auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (CoNAC-AUX) was implemented, which only considered the weight norm constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ and input bound constraint $c_{\overline\tau_1}$ and $c_{\underline\tau_1}$ introduced in \eqref{eq:cstr:input:bound} and not the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}.
+Besides, the proposed controller, CoNAC, rigorously considered the weight norm constraint, and input bound and norm constraints simultaneously within a constrained optimization framework. 
+The properties of the controllers are summarized in Table \ref{table:controller}.
+
+% ------------------------------------
+% Aux. system in CoNAC-AUX
+% ------------------------------------
+The auxiliary system in CoNAC-AUX is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} =
+\tau_{1}-\max(\underline\tau_1,\min(\overline\tau_1,\tau_1))$.
 The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
-
-% ------------------------------------
-% CoNAC
-% ------------------------------------
-The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq:control:est}. 
-The update rates for the multipliers were set as \MSRY{SEE HERE}$\beta_{j}=0.1$. The weight matrix $W$ was selected as $W=\mydiag([5,1,15,15])]$.
+Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.
 
@@
 % ------------------------------------
-For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix.
-Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$.
-The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ \MSRY{SEE HERE}.
-The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
-The sampling time of the simulations was selected as $T_s=10^{-4}$.
-% The parameters for CoNAC to NAC-AUX were listed in Table.~\ref{table:controller:params}. 
-% The same values were assigned across all the controllers for the common parameters for a fair comparison.
+For all controllers (CoNAC, and CoNAC-AUX), the NN input vector ${\q}_n$ was set as ${\q}_n=[\q^\top,\dq^\top,\fe^\top,1]^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
+Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\Gamma=\mydiag([1.5,1.0])$. 
+The constraint parameters were $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$. 
+The sampling rate of the controller was set to $250$ Hz, and $1000$ Hz for the simulation.
+
+The quantitative comparison of the tracking performance and the control input constraint violations were evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h},\der t}$, where $h\in\{r_1,r_2,\max(0,c_{\rbu}),\max(0,c_{\overline\tau_1}+c_{\underline\tau_1})$ and $T\in\R_{>0}$ denotes the episode duration time.
+Note that $c_{\overline\tau_1}$ and $c_{\underline\tau_1}$ can not be active at the same time, so $\max(0,c_{\overline\tau_1}+c_{\underline\tau_1})$ is used to evaluate the control bound constraint violation.
+To investigate the parameter dependencies, the parameters of the controllers $\beta_u,\beta_{\overline\tau},\beta_{\underline\tau}$ \MSRY{CORRECT} were varied within the range of \MSRY{SEE HERE} $[0.5,1.5]$ across 100000 samples.
 
@@
     \centering
-    \begin{tabular}{l c c}
+    \begin{tabular}{c c c}
     \hline
@@
     \hline
-    \multirow{2}{*}{\bf{NAC-AUX}} & O & $\triangle$ \\
+    \multirow{2}{*}{\bf{CoNAC-AUX}} & O & $\triangle$ \\
         & (by optimization) & (by aux. system)\\
@@
     \end{tabular}
+\end{table}
+
+% ------------------------------------
+% Parameter Variation 
+% ------------------------------------
+\begin{figure}[!t]      
+    \centering
+    {\includegraphics[width=\figSizeOneCol\linewidth]{
+        src/measurement/figures/Fig11.eps
+    }}
+\caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX across various parameter values.}
+    \label{fig:ctrl:result:var}
+\end{figure}
+
+\begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    \caption{Quantitative comparison of $L_2$-norms of the tracking performances and control input constraint violations.}
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+        \!&\!Maximum\!&\!Median\!&\!Minimum\!\\
+    \hline
+    \hline
+    \textbf{CoNAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
+    \hline
+    \textbf{CoNAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
+    \hline
+    \end{tabular}
+    \label{table:ctrl:result:var}
 \end{table}
@@
 %     \hline
-%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\bar\theta_0$ & $\bar\theta_1$ & $\bar\theta_2$ & $\bar\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
+%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\Gamma$ & $\beta$ & $\overline\theta_0$ & $\overline\theta_1$ & $\overline\theta_2$ & $\overline\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
 %     \hline
@@
 %     % \hline
-%         \bf{NAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
+%         \bf{CoNAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
 %     \hline
@@
         \label{fig:ctrl:result:tau:2}}
+        \vfill
+    \subfloat[Norm of weights $\hat\theta_i$.]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+        src/measurement/figures/Fig5.eps
+        }%
+        \label{fig:ctrl:result:opt:norm}}
+        % \vfill
+    \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+        src/measurement/figures/Fig6.eps
+        }%
+        \label{fig:ctrl:result:opt:multiplier}}
+        \vfill
+    \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+            src/measurement/figures/Fig8.eps
+        }%
+        \label{fig:ctrl:result:opt:zeta}}
+        % \vfill
+    \subfloat[Control input $\tau$ in time interval from $1$ s to $3$ s (bird's eye view).]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+            src/measurement/figures/Fig9.eps
+        }%
+        \label{fig:ctrl:result:control}}
   \caption{
-  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
+  Simulation results of the CoNAC (blue) and CoNAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
   }
@@
 \end{figure*}
-
-\begin{figure}[t]
-  \centering
-    \subfloat[Norm of weights $\hat\theta_i$.]{
-      \includegraphics[width=\figSizeOneCol\linewidth]
-      {
-        src/measurement/figures/Fig5.eps
-      }%
-      \label{fig:ctrl:result:opt:norm}}
-    \vspace{2mm}
-    \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
-      \includegraphics[width=\figSizeOneCol\linewidth]
-      {
-        src/measurement/figures/Fig6.eps
-      }%
-      \label{fig:ctrl:result:opt:multiplier}}
-    \vspace{2mm}
-      \subfloat[Auxiliary states $\mv{\zeta}$ of NAC-AUX.]{
-        \includegraphics[width=\figSizeOneCol\linewidth]
-        {
-          src/measurement/figures/Fig8.eps
-        }%
-        \label{fig:ctrl:result:opt:zeta}}
-  \caption{
-  ...
-  }
-  \label{fig:ctrl:result:opt}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-      \includegraphics[width=\figSizeOneCol\linewidth]
-      {
-        src/measurement/figures/Fig9.eps
-      }%
-  \caption{
-Control input $\tau$ in time interval $[??, ??]$ s (bird's eye view).
-  }
-  \label{fig:ctrl:result:conrol}
-\end{figure}
 
@@
 % ------------------------------------
-\subsubsection{Learning Capability of Neural Network}
-
-The tracking results of CoNAC and NAC-AUX are shown in Fig.~\ref{fig:ctrl:result}.
-To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties.
-As a result,
-BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.
-
-By leveraging the DNN to compensate for the lumped system uncertainty within the BSC, DNN-BSC achieved improved tracking performance compared to BSC, as seen in Fig.~\ref{fig: tracking_CM2}.
-Fig.~\ref{fig: tracking_CM3} shows that DNN-BSC-A enhanced tracking performance for $q_2$, but tracking for $q_1$ remained unsatisfactory due to incomplete constraint handling, which will be discussed in detail in Section \ref{sec:sim_cnst}.
-%By compensating the uncertain terms the control input of CM2 in Fig.~\ref{fig: control_CM2} is saturated.
-
-Finally, CoNAC, which directly approximates the stabilizing control law along with the compensation term, demonstrated satisfactory tracking performance across both states, as illustrated in Fig.~\ref{fig: tracking_CoNAC}.
+\subsubsection{Parameter Dependency and Tracking Performance}
+
+The quantitative study of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX are shown in Fig.~\ref{fig:ctrl:result} and Table.~\ref{table:ctrl:result:var}.
 
@@
 
-The resulting control input $\tau$ and physically saturation control input $h(\tau)$ for the selected controllers are shown in Fig.~\ref{fig: control}.
-As illustrated in Fig.~\ref{fig: control_CM1}, BSC did not violate the input norm constraint (\ie $\tau = h(\tau)$).
-However, in DNN-BSC, the added compensation term from the DNN caused violations of the input norm constraint (\ie $\tau > h(\tau)$) at several points; see Fig.~\ref{fig: control_CM2}.
-This failure to account for the input norm constraint led to oscillations in the control input $\tau$.
-The DNN adaptation process attempted to increase the weights to reduce the residual errors that were not constrained by saturation, but after saturation ceased, the control input had to rapidly adjust back to realistic levels, leading to oscillatory behavior.
-Such high-frequency oscillations may induce instability in the control system or cause fatigue in the actuators.
-
-On the other hand, both DNN-BSC-A and CoNAC successfully handled their imposed input constraints, as shown in Fig.~\ref{fig: control_CM3} and Fig.~\ref{fig: control_CoNAC}, respectively, without causing notable oscillations in the control input $\tau$ even after the input constraint was activated.
-However, the tracking performance of DNN-BSC-A was lower than that of DNN-BSC and CoNAC, as the auxiliary system used in DNN-BSC-A approximated the input norm constraint with an input bound constraint, creating a rectangular constraint in the $\tau$-space (see Fig.~\ref{fig: ball control}).
-In contrast, CoNAC satisfied the nonlinear input norm constraint and produced the physically maximum control input, resulting in improved tracking performance.
-
-It is also important to note that the control input trajectory in DNN-BSC-A depends on the dynamics of the auxiliary system.
-The auxiliary system regulates the violated control input after sufficient auxiliary state $\zeta$ is generated to compensate for the violation.
-This can be observed in Fig.~\ref{fig: ball control}, where DNN-BSC-A exhibited minor violations of the input bound constraint.
-In contrast, CoNAC satisfied the constraint without being affected by such dynamics, as its Lagrange multiplier adjusted as soon as the constraint was violated.
-
-%Meanwhile, CM2 and CM3 is based on BSC, and the desired controller $\tau^*$ of CoNAC is based on the BSC which may produce larger control input by canceling the stabilizing system dynamics.
-%Therefore, CM2, CM3, and CoNAC produced the saturated control input.
-%These control results show why the control saturation should be handled.
-
-% ------------------------------------
-% Weight Norm Constraint Handling
-% ------------------------------------
-The resulting weight norms of DNN-BSC, DNN-BSC-A, and CoNAC, along with the Lagrange multipliers of CoNAC, are shown in Fig.~\ref{fig: weight and multiplier}.
-All three controllers—DNN-BSC, DNN-BSC-A, and CoNAC—maintained weight norms within the imposed weight norm constraints.
-
-IN DNN-BSC, as shown in Fig.~\ref{fig: weight_CM2}, the weight norm of the last layer (\ie $\Vert {{{\hat \wth }_2}} \Vert$) fluctuated significantly over time, proportional to the control input norm.
-This is because the last layer’s weights directly determine the control input.
-When the control input violated the input norm constraint, the last layer’s weight norm hit the boundary and stayed there due to the projection operator.
-However, the projection operator only responded to violations without considering optimality or behavior.
-%In the case of CM2 which does not consider the control input constraint, the weight norm of the last layer reaches the maximum weight norm value, when the control is saturated.
-%It is because the weights get increased to produce larger control input to reduce the tracking error of $q_2$.
-(\ie the maximum magnitude of the control input depends on the weight norm of the last layer, since the activation function is bounded.)
-
-In DNN-BSC-A, none of the weight norms reached their boundaries, as shown in Fig.~\ref{fig: weight_CM3}.
-This was due to the auxiliary system, where the auxiliary state $\zeta$ reduced the control input, ensuring it stayed within the input constraint.
-
-In CoNAC, all weight norms complied with the imposed constraints through the constrained optimization approach, as illustrated in Fig.\ref{fig: weight_CoNAC}.
-When any weight norm approached its upper limit, the Lagrange multiplier was promptly activated to steer the weight adaptation direction towards a constraint-satisfactory point (see Fig.\ref{fig: multiplier_CoNAC}).
-Notably, the weight norms of the first and second layers ($\Vert {{{\hat \wth }_0}} \Vert$ and $\Vert {{{\hat \wth }_1}} \Vert$) remained nearly constant throughout the control period.
-The weight norm of the last layer $\Vert {{{\hat \wth }_2}} \Vert$ stabilized within the upper bound by around 6.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (B)), coinciding with the activation of the input norm constraint.
-This quasi-static behavior of the weight norm (\ie $d{\estwth}/dt=-\alpha\partial L/\partial \estwth \approx 0$) along with the quasi-static behavior of the Lagrange multipliers (\ie $\dot\lambda_j = \beta_j c_j \approx 0$) implies that the weights were updated near the KKT conditions, signifying local optimality in CoNAC.
-However, at around 2.5 seconds (see Fig.~\ref{fig: weight_CoNAC} (A)), the weight norm of the last layer reached the upper limit earlier, despite similar control conditions as the case at 6.5 seconds.
-This earlier saturation likely occurred because the optimization process had not yet fully converged to the optimal weight values.
-%(\ie $\partial J/\partial\estwth = \sum_{j\in\mathcal {A}}\lambda_j\nabla_{\estwth} c_j)$.
-%, by the multipliers increased due to the violation of the constraints as shown in Fig.~\ref{fig: multiplier_CoNAC}.
-
-The overall weight norms of CoNAC were larger than those of DNN-BSC and DNN-BSC-A, since CoNAC approximated the entire stabilizing control law, whereas DNN-BSC and DNN-BSC-A only approximated the system uncertainty term within the BSC framework.
-
-%Because the simulation is implemented in a digital computer, the multipliers repeat to disappear and be generated, since the constraints are satisfied and violated in the digital process.
-
-%\subsection{Analysis of the Neural Network}
-
-%Generally, the existing literature states that the maximum norms of the weights should be sufficiently large (\ie $\bar\wth_i \gg 0$) since the designer does not know where the global optimal point of the weights is.
-%However, using the physical prior knowledge of the system, one can guess the proper value of the maximum norm, since the magnitude of the control input depends on the last layer's weights due to the bounded activation function.
-%Furthermore, the simulation study shows that the selected controllers have sufficiently good performances with the small maximum weight norms.
-%It means that the local optimal point of the weights are more effective for the stability analysis and the limitating the control input's amplitude.
-
-%Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
-%However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}.
-(\ie the weight updates are smaller as its layer is closer to the input layer.)
-%To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            fig/exp_set.jpg
+        }%
+    \caption{
+        Robot setup for the real-time experiment.
+    }
+    \label{fig:ctrl:exp:set}
+  \end{figure}
+
+\subsection{Real-time Experiment Validation}
+
+The proposed CoNAC was also validated through real-time experiments on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
+\color{red}
+The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two Dynamixel MX-28 servos.
+The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB.
+The reference trajectory was generated using the same method as in the numerical simulation.
+\color{black}
+The equal reference trajectory was applied and the parameters of the CoNAC were set to those whose best performance was achieved in the simulation (\ie $\beta=...$).
+Additionally, the computational time was measured to validate the effectiveness of the proposed CoNAC in real-time applications.
+
+The tracking result of the real-time experiment is shown in Fig.~\ref{fig:ctrl:result:exp}.
+
+is shown in Fig.~\ref{fig:ctrl:result:cmp:time}. The computational time of CoNAC was 0.5 ms, which is less than the sampling time of 4 ms. 
+This indicates that the proposed CoNAC can be implemented in real-time applications.
+
+\begin{figure*}[t]
+    \centering
+      \subfloat[Tracking result of $q_1$.]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+          src/measurement/figures/Fig1.eps
+        }%
+        \label{fig:ctrl:real:result:q1}}
+      % \vfill
+      \subfloat[Tracking result of $q_2$.]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+          src/measurement/figures/Fig2.eps
+        }%
+        \label{fig:ctrl:real:result:q2}}
+      \vfill
+        \subfloat[Control input $\tau_1$.]{
+          \includegraphics[width=\figSizeTwoCol\linewidth]
+          {
+            src/measurement/figures/Fig3.eps
+          }%
+          \label{fig:ctrl:real:result:tau:1}}
+      % \vfill
+        \subfloat[Control input $\tau_2$.]{
+          \includegraphics[width=\figSizeTwoCol\linewidth]
+          {
+            src/measurement/figures/Fig4.eps
+          }%
+          \label{fig:ctrl:real:result:tau:2}}
+          \vfill
+      \subfloat[Norm of weights $\hat\theta_i$.]{
+          \includegraphics[width=\figSizeTwoCol\linewidth]
+          {
+          src/measurement/figures/Fig5.eps
+          }%
+          \label{fig:ctrl:real:result:opt:norm}}
+          % \vfill
+      \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
+          \includegraphics[width=\figSizeTwoCol\linewidth]
+          {
+          src/measurement/figures/Fig6.eps
+          }%
+          \label{fig:ctrl:real:result:opt:multiplier}}
+          \vfill
+      \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
+          \includegraphics[width=\figSizeTwoCol\linewidth]
+          {
+              src/measurement/figures/Fig8.eps
+          }%
+          \label{fig:ctrl:real:result:opt:zeta}}
+          % \vfill
+      \subfloat[Control input $\tau$ in time interval from $1$ s to $3$ s (bird's eye view).]{
+          \includegraphics[width=\figSizeTwoCol\linewidth]
+          {
+              src/measurement/figures/Fig9.eps
+          }%
+          \label{fig:ctrl:real:result:control}}
+    \caption{
+    Simulation results of the CoNAC (blue) and CoNAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
+    }
+  \label{fig:ctrl:real:result}
+  \end{figure*}
+
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+          src/measurement/figures/Fig10.eps
+        }%
+    \caption{
+        Computational time of CoNAC and CoNAC-AUX. 
+    }
+    \label{fig:ctrl:real:result:cmp:time}
+  \end{figure}
 
@@
 
-This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+This paper presented a constrained optimization-\allowbreak based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
 The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
@@
 \begin{equation}
-    c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
+    c_{\rbu}=\norm{\mv{\tau}}^2 -\overline\tau^2  \le 0
     ,
@@
 \end{equation}
-with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
+with $\overline\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude.
 This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
 % The corresponding Lagrangian multiplier is $\lambda_{u_b}$. 
-The gradients of $c_{u}$ with respect to $\estwth$ are given by
-\begin{equation}
-    \pptfrac{\boldsymbol c_{u}}{\estwth}
+The gradients of $c_{\rbu}$ with respect to $\estwth$ are given by
+\begin{equation}
+    \pptfrac{\boldsymbol c_{\rbu}}{\estwth}
     \!=\! 
@@
 \bibliographystyle{elsarticle-harv} 
-\bibliography{refs}
+\bibliography{\template/refs}
 

### 2025-04-08 src/archive/script_simulation/dynamics_model/ref2_load.m

@@ -1,18 +1,0 @@
-function [r, rd, rdd] = ref2_load(x, t)
-
-dt = 1e-4;
-r = @(x, t)[ % desired trajectory
-    10
-    10
-    ] ;
-
-rd = @(x,t) [ 
-    0
-    0
-];
-
-rdd = @(x, t) [
-    0;0
-];
-
-end

### 2025-04-08 src/archive/script_simulation/dynamics_model/system2.m

@@ -1,80 +1,0 @@
-function [grad_x, r, rd, rdd, IC] = system2()
-
-% x = [q1 q2 \dot{q1} \dot{q2}]
-
-%% INITIAL CONDITION
-% ********************************************************
-IC.x = [1;-1;0;0];  
-IC.u = [0; 0];
-
-%% SYSTEM DYNAMICS
-% ********************************************************
-
-env.v = 13.33;
-env.q01 = 8.98;
-env.q02 = 8.75;
-env.g = 9.8;
-env.alpha = 3;
-env.gamma = 20;
-env.k1 = 0.001;
-
-M = @(x) [
-    env.v+env.q01+2*env.gamma*cos(x(2))     env.q01+env.q02*cos(x(2))
-    env.q01+env.q02*cos(x(2))               env.q01
-    ];
-
-C = @(x) [
-    -env.q02*x(4)*sin(x(2))                 -env.q02*(x(3)+x(4))*sin(x(2))
-    env.q02*x(3)*sin(x(2))                  0
-    ];
-    
-
-G = @(x) [
-    15*env.g*cos(x(1))+8.75*env.g*cos(x(1)+x(2))
-    8.75*env.g*cos(x(1)+x(2))
-    ];
-
-% d = @(x) zeros(2,1);
-d = @(x, t) [
-    tanh(x(1))*20 + sin(5*t)*3e1
-    -tanh(x(2))*20 + cos(5*t)*3e1
-];
-
-grad_x = @(x,u, t) blkdiag(eye(2), M(x)) \ ...
-    ([zeros(2) eye(2); zeros(2) -C(x)] * x + [zeros(2);eye(2)] * (-G(x)+u+d(x, t)));
-
-%% REFERENCE SIGNAL
-% ********************************************************
-
-
-% dt = 1e-4;
-% r = @(x, t)[ % desired trajectory
-%     heaviside(t - 3) + 1
-%     heaviside(t - 3) - 1
-%     ] ;
-% 
-% rd = @(x,t) [ 
-%     1/dt * (heaviside(t - 3) - heaviside(t - 3-dt))
-%     1/dt * (heaviside(t - 3) - heaviside(t - 3-dt))
-% ];
-% 
-% rdd = @(x, t) [
-%     0;0
-% ];
-
-r = @(x, t)[ % desired trajectory
[…]

### 2025-04-08 src/archive/script_simulation/simulate.m

@@ -1,309 +1,0 @@
-%% REPORTY SIMULATION
-fprintf("                                   \n");
-fprintf("***********************************\n");
-fprintf("*    Optimization based NN Ctrl   *\n");
-fprintf("***********************************\n");
-
-fprintf("                                 \n");
-fprintf(" Controller:\n");
-fprintf("     "+string(c_idx)+"\n");
-fprintf("\n");
-fprintf(" FLAGs\n");
-fprintf("     animation      : "+string(ANIMATION_FLAG)+"\n");
-fprintf("     animation save : "+string(AINMATION_SAVE_FLAG)+"\n");
-fprintf("     figure save    : "+string(FIGURE_SAVE_FLAG)+"\n");
-fprintf("     result save    : "+string(RESULT_SAVE_FLAG)+"\n");
-fprintf("\n");
-
-%% SYSTEM DECLARE
-[grad_x, IC] = model1_load();
-[r_f, rd_f, rdd_f] = ref1_load(); % sin func
-% [r_f, rd_f, rdd_f] = ref2_load(); % step func
-
-%% INITIAL CONDITION
-x = IC.x;
-u = IC.u;
-r1 = r_f(x, 0);
-r2 = rd_f(x, 0);
-
-%% NUERAL NETWORK DECLARE
-nn = nn_init(nnOpt);
-
-
-%% RECORDER
-num_x = length(x); num_u = length(u);
-num_t = length(t);
-
-x_hist = zeros(num_x, num_t); x_hist(:, 1) = x;
-r_hist = zeros(num_x/2, num_t); r_hist(:, 1) = r1;
-rd_hist = zeros(num_x/2, num_t); rd_hist(:, 1) = r2;
-u_hist = zeros(num_u, num_t); u_hist(:, 1) = u;
-uSat_hist = zeros(num_u, num_t); uSat_hist(:, 1) = u;
-L_hist = zeros(length(nnOpt.beta), num_t); L_hist(:,1) = zeros(length(nnOpt.beta),1);
-dot_L_hist = zeros(1, num_t); dot_L_hist(:,1) = 0;
-V_hist = zeros(nnOpt.l_size-1, num_t); V_hist(:, 1) = nn_V_norm_cal(nn.V, nnOpt);
-aux_hist = zeros(num_x/2, num_t);
-
-comp_control_hist = zeros(1, num_t);
[…]

### 2025-04-08 src/archive/script_simulation/test/nn_opt_bck.m

@@ -1,117 +1,0 @@
-function nnOpt = nn_opt(ctrl_name, dt)
-    %% DEFAULT PARAMETERS
-    nnOpt.dt = dt; % sampling time
-
-    nnOpt.e_tol = 0e-3; % error tolerance
-
-    nnOpt.init_range = 1e-3; % weight init range
-
-    % nnOpt.W = eye(4);
-    nnOpt.W = diag([1 1 15 15]);
-
-    %% CONTROLLER PARAMETERS
-    nnOpt.ctrl_param.k1 = 1.1;
-    nnOpt.ctrl_param.k2 = 10;
-    
-    nnOpt.ctrl_param.Azeta = diag([1 1]) * 1e1 * 2.0;
-    nnOpt.ctrl_param.Bzeta = diag([1 1]) * 1e0 * 10;
-    % nnOpt.ctrl_param.delta = 1e-1;
-    nnOpt.ctrl_param.delta = 1e3;
-
-    nnOpt.ctrl_param.M = eye(2) * 1;
-    nnOpt.ctrl_param.C = eye(2) * 1;
-    nnOpt.ctrl_param.G = zeros(2,1);
-    nnOpt.ctrl_param.inv_M = inv(nnOpt.ctrl_param.M);
-
-    %% ALGORITHM PARAMETERS
-    if strcmp(ctrl_name, "CTRL2")
-        nnOpt.alg = "Dixon";
-
-        nnOpt.alpha = 2e3; % learning rate
-        % nnOpt.rho = nnOpt.alpha * 1e-2; % e-modification
-        nnOpt.rho = 0;      
-        
-    elseif strcmp(ctrl_name, "CTRL3")
-        nnOpt.alg = "Dixon";
-
-        nnOpt.alpha = 2e3; % learning rate
-        % nnOpt.rho = nnOpt.alpha * 1e-2; % e-modification
-        nnOpt.rho = 0;
-
-%     elseif strcmp(ctrl_name, "Kasra")
-%         error("not use now")
-
-    elseif strcmp(ctrl_name, "CTRL4")
-        nnOpt.alg = "Proposed";
-
-        nnOpt.alpha = 1e3; % learning rate
-
-        c_num = 8;
-
-        nnOpt.Lambda = zeros(c_num,1);
-%         nnOpt.Beta = ones(c_num,1) * 1e+0;
-        nnOpt.Beta = [ ...
-            1 1 1 ...   % weight ball
-            0 0 ...     % maximum input
-            0 0 ...     % minimum input
[…]

### 2025-04-08 src/archive/script_simulation/test/opt_read_test.m

@@ -1,93 +1,0 @@
-clear
-
-opts = readtable("ctrlOpts.csv",'delimiter', ',', 'TextType', 'string','ReadVariableNames',0, 'ReadRowNames', 1);
-
-type_idx = find(opts.Properties.RowNames == "type");
-alg_idx = find(opts.Properties.RowNames == "alg");
-e_tol_idx = find(opts.Properties.RowNames == "e_tol");
-init_range_idx = find(opts.Properties.RowNames == "init_range");
-k1_idx = find(opts.Properties.RowNames == "k1");
-k2_idx = find(opts.Properties.RowNames == "k2");
-M_idx = find(opts.Properties.RowNames == "M");
-C_idx = find(opts.Properties.RowNames == "C");
-G_idx = find(opts.Properties.RowNames == "G");
-NN_size_idx = find(opts.Properties.RowNames == "NN_size");
-alpha_idx = find(opts.Properties.RowNames == "alpha");
-rho_idx = find(opts.Properties.RowNames == "rho");
-beta_idx = find(opts.Properties.RowNames == "beta");
-V_max_idx = find(opts.Properties.RowNames == "V_max");
-U_max_idx = find(opts.Properties.RowNames == "U_max");
-U_min_idx = find(opts.Properties.RowNames == "U_min");
-u_ball_idx = find(opts.Properties.RowNames == "u_ball");
-Azeta_idx = find(opts.Properties.RowNames == "Azeta");
-Bzeta_idx = find(opts.Properties.RowNames == "Bzeta");
-
-c_idx = 1;
-
-type = opts{type_idx, c_idx};
-
-if strcmp(type, "CTRL1") % BSC
-    ctrlOpt.k1 = str2num(opts{k1_idx, c_idx});
-    ctrlOpt.k2 = str2num(opts{k2_idx, c_idx});
-
-    ctrlOpt.M = str2num(opts{M_idx, c_idx});
-    ctrlOpt.C = str2num(opts{C_idx, c_idx});
-    ctrlOpt.G = str2num(opts{G_idx, c_idx});
-
-elseif strcmp(type, "CTRL2") % BSC + Dixon
-    nnOpt.e_tol = str2num(opts{e_tol_idx, c_idx});
[…]

### 2025-04-08 src/archive/script_simulation/utils_NN/nn_cstr.m

@@ -1,57 +1,0 @@
-function [c, cd] = nn_cstr(nn, nnOpt, u_NN, nnGrad)
-    %% CONSTRAINTS PARAMETERS
-    V_max = nnOpt.cstr.V_max;
-    U_max = nnOpt.cstr.U_max;
-    U_min = nnOpt.cstr.U_min;
-    u_ball = nnOpt.cstr.u_ball;
-    
-    %% ERROR CHECK
-    assert(length(V_max) == nnOpt.l_size-1)
-    
-    %% ACTIVE SET CHECK
-    % ball condition
-    c_b = zeros(nnOpt.l_size-1, 1);
-    
-    cumsum_V = [0;cumsum(nnOpt.v_size_list)];
-    for l_idx = 1:1:nnOpt.l_size-1
-        start_pt = cumsum_V(l_idx)+1;
-        end_pt = cumsum_V(l_idx+1);   
-
-        c_b(l_idx) = norm(nn.V(start_pt: end_pt))^2 ...
-            - V_max(l_idx)^2;
-    end
-    
-    % input saturation 
-    u = -u_NN;
-    c_M = u - U_max;
-    c_m = U_min - u;
-    
-    % input ball
-    c_ub = norm(u)^2 - u_ball^2;
-
-    % summary
-    c = [c_b; c_M; c_m; c_ub];
-    
-    %% ACTIVE SET CONSTRAINT GRADIENT CALC
-    cd = zeros(length(c), nnOpt.v_size);
-    for l_idx = 1:1:length(V_max)
-        start_pt = cumsum_V(l_idx)+1;
-        end_pt = cumsum_V(l_idx+1);
-        cd(l_idx, start_pt:end_pt) = 2 * nn.V(start_pt:end_pt,1);
-    end
-    
-    cd(l_idx+1:end, :) = [
-        -nnGrad;
-        +nnGrad;
-        2*u(1)*-nnGrad(1,:) + 2*u(2)*-nnGrad(2,:)
-        ];
-end
-
-
-
-
-
-
-
-
-

### 2025-04-08 src/archive/script_simulation/utils_NN/opt_load.m

@@ -1,177 +1,0 @@
-function [ctrlOpt, nnOpt] = opt_load(c_idx, opts, dt)
-
-    type_idx = find(opts.Properties.RowNames == "type");
-    alg_idx = find(opts.Properties.RowNames == "alg");
-    e_tol_idx = find(opts.Properties.RowNames == "e_tol");
-    init_range_idx = find(opts.Properties.RowNames == "init_range");
-    k1_idx = find(opts.Properties.RowNames == "k1");
-    k2_idx = find(opts.Properties.RowNames == "k2");
-    M_idx = find(opts.Properties.RowNames == "M");
-    C_idx = find(opts.Properties.RowNames == "C");  
-    G_idx = find(opts.Properties.RowNames == "G");
-    NN_size_idx = find(opts.Properties.RowNames == "NN_size");
-    alpha_idx = find(opts.Properties.RowNames == "alpha");
-    rho_idx = find(opts.Properties.RowNames == "rho");
-    W_idx = find(opts.Properties.RowNames == "W");
-    beta_idx = find(opts.Properties.RowNames == "beta");
-    V_max_idx = find(opts.Properties.RowNames == "V_max");
-    U_max_idx = find(opts.Properties.RowNames == "U_max");
-    U_min_idx = find(opts.Properties.RowNames == "U_min");
-    u_ball_idx = find(opts.Properties.RowNames == "u_ball");
-    Azeta_idx = find(opts.Properties.RowNames == "Azeta");
-    Bzeta_idx = find(opts.Properties.RowNames == "Bzeta");
-    L2_idx = find(opts.Properties.RowNames == "L2");
- 
-    %% DEFAULT PARAMETERS
-    nnOpt.dt = dt; % sampling time
-
-    type = opts{type_idx, c_idx};
-
-    if strcmp(type, "CTRL1") % BSC
-        ctrlOpt.type = type;
-        nnOpt.alg = opts{alg_idx, c_idx};
-
-        ctrlOpt.k1 = str2num(opts{k1_idx, c_idx});
-        ctrlOpt.k2 = str2num(opts{k2_idx, c_idx});
-    
-        ctrlOpt.M = str2num(opts{M_idx, c_idx});
[…]

### 2025-04-08 src/measurement/plot_idv.m

@@ -1,0 +1,247 @@
+
+%% RESULT PLOTTER
+t1 =data(ep_idx,1);
+t1 = t1-t1(1);
+T = t1(end);
+obs_t1 = 1:length(t1);
+
+start_time = 8.5;
+end_time = 9.9;
+
+obs_t1_1 = find(t1 >= start_time & t1 <= end_time);
+
+c1_x1 =     transpose(data(ep_idx,[3,4]));
+c1_x2 =     transpose(data(ep_idx,[5,6]));
+c1_xd1 =    transpose(data(ep_idx,[7,8]));
+c1_xd2 =    transpose(data(ep_idx,[9,10]));
+c1_u =      transpose(data(ep_idx,[11,12]));
+c1_uSat =   transpose(data(ep_idx,[13,14]));
+c1_lbd =    transpose(data(ep_idx,15:22));
+c1_th =     transpose(data(ep_idx,23:25));
+c1_zeta =   transpose(data(ep_idx,26:27));
+c1_cmp =    transpose(data(ep_idx,28));
+
+%%
+% ============================================
+%     Fig. 1: Current d-axis (Ref vs Obs)
+% ============================================
+figure(1); clf;
+hF = gcf; 
+hF.Position(3:4) = [fig_width, fig_height];
+
+plot(t1(obs_t1), c1_x1(1,obs_t1), "Color", "blue", "LineWidth", line_width, "LineStyle", "-"); hold on
+plot(t1(obs_t1), c1_xd1(1,obs_t1), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
+
+grid on; grid minor;
+xlabel('Time / s', 'FontSize', font_size, 'Interpreter', 'latex');
+ylabel('$q_1$ / rad', 'FontSize', font_size, 'Interpreter', 'latex');
+% maxVal = max(id_ref.Data); minVal = min(id_ref.Data); 
+maxVal = 2; minVal = -2; 
+len = maxVal-minVal; ratio = .3;
+ylim([minVal-len*ratio maxVal+len*ratio]);
+xlim([0 T])
+    ax = gca;
+    ax.FontSize = font_size; 
+    ax.FontName = 'Times New Roman';
+
+% ============================================
+%     Fig. 2: Current q-axis (Ref vs Obs)
+% ============================================
+figure(2); clf;
+hF = gcf; 
+hF.Position(3:4) = [fig_width, fig_height];
+
[…]

### 2025-04-08 src/measurement/post_procc.m

@@ -1,6 +1,6 @@
 function [data, loss_ratio] = post_procc(ctrl_name)
 
-    data = readtable("sim_result/"+ctrl_name+".csv");
+    data = readtable("sim_result/"+ctrl_name);
     data = data{1:end-1, 1:28};
 
     del_ts = [0.001, 0.004];

### 2025-04-08 src/measurement/post_procc_sep.m

@@ -1,0 +1,105 @@
+function [data, loss_ratio] = post_procc_sep(ctrl_name)
+
+    % remove the data with large change
+    data = readtable("sim_result/"+ctrl_name);
+    data = data{1:end-1, 1:28};
+    ori_num = length(data);
+
+    pt = 1:size(data,1);
+    thr = 2e0;
+    for idx = 3:28
+        tmp_pt = find((data(2:end,idx) - data(1:end-1,idx)).^2 > thr);
+        pt = setdiff(pt, tmp_pt);
+    end
+    
+    data = data(pt, :);
+    mod_num = length(data);
+    loss_ratio = (ori_num - mod_num) / ori_num;
+    fprintf('loss ratio: %.3f%%\n', loss_ratio*1e2);
+
+    % seperate
+    pt1 = find(data(:,2) == 2);
+    pt2 = find(data(:,2) == 3); 
+    pt = setdiff(1:size(data,1), pt1);ww
+    pt = setdiff(pt, pt2);
+    data(pt, 2) = zeros(length(pt), 1);
+    
+    figure(1); clf;
+    plot(data(:,1), data(:,2)); hold on
+    plot(data(:,1), data(:,4)); hold on
+
+    rise_flag = find(data(2:end,2) - data(1:end-1,2) > 0);
+    rise_t = data(rise_flag, 1);
+    fall_flag = find(data(2:end,2) - data(1:end-1,2) < 0);
+    fall_t = data(fall_flag, 1);
+
+    assert(length(rise_flag) == length(fall_flag), "rise and fall flag length mismatch");
+
+
+
+
+    return
+
+    del_ts = [0.001, 0.004];
+
+    pt = find(data(:,2).^2 > 1e-6);
+    data = data(pt, :);
+    ori_num = length(data);
+
+    pt = [];
+    % sampling time check
+    for idx = 1:length(del_ts)
+        del_t = del_ts(idx);
+        tmp_pt = find((data(2:end,1) - data(1:end-1,1) - del_t).^2 < 1e-6);
+        
+        pt = union(pt, tmp_pt);
+    end
+
+    % remove the data with large change
+    thr = 1e0;
+    for idx = 3:28
[…]

### 2025-04-09 presentation/presentation.tex
add presentation

% https://www.overleaf.com/learn/latex/Beamer#Using_a_colortheme

% Inbuilt themes in beamer
\documentclass{beamer}

% Theme choice:
\usetheme{Antibes}
\usecolortheme{beaver}

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro–Adaptive Control 
} 
\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, \and Kyunghwan Choi\inst{1}}
\date{\today}

\institute % (optional)
{
  \inst{1}%
  Department of Mechanical and Robotics Engineering\\
  Gwangju Institute of Science and Technology 
  \and
  \inst{2}%
  AI Graduate School\\
  Gwangju Institute of Science and Technology 
}

\logo{
    \includegraphics[height=1cm]{../template/figs/logo_GIST.png}
}

\begin{document}

% Title page frame
\begin{frame}
    \titlepage 
\end{frame}

% Remove logo from the next slides
\logo{}

% Outline frame
\begin{frame}{Outline}
    \tableofcontents
\end{frame}

% Lists frame
\section{Lists in Beamer}
\begin{frame}{Lists in Beamer}

This is an unordered list:
\begin{itemize}
    \item Item 1
    \item Item 2
    \item Item 3
\end{itemize}

and this is an ordered list:
\begin{enumerate}
    \item Item 1
    \item Item 2
    \item Item 3
\end{enumerate}

\end{frame}

% Blocks frame
\section{Blocks in Beamer}
\begin{frame}{Blocks in Beamer}
    \begin{block}{Standard Block}
        This is a standard block.
    \end{block}
    \begin{alertblock}{Alert Message}
        This block presents alert message.
    \end{alertblock}
    \begin{exampleblock}{An example of typesetting tool}
        Example: MS Word, \LaTeX{}
    \end{exampleblock}
\end{frame}

\end{document}

### 2025-04-09 src/measurement/var_plot.m
new figures

@@ -11,14 +11,14 @@ fig_height = 230 * 1.5;
 fig_width = 800 * 1;
 
 % 
-ctrl_name = "beta10_to_90";
+ctrl_name = "COM4_2025_04_09";
 
 sim_dt = 1/250;
 ISE = @(e) sqrt(sum(e.^2)*sim_dt);
 
-u_max1 = 10;
-u_max2 = 2;
-u_ball = 10;
+u_max1 = 11.5;
+u_max2 = 16;
+u_ball = 12;
 th_max = [11,12,13];
 
 [~,~] = mkdir("figures/"+ctrl_name);
@@ -28,7 +28,7 @@ th_max = [11,12,13];
 [~,~] = mkdir("figures/"+ctrl_name+"/c1/fig2");
 [~,~] = mkdir("figures/"+ctrl_name+"/c1/fig3");
 [~,~] = mkdir("figures/"+ctrl_name+"/c1/fig4");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig5");
+[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig5"); 
 [~,~] = mkdir("figures/"+ctrl_name+"/c1/fig6");
 [~,~] = mkdir("figures/"+ctrl_name+"/c1/fig7");
 [~,~] = mkdir("figures/"+ctrl_name+"/c1/fig8");
@@ -52,6 +52,12 @@ data = readtable("sim_result/"+ctrl_name);
 data = data{1:end-1, 1:28};
 ori_num = length(data);
 
+
+figure(12); clf;
+plot(data(:,2)); hold on
+% % plot(data(:,1), data(:,9)); hold on
+
+
 del_ts = [0.001, 0.004];
 pt = [];
 % sampling time check
@@ -64,7 +70,7 @@ end
 data = data(pt, :);
 
 pt = 1:size(data,1);
-thr = 1e0;
+thr = 1e-1;
 for idx = 3:28
     tmp_pt = find((data(2:end,idx) - data(1:end-1,idx)).^2 > thr);
     pt = setdiff(pt, tmp_pt);
@@ -76,17 +82,18 @@ loss_ratio = (ori_num - mod_num) / ori_num;
 fprintf('loss ratio: %.3f%%\n', loss_ratio*1e2);
 
 % seperate
-pt1 = find(data(:,2) == 2);
-pt2 = find(data(:,2) == 3);
[…]

### 2025-04-11 manuscript.tex
new figures
update new simuilation results

@@
     \centering
-    \includegraphics[width=0.9\linewidth]{src/figures/Controller.drawio.png}
+    \includegraphics[width=0.8\linewidth]{src/figures/Controller.drawio.png}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
 \end{equation}
-where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
+where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}_{>0}$ is a user-designed filtering matrix.
 Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
@@
     \begin{cases}
-        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
+        (
+            \mm I_{l_{k+1}}
+            \otimes 
+            \act_{k}^\top  
+        )
+        , 
         &
-        i=k,
-        \\
-        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
+        i=k
+        ,
+        \\
+        \wV_k^\top\act_{k}' 
+        (
+            \mm I_{l_{k}}
+            \otimes  
+            \act_{k-1}^\top  
+        )
+        , 
         & 
-        i=k-1,
+        i=k-1
+        ,
         \\
@@
         \\
-        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes {\q}_n^\top  ), 
+        \wV_k^\top\act'_{k} 
+        \cdots 
+        \wV_1^\top\act_1' 
+        (
+            \mm I_{l_1}
+            \otimes 
+            {\q}_n^\top  
+        )
+        , 
         &
-        i = 0,
+        i = 0
+        ,
     \end{cases}
@@
 \end{equation}
-where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
+and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
 
@@
         \min_{\estwth} \ J(\fe;\estwth):= 
-        \tfrac{1}{2} \fe^\top \fe
+        \tfrac{1}{2} \fe^\top \fe₩
         \\ \\
         \begin{aligned}
-        \text{s.t. }&c_{j}(\estwth) 
+        \text{subject to }&c_{j}(\estwth) 
         \le0, \quad j\in\mathcal{I},
@@
             =
-            -\Gamma \pptfrac{L}{\estwth}
-            =
-            -\Gamma 
+            -\alpha \pptfrac{L}{\estwth}
+            =
+            -\alpha 
             \left(
@@
 \end{subequations}
-where $\Gamma=\Gamma^\top:=\mydiag([\gamma_1,\cdots,\gamma_n])\in\R^{n\times n}_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
-By selecting $\gamma_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
+where $\alpha=\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+% By selecting $\alpha_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
 The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
@@
     \approx
-    -\Gamma 
+    -\alpha 
     \left(
@@
 For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
-If a large $T_s$ is used, $\Gamma$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
+If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
 
@@
 
-To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2}\estwth_k^\top\Gamma^{-1} \estwth_k$.
+To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
 Taking the time derivative of $V_2$ yields:
@@
         -\estwth_k^\top 
-        \Gamma^{-1}\Gamma
         (
@@
     =
-    -\Gamma
+    -\alpha
     \left(
@@
 % ------------------------------------
-To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_1}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
+To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
 %
@@
             \mid
-            \norm{\rbu} \le \overline\tau
+            \norm{\rbu} \le 
+            10
+            % \overline\tau
         \right\}
@@
         \\
-        \Theta_{\mysat, {\tau_1}}
+        \Theta_{\mysat, {\tau_2}}
         :=&
         \left\{
-            \tau_1
+            \tau_2
             \mid
-            \vert{\tau_1}\vert \le \overline\tau_1
+            \vert{\tau_2}\vert \le 
+            2.5
+            % \overline\tau_2
         \right\}
-        ,
-        \label{eq:sat:tau1}
+        .
+        \label{eq:sat:tau2}
     \end{align}
@@
 %
-\MSRY{CORRECT HERE}
-with $\overline\tau=10$ and $\overline\tau_1=9$ are the saturation limit values for the norm of the control input norm and the first links, respectively. 
-These domains \ref{eq:sat:norm} and \ref{eq:sat:tau1} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the first link actuator.
+These domains \ref{eq:sat:norm} and \ref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator.
 
@@
 % ------------------------------------
-For a comparative study, CoNAC with the auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (CoNAC-AUX) was implemented, which only considered the weight norm constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ and input bound constraint $c_{\overline\tau_1}$ and $c_{\underline\tau_1}$ introduced in \eqref{eq:cstr:input:bound} and not the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}.
-Besides, the proposed controller, CoNAC, rigorously considered the weight norm constraint, and input bound and norm constraints simultaneously within a constrained optimization framework. 
-The properties of the controllers are summarized in Table \ref{table:controller}.
-
-% ------------------------------------
-% Aux. system in CoNAC-AUX
-% ------------------------------------
-The auxiliary system in CoNAC-AUX is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} =
+For a comparative study, we implemented 3 controllers:
+
+% ------------------------------------
+% Controllers: CoNAC 
+% ------------------------------------
+\subsubsection*{Controller 1: (C$_1$) proposed}
+
+To handle the input saturation, the proposed CoNAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
+\begin{equation}
+    \begin{aligned}
+        c_{\overline\tau_2}     
+        =&
+        \tau_2-\overline\tau_2
+        \le 0
+        ,
+        \quad
+        c_{\underline\tau_2} 
+        =&
+        \underline\tau_2-\tau_2
+        \le 0
+        ,
+        \quad
+        c_{\rbu}
+        =&
+        \tfrac{1}{2}
+        (
+            \norm{\rbu}-\overline\tau
+        )^2 
+        ,
+    \end{aligned}
+    \label{eq:sim:cstr:CoNAC}
+\end{equation}
+where $\overline\tau_2=2.5$ and $\underline\tau_2=-2.5$ are the upper and lower bounds of the second link actuator, respectively, and $\overline\tau=10$ is the maximum allowable norm of the control input.
+Hence, (C$_1$) is possible to use full capability of the actuator.
+The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
+As described in \eqref{eq:control:est}, the control input is equal to the output of the NN $\rbu$, and the adaptation law is defined in \eqref{eq:adaptation law}.
+
+% ------------------------------------
+% Controllers: Aux. system in CoNAC-AUX
+% ------------------------------------
+\subsubsection*{Controller 2: (C$_2$) CoNAC with auxiliary system}
+
+On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
+The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} =
 \tau_{1}-\max(\underline\tau_1,\min(\overline\tau_1,\tau_1))$.
+Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$.
+
 The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
@@
 % ------------------------------------
+% Controllers: CoNAC with small beta
+% ------------------------------------
+\subsubsection*{Controller 3: (C$_3$) CoNAC with small $\beta_i$}
+
+To investigate the effect of the update rate of Lagrange multipliers, C$_3$ was implemented with small $\beta_i$ values.
+
+\hfill
+
+% ------------------------------------
 % Controller Parameters
 % ------------------------------------
-For all controllers (CoNAC, and CoNAC-AUX), the NN input vector ${\q}_n$ was set as ${\q}_n=[\q^\top,\dq^\top,\fe^\top,1]^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=[\q^\top,\dq^\top,\fe^\top,1]^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
 The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
-Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\Gamma=\mydiag([1.5,1.0])$. 
-The constraint parameters were $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$. 
-The sampling rate of the controller was set to $250$ Hz, and $1000$ Hz for the simulation.
-
-The quantitative comparison of the tracking performance and the control input constraint violations were evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h},\der t}$, where $h\in\{r_1,r_2,\max(0,c_{\rbu}),\max(0,c_{\overline\tau_1}+c_{\underline\tau_1})$ and $T\in\R_{>0}$ denotes the episode duration time.
-Note that $c_{\overline\tau_1}$ and $c_{\underline\tau_1}$ can not be active at the same time, so $\max(0,c_{\overline\tau_1}+c_{\underline\tau_1})$ is used to evaluate the control bound constraint violation.
-To investigate the parameter dependencies, the parameters of the controllers $\beta_u,\beta_{\overline\tau},\beta_{\underline\tau}$ \MSRY{CORRECT} were varied within the range of \MSRY{SEE HERE} $[0.5,1.5]$ across 100000 samples.
+Each NN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=1$.
+The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,5])$.
+The sampling rate of the controller was $250$ Hz, and $1000$ Hz for the simulation.
+To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.
+
+The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h},\der t}$, where $h\in\{r_1,r_2\}$ and $T\in\R_{>0}$ denotes the episode duration time.
+Note that $c_{\overline\tau_i}$ and $c_{\underline\tau_i},\ \forall i\in\{1,2\}$ can not be active at the same time.
 
@@
     \centering
-    \begin{tabular}{c c c}
-    \hline
-        & \multicolumn{2}{c}{\bf{Handling Capability}}\\
-        & Weight Constraint & Input Constraint\\
-    \hline
-    \hline
-    \multirow{2}{*}{\bf{CoNAC}} & O & O \\
-        & (by optimization) &  (by optimization)\\
-    \hline
-    \multirow{2}{*}{\bf{CoNAC-AUX}} & O & $\triangle$ \\
-        & (by optimization) & (by aux. system)\\
+    \begin{tabular}{c l l}
+    \hline
+        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
+    \hline
+    \hline
+        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
+    \hline
+        (C$_2$) & aux. sys. & $\overline{\tau_1}=-\underline{\tau_1}=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
+    \hline
+        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
     \hline
@@
 % ------------------------------------
-\begin{figure}[!t]      
-    \centering
-    {\includegraphics[width=\figSizeOneCol\linewidth]{
-        src/measurement/figures/Fig11.eps
-    }}
-\caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX across various parameter values.}
-    \label{fig:ctrl:result:var}
-\end{figure}
-
-\begin{table}[!t]
-    \renewcommand{\arraystretch}{1.3}
-    \caption{Quantitative comparison of $L_2$-norms of the tracking performances and control input constraint violations.}
-    \centering
-    \begin{tabular}{c c c c}
-    \hline
-        \!&\!Maximum\!&\!Median\!&\!Minimum\!\\
-    \hline
-    \hline
-    \textbf{CoNAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
-    \hline
-    \textbf{CoNAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
-    \hline
-    \end{tabular}
-    \label{table:ctrl:result:var}
-\end{table}
+% \begin{figure}[!t]      
+%     \centering
+%     {\includegraphics[width=\figSizeOneCol\linewidth]{
+%         src/measurement/figures/Fig11.eps
+%     }}
+% \caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX across various parameter values.}
+%     \label{fig:ctrl:result:var}
+% \end{figure}
+
+% \begin{table}[!t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Quantitative comparison of $L_2$-norms of the tracking performances and control input constraint violations.}
+%     \centering
+%     \begin{tabular}{c c c c}
+%     \hline
+%         \!&\!Maximum\!&\!Median\!&\!Minimum\!\\
+%     \hline
+%     \hline
+%     \textbf{CoNAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
+%     \hline
+%     \textbf{CoNAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
+%     \hline
+%     \end{tabular}
+%     \label{table:ctrl:result:var}
+% \end{table}
 
@@
 %     \hline
-%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\Gamma$ & $\beta$ & $\overline\theta_0$ & $\overline\theta_1$ & $\overline\theta_2$ & $\overline\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
+%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\overline\theta_0$ & $\overline\theta_1$ & $\overline\theta_2$ & $\overline\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
 %     \hline
@@
       {
-        src/measurement/figures/Fig1.eps
+        % src/script_simulation/figures/compare/Fig10.eps
+        src/script_simulation/figures/compare/Fig1.eps
       }%
@@
       {
-        src/measurement/figures/Fig2.eps
+        % src/script_simulation/figures/compare/Fig11.eps
+        src/script_simulation/figures/compare/Fig2.eps
       }%
@@
         {
-          src/measurement/figures/Fig3.eps
+            src/script_simulation/figures/compare/Fig3.eps
         }%
@@
         {
-          src/measurement/figures/Fig4.eps
+            src/script_simulation/figures/compare/Fig4.eps
         }%
@@
         \vfill
+    \subfloat[Norm of control input $\tau$.]{
+        \includegraphics[width=\figSizeTwoCol\linewidth]
+        {
+            src/script_simulation/figures/compare/Fig5.eps
+        }%
+        \label{fig:ctrl:result:opt:norm}}
     \subfloat[Norm of weights $\hat\theta_i$.]{
@@
         {
-        src/measurement/figures/Fig5.eps
-        }%
-        \label{fig:ctrl:result:opt:norm}}
-        % \vfill
-    \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
-        \includegraphics[width=\figSizeTwoCol\linewidth]
-        {
-        src/measurement/figures/Fig6.eps
+            src/script_simulation/figures/compare/Fig7.eps
         }%
         \label{fig:ctrl:result:opt:multiplier}}        
-        \vfill
-    \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
-        \includegraphics[width=\figSizeTwoCol\linewidth]
-        {
-            src/measurement/figures/Fig8.eps
-        }%
-        \label{fig:ctrl:result:opt:zeta}}
-        % \vfill
-    \subfloat[Control input $\tau$ in time interval from $1$ s to $3$ s (bird's eye view).]{
-        \includegraphics[width=\figSizeTwoCol\linewidth]
-        {
-            src/measurement/figures/Fig9.eps
-        }%
-        \label{fig:ctrl:result:control}}
     \caption{
@@
 \end{figure*}
+
+\begin{figure}[t]
+    \centering
+    \subfloat[Control input $\tau$ in time interval from $19$ s to $20$ s (bird's eye view).]{
+    % \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            src/script_simulation/figures/compare/Fig6.eps
+        }%
+        \label{fig:ctrl:result:scope:opt:zeta}}
+        \vfill
+    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $20$ s.]{
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            src/script_simulation/figures/compare/Fig8.eps
+        }%
+        \label{fig:ctrl:result:scope:control}}
+        \vfill
+    \subfloat[Auxiliary states in time interval from $19$ s to $20$ s.]{
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            src/script_simulation/figures/compare/Fig9.eps
+        }%
+        \label{fig:ctrl:result:scope:aux}}
+  \caption{
+  Simulation results of the CoNAC (blue) and CoNAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
+  }
+\label{fig:ctrl:result:scope}
+\end{figure}
 
@@
 % ------------------------------------
+% Norm of error in Episode 1: 
+% C1 r1 ep1: 0.317
+% C1 r2 ep1: 0.467
+% C2 r1 ep1: 0.326
+% C2 r2 ep1: 0.475
+% C3 r1 ep1: 0.318
+% C3 r2 ep1: 0.471
+% Norm of error in Episode 2: 
+% C1 r1 ep2: 0.055
+% C1 r2 ep2: 0.155
+% C2 r1 ep2: 0.070
+% C2 r2 ep2: 0.179
+% C3 r1 ep2: 0.058
+% C3 r2 ep2: 0.190
+% Improvement in Episode 2: 
+% C1 r1: 0.827
+% C1 r2: 0.668
+% C2 r1: 0.785
+% C2 r2: 0.625
+% C3 r1: 0.818
+% C3 r2: 0.596
+% ------------------------------------
+\begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    \caption{Quantitative comparison of performances' $L_2$ norm.}
+    \centering
+    \begin{tabular}{c c c c c c c}
+    \hline
+		& \multicolumn{3}{c}{\textbf{Episode 1}}  & \multicolumn{3}{c}{\textbf{Episode 2}} \\
+    \hline
+	\hline 
+		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_1$) & (C$_2$) & (C$_3$) \\
+	\hline
+		$r_1$ & $0.317$ & $0.326$ & $0.318$ & $0.055$ & $0.070$ & $0.058$ \\
+	\hline
+        $r_2$ & $0.467$ & $0.475$ & $0.471$ & $0.155$ & $0.179$ & $0.190$ \\
+	\hline
+    \end{tabular}
+    \label{tab:sim:L2}
+\end{table}
+
+% ------------------------------------
 % Tracking Performance
 % ------------------------------------
-\subsubsection{Parameter Dependency and Tracking Performance}
-
-The quantitative study of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX are shown in Fig.~\ref{fig:ctrl:result} and Table.~\ref{table:ctrl:result:var}.
+\subsubsection{Tracking Performance}
+
+The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is shown in Table~\ref{tab:sim:L2}.
 
@@
 
+% ------------------------------------
+% Real-time Implementation Set-up
+% ------------------------------------
 \begin{figure}[t]

### 2025-04-11 src/script_simulation/controllers/CoNAC-Aux/initControl.m

@@ -1,0 +1,5 @@
+z = zeros(length(u), 1);
+
+%% NEURAL NETOWORK INITIAILIZATION
+nn.th = (rand(opt.th_size,1)-1/2)*2*opt.init_range;
+nn.tape = zeros(opt.tp_size, 1);

### 2025-04-11 src/script_simulation/controllers/CoNAC-Aux/loadOpts.m

@@ -1,0 +1,37 @@
+function opt = loadOpts(dt)
+    opt.dt = dt;
+
+    opt.e_tol = 0e-3;
+    opt.init_range = 1e-3;
+    
+    opt.Lambda = diag([1 1]) * 5e0;
+
+    opt.alpha = 8e-1;
+    opt.rho = opt.alpha*0e-2;
+    opt.NN_size = [6,8,8,2];
+    opt.W = 1;
+    opt.e_size = 2;
+
+    % opt.beta = [1 1 1] * 1e-1;
+    opt.beta(1:3) = [1 1 1] * 0e-3;
+    opt.beta(4) = 0e-2; % control ipnut
+    opt.cstr.th_max = [11;12;13] * 1e0;
+    opt.cstr.u_ball = 20;
+
+    c_num = length(opt.beta);
+    opt.lbd = zeros(c_num,1);
+    
+%% PASSIVE NUMBER
+    % layer number
+    opt.l_size = length(opt.NN_size);
+    % total tape number
+    opt.tp_size = sum(opt.NN_size(1:end-1));
+    % total weight number (will be calc-ed)
+    opt.th_size_list = zeros(opt.l_size-1 ,1);    
+    for idx = 1:1:opt.l_size-1
+        opt.th_size_list(idx) = (opt.NN_size(idx)+1) * opt.NN_size(idx+1);
+    end
+
+    opt.th_size = sum(opt.th_size_list);    
+
+end

### 2025-04-11 src/script_simulation/controllers/CoNAC-Aux/postControl.m

@@ -1,0 +1,16 @@
+
+del_u = zeros(2,1);
+if u(1) > opt.cstr.uMax1
+    del_u(1) = u(1) - opt.cstr.uMax1;
+elseif u(1) < -opt.cstr.uMax1
+    del_u(1) = u(1) + opt.cstr.uMax1;
+end
+if u(2) > opt.cstr.uMax2
+    del_u(2) = u(2) - opt.cstr.uMax2;
+elseif u(2) < -opt.cstr.uMax2
+    del_u(2) = u(2) + opt.cstr.uMax2;
+end
+
+z = z + (opt.A_zeta*z + opt.B_zeta*del_u) * opt.dt;
+
+[nn, opt] = nnBackward(nn, opt, r+z, u_NN);

### 2025-04-11 src/script_simulation/controllers/CoNAC-Aux/preControl.m

@@ -1,0 +1,8 @@
+
+x_in = [x1;x2;r];
+
+[nn, u_NN] = nnForward(nn, opt, x_in);
+u = u_NN;
+
+
+

### 2025-04-11 src/script_simulation/controllers/NAC-Aux/postControl.m

@@ -1,16 +1,0 @@
-
-del_u = zeros(2,1);
-if u(1) > opt.cstr.uMax1
-    del_u(1) = u(1) - opt.cstr.uMax1;
-elseif u(1) < -opt.cstr.uMax1
-    del_u(1) = u(1) + opt.cstr.uMax1;
-end
-if u(2) > opt.cstr.uMax2
-    del_u(2) = u(2) - opt.cstr.uMax2;
-elseif u(2) < -opt.cstr.uMax2
-    del_u(2) = u(2) + opt.cstr.uMax2;
-end
-
-z = z + (opt.A_zeta*z + opt.B_zeta*del_u) * opt.dt;
-
-[nn, opt] = nnBackward(nn, opt, r+z, u_NN);

### 2025-04-11 src/script_simulation/controllers/NAC-Aux/utils/nnBackward.m

@@ -1,25 +1,0 @@
-function [nn, opt] = nnBackward(nn, opt, e, u_NN)
-
-    %% NN GRADIENT CALCULATION
-    nnGrad = nnGradient(nn, opt);
-
-    % dead-zone
-    if norm(e) < opt.e_tol
-        return;
-    end
-
-    %% UPDATE
-    % active set check
-    [c, cd] = nnCstr(nn, opt, nnGrad);
-
-    % find gradient; theta, lambda
-    th_grad = - opt.alpha * (nnGrad'*opt.W*e);
-    th_grad = th_grad + - opt.rho * nn.th;
-
-    th_grad = th_grad * opt.dt;
-    % update
-    nn.th = nn.th + th_grad;
-
-    %% TERMINATION
-    
-end

### 2025-04-11 src/script_simulation/controllers/NAC-Aux/utils/nnForward.m

@@ -1,46 +1,0 @@
-function [nn, out] = nnForward(nn, opt, in)
-    
-    %% POINTER TO START POINT
-    pt_V = 1;
-    pt_tape = 1;
-
-    %% FORWARD
-    % save to gradient tape
-    nn.tape(1: 1+opt.NN_size(1)-1) = in;
-    pt_tape = pt_tape + opt.NN_size(1);
-
-    for l_idx = 1:1:opt.l_size-1
-        n = opt.NN_size(l_idx)+1;
-        m = opt.NN_size(l_idx+1);
-
-        % get V weight
-        V = reshape(nn.th(pt_V: pt_V+(n*m)-1), n,m);
-    
-        % phi_k = tanh(nn_out); 1]
-        if l_idx == 1
-            in = [in; 1]; % only one augmentation for 1st layer
-        else
-            in = [tanh(in); 1];
-        end
-
-        % forward
-        in = V'*in;
-        
-        % save to gradient tape
-        if l_idx~=opt.l_size-1
-            nn.tape(pt_tape: pt_tape+m-1) = in;
-        end
-
-        % pointer to next
-        pt_V = pt_V + (n*m);
-        pt_tape = pt_tape + m;
-    end
-
-    %% ERROR CHECK
-    assert(pt_V-1 == opt.th_size);
-%     assert(pt_tape-1 == opt.t_size);
-
-    %% TERMINATION
-    out = in;    
-
-end

### 2025-04-11 src/script_simulation/controllers/NAC-Aux/utils/nnGradient.m

@@ -1,58 +1,0 @@
-function total_grad = nnGradient(nn, nnOpt)
-
-    %% PRE-ALLOCATION
-    total_grad = zeros(nnOpt.NN_size(end), nnOpt.th_size);
-    
-    %% 
-    pt_V = nnOpt.th_size;
-    pt_tape = nnOpt.tp_size;
-
-    grad_to_back = 1;
-
-    %% BACKWARD (TOTAL NN GRDIENT CALCULATION)
-    for l_idx = flip(2:1:nnOpt.l_size)
-        l2 = nnOpt.NN_size(l_idx);        
-        l1 = nnOpt.NN_size(l_idx-1);        
-        
-        % pre_Phi
-        Phi = nn.tape(pt_tape-l1+1: pt_tape);
-        aug_phi = [tanh(Phi); 1];
-
-        % (I \otimes phi_k^T)
-        grad = kron(eye(l2), aug_phi');
-        if l_idx ~= nnOpt.l_size
-            n = l2+1; m = nnOpt.NN_size(l_idx+1);
-            % get phi_dot
-            phi_dot = tanh_dot(pre_Phi);
-            % get V weight
-            V = reshape(nn.th(pt_V-(n*m)+1: pt_V), n,m);
-            grad_to_back = grad_to_back * V'*phi_dot;
-
-            % pointer to next
-            pt_V = pt_V - (n*m);
-        end
-        grad = grad_to_back*grad;
-
-        % save to total grad
-        total_grad(:, pt_V-((l1+1)*l2)+1: pt_V) = grad;
-
-        % pointer to next
-        pt_tape = pt_tape - l1;
-
-        % for efficiency
-        pre_Phi = Phi;
-
-    end
-
-    %% ERROR CHECK
-    assert(pt_V == (nnOpt.NN_size(1)+1)*nnOpt.NN_size(2));
-    assert(pt_tape == 0);
-end
-
-%% LOCAL FUNCTIONS
-function phi_dot = tanh_dot(Phi)
-    phi_dot = zeros(length(Phi)+1, length(Phi));
-    for idx = 1:1:length(Phi)
-        phi_dot(idx,idx) = 1-tanh(Phi(idx))^2;
-    end
-end

### 2025-04-11 src/script_simulation/controllers/NAC-Aux/utils/nnWeightNorm.m

@@ -1,13 +1,0 @@
-function Vn = nnWeightNorm(th, nnOpt)
-
-    Vn = zeros(nnOpt.l_size-1,1);
-
-    cumsum_V = [0;cumsum(nnOpt.th_size_list)];
-    for l_idx = 1:1:nnOpt.l_size-1
-        start_pt = cumsum_V(l_idx)+1;
-        end_pt = cumsum_V(l_idx+1);   
-
-        Vn(l_idx) = norm(th(start_pt: end_pt));
-    end
-    
-end

### 2025-04-11 src/script_simulation/controllers/loadGlobalOpts.m

@@ -2,30 +2,30 @@ function opt = loadGlobalOpts(dt, CONTROL_NUM)
     opt.dt = dt;
 
     opt.e_tol = 0e-3;
-    opt.init_range = 1e-5;
+    opt.init_range = 1e-1;
     
-    opt.Lambda = diag([1 1]) * 5e0;
+    opt.Lambda = diag([5 15]) * 1;
 
-    opt.alpha = 1.5;
+    opt.alpha = .5;
     opt.rho = opt.alpha*0e-2;
     opt.NN_size = [6,4,4,2];
-    opt.W = 1;
+    opt.W = diag([1 1]);
     opt.e_size = 2;
 
     opt.cstr.th_max = [11;12;13] * 1e0;
-    opt.cstr.u_ball = 7;
-    opt.cstr.uMax1 = 7;
+    opt.cstr.u_ball = 10;
+    opt.cstr.uMax1 = 9.682;
     opt.cstr.uMax2 = 2.5;
 
     if CONTROL_NUM == 1
         % opt.beta = [1 1 1] * 1e-1;
         opt.beta(1:3) = [1 1 1] * 1e-3;
-        opt.beta(4) = 1e2; % control ipnut ball
-        opt.beta(5) = 0e2; % control ipnut 1 Max
-        opt.beta(6) = 0e4; % control ipnut 2 Max
-        opt.beta(7) = opt.beta(5); % control ipnut 1 Min
-        opt.beta(8) = opt.beta(6); % control ipnut 2 Min
-        opt.beta = opt.beta/opt.alpha;
+        opt.beta(4) = 1e0; % control input ball
+        opt.beta(5) = 0e2; % control input 1 Max
+        opt.beta(6) = 10e1; % control input 2 Max
+        opt.beta(7) = opt.beta(5); % control input 1 Min
+        opt.beta(8) = opt.beta(6); % control input 2 Min
+        % opt.beta = opt.beta/opt.alpha;
 
         c_num = length(opt.beta);
         opt.lbd = zeros(c_num,1);

### 2025-04-11 src/script_simulation/main_TNNLS.m

@@ -1,165 +1,0 @@
-%% INITIALIZATION
-clear  
-clc
-
-addpath("models");
-
-fprintf("                                   \n");
-fprintf("***********************************\n");
-fprintf("*    Optimization based NN Ctrl   *\n");
-fprintf("***********************************\n");
-
-FIGURE_PLOT_FLAG    = 1;
-ANIMATION_FLAG      = 0;
-AINMATION_SAVE_FLAG = 0;
-FIGURE_SAVE_FLAG    = 0;
-RESULT_SAVE_FLAG    = 0;
-CONTROL_NUM = 1;    % 1: CoNAC, 2: Aux.
-
-% seed = 18; rng(seed);
-
-%% SIMULATION SETTING
-ctrl_dt = 1/250;
-dt = 1/1000;
-% dt = ctrl_dt * 1/10;
-T = 30;
-t = 0:dt:T;
-rpt_dt = 1;
-
-%% SYSTEM DECLARE
-grad_x = model1_load();
-% [xd1_f, xd2_f] = ref1_load(); % sin func
-r_func = ref4_load(); 
-
-% x1 = [0;0];  
-x1 = [deg2rad(-90);0];  
-x2 = [0;0];
-u = [0;0];
-
-%% CONTROLLER LOAD
-%  TODO: design more controllers
-if CONTROL_NUM == 1    % CoNAC
-    ctrl_path = "CoNAC";
-elseif CONTROL_NUM == 2 % Aux.
-    ctrl_path = "Aux";
-end
-
-addpath("controllers/"+ctrl_path);
-addpath(genpath('controllers/'+ctrl_path));
-
-% opt = loadOpts(ctrl_dt);
-addpath("controllers");
-opt = loadGlobalOpts(ctrl_dt, CONTROL_NUM);
-
-initControl;
-
-%% RECORDER INITIALIZATION
-addpath("recorder");
-recInit;
-
-%% MAIN SIMULATION
-% ********************************************************
-fprintf("[INFO] Simulation Start\n");
-
-for t_idx = 2:1:num_t
-    [xd1,xd2] = r_func(t(t_idx));
-    
-    e1 = x1 - xd1;
-    e2 = x2 - xd2;
-
-    r = e2 + opt.Lambda * e1;
-
-    if t_idx==2 || rem(t(t_idx)/dt, ctrl_dt/dt) == 0
-        preControl
-        postControl
-    end
-
-    % control input saturation
-    u_sat = sat(u, opt, CONTROL_NUM);
-
[…]

### 2025-04-11 src/script_simulation/main_plotter.m

@@ -1,7 +1,7 @@
 clear
 
 %%
-SAVE_FLAG = 0;
+SAVE_FLAG = 1;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
 gray = "#808080";
 
@@ -9,12 +9,14 @@ more_blue = "#0072BD";
 more_red = "#A2142F";
 
 %% 
-ctrl1_name = "3-Apr-2025_17-38-31"; % CoNAC
-ctrl2_name = "3-Apr-2025_17-38-57"; % Aux.
+ctrl1_name = "11-Apr-2025_15-56-43"; % CoNAC
+ctrl2_name = "11-Apr-2025_15-57-02"; % Aux.
+ctrl3_name = "11-Apr-2025_15-57-25"; % CoNAC 2.
 
 %%
 ctrl1_log = load("sim_result/"+ctrl1_name+".mat");
 ctrl2_log = load("sim_result/"+ctrl2_name+".mat");
+ctrl3_log = load("sim_result/"+ctrl3_name+".mat");
 
 %% RESULT PLOTTER
 T = ctrl1_log.T;
@@ -22,6 +24,7 @@ t = ctrl1_log.t;
 obs_t = 1:length(t);
 opt1 = ctrl1_log.opt;
 opt2 = ctrl2_log.opt;
+opt3 = ctrl3_log.opt;
 
 c1_x1 = ctrl1_log.x1_hist;
 c1_x2 = ctrl1_log.x2_hist;
@@ -38,9 +41,18 @@ c2_xd1 = ctrl2_log.xd1_hist;
 c2_xd2 = ctrl2_log.xd2_hist;
 c2_u = ctrl2_log.u_hist;
 c2_uSat = ctrl2_log.uSat_hist;
-c2_lbd = ctrl2_log.lbd_hist;
+% c2_lbd = ctrl2_log.lbd_hist;
 c2_zeta = ctrl2_log.zeta_hist;
 c2_th = ctrl2_log.th_hist;
+
+c3_x1 = ctrl3_log.x1_hist;
+c3_x2 = ctrl3_log.x2_hist;
+c3_xd1 = ctrl3_log.xd1_hist;
+c3_xd2 = ctrl3_log.xd2_hist;
+c3_u = ctrl3_log.u_hist;
+c3_uSat = ctrl3_log.uSat_hist;
+c3_lbd = ctrl3_log.lbd_hist;
+c3_th = ctrl3_log.th_hist;
 
[…]

### 2025-04-11 src/script_simulation/models/model1.m

@@ -5,7 +5,8 @@ function [M, C, G, F, J] = model1(q, u, t)
 % ********************************************************
 
 m1 = 2.465;             % [kg]
-m2 = 1.093;
+m2 = 2.465;             % [kg]
+% m2 = 1.093;
 L1 = .2;             % [m]
 L2 = .15+.01+.02;
 Lc1 = .13888;             % [m]
@@ -22,12 +23,12 @@ g = 9.81;             % [m/s^2]
 % fc1 = 7.17;             % [Nm]
 % fc2 = 1.734;
 
-b1 = .2;
+b1 = .1;
 b2 = .1;
-fc1 = .35;
-fc2 = .2;
-fs1 = .7;
-fs2 = .4;
+fc1 = .24;
+fc2 = .24;
+fs1 = .3;
+fs2 = .3;
 
 I1 = .06911;
 I2 = .01532;
@@ -78,17 +79,49 @@ Jmat12 = (-1).*L2.*sin(q1+q2);
 Jmat21 = L1.*cos(q1)+L2.*cos(q1+q2); 
 Jmat22 = L2.*cos(q1+q2);
 
-if abs(u(1)) > fs1
-    Fmat1=b1*sign(qd1)+fc1*qd1;
+f_thr = 1e-3;
+
+Fc1 = fc1*qd1;
+Fc2 = fc2*qd2;
+
+
+
+if abs(qd1) < f_thr 
+    if abs(u(1)) < fs1
+        Fmat1 = u(1)-Gmat1;
+    else
+        if u(1)-Gmat1 >= 0
+            Fmat1 = b1*qd1+fc1;
+        else
+            Fmat1 = b1*qd1-fc1;
+        end
+    end
 else
-    Fmat1 = u(1)-Gmat1;
+    if qd1 >=0 
+        Fmat1 = fc1 + b1*qd1;
+    elseif q(3) < 0
+        Fmat1 = -fc1 + b1*qd1;
+    end
 end
 
-if abs(u(2)) > fs2
-    Fmat2=b2*sign(qd2)+fc2*qd2;
+if abs(qd2) < f_thr 
+    if abs(u(2)) < fs2
+        Fmat2 = u(2)-Gmat2;
+    else
+        if u(2)-Gmat2 >= 0
+            Fmat2 = b2*qd2+fc2;
+        else
+            Fmat2 = b2*qd2-fc2;
+        end
+    end
 else
[…]

### 2025-04-11 src/script_simulation/models/ref4_load.m

@@ -1,23 +1,42 @@
 function r_func = ref4_load()
 
-r_func = @(t) ref_gen(t);
+r_func = @(t) epi_gen(t);
 
 end
 
-function [r1,r2] = ref_gen(t)
-    x0 = deg2rad([-90;0]);  
-    xd1 = deg2rad([0;90]);
-    xd2 = deg2rad([135;-135]);
-    T = 2;    
+function [r1, r2] = epi_gen(t)
+    T = 3; % traj. duration
+    POINT_NUM = 4; % number of points in one cycle
+    CYCLE_TIME = T*POINT_NUM;
+    CYCLE_NUM = 3;
+    EPI_T = CYCLE_TIME*CYCLE_NUM;
 
-    t = mod(t, 3*T);
+
+    cycle = floor(t/CYCLE_TIME)+1;
+
+    t = mod(t, CYCLE_TIME);
+
+    x0 = deg2rad([-90;0]);  
+    xd1 = deg2rad([45;-135]);
+    xd2 = deg2rad([-45;45]);
+    % xd3 = deg2rad([-50;-145]);
+    xd3 = xd1;
+
+    [r1,r2] = ref_gen(t, T, x0, xd1, xd2, xd3);
+end
+
+function [r1,r2] = ref_gen(t, T, x0, xd1, xd2, xd3)
+
+    t = mod(t, 4*T);
 
     if t < T
         [r1,r2] = poly_filter(x0, xd1, T, t);
     elseif t < 2*T
         [r1,r2] = poly_filter(xd1, xd2, T, (t-T));
+    elseif t < 3*T
+        [r1,r2] = poly_filter(xd2, xd3, T, (t-2*T));
     else
-        [r1,r2] = poly_filter(xd2, x0, T, (t-2*T));
+        [r1,r2] = poly_filter(xd3, x0, T, (t-3*T));
     end
 end
 

### 2025-04-11 src/script_simulation/models/sat.m

@@ -1,5 +1,5 @@
 function u = sat(u, opt, CONTROL_NUM)
-    u = u; return;
+    % u = u; return;
     u_ball = opt.cstr.u_ball;
     uMax1 = opt.cstr.uMax1;
     uMax2 = opt.cstr.uMax2;
@@ -8,14 +8,14 @@ function u = sat(u, opt, CONTROL_NUM)
         u = u/norm(u)*u_ball;
     end
 
-    % if CONTROL_NUM == 1 && (u(2) > uMax2 || u(2) < -uMax2)
-    %     uMax2 = uMax2*sign(u(2));
-    %     u(1) = uMax2*u(1)/u(2);
-    %     u(2) = uMax2;
-    % end
-    if u(1) > uMax1 || u(1) < -uMax1
-        uMax1 = uMax1*sign(u(1));
-        u(2) = uMax1*u(2)/u(1);
-        u(1) = uMax1;
+    if (u(2) > uMax2 || u(2) < -uMax2)
+        uMax2 = uMax2*sign(u(2));
+        u(1) = uMax2*u(1)/u(2);
+        u(2) = uMax2;
     end
+    % if u(1) > uMax1 || u(1) < -uMax1
+    %     uMax1 = uMax1*sign(u(1));
+    %     u(2) = uMax1*u(2)/u(1);
+    %     u(1) = uMax1;
+    % end
 end

### 2025-04-11 src/script_simulation/plot_idv.m

@@ -1,0 +1,253 @@
+
+%% RESULT PLOTTER
+t1 = data.t;
+T = data.T;
+obs_t1 = 1:length(t1);
+
+start_time = 31.4;
+end_time = 32.4;
+
+obs_t1_1 = find(t1 >= start_time & t1 <= end_time);
+
+c1_x1 =     data.x1_hist;
+c1_x2 =     data.x2_hist;
+c1_xd1 =    data.xd1_hist;
+c1_xd2 =    data.xd2_hist;
+c1_u =      data.u_hist;
+c1_uSat =   data.uSat_hist;
+c1_th =     data.th_hist;
+if CONTROL_NUM == 1
+    c1_lbd =    data.lbd_hist;
+elseif CONTROL_NUM == 2
+    c1_zeta =   data.zeta_hist;
+end
+
+%%
+if FIGURE_PLOT_FLAG
+% ============================================
+%     Fig. 1: Current d-axis (Ref vs Obs)
+% ============================================
+figure(1); clf;
+hF = gcf; 
+hF.Position(3:4) = [fig_width, fig_height];
+
+plot(t1(obs_t1), c1_x1(1,obs_t1), "Color", "blue", "LineWidth", line_width, "LineStyle", "-"); hold on
+plot(t1(obs_t1), c1_xd1(1,obs_t1), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
+
+grid on; grid minor;
+xlabel('Time / s', 'FontSize', font_size, 'Interpreter', 'latex');
+ylabel('$q_1$ / rad', 'FontSize', font_size, 'Interpreter', 'latex');
+% maxVal = max(id_ref.Data); minVal = min(id_ref.Data); 
+maxVal = 2; minVal = -2; 
+len = maxVal-minVal; ratio = .3;
+ylim([minVal-len*ratio maxVal+len*ratio]);
+xlim([0 T])
+    ax = gca;
+    ax.FontSize = font_size; 
+    ax.FontName = 'Times New Roman';
+
+% ============================================
+%     Fig. 2: Current q-axis (Ref vs Obs)
+% ============================================
+figure(2); clf;
+hF = gcf; 
+hF.Position(3:4) = [fig_width, fig_height];
+
+plot(t1(obs_t1), c1_x1(2,obs_t1), "Color", "blue", "LineWidth", line_width, "LineStyle", "-"); hold on
[…]

### 2025-04-11 src/script_simulation/simulate.m

@@ -1,272 +1,0 @@
-%% REPORTY SIMULATION
-fprintf("                                   \n");
-fprintf("***********************************\n");
-fprintf("*    Optimization based NN Ctrl   *\n");
-fprintf("***********************************\n");
-
-fprintf("                                 \n");
-fprintf(" Controller:\n");
-fprintf("     "+string(c_idx)+"\n");
-fprintf("\n");
-fprintf(" FLAGs\n");
-fprintf("     animation      : "+string(ANIMATION_FLAG)+"\n");
-fprintf("     animation save : "+string(AINMATION_SAVE_FLAG)+"\n");
-fprintf("     figure save    : "+string(FIGURE_SAVE_FLAG)+"\n");
-fprintf("     result save    : "+string(RESULT_SAVE_FLAG)+"\n");
-fprintf("\n");
-
-%% SYSTEM DECLARE
-[grad_x, IC] = model1_load();
-[r_f, rd_f, rdd_f] = ref1_load(); % sin func
-% [r_f, rd_f, rdd_f] = ref2_load(); % step func
-
-%% INITIAL CONDITION
-x = IC.x;
-u = IC.u;
-r1 = r_f(x, 0);
-r2 = rd_f(x, 0);
-
-%% RECORDER
-num_x = length(x); num_u = length(u);
-num_t = length(t);
-
-x_hist = zeros(num_x, num_t); x_hist(:, 1) = x;
-r_hist = zeros(num_x/2, num_t); r_hist(:, 1) = r1;
-rd_hist = zeros(num_x/2, num_t); rd_hist(:, 1) = r2;
-u_hist = zeros(num_u, num_t); u_hist(:, 1) = u;
-uSat_hist = zeros(num_u, num_t); uSat_hist(:, 1) = u;
-L_hist = zeros(length(nnOpt.beta), num_t); L_hist(:,1) = zeros(length(nnOpt.beta),1);
-dot_L_hist = zeros(1, num_t); dot_L_hist(:,1) = 0;
-V_hist = zeros(nnOpt.l_size-1, num_t); V_hist(:, 1) = nn_V_norm_cal(nn.V, nnOpt);
-aux_hist = zeros(num_x/2, num_t);
-
-comp_control_hist = zeros(1, num_t);
-comp_train_hist = zeros(1, num_t);
-
-%% MAIN SIMULATION
[…]

### 2025-04-11 manuscript.tex
update sim result and new figures; and new ref. points

@@
         \min_{\estwth} \ J(\fe;\estwth):= 
-        \tfrac{1}{2} \fe^\top \fe₩
+        \tfrac{1}{2} \fe^\top \fe
         \\ \\
@@
 % ------------------------------------
+% Robot Model Figure and Table
+% ------------------------------------
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.75\linewidth]{fig/RobotModel.drawio.png}
+    \caption{Two-link manipulator model.}
+    \label{fig: manipulator}
+\end{figure}
+
+\begin{table}[t]
+    \renewcommand{\arraystretch}{1.3}
+    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
+    \centering
+    \begin{tabular}{c m{6.5em} c c c }
+    % \begin{tabular}{c c c c c}
+    \hline
+    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+    \hline
+    \hline 
+    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
+    \hline
+    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
+    \hline
+    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
+    \hline
+    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
+    \hline
+    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
+    \hline
+    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
+    \hline
+    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
+    \hline
+    \end{tabular}
+    \label{table:system:params}
+\end{table}
+
+% ------------------------------------
 % Reference Trajectory
@@
 \end{equation}
-where ${\qd}_0=[0,0]^\top$, ${\qd}_1=[\tfrac{5}{8}\pi,-\tfrac{3}{8}\pi]^\top$, ${\qd}_2=[\tfrac{5}{4}\pi/2,-\tfrac{3}{4}\pi]^\top$, and $t_f=4$ s.
-
-However, since the NN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
-Hence, the reference trajectory was applied 3 times by proportionally increasing the amplitude of the desired trajectory to the original ${\qd}_i,\ \forall i\in\{1,2\}$.
-Let us call the $i\textsuperscript{th}$ iteration of the reference trajectory as Episode $i,\ \forall i\in[1,2,3]$.
+where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{5}{4}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
+To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.
+
+% However, since the NN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
+% Hence, the reference trajectory was applied $2$ times by proportionally increasing the amplitude of the desired trajectory to the original ${\qd}_i,\ \forall i\in\{1,2\}$.
+% Let us call the $i\textsuperscript{th}$ iteration of the reference trajectory as Episode $i,\ \forall i\in\{1,2\}$.
 
@@
 %
-These domains \ref{eq:sat:norm} and \ref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator.
+These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator.
 
@@
     }
-    \caption{Saturation function.}
+    \caption{Control input saturation function.}
     \label{fig:sat}
@@
 
-% ------------------------------------
-% Robot Model Figure and Table
-% ------------------------------------
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.75\linewidth]{fig/RobotModel.drawio.png}
-    \caption{Two-link manipulator model.}
-    \label{fig: manipulator}
-\end{figure}
-
-\begin{table}[t]
-    \renewcommand{\arraystretch}{1.3}
-    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
-    \centering
-    \begin{tabular}{c m{6.5em} c c c }
-    % \begin{tabular}{c c c c c}
-    \hline
-    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
-    \hline
-    \hline 
-    $m_p$ & Mass & 2.465 (kg) & 1.093 (kg) \\
-    \hline
-    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
-    \hline
-    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
-    \hline
-    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
-    \hline
-    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.16 (Nm) \\
-    \hline
-    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
-    \hline
-    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
-    \hline
-    \end{tabular}
-    \label{table:system:params}
-\end{table}
+\hfill
 
@@
 % ------------------------------------
-For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=[\q^\top,\dq^\top,\fe^\top,1]^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
 The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
-Each NN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=1$.
-The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,5])$.
+Each NN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
+The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
 The sampling rate of the controller was $250$ Hz, and $1000$ Hz for the simulation.
 To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.
+The readers are referred to the other papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to handle the weight constraints.
 
@@
     \hline
-        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
-    \hline
-        (C$_2$) & aux. sys. & $\overline{\tau_1}=-\underline{\tau_1}=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
-    \hline
-        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
+        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
+    \hline
+        (C$_2$) & aux. sys. & $\overline{\tau}_1=-\underline{\tau}_1=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
+    \hline
+        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
     \hline
@@
       \label{fig:ctrl:result:q1}}
-    % \vfill
+    \hfill
     \subfloat[Tracking result of $q_2$.]{
@@
         \label{fig:ctrl:result:tau:1}}
-    % \vfill
+    \hfill
       \subfloat[Control input $\tau_2$.]{
@@
         }%
-        \label{fig:ctrl:result:opt:norm}}
+        \label{fig:ctrl:result:tau:norm}}
+    \hfill
     \subfloat[Norm of weights $\hat\theta_i$.]{
@@
         }%
-        \label{fig:ctrl:result:opt:multiplier}}        
+        \label{fig:ctrl:result:weight}}        
     \caption{
-  Simulation results of the CoNAC (blue) and CoNAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
+  Simulation results of the (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
   }
@@
         }%
-        \label{fig:ctrl:result:scope:opt:zeta}}
+        \label{fig:ctrl:result:scope:control}}
         \vfill
@@
         }%
-        \label{fig:ctrl:result:scope:control}}
+        \label{fig:ctrl:result:scope:beta}}
         \vfill
@@
 	\caption{
-		The effect of Lagrange multiplier $\lambda_{\theta_i}$ on the adaptation direction of $\widehat{ \mv{\theta}}_i$.
-		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively (i.e., $\lambda_{\theta_1}' > \lambda_{\theta_1}''$).
+		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_1$.
+		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively (i.e., $\lambda_{j}' > \lambda_{j}''$).
 	}
@@
 
-The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is shown in Table~\ref{tab:sim:L2}.
+The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
+Across the two episodes, all controllers enhanced their tracking performances about 
+82.7 \% for (C$_1$), 78.5 \% for (C$_2$), and 81.8 \% for (C$_3$) in $L_2$ norm of $r_1$, and 66.8 \% for (C$_1$), 62.5 \% for (C$_2$), and 59.6 \% for (C$_3$) in $L_2$ norm of $r_2$, respectively, by adapting their weights.
+Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were reduced in the second episode, as well.
+
+The tracking performance of (C$_1$) outperformed (C$_2$) and (C$_3$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
+This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was not able to use the full capability of the actuator due to the limitation of the auxiliary system and (C$_3$) occurred oscillations in constraint handling.
 
@@
 % ------------------------------------
-\subsubsection{Input Constraint Handling}
+\subsubsection{Constraint Handling} \label{sec:sim:constraint}
+
+In this section, the constraint handling capability of all controllers are investigated.
+First, the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$ were not violated, as shown in Fig.~\ref{fig:ctrl:result:weight}, since the limits $\overline{\theta}_i,\ \forall i\in\{0,1,2\}$ were set sufficiently large.
+
+In Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers satisfied the control input saturation illustrated in Fig.~\ref{fig:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$) and (C$_3$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_2$), as the weights were adapted to reduce the constraint violations.
+It is notable that the control input constraints were frequently active, since the controllers were implemented in discrete time with a sampling rate of $250$ Hz.
+
+Even though all controllers satisfied the input saturation, (C$_2$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $19$ s to $20$ s.
+This is because, as aforementioned, the auxiliary system only considers the input bound constraint, and the control input bound constraint for first link was imposed to approximately match the maximum allowable norm of the control input $\overline\tau$.
+In contrast, (C$_1$) and (C$_3$) were able to use the full capability of the actuator.
+
+\hfill
+
+% zeta
+The detail of the constraint handling is now investigated.
+First, for (C$_2$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. 
+As the weights were adapted to reduce not only $\fe$ but also $\mv{\zeta}$, the constraint violation of $c_{\overline\tau_1}$ was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
+After the constraint was satisfied, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1}$.
+
+% beta + zeta
+For (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ adjusted the adaptation direction of the weights $\widehat{ \mv{\theta}}_1$ to reduce the constraint violations, as the $\lambda_j$ increased by the constraint violations.
+% comparison; big, small beta
+For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
+With the bigger $\lambda_j$, the adaptation of $\widehat{ \mv{\theta}}_1$ is more assertive than that with smaller $\lambda_j$.
+This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but the oscillations of the violations.
+In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_j$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_j,\ \forall j\in\mathcal I$ was satisfied and violated, respectively, in the discrete time implementation.
+Besides, with small $\lambda_j$, the adaptation direction of $\widehat{ \mv{\theta}}_1$ is more conservative, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
+This allows the controller to show a smoother control input.
+However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt with respect to the filtered error $\fe$.
 
@@
 \color{red}
-The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two Dynamixel MX-28 servos.
+The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
 The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
@@
 
-The tracking result of the real-time experiment is shown in Fig.~\ref{fig:ctrl:result:exp}.
-
-is shown in Fig.~\ref{fig:ctrl:result:cmp:time}. The computational time of CoNAC was 0.5 ms, which is less than the sampling time of 4 ms. 
+The tracking result of the real-time experiment is shown in Fig.~\ref{fig:ctrl:real:result}.
+
+is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CoNAC was 0.5 ms, which is less than the sampling time of 4 ms. 
 This indicates that the proposed CoNAC can be implemented in real-time applications.
@@
         {
-          src/measurement/figures/Fig1.eps
+            src/script_simulation/figures/compare/Fig1.eps
         }%
@@
         {
-          src/measurement/figures/Fig2.eps
+            src/script_simulation/figures/compare/Fig2.eps
         }%
@@
           {
-            src/measurement/figures/Fig3.eps
+            src/script_simulation/figures/compare/Fig3.eps
           }%
@@
           {
-            src/measurement/figures/Fig4.eps
+            src/script_simulation/figures/compare/Fig4.eps
           }%
@@
           {
-          src/measurement/figures/Fig5.eps
+            src/script_simulation/figures/compare/Fig5.eps
           }%
@@
           {
-          src/measurement/figures/Fig6.eps
+            src/script_simulation/figures/compare/Fig6.eps
           }%
@@
           {
-              src/measurement/figures/Fig8.eps
+            src/script_simulation/figures/compare/Fig7.eps
           }%
@@
           {
-              src/measurement/figures/Fig9.eps
+            src/script_simulation/figures/compare/Fig8.eps
           }%
@@
         {
-          src/measurement/figures/Fig10.eps
+            src/script_simulation/figures/compare/Fig9.eps
         }%
@@
 
-This paper presented a constrained optimization-\allowbreak based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
 The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.

### 2025-04-11 src/script_simulation/controllers/loadGlobalOpts.m

@@ -20,9 +20,9 @@ function opt = loadGlobalOpts(dt, CONTROL_NUM)
     if CONTROL_NUM == 1
         % opt.beta = [1 1 1] * 1e-1;
         opt.beta(1:3) = [1 1 1] * 1e-3;
-        opt.beta(4) = 1e0; % control input ball
+        opt.beta(4) = 1e1; % control input ball
         opt.beta(5) = 0e2; % control input 1 Max
-        opt.beta(6) = 10e1; % control input 2 Max
+        opt.beta(6) = 1e3; % control input 2 Max
         opt.beta(7) = opt.beta(5); % control input 1 Min
         opt.beta(8) = opt.beta(6); % control input 2 Min
         % opt.beta = opt.beta/opt.alpha;

### 2025-04-11 src/script_simulation/main.m

@@ -13,7 +13,7 @@ FIGURE_PLOT_FLAG    = 1;
 ANIMATION_FLAG      = 0;
 AINMATION_SAVE_FLAG = 0; 
 FIGURE_SAVE_FLAG    = 0;
-RESULT_SAVE_FLAG    = 1;
+RESULT_SAVE_FLAG    = 0;
 CONTROL_NUM         = 1;    % 1: CoNAC, 2: Aux.
 
 seed = 18; rng(seed);

### 2025-04-11 src/script_simulation/main_plotter.m

@@ -9,9 +9,13 @@ more_blue = "#0072BD";
 more_red = "#A2142F";
 
 %% 
-ctrl1_name = "11-Apr-2025_15-56-43"; % CoNAC
-ctrl2_name = "11-Apr-2025_15-57-02"; % Aux.
-ctrl3_name = "11-Apr-2025_15-57-25"; % CoNAC 2.
+ctrl1_name = "12-Apr-2025_00-22-05"; % CoNAC
+ctrl2_name = "12-Apr-2025_00-22-27"; % Aux.
+ctrl3_name = "12-Apr-2025_00-22-18"; % CoNAC 2.
+
+% ctrl1_name = "11-Apr-2025_15-56-43"; % CoNAC
+% ctrl2_name = "11-Apr-2025_15-57-02"; % Aux.
+% ctrl3_name = "11-Apr-2025_15-57-25"; % CoNAC 2.
 
 %%
 ctrl1_log = load("sim_result/"+ctrl1_name+".mat");
@@ -62,6 +66,10 @@ th_max = opt1.cstr.th_max;
 %%
 ep_time = 12;
 
+start_t = 19;
+end_t = 21;
+ctrl_obs_idx = find(t >= start_t & t <= end_t);
+
 % font_size = 16;
 % line_width = 2;
 % lgd_size = 12;
@@ -69,11 +77,11 @@ ep_time = 12;
 % fig_height = 210 * 1; 
 % fig_width = 450 * 1;
 
-font_size = 20;
+font_size = 18;
 line_width = 1.5;
 lgd_size = 16;
     
-fig_height = 230 * 1; 
+fig_height = 200 * 1; 
 fig_width = 800 * 1;
 %% FIG. 1; STATE 1
 figure(1); clf;
@@ -81,8 +89,8 @@ hF = gcf;
 hF.Position(3:4) = [fig_width, fig_height];
 
 plot([ep_time ep_time], [-5e1 5e1], "Color", "black", "LineWidth", line_width, "LineStyle", "-."); hold on
-text(.2, -2, "Episode 1", "FontSize", font_size, "FontName", 'Times New Roman')
-text(ep_time+.2, -2, "Episode 2", "FontSize", font_size, "FontName", 'Times New Roman')
+text(.2, -1.8, "Episode 1", "FontSize", font_size, "FontName", 'Times New Roman')
+text(ep_time+.2, -1.8, "Episode 2", "FontSize", font_size, "FontName", 'Times New Roman')
 
[…]

### 2025-04-11 src/script_simulation/models/ref4_load.m

@@ -15,9 +15,9 @@ function [r1, r2] = epi_gen(t)
     cycle = floor(t/CYCLE_TIME)+1;
 
     t = mod(t, CYCLE_TIME);
-
+2.1
     x0 = deg2rad([-90;0]);  
-    xd1 = deg2rad([45;-135]);
+    xd1 = deg2rad([45;-90]);
     xd2 = deg2rad([-45;45]);
     % xd3 = deg2rad([-50;-145]);
     xd3 = xd1;

### 2025-04-12 manuscript.tex
finalize sim reulst

@@
     \item $\lambda_{\min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
-    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
+    \item $\mm I_n$ denotes the $n\times n$ identity matrix, and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
 \end{itemize}
@@
 However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
+\MSRY{여기서는 MVT, IFT을 사용하지 않았기 때문에 아이디얼 제어가 포화되지 않을 필요성이 없다. 실험에서도 포화를 핸들링하는 중에 추종이 완벽히 되지 못하는 것을 보인다.}
 
@@
 
-The proposed CoNAC was validated via numerical simulations and real-time experiments on a two-link manipulator.
+The proposed CoNAC was validated via numerical simulation and real-time experiment on a two-link manipulator.
 
@@
 % ------------------------------------
-The proposed CoNAC was implemented using the OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency.
-The two-link manipulator model is depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
+The two-link manipulator model is depicted in Fig.~\ref{fig:robot:model}, adapted from \cite{Markus:2013aa}. 
 \MSRY{CORRECT HERE}
@@
     \centering
-    \includegraphics[width=0.75\linewidth]{fig/RobotModel.drawio.png}
-    \caption{Two-link manipulator model.}
-    \label{fig: manipulator}
+    \subfloat[Two-link manipulator model.]{
+        \includegraphics[width=0.75\linewidth]{src/figures/RobotModel.drawio.pdf}
+        \label{fig:robot:model}
+    }
+    \hfill
+    \subfloat[Control input saturation function.\MSRY{sat이 아니라 집합으로 표현하기}]{
+        \includegraphics[width=0.45\linewidth]{src/figures/saturation.drawio.pdf}
+        \label{fig:robot:sat}
+    }
+    \caption{Two-link manipulator model and control saturation function.}
+    \label{fig:robot}
 \end{figure}
 
+% ------------------------------------
+% Robot Model Parameters
+% -----------------------------------
 \begin{table}[t]
@@
 \end{equation}
-where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{5}{4}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
+where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
 To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.
@@
 % ------------------------------------
-To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to satisfy the following domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:sat}, where
+To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
 %
@@
 %
-These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.45\linewidth]{
-        src/figures/saturation.drawio.pdf
-    }
-    \caption{Control input saturation function.}
-    \label{fig:sat}
-\end{figure}
+These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
 
@@
 % ------------------------------------
-% Controllers
-% ------------------------------------
-For a comparative study, we implemented 3 controllers:
+% Comparative Study
+% ------------------------------------
+For a comparative study, we implemented 3 controllers.
+The properties of the controllers are summarized in Table~\ref{table:controllers}.
 
@@
 % ------------------------------------
-\subsubsection*{Controller 1: (C$_1$) proposed}
+\subsubsection*{Controller 1: (C$_1$) CoNAC; proposed}
 
@@
 \begin{equation}
-    \begin{aligned}
     c_{\overline\tau_2}     
-        =&
+    =
     \tau_2-\overline\tau_2
@@
     ,
-        \quad
+    \;
     c_{\underline\tau_2} 
-        =&
+    =
     \underline\tau_2-\tau_2
@@
     ,
-        \quad
+    \;
     c_{\rbu}
-        =&
+    =
     \tfrac{1}{2}
@@
     )^2 
-        ,
-    \end{aligned}
+    <0
+    ,
     \label{eq:sim:cstr:CoNAC}
 \end{equation}
-where $\overline\tau_2=2.5$ and $\underline\tau_2=-2.5$ are the upper and lower bounds of the second link actuator, respectively, and $\overline\tau=10$ is the maximum allowable norm of the control input.
+where $\overline\tau_2=-\underline{\tau}_2=2.5$ are the absolute bound of the second link actuator, and $\overline\tau=10$ is the maximum feasible norm of the control input.
 Hence, (C$_1$) is possible to use full capability of the actuator.
 The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
-As described in \eqref{eq:control:est}, the control input is equal to the output of the NN $\rbu$, and the adaptation law is defined in \eqref{eq:adaptation law}.
+As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.
+
+The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.
 
@@
 On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
-The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$ and $\mm{B}_\zeta\in\R^{n\times n}$, and $\Delta\tau_{1} =
-\tau_{1}-\max(\underline\tau_1,\min(\overline\tau_1,\tau_1))$.
-Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$.
-
-The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
+The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
+The auxiliary state $\mv{\zeta}$ is affected by the saturated control input $\Delta\rbu$, whose entry is defined as $\Delta\tau_{i} = 
+\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
+Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$).
+
+The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
 Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.
 
+The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
+\MSRY{sensitivity와 convergence에 대해서 더 설명이 필요한가?}
+
 % ------------------------------------
@@
 
-To investigate the effect of the update rate of Lagrange multipliers, C$_3$ was implemented with small $\beta_i$ values.
+To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=1$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.
+The remaining parameters are the same as (C$_1$).
 
@@
 For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
-The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$.
-Each NN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
+The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
+Each NN architecture had two hidden layers with four nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
 The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
-The sampling rate of the controller was $250$ Hz, and $1000$ Hz for the simulation.
+The sampling rate of the controller was $250$ Hz considering the further real-time implementation, and $1000$ Hz for the simulation.
 To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.
-The readers are referred to the other papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to handle the weight constraints.
-
-The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h},\der t}$, where $h\in\{r_1,r_2\}$ and $T\in\R_{>0}$ denotes the episode duration time.
-Note that $c_{\overline\tau_i}$ and $c_{\underline\tau_i},\ \forall i\in\{1,2\}$ can not be active at the same time.
+The readers are referred to the previous papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to address the weight constraints.
+
+The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{r_1,r_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.
 
@@
     \end{tabular}
+    \label{table:controllers}
 \end{table}
@@
     \caption{
-  Simulation results of the (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
+  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
   }
@@
     \centering
-    \subfloat[Control input $\tau$ in time interval from $19$ s to $20$ s (bird's eye view).]{
+    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
     % \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
@@
         \vfill
-    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $20$ s.]{
+    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
         \includegraphics[width=\figSizeOneCol\linewidth]
@@
         \vfill
-    \subfloat[Auxiliary states in time interval from $19$ s to $20$ s.]{
+    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
         \includegraphics[width=\figSizeOneCol\linewidth]
@@
   \caption{
-  Simulation results of the CoNAC (blue) and CoNAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
+    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
   }
@@
 % Norm of error in Episode 1: 
-% C1 r1 ep1: 0.317
-% C1 r2 ep1: 0.467
-% C2 r1 ep1: 0.326
-% C2 r2 ep1: 0.475
-% C3 r1 ep1: 0.318
-% C3 r2 ep1: 0.471
+% C1 r1 ep1: 0.389
+% C1 r2 ep1: 0.426
+% C2 r1 ep1: 0.403
+% C2 r2 ep1: 0.456
+% C3 r1 ep1: 0.370
+% C3 r2 ep1: 0.427
 % Norm of error in Episode 2: 
-% C1 r1 ep2: 0.055
-% C1 r2 ep2: 0.155
-% C2 r1 ep2: 0.070
-% C2 r2 ep2: 0.179
-% C3 r1 ep2: 0.058
-% C3 r2 ep2: 0.190
+% C1 r1 ep2: 0.155
+% C1 r2 ep2: 0.066
+% C2 r1 ep2: 0.191
+% C2 r2 ep2: 0.094
+% C3 r1 ep2: 0.141
+% C3 r2 ep2: 0.083
 % Improvement in Episode 2: 
-% C1 r1: 0.827
-% C1 r2: 0.668
-% C2 r1: 0.785
-% C2 r2: 0.625
-% C3 r1: 0.818
-% C3 r2: 0.596
+% C1 r1: 0.602
+% C1 r2: 0.845
+% C2 r1: 0.527
+% C2 r2: 0.793
+% C3 r1: 0.619
+% C3 r2: 0.805
 % ------------------------------------
@@
 	\hline
-		$r_1$ & $0.317$ & $0.326$ & $0.318$ & $0.055$ & $0.070$ & $0.058$ \\
-	\hline
-        $r_2$ & $0.467$ & $0.475$ & $0.471$ & $0.155$ & $0.179$ & $0.190$ \\
+		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.155$ & $0.191$ & $0.141$ \\ 
+	\hline
+        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.066$ & $0.094$ & $0.083$ \\
 	\hline
@@
 Across the two episodes, all controllers enhanced their tracking performances about 
-82.7 \% for (C$_1$), 78.5 \% for (C$_2$), and 81.8 \% for (C$_3$) in $L_2$ norm of $r_1$, and 66.8 \% for (C$_1$), 62.5 \% for (C$_2$), and 59.6 \% for (C$_3$) in $L_2$ norm of $r_2$, respectively, by adapting their weights.
-Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were reduced in the second episode, as well.
-
-The tracking performance of (C$_1$) outperformed (C$_2$) and (C$_3$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
-This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was not able to use the full capability of the actuator due to the limitation of the auxiliary system and (C$_3$) occurred oscillations in constraint handling.
+$60.2 \%$ for (C$_1$), $52.7 \%$ for (C$_2$), and $61.9 \%$ for (C$_3$) in $L_2$ norm of $r_1$, and $84.5 \%$ for (C$_1$), $79.3 \%$ for (C$_2$), and $80.5 \%$ for (C$_3$) in $L_2$ norm of $r_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
+Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
+This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
+Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CoNAC was demonstrated.
+
+In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time interval from $7.5$ s to $8.5$ for Episode $1$, and from $19.5$ s to $20.5$ s for Episode $2$.
+This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
+However,
+
+The tracking performance of CoNAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
+This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was limited its first link actuator due to the feature of the auxiliary system.
 
@@
 
-In Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers satisfied the control input saturation illustrated in Fig.~\ref{fig:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$) and (C$_3$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_2$), as the weights were adapted to reduce the constraint violations.
-It is notable that the control input constraints were frequently active, since the controllers were implemented in discrete time with a sampling rate of $250$ Hz.
-
-Even though all controllers satisfied the input saturation, (C$_2$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $19$ s to $20$ s.
-This is because, as aforementioned, the auxiliary system only considers the input bound constraint, and the control input bound constraint for first link was imposed to approximately match the maximum allowable norm of the control input $\overline\tau$.
-In contrast, (C$_1$) and (C$_3$) were able to use the full capability of the actuator.
+As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$) and (C$_3$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_2$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$, and auxiliary state $\mv{\zeta}$, respectively.
+It is worth to note that the control input constraints were violated repeatedly, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
 
@@
 
+Even though all controllers satisfied the input saturation, (C$_2$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $19$ s to $21$ s.
+This is because, as aforementioned, the auxiliary system only considers the input bound constraint, and the control input bound constraint for first link was imposed to approximately match the maximum allowable norm of the control input $\overline\tau$, instead of $c_{\rbu}$.
+In contrast, (C$_1$) and (C$_3$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$.
+
+\hfill
+
 % zeta
-The detail of the constraint handling is now investigated.
+The detail of the constraint handling in the time interval from $19$ s to $21$ s, is now investigated.
 First, for (C$_2$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. 
 As the weights were adapted to reduce not only $\fe$ but also $\mv{\zeta}$, the constraint violation of $c_{\overline\tau_1}$ was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
-After the constraint was satisfied, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\tau_{1}$.
+After the constraint was satisfied, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$.
 
 % beta + zeta
-For (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ adjusted the adaptation direction of the weights $\widehat{ \mv{\theta}}_1$ to reduce the constraint violations, as the $\lambda_j$ increased by the constraint violations.
+For the cases of (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\widehat{ \mv{\theta}}_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
 % comparison; big, small beta
-For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
+For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for convex constraint $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
 With the bigger $\lambda_j$, the adaptation of $\widehat{ \mv{\theta}}_1$ is more assertive than that with smaller $\lambda_j$.
-This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but the oscillations of the violations.
+This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but this also causes oscillation in the adaptation process.
 In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_j$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_j,\ \forall j\in\mathcal I$ was satisfied and violated, respectively, in the discrete time implementation.
-Besides, with small $\lambda_j$, the adaptation direction of $\widehat{ \mv{\theta}}_1$ is more conservative, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
+Besides, with small $\lambda_j$, the adaptation direction of $\widehat{ \mv{\theta}}_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
 This allows the controller to show a smoother control input.
-However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt with respect to the filtered error $\fe$.
+However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt the weights with respect to the filtered error $\fe$.
 
@@
 
-The proposed CoNAC was also validated through real-time experiments on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
+To validate the effectiveness of the proposed CoNAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
+The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
 \color{red}
@@
 Additionally, the computational time was measured to validate the effectiveness of the proposed CoNAC in real-time applications.
-
-The tracking result of the real-time experiment is shown in Fig.~\ref{fig:ctrl:real:result}.
-
-is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CoNAC was 0.5 ms, which is less than the sampling time of 4 ms. 
-This indicates that the proposed CoNAC can be implemented in real-time applications.
 
@@
 
+\subsubsection{Tracking Performance and Constraint Handling}
+
+% ----------------------------
+% tracking performance + learning
+% ----------------------------
+The tracking result of the real-time experiment is shown in Fig.~\ref{fig:ctrl:real:result}.
+
+% ----------------------------
+% cosntraint handling
+% ----------------------------
+
+% ----------------------------
+% computational time
+% ----------------------------
+\subsubsection{Computational Time}
+is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CoNAC was 0.5 ms, which is less than the sampling time of 4 ms. 
+This indicates that the proposed CoNAC can be implemented in real-time applications.
+
 %  SECTION CONCLUSION ======================================

### 2025-04-12 src/script_simulation/main_plotter.m

@@ -9,9 +9,9 @@ more_blue = "#0072BD";
 more_red = "#A2142F";
 
 %% 
-ctrl1_name = "12-Apr-2025_00-22-05"; % CoNAC
-ctrl2_name = "12-Apr-2025_00-22-27"; % Aux.
-ctrl3_name = "12-Apr-2025_00-22-18"; % CoNAC 2.
+ctrl1_name = "12-Apr-2025_16-42-57"; % CoNAC
+ctrl2_name = "12-Apr-2025_16-35-02"; % Aux.
+ctrl3_name = "12-Apr-2025_16-43-22"; % CoNAC 2.
 
 % ctrl1_name = "11-Apr-2025_15-56-43"; % CoNAC
 % ctrl2_name = "11-Apr-2025_15-57-02"; % Aux.
@@ -88,14 +88,14 @@ figure(1); clf;
 hF = gcf; 
 hF.Position(3:4) = [fig_width, fig_height];
 
-plot([ep_time ep_time], [-5e1 5e1], "Color", "black", "LineWidth", line_width, "LineStyle", "-."); hold on
-text(.2, -1.8, "Episode 1", "FontSize", font_size, "FontName", 'Times New Roman')
-text(ep_time+.2, -1.8, "Episode 2", "FontSize", font_size, "FontName", 'Times New Roman')
-
 plot(t(obs_t), c1_xd1(1,obs_t), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
 plot(t(obs_t), c3_x1(1,obs_t), "Color", gray, "LineWidth", line_width, "LineStyle", "-"); hold on
 plot(t(obs_t), c2_x1(1,obs_t), "Color", "cyan", "LineWidth", line_width, "LineStyle", "-"); hold on
 plot(t(obs_t), c1_x1(1,obs_t), "Color", "blue", "LineWidth", line_width, "LineStyle", "-"); hold on
+
+plot([ep_time ep_time], [-5e1 5e1], "Color", "black", "LineWidth", line_width, "LineStyle", "-."); hold on
+text(.2, -1.8, "Episode 1", "FontSize", font_size, "FontName", 'Times New Roman')
+text(ep_time+.2, -1.8, "Episode 2", "FontSize", font_size, "FontName", 'Times New Roman')
 
 grid on; grid minor;
 xlabel('Time / s', 'FontSize', font_size, 'Interpreter', 'latex');
[…]

### 2025-04-12 src/script_simulation/models/ref4_load.m

@@ -15,7 +15,7 @@ function [r1, r2] = epi_gen(t)
     cycle = floor(t/CYCLE_TIME)+1;
 
     t = mod(t, CYCLE_TIME);
-2.1
+
     x0 = deg2rad([-90;0]);  
     xd1 = deg2rad([45;-90]);
     xd2 = deg2rad([-45;45]);

### 2025-04-12 manuscript.tex
update notations

@@
 where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
-The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
+The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
 Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).
@@
 For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
-The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in \{0,\cdots,k\}$ as 
 \begin{equation}
     \wth := 
-    \begin{bmatrix}
+    \begin{pmatrix}
         \wth_k\\
@@
         \wth_0
-    \end{bmatrix}
-    =
-    \begin{bmatrix}
+    \end{pmatrix}
+    =
+    \begin{pmatrix}
         \myvec(\wV_k)\\
@@
         \myvec(\wV_0)
-    \end{bmatrix},
+    \end{pmatrix},
 \end{equation}
@@
         \text{subject to }&c_{j}(\estwth) 
-        \le0, \quad j\in\mathcal{I},
+        \le0, \quad \forall j\in\mathcal{I},
         \end{aligned}
@@
 where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
-Inequality constraints $c_j,\ j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
+Inequality constraints $c_j,\ \forall j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
 Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
@@
 \end{subequations}
-where $\alpha=\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
 % By selecting $\alpha_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
@@
 Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
-Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max(\lambda_j-\tfrac{c_j}{\mu},0)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max\left(\lambda_j-\tfrac{c_j}{\mu},0\right)$, with $\mu\in\R_{>0}$ being the penalty parameter.
 
@@
         \mysign(\pptfrac{r_i}{\tau_j})
-    ]_{i,j\in[1,\cdots,m]}
+    ]_{i,j\in\{1,\cdots,m\}}
 $ using the sign of each entry (\ie control direction).
@@
 The weight constraints are essential to prevent the weights from diverging during the adaptation process.
-The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
 \begin{equation}
@@
 
-Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in\{0,\cdots,k\}}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
 The following lemma is introduced for the stability analysis.
@@
 \begin{lem} 
-    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i,\ \forall i\in[k,\cdots, i+1]$, remain bounded.
+    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
     \label{lem:cstr:grad:bound}
@@
 
-The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
+The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, with respect to $\estwth_i$ is represented as
 \begin{equation}
@@
         \textstyle\sum_{
-            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
         }
@@
 The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
-Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
 It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
@@
 
-The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
-The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
+The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
+The dynamics of $\estwth_i,\ \forall i\in\{k-1,\cdots,0\}$ are represented as
 \begin{equation}
@@
 \end{equation}
-Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in\{k,\cdots,i+1\}$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
 Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
@@
 % ------------------------------------
-The desired trajectory for $\q=[q_1,q_2]^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
+The desired trajectory for $\q=\left(q_1,q_2\right)^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
 The desired trajectory is defined as follows:
@@
     \!=\! 
-    \begin{bmatrix}
+    \begin{pmatrix}
         {q_d}_1\\{q_d}_2
-    \end{bmatrix}
+    \end{pmatrix}
     \!=\!
@@
         \!&\!
-        \text{if } 0\le t < t_f 
+        \text{if } 0\!\le\!t\!<\!t_f 
         ,
@@
         \!&\!
-        \text{if } t_f\le t < 2t_f 
+        \text{if } t_f\!\le\!t\!<\!2t_f 
         ,
@@
         \!&\! 
-        \text{if } 2t_f\le t < 3t_f 
+        \text{if } 2t_f\!\le\!t\!<\!3t_f 
         .
@@
         \!&\!    
-        \text{if } 3t_f\le t < 4t_f 
+        \text{if } 3t_f\!\le\!t\!<\!4t_f 
         ,

### 2025-04-12 manuscript.tex
add matlab fig to tikz fig converter
mat2pdf moved to template

@@
     \subfloat[Tracking result of $q_1$.]{
-      \includegraphics[width=\figSizeTwoCol\linewidth]
+      \includegraphics
+    %   \includegraphics[width=\figSizeTwoCol\linewidth]
       {
-        % src/script_simulation/figures/compare/Fig10.eps
-        src/script_simulation/figures/compare/Fig1.eps
+        fig/Fig1.pdf
+        % src/script_simulation/figures/compare/Fig1.eps
       }%
@@
     \subfloat[Norm of weights $\hat\theta_i$.]{
+        % \includegraphics
         \includegraphics[width=\figSizeTwoCol\linewidth]
         {
+            % fig/Fig7.pdf
             src/script_simulation/figures/compare/Fig7.eps
@@
 However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt the weights with respect to the filtered error $\fe$.
+
+% ------------------------------------
+% Karsh-Kuhn-Tucker (KKT) conditions}
+% ------------------------------------
+\subsubsection{Satisfaction of Karsh-Kuhn-Tucker (KKT) conditions}
+
+\color{red}
+The KKT conditions defined in \cite[Def.
+@@]{Nocedal:2006aa} were satisfied in the simulation, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
+\color{black}
 

### 2025-04-12 toPDF.py

@@ -1,71 +1,0 @@
-import os
-
-fig_num = 11
-
-try:
-    for i in range(1, fig_num + 1):
-        print(f"Converting Fig{i} to PDF...")
-
-        tmp_file_name = f"tmp_fig_{i}"
-
-        with open(f"{tmp_file_name}.tex", "w") as tex_file:
-
-            tex_content = f"""
-    \\documentclass{{standalone}}
-
-    \\usepackage{{pgfplots}}
-    \\pgfplotsset{{compat=newest}}
-    %% the following commands are needed for some matlab2tikz features
-    % \\usetikzlibrary{{plotmarks}}
-    % \\usetikzlibrary{{arrows.meta}}
-    % \\usepgfplotslibrary{{patchplots}}
-    % \\usepackage{{grffile}}
-    % \\usepackage{{amsmath}}
-
-    \\usepgfplotslibrary{{external}} 
-    \\tikzexternalize
-
-    %% you may also want the following commands
-    %   \\pgfplotsset{{plot coordinates/math parser=false}}
-    %   \\newlength\\figureheight
-    %   \\newlength\\figurewidth
-
-    \\begin{{document}}
-    \\input{{src/script_simulation/figures/compare/Fig{i}.tex}}
-    \\end{{document}}
-            """
-            tex_file.write(tex_content)
-            tex_file.close()
-
-        print(f"Compiling {tmp_file_name}.tex to PDF...")
-        os.system(f"lualatex -shell-escape -interaction=nonstopmode -halt-on-error {tmp_file_name}.tex > /dev/null 2>&1")
-        os.system(f"mv {tmp_file_name}-figure0.pdf fig/Fig{i}.pdf")
-        print(f"PDF file fig/Fig{i}.pdf created successfully.")
-
-        print(f"Cleaning up temporary files...")
-        os.system(f"rm -f {tmp_file_name}.tex")
-        os.system(f"rm -f {tmp_file_name}.aux")
-        os.system(f"rm -f {tmp_file_name}.log")
-        os.system(f"rm -f {tmp_file_name}.auxlock")
-        os.system(f"rm -f {tmp_file_name}-figure0.dpth")
-        os.system(f"rm -f {tmp_file_name}-figure0.log")
-        os.system(f"rm -f {tmp_file_name}-figure0.md5")
-        os.system(f"rm -f {tmp_file_name}.pdf")
-        print(f"Temporary files cleaned up.")
[…]

### 2025-04-14 manuscript.tex
resize figure; add .spl in gitignore

@@
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
-Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+\ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
 
@@
 \begin{prop} 
-    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $(\dot{\rbM}-2\rbVm)$ is skew-symmetric.
+    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $\dot{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\dot{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
     \label{prop:skew}
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=0.8\linewidth]{src/figures/Controller.drawio.png}
+    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
     \label{fig:ctrl:diagram}
-\end{figure*}
+\end{figure}
 
@@
         =&
-        \fe^\top \rbM (
+        \fe^\top \dot{\rbM}\fe + \tfrac{1}{2}\fe^\top \ddtfrac{\rbM}{\fe}\fe
+        \\
+        =&
+        \fe^\top (
             -\rbVm \fe -\mm K \fe + \mv f
@@
       {
-        fig/Fig1.pdf
-        % src/script_simulation/figures/compare/Fig1.eps
+        % fig/Fig1.pdf
+        src/script_simulation/figures/compare/Fig1.eps
       }%

### 2025-04-15 manuscript.tex
minor changes on plotter

@@
 \title{
-  Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
+  Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
 } %% Article title
@@
     \subfloat[Tracking result of $q_1$.]{
-      \includegraphics
-    %   \includegraphics[width=\figSizeTwoCol\linewidth]
+    %   \includegraphics
+      \includegraphics[width=\figSizeTwoCol\linewidth]
       {

### 2025-04-15 src/measurement/main_plotter.m

@@ -2,7 +2,7 @@ clear
 
 ANITMATE = 0;
 AINMATION_SAVE_FLAG = 0;
-SAVE_FLAG = 1;
+SAVE_FLAG = 0;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
 
 %%
@@ -25,12 +25,12 @@ lgd_size = 16;
 fig_height = 230 * 1; 
 fig_width = 800 * 1;
 %% 
-ctrl1_name = "c1.csv"; % CoNAC
+ctrl1_name = "c2-2.csv"; % CoNAC
 ctrl2_name = "c2.csv"; % Aux.
 
 %%
-ctrl1_log = post_procc(ctrl1_name);
-ctrl2_log = post_procc(ctrl2_name);
+ctrl1_log = post_procc(ctrl1_name, 4);
+ctrl2_log = post_procc(ctrl2_name, 4);
 
 %% RESULT PLOTTER
 % T = ctrl1_log.T;
@@ -42,8 +42,8 @@ T = t1(end);
 obs_t1 = 1:length(t1);
 obs_t2 = 1:length(t2);
 
-start_time = 8.5;
-end_time = 9.9;
+start_time = 19;
+end_time = 21;
 
 obs_t1_1 = find(t1 >= start_time & t1 <= end_time);
 obs_t2_1 = find(t2 >= start_time & t2 <= end_time);
@@ -73,9 +73,9 @@ c2_th =     transpose(ctrl2_log(:,23:25));
 c2_zeta =   transpose(ctrl2_log(:,26:27));
 c2_cmp =   transpose(ctrl2_log(:,28));
 
-u_max1 = 10;
-u_max2 = 2;
-u_ball = 10;
+u_ball = 11.5;
+u_max2 = 4;
+u_max1 = sqrt(u_ball^2 - u_max2^2);
 th_max = [11,12,13];
 
 %%
@@ -356,7 +356,7 @@ xlim([0 T])
 % ============================================
 %    Fig. 11: Box-Whisker Plot
 % ============================================
-var_plot
+% var_plot
 
 %% ============================================
 %% SAVE FIGURES

### 2025-04-15 src/measurement/post_procc.m

@@ -1,13 +1,11 @@
-function [data, loss_ratio] = post_procc(ctrl_name)
+function [data, loss_ratio] = post_procc(ctrl_name, ctrl_num)
 
+    % remove the data with large change
     data = readtable("sim_result/"+ctrl_name);
     data = data{1:end-1, 1:28};
-
-    del_ts = [0.001, 0.004];
-
-    pt = find(data(:,2).^2 > 1e-6);
-    data = data(pt, :);
     ori_num = length(data);
+
+    del_ts = [0.002, 0.004];
 
     pt = [];
     % sampling time check
@@ -18,18 +16,28 @@ function [data, loss_ratio] = post_procc(ctrl_name)
         pt = union(pt, tmp_pt);
     end
 
+    control_num = ctrl_num;
     % remove the data with large change
+    tmp_pt = find((data(:,2) - control_num).^2 < 1e-6);
+    data = data(tmp_pt, :);
+
+    pt = 1:size(data,1);
     thr = 1e0;
     for idx = 3:28
         tmp_pt = find((data(2:end,idx) - data(1:end-1,idx)).^2 > thr);
         pt = setdiff(pt, tmp_pt);
     end
-
+    
     data = data(pt, :);
     mod_num = length(data);
-
     loss_ratio = (ori_num - mod_num) / ori_num;
     fprintf('loss ratio: %.3f%%\n', loss_ratio*1e2);
+    
+    % figure(1); clf;
+    % plot(data(:,1), data(:,2)); hold on
+    % plot(data(:,1), data(:,4)); hold on
+
+
 end
 
 

### 2025-04-15 src/script_simulation/controllers/loadGlobalOpts.m

@@ -13,16 +13,16 @@ function opt = loadGlobalOpts(dt, CONTROL_NUM)
     opt.e_size = 2;
 
     opt.cstr.th_max = [11;12;13] * 1e0;
-    opt.cstr.u_ball = 10;
-    opt.cstr.uMax1 = 9.682;
-    opt.cstr.uMax2 = 2.5;
+    opt.cstr.u_ball = 11.5;
+    opt.cstr.uMax2 = 4;
+    opt.cstr.uMax1 = sqrt(opt.cstr.u_ball^2 - opt.cstr.uMax2^2);
 
     if CONTROL_NUM == 1
         % opt.beta = [1 1 1] * 1e-1;
         opt.beta(1:3) = [1 1 1] * 1e-3;
         opt.beta(4) = 1e1; % control input ball
         opt.beta(5) = 0e2; % control input 1 Max
-        opt.beta(6) = 1e3; % control input 2 Max
+        opt.beta(6) = 1e4; % control input 2 Max
         opt.beta(7) = opt.beta(5); % control input 1 Min
         opt.beta(8) = opt.beta(6); % control input 2 Min
         % opt.beta = opt.beta/opt.alpha;

### 2025-04-15 src/script_simulation/main_plotter.m

@@ -31,9 +31,9 @@ end
 
 
 %% 
-ctrl1_name = "12-Apr-2025_16-42-57"; % CoNAC
-ctrl2_name = "12-Apr-2025_16-35-02"; % Aux.
-ctrl3_name = "12-Apr-2025_16-43-22"; % CoNAC 2.
+ctrl1_name = "14-Apr-2025_13-30-51"; % CoNAC
+ctrl2_name = "14-Apr-2025_13-31-05"; % Aux.
+ctrl3_name = "14-Apr-2025_13-31-26"; % CoNAC 2.
 
 % ctrl1_name = "11-Apr-2025_15-56-43"; % CoNAC
 % ctrl2_name = "11-Apr-2025_15-57-02"; % Aux.

### 2025-04-15 src/script_simulation/models/model1.m

@@ -8,9 +8,11 @@ m1 = 2.465;             % [kg]
 m2 = 2.465;             % [kg]
 % m2 = 1.093;
 L1 = .2;             % [m]
-L2 = .15+.01+.02;
+L2 = .2;             % [m]
+% L2 = .15+.01+.02;
 Lc1 = .13888;             % [m]
-Lc2 = .08691;
+Lc2 = .13888;             % [m]
+% Lc2 = .08691;
 g = 9.81;             % [m/s^2]
 
 % b1 = 0;             % [Nms]
@@ -31,7 +33,8 @@ fs1 = .3;
 fs2 = .3;
 
 I1 = .06911;
-I2 = .01532;
+I2 = .06911;
+% I2 = .01532;
 
 %% from 10.1109/AFRCON.2013.6757809
 

### 2025-04-15 manuscript.tex
refresh plotter

@@
 \title{
-  Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
+  Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints 
 } %% Article title
@@
 \begin{abstract}
-  This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints.
-A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints.
+  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for weight norm and convex input constraints. 
+  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while addressing both types of constraints. 
   The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. 
   The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
-Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
+  Real-time implementation was conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
 \end{abstract}
@@
 \begin{keyword}
-Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep Euler-Lagrange system \sep input constraint
+Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep input constraint
 
@@
     \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
-    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
+    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
         \mm A
@@
         _{
-            i\in[1,\cdots,n],j\in[1,\cdots ,m]
+            i\in\{1,\cdots,n\},j\in\{1,\cdots ,m\}
         }\allowbreak\in\R^{n\times m}
@@
 \begin{itemize}
-    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
-    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
+    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
+    \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
 The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
-    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
+    % \item The forward sensitivity method is applied in CONAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
     %, enabling more precise real-time adaptation.
@@
 In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
-Candidates of input constraints are presented in \ref{sec:appen:cstr}.
 Section \ref{sec:stability} analyzes the stability of the proposed controller.
-A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
+A real-time implementation of the proposed controller is presented in Section \ref{sec:sim}, where the proposed controller is applied to a 2-DOF robotic manipulator.
 Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
-% The appendices provide the proof of the lemma used in the stability analysis.
-
-%  SECTION PROBLEM FORMULATION ============================
+The candidates of input constraints are presented in \ref{sec:appen:cstr}.
+
+% ====================================
+%  SECTION PROBLEM FORMULATION 
+% ====================================
 \section{Problem Formulation}\label{sec:Problem Formulation}
@@
 
-The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
+The architecture of the proposed CONAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
 Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model.
@@
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
     \label{fig:ctrl:diagram}
@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.99\linewidth]{src/figures/DNN.drawio.pdf}
+    \caption{
+        Architecture of the DNN $\NN({\q}_n;\wth)$ with $2$ hidden layers.
+    }
+    \label{fig:DNN}
+\end{figure}
+
 The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
@@
     \begin{cases}
-        \wV_i^\top \NN_i(\NN_{i-1}), 
+        \wV_i^\top \act_i(\NN_{i-1}), 
         &
@@
 %  SECTION SIMULATION ======================================
-\section{Implementation and Validation}\label{sec:sim}
-
-The proposed CoNAC was validated via numerical simulation and real-time experiment on a two-link manipulator.
-
-\subsection{Numerical Simulation Validation}
-
-% ------------------------------------
-% MCU & Robot Model and Ref. Trajectory
+\section{Real-Time Implementation and Validation}\label{sec:sim}
+
+The proposed CONAC was validated via real-time experiment on a two-link manipulator.
+
+\subsection{Validation Setup}
+
+% ------------------------------------
+% Real-time Implementation Set-up
+% ------------------------------------
+\begin{figure}[t]
+    \centering
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            fig/exp_set.jpg
+        }%
+    \caption{
+        Robot setup for the real-time experiment.
+    }
+    \label{fig:ctrl:exp:set}
+  \end{figure}
+
+To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
+The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
+\color{red}
+The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
+The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
+The reference trajectory was generated using the same method as in the numerical simulation.
+\color{black}
+
+% ------------------------------------
+% Robot Model and Ref. Trajectory
 % ------------------------------------
@@
 % ------------------------------------
-To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
+To demonstrate the effectiveness of the proposed CONAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
 %
@@
 % ------------------------------------
-% Controllers: CoNAC 
-% ------------------------------------
-\subsubsection*{Controller 1: (C$_1$) CoNAC; proposed}
-
-To handle the input saturation, the proposed CoNAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
+% Controllers: CONAC 
+% ------------------------------------
+\subsubsection*{Controller 1: (C$_1$) CONAC; proposed}
+
+To handle the input saturation, the proposed CONAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
 \begin{equation}
@@
     ,
-    \label{eq:sim:cstr:CoNAC}
+    \label{eq:sim:cstr:CONAC}
 \end{equation}
@@
 Hence, (C$_1$) is possible to use full capability of the actuator.
-The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CoNAC.
+The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CONAC.
 As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.
@@
 % ------------------------------------
-% Controllers: Aux. system in CoNAC-AUX
-% ------------------------------------
-\subsubsection*{Controller 2: (C$_2$) CoNAC with auxiliary system}
+% Controllers: Aux. system in CONAC-AUX
+% ------------------------------------
+\subsubsection*{Controller 2: (C$_2$) CONAC with auxiliary system}
 
@@
 % ------------------------------------
-% Controllers: CoNAC with small beta
-% ------------------------------------
-\subsubsection*{Controller 3: (C$_3$) CoNAC with small $\beta_i$}
+% Controllers: CONAC with small beta
+% ------------------------------------
+\subsubsection*{Controller 3: (C$_3$) CONAC with small $\beta_i$}
 
@@
 The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
-The sampling rate of the controller was $250$ Hz considering the further real-time implementation, and $1000$ Hz for the simulation.
+The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.
+\MSRY{CAN Hz?}
 To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.
-The readers are referred to the previous papers of the author's \MSRY{ECC, IECON paper} for the demonstration of the capabilities of the proposed CoNAC to address the weight constraints.
 
@@
 %     }}
-% \caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CoNAC and CoNAC-AUX across various parameter values.}
+% \caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CONAC and CONAC-AUX across various parameter values.}
 %     \label{fig:ctrl:result:var}
@@
 %     \hline
-%     \textbf{CoNAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
+%     \textbf{CONAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
 %     \hline
-%     \textbf{CoNAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
+%     \textbf{CONAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
 %     \hline
@@
 %     % \hline
-%         \bf{CoNAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
+%         \bf{CONAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
 %     \hline
@@
     \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
-    % \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
+    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
         \includegraphics[width=\figSizeOneCol\linewidth]
@@
 This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
-Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CoNAC was demonstrated.
+Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.
 
@@
 
-The tracking performance of CoNAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
+The tracking performance of CONAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
 This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was limited its first link actuator due to the feature of the auxiliary system.
@@
 
-% ------------------------------------
-% Real-time Implementation Set-up
-% ------------------------------------
-\begin{figure}[t]
-    \centering
-        \includegraphics[width=\figSizeOneCol\linewidth]
-        {
-            fig/exp_set.jpg
-        }%
-    \caption{
-        Robot setup for the real-time experiment.
-    }
-    \label{fig:ctrl:exp:set}
-  \end{figure}
-
-\subsection{Real-time Experiment Validation}
-
-To validate the effectiveness of the proposed CoNAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
-The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
-\color{red}
-The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
-The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
-The reference trajectory was generated using the same method as in the numerical simulation.
-\color{black}
-The equal reference trajectory was applied and the parameters of the CoNAC were set to those whose best performance was achieved in the simulation (\ie $\beta=...$).
-Additionally, the computational time was measured to validate the effectiveness of the proposed CoNAC in real-time applications.
-
-\begin{figure*}[t]
-    \centering
-      \subfloat[Tracking result of $q_1$.]{
-        \includegraphics[width=\figSizeTwoCol\linewidth]
-        {
-            src/script_simulation/figures/compare/Fig1.eps
-        }%
-        \label{fig:ctrl:real:result:q1}}
-      % \vfill
-      \subfloat[Tracking result of $q_2$.]{
-        \includegraphics[width=\figSizeTwoCol\linewidth]
-        {
-            src/script_simulation/figures/compare/Fig2.eps
-        }%
-        \label{fig:ctrl:real:result:q2}}
-      \vfill
-        \subfloat[Control input $\tau_1$.]{
-          \includegraphics[width=\figSizeTwoCol\linewidth]
-          {
-            src/script_simulation/figures/compare/Fig3.eps
-          }%
-          \label{fig:ctrl:real:result:tau:1}}
-      % \vfill
-        \subfloat[Control input $\tau_2$.]{
-          \includegraphics[width=\figSizeTwoCol\linewidth]
-          {
-            src/script_simulation/figures/compare/Fig4.eps
-          }%
-          \label{fig:ctrl:real:result:tau:2}}
-          \vfill
-      \subfloat[Norm of weights $\hat\theta_i$.]{
-          \includegraphics[width=\figSizeTwoCol\linewidth]
-          {
-            src/script_simulation/figures/compare/Fig5.eps
-          }%
-          \label{fig:ctrl:real:result:opt:norm}}
-          % \vfill
-      \subfloat[Lagrange multipliers $\lambda_j$ in logarithmic scale.]{
-          \includegraphics[width=\figSizeTwoCol\linewidth]
-          {
-            src/script_simulation/figures/compare/Fig6.eps
-          }%
-          \label{fig:ctrl:real:result:opt:multiplier}}
-          \vfill
-      \subfloat[Auxiliary states $\mv{\zeta}$ of CoNAC-AUX.]{
-          \includegraphics[width=\figSizeTwoCol\linewidth]
-          {
-            src/script_simulation/figures/compare/Fig7.eps
-          }%
-          \label{fig:ctrl:real:result:opt:zeta}}
-          % \vfill
-      \subfloat[Control input $\tau$ in time interval from $1$ s to $3$ s (bird's eye view).]{
-          \includegraphics[width=\figSizeTwoCol\linewidth]
-          {
-            src/script_simulation/figures/compare/Fig8.eps
-          }%
-          \label{fig:ctrl:real:result:control}}
-    \caption{
-    Simulation results of the CoNAC (blue) and CoNAC-AUX (cyan), and reference signal of $\qd$ (red dashed line).
-    }
-  \label{fig:ctrl:real:result}
-  \end{figure*}
+\subsubsection{Computational Time}
+is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 0.5 ms, which is less than the sampling time of 4 ms. 
+This indicates that the proposed CONAC can be implemented in real-time applications.
 
@@
     \caption{
-        Computational time of CoNAC and CoNAC-AUX. 
+        Computational time of CONAC and CONAC-AUX. 
     }
@@
 
-\subsubsection{Tracking Performance and Constraint Handling}
-
-% ----------------------------
-% tracking performance + learning
-% ----------------------------
-The tracking result of the real-time experiment is shown in Fig.~\ref{fig:ctrl:real:result}.
-
-% ----------------------------
-% cosntraint handling
-% ----------------------------
-
-% ----------------------------
-% computational time
-% ----------------------------
-\subsubsection{Computational Time}
-is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CoNAC was 0.5 ms, which is less than the sampling time of 4 ms. 
-This indicates that the proposed CoNAC can be implemented in real-time applications.
-
 %  SECTION CONCLUSION ======================================
@@
 
-This paper presented a constrained optimization-based neuro-adaptive controller (CoNAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+This paper presented a constrained optimization-based neuro-adaptive controller (CONAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
 The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
@@
 The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds.
-By formulating these constraints as part of the optimization process, CoNAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
-
-Simulation results validated the superior performance of CoNAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
-CoNAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
+By formulating these constraints as part of the optimization process, CONAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
+
+Simulation results validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
 

### 2025-04-15 latexdiff.py

@@ -1,88 +1,117 @@
 """
 latexdiff.py
-- COMMIT1: Default hash for the first commit (most recent).
-- COMMIT2: Default hash for the second commit.
-- `latexdiff` and `pdflatex` must be installed and available in the system PATH.
-Note:
-- Ensure that the `manuscript.tex` file exists in the specified commits.
-- The script performs cleanup by removing intermediate files generated during 
-    the process.
+- COMMIT1: new commit hash.
+- COMMIT2: old commit hash.
+
+OUTPUT:
+- diff.pdf
 
 - Myeongseok Ryu
 - 2025.04.14
 """
 
 import os
+import subprocess
 
-COMMIT1 = "6aeb18adc1837a672b27f840c0d8db9bda24ddea" # recent
-COMMIT2 = "1e867d3f66016f2603fbf7f1138cdaa9d0be86cb"
+COMMIT1 = "6aeb18adc1837a672b27f840c0d8db9bda24ddea" # new
+COMMIT2 = "732664d84fa6e31b4a6167434ca7f8a5d4d41687" # old
+TEX_FILE_NAME = "{tex_file_name}"
 
 SAVE_DIR = "."
 
+def run_terminal_command(command):
+    print(f"$ {command}")
+    os.system(command)
+
+def compile_tex(file_name):
+    run_terminal_command("pdflatex -interaction=batchmode {file_name}")
+    run_terminal_command("bibtex {file_name[:-4]}.aux")
+    run_terminal_command("pdflatex -interaction=batchmode {file_name}")
+    run_terminal_command("pdflatex -interaction=batchmode {file_name}")
+
+def clean_up():
+    print("Cleaning up...")
+    run_terminal_command("rm tmp1.tex")
+    run_terminal_command("rm tmp2.tex")
+    run_terminal_command("rm tmp1.pdf")
+    run_terminal_command("rm tmp2.pdf")
+    run_terminal_command("rm diff.tex")
+    run_terminal_command("rm *.aux")
+    run_terminal_command("rm *.log")
+    run_terminal_command("rm *.out")
+    run_terminal_command("rm *.bbl")
+    run_terminal_command("rm *.blg")
+    run_terminal_command("rm *.run.xml")
+    run_terminal_command("rm *.toc")   
+    run_terminal_command("rm *.synctex.gz")
+    run_terminal_command("rm *.fdb_latexmk")
+    run_terminal_command("rm *.fls")
[…]

### 2025-04-15 src/measurement/animate.m

@@ -1,31 +1,91 @@
+clear
+figure(1); close
+figure(1);
 
-figure(7); clf
+AINMATION_SAVE_FLAG = 1;
+video_name = "sample";
+gray = "#808080";
 
+more_blue = "#0072BD";
+more_red = "#A2142F";
+
+line_width = 1.5;
+font_size = 12;
+T = 24;
+
+%% 
+ctrl1_name = "2025_04_09_13_30"; % CoNAC
+ctrl2_name = "2025_04_09_13_30"; % Aux.
+ctrl3_name = "2025_04_09_13_30"; % CoNAC 2.
+ctrl4_name = "2025_04_09_13_30"; % CoNAC 2.
+
+%%
+data1 = post_procc(ctrl1_name, 4);
+data2 = post_procc(ctrl2_name, 4);
+data3 = post_procc(ctrl3_name, 4);
+data4 = post_procc(ctrl4_name, 4);
+
+c1 = "blue"; c2="cyan"; c3=gray; c4="yellow";
+th_max = [11 12 13];
+u_ball = 12;
+u_max1 = 10;
+u_max2 = 3;
+
+%%
+dt = data1.t(2) - data1.t(1);
+
+%%
 L1 = .45;            
 L2 = .45;
 
-accel = 1;
-
+%% SAVE VIDEO
 if AINMATION_SAVE_FLAG
-    v = VideoWriter("sim_result/"+ctrl_name, 'MPEG-4');
+    v = VideoWriter("sim_result/"+video_name, 'MPEG-4');
     % v.Quality = 100;
-    v.FrameRate = 1/dt/accel; 
+    v.FrameRate = 1/dt; 
     open(v);
 end
 
-for t_idx = 1:accel:length(t)
-    pause(1e-3)
+%% ANIMATE
+for t = 0:dt:T
+    pause(0.001)
     clf
 
-    q1_c1 = c1_x1(1, t_idx); q2_c1 = c1_x1(2, t_idx);
-    q1_c2 = c2_x1(1, t_idx); q2_c2 = c2_x1(2, t_idx);
-    r1 = c1_xd1(1, t_idx); r2 = c1_xd1(2, t_idx);
+    t_idx1 = find(data1.t >= t, 1);
+    t_idx2 = find(data2.t >= t+1, 1);
+    t_idx3 = find(data3.t >= t+2, 1);
+    t_idx4 = find(data4.t >= t+3, 1);
+
[…]

### 2025-04-15 src/measurement/main_plotter.m

@@ -1,113 +1,88 @@
 clear
 
-ANITMATE = 0;
-AINMATION_SAVE_FLAG = 0;
+%%
 SAVE_FLAG = 0;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
-
-%%
+TEX_CONVERT_FLAG = 0;
 gray = "#808080";
 
 more_blue = "#0072BD";
 more_red = "#A2142F";
 
-% font_size = 16;
-% line_width = 2;
-% lgd_size = 12;
-    
-% fig_height = 210 * 1; 
-% fig_width = 450 * 1;
+%%
+if TEX_CONVERT_FLAG
+    font_size = 4;
+    line_width = .5;
+    lgd_size = 2;
 
-font_size = 20;
-line_width = 2;
-lgd_size = 16;
-    
-fig_height = 230 * 1; 
-fig_width = 800 * 1;
+    fig_height = 8.89/4;
+    fig_width = 8.89;
+
+    fig_unit = 'centimeters';
+else
+    font_size = 18;
+    line_width = 1.5;
+    lgd_size = 16;
+        
+    fig_height = 200;
+    fig_width = 800;
+
+    fig_unit = 'pixels';
+end
+
 %% 
-ctrl1_name = "c2-2.csv"; % CoNAC
-ctrl2_name = "c2.csv"; % Aux.
+ctrl1_name = "2025_04_09_13_30"; % CoNAC
+ctrl2_name = "2025_04_09_13_30"; % Aux.
+ctrl3_name = "2025_04_09_13_30"; % CoNAC 2.
+ctrl4_name = "2025_04_09_13_30"; % CoNAC 2.
 
 %%
-ctrl1_log = post_procc(ctrl1_name, 4);
-ctrl2_log = post_procc(ctrl2_name, 4);
+data1 = post_procc(ctrl1_name, 4);
+data2 = post_procc(ctrl2_name, 4);
+data3 = post_procc(ctrl3_name, 4);
+data4 = post_procc(ctrl4_name, 4);
 
-%% RESULT PLOTTER
-% T = ctrl1_log.T;
-t1 = ctrl1_log(:,1);
-t1 = t1-t1(1);
-t2 = ctrl2_log(:,1);
-t2 = t2-t2(1);
-T = t1(end);
-obs_t1 = 1:length(t1);
-obs_t2 = 1:length(t2);
-
-start_time = 19;
-end_time = 21;
-
[…]

### 2025-04-15 src/measurement/var_plot.m

@@ -1,194 +1,0 @@
-SAVE_FLAG = 1;
-
-save_idx = [];
-
-%%
-font_size = 20;
-line_width = 2;
-lgd_size = 16;
-    
-fig_height = 230 * 1.5; 
-fig_width = 800 * 1;
-
-% 
-data_num = "10-Apr-2025_11-56-08";
-
-sim_dt = 1/250;
-ISE = @(e) sqrt(sum(e.^2)*sim_dt);
-
-u_max1 = 11.5;
-u_max2 = 16;
-u_ball = 12;
-th_max = [11,12,13];
-
-[~,~] = mkdir("figures/"+ctrl_name);
-[~,~] = mkdir("figures/"+ctrl_name+"/c1");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig1");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig2");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig3");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig4");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig5"); 
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig6");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig7");
-[~,~] = mkdir("figures/"+ctrl_name+"/c1/fig8");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig1");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig2");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig3");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig4");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig5");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig6");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig7");
-[~,~] = mkdir("figures/"+ctrl_name+"/c2/fig8");
-
-
-VAR_NUM = 9;
-
-%% DATA PRE-PROCESSING
-PI1 = []; PI2 = [];
-
-% remove the data with large change
-data = readtable("sim_result/"+ctrl_name);
-data = data{1:end-1, 1:28};
[…]

### 2025-04-16 src/measurement/main_plotter.m
correct figure

@@ -345,62 +345,33 @@ ylim([minVal-len*ratio maxVal+len*ratio]);
     ax.FontSize = font_size; 
     ax.FontName = 'Times New Roman';
 
-% %% FIG. 10, 11; FILTERED ERROR
-% figure(10); clf;
-% hF = gcf;
-% hF.Units = fig_unit;
-% hF.Position(3:4) = [fig_width, fig_height];
 
-% e1 = c1_x1-c1_xd1; ed1 = c1_x2-c1_xd2;
-% e2 = c2_x1-c2_xd1; ed2 = c2_x2-c2_xd2;
-% e3 = c3_x1-c3_xd1; ed3 = c3_x2-c3_xd2;
+% =============================================
+%    Fig. 10: Computational Time
+% =============================================
+figure(10); clf;
+hF = gcf; 
+hF.Position(3:4) = [fig_width, fig_height];
 
-% r1 = ed1+[5 0; 0 15]*e1;
-% r2 = ed2+[5 0; 0 15]*e2;
-% r3 = ed3+[5 0; 0 15]*e3;
+plot(data4.t(data4.obs), data4.cmp(1,data4.obs)*1e3, "color", c4, "LineWidth", line_width, "LineStyle", "-"); hold on
+plot(data3.t(data3.obs), data3.cmp(1,data3.obs)*1e3, "color", c3, "LineWidth", line_width, "LineStyle", "-"); hold on
+plot(data2.t(data2.obs), data2.cmp(1,data2.obs)*1e3, "color", c2, "LineWidth", line_width, "LineStyle", "-"); hold on
+plot(data1.t(data1.obs), data1.cmp(1,data1.obs)*1e3, "color", c1, "LineWidth", line_width, "LineStyle", "-"); hold on
 
-% plot(t(obs), r3(1,obs), "Color", gray, "LineWidth", line_width, "LineStyle", "-"); hold on
-% plot(t(obs), r2(1,obs), "Color", "cyan", "LineWidth", line_width, "LineStyle", "-"); hold on
-% plot(t(obs), r1(1,obs), "Color", "blue", "LineWidth", line_width, "LineStyle", "-"); hold on
+xlabel("Time / s", "Interpreter", "latex")
+ylabel("Cmp. Time / ms", "Interpreter", "latex")
+set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+grid on 
+xlim([0 T])
+% ylim([-u_max2*1.25, u_max2*1.25])
[…]

### 2025-04-16 manuscript.tex
correct figure
exp. set upload

@@
         {
-            fig/exp_set.jpg
+            src/figures/exp_set.drawio.png
         }%
@@
     \hfill
-    \subfloat[Control input saturation function.\MSRY{sat이 아니라 집합으로 표현하기}]{
-        \includegraphics[width=0.45\linewidth]{src/figures/saturation.drawio.pdf}
+    \subfloat[Control input saturation function.]{
+        \includegraphics[width=0.55\linewidth]{src/figures/saturation.drawio.pdf}
         \label{fig:robot:sat}

### 2025-04-17 manuscript.tex
add forth controlller

@@
 % ------------------------------------
-For a comparative study, we implemented 3 controllers.
+For a comparative study, we implemented 4 controllers.
 The properties of the controllers are summarized in Table~\ref{table:controllers}.
@@
 The remaining parameters are the same as (C$_1$).
+
+% ------------------------------------
+% Controllers: CONAC without ctrl cstr
+% ------------------------------------
+\subsubsection*{Controller 4: (C$_4$) CONAC without control input constraints}
+
+The controller 4 is the same as (C$_1$) but without the control input constraints, to show the effect of the control input constraints.
+In this case, the update rate of the Lagrange multipliers regarding the control input constraints \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$ was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated.
 
@@
     \hline
-        (C$_1$) & proposed & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
-    \hline
-        (C$_2$) & aux. sys. & $\overline{\tau}_1=-\underline{\tau}_1=9.682$ and $\overline{\tau_2}=-\underline{\tau_2}=2.5$ \\
-    \hline
-        (C$_3$) & small $\beta_i$ & $\overline{\tau}=10$ and $\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
+        (C$_1$)\!&\!proposed\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
+    \hline
+        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
+    \hline
+        (C$_3$)\!&\!small $\beta_i$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
+    \hline
+        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
     \hline
@@
     \centering
-    \begin{tabular}{c c c c c c c}
-    \hline
-		& \multicolumn{3}{c}{\textbf{Episode 1}}  & \multicolumn{3}{c}{\textbf{Episode 2}} \\
-    \hline
-	\hline 
-		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_1$) & (C$_2$) & (C$_3$) \\
-	\hline
-		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.155$ & $0.191$ & $0.141$ \\ 
-	\hline
-        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.066$ & $0.094$ & $0.083$ \\
+    \begin{tabular}{c c c c c}
+    \hline
+		& \multicolumn{4}{c}{\textbf{Episode 1}} \\
+    \hline
+	\hline 
+		& (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
+	\hline
+		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
+	\hline
+        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
+	\hline
+        & \multicolumn{4}{c}{\textbf{Episode 2}} \\
+    \hline
+    \hline
+        & (C$_1$) & (C$_2$) & (C$_3$) & (C$_4$) \\
+	\hline
+		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
+	\hline
+        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
     \hline

### 2025-04-18 manuscript.tex
new plotter for new measurement method (CAN)

@@
         =&
-        \fe^\top \dot{\rbM}\fe + \tfrac{1}{2}\fe^\top \ddtfrac{\rbM}{\fe}\fe
+        \fe^\top \rbM \ddtt \fe
+        +
+        \tfrac{1}{2}\fe^\top \dot{\rbM}\fe
         \\
@@
 However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
-\MSRY{여기서는 MVT, IFT을 사용하지 않았기 때문에 아이디얼 제어가 포화되지 않을 필요성이 없다. 실험에서도 포화를 핸들링하는 중에 추종이 완벽히 되지 못하는 것을 보인다.}
 
@@
     \caption{
-        Architecture of the DNN $\NN({\q}_n;\wth)$ with $2$ hidden layers.
+        Architecture of the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3,l_3=2$.
     }
@@
 In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
-Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and $\act^{*'}_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
-Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i:=\act_i(\hat\NN_{i-1})$ and $\hat\act_i':= \pptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.
+Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \pptfrac{\estact_i}{\estNN_{i-1}}$, respectively.
 
@@
     =
-    ((\pptfrac{\fe}{\rbu})(\pptfrac{\rbu}{\estwth}))^\top \fe
-    =
-    ((\pptfrac{\fe}{\rbu})(\pptfrac{\estNN}{\estwth}))^\top \fe
+    \left(
+        (\pptfrac{\fe}{\rbu})
+        (\pptfrac{\rbu}{\estwth})
+    \right)
+    ^\top \fe
+    =
+    \left(
+        (\pptfrac{\fe}{\rbu})
+        (\pptfrac{\estNN}{\estwth})
+    \right)
+    ^\top \fe
 $). 
@@
     \tfrac{1}{2}
-    (
+    \left(
         \Vert \estwth_i\Vert^2 
@@
         \overline\theta_i^2 
-    )    
+    \right)    
     \le 0
@@
         (
-            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
             \fe
@@
         \underbrace{
-            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
+            \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
         }_{:=c_1\in\R_{>0}}
@@
         -\estwth_k^\top (
-            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
+            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
             \fe
@@
         \vfill
-    \subfloat[Norm of control input $\tau$.]{
+    \subfloat[Norm of control input $\rbu$.]{
         \includegraphics[width=\figSizeTwoCol\linewidth]
@@
     \hfill
-    \subfloat[Norm of weights $\hat\theta_i$.]{
+    \subfloat[Norm of weights ${\estwth}_i$.]{
         % \includegraphics
@@
 % beta + zeta
-For the cases of (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\widehat{ \mv{\theta}}_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
+For the cases of (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\estwth_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
 % comparison; big, small beta
 For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for convex constraint $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
-With the bigger $\lambda_j$, the adaptation of $\widehat{ \mv{\theta}}_1$ is more assertive than that with smaller $\lambda_j$.
+With the bigger $\lambda_j$, the adaptation of $\estwth_1$ is more assertive than that with smaller $\lambda_j$.
 This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but this also causes oscillation in the adaptation process.
 In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_j$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_j,\ \forall j\in\mathcal I$ was satisfied and violated, respectively, in the discrete time implementation.
-Besides, with small $\lambda_j$, the adaptation direction of $\widehat{ \mv{\theta}}_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
+Besides, with small $\lambda_j$, the adaptation direction of $\estwth_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
 This allows the controller to show a smoother control input.

### 2025-04-18 src/measurement/animate.m

@@ -2,7 +2,7 @@ clear
 figure(1); close
 figure(1);
 
-AINMATION_SAVE_FLAG = 1;
+AINMATION_SAVE_FLAG = 0;
 video_name = "sample";
 gray = "#808080";
 
@@ -12,27 +12,27 @@ more_red = "#A2142F";
 line_width = 1.5;
 font_size = 12;
 T = 24;
-
+accel = 10;
 %% 
-ctrl1_name = "2025_04_09_13_30"; % CoNAC
-ctrl2_name = "2025_04_09_13_30"; % Aux.
-ctrl3_name = "2025_04_09_13_30"; % CoNAC 2.
-ctrl4_name = "2025_04_09_13_30"; % CoNAC 2.
+ctrl1_name = "c1 1.trc"; % CoNAC
+ctrl2_name = "c1 2.trc"; % Aux.
+ctrl3_name = "c1 1.trc"; % CoNAC 2.
+ctrl4_name = "c1 3.trc"; % CoNAC 2.
 
 %%
-data1 = post_procc(ctrl1_name, 4);
-data2 = post_procc(ctrl2_name, 4);
-data3 = post_procc(ctrl3_name, 4);
-data4 = post_procc(ctrl4_name, 4);
+data1 = trc2data(ctrl1_name, 1);
+data2 = trc2data(ctrl2_name, 1);
+data3 = trc2data(ctrl3_name, 1);
+data4 = trc2data(ctrl4_name, 1);
 
-c1 = "blue"; c2="cyan"; c3=gray; c4="yellow";
+c1 = "blue"; c2="cyan"; c3=gray; c4=[1 0.5 1 ];
 th_max = [11 12 13];
 u_ball = 12;
 u_max1 = 10;
 u_max2 = 3;
 
 %%
-dt = data1.t(2) - data1.t(1);
+dt = data1.q1.Time(2) - data1.q1.Time(1);
 
 %%
 L1 = .45;            
@@ -42,35 +42,27 @@ L2 = .45;
 if AINMATION_SAVE_FLAG
     v = VideoWriter("sim_result/"+video_name, 'MPEG-4');
     % v.Quality = 100;
-    v.FrameRate = 1/dt; 
+    v.FrameRate = 1/dt/accel; 
     open(v);
 end
 
 %% ANIMATE
-for t = 0:dt:T
-    pause(0.001)
-    clf
+for t = 0:dt*accel:T
[…]

### 2025-04-18 src/measurement/indv_animate.m

@@ -1,0 +1,168 @@
+clear
+figure(1); close
+figure(1);
+
+AINMATION_SAVE_FLAG = 0;
+video_name = "sample";
+gray = "#808080";
+
+more_blue = "#0072BD";
+more_red = "#A2142F";
+
+line_width = 1.5;
+font_size = 12;
+T = 24;
+
+%% 
+ctrl1_name = "2025_04_09_13_30"; % CoNAC
+
+%%
+data1 = post_procc(ctrl1_name, 4);
+
+c1 = "blue"; 
+th_max = [11 12 13];
+u_ball = 12;
+u_max1 = 10;
+u_max2 = 3;
+
+%%
+dt = data1.t(2) - data1.t(1);
+
+%%
+L1 = .45;            
+L2 = .45;
+
+%% SAVE VIDEO
+if AINMATION_SAVE_FLAG
+    v = VideoWriter("sim_result/"+video_name, 'MPEG-4');
+    % v.Quality = 100;
+    v.FrameRate = 1/dt; 
+    open(v);
+end
+
+%% ANIMATE
+for t = 0:dt:T
+    pause(0.001)
+    clf
+
+    t_idx1 = find(data1.t >= t, 1);
+
+    q1_c1 = data1.x1(1, t_idx1); q2_c1 = data1.x1(2, t_idx1);
+
+    r1 = data1.xd1(1, t_idx1); r2 = data1.xd1(2, t_idx1);
+
+    plot( ...
+        L1* [0 cos(r1), cos(r1)+cos(r1+r2)], ...
+        L1* [0 sin(r1), sin(r1)+sin(r1+r2)], ...
+        "Color", "red", ...c
+        "LineStyle","--", ...
+        "Marker","o", ...
+        "LineWidth", line_width ...
+        ); hold on
+
+    plot( ...
+        L1* [0 cos(q1_c1), cos(q1_c1)+cos(q1_c1+q2_c1)], ...
+        L1* [0 sin(q1_c1), sin(q1_c1)+sin(q1_c1+q2_c1)], ...
+        "Color", c1, ...
+        "LineStyle","-", ...
+        "Marker","o", ...
+        "LineWidth", line_width ...
+        ); hold on
+
+    % time 
+    text(.25,.85,0, ...
+        sprintf( ...
+            'Time: %.2f/%.0f s (%.1f%%) ', t, T, round(t/T*100, 3) ...
+        ), ...
+        "FontSize", font_size, ...
+        "FontName", "Times New Roman" ...
+        );
+    grid on
[…]

### 2025-04-18 src/measurement/indv_main_plotter.m

@@ -1,0 +1,342 @@
+clear
+
+%%
+SAVE_FLAG = 0;
+POSITION_FLAG = 1; % it will plot fiugures in the same position
+TEX_CONVERT_FLAG = 0;
+gray = "#808080";
+
+more_blue = "#0072BD";
+more_red = "#A2142F";
+
+%%
+font_size = 18;
+line_width = 1.5;
+lgd_size = 16;
+    
+fig_height = 200;
+fig_width = 400;
+
+fig_unit = 'pixels';
+
+%% 
+ctrl1_name = "c1 1.trc";
+
+%%
+ctrl_num = 1;
+% data1 = post_procc(ctrl1_name, ctrl_num);
+data1 = trc2data(ctrl1_name, ctrl_num);
+
+c1 = "blue";
+th_max = [8 7 6];
+u_ball = 11.5;
+u_max1 = 10.7819;
+u_max2 = 4;
+
+%%
+ep_time = 12; T = ep_time * 2;
+
+start_t = 19;
+end_t = 21;
+
+%% FIG. 1; STATE 1
+figure(1); clf;
+hF = gcf; 
+hF.Units = fig_unit;
+hF.Position(3:4) = [fig_width, fig_height];
+
+plot(data1.q1.Time, data1.q1.Data, "Color", c1, "LineWidth", line_width, "LineStyle", "-"); hold on
+
+plot(data1.r1.Time, data1.r1.Data, "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
+
+plot([ep_time ep_time], [-5e1 5e1], "Color", "black", "LineWidth", line_width, "LineStyle", "-."); hold on
+text(.2, -1.8, "Episode 1", "FontSize", font_size, "FontName", 'Times New Roman')
+text(ep_time+.2, -1.8, "Episode 2", "FontSize", font_size, "FontName", 'Times New Roman')
+
+grid on; grid minor;
+xlabel('Time / s', 'FontSize', font_size, 'Interpreter', 'latex');
+ylabel('$q_1$ / rad', 'FontSize', font_size, 'Interpreter', 'latex');
+maxVal = max(data1.r1.Data); minVal = min(data1.r1.Data); 
+len = maxVal-minVal; ratio = .3;
+ylim([minVal-len*ratio maxVal+len*ratio]);
+xlim([0 T])
+    ax = gca;
+    ax.FontSize = font_size; 
[…]

### 2025-04-18 src/measurement/main_plotter.m

@@ -37,10 +37,16 @@ ctrl3_name = "2025_04_09_13_30"; % CoNAC 2.
 ctrl4_name = "2025_04_09_13_30"; % CoNAC 2.
 
 %%
-data1 = post_procc(ctrl1_name, 4);
-data2 = post_procc(ctrl2_name, 4);
-data3 = post_procc(ctrl3_name, 4);
-data4 = post_procc(ctrl4_name, 4);
+% data1 = post_procc(ctrl1_name, 4);
+% data2 = post_procc(ctrl2_name, 4);
+% data3 = post_procc(ctrl3_name, 4);
+% data4 = post_procc(ctrl4_name, 4);
+
+data1 = trc2data(ctrl1_name, 1);
+data2 = trc2data(ctrl2_name, 2);
+data3 = trc2data(ctrl3_name, 3);
+data4 = trc2data(ctrl4_name, 4);
+
 
 c1 = "blue"; c2="cyan"; c3=gray; c4="yellow";
 th_max = [11 12 13];
@@ -54,26 +60,21 @@ ep_time = 12; T = ep_time * 2;
 start_t = 19;
 end_t = 21;
 
-focus_c1 = find(data1.t >= start_t & data1.t <= end_t);
-focus_c2 = find(data2.t >= start_t & data2.t <= end_t);
-focus_c3 = find(data3.t >= start_t & data3.t <= end_t);
-focus_c4 = find(data4.t >= start_t & data4.t <= end_t);
-
 %% FIG. 1; STATE 1
 figure(1); clf;
 hF = gcf; 
 hF.Units = fig_unit;
 hF.Position(3:4) = [fig_width, fig_height];
 
-plot(data4.t(data4.obs), data4.xd1(1,data4.obs), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
-plot(data3.t(data3.obs), data3.xd1(1,data3.obs), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
-plot(data2.t(data2.obs), data2.xd1(1,data2.obs), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
-plot(data1.t(data1.obs), data1.xd1(1,data1.obs), "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
+plot(data4.r1.Time, data4.r1.Data, "Color", "red", "LineWidth", line_width, "LineStyle", "--"); hold on
[…]

### 2025-04-22 manuscript.tex
convert to ieee journal

@@
-%% 
-%% Copyright 2007-2025 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.3 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.3 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-
-% \documentclass[preprint,12pt,authoryear]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times,authoryear]{elsarticle}
-% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
-% \documentclass[final,3p,times,authoryear]{elsarticle}
-% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
-% \documentclass[final,5p,times,authoryear]{elsarticle}
-\documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-% \usepackage{balance}
+\documentclass[lettersize,journal]{IEEEtran}
+
 \def\pub{false} % true for publication, false for draft
 \newcommand*{\template}{template}
-\input{\template/preamble/preamble_Elsevier.tex}
+\input{\template/preamble/preamble_journal.tex}
 
@@
 
-% %% The amssymb package provides various useful mathematical symbols
-% \usepackage{amssymb}
-% %% The amsmath package provides various useful equation environments.
-% \usepackage{amsmath}
-% %% The amsthm package provides extended theorem environments
-% %% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-\journal{Nuclear Physics B}
+\addbibresource{\template/refs.bib}
 
 \begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \affiliation for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \affiliation{organization={},
-%%            addressline={}, 
-%%            city={},
-%%            postcode={}, 
-%%            state={},
-%%            country={}}
-%% \fntext[label3]{}
 
@@
 
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \affiliation[label1]{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-%%
-%% \affiliation[label2]{organization={},
-%%             addressline={},
-%%             city={},
-%%             postcode={},
-%%             state={},
-%%             country={}}
-
 \author{
   Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
-} %% Author name
-
-%% Author affiliation
-\affiliation{organization={
-  Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST)
-},%Department and Organization
-            addressline={123 Cheomdangwagi-ro, Buk-gu}, 
-            city={Gwangju},
-            postcode={61005}, 
-            % state={},
-            country={Korea}}
+\thanks{
+    Myeongseok Ryu, Donghwa Hong and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: \{dding\_98, ???, khchoi\}@gist.ac.kr).
+
+    This work was supported in part by a Korea Research Institute for Defense Technology planning and advancement (KRIT) grant funded by Korea government DAPA (Defense Acquisition Program Administration) (No.
+KRIT-CT-22-087, Synthetic Battlefield Environment based Integrated Combat Training Platform) and in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (RS-2025- 00554087).
+(Corresponding author: Kyunghwan Choi)
+    }}
+
+\markboth{Journal of \LaTeX\ Class Files,~Vol.~18, No.~9, September~2020}%
+{How to Use the IEEEtran \LaTeX \ Templates}
+
+\maketitle
 
@@
 
-%%Graphical abstract
-\begin{graphicalabstract}
-%\includegraphics{grabs}
-\end{graphicalabstract}
-
-%%Research highlights
-\begin{highlights}
-\item Research highlight 1
-\item Research highlight 2
-\end{highlights}
-
-%% Keywords
-\begin{keyword}
-Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep input constraint
-
-%% keywords here, in the form: keyword \sep keyword
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%% Add \usepackage{lineno} before \begin{document} and uncomment 
-%% following line to enable line numbers
-%% \linenumbers
-
-%% main text
-%%
+\begin{IEEEkeywords}
+    Neuro-adaptive control, constrained optimization, deep neural network, input constraint.
+\end{IEEEkeywords}
 
@@
 
-Many engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
+\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
 These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
@@
 
-Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
+Therefore, addressing these two key issues—eensuring weight boundedness and satisfying input constraints—is essential for th reliable design of neuro-adaptive controllers. 
 he following section will provide a detailed review of the existing solutions to these challenges.
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
     \centering
-    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
+    \includegraphics[width=.69\linewidth]{src/figures/Controller.drawio.pdf}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
     \label{fig:ctrl:diagram}
-\end{figure}
+\end{figure*}
 
@@
     \centering
-    \begin{tabular}{c m{6.5em} c c c }
+    \begin{tabular}{c m{9.5em} c c c }
     % \begin{tabular}{c c c c c}
@@
 
-%% If you have bib database file and want bibtex to generate the
-%% bibitems, please use
-%%
-\bibliographystyle{elsarticle-harv} 
-\bibliography{\template/refs}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-%% Refer following link for more details about bibliography and citations.
-%% https://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
-
-% \bibliographystyle{elsarticle-harv}
-% % \bibliography{}
-% \bibliography{\template/refs}
+\printbibliography
+
+% \begin{IEEEbiographynophoto}{Jane Doe}
+%     Biography text here without a photo.
+% \end{IEEEbiographynophoto}
+
+\begin{IEEEbiography}[{
+    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/msRyu.jpg}}]{IEEE Publications Technology Team}
+    In this paragraph you can place your educational, professional background and research and other interests.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{
+    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/dhHong.jpg}}]{IEEE Publications Technology Team}
+    In this paragraph you can place your educational, professional background and research and other interests.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{
+    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/khChoi.jpg}}]{IEEE Publications Technology Team}
+    In this paragraph you can place your educational, professional background and research and other interests.
+\end{IEEEbiography}
 
 \end{document}
-
-\endinput
-%%
-%% End of file `elsarticle-template-harv.tex'.

### 2025-04-22 presentation/presentation.tex
ppt update logo
ppt minor update

@@
 % Inbuilt themes in beamer
-\documentclass{beamer}
+\documentclass[aspectratio=169]{beamer}
 
@@
 \usetheme{Antibes}
-\usecolortheme{beaver}
+% \usecolortheme{beaver}
 
@@
 } 
-\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, \and Kyunghwan Choi\inst{1}}
+\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}}
 \date{\today}
@@
 \logo{
-    \includegraphics[height=1cm]{../template/figs/logo_GIST.png}
+    \includegraphics[height=0.4cm]{logo_KAIST.png}
+    \hspace{.5cm}%
+    \includegraphics[height=0.4cm]{logo_KAIST.png}
+}
+
+\AtBeginSection[]{%
+  \frame<beamer>{ 
+    \frametitle{Outline}   
+    \tableofcontents[currentsection] 
+  }
 }
@@
 
-% Remove logo from the next slides
-\logo{}
-
 % Outline frame
@@
 % Lists frame
-\section{Lists in Beamer}
-\begin{frame}{Lists in Beamer}
+\section{Background and Contributions}
 
-This is an unordered list:
-\begin{itemize}
-    \item Item 1
-    \item Item 2
-    \item Item 3
-\end{itemize}
+\subsection{Introduction to Neuro–Adaptive Control}
 
-and this is an ordered list:
-\begin{enumerate}
-    \item Item 1
-    \item Item 2
-    \item Item 3
-\end{enumerate}
+\begin{frame}{Introduction to Neuro–Adaptive Control}
 
-\end{frame}
-
-% Blocks frame
-\section{Blocks in Beamer}
-\begin{frame}{Blocks in Beamer}
     \begin{block}{Standard Block}
@@
     \end{exampleblock}
+
+\end{frame}
+
+\subsection{Limitations of Neuro–Adaptive Control}
+
+\begin{frame}
+
+\end{frame}
+
+\section{Proposed Method}
+\subsection{Weight Norm Constraint}
+\begin{frame}{Weight Norm Constraint}
+    \begin{block}{Weight Norm Constraint}
+        \begin{itemize}
+            \item This is a list item.
+            \item This is another list item.
+        \end{itemize}
+    \end{block}
+\end{frame}
+
+\section{Numerical Validation}
+
+\subsection{Simulation Setup}
+\begin{frame}{Weight Norm Constraint}
+    \begin{block}{Weight Norm Constraint}
+        \begin{itemize}
+            \item This is a list item.
+            \item This is another list item.
+        \end{itemize}
+    \end{block}
+\end{frame}
+
+\subsection{Simulation Results}
+\begin{frame}{Weight Norm Constraint}
+    \begin{block}{Weight Norm Constraint}
+        \begin{itemize}
+            \item This is a list item.
+            \item This is another list item.
+        \end{itemize}
+    \end{block}
+\end{frame}
+
+\section{Conclusion}
+
+\subsection{Conclusion and Future Work}
+\begin{frame}{Conclusion}
+    \begin{block}{Weight Norm Constraint}
+        \begin{itemize}
+            \item This is a list item.
+            \item This is another list item.
+        \end{itemize}
+    \end{block}
+\end{frame}
+
+\section{}
+\begin{frame}{}
+    \centering \Large
+    \emph{Thank you for your attention!}
 \end{frame}

### 2025-04-23 manuscript.tex
readme update

@@
 \thanks{
-    Myeongseok Ryu, Donghwa Hong and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: \{dding\_98, ???, khchoi\}@gist.ac.kr).
+    Myeongseok Ryu is with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr).
+
+    Donghwa Hong is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: ???@gist.ac.kr).
+
+    Kyunghwan Choi is with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: khchoi@kaist.ac.kr).
 
@@
   The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
-  Real-time implementation was conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
+  The proposed controller was validated via real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
 \end{abstract}
@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
+    \item $\myvec(\mm A):= \left(\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  \right)^\top   $ for $\mm A\in\R^{n\times m}$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.

### 2025-04-24 manuscript.tex
minor change

@@
 where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
-    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
+    \mv f:= \mv f(\q,\dq,\qd,\dqd,\ddqd)
     =
@@
         &
-        i\in[1,\dots,k],
+        i\in\{1,\dots,k\},
         \\
@@
             \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
-        }_{:=c_1\in\R_{>0}}
+        }_{=:c_1\in\R_{>0}}
         \norm{\fe}
@@
         \estwth_k^\top \pptfrac{c_j}{\estwth_k}
-        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        }_{=: c_2 \in\R_{>0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
         \\
@@
     \hline 
-    $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
+    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
     \hline
@@
     \hline
-    $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
-    \hline
-    ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
+    $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
+    \hline
+    ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
     \hline
@@
 \end{table}
+
+% \begin{table}[t]
+%     \renewcommand{\arraystretch}{1.3}
+%     \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
+%     \centering
+%     \begin{tabular}{c m{9.5em} c c c }
+%     % \begin{tabular}{c c c c c}
+%     \hline
+%     \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+%     \hline
+%     \hline 
+%     $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
+%     \hline
+%     $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
+%     \hline
+%     ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
+%     \hline
+%     $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
+%     \hline
+%     ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
+%     \hline
+%     ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
+%     \hline
+%     $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
+%     \hline
+%     \end{tabular}
+%     \label{table:system:params}
+% \end{table}
 
@@
     \hline
-        (C$_1$)\!&\!proposed\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
+        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
     \hline
@@
     \hline
-        (C$_3$)\!&\!small $\beta_i$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
+        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
     \hline
@@
         {
-            src/script_simulation/figures/compare/Fig9.eps
+            src/measurement/figures/Fig10.eps
         }%

### 2025-05-02 manuscript.tex
new measurement result

@@
 
-The proposed CONAC was validated via real-time experiment on a two-link manipulator.
-
 \subsection{Validation Setup}
@@
 To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
-The OpenCR1.0 \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
+The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
 \color{red}
 The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
-The servos were controlled using the OpenCR1.0 board, which was connected to a computer via USB. 
-The reference trajectory was generated using the same method as in the numerical simulation.
+The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
 \color{black}
-
-% ------------------------------------
-% Robot Model and Ref. Trajectory
-% ------------------------------------
-The two-link manipulator model is depicted in Fig.~\ref{fig:robot:model}, adapted from \cite{Markus:2013aa}. 
-\MSRY{CORRECT HERE}
-The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, and for the numerical validation, the parameters are assumed to be constant such that $\rbM=\mydiag([m_1,m_2])$, $\rbVm=\mydiag([b_1,b_2])$, and $\rbF=\mydiag([f_{c_1},f_{s_1},f_{c_2},f_{s_2}])$,
-where the parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p,{f_c}_p$ and ${f_s}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous friction coefficient, coulomb friction coefficient, and static friction coefficient, respectively, for link $p\in[1,2]$.
-The values of the system model parameters are provided in Table~\ref{table:system:params}.
+The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.
 
@@
         % fig/Fig1.pdf
-        src/script_simulation/figures/compare/Fig1.eps
+        src/measurement/figures/compare/Fig1.eps
       }%
@@
       {
-        % src/script_simulation/figures/compare/Fig11.eps
-        src/script_simulation/figures/compare/Fig2.eps
+        % src/measurement/figures/compare/Fig11.eps
+        src/measurement/figures/compare/Fig2.eps
       }%
@@
         {
-            src/script_simulation/figures/compare/Fig3.eps
+            src/measurement/figures/compare/Fig3.eps
         }%
@@
         {
-            src/script_simulation/figures/compare/Fig4.eps
+            src/measurement/figures/compare/Fig4.eps
         }%
@@
         {
-            src/script_simulation/figures/compare/Fig5.eps
+            src/measurement/figures/compare/Fig5.eps
         }%
@@
             % fig/Fig7.pdf
-            src/script_simulation/figures/compare/Fig7.eps
+            src/measurement/figures/compare/Fig7.eps
         }%
@@
         {
-            src/script_simulation/figures/compare/Fig6.eps
+            src/measurement/figures/compare/Fig6.eps
         }%
@@
         {
-            src/script_simulation/figures/compare/Fig8.eps
+            src/measurement/figures/compare/Fig8.eps
         }%
@@
         {
-            src/script_simulation/figures/compare/Fig9.eps
+            src/measurement/figures/compare/Fig9.eps
         }%
@@
 % Norm of error in Episode 1: 
-% C1 r1 ep1: 0.389
-% C1 r2 ep1: 0.426
-% C2 r1 ep1: 0.403
-% C2 r2 ep1: 0.456
-% C3 r1 ep1: 0.370
-% C3 r2 ep1: 0.427
+% C1 e1 ep1: 0.025
+% C1 e2 ep1: 0.023
+% C2 e1 ep1: 0.022
+% C2 e2 ep1: 0.011
+% C3 e1 ep1: 0.023
+% C3 e2 ep1: 0.013
+% C4 e1 ep1: 0.024
+% C4 e2 ep1: 0.013
 % Norm of error in Episode 2: 
-% C1 r1 ep2: 0.155
-% C1 r2 ep2: 0.066
-% C2 r1 ep2: 0.191
-% C2 r2 ep2: 0.094
-% C3 r1 ep2: 0.141
-% C3 r2 ep2: 0.083
+% C1 e1 ep2: 0.008
+% C1 e2 ep2: 0.003
+% C2 e1 ep2: 0.008
+% C2 e2 ep2: 0.002
+% C3 e1 ep2: 0.008
+% C3 e2 ep2: 0.004
+% C4 e1 ep2: 0.020
+% C4 e2 ep2: 0.004
 % Improvement in Episode 2: 
-% C1 r1: 0.602
-% C1 r2: 0.845
-% C2 r1: 0.527
-% C2 r2: 0.793
-% C3 r1: 0.619
-% C3 r2: 0.805
+% C1 e1: 0.700
+% C1 e2: 0.884
+% C2 e1: 0.631
+% C2 e2: 0.769
+% C3 e1: 0.637
+% C3 e2: 0.728
+% C4 e1: 0.185
+% C4 e2: 0.671
 % ------------------------------------
@@
         {
-            src/measurement/figures/Fig10.eps
+            src/measurement/figures/compare/Fig10.eps
         }%

### 2025-05-02 src/measurement/main_plotter.m

@@ -1,13 +1,14 @@
 clear
 
 %%
-SAVE_FLAG = 0;
+SAVE_FLAG = 1;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
 TEX_CONVERT_FLAG = 0;
 gray = "#808080";
 
 more_blue = "#0072BD";
 more_red = "#A2142F";
+
 
 %%
 if TEX_CONVERT_FLAG
@@ -31,16 +32,10 @@ else
 end
 
 %% 
-ctrl1_name = "2025_04_09_13_30"; % CoNAC
-ctrl2_name = "2025_04_09_13_30"; % Aux.
-ctrl3_name = "2025_04_09_13_30"; % CoNAC 2.
-ctrl4_name = "2025_04_09_13_30"; % CoNAC 2.
-
-%%
-% data1 = post_procc(ctrl1_name, 4);
-% data2 = post_procc(ctrl2_name, 4);
-% data3 = post_procc(ctrl3_name, 4);
-% data4 = post_procc(ctrl4_name, 4);
+ctrl1_name = "c1.trc"; 
+ctrl2_name = "c2.trc";
+ctrl3_name = "c3.trc"; 
+ctrl4_name = "c4.trc"; 
 
 data1 = trc2data(ctrl1_name, 1);
 data2 = trc2data(ctrl2_name, 2);
@@ -48,17 +43,29 @@ data3 = trc2data(ctrl3_name, 3);
 data4 = trc2data(ctrl4_name, 4);
 
 
-c1 = "blue"; c2="cyan"; c3=gray; c4="yellow";
-th_max = [11 12 13];
-u_ball = 12;
-u_max1 = 10;
-u_max2 = 3;
+c1 = "blue"; c2="cyan"; c3=gray; c4="magenta";
+th_max = [5 5.5 6];
+u_ball = 11;
+u_max2 = 3.5;
+u_max1 = sqrt(u_ball^2 - u_max2^2);
+
 
 %%
+idleTime1 = 3+8;
+idleTime2 = 4;
+
 ep_time = 12; T = ep_time * 2;
 
-start_t = 19;
-end_t = 21;
+start_t = 29.4;
+end_t   = 31.9;
+
+% general_lim = [start_t end_t];
+general_lim = [idleTime1 idleTime1+T];
+
+focus_c1 = find(data1.u1.Time >= start_t & data1.u1.Time <= end_t);
[…]

### 2025-05-02 manuscript.tex
Refactor code structure for improved readability and maintainability

@@
 The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
-\color{red}
-The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
+\DHHO{
+The experimental setup consisted of a two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
 The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
-\color{black}
+}
 The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.
@@
     \hline
-    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
-    \hline
-    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
+    $l_p$  & Length & \multicolumn{2}{c}{0.2 (m)} \\  
+    \hline
+    ${l_c}_p$ & Center of mass & \multicolumn{2}{c}{0.139 (m)} \\
     \hline
@@
     \hline
-    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
+    $I_p$  & Inertia & \multicolumn{2}{c} {0.069 (kgm\textsuperscript{2})} \\
     \hline
@@
 \end{equation}
-where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
+where ${\qd}_0:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
 To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.
@@
             \norm{\rbu} \le 
-            10
+            11
             % \overline\tau
@@
             \vert{\tau_2}\vert \le 
-            2.5
+            3.5
             % \overline\tau_2
@@
 \end{equation}
-where $\overline\tau_2=-\underline{\tau}_2=2.5$ are the absolute bound of the second link actuator, and $\overline\tau=10$ is the maximum feasible norm of the control input.
+where $\overline\tau_2=-\underline{\tau}_2=3.5$ are the absolute bound of the second link actuator, and $\overline\tau=11$ is the maximum feasible norm of the control input.
 Hence, (C$_1$) is possible to use full capability of the actuator.
@@
 
-The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.
+The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{0},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10^{1}$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.
 
@@
 \tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
-Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$).
+Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$).
 
@@
 
-The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
+The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([800,800])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
 \MSRY{sensitivity와 convergence에 대해서 더 설명이 필요한가?}
@@
 
-To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=1$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.
+To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=10^{-1}$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{0}$.
 The remaining parameters are the same as (C$_1$).
@@
 For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
-The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
-Each NN architecture had two hidden layers with four nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
+The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.5,0.5]$, and the same random seed.
+Each NN architecture had two hidden layers with four nodes \DHHO{k=2? (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$)}, and the adaptation gain was set to $\alpha=0.2$.
 The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
-The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.
+\DHHO{ simulation?
+    The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.}
 \MSRY{CAN Hz?}
@@
     \hline
-        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
-    \hline
-        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
-    \hline
-        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
+        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+    \hline
+        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!10.428,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!3.5$\!\\
+    \hline
+        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
     \hline

### 2025-05-02 manuscript.tex
1. check the words "simulation" 2. paramters were fixed 3. add the comment for servo

@@
 \MSRY{CAN Hz?}
-To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.
+To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=5.0, \overline\wth_1=5.5$, and $\overline\wth_2=6.0$), avoiding the violation of the weight constraints.
 
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Properties of the controllers used in simulation}
+    \caption{Properties of the controllers used in \DHHO{sim? simulation}}
     \label{table:controller}
@@
     \caption{
-  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
+  \DHHO{sim?: Simulation} results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
   }
@@
 
-The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
+\DHHO{sim? The simulation} results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
 Across the two episodes, all controllers enhanced their tracking performances about 
@@
 \color{red}
-The KKT conditions defined in \cite[Def.
-@@]{Nocedal:2006aa} were satisfied in the simulation, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
+\DHHO{sim?: The KKT conditions defined in \cite[Def.
+@@]{Nocedal:2006aa} were satisfied in the simulation}, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
 \color{black}
@@
 \subsubsection{Computational Time}
-is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 0.5 ms, which is less than the sampling time of 4 ms. 
+is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 
+\DHHO{
+    3.4 ms?,} which is less than the sampling time of 4 ms. 
 This indicates that the proposed CONAC can be implemented in real-time applications.
@@
 
-Simulation results validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+\DHHO{sim?
+: Simulation results} validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
 CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.

### 2025-05-02 manuscript.tex
WIP: 67e45c6 new measurement result

@@
 \title{
-  Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints 
+    Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Euler-Lagrange Systems Under Weight and Input Constraints
 } %% Article title
@@
     \centering
-    \includegraphics[width=.69\linewidth]{src/figures/Controller.drawio.pdf}
+    \includegraphics[width=.55\linewidth]{src/figures/Controller.drawio.pdf}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
 % ------------------------------------
-The desired trajectory for $\q=\left(q_1,q_2\right)^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
+The desired trajectory for $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
 The desired trajectory is defined as follows:
@@
 
-% However, since the NN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
-% Hence, the reference trajectory was applied $2$ times by proportionally increasing the amplitude of the desired trajectory to the original ${\qd}_i,\ \forall i\in\{1,2\}$.
-% Let us call the $i\textsuperscript{th}$ iteration of the reference trajectory as Episode $i,\ \forall i\in\{1,2\}$.
+However, since the NN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
+Hence, in advance of the reference trajectory, the manipulator was initially positioned at ${\qd}^{\rm{origin}}=\left(-\tfrac{1}{2}\pi,0\right)^\top$ (\ie stable equilibrium point).
+Then, a reference trajectory was applied to the manipulator to move from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ which is the initial and final points of the episode.
+After the manipulator reached ${\qd}_0$, the constant reference trajectory $\qd={\qd}_0$ was applied for $t_f=8$ s to be steady and to avoid the effect of the transient response.
 
@@
 % ------------------------------------
-To demonstrate the effectiveness of the proposed CONAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
-%
+The effectiveness of the proposed CONAC to handle the combination of the convex input constraints was demonstrated by defining the saturation function which projects the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
 \begin{subequations}
@@
 \end{subequations}
-%
 These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
@@
 % ------------------------------------
-\subsubsection*{Controller 1: (C$_1$) CONAC; proposed}
-
-To handle the input saturation, the proposed CONAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
+\subsubsection*{Controller 1: (C$_1$) CONAC with large $\beta_j$}
+
+To handle the input saturation, the proposed CONAC was implemented with the input bound constraint \eqref{eq:cstr:input:bound} for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
 \begin{equation}
@@
     \tau_2-\overline\tau_2
-    \le 0
+    % \le 0
     ,
@@
     \underline\tau_2-\tau_2
-    \le 0
+    % \le 0
     ,
@@
     )^2 
-    <0
+    % <0
     ,
@@
 
-The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{0},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10^{1}$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.
+The update rate of the Lagrange multipliers was set to large values such that $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$, to investigate the effect of the large update rate of Lagrange multipliers.
+
+% ------------------------------------
+% Controllers: CONAC with small beta
+% ------------------------------------
+\subsubsection*{Controller 2: (C$_2$) CONAC with small $\beta_j$}
+
+As the second controller, the proposed CONAC was implemented with the same input bound constraint \eqref{eq:sim:cstr:CONAC} as (C$_1$), but with small $\beta_j$ values such that $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.
+The remaining parameters were the same as (C$_1$).
+
+% ------------------------------------
+% Controllers: CONAC without ctrl cstr
+% ------------------------------------
+\subsubsection*{Controller 3: (C$_3$) CONAC without control input constraints}
+
+The third controller was the same as (C$_1$) and (C$_2$), but without the control input constraints, to emphasize the control input constraint handling capability of the proposed CONAC.
+In this case, the update rate of the Lagrange multipliers regarding the control input constraints \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$ was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated.
+The remaining properties were the same as (C$_1$) and (C$_2$).
 
@@
 % ------------------------------------
-\subsubsection*{Controller 2: (C$_2$) CONAC with auxiliary system}
-
-On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
+\subsubsection*{Controller 4: (C$_4$) CONAC with auxiliary system instead of control input constraints}
+
+On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC.
 The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
-The auxiliary state $\mv{\zeta}$ is affected by the saturated control input $\Delta\rbu$, whose entry is defined as $\Delta\tau_{i} = 
+The auxiliary state $\mv{\zeta}$ is affected by the overflow amount of the control input $\Delta\rbu$, whose entries are defined as $\Delta\tau_{i} = 
 \tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
-Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$).
-
 The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
-Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$.
-
-The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([800,800])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
-\MSRY{sensitivity와 convergence에 대해서 더 설명이 필요한가?}
-
-% ------------------------------------
-% Controllers: CONAC with small beta
-% ------------------------------------
-\subsubsection*{Controller 3: (C$_3$) CONAC with small $\beta_i$}
-
-To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=10^{-1}$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{0}$.
-The remaining parameters are the same as (C$_1$).
-
-% ------------------------------------
-% Controllers: CONAC without ctrl cstr
-% ------------------------------------
-\subsubsection*{Controller 4: (C$_4$) CONAC without control input constraints}
-
-The controller 4 is the same as (C$_1$) but without the control input constraints, to show the effect of the control input constraints.
-In this case, the update rate of the Lagrange multipliers regarding the control input constraints \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$ was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated.
+Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.
+
+The matrices of the auxiliary system were set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed of the auxiliary system.
+Since, the auxiliary system only considers the saturation of each control input (\ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}), $\overline{\tau}_1$ was set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$).
 
@@
 % ------------------------------------
-For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
-The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.5,0.5]$, and the same random seed.
-Each NN architecture had two hidden layers with four nodes \DHHO{k=2? (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$)}, and the adaptation gain was set to $\alpha=0.2$.
+For all controllers ((C$_1$), (C$_2$), (C$_3$), and (C$_4$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
+Each NN architecture had two hidden layers with four nodes (\ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
 The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
-\DHHO{ simulation?
-    The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.}
-\MSRY{CAN Hz?}
-To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=5.0, \overline\wth_1=5.5$, and $\overline\wth_2=6.0$), avoiding the violation of the weight constraints.
-
-The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{r_1,r_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.
+The sampling rate of the controller was $250$ Hz considering the real-time implementation.
+The weight constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$. 
+The control results were collected via CAN communication with PCAN USB  and recorded in a computer with a sampling rate of $250$ Hz.
+
+The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.
 
@@
     \hline
-        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!10.428,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!3.5$\!\\
-    \hline
-        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
-    \hline
-        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
+        (C$_2$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
+    \hline
+        (C$_3$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
+    \hline
+        (C$_4$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
     \hline
@@
 \end{table}
-
-% ------------------------------------
-% Parameter Variation 
-% ------------------------------------
-% \begin{figure}[!t]      
-%     \centering
-%     {\includegraphics[width=\figSizeOneCol\linewidth]{
-%         src/measurement/figures/Fig11.eps
-%     }}
-% \caption{Box-and-Whisker plot of $L_2$-norms of the tracking performances and control input constraint violations of CONAC and CONAC-AUX across various parameter values.}
-%     \label{fig:ctrl:result:var}
-% \end{figure}
-
-% \begin{table}[!t]
-%     \renewcommand{\arraystretch}{1.3}
-%     \caption{Quantitative comparison of $L_2$-norms of the tracking performances and control input constraint violations.}
-%     \centering
-%     \begin{tabular}{c c c c}
-%     \hline
-%         \!&\!Maximum\!&\!Median\!&\!Minimum\!\\
-%     \hline
-%     \hline
-%     \textbf{CONAC}\!&\!$11.176\!\times\!10^{-3}$\!&\!$0.590\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
-%     \hline
-%     \textbf{CONAC-AUX}\!&\!$0.560\!\times\!10^{-3}$\!&\!$0.552\!\times\!10^{-3}$\!&\!$0.543\!\times\!10^{-3}$ \\
-%     \hline
-%     \end{tabular}
-%     \label{table:ctrl:result:var}
-% \end{table}
-
-% ------------------------------------
-% Controller Parameters
-% ------------------------------------
-% \begin{table}[t]
-%     \renewcommand{\arraystretch}{1.3}
-%     \caption{Parameters of the controllers used in simulation}
-%     \label{table:controller:params}
-%     \centering
-%     \begin{tabular}{c | c c c c c c c c c c c c c c}
-%     \hline
-%         & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\overline\theta_0$ & $\overline\theta_1$ & $\overline\theta_2$ & $\overline\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
-%     \hline
-%     \hline
-%         \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
-%     % \hline
-%         \bf{CONAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
-%     \hline
-%     \end{tabular}
-% \end{table}
 
@@
 % Norm of error in Episode 1: 
-% C1 e1 ep1: 0.025
-% C1 e2 ep1: 0.023
-% C2 e1 ep1: 0.022
-% C2 e2 ep1: 0.011
-% C3 e1 ep1: 0.023
-% C3 e2 ep1: 0.013
-% C4 e1 ep1: 0.024
-% C4 e2 ep1: 0.013
+% C1 e1 ep1: 25.013
+% C1 e2 ep1: 22.651
+% C2 e1 ep1: 21.719
+% C2 e2 ep1: 10.530
+% C3 e1 ep1: 23.168
+% C3 e2 ep1: 13.062
+% C4 e1 ep1: 24.195
+% C4 e2 ep1: 12.927
 % Norm of error in Episode 2: 
-% C1 e1 ep2: 0.008
-% C1 e2 ep2: 0.003
-% C2 e1 ep2: 0.008
-% C2 e2 ep2: 0.002
-% C3 e1 ep2: 0.008
-% C3 e2 ep2: 0.004
-% C4 e1 ep2: 0.020
-% C4 e2 ep2: 0.004
+% C1 e1 ep2: 7.513
+% C1 e2 ep2: 2.617
+% C2 e1 ep2: 8.021
+% C2 e2 ep2: 2.435
+% C3 e1 ep2: 8.408
+% C3 e2 ep2: 3.553
+% C4 e1 ep2: 19.721
+% C4 e2 ep2: 4.256
 % Improvement in Episode 2: 
@@
 	\hline
-		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
-	\hline
-        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
+		$e_1\times10^{3}$ & $25.013$ & $21.719$ & $23.168$ & $24.195$ \\
+	\hline
+        $e_2\times10^{3}$ & $22.651$ & $10.530$ & $13.062$ & $12.927$ \\
 	\hline
@@
 	\hline
-		$r_1$ & $0.389$ & $0.403$ & $0.370$ & $0.370$ \\ 
-	\hline
-        $r_2$ & $0.426$ & $0.456$ & $0.427$ & $0.370$ \\
+		$e_1\times10^{3}$ & $7.513$ & $8.021$ & $8.408$ & $19.721$ \\
+	\hline
+        $e_2\times10^{3}$ & $2.617$ & $2.435$ & $3.553$ & $4.256$ \\
     \hline
@@
 
+\subsection{Validation Results}
+
 % ------------------------------------
@@
 
-\DHHO{sim? The simulation} results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
-Across the two episodes, all controllers enhanced their tracking performances about 
-$60.2 \%$ for (C$_1$), $52.7 \%$ for (C$_2$), and $61.9 \%$ for (C$_3$) in $L_2$ norm of $r_1$, and $84.5 \%$ for (C$_1$), $79.3 \%$ for (C$_2$), and $80.5 \%$ for (C$_3$) in $L_2$ norm of $r_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
+The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
+Across the two episodes, all controllers enhanced their tracking performances about $70 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
 Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
@@
 \begin{IEEEbiography}[{
-    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/msRyu.jpg}}]{IEEE Publications Technology Team}
-    In this paragraph you can place your educational, professional background and research and other interests.
+    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/msRyu.jpg}}]{Myeongseok Ryu}
+    received the B.S.
+degree in mechanical engineering from Incheon National University, South Korea, in 2023, abd the M.S.
+degree in mechanical engineering from Gwangju Institute of Science and Technology (GIST), South Korea, in 2025.
+    He is currently pursuing the Ph.D. degree in mechanical engineering at GIST.
+    His research interests include adaptive control, neural-networks, and constrained optimization.
 \end{IEEEbiography}

### 2025-05-02 manuscript.tex
DH's comment remove

@@
 The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
-\DHHO{
-The experimental setup consisted of a two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
+The two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
 The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
-}
 The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.

### 2025-05-02 manuscript.tex
writing... use colored line

@@
     \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
-    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
+    \item A vector and matrix are denoted by $\mv{x}=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
         \mm A
@@
         }\allowbreak\in\R^{n\times m}
-        $ denote a vector and a matrix.
+        $, respectively.
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item $\myvec(\mm A):= \left(\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  \right)^\top   $ for $\mm A\in\R^{n\times m}$.
+    \item $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top$ for $\mm{A}\in\R^{n\times m}$, denotes vectorization of $\mm A$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
     \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
-The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
+The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions defined in \cite[Chap.
+12 Thm.
+12.1]{Nocedal:2006aa}.
     % \item The forward sensitivity method is applied in CONAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
@@
 
-The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
+The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see,][Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
 We introduce the following properties:
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=.55\linewidth]{src/figures/Controller.drawio.pdf}
+    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
     \in\R^{n \times \Xi}
-    \label{eq. nabla phi}
+    \label{eq:gradient:phi}
 \end{equation}
@@
     \hline
-    $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
-    \hline
-    ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
-    \hline
-    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
-    \hline
+    % $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
+    % \hline
+    % ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
+    % \hline
+    % ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
+    % \hline
     $I_p$  & Inertia & \multicolumn{2}{c} {0.069 (kgm\textsuperscript{2})} \\
@@
 The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
-Hence, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.
+Consequently, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.
 
@@
 The weight constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$.
+\MSRY{어차피 내부는 안걸리니까 그림 더 깔끔하게 다 6이라고 함} 
 The control results were collected via CAN communication with PCAN USB  and recorded in a computer with a sampling rate of $250$ Hz.
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Properties of the controllers used in \DHHO{sim? simulation}}
+    \caption{Properties of the controllers}
     \label{table:controller}
@@
     \caption{
-  \DHHO{sim?: Simulation} results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
+    Real-time implementation results of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid}, and reference signal $\qd$ \protect\colorLine{red}{dashed}.
   }
@@
     \centering
-    \subfloat[Control input $\tau$ in time interval from $19$ s to $21$ s (bird's eye view).]{
+    \subfloat[Control input $\tau$ in time interval from $29.4$ s to $31.9$ s (bird's eye view).]{
     % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
@@
         \vfill
-    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $19$ s to $21$ s.]{
+    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
         \includegraphics[width=\figSizeOneCol\linewidth]
@@
         \vfill
-    \subfloat[Auxiliary states in time interval from $19$ s to $21$ s.]{
+    \subfloat[Auxiliary states in time interval from $29.4$ s to $31.9$ s.]{
         \includegraphics[width=\figSizeOneCol\linewidth]
@@
   \caption{
-    Constraint handling process of (C$_1$) (blue), (C$_2$) (cyan), and (C$_3$) (gray) in time interval from $19$ s to $21$ s.
+    Constraint handling process of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid} in time interval from $29.4$ s to $31.9$ s.
   }
@@
 
-The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
+The real-time implementation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
 Across the two episodes, all controllers enhanced their tracking performances about $70 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
-Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
+Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode.
 This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
@@
 
-In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time interval from $7.5$ s to $8.5$ for Episode $1$, and from $19.5$ s to $20.5$ s for Episode $2$.
+In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time interval from $17.5$ s to $19.9$ for Episode $1$, and from $29.5$ s to $31.9$ s for Episode $2$.
 This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
-However,
-
-The tracking performance of CONAC, (\ie (C$_1$), and (C$_3$)), outperformed (C$_2$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
-This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$) was able to use the full capability of the actuator, while (C$_2$) was limited its first link actuator due to the feature of the auxiliary system.
+
+The tracking performances of CONAC with control input constraints, (\ie (C$_1$), and (C$_2$)), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
+This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
+The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).
 
@@
 % ------------------------------------
+\hfill
 \subsubsection{Constraint Handling} \label{sec:sim:constraint}
@@
 In this section, the constraint handling capability of all controllers are investigated.
-First, the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$ were not violated, as shown in Fig.~\ref{fig:ctrl:result:weight}, since the limits $\overline{\theta}_i,\ \forall i\in\{0,1,2\}$ were set sufficiently large.
-
-As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$) and (C$_3$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_2$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$, and auxiliary state $\mv{\zeta}$, respectively.
+
+\hfill
+
+As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$), and (C$_2$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_4$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$, and auxiliary state $\mv{\zeta}$, respectively.
 It is worth to note that the control input constraints were violated repeatedly, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
@@
 
-Even though all controllers satisfied the input saturation, (C$_2$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $19$ s to $21$ s.
-This is because, as aforementioned, the auxiliary system only considers the input bound constraint, and the control input bound constraint for first link was imposed to approximately match the maximum allowable norm of the control input $\overline\tau$, instead of $c_{\rbu}$.
-In contrast, (C$_1$) and (C$_3$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$.
+Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $29.4$ s to $31.9$ s.
+This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$, instead of $c_{\rbu}$.
+In contrast, (C$_1$), and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$.
 
@@
 % zeta
-The detail of the constraint handling in the time interval from $19$ s to $21$ s, is now investigated.
-First, for (C$_2$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. 
+The detail of the constraint handling in the time interval from $29.4$ s to $31.9$ s, is now investigated.
+First, for (C$_4$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. 
 As the weights were adapted to reduce not only $\fe$ but also $\mv{\zeta}$, the constraint violation of $c_{\overline\tau_1}$ was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
@@
 % beta + zeta
-For the cases of (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\estwth_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
+For the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\estwth_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
 % comparison; big, small beta
@@
 
+\hfill
+
+Finally, the weight norm constraints $c_{\theta_i},\ \forall i\in\mathcal I$ are investigated.
+The weight norm constraints were not activated except for the outer layer weights $c_{\theta_2}$ of (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}.
+This is because the weights of (C$_1$), (C$_2$), and (C$_4$) were suppressed by the control input constraints, while (C$_3$) was not.
+In addition, the inner and hidden layer weights constraints were not violated (\ie $\norm{\estwth_0},\norm{\estwth_1}$ were uniformly lower than $\norm{\estwth_2}$), since the backpropagated error was multiplied by the gradient of the activation function, which is limited from $-1$ to $1$, \ie see, \eqref{eq:gradient:phi}.
+
+The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
+In Fig.~\ref{fig:ctrl:result:scope:beta}, the Lagrange multipliers $\lambda_{\theta_2}$ were increased by the constraint violations, and the adaptation direction of the weights $\estwth_2$ was adjusted to reduce the constraint violations.
+
 % ------------------------------------
@@
 % ------------------------------------
+\hfill
 \subsubsection{Satisfaction of Karsh-Kuhn-Tucker (KKT) conditions}
 
-\color{red}
-\DHHO{sim?: The KKT conditions defined in \cite[Def.
-@@]{Nocedal:2006aa} were satisfied in the simulation}, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
-\color{black}
-
-\subsubsection{Computational Time}
-is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 
-\DHHO{
-    3.4 ms?,} which is less than the sampling time of 4 ms. 
-This indicates that the proposed CONAC can be implemented in real-time applications.
+\MSRY{ADD MORE DETAILS}
+
+The KKT conditions were satisfied in the simulation, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
+
+% ------------------------------------
+% Computational Time
+% ------------------------------------
+\hfill
+\subsubsection{Effectiveness of CONAC in Real-time Applications}
+
+The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time measured using CPU clock ticks.
+The computational times are shown in Fig.~\ref{fig:ctrl:real:result:cmp:time} indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz.
+In addition, it is notable that the computational time decreased as the weights converged.
 
@@
     \caption{
-        Computational time of CONAC and CONAC-AUX. 
+        Computational time of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, and (C$_4$) \protect\colorLine{magenta}{solid}.
     }
@@
 
-\DHHO{sim?
-: Simulation results} validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
+A real-time implementation validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
 CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
@@
     \begin{aligned}
-        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
+        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}}
         ,
         \quad
-        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
+        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)}
         ,
@@
             +\pptfrac{\estNN}{\estwth}
-        %     \\
-        % =&
+            \\
+        =&
         =
@@
         -\pptfrac{\estNN}{\estwth}
-        % \\
-        % =&
+        \\
+        =&
         =
@@
 \begin{equation}
-    c_{\rbu}=\norm{\mv{\tau}}^2 -\overline\tau^2  \le 0
+    c_{\rbu}=\norm{\mv{\tau}}^2 -\overline\tau^2
     ,
@@
     He is currently pursuing the Ph.D. degree in mechanical engineering at GIST.
+
     His research interests include adaptive control, neural-networks, and constrained optimization.

### 2025-05-02 src/measurement/main_plotter.m

@@ -381,7 +381,7 @@ plot(data2.cmp.Time, data2.cmp.Data, "color", c2, "LineWidth", line_width, "Line
 plot(data1.cmp.Time, data1.cmp.Data, "color", c1, "LineWidth", line_width, "LineStyle", "-"); hold on
 
 xlabel("Time / s", "Interpreter", "latex")
-ylabel("Cmp. Time / ms", "Interpreter", "latex")
+ylabel("Comp. Time / ms", "Interpreter", "latex")
 set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
 grid on 
 xlim(general_lim)

### 2025-05-03 src/measurement/animate.m
make animation; clear unused figures

@@ -2,7 +2,7 @@ clear
 figure(1); close
 figure(1);
 
-AINMATION_SAVE_FLAG = 0;
+AINMATION_SAVE_FLAG = 1;
 video_name = "sample";
 gray = "#808080";
 
@@ -11,13 +11,26 @@ more_red = "#A2142F";
 
 line_width = 1.5;
 font_size = 12;
-T = 24;
+ep_time = 12;
+T = 2*ep_time;
 accel = 10;
+idleTime1 = 3+8;
+idleTime2 = 4;
+
+animation_end_t = T + idleTime1;
+
+PhaseList = {
+    "Idle 1",
+    "Episode 1",
+    "Episode 2",
+    "Idle 2"
+};
+
 %% 
-ctrl1_name = "c1 1.trc"; % CoNAC
-ctrl2_name = "c1 2.trc"; % Aux.
-ctrl3_name = "c1 1.trc"; % CoNAC 2.
-ctrl4_name = "c1 3.trc"; % CoNAC 2.
+ctrl1_name = "c1.trc"; 
+ctrl2_name = "c2.trc";
+ctrl3_name = "c3.trc"; 
+ctrl4_name = "c4.trc"; 
 
 %%
 data1 = trc2data(ctrl1_name, 1);
@@ -25,11 +38,11 @@ data2 = trc2data(ctrl2_name, 1);
 data3 = trc2data(ctrl3_name, 1);
 data4 = trc2data(ctrl4_name, 1);
 
-c1 = "blue"; c2="cyan"; c3=gray; c4=[1 0.5 1 ];
-th_max = [11 12 13];
-u_ball = 12;
-u_max1 = 10;
-u_max2 = 3;
+c1 = "blue"; c2="cyan"; c3=gray; c4="magenta";
+th_max = [6 6 6];
+u_ball = 11;
+u_max2 = 3.5;
+u_max1 = sqrt(u_ball^2 - u_max2^2);
 
 %%
 dt = data1.q1.Time(2) - data1.q1.Time(1);
@@ -40,14 +53,14 @@ L2 = .45;
 
 %% SAVE VIDEO
 if AINMATION_SAVE_FLAG
-    v = VideoWriter("sim_result/"+video_name, 'MPEG-4');
+    v = VideoWriter("figures/"+video_name, 'MPEG-4');
     % v.Quality = 100;
     v.FrameRate = 1/dt/accel; 
     open(v);
 end
 
 %% ANIMATE
[…]

### 2025-05-03 src/measurement/main_plotter.m

@@ -1,7 +1,7 @@
 clear
 
 %%
-SAVE_FLAG = 1;
+SAVE_FLAG = 0;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
 TEX_CONVERT_FLAG = 0;
 gray = "#808080";
@@ -44,7 +44,7 @@ data4 = trc2data(ctrl4_name, 4);
 
 
 c1 = "blue"; c2="cyan"; c3=gray; c4="magenta";
-th_max = [5 5.5 6];
+th_max = [6 6 6];
 u_ball = 11;
 u_max2 = 3.5;
 u_max1 = sqrt(u_ball^2 - u_max2^2);

### 2025-05-03 src/measurement/trc2data.m

@@ -142,6 +142,12 @@ for data_idx = 1:length(data_names)
     data.(data_name).Time = data.(data_name).Time(start_idx:end_idx)-start_time;
 end
 
+%% OVERFLOW CORRECTION
+data.q1                 = pseudoEdit(data.q1, 2, -1.5);
+% data.q2                 = pseudoEdit(data.q2, 1.5, -3);
+data.r1                 = pseudoEdit(data.r1, 2, -1.5);
+% data.r2                 = pseudoEdit(data.r2, 1.5, -3);
+
 end
 
 %% LOCAL FUNCTIONS
@@ -187,5 +193,19 @@ function data = norm2ori(data, M, m)
 
     data = data * 1e3;
     data = .5*( (M-m)*data/bit_max + (M+m) );
+end
+
+function data = pseudoEdit(data, M, m)
+
+    idleTime1 = 3+8;
+    T = 24;
+
+    check_range = union(find(data.Time >= 35), find(data.Time <= 11));
+    % check_range = union(find(data.Time >= idleTime1+T), find(data.Time <= idleTime1));
+    edit_idx = setdiff(check_range, find(data.Data < 0));
+    % edit_idx = check_range;
+
+    data.Data(edit_idx) = data.Data(edit_idx) - (M-m);
+
 end
 

### 2025-05-03 manuscript.tex
make animation; clear unused figures
update drawio figures

@@
 \begin{abstract}
-  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for weight norm and convex input constraints. 
-  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while addressing both types of constraints. 
+  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems under weight norm and convex input constraints. 
+  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while learning the unknown system dynamics and,  addressing both types of constraints, simultaneously.
   The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. 
   The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
-  The proposed controller was validated via real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
+  The proposed controller was validated via a real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
 \end{abstract}
@@
 \begin{itemize}
-    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
+    \item $\otimes$ denotes the Kronecker product \cite[Chap. 7 Def. 7.1.2]{Bernstein:2009aa}.
     \item A vector and matrix are denoted by $\mv{x}=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
@@
 Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
-The candidates of input constraints are presented in \ref{sec:appen:cstr}.
+The candidates of input constraints are presented in Appendix \ref{sec:appen:cstr}.
 
@@
 
-Consider an uncertain Euler-Lagrange system modeled as
+We consider an uncertain Euler-Lagrange system modeled as
 \begin{equation}
@@
 \end{equation}
-where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the control input. 
-The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
+where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
+The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector and gravity vector
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
-\ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
-
-The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see,][Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
+Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.
+
+The Euler-Lagrange system \eqref{eq:sys1} satisfies some important physical properties \cite[Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
 We introduce the following properties:
@@
 \begin{prop} 
-    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $\dot{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\dot{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
+    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
     \label{prop:skew}
@@
 
-In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
-Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
+In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R_{\ge0} \to \R^n$, compensating for the unknown system dynamics while addressing the imposed constraints.
+The desired trajectory $\qd(t)$ is supposed to satisfy the following assumption:
 \begin{assum}
-    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \overline{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
+    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \overline{q}_d$ and available to design a bounded control input. 
+    \MSRY{수정이 필요할 수 있음}
     \label{assum:feasible}
@@
 The architecture of the proposed CONAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
-Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model.
-The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.
+Before we proceed to the controller design, we first revisit some mathematical preliminaries in Section \ref{sec:sub:math preliminaries}. 
+Then, we introduce the neuro-adaptive controller in Section \ref{sec:sub:NAC}, followed by the DNN model in Section \ref{sec:sub:NN definition}. 
+The constrained optimization-based weight adaptation laws will be presented in Section \ref{sec:adap_laws}.
 
@@
 
+\subsection{Mathematical Preliminaries}\label{sec:sub:math preliminaries}
+
+Later, the following proposition and lemma will be used in further sections:
+
+\begin{propsit}[see, {\cite[Chap. 7 Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
+	For matrix $\mm A\in\R^{n\times m}$ and vector $\mv b\in\mathbb R^n$, we have the following property
+	\begin{equation}
+		\mm A^\top \mv b 
+		= 
+		\myvec(\mm A^\top\mv b)
+		=
+		\myvec(\mv b^\top\mm A)
+		= 
+		(\mm{I}_{m}\otimes \mv b^\top) \myvec(\mm A)
+		.
+	\end{equation}
+\end{propsit}
+
+\begin{lem} \label{lem:stable:set}
+    For Lyapunov function $V:=V(\mv{x})\ge0$ with $\mv{x}\in\R^n$, if the time derivative of $V$ is given by $\ddtt V\le -a_1 \mv{x}^\top \mv{x} + a_2 \mv{x}$ for some positive constants $a_1\in\R$ and $a_2\in\R$, then $\mv{x}$ is bounded by $\mv{x}\in\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
+\end{lem}
+
+\begin{proof}
+    The time derivative of $V$ can be rewritten as
+    \begin{equation}
+        \ddtt V
+        \le
+        -a_1 \norm{\mv{x}}^2 + a_2 \norm{\mv{x}}
+        =
+        -a_1
+        \left(
+            \norm{\mv{x}}-\tfrac{a_2}{2a_1}
+        \right)^2
+        -
+        \tfrac{a_2^2}{4a_1}
+        .
+        \label{eq:lem:lya:dot}
+    \end{equation}
+    According to \eqref{eq:lem:lya:dot}, one can conclude that $\ddtt V$ is negative definite if $\norm{\mv{x}}\le\tfrac{a_2}{a_1}$ holds.
+    In other words, $\mv{x}$ remains within the bounded set $\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
+\end{proof}
+
 \subsection{Neuro-Adaptive Controller Design}\label{sec:sub:NAC}
@@
 \begin{equation}
-    \fe := \dot{\mv e}-\mm\Lambda \mv e
+    \fe := \ddtt{\mv e}-\mm\Lambda \mv e
     ,
@@
 \end{equation}
-where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}_{>0}$ is a user-designed filtering matrix.
+where $\mv e := \q - \qd$ denotes the tracking error, $\ddtt{\mv e} := \dq - \dqd$ represents the time derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}_{>0}$ is a user-designed filtering matrix.
 Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.
@@
 \begin{equation}
-    \rbM \dot\fe
+    \rbM \ddtt\fe
     =
@@
 \end{equation}
-where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
+where $\mm{K}=\mm{K}^\top\in\R^{n\times n}_{>0}$ denotes arbitrary unknown matrix and $
     \mv f:= \mv f(\q,\dq,\qd,\dqd,\ddqd)
@@
     \mm K \fe
-    +\rbM(-\ddqd+\mm\Lambda\dot{\mv e})
+    +\rbM(-\ddqd+\mm\Lambda\ddtt{\mv e})
     +
@@
 $ denotes the lumped system uncertainty.
+\color{red}
+The unknown matrix $\mm{K}$ is not available to design in practice, 
+\color{black}
 
@@
         +
-        \tfrac{1}{2}\fe^\top \dot{\rbM}\fe
+        \tfrac{1}{2}\fe^\top \ddtt{\rbM}\fe
         \\
@@
         \tfrac{1}{2}
-        \fe^\top \dot{\rbM}\fe
+        \fe^\top \ddtt{\rbM}\fe
         \\
@@
         \tfrac{1}{2}
-        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
+        \fe^\top(\ddtt{\rbM}- 2\rbVm)\fe
         \\
@@
         \fe^\top (\mv f+\mysat(\rbu))
-        \\
-        \le&
-        -\lambda_{\min}(\mm K)\norm{\fe}^2
-        +
-        \overline\tau_d\norm{\fe}
-        +
-        \fe^\top (\mysat(\rbu)-\rbu^*)
-        ,
+        % \\
+        % \le&
+        % -\lambda_{\min}(\mm K)\norm{\fe}^2
+        % +
+        % \overline\tau_d\norm{\fe}
+        % +
+        % \fe^\top (\mysat(\rbu)-\rbu^*)
+        .
     \end{aligned}
@@
 \end{equation} 
-where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
-Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
-However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
+Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if the lumped system uncertainty $\mv f$ can be cancelled out by the control input $\rbu$ neglecting the control input saturation.
+Hence, let us define the ideal control input $\rbu^*$ as $-\mv f$.
+However, $\rbu^*$ is not available in practice, since system dynamics in $\mv f$ is unknown.
 
@@
 The architecture of $\NN({\q}_n;\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
-According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
-Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, for instance $\mv g(\cdot)$, with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
+% Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
 In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
@@
 \begin{align}
-    \rbu^*=& \idealNN+\mv\epsilon,
+    \rbu^*=& \idealNN+\mv\epsilon
+    ,
     \label{eq:control:ideal}
 \end{align}
-which is estimated online by
+where $\mv\epsilon\in\R^n$ is the approximation error vector, which is bounded by $\norm{\mv\epsilon}\le \epsilon$.
+The approximated control input $\rbu^*$ is estimated online by
 \begin{align}
@@
 Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).
+Importantly, input (voltage) saturation
+is not yet considered; this will be done next.
+Note that the control input saturation is not considered in derivation of the ideal control input; this will be addressed in further section.
 
@@
     \caption{
-        Architecture of the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3,l_3=2$.
+        Architecture of the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3$, and $l_3=2$.
     }
@@
         &
-        i\in\{1,\dots,k\},
+        i\in\{1,\dots ,k\},
         \\
@@
 However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
-These functions simplify stability analysis due to their continuous differentiability, and their outputs and gradients satisfy $\norm{\act_i(\mv x)} < \infty$ and  $\norm{\ddtfrac{\act_i(\mv x)}{\mv x}}_F < \infty,\ \forall\mv x\in\R^{l_i}$.
-In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}< 1$.
+These functions simplify stability analysis, since they are continuously differentiable and their outputs and gradients are bounded. 
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}\le 1$.
 
@@
 \end{equation}
-where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ is defined as
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. 
+The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ can be obtained using Proposition \ref{propsit:kron} and the chain rule as follows:
 \begin{equation}
@@
 \end{equation}
-and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.
+and $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \ddtfrac{\act_i}{\NN_{i-1}}$.
 
 In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
-Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
-Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \pptfrac{\estact_i}{\estNN_{i-1}}$, respectively.
+Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \ddtfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \ddtfrac{\estact_i}{\estNN_{i-1}}$, respectively.
 
@@
 where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
-Inequality constraints $c_j,\ \forall j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
+Inequality constraints $c_j:=c_j(\estwth),\ \forall j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
 Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
@@
 
-The adaptation laws for $\estwth$ and $[\lambda]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda]_{j\in\mathcal I})$), as follows:
+The adaptation laws for $\estwth$ and $[\lambda_j]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie  $\min_{\estwth} \max_{[\lambda_j]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda_j]_{j\in\mathcal I})$), as follows:
 \begin{subequations}
@@
     \end{align}
-    \label{eq:adaptation law}
+    \label{eq:adaptation law}%             %%
 \end{subequations}
@@
 % By selecting $\alpha_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
-The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, and they become zero when their corresponding constraints are inactive.
-When a constraint $c_j$ becomes active (\ie violated), the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation.
-Once the violation is resolved and the constraint is no longer active (\ie $c_j < 0$), the multiplier decreases gradually until it returns to zero.
-Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max\left(\lambda_j-\tfrac{c_j}{\mu},0\right)$, with $\mu\in\R_{>0}$ being the penalty parameter.
-
-At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\pptfrac{L}{\estwth}=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$ \cite[Chap.~12 T.~12.1]{Nocedal:2006aa}.
+The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, due to \eqref{eq:adap:lbd:max}. 
+When a constraint $c_j$ becomes active, \ie $c_j > 0$, the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation, \ie see, \eqref{eq:adap:lbd}.
+Once the violation is resolved and the constraint is no longer active, \ie $c_j \le 0$, the multiplier decreases gradually until it returns to zero.
+Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max\left(\lambda_j+\tfrac{c_j}{\mu},0\right)$, with $\mu\in\R_{>0}$ being the penalty parameter.
+
+At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\pptfrac{L}{\estwth}=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$.
 In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
@@
 
-The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\rbu}$ (\ie 
+The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the filtered error with respect to control input $\pptfrac{\fe}{\rbu}$, \ie 
 $
@@
     ^\top \fe
-$). 
-Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
-The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
+$. 
+Since the objective function depends on $\fe$ of a dynamic system, obtaining $\pptfrac{\fe}{\rbu}$ is not straightforward. 
+The recommended method to calculate the exact value of $\pptfrac{\fe}{\rbu}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
 \begin{equation}
@@
     }
-    \left[
+    \left(
         \rbM^{-1}(
@@
         )
-    \right]
+    \right)
     .
 \end{equation}
-However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\rbM,\rbVm, \rbF$ and $ \rbG$).
+However, this method cannot be realized, since we do not have the exact system dynamics, \ie $\rbM,\rbVm, \rbF$ and $ \rbG$.
 Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
@@
     \approx
-    [
+    \left[
         \mysign(\pptfrac{r_i}{\tau_j})
-    ]_{i,j\in\{1,\cdots,m\}}
-$ using the sign of each entry (\ie control direction).
-However, this method is not suitable for \eqref{eq:sys1}, since the control directions are unknown, but the sign of the control input is known (\ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}).
+    \right]_{i,j\in\{1,\cdots,m\}}
+$ using the sign of each entry, \ie control direction.
+However, this method is not suitable for \eqref{eq:sys:filtered}, since the control directions are unknown, but the sign of the control input is known, \ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}.
 Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
@@
 %         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
-%         \STATE Determine update matrix $\dot\eta$ using \eqref{eq. eta dynamics 1};
-%         \STATE Update $\eta\leftarrow \eta +\dot\eta\cdot T_s$; 
-%         \STATE Determine update directions $\dot{\estwth}$, $[\dot\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
-%         \STATE Update weight vector $\estwth\leftarrow \estwth+\dot{\estwth}\cdot T_s$;
-%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\dot\lambda_j]_{j\in\mathcal A}\cdot T_s$;
+%         \STATE Determine update matrix $\ddtt\eta$ using \eqref{eq. eta dynamics 1};
+%         \STATE Update $\eta\leftarrow \eta +\ddtt\eta\cdot T_s$; 
+%         \STATE Determine update directions $\ddtt{\estwth}$, $[\ddtt\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
+%         \STATE Update weight vector $\estwth\leftarrow \estwth+\ddtt{\estwth}\cdot T_s$;
+%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\ddtt\lambda_j]_{j\in\mathcal A}\cdot T_s$;
 %         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
@@
 This section introduces conditions which imposed constraints must satisfy and the weight constraints.
+\MSRY{assumption 2 세타 기준으로 바꾸기; 위에 어펜딕스 순서를 좀 바꿔봐}
 The potential control input constraints are presented in Appendix \ref{sec:appen:cstr}.
@@
     \right)    
-    \le 0
+    % \le 0
     \label{eq:cstr:weight:ball}
@@
     \end{align}
-    \label{eq:sat}
+    \label{eq:sat}% %%
 \end{subequations}
@@
 Since, the auxiliary system only considers the saturation of each control input (\ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}), $\overline{\tau}_1$ was set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$).
+For simplicity, let (C$_4$) be imposed with input bound constraint for the first link actuator, \ie $c_{\overline{\tau}_1}$ and $c_{\underline{\tau}_1}$.
 
@@
 	\hline
-		$e_1\times10^{3}$ & $25.013$ & $21.719$ & $23.168$ & $24.195$ \\
-	\hline
-        $e_2\times10^{3}$ & $22.651$ & $10.530$ & $13.062$ & $12.927$ \\
+		$e_1\times10^{3}$ / rad & $25.013$ & $21.719$ & $23.168$ & $24.195$ \\
+	\hline
+        $e_2\times10^{3}$ / rad & $22.651$ & $10.530$ & $13.062$ & $12.927$ \\
 	\hline
@@
 	\hline
-		$e_1\times10^{3}$ & $7.513$ & $8.021$ & $8.408$ & $19.721$ \\
-	\hline
-        $e_2\times10^{3}$ & $2.617$ & $2.435$ & $3.553$ & $4.256$ \\
+		$e_1\times10^{3}$ / rad & $7.513$ & $8.021$ & $8.408$ & $19.721$ \\
+	\hline
+        $e_2\times10^{3}$ / rad & $2.617$ & $2.435$ & $3.553$ & $4.256$ \\
     \hline

### 2025-05-07 manuscript.tex
review overall paper

@@
 
-Therefore, addressing these two key issues—eensuring weight boundedness and satisfying input constraints—is essential for th reliable design of neuro-adaptive controllers. 
+Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for th reliable design of neuro-adaptive controllers. 
 he following section will provide a detailed review of the existing solutions to these challenges.
@@
 \begin{itemize}
-    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
+    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of DNN weights are formulated as inequality constraints within the adaptation process.
     \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
@@
 \subsection{Organization}
+
+\MSRY{Started from here}
 
@@
     The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \overline{q}_d$ and available to design a bounded control input. 
-    \MSRY{수정이 필요할 수 있음}
     \label{assum:feasible}
@@
 $ denotes the lumped system uncertainty.
-\color{red}
-The unknown matrix $\mm{K}$ is not available to design in practice, 
-\color{black}
+% \color{red}
+% The unknown matrix $\mm{K}$ is not available to design in practice, 
+% \color{black}
 
@@
 \end{equation} 
-Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if the lumped system uncertainty $\mv f$ can be cancelled out by the control input $\rbu$ neglecting the control input saturation.
+Therefore, invoking Lemma \ref{lem:stable:set}, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if the lumped system uncertainty $\mv f$ can be cancelled out by the control input $\rbu$ neglecting the control input saturation.
 Hence, let us define the ideal control input $\rbu^*$ as $-\mv f$.
@@
 To overcome this issue, a DNN is employed to approximate $\rbu^*$.
-Let $\NN:=\NN({\q}_n;\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
+Let $\NN:=\NN({\q}_n;\wth): \R^{l_0+1}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l_0+1}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
 The architecture of $\NN({\q}_n;\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
@@
 \end{align}
-where $\mv\epsilon\in\R^n$ is the approximation error vector, which is bounded by $\norm{\mv\epsilon}\le \epsilon$.
+where $\mv\epsilon\in\R^n$ is the approximation error vector, which is bounded by $\norm{\mv\epsilon}\le \bar{\epsilon}$.
 The approximated control input $\rbu^*$ is estimated online by
@@
 \end{subequations}
-where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L$ and $J$ are suppressed for brevity.
+where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L(\cdot)$ and $J(\cdot)$ are suppressed for brevity.
 % By selecting $\alpha_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
@@
 \begin{equation}
-    \ddtt (
+    \ddtt 
+    \left(
         \pptfrac{\fe}{\rbu}
-    )
+    \right)
     =
@@
 However, this method cannot be realized, since we do not have the exact system dynamics, \ie $\rbM,\rbVm, \rbF$ and $ \rbG$.
-Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.
+Additionally, the computational cost of the forward sensitivity method is high, as the number of DNN's weights are generally large.
 
@@
 
-\subsection{Constraint Candidates}\label{sec:sub:cstr}
-
-This section introduces conditions which imposed constraints must satisfy and the weight constraints.
-\MSRY{assumption 2 세타 기준으로 바꾸기; 위에 어펜딕스 순서를 좀 바꿔봐}
-The potential control input constraints are presented in Appendix \ref{sec:appen:cstr}.
-First, we introduce the following assumptions for the constraints.
-
-\begin{assum}
-    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
-    \label{assum:convex}
-\end{assum}
-
-\begin{assum}
-    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
-    \label{assum:LICQ}
-\end{assum}
-
-\begin{remark}
-    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex in practice including the origin.
-    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
-    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
-\end{remark}
-
-The following Lemma is introduced for the stability analysis.
-\begin{lem}
-    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
-    \label{lem:convex:angle}
-\end{lem}
-
-\begin{proof}
-
-Since $\rbu = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\rbu$ can be derived: 
-\begin{equation}\label{eq:linear:map}
-    \begin{aligned}
-    \rbu 
-    = 
-    &
-    \estNN 
-    % = 
-    % \myvec(\estNN)
-    =
-    \myvec(
-        \estwV_k^\top \estact_k
-    ) 
-    = 
-    (
-        \mm I_{l_{k+1}}
-        \otimes 
-        \estact_k^\top
-    )^\top
-    \myvec(\estwV_k)
-    \\
-    = &
-    \underbrace{
-        (
-        \mm I_{l_{k+1}}
-        \otimes 
-        \estact_k^\top
-    )^\top}_{:=\mm T(\estact_k)}
-    \estwth_k 
-    =
-    \mm T(\estact_k) \estwth_k.
-    \end{aligned}
-\end{equation}
-Therefore, the convexity of the input constraints in $\rbu$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
-that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
-
-\end{proof}
-
-The weight constraints are essential to prevent the weights from diverging during the adaptation process.
-The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+\subsection{Essential and Potential Constraint Candidates}\label{sec:sub:cstr}
+
+This section introduces essential constraint to be imposed for the stability of the proposed CONAC, and conditions for the potential control input constraints.
+
+First, weight constraints are essential to prevent the weights from diverging during the adaptation process.
+The weight constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
 \begin{equation}
@@
 \end{equation}
-with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
-The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
+with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$, and the arguments of $c_{\theta_i}(\cdot)$ are omitted for brevity.
+The gradient of $\mv{c}_\theta:=\mv c_{\theta}(\estwth)$ with respect to $\estwth$ is given by
 \begin{equation}
@@
 \end{equation}
-Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.
+
+Next, we introduce the conditions for the potential control input constraints presented in Appendix \ref{sec:appen:cstr} as follows:
+
+\begin{assum}
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ \color{red} and $c_j(\idealwth)\le 0$ \color{black}.
+\MSRY{desired controller가 제약조건 밖으로 나갈 수 있기 때문에 적절하지 않을 수 있음}
+    \label{assum:convex}
+\end{assum}
+
+\begin{assum}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
+    \label{assum:LICQ}
+\end{assum}
+
+\begin{remark}
+    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex in practice including the origin.
+    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
+    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
+\end{remark}
 
@@
 Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in\{0,\cdots,k\}}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
-The following lemma is introduced for the stability analysis.
+The following lemmas are introduced for the stability analysis.
 
 \begin{lem}
-    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    \label{lem:convex:angle}
+\end{lem}
+
+\begin{proof}
+
+Since $\rbu = \estNN$, using Proposition \ref{propsit:kron}, a linear map $\mm T(\cdot):\estwth_k\to\rbu$ which is independent of $\estwth_k$, can be derived: 
+\begin{equation}\label{eq:linear:map}
+    \begin{aligned}
+    \rbu 
+    = 
+    &
+    \estNN 
+    % = 
+    % \myvec(\estNN)
+    =
+    \myvec(
+        \estwV_k^\top \estact_k
+    ) 
+    = 
+    (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top
+    \myvec(\estwV_k)
+    \\
+    = &
+    \underbrace{
+        (
+        \mm I_{l_{k+1}}
+        \otimes 
+        \estact_k^\top
+    )^\top}_{=:\mm T(\estact_k)}
+    \estwth_k 
+    =
+    \mm T(\estact_k) \estwth_k.
+    \end{aligned}
+\end{equation}
+Therefore, the convexity of the input constraints in $\rbu$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+
+\end{proof}
+
+\begin{lem} 
+    If control input constraint $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
     \label{lem:cstr:grad:bound}
@@
 From the linear mapping in \eqref{eq:linear:map}, $\rbu$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
-By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
+By Assumption \ref{assum:convex}, the function $c_j$ is convex in $\rbu$-space.
 The convex function has a bounded derivative with respect to $\rbu$, since $\rbu$ is a bounded variable (\ie $\pptfrac{c_j}{\rbu}$ is bounded). 
@@
 This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
-Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.
+Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, is bounded, when $\estwth_i,\ \forall i\in \{k,\cdots,i+1\}$ are bounded.
 
@@
 \begin{theorem}
-    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$.
-    This holds with the weight norm constraint \eqref{eq:cstr:weight:ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
+    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$ under control input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}
+    This holds with the weight norm constraint \eqref{eq:cstr:weight:ball}.
 \end{theorem}
@@
 
-The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
-Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
-This assumption is reasonable, since even if the constraint is inactive 
-\MSRY{Add the reason why it is reasonable.}
-We consider two cases: (C$_1$) control input constraints are active, and (C$_2$) control input constraints are inactive.
-Using the fact that amplitude of the control input is only depends on $\estwth_k$ (\ie see \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$), the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
-
-\subsection*{Case (C$_1$): Control input constraints are active.}
-
-As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as w
-\begin{equation}
-    \Theta_{\fe}^{c_1} 
+% The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
+Invoking the fact that amplitude of the control input is only depends on $\estwth_k$, \ie see, \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
+Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ is supposed to be active.
+This assumption is reasonable, since even if $c_{\theta_i}$ is inactive, $\estwth$ is adapted to reduce $J(·)$ without considering the constraint, unless $c_{\theta_i}$ is
+violated.
+We consider two cases: control input is saturated, and control input is not saturated.
+
+\subsection*{Case 1: Control input is saturated.}
+
+As the result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative) can be obtained using Lemma \ref{lem:stable:set} as follows:
+\begin{equation}
+    \Theta_{\fe}^{1} 
     = 
@@
         \le 
-        \tfrac{2\overline\tau+\overline\tau_d}{\lambda_{\min}(\mm K)}
+        \tfrac{
+            \overline\tau_d
+            +
+            \overline\tau
+            +
+            \bar{\theta}_k\sqrt{l_{k}+1}
+            +
+            \bar{\epsilon}
+        }{
+            \lambda_{\min}(\mm K)
+        }
     \right\}
@@
 \end{equation}
-
+It is notable that the ideal DNN $\idealNN_k={\idealwV_k}^\top\idealact$ is bounded by $\bar{\theta}_k\sqrt{l_{k}+1}$, since $\norm{\idealwV_k}_F = \norm{\idealwth}_k \le \bar{\theta}_k$, and $\norm{\idealact_k}\le \sqrt{l_{k}+1}$.
+
+\MSRY{Explain with active set, later}
 To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
@@
         -\estwth_k^\top 
-        (
+        \left(
             (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
@@
             \pptfrac{c_j}{\estwth_k}
-        )
+        \right)
         \\
@@
         -\estwth_k^\top 
-        (
+        \Big(
             (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
@@
             \pptfrac{c_j}{\estwth_k}
-        )
+        \Big)
         \\
@@
             \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
-        }_{=:c_1\in\R_{>0}}
+        }_{=:{\gamma}_1\in\R_{>0}}
         \norm{\fe}
@@
         &
+        \underbrace{
             -
-        \underbrace{
             \textstyle\sum_{
@@
             \estwth_k^\top \pptfrac{c_j}{\estwth_k}
-        }_{=: c_2 \in\R_{>0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        }_{=:{\gamma}_2<0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
         \\
@@
         +
-        c_1     
+        {\gamma}_1     
         \norm{\fe}
@@
 \end{equation}
-According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
-\begin{equation}
-    \Theta_{\theta_k}^{c_1} 
+According to \eqref{eq:lya2:dot} and Lemma \ref{lem:stable:set}, the invariant set of $\estwth_k$ is defined as
+\begin{equation}
+    \Theta_{\theta_k}^{1} 
     = 
@@
         \tfrac{
-            c_1(2\overline\tau+\overline\tau_d)
+            {\gamma}_1
+            (
+                \overline\tau_d
+                +
+                \overline\tau
+                +
+                \bar{\theta}_k\sqrt{l_{k}+1}
+                +
+                \bar{\epsilon}
+            )
         }{
@@
 The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
-For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{c_1}$ is squeezed to a point.
-The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
-Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
-It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
-This drives $\estwth_k$ to the origin until the constraint is satisfied (\ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space).
-
-Therefore, the boundedness of $\estwth$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{c_1}$ and $\Theta_{\theta_k}^{c_1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
-
-\subsection*{Case (C$_2$): Control input constraints are inactive.}
-
-Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
+For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{1}$ is squeezed to a point.
+The satisfactions of the remaining control input constraints can be verified implicitly using ${\gamma}_2$ in \eqref{eq:lya2:dot}.
+Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does ${\gamma}_2$.
+It makes ${\gamma}_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
+This drives $\estwth_k$ to the origin until the constraint is satisfied, \ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space.
+
+Therefore, the boundedness of $\estwth_k$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{1}$ and $\Theta_{\theta_k}^{1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
+
+\subsection*{Case 2: Control input is not saturated.}
+
+Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{\{i\in[0,\cdots,k\}}$ in \eqref{eq:lya2:dot} can be removed.
 Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
@@
             \overline\tau_d+\norm{
-                \underbrace{
                 \idealNN+\mv\epsilon
-                }_{=\rbu^*}
             }
@@
         \le&
-        -\lambda_{\min}(\mm K)\norm{\fe}^2
-        +(\overline\tau_d+\overline\tau)
+        -
+        \lambda_{\min}(\mm K)
+        \norm{\fe}^2
+        +
+        \left(
+            \overline\tau_d
+            +
+            \bar{\theta}_k\sqrt{l_{k}+1}
+            +
+            \bar{\epsilon}
+        \right)
         \norm{\fe}
-        -\lambda_{\theta_k}\norm{\estwth_k}^2
+        \\
+        &
+        -
+        \lambda_{\theta_k}\norm{\estwth_k}^2
         .
@@
 \end{equation}
-Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
-\begin{equation}
-    \Theta_{\fe}^{c_2}
+Like in Case 1, the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{2}$ defined as
+\begin{equation}
+    \Theta_{\fe}^{2}
     =
@@
         \tfrac{
-            \overline\tau_d+\overline\tau
+            \overline\tau_d
+            +
+            \bar{\theta}_k\sqrt{l_{k}+1}
+            +
+            \bar{\epsilon}
         }{
@@
 \end{equation}
-The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ exists positive unless $c_{\theta_k}$ is satisfied.
 
@@
 
-The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
+The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$ can be shown recursively, using \cite[Chap.~4 Thm.~1.9]{Desoer:2009aa}.
 The dynamics of $\estwth_i,\ \forall i\in\{k-1,\cdots,0\}$ are represented as
@@
 The two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
-The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
-The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.
+The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
+The system dynamics of the two-link manipulator can be represented as Euler-Lagrange equation \eqref{eq:sys1} and described as Fig.~\ref{fig:robot:model}, and the estimated system parameters are provided in Table~\ref{table:system:params}.
 
@@
     \centering
-    \subfloat[Two-link manipulator model.]{
+    \subfloat[Two-link manipulator model.\MSRY{ADD inertia}]{
         \includegraphics[width=0.75\linewidth]{src/figures/RobotModel.drawio.pdf}
@@
 % ------------------------------------
-The desired trajectory for $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
+The desired trajectory for $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using the quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
 The desired trajectory is defined as follows:
@@
     \qd(t) 
-    \!=\! 
+    =
     \begin{pmatrix}
-        {q_d}_1\\{q_d}_2
+        {\qd}_1
+        \\
+        {\qd}_2
     \end{pmatrix}
-    \!=\!
+    =
     \begin{cases}
-    \mypoly^5({\qd}_0,{\qd}_1,t_f,t),
-        \!&\!
-        \text{if } 0\!\le\!t\!<\!t_f 
-        ,
-        \\
-    \mypoly^5({\qd}_1,{\qd}_2,t_f,t-t_f),
-        \!&\!
-        \text{if } t_f\!\le\!t\!<\!2t_f 
-        ,
-        \\
-    \mypoly^5({\qd}_2,{\qd}_1,t_f,t-2t_f),
-        \!&\! 
-        \text{if } 2t_f\!\le\!t\!<\!3t_f 
-        .
-        \\
-    \mypoly^5({\qd}_1,{\qd}_0,t_f,t-3t_f),
-        \!&\!    
-        \text{if } 3t_f\!\le\!t\!<\!4t_f 
+    \mathcal{P}^5(t;{\qd}_0,{\qd}_1,t_f),
+        &
+        \text{if } 0 \le t < t_f 
+        ,
+        \\
+    \mathcal{P}^5(t;{\qd}_1,{\qd}_2,t_f),
+        &
+        \text{if } t_f \le t < 2t_f 
+        ,
+        \\
+    \mathcal{P}^5(t;{\qd}_2,{\qd}_1,t_f),
+        & 
+        \text{if } 2t_f \le t < 3t_f 
+        ,
+        \\
+    \mathcal{P}^5(t;{\qd}_1,{\qd}_0,t_f),
+        &    
+        \text{if } 3t_f \le t < 4t_f 
         ,
@@
 \end{equation}
-where ${\qd}_0:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
-To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.
-
-However, since the NN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
+where ${\qd}_0:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s, and illustrated in Fig.~\ref{fig:robot:model}.
+To demonstrate the learning capability of DNN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.
+
+However, since the DNN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
 Hence, in advance of the reference trajectory, the manipulator was initially positioned at ${\qd}^{\rm{origin}}=\left(-\tfrac{1}{2}\pi,0\right)^\top$ (\ie stable equilibrium point).
-Then, a reference trajectory was applied to the manipulator to move from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ which is the initial and final points of the episode.
-After the manipulator reached ${\qd}_0$, the constant reference trajectory $\qd={\qd}_0$ was applied for $t_f=8$ s to be steady and to avoid the effect of the transient response.
+Then, a reference trajectory was applied to the manipulator to move from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ in 3 seconds, \ie $\mathcal{P}^5(t;{\qd}^{\rm{origin}},{\qd}_0,3)$, which is the initial and final points of the episode.
+After the manipulator reached ${\qd}_0$, the constant reference trajectory $\qd={\qd}_0$ was applied for 8 seconds to be steady and to avoid the effect of the transient response.
 
@@
 % ------------------------------------
-The effectiveness of the proposed CONAC to handle the combination of the convex input constraints was demonstrated by defining the saturation function which projects the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
+The effectiveness of the proposed CONAC to handle the combination of the convex input constraints was demonstrated by defining the saturation function which projects the control input onto following convex set $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
 \begin{subequations}
@@
 \end{subequations}
-These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
+These sets \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
 
@@
 % ------------------------------------
-\subsubsection*{Controller 1: (C$_1$) CONAC with large $\beta_j$}
-
-To handle the input saturation, the proposed CONAC was implemented with the input bound constraint \eqref{eq:cstr:input:bound} for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
+\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large $\beta_j$}}
+
+To handle the input saturation, the proposed CONAC was implemented with the input bound constraint \eqref{eq:cstr:input:bound} $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for second link, and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
 \begin{equation}
@@
     \tfrac{1}{2}
-    (
+    \left(
         \norm{\rbu}-\overline\tau
-    )^2 
+    \right)^2 
     % <0
@@
 \end{equation}
-where $\overline\tau_2=-\underline{\tau}_2=3.5$ are the absolute bound of the second link actuator, and $\overline\tau=11$ is the maximum feasible norm of the control input.
+where $\overline\tau_2=-\underline{\tau}_2=3.5$ are the absolute bound of the second link actuator's torque, and $\overline\tau=11$ is the maximum feasible norm of the first and second torques.
 Hence, (C$_1$) is possible to use full capability of the actuator.
-The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CONAC.
-As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.
-
-The update rate of the Lagrange multipliers was set to large values such that $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$, to investigate the effect of the large update rate of Lagrange multipliers.
+The weight constraints $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ were also considered in the CONAC.
+As described in \eqref{eq:control:est}, the control input (torques) is equal to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
+
+The update rates of the Lagrange multipliers for weight constraints were set to $\beta_{\theta_i}=10^{-3},\ \forall i\in\{0,\cdots,k\}$, and ,for control input constraints, the update rates were set to large values such that $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$ to investigate the effect of the large values of update rates.
 
@@
 % ------------------------------------
-\subsubsection*{Controller 2: (C$_2$) CONAC with small $\beta_j$}
-
-As the second controller, the proposed CONAC was implemented with the same input bound constraint \eqref{eq:sim:cstr:CONAC} as (C$_1$), but with small $\beta_j$ values such that $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.
-The remaining parameters were the same as (C$_1$).
+\subsubsection*{Controller 2: \normalfont{(C$_2$)} \textit{CONAC with small $\beta_j$}}
+
+As the second controller, the proposed CONAC was implemented with the same input bound constraint \eqref{eq:sim:cstr:CONAC} as (C$_1$), but with small update rate values such that $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.
+The remaining properties and parameters were the same as (C$_1$).
 
@@
 % ------------------------------------
-\subsubsection*{Controller 3: (C$_3$) CONAC without control input constraints}
+\subsubsection*{Controller 3: \normalfont{(C$_3$)} \textit{CONAC without control input constraints}}
 
 The third controller was the same as (C$_1$) and (C$_2$), but without the control input constraints, to emphasize the control input constraint handling capability of the proposed CONAC.
-In this case, the update rate of the Lagrange multipliers regarding the control input constraints \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$ was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated.
-The remaining properties were the same as (C$_1$) and (C$_2$).
+In this case, the update rate of the Lagrange multipliers regarding the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated (see, \eqref{eq:adap:lbd}).
+The remaining properties and parameters were the same as (C$_1$) and (C$_2$).
 
@@
 % ------------------------------------
-\subsubsection*{Controller 4: (C$_4$) CONAC with auxiliary system instead of control input constraints}
-
-On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC.
-The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
+\subsubsection*{Controller 4: \normalfont{(C$_4$)} \textit{CONAC with auxiliary system instead of control input constraints}}
+
+On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC with control input constraints by replacing them with the auxiliary system.
+The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state variables, and $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$ are user-designed matrices.
 The auxiliary state $\mv{\zeta}$ is affected by the overflow amount of the control input $\Delta\rbu$, whose entries are defined as $\Delta\tau_{i} = 
@@
 The matrices of the auxiliary system were set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed of the auxiliary system.
-Since, the auxiliary system only considers the saturation of each control input (\ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}), $\overline{\tau}_1$ was set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$).
-For simplicity, let (C$_4$) be imposed with input bound constraint for the first link actuator, \ie $c_{\overline{\tau}_1}$ and $c_{\underline{\tau}_1}$.
+Since, the auxiliary system only considers the saturation of each control input, \ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}, $\overline{\tau}_1$ was set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$).
+For simplicity, let say (C$_4$) was imposed with input bound constraint for the first link actuator, \ie $c_{\overline{\tau}_1}$ and $c_{\underline{\tau}_1}$.
+\MSRY{사실, 제약조건이 부여된 것은 아니기 떄문에 위와 같이 표현하였음}
 
@@
 % ------------------------------------
-For all controllers ((C$_1$), (C$_2$), (C$_3$), and (C$_4$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
-The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
-Each NN architecture had two hidden layers with four nodes (\ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
+For all controllers ((C$_1$), (C$_2$), (C$_3$), and (C$_4$)), the DNN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+The DNNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
+All DNN architectures have two hidden layers with four nodes, \ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$, and the adaptation gain was set to $\alpha=0.5$.
 The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
@@
     \hline
-        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
-    \hline
-    \hline
-        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
-    \hline
-        (C$_2$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
-    \hline
-        (C$_3$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
-    \hline
-        (C$_4$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
+        &\bf{Description}&\bf{Input Constraint}\\
+    \hline
+    \hline
+        (C$_1$)&large $\beta_j$&$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+    \hline
+        (C$_2$)&small $\beta_j$&$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
+    \hline
+        (C$_3$)&no $\rbu$ constraints&$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
+    \hline
+        (C$_4$)&aux. sys.&$\overline{\tau}_1=-\underline{\tau}_1=10.428,\overline{\tau_2}=-\underline{\tau_2}=3.5$\\
     \hline
@@
 
-\begin{figure}[t]
-    \centering
-    \subfloat[Control input $\tau$ in time interval from $29.4$ s to $31.9$ s (bird's eye view).]{
-    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
-        \includegraphics[width=\figSizeOneCol\linewidth]
-        {
-            src/measurement/figures/compare/Fig6.eps
-        }%
-        \label{fig:ctrl:result:scope:control}}
-        \vfill
-    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
-        \includegraphics[width=\figSizeOneCol\linewidth]
-        {
-            src/measurement/figures/compare/Fig8.eps
-        }%
-        \label{fig:ctrl:result:scope:beta}}
-        \vfill
-    \subfloat[Auxiliary states in time interval from $29.4$ s to $31.9$ s.]{
-        \includegraphics[width=\figSizeOneCol\linewidth]
-        {
-            src/measurement/figures/compare/Fig9.eps
-        }%
-        \label{fig:ctrl:result:scope:aux}}
-  \caption{
-    Constraint handling process of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid} in time interval from $29.4$ s to $31.9$ s.
-  }
-\label{fig:ctrl:result:scope}
-\end{figure}
-
-\begin{figure}[!t]
-	\centering
-	\includegraphics[width=0.6\linewidth]{
-		src/figures/lambda_effect.drawio.pdf
-		}
-	\caption{
-		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_1$.
-		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively (i.e., $\lambda_{j}' > \lambda_{j}''$).
-	}
-	% \vspace{1mm}
-	\label{fig:lambda_effect}
-\end{figure}
-
 % ------------------------------------
@@
 Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode.
-This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
+This results lead to the conclusion that the DNNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was unknown in advance.
 Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.
 
-In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time interval from $17.5$ s to $19.9$ for Episode $1$, and from $29.5$ s to $31.9$ s for Episode $2$.
+In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time intervals from $17.5$ s to $19.9$ for Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s for Episode $2$.
 This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
 
-The tracking performances of CONAC with control input constraints, (\ie (C$_1$), and (C$_2$)), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
+The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
 This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
 The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).
+Without consideration of the control input saturation, DDN became confused by the difference between its output (control input) and the saturated control input, which leads to the poor performance of (C$_3$).
 
@@
 % ------------------------------------
+\begin{figure}[t]
+    \centering
+    \subfloat[Control input $\tau$ in time interval from $29.4$ s to $31.9$ s (bird's eye view).]{
+    % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            src/measurement/figures/compare/Fig6.eps
+        }%
+        \label{fig:ctrl:result:scope:control}}
+        \vfill
+    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            src/measurement/figures/compare/Fig8.eps
+        }%
+        \label{fig:ctrl:result:scope:beta}}
+        \vfill
+    \subfloat[Auxiliary states in time interval from $29.4$ s to $31.9$ s.]{
+        \includegraphics[width=\figSizeOneCol\linewidth]
+        {
+            src/measurement/figures/compare/Fig9.eps
+        }%
+        \label{fig:ctrl:result:scope:aux}}
+  \caption{
+    Constraint handling process of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, and (C$_4$) \protect\colorLine{magenta}{solid} in time interval from $29.4$ s to $31.9$ s.
+  }
+\label{fig:ctrl:result:scope}
+\end{figure}
+
+\begin{figure}[!t]
+	\centering
+	\includegraphics[width=0.6\linewidth]{
+		src/figures/lambda_effect.drawio.pdf
+		}
+	\caption{
+		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_1$.
+		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively (i.e., $\lambda_{j}' > \lambda_{j}''$).
+	}
+	% \vspace{1mm}
+	\label{fig:lambda_effect}
+\end{figure}
+
 \hfill
@@
 
-\hfill
-
-As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$), and (C$_2$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_4$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$, and auxiliary state $\mv{\zeta}$, respectively.
+As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$), and (C$_2$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_4$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}$, and auxiliary state $\mv{\zeta}$, respectively.
 It is worth to note that the control input constraints were violated repeatedly, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
-
-\hfill
 
@@
 In contrast, (C$_1$), and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$.
-
-\hfill
 
@@
 This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but this also causes oscillation in the adaptation process.
-In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_j$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_j,\ \forall j\in\mathcal I$ was satisfied and violated, respectively, in the discrete time implementation.
-Besides, with small $\lambda_j$, the adaptation direction of $\estwth_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
+In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_{\rbu}$ was satisfied and violated, respectively, in the discrete time implementation.
+Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
 This allows the controller to show a smoother control input.
@@
 
-Finally, the weight norm constraints $c_{\theta_i},\ \forall i\in\mathcal I$ are investigated.
+Finally, the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,\cdots,2\}$ are investigated.
 The weight norm constraints were not activated except for the outer layer weights $c_{\theta_2}$ of (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}.
 This is because the weights of (C$_1$), (C$_2$), and (C$_4$) were suppressed by the control input constraints, while (C$_3$) was not.
+\MSRY{필요하다면 왜 제어입력 제약하는게 가중치 제약도 되는지 추가 가능}
 In addition, the inner and hidden layer weights constraints were not violated (\ie $\norm{\estwth_0},\norm{\estwth_1}$ were uniformly lower than $\norm{\estwth_2}$), since the backpropagated error was multiplied by the gradient of the activation function, which is limited from $-1$ to $1$, \ie see, \eqref{eq:gradient:phi}.
@@
 
-\MSRY{ADD MORE DETAILS}
-
-The KKT conditions were satisfied in the simulation, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
+\MSRY{이 부분도 IECON과 마찬가지로 이산으로 돌아감으로 바로 보여주기는 힘들 수 있을 것 같습니다. 실제로 보시면 많은 진동이 보여서 정상상태의 KKT를 주장할 수 있을지 의문입니다.}
+
+Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
+However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of active constraints were positive and inactive constraints were zero.
 
@@
 
-The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time measured using CPU clock ticks.
+The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time measured using CPU clock ticks of the OpenCR1.0 board.
 The computational times are shown in Fig.~\ref{fig:ctrl:real:result:cmp:time} indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz.
 In addition, it is notable that the computational time decreased as the weights converged.
+\MSRY{삭제해야할수있음; C4는 그러하지 않기 때문}
 
@@
 
-This paper presented a constrained optimization-based neuro-adaptive controller (CONAC) for the uncertain Euler-Lagrange system, addressing both weight norm and input constraints through a rigorous optimization framework.
+This paper presented a constrained optimization-based neuro-adaptive controller (CONAC) for the uncertain Euler-Lagrange system, addressing both weight and input constraints through a rigorous optimization framework.
 The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
@@
 
-A real-time implementation validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A.
-CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
+A real-time implementation validated the superior performance of CONAC compared to conventional method. 
+The CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
 
@@
 
-\section{Input Constraint Candidates}\label{sec:appen:cstr}
-
-This section introduces potential weight and input constraints that can be used in the proposed neuro-adaptive controller.
-
-\subsection{Input Bound Constraint}\label{sec:appen:cstr:input:bound}
+\subsection{Input Constraint Candidates}\label{sec:appen:cstr}
+
+This section introduces potential weight and input constraints that can be used in the proposed CONAC.
+
+\subsubsection{Input Bound Constraint}\label{sec:appen:cstr:input:bound}
 
 Most physical systems have control input limits due to electrical and mechanical limitations.
-These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+These are expressed as $\mv{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\mv{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
 \begin{equation}
@@
 \end{equation}
-with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
+with $\tau_{\overline \tau_i}\in\R_{>0}$ and $\tau_{\underline\tau_i}\in\R_{>0}$ representing the maximum and minimum control input bounds, respectively.
 % The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
-The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
+The gradients of $\mv{c}_{\overline \tau}$ and $\mv{c}_{\underline\tau}$ with respect to $\estwth$ are given by
 \begin{equation}
     \begin{aligned}
-        \pptfrac{\boldsymbol c_{\overline \tau}}{\estwth}
+        \pptfrac{\mv c_{\overline \tau}}{\estwth}
         =& 
+        \left[
+            \pptfrac{c_{\overline \tau_i}}{\estwth}^\top
+        \right]_{i\in\{1,\cdots,n\}}
+        % \begin{bmatrix}
+        %     \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
+        %     \vdots \\
+        %     \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
+        % \end{bmatrix}
+        = 
+            +\pptfrac{\estNN}{\estwth}
+            \\
+        =&
+        =
+        +
         \begin{bmatrix}
-            \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
-            \vdots \\
-            \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
-        \end{bmatrix}
-        = 
-            +\pptfrac{\estNN}{\estwth}
-            \\
-        =&
-        =
-        +
-        \begin{bmatrix}
-            (I_{l_{k+1}}\otimes \estact_{k}^\top)&
+            (\mm{I}_{l_{k+1}}\otimes \estact_{k}^\top)&
             \!\cdots\! &
@@
         \\
-        \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
-        =
-        & 
-        \begin{bmatrix}
-            \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
-            \vdots \\
-            \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
-        \end{bmatrix}
+        \pptfrac{\mv c_{\underline\tau}}{\estwth}         
+        =
+        & 
+        \left[
+            \pptfrac{c_{\underline\tau_i}}{\estwth}^\top
+        \right]_{i\in\{1,\cdots,n\}}
+        % \begin{bmatrix}
+        %     \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
+        %     \vdots \\
+        %     \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
+        % \end{bmatrix}
         = 
@@
         -\begin{bmatrix}
-            (I_{l_{k+1}}\otimes \estact_{k}^\top)&
+            (\mm{I}_{l_{k+1}}\otimes \estact_{k}^\top)&
             % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
@@
 
-\subsection{Input Norm Constraint}\label{sec:appen:cstr:input:norm}
-
-Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate.
+\subsubsection{Input Norm Constraint}\label{sec:appen:cstr:input:norm}
+
+Consider the control input $\rbu$ as the torque of each actuator corresponding to its generalized coordinate.
 Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.
@@
 \begin{equation}
-    c_{\rbu}=\norm{\mv{\tau}}^2 -\overline\tau^2
+    c_{\rbu}
+    =
+    \norm{
+        \mv{\tau}
+    }^2 
+    -
+    \overline\tau^2
     ,
@@
 \begin{equation}
-    \pptfrac{\boldsymbol c_{\rbu}}{\estwth}
+    \pptfrac{\mv c_{\rbu}}{\estwth}
     \!=\! 
-    \textstyle\sum_{i=1}^n 2\tau_{(i)} 
+    \textstyle\sum_{i=1}^n 2\tau_{i} 
     \left(
         \myrow_i
-        (
+        \left(
             \pptfrac{\estNN}{\estwth}
-        )
+        \right)
     \right)^\top  
@@
 \end{equation}
-It should be noted that constraints \eqref{eq:cstr:input:bound} and \eqref{eq:cstr:input:norm} can be imposed simultaneously, as their gradients \eqref{eq:cstr:input:bound:grad} and \eqref{eq:cstr:input:norm:grad} are linearly independent, satisfying the LICQ condition.
+It should be noted that constraints \eqref{eq:cstr:input:bound} and \eqref{eq:cstr:input:norm} can be imposed simultaneously, as their gradients \eqref{eq:cstr:input:bound:grad} and \eqref{eq:cstr:input:norm:grad} are linearly independent, satisfying Assumption \ref{assum:LICQ}, \ie the LICQ condition.
 
@@
     received the B.S.
-degree in mechanical engineering from Incheon National University, South Korea, in 2023, abd the M.S.
+degree in mechanical engineering from Incheon National University, South Korea, in 2023, and the M.S.
 degree in mechanical engineering from Gwangju Institute of Science and Technology (GIST), South Korea, in 2025.

### 2025-05-09 manuscript.tex
minor change

@@
 \thanks{
-    Myeongseok Ryu is with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr).
-
-    Donghwa Hong is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: ???@gist.ac.kr).
-
-    Kyunghwan Choi is with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: khchoi@kaist.ac.kr).
+    Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr and khchoi@kaist.ac.kr).
+
+    Donghwa Hong is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: fairytale@gm.gist.ac.kr).
 

### 2025-05-13 presentation/presentation.tex
new ppt style

@@
-% https://www.overleaf.com/learn/latex/Beamer#Using_a_colortheme
+% https://www.overleaf.com/learn/latex/Beamer#Using_a_colorthemev
 
 % Inbuilt themes in beamer
-\documentclass[aspectratio=169]{beamer}
+\documentclass[8pt, aspectratio=169]{beamer}
 
-% Theme choice:
-\usetheme{Antibes}
-% \usecolortheme{beaver}
+% % Theme choice:
+% \usetheme{Antibes}
+% % \usecolortheme{beaver}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Use roboto Font (recommended)
+\usepackage[sfdefault]{roboto}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Use roboto Font (recommended)
+\usepackage[sfdefault]{roboto}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Define where theme files are located. ('/styles')
+\usepackage{styles/fluxmacros}
+\usefolder{styles}
+% Use Flux theme v0.1 beta
+% Available style: asphalt, blue, red, green, gray 
+\usetheme[style=blue]{flux}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Extra packages for the demo:
+\usepackage{booktabs}
+\usepackage{colortbl}
+\usepackage{ragged2e}
+\usepackage{schemabloc}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\usepackage{calc}
 
@@
 } 
+\subtitle{
+    \textit{IEEE European Control Conference (ECC) 2025}\\
+}
 \author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}}
 \date{\today}
-
-\institute % (optional)
-{
+% \institute[short]{\inst{1} First \samelineand \inst{2} Second \samelineand \inst{3} Third}
+\newcommand{\samelineand}{\\}
+\institute{%
+    \begin{minipage}[c]{\linewidth}
+        \centering
         \inst{1}%
@@
         Gwangju Institute of Science and Technology
+  \end{minipage}
 }
+% make institute font size smaller
+\setbeamerfont{institute}{size=\normalsize}
 
 \logo{
-    \includegraphics[height=0.4cm]{logo_KAIST.png}
+    \includegraphics[height=0.3cm]{logo_KAIST.png}
     \hspace{.5cm}%
-    \includegraphics[height=0.4cm]{logo_KAIST.png}
+    \includegraphics[height=0.3cm]{logo_KAIST.png}
 }
@@
 }
+\titlegraphic{logo_KAIST.png}
 
@@
 % Title page frame
-\begin{frame}
+% \begin{frame}
 \titlepage 
-\end{frame}
+% \end{frame}
 
@@
 
+% FOLLOWING SLIDES ARE EXAMPLES
+
+\section{Presentation}
+
+\subsection{introduction}
+
+%\begin{frame}{Flux}{introduction}
+\begin{frame}{Flux}{}
+	\justifying
+ Flux is a modern style beamer presentation. It is provided as a work in progress version and may suffer from inconsistencies. Sources and complementary information are available at\\[0.3cm]
+ 	\centering\textbf{github.com/pvanberg/flux-beamer}
+\end{frame}
+
+\def\beamer@mytheme@style{green}
+\begin{frame}[fragile]{Flux}{colors}
+	\centering
+	Flux provides five differents color palettes.\\
+	\verb+\usetheme[style=asphalt]{flux}+\\[0.8cm]
+	\newcommand{\colorRow}[1]{
+	\begin{tabular}{p{4cm}cccc}
+	#1 & \cellcolor{primary}\hspace*{1cm} &\cellcolor{primaryLight}\hspace*{1cm}&\cellcolor{secondary}\hspace*{1cm}&\cellcolor{tertiary}\hspace*{1cm}\\
+ 	\end{tabular}
+ 	}
+ 	\colorRow{Asphalt}\\[0.3cm]
+	\definecolor{primaryLight}{HTML}{3a99d9}
+	\definecolor{primary}{HTML}{2e81b7}
+	\definecolor{secondary}{HTML}{2e81b7}
+	\definecolor{tertiary}{HTML}{e76d55}
+ 	\colorRow{Blue}\\[0.3cm]
+    \definecolor{primaryLight}{HTML}{77933c}
+    \definecolor{primary}{HTML}{4f622a}
+    \definecolor{secondary}{HTML}{884F4D}
+    \definecolor{tertiary}{HTML}{2B3234}
+ 	\colorRow{Green}\\[0.3cm]
+ 	\definecolor{primaryLight}{HTML}{C0392B}
+    \definecolor{primary}{HTML}{96281B}
+    \definecolor{secondary}{HTML}{347986}
+    \definecolor{tertiary}{HTML}{56423e}
+ 	\colorRow{Red}\\[0.3cm]
+ 	\definecolor{primaryLight}{HTML}{616161}
+	\definecolor{primary}{HTML}{424242}
+	\definecolor{secondary}{HTML}{518071}
+	\definecolor{tertiary}{HTML}{8b7687}
+ 	\colorRow{Gray}\\[0.3cm]
+\end{frame}
+
+\subsection{fonts}
+
+\begin{frame}[fragile]{Flux}{fonts}
+ Flux recommends the use of Roboto or Overpass font and a font size of 9pt.\\[0.2cm]
+ \begin{center}
+ 	\verb+\documentclass[9pt]{beamer}+\\
+	\verb+\usepackage[sfdefault]{roboto}+
+ \end{center}
+
+  Flux also implements default typographies.
+
+	\begin{itemize}
+		\item Regular
+		\item \alert{Alert}
+		\item \example{Example}
+		\item \textit{Italic}
+		\item \textbf{Bold}
+	\end{itemize}
+
+\end{frame}
+
+\subsection{footnotes}
+
+\begin{frame}{Flux}{footnotes}
+		Flux also includes custom footnote integration.
+For instance, this \textbf{element}\footnote{Footnotes are notes placed at the bottom of a page.
+They cite references or comment on a designated part of the text above it.
+For example, say you want to add an interesting comment to a sentence you have written, but the comment is not directly related to the argument of your paragraph.
+} and this \textbf{element}\footnote{Footnotes are not just for interesting comments, however.
+Sometimes they simply refer to relevant sources -- they let your reader know where certain material came from, or where they can look for other sources on the subject.} provide a footnote.
+\end{frame}
+
+\section{Collections}
+\subsection{lists}
+
+\begin{frame}{Flux}{lists}
+   \begin{columns}[T,onlytextwidth]
+    \column{0.33\textwidth}
+      \textbf{Items}
+      \begin{itemize}
+        \item Cats \item Dogs \item Birds
+      \end{itemize}
+
+    \column{0.33\textwidth}
+      \textbf{Enumerations}
+      \begin{enumerate}
+        \item First \item Second \item Last
+      \end{enumerate}
+
+    \column{0.33\textwidth}
+      \textbf{Descriptions}
+      \begin{description}
+        \item[Apples] Yes \item[Oranges] No \item[Grappes] No
+      \end{description}
+\end{columns}
+\let\thefootnote\relax\footnote{Note the following demo slides are directly taken from metropolis theme. Copyright 2014 Matthias Vogelgesang.\\
+Give a look at https://github.com/matze/mtheme/tree/master/demo}
+\end{frame}
+
+\subsection{tables}
+
+\begin{frame}{Flux}{tables}
+  \begin{table}
+    \caption{Largest cities in the world (source: Wikipedia)}
+    \begin{tabular}{@{} lr @{}}
+      \toprule
+      City & Population\\
+      \midrule
+      Mexico City & 20,116,842\\
+      Shanghai & 19,210,000\\
+      Peking & 15,796,450\\
+      Istanbul & 14,160,467\\
+      \bottomrule
+    \end{tabular}
+    \hspace*{1cm}
+        \setlength\extrarowheight{3pt}
+    \begin{tabular}{|lr|}
+      \hline
+      \rowcolor{primaryLight}\color{background}City & \color{background}Population\\
+      \hline
+      Mexico City & 20,116,842\\
+      Shanghai & 19,210,000\\
+      Peking & 15,796,450\\
+      Istanbul & 14,160,467\\
+      \hline
+    \end{tabular}
+\end{table}
+\end{frame}
+
+\subsection{blocs}
+
+\begin{frame}[fragile]{Flux}{blocks}
+  		Flux theme comes with three pre-defined block style collections.\\
+  		Native style (default) available as \verb+\setblockstyle{native}+\\[0.5cm]
+
+   \setblockstyle{native} % Default behavior, optional line.
+   \centering
+	\begin{minipage}[b]{0.5\textwidth}
+
+	  \begin{block}{Default}
+        Block content.
+      \end{block}
+
+      \begin{alertblock}{Alert}
+        Block content.
+      \end{alertblock}
+
+      \begin{exampleblock}{Example}
+        Block content.
+      \end{exampleblock}
+
+	\end{minipage}
+
+\end{frame}
+
+\begin{frame}[fragile]{Flux}{blocks}
+  		Flux theme comes with three pre-defined block style collections.\\
+  		NoBackground style available as \verb+\setblockstyle{nobackground}+\\[0.5cm]
+
+   \setblockstyle{nobackground}
+   \centering
+	\begin{minipage}[b]{0.5\textwidth}
+
+	  \begin{block}{Default}
+        Block content.
+      \end{block}
+
+      \begin{alertblock}{Alert}
+        Block content.
+      \end{alertblock}
+
+      \begin{exampleblock}{Example}
+        Block content.
+      \end{exampleblock}
+
+	\end{minipage}
+
+\end{frame}
+
+\begin{frame}[fragile]{Flux}{blocks}
+  		Flux theme comes with three pre-defined block style collections.\\
+  		Metropolis style available as \verb+\setblockstyle{metropolis}+\\[0.5cm]
+
+   \setblockstyle{metropolis}
+   \centering
+	\begin{minipage}[b]{0.5\textwidth}
+
+	  \begin{block}{Default}
+        Block content.
+      \end{block}
+
+      \begin{alertblock}{Alert}
+        Block content.
+      \end{alertblock}
+
+      \begin{exampleblock}{Example}
+        Block content.
+      \end{exampleblock}
+
+	\end{minipage}
+
+\end{frame}
+
+\begin{frame}{Flux}{diagrams}
+\centering
+\begin{tikzpicture}
+    \sbEntree{E}
+    \sbComp{a}{E}
+    \sbBlocL{c}{$H_2$}{a}
+            \sbRelier[$\epsilon$]{a}{c}
+    \sbComph{d}{c}
+            \sbRelier[u]{c}{d}
+    \sbBlocL{e}{$H_3$}{d}
+    \sbBlocL{f}{$H_4$}{e}
+    \sbSortie[5]{S1}{f}
+            \sbRelier{f}{S1}
+            \sbNomLien[0.8]{S1}{$S_1$}
+    \sbDecaleNoeudy[-4]{f}{u}
+    \sbDecaleNoeudy{e}{v}
+    \sbBlocr{r1}{$R_1$}{u}
+    \sbBlocr{r2}{$R_2$}{v}
+    \sbBlocrL{r3}{$R_3$}{r2}
+    \sbRelieryx{f-S1}{r1}
+    \sbRelierxy[n1]{r1}{d}
+    \sbRelieryx{e-f}{r2}
+    \sbRelierxy[n2]{r3}{a}
+\end{tikzpicture}\\[0.4cm]
+Bloc diagram example from \textbf{texample.net}
+\end{frame}
+
+\begin{frame}{Flux}{plots}
+	\begin{minipage}{0.56\textwidth}
+		\begin{figure}
+			\includegraphics[width=\textwidth]{assets/plot.png}
+		\end{figure}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.38\textwidth}
+		\begin{block}{Binary Softmax classifier}
+			\centering
+			$\sigma(\sum_i w_ix_i + b)$
+		\end{block}
+		\begin{exampleblock}{Loss function}
+			\centering\vspace*{0.1cm}
+			$L_i = -log(\frac{e^{f_{y_i}}}{\sum_j e^{f_j}})$\\[0.1cm]
+			cross entropy
+		\end{exampleblock}
+	\end{minipage}
+\end{frame}
+
+% The [plain] causes the headlines, footlines, and sidebars 
+% to be suppressed. Useful for showing large pictures
+\begin{frame}[plain]
+	\begin{center}
+	  This is a plain frame.\\
+	  Use it to display full page images.
+	  \end{center}
+\end{frame}
+
+\begin{frame}[allowframebreaks]{References}
+
+  \nocite{*}
+  \bibliography{demo}
+  \bibliographystyle{abbrv}
+
+\end{frame}
+
+\section{Next section}
+\subsection{subsection 1}
+\subsection{subsection 2}
+\subsection{subsection 3}
+\section{One more section}
+\subsection{subsection 1}
+\subsection{subsection 2}
+\subsection{subsection 3}
+
+\begin{frame}
+ \centering
+ \frametitle{Flux}
+ \framesubtitle{license}
+ Flux is licensed under GNU General Public License v3.\\[0.3cm]
+ 	\centering\textbf{http://www.gnu.org/licenses}\\[0.3cm]
+Inspired by \textbf{Metropolis} theme from Matthias Vogelgesang.\\
+https://github.com/matze/mtheme
+
+\end{frame}
+
 \end{document}

### 2025-05-14 manuscript.tex
add choi comment

@@
 \thanks{
-    Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr and khchoi@kaist.ac.kr).
+    Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr and kh.choi@kaist.ac.kr).
 
@@
 \begin{abstract}
-  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems under weight norm and convex input constraints. 
-  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, while learning the unknown system dynamics and,  addressing both types of constraints, simultaneously.
-  The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. 
-  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. 
-  The proposed controller was validated via a real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
+  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems subject to weight norm and convex input constraints. 
+  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a constrained optimization framework.
+  The weight adaptation laws are formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
+  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
+  The proposed controller is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
+
+  via a real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
 \end{abstract}
@@
     \item $\otimes$ denotes the Kronecker product \cite[Chap. 7 Def. 7.1.2]{Bernstein:2009aa}.
-    \item A vector and matrix are denoted by $\mv{x}=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
+    \item A vector and a matrix are denoted by $\mv{x}=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
         \mm A
@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top$ for $\mm{A}\in\R^{n\times m}$, denotes vectorization of $\mm A$.
+    \item For $\mm{A}\in\R^{n\times m}$, denotes the vectorization of $\mm A$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
 NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
-Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
 SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}.
@@
 
-Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for th reliable design of neuro-adaptive controllers. 
-he following section will provide a detailed review of the existing solutions to these challenges.
+Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
+The following section provides a detailed review of existing solutions to these challenges.
 
@@
 
+\KHCH{Abstract에 있는 것처럼 이 내용도 하나 추가해두죠.
+
+The controller’s stability is rigorously
+analyzed using Lyapunov theory, guaranteeing bounded
+tracking errors and DNN weights.}
+
 The main contributions of this study are listed as follows:
 \begin{itemize}
-    \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of DNN weights are formulated as inequality constraints within the adaptation process.
-    \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
+    \item A constrained optimization-based neuro-adaptive controller (CONAC) is proposed, where the design of a deep neural network (DNN) is formulated as a constrained optimization problem.
+In this formulation, weight norm and convex input constraints are incorporated as inequality constraints, while minimizing a given objective function.
+    % \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of DNN weights are formulated as inequality constraints within the adaptation process.
+    \item The adaptation laws for DNN weights in CONAC are systematically derived to solve the defined problem, using constrained optimization theory.
+These laws guarantee convergence to the first-order optimality conditions, specifically the Karush–Kuhn–Tucker (KKT) conditions, as described in \cite[Chap.
+12 Thm.
+12.1]{Nocedal:2006aa}.
+    % \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
 The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions defined in \cite[Chap.
@@
 \end{equation}
-where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
-The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$ and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector and gravity vector
+where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
+The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
@@
 
-The Euler-Lagrange system \eqref{eq:sys1} satisfies some important physical properties \cite[Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
-We introduce the following properties:
+The Euler-Lagrange system \eqref{eq:sys1} satisfies several important physical properties, as presented in \cite[Chap. 3 Tab. 3.2.1]{Lewis:1998aa}. 
+The key properties are introduced below:
 \begin{prop} 
-    The inertia matrix $\rbM$ is symmetric, positive definite and bounded.
+    The inertia matrix $\rbM$ is symmetric, positive definite, and bounded.
     \label{prop:M}
@@
 \begin{prop} 
-    The Coriolis/centripetal matrix $\rbVm$ can always be selected so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
+    The Coriolis/centripetal\MSRY{인용 책 그대로 적은 것입니다.} matrix $\rbVm$ can always be selected\MSRY{상동.} so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
     \label{prop:skew}
@@
 \begin{prop}
-    The disturbance $\rbd$ is bounded so that $\norm{\rbd}\le \overline\tau_d$.
+    The disturbance $\rbd$ is bounded, \ie $\norm{\rbd}\le \overline\tau_d$.
     \label{prop:dis_bound}
@@
 
-In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R_{\ge0} \to \R^n$, compensating for the unknown system dynamics while addressing the imposed constraints.
+The control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R_{\ge0} \to \R^n$, compensating for the unknown system dynamics while addressing the imposed constraints.
 The desired trajectory $\qd(t)$ is supposed to satisfy the following assumption:
 \begin{assum}
-    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \overline{q}_d$ and available to design a bounded control input. 
+    The desired trajectory $\qd(t)$ is assumed to be bounded, i.e., $\norm{\qd(t)}\le \overline{q}_d$ , and available for designing a bounded control input.
     \label{assum:feasible}
@@
 
-The architecture of the proposed CONAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
-Before we proceed to the controller design, we first revisit some mathematical preliminaries in Section \ref{sec:sub:math preliminaries}. 
-Then, we introduce the neuro-adaptive controller in Section \ref{sec:sub:NAC}, followed by the DNN model in Section \ref{sec:sub:NN definition}. 
-The constrained optimization-based weight adaptation laws will be presented in Section \ref{sec:adap_laws}.
+The architecture of the proposed CONAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, and consists of a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN.
+Before proceeding to the controller design, some mathematical preliminaries are revisited in Section \ref{sec:sub:math preliminaries}. 
+Section \ref{sec:sub:NAC} introduces the neuro-adaptive controller, followed by the DNN model in Section \ref{sec:sub:NN definition}. 
+The constrained optimization-based weight adaptation laws are presented in Section \ref{sec:adap_laws}.
 
@@
 
-Later, the following proposition and lemma will be used in further sections:
+The following proposition and lemma will be used in subsequent sections:
 
 \begin{propsit}[see, {\cite[Chap. 7 Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
-	For matrix $\mm A\in\R^{n\times m}$ and vector $\mv b\in\mathbb R^n$, we have the following property
+	For matrix $\mm A\in\R^{n\times m}$ and vector $\mv b\in\mathbb R^n$, the following property holds:
 	\begin{equation}
@@
 \begin{lem} \label{lem:stable:set}
-    For Lyapunov function $V:=V(\mv{x})\ge0$ with $\mv{x}\in\R^n$, if the time derivative of $V$ is given by $\ddtt V\le -a_1 \mv{x}^\top \mv{x} + a_2 \mv{x}$ for some positive constants $a_1\in\R$ and $a_2\in\R$, then $\mv{x}$ is bounded by $\mv{x}\in\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
+    For Lyapunov function $V:=V(\mv{x})\ge0$ with $\mv{x}\in\R^n$, if the time derivative of $V$ is given by $\ddtt V\le -a_1 \mv{x}^\top \mv{x} + a_2 \mv{x}$ for some positive constants $a_1\in\R$ and $a_2\in\R$, then $\mv{x}$ is bounded as $\mv{x}\in\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
 \end{lem}
@@
 
-First, let us define the filtered tracking error $\fe\in\R^n$ as 
+First, the filtered tracking error $\fe\in\R^n$ is defined as 
 \begin{equation}
@@
 \end{equation}
-where $\mm{K}=\mm{K}^\top\in\R^{n\times n}_{>0}$ denotes arbitrary unknown matrix and $
+where $\mm{K}=\mm{K}^\top\in\R^{n\times n}_{>0}$ denotes an arbitrary unknown matrix and $
     \mv f:= \mv f(\q,\dq,\qd,\dqd,\ddqd)
@@
 \end{equation} 
-Therefore, invoking Lemma \ref{lem:stable:set}, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if the lumped system uncertainty $\mv f$ can be cancelled out by the control input $\rbu$ neglecting the control input saturation.
-Hence, let us define the ideal control input $\rbu^*$ as $-\mv f$.
-However, $\rbu^*$ is not available in practice, since system dynamics in $\mv f$ is unknown.
+Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped system uncertainty $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
+Hence, the ideal control input $\rbu^*$ is defined as $-\mv f$.
+However, $\rbu^*$ is not available in practice, since system dynamics encapsulated in $\mv f$ are unknown.
 
@@
 Let $\NN:=\NN({\q}_n;\wth): \R^{l_0+1}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l_0+1}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
-The architecture of $\NN({\q}_n;\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
-According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, for instance $\mv g(\cdot)$, with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
+The architecture of $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an ideal weight vector $\idealwth$ over a compact subset $\Omega_{NN}\in\R^{l}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
 % Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
-In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.
-
-In conclusion, the ideal control law $\rbu^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN({\q}_n;\idealwth)$ as follows:
+In this study, $\idealwth$ is considered a locally optimal solution, rather than a global one.
+
+Accordingly, the ideal control law $\rbu^*$ can be approximated by the DNN with the ideal weight vector $\idealNN:=\NN({\q}_n;\idealwth)$ as follows:
 \begin{align}
@@
 \end{align}
-where $\mv\epsilon\in\R^n$ is the approximation error vector, which is bounded by $\norm{\mv\epsilon}\le \bar{\epsilon}$.
-The approximated control input $\rbu^*$ is estimated online by
+where $\mv\epsilon\in\R^n$ is the approximation error vector, bounded by $\norm{\mv\epsilon}\le \bar{\epsilon}$.
+The control input $\rbu^*$ is estimated online by
 \begin{align}
@@
 \end{equation}
-Finally, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$).
-Importantly, input (voltage) saturation
-is not yet considered; this will be done next.
-Note that the control input saturation is not considered in derivation of the ideal control input; this will be addressed in further section.
+Therefore, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$), neglecting the effect of input saturation.
+Note that the control input saturation has not yet been considered in the derivation of the ideal control input; this will be addressed in the subsequent section.
 
@@
 Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \ddtfrac{\idealact_i}{\idealNN_{i-1}}$. 
-Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \ddtfrac{\estact_i}{\estNN_{i-1}}$, respectively.
+Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \ddtfrac{\estact_i}{\estNN_{i-1}}$.
 
@@
 Inequality constraints $c_j:=c_j(\estwth),\ \forall j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
-Here, $\fe$ is considered a pre-defined data or parameter for this optimization problem. The Lagrangian function is defined as
+Here, $\fe$ is considered a pre-defined data or static parameter for this optimization problem, so that the adaptation process does not consider the dynamics of $\fe$.
+The Lagrangian function is defined as
 \begin{equation}
@@
             \\
-            \lambda_j & = \max(\lambda_j,0) ,
+            \lambda_j & \leftarrow \max(\lambda_j,0) ,
         \label{eq:adap:lbd:max}
@@
 
-This paper presented a constrained optimization-based neuro-adaptive controller (CONAC) for the uncertain Euler-Lagrange system, addressing both weight and input constraints through a rigorous optimization framework.
-The stability of the proposed controller was analyzed using Lyapunov theory, ensuring that the system maintained bounded tracking and estimation errors under real-time adaptation.
-
-The controller effectively incorporated both the input (bound or norm) constraint and the weight norm constraint, ensuring that both actuator limitations and neural network weights were kept within predefined bounds.
-By formulating these constraints as part of the optimization process, CONAC ensured that the weights converged in a way that satisfied the Karush-Kuhn-Tucker (KKT) conditions, guaranteeing optimality and stability.
-
-A real-time implementation validated the superior performance of CONAC compared to conventional method. 
-The CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
-
-Future work may extend this approach to address constraints on both the system inputs and states, further enhancing the flexibility and robustness of neuro-adaptive control systems using constrained optimization.
+This paper proposed a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems, addressing both weight norm and input constraints through a rigorous optimization framework.
+The stability of the proposed controller was analyzed via Lyapunov theory, demonstrating bounded tracking and estimation errors under real-time adaptation.
+
+The controller effectively incorporated both convex input constraints and weight norm constraints, ensuring that actuator limitations and neural network parameters\MSRY{Weight?} remained within predefined bounds.
+By embedding these constraints into the optimization process, CONAC ensured convergence of the weights in accordance with the Karush-Kuhn-Tucker (KKT) conditions, thereby achieving both stability and optimality.
+
+A real-time implementation validated the superior performance of CONAC compared to conventional methods. 
+The proposed controller successfully handled complex input constraints while rigorously managing weight norms, resulting in improved tracking accuracy and stable performance without significant oscillations.
+
+Future work may extend this approach to include constraints on both control inputs and system states, further enhancing the flexibility and robustness of neuro-adaptive control systems within constrained optimization frameworks.
 
@@
 degree in mechanical engineering from Gwangju Institute of Science and Technology (GIST), South Korea, in 2025.
-    He is currently pursuing the Ph.D. degree in mechanical engineering at GIST.
-
+    He is currently serving as a researcher at the Cho Chun Shik Graduate School of Mobility, KAIST, South Korea.
     His research interests include adaptive control, neural-networks, and constrained optimization.
@@
 \begin{IEEEbiography}[{
-    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/khChoi.jpg}}]{IEEE Publications Technology Team}
-    In this paragraph you can place your educational, professional background and research and other interests.
+    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/khChoi.jpg}}]{Kyunghwan Choi}
+    Kyunghwan Choi received his B.S., M.S., and Ph.D.
+degrees in Mechanical Engineering from KAIST, Daejeon, South Korea, in 2014, 2016, and 2020, respectively.
+Following his Ph.D., he worked at the Center for Eco-Friendly \& Smart Vehicles at KAIST as a Postdoctoral Fellow and later as a Research Assistant Professor.
+In 2022, he joined GIST as an Assistant Professor in the Department of Mechanical and Robotics Engineering.
+Currently, he serves as an Assistant Professor at the Cho Chun Shik Graduate School of Mobility at KAIST, where he is also the Director of the Mobility Intelligence and Control Laboratory.
+His research focuses on optimal and learning-based control for connected, automated, and electrified vehicles (CAEVs).
 \end{IEEEbiography}

### 2025-05-15 manuscript.tex
ediittt Prof comment

@@
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).
+\MSRY{SAT은 좀더 명확히 하기 위해서 사용하였음; 그렇지 않으면 아래 실험 피규어를 통해 포화를 넘어선 제어가 이ㅔㅂ력된다고 생각할까봐 그렇습니다; ddt의 경우 수식과 통일하기 위함이 맞습니다.}}
     \label{fig:ctrl:diagram}
@@
 
-In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ as $
+\KHCH{control direction과 sign of control input이 서로 다른 의미를 가지고 있지만 독자가 헷갈려할 수도 있을 것 같습니다. 이 부분 고민해주세요.}
+In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ by taking the sign of each entry, \ie
+$
     \pptfrac{\fe}{\rbu}
@@
     \right]_{i,j\in\{1,\cdots,m\}}
-$ using the sign of each entry, \ie control direction.
-However, this method is not suitable for \eqref{eq:sys:filtered}, since the control directions are unknown, but the sign of the control input is known, \ie $\rbM^{-1}$ is positive definite matrix in the view of Property \ref{prop:M}.
-Therefore, we propose to approximate $\pptfrac{\fe}{\rbu}$ as $\pptfrac{\fe}{\rbu}\approx \mm I_n$ and one can conclude \eqref{eq:adap:th} as follows:
+$ 
+assuming known control directions.
+However, this approach is not applicable to \eqref{eq:sys:filtered}, where control directions are unknown.
+Instead, since the sign of the control input is known—owing to the positive definiteness of $\rbM^{-1}$ (see, Property \ref{prop:M})—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
+Consequently, the adaptation law in \eqref{eq:adap:th} becomes:
 \begin{equation}
@@
 
-This section introduces essential constraint to be imposed for the stability of the proposed CONAC, and conditions for the potential control input constraints.
+This section introduces essential constraints required to ensure the stability of the proposed CONAC, as well as candidate conditions for potential control input constraints.
 
@@
 
-Next, we introduce the conditions for the potential control input constraints presented in Appendix \ref{sec:appen:cstr} as follows:
+Next, we present the following assumptions, which specify the conditions for the potential control input constraints introduced in Appendix \ref{sec:appen:cstr}:
 
 \begin{assum}
-    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$ are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ \color{red} and $c_j(\idealwth)\le 0$ \color{black}.
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$, are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ \color{red} and $c_j(\idealwth)\le 0$ \color{black}.
 \MSRY{desired controller가 제약조건 밖으로 나갈 수 있기 때문에 적절하지 않을 수 있음}
@@
 \begin{remark}
-    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex in practice including the origin.
+    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex\KHCH{앞에 convex라는 표현이 나오지 않았는데 확인부탁합니다.}\MSRY{컨벡스란 말이 없지만 practical하게 대부분의 포화 함수는 컨벡스라는 말을 의도하였습니다.} in practice including the origin.
     Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
@@
 \begin{lem}
-    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} hold, then for each active constraint $c_j$, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive; that is $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
     \label{lem:convex:angle}
@@
 
-Since $\rbu = \estNN$, using Proposition \ref{propsit:kron}, a linear map $\mm T(\cdot):\estwth_k\to\rbu$ which is independent of $\estwth_k$, can be derived: 
+Since $\rbu = \estNN$, using Proposition \ref{propsit:kron}, a linear mapping $\mm T(\cdot):\estwth_k\to\rbu$ that is independent of $\estwth_k$, can be derived using Proposition \ref{propsit:kron}:
 \begin{equation}\label{eq:linear:map}
@@
 \end{equation}
-Therefore, the convexity of the input constraints in $\rbu$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
+Therefore, the convexity of the input constraints in the $\rbu$-space (see, Assumption \ref{assum:convex}) is preserved in $\estwth_k$-space, implying
 that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
@@
 
-The following theorem shows that $\estwth$ and $\fe$ are bounded.
+The following theorem states that $\estwth$ and $\fe$ are bounded.
 
 \begin{theorem}
-    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$ under control input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}
+    For the dynamical system described in \eqref{eq:sys1}, the neuro-adaptive controller in \eqref{eq:control:est} with the weight adaptation laws in \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
     This holds with the weight norm constraint \eqref{eq:cstr:weight:ball}.
@@
 % The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
-Invoking the fact that amplitude of the control input is only depends on $\estwth_k$, \ie see, \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.
+Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights follows once the boundedness of $\estwth_k$ and $\fe$ is established.
 Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ is supposed to be active.
-This assumption is reasonable, since even if $c_{\theta_i}$ is inactive, $\estwth$ is adapted to reduce $J(·)$ without considering the constraint, unless $c_{\theta_i}$ is
-violated.
-We consider two cases: control input is saturated, and control input is not saturated.
+This assumption is justified because, even if $c_{\theta_i}$ is inactive, $\estwth$ is adapted to minimize the objective function $J(·)$ as long as the constraint is not violated.
+We consider two cases: (1) the control input is saturated, and (2) the control input is not saturated.
 
@@
 
-As the result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative) can be obtained using Lemma \ref{lem:stable:set} as follows:
+As a\MSRY{a?} result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative) can be obtained using Lemma \ref{lem:stable:set} as follows:
 \begin{equation}
@@
 
-The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
-For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{1}$ is squeezed to a point.
-The satisfactions of the remaining control input constraints can be verified implicitly using ${\gamma}_2$ in \eqref{eq:lya2:dot}.
-Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does ${\gamma}_2$.
+The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
+For the weight constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
+The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
+Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, leading to increase in ${\gamma}_2$.
 It makes ${\gamma}_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
-This drives $\estwth_k$ to the origin until the constraint is satisfied, \ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space.
-
-Therefore, the boundedness of $\estwth_k$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{1}$ and $\Theta_{\theta_k}^{1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.
+This drives $\estwth_k$ to the origin until the constraint is satisfied.
+By Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in the $\estwth_k$-space.
+
+Therefore, the boundedness of $\estwth_k$ and $\fe$ is guaranteed by the invariant sets $\Theta_{\fe}^{1}$ and $\Theta_{\theta_k}^{1}$, and the satisfactions of $c_j,\ \forall j\in\mathcal{I}$ is ensured.
 
@@
 
-Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{\{i\in[0,\cdots,k\}}$ in \eqref{eq:lya2:dot} can be removed.
-Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
+Since, the control input constraints are inactive, the saturation function $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and the constraint functions $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{\{i\in[0,\cdots,k\}}$ in \eqref{eq:lya2:dot} can be removed.
+Consider the Lyapunov function candidate $V_3:=V_1+V_2$, whose time derivative is given by:
 \begin{equation}
@@
 \end{equation}
-Like in Case 1, the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{2}$ defined as
+Following the same reasoning as in Case 1, the boundedness of $\fe$ is ensured by the invariant set:
 \begin{equation}
@@
 \end{equation}
-The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ exists positive unless $c_{\theta_k}$ is satisfied.
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ remains positive unless the weight constraint $c_{\theta_k}$ is satisfied.
 
@@
 
-The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$ can be shown recursively, using \cite[Chap.~4 Thm.~1.9]{Desoer:2009aa}.
-The dynamics of $\estwth_i,\ \forall i\in\{k-1,\cdots,0\}$ are represented as
+The boundedness of the inner-layer weights and the satisfaction of their corresponding constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$, can be established recursively using \cite[Chap.~4 Thm.~1.9]{Desoer:2009aa}.
+The dynamics of $\estwth_i,\ \forall i\in\{k-1,\cdots,0\}$, are represented as
 \begin{equation}
@@
 \end{equation}
-Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in\{k,\cdots,i+1\}$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
-Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
+By Lemma \ref{lem:cstr:grad:bound} $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in\{k,\cdots,i+1\}$, are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+Therefore, starting from the $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
 
@@
 
-Finally, the filtered error $\fe$ and the estimated weights $\estwth$ are bounded and the imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
+In conclusion, the filtered tracking error $\fe$ and the entire set of estimated weights $\estwth$ are bounded, and all imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
 
@@
     \caption{
-        Robot setup for the real-time experiment.
+        Experimental setup of the two-link robotic manipulator used for real-time validation.
     }
@@
 The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
-The system dynamics of the two-link manipulator can be represented as Euler-Lagrange equation \eqref{eq:sys1} and described as Fig.~\ref{fig:robot:model}, and the estimated system parameters are provided in Table~\ref{table:system:params}.
+The system dynamics of the two-link manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and are illustrated in Fig.~\ref{fig:robot:model}. 
+The estimated system parameters are provided in Table~\ref{table:system:params}.
 
@@
 % ------------------------------------
-The desired trajectory for $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using the quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
-The desired trajectory is defined as follows:
+The desired trajectory $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, which satisfy the initial and final joint angles $\mv{x}_1$ and $\mv{x}_2$, as well as zero initial and final joint velocities.
+Here, $t_f$ denotes the duration of each segment.
+The desired (reference) trajectory is defined as follows:
 \begin{equation}
@@
     \begin{pmatrix}
-        {\qd}_1
-        \\
-        {\qd}_2
+        {q_d}_1
+        \\
+        {q_d}_2
     \end{pmatrix}
@@
     \begin{cases}
-    \mathcal{P}^5(t;{\qd}_0,{\qd}_1,t_f),
+    \mathcal{P}^5(t;\mv{q}_d^{(0)},\mv{q}_d^{(1)},t_f),
         &
@@
         \\
-    \mathcal{P}^5(t;{\qd}_1,{\qd}_2,t_f),
+    \mathcal{P}^5(t;\mv{q}_d^{(1)},\mv{q}_d^{(2)},t_f),
         &
@@
         \\
-    \mathcal{P}^5(t;{\qd}_2,{\qd}_1,t_f),
+    \mathcal{P}^5(t;\mv{q}_d^{(2)},\mv{q}_d^{(1)},t_f),
         & 
@@
         \\
-    \mathcal{P}^5(t;{\qd}_1,{\qd}_0,t_f),
+    \mathcal{P}^5(t;\mv{q}_d^{(1)},\mv{q}_d^{(0)},t_f),
         &    
@@
 \end{equation}
-where ${\qd}_0:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s, and illustrated in Fig.~\ref{fig:robot:model}.
-To demonstrate the learning capability of DNN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.
+where 
+$
+    \mv{q}_d^{(0)}:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top
+$, 
+$
+    \mv{q}_d^{(1)}:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top
+$, 
+$
+    \mv{q}_d^{(2)}:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top
+$, 
+and $t_f=3$ s, and the reference trajectory is illustrated in Fig.~\ref{fig:robot:model}.
+To demonstrate the learning capability of the DNN, the desired trajectory was applied twice. 
+The first and second repetitions of the reference trajectory are referred to as Episode $1$ and Episode $2$, respectively.
 
@@
 degree in mechanical engineering from Gwangju Institute of Science and Technology (GIST), South Korea, in 2025.
-    He is currently serving as a researcher at the Cho Chun Shik Graduate School of Mobility, KAIST, South Korea.
+    He is currently serving as a researcher at the Cho Chun Shik Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), South Korea.
     His research interests include adaptive control, neural-networks, and constrained optimization.
@@
 \begin{IEEEbiography}[{
-    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/dhHong.jpg}}]{IEEE Publications Technology Team}
-    In this paragraph you can place your educational, professional background and research and other interests.
+    \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/dhHong.jpg}}]{Donghwa Hong}
+    Donghwa Hong received his B.S.
+degree in Physics and Engineering Physics from Yonsei University, Wonju, South Korea, in 2023.
+He is currently pursuing the M.S.
+degree in Mechanical Engineering from GIST, Gwangju, South Korea.
+His research interests include robot control, neural-networks, and model identification. 
 \end{IEEEbiography}

### 2025-05-19 IWIS_manuscript.tex
IWIS update

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\makeatletter
\let\NAT@parse\undefined
\makeatother

\def\pub{true} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_conf.tex}

\title{\LARGE \bf
    WIP: Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Constrained Systems
}

\author{Myeongseok Ryu, and Kyunghwan Choi% <-this % stops a space
    \thanks{
        Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small \{dding\_98, kh.choi\}@kaist.ac.kr}
    }%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    This paper reports on work in progress to review and improve the effectiveness of the constrained optimization-based neuro-adaptive control (CONAC) for weight, control input, and state constraints.
    Our preliminary results show that the CONAC can handle the weight constraints and control input constraints.
  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing the constraints within a constrained optimization framework.
  The weight adaptation laws are formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
  The CONAC is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
  Finally, we discuss the extension of the CONAC to handle state constraints, which is a crucial aspect for practical applications in various engineering systems.
\end{abstract}

\section{Introduction}

Many engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
To address these uncertainties, adaptive control techniques have been widely employed.

More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs). 
NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations. 
SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2015aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}. 
Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.

A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated. 
Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.

However, significant challenges persist in using NNs for adaptive control. 
First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs. 
When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. 
Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{Esfandiari:2021aa}. 
Failing to address these constraints can degrade control performance or even destabilize the system.
Moreover, the excessive control inputs may lead to violations of the state constraints, which are often related to safety and performance requirements in practical applications.
Therefore, addressing these constraints is essential for the reliable design of neuro-adaptive controllers.

\section{Constrained Optimization-based Neuro-Adaptive Control}

In this section, we revisit our previous work on the constrained optimization-based neuro-adaptive control (CONAC) for weight \cite{Ryu:2024aa} and control constraints \cite{Ryu:2024ab,Ryu:2025aa}.

\subsection{CONAC for Weight Constraints}

In \cite{Ryu:2024aa}, we proposed the first version of the CONAC to handle weight constraints.
By formulating the boundedness of the NN weights as a inequality constraint, a unified constrained optimization problem was defined as follows:
\begin{equation}
    \begin{matrix}
        \min_{\estwth} \ J(\mv{e};\estwth):= 
        \tfrac{1}{2} \mv{e}^\top \mv{e}
        \\ \\
        \begin{aligned}
        \text{subject to }&
            c_i(\estwth)
            :=
            \tfrac{1}{2}
            \left(
                \estwth_i^\top \estwth_i - {\bar\theta}_i^2
            \right)
        \le0, \quad \forall i\in\{0,\ldots,k\} \\
        \end{aligned}
        ,
    \end{matrix}
    \label{eq:opt:problem1}
\end{equation}
where $J(\cdot)$ denotes the objective function, $c_i(\cdot)$ denotes the constraint function, $\estwth=[\estwth_i]_{\{0,\cdots,k\}}$ is the vector of NN weights, $\mv{e}$ is the tracking error, and $\bar\theta_i$ is the upper bound of the $i\textsuperscript{th}$ layer's weight of $k$ layers.
The optimization problem \eqref{eq:opt:problem1} was reformulated as a Lagrangian function as follows:
$
    L(\estwth,\mv{\lambda}) = J(\mv{e};\estwth) + \sum_{i=0}^k \lambda_i \tfrac{1}{2}(\estwth_i^\top \estwth_i - {\bar\theta}_i^2)
    ,
$
where $\lambda_i$ is the Lagrange multiplier associated with the $i\textsuperscript{th}$ constraint $c_i(\estwth)$.
To solve the dual problem of the Lagrangian function, the adaptation law was derived using gradient descent method for weight adaptation and gradient ascent method for Lagrange multipliers as follows:
\begin{subequations}
    \begin{align}
            \ddtt{\estwth}
            &
            =
            -\alpha \pptfrac{L}{\estwth}
            =
            -\alpha 
            \left(
                \pptfrac{J}{\estwth}
                +
                \textstyle\sum_{i=0}^k
                \lambda_i
                \pptfrac{c_i}{\estwth}
            \right),
        \label{eq:adap:th}
            \\
            \ddtt\lambda_i
            & 
            = 
            \beta_i\pptfrac{L}{\lambda_i} 
            = 
            \beta_i c_i ,
            \quad \forall i\in\{0,\ldots,k\}
        \label{eq:adap:lbd}
            \\
            \lambda_i & \leftarrow \max(\lambda_i,0) ,
        \label{eq:adap:lbd:max}
    \end{align}
    \label{eq:adaptation law}%             %%
\end{subequations}

The stability of the CONAC under weight constraints was rigorously analyzed using Lyapunov theory, \ie see, Theorem 1 in \cite{Ryu:2024aa}.
The theorem guarantees that the tracking error $\mv{e}$ and the DNN weights $\estwth$ are bounded, ensuring that weight constraints are satisfied.

The numerical simulation demonstrated the effectiveness of the CONAC in handling weight constraints in a 2-DOF robotic manipulator system, comparing the existing adaptive control methods including $\epsilon$-modification and $\sigma$-modification methods.
The results showed that the CONAC outperformed these methods in terms of tracking performance and weight constraint satisfaction with smaller dependency on the tuning parameters.

\subsection{CONAC for Control Constraints}

The CONAC was further extended to handle control input constraints in \cite{Ryu:2024ab,Ryu:2025aa}.
In \cite{Ryu:2024ab}, the CONAC was formulated to handle a control input saturation defined as $\mysat(\mv{u})=\tfrac{\mv{u}}{\norm{\mv{u}}}\cdot\bar{u}$ if $\norm{\mv{u}}>\bar{u}$, and $\mv{u}$ otherwise, where $\bar{u}$ is the upper bound of the control input.
Furthermore, the CONAC was extended for any convex control input constraints in \cite{Ryu:2025aa}.

In other words, the control input constraint is defined as an inequality constraint as follows:
\begin{equation}
    \begin{matrix}
        \min_{\estwth} \ J(\mv{e};\estwth):= 
        \tfrac{1}{2} \mv{e}^\top \mv{e}
        \\ \\
        \begin{aligned}
        \text{subject to }&
        \tfrac{1}{2}
            \left(
                \estwth_i^\top \estwth_i - {\bar\theta}_i^2
            \right)
        \le0, &\forall 0\in\{1,\ldots,k\}, \\
        &
        c_j(\estwth) \le 0, &\forall j\in\mathcal{I}
        ,
        \end{aligned}
    \end{matrix}
    \label{eq:opt:problem2}
\end{equation}
where $c_j(\estwth)$ denotes convex constraint function, and $\mathcal{I}$ is the set of indices of the convex constraints.
For example, the 
$
    \tfrac{1}{2}
    \left(
        \norm{\mv{u}}^2 - {\bar u}^2
    \right)
    \le0
$
is imposed for the case of \cite{Ryu:2024ab}.

The adaptation law is derived using the same approach as in \eqref{eq:adaptation law}.
The stability of the extended CONAC was also analyzed using Lyapunov theory, ensuring that the tracking error $\mv{e}$ and the DNN weights $\estwth$ are bounded, and the control input constraints are satisfied.

To demonstrate the effectiveness of the CONAC, a numerical simulation was conducted on a nonlinear synchronous machine drive with control input constraints \cite{Ryu:2024ab} and real-time implementation on a 2-DOF robotic manipulator \cite{Ryu:2025aa}.
Both results showed that the CONAC can effectively handle control input constraints while achieving accurate trajectory tracking.

\section{Extension to State Constraints}

The preliminary results of the CONAC for weight and control input constraints are promising.
However, for safety and performance requirements in practical applications, it is crucial to extend the CONAC to handle state constraints.
We are currently working on this extension to handle state constraints by integrating the existing methods for state constraints such as barrier Lyapunov functions (BLFs) \cite{Ames:2019aa}.
This extension can be applied to various control problems, including robotic systems with limited manipulability, vehicle systems with limited velocity, and other systems with state constraints.

\section{Conclusion}

In this paper, we reviewed our previous work on the constrained optimization-based neuro-adaptive controller (CONAC) for weight and control input constraints and presented further development.
The CONAC has shown promising results in numerical simulations and real-time implementations, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
Moreover, since the NNs in the CONAC have the online learning capability and stability guarantee, the CONAC can be applied to various engineering systems with uncertainties and constraints, even in systems with no prior knowledge of the dynamics.
The extension to handle state constraints is an important step towards practical applications, and we are actively working on this aspect.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{APPENDIX}

% Appendixes should appear before the acknowledgment.

% \section*{ACKNOWLEDGMENT}

% The preferred spelling of the word ÒacknowledgmentÓ in America is without an ÒeÓ after the ÒgÓ. Avoid the stilted expression, ÒOne of us (R. B. G.) thanks . . .Ó  Instead, try ÒR. B. G. thanksÓ. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% {\footnotesize
    \bibliographystyle{ieeetr}
    \bibliography{\template/refs}
% }

\end{document}

### 2025-05-19 IWIS_manuscript.tex
IWIS update final

@@
-\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
+% \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper
+\documentclass[conference]{IEEEtran}
 
@@
 
-\overrideIEEEmargins                                      % Needed to meet printer requirements.
+% \overrideIEEEmargins                                      % Needed to meet printer requirements.
 
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
+% \makeatletter
+% \let\NAT@parse\undefined
+% \makeatother
 
@@
 
-\title{\LARGE \bf
-    WIP: Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Constrained Systems
-}
-
-\author{Myeongseok Ryu, and Kyunghwan Choi% <-this % stops a space
-    \thanks{
-        Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Republic of Korea {\tt\small \{dding\_98, kh.choi\}@kaist.ac.kr}
-    }%
-}
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+\pagestyle{empty}
 
@@
 
+\title{\LARGE \bf
+    Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Constrained Systems
+}
+
+\author{
+    \IEEEauthorblockN{1\textsuperscript{st}\,Myeongseok\,Ryu and 2\textsuperscript{nd}\,Kyunghwan\,Choi}
+    \IEEEauthorblockA{\textit{Cho Chun Shik Graduate School of Mobility} \\
+    \textit{Korea Advanced Institute of Science and Technology}\\
+    Daejeon, Republic of Korea \\
+    \{dding\_98, kh.choi\}@kaist.ac.kr}
+    }
+
 \maketitle
 \thispagestyle{empty}
-\pagestyle{empty}
+% \pagestyle{empty}
 
@@
     Our preliminary results show that the CONAC can handle the weight constraints and control input constraints.
-  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing the constraints within a constrained optimization framework.
-  The weight adaptation laws are formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
-  The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
-  The CONAC is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
+  A neural network (NN) was employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing the constraints within a constrained optimization framework.
+  The controller's stability was rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded NN weights. 
+  The CONAC was validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
   Finally, we discuss the extension of the CONAC to handle state constraints, which is a crucial aspect for practical applications in various engineering systems.
 \end{abstract}
+\begin{IEEEkeywords}
+	Neuro-adaptive control, Constrained Optimization, Constrained Systems
+\end{IEEEkeywords}
 
@@
 The stability of the CONAC under weight constraints was rigorously analyzed using Lyapunov theory, \ie see, Theorem 1 in \cite{Ryu:2024aa}.
-The theorem guarantees that the tracking error $\mv{e}$ and the DNN weights $\estwth$ are bounded, ensuring that weight constraints are satisfied.
+The theorem guarantees that the tracking error $\mv{e}$ and the NN weights $\estwth$ are bounded, ensuring that weight constraints are satisfied.
 
@@
 The adaptation law is derived using the same approach as in \eqref{eq:adaptation law}.
-The stability of the extended CONAC was also analyzed using Lyapunov theory, ensuring that the tracking error $\mv{e}$ and the DNN weights $\estwth$ are bounded, and the control input constraints are satisfied.
+The stability of the extended CONAC was also analyzed using Lyapunov theory, ensuring that the tracking error $\mv{e}$ and the NN weights $\estwth$ are bounded, and the control input constraints are satisfied.
 

### 2025-05-19 manuscript.tex
IWIS update
comment on paper

@@
 
-\addbibresource{\template/refs.bib}
+% \addbibresource{\template/refs.bib}
 
@@
   The proposed controller is validated through a real-time implementation on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
-
-  via a real-time implementation conducted on a 2-DOF robotic manipulator, demonstrating the controller's effectiveness in achieving desired trajectory tracking while satisfying constraints.
 \end{abstract}
@@
 \subsection{Organization}
-
-\MSRY{Started from here}
 
@@
     For the dynamical system described in \eqref{eq:sys1}, the neuro-adaptive controller in \eqref{eq:control:est} with the weight adaptation laws in \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
-    This holds with the weight norm constraint \eqref{eq:cstr:weight:ball}.
+    This holds under the weight norm constraint \eqref{eq:cstr:weight:ball}.
 \end{theorem}
@@
 % The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
-Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights follows once the boundedness of $\estwth_k$ and $\fe$ is established.
+Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, and \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights follows once the boundedness of $\estwth_k$ and $\fe$ is established.
 Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ is supposed to be active.
@@
 The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
-For the weight constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
+For the weight constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large \MSRY{본래 infinitely였습니다만 무한까지 가는 것을 가정하지 않기 때문에 충분히 커질때로 바꿈} due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
 The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
-Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, leading to increase in ${\gamma}_2$.
+Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases sufficiently large \MSRY{위와 같은 이유로 변경}, leading to increase in ${\gamma}_2$.
 It makes ${\gamma}_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
@@
 
+\KHCH{여기 아래부터는 글이 많아서 표현 수정을 하나씩 하지 못했습니다. 우선 아래에 있는 메모 반영해주시고, 최종적으로 chatGPT 등 통해서 표현 정리해주세요.
+
+표현이 조금 어색하거나 구어스러운 부분들이 있습니다.}
+
 However, since the DNN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
@@
 \end{subequations}
-These sets \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
-
+These sets, \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, can be physically interpreted as the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
+\KHCH{
+    (30a)의 의미를 다음과 같이 바꾸는게 명확하겠습니다. 
+    These sets, (30a) and (30b), can be physically interpreted as the current limitation imposed by the power source and the torque limitation of the second joint actuator, respectively.
+}
+\MSRY{
+    전압 제한이 곧 전류 제한인 것인가요?
+    전류 제한이라 하면 상태에 대한 제약조건이 부여된 것인가라는 오해가 생길가 걱정입니다.
+}
+The corresponding control input constraints of \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, are defined in Appendix \ref{sec:appen:cstr} as input bound constraint \eqref{eq:cstr:input:norm} and nonlinear input norm constraint \eqref{eq:cstr:input:bound}, respectively.
+\MSRY{sets들과 제약조건을 이어주기 위하여 추가}
+
+% ------------------------------------
+% Comparative Study
+% ------------------------------------
 \hfill
-
-% ------------------------------------
-% Comparative Study
-% ------------------------------------
 For a comparative study, we implemented 4 controllers.
@@
 % ------------------------------------
-\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large $\beta_j$}}
+\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large update rate of Lagrange Multipliers, $\beta_j,\forall j\in\mathcal{I}$}}
 
@@
 % ------------------------------------
-\subsubsection*{Controller 2: \normalfont{(C$_2$)} \textit{CONAC with small $\beta_j$}}
+\subsubsection*{Controller 2: \normalfont{(C$_2$)} \textit{CONAC with small update rate of Lagrange Multipliers, $\beta_j,\forall j\in\mathcal{I}$}}
 
@@
 	\hline
-		$e_1\times10^{3}$ / rad & $7.513$ & $8.021$ & $8.408$ & $19.721$ \\
-	\hline
-        $e_2\times10^{3}$ / rad & $2.617$ & $2.435$ & $3.553$ & $4.256$ \\
+    \multirow{2}{*}{$e_1\times10^{3}$ / rad} 
+        & $7.513$ & $8.021$ & $8.408$ & $19.721$ \\
+        & ($-70.0\%$) & ($-63.1\%$) & ($-63.7\%$) & ($-18.5\%$) \\
+    \hline
+    \multirow{2}{*}{$e_2\times10^{3}$ / rad} 
+        & $2.617$ & $2.435$ & $3.553$ & $4.256$ \\
+        & ($-88.4\%$) & ($-76.9\%$) & ($-72.8\%$) & ($-67.1\%$) \\
     \hline
@@
 This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
+\KHCH{
+    문단이 misleading 할 수 있습니다.
+C3가 C4보다는 낫다고 되어 있는데 마지막에는 C3가 poor 하다고 합니다. 명료한 결론으로 바꿔주세요.
+명확하지 않게 C4처럼 constraint를 고려하면 고려안하는 C3보다 더 안 좋아질 수 있다 등의 논리가 필요해보입니다.   
+}
 The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).
@@
 The detail of the constraint handling in the time interval from $29.4$ s to $31.9$ s, is now investigated.
-First, for (C$_4$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. 
+First, for (C$_4$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. \KHCH{FIg6c를 언급하며 설명되면 좋겠습니다}
 As the weights were adapted to reduce not only $\fe$ but also $\mv{\zeta}$, the constraint violation of $c_{\overline\tau_1}$ was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
@@
 % comparison; big, small beta
+\KHCH{여기 아래 부터는, beta의 영향에 대해 설명하는데 lambda가 크고 작음만 언급됩니다. 명료하게 설명 수정해주세요.}
 For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for convex constraint $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
@@
 This allows the controller to show a smoother control input.
+\KHCH{흐름상 잘 이해되지 않습니다}
 However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt the weights with respect to the filtered error $\fe$.
@@
 
+\KHCH{반복해서 이 내용을 설명할 필요가 있을까요?}
 The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
@@
 
-\MSRY{이 부분도 IECON과 마찬가지로 이산으로 돌아감으로 바로 보여주기는 힘들 수 있을 것 같습니다. 실제로 보시면 많은 진동이 보여서 정상상태의 KKT를 주장할 수 있을지 의문입니다.}
-
 Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
 However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of active constraints were positive and inactive constraints were zero.
+
+\MSRY{이 부분도 IECON과 마찬가지로 이산으로 돌아감으로 바로 보여주기는 힘들 수 있을 것 같습니다. 실제로 보시면 많은 진동이 보여서 정상상태의 KKT를 주장할 수 있을지 의문입니다.}
+% reference 자체가 계속 움직이니까 엄밀하게는 steady state를 보장할 수 없습니다. rough 하게는 theta norm이 어느정도 수렴하므로 이 것을 기반으로 주장해볼 수도 있습니다. theta_dot이 평균적으로는 0에 가까운 것 같서요
 
@@
 
-\printbibliography
-
-% \begin{IEEEbiographynophoto}{Jane Doe}
-%     Biography text here without a photo.
-% \end{IEEEbiographynophoto}
+\bibliographystyle{IEEEtran}
+\bibliography{\template/refs}
 

### 2025-05-19 manuscript.tex
minor update

@@
 
-    Donghwa Hong is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: fairytale@gm.gist.ac.kr).
+    Donghwa Hong is with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST), Gwangju 61005, Korea (e-mail: fairytalef00@gm.gist.ac.kr).
 
@@
     \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).
-\MSRY{SAT은 좀더 명확히 하기 위해서 사용하였음; 그렇지 않으면 아래 실험 피규어를 통해 포화를 넘어선 제어가 이ㅔㅂ력된다고 생각할까봐 그렇습니다; ddt의 경우 수식과 통일하기 위함이 맞습니다.}}
+\MSRY{SAT은 좀더 명확히 하기 위해서 사용하였음; 그렇지 않으면 아래 실험 피규어를 통해 포화를 넘어선 제어가 입력된다고 생각할까봐 그렇습니다; ddt의 경우 수식과 통일하기 위함이 맞습니다.}}
     \label{fig:ctrl:diagram}
@@
 \begin{assum}
-    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$, are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ \color{red} and $c_j(\idealwth)\le 0$ \color{black}.
-\MSRY{desired controller가 제약조건 밖으로 나갈 수 있기 때문에 적절하지 않을 수 있음}
+    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$, are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
     \label{assum:convex}
@@
 The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
-For the weight constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large \MSRY{본래 infinitely였습니다만 무한까지 가는 것을 가정하지 않기 때문에 충분히 커질때로 바꿈} due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
+For the weight constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ \color{red}increases sufficiently large\color{black} \MSRY{본래 infinitely였습니다만 무한까지 가는 것을 가정하지 않기 때문에 충분히 커질때로 바꿈} due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
 The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
@@
 \KHCH{여기 아래부터는 글이 많아서 표현 수정을 하나씩 하지 못했습니다. 우선 아래에 있는 메모 반영해주시고, 최종적으로 chatGPT 등 통해서 표현 정리해주세요.
-
 표현이 조금 어색하거나 구어스러운 부분들이 있습니다.}
@@
 However, since the DNN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
-Hence, in advance of the reference trajectory, the manipulator was initially positioned at ${\qd}^{\rm{origin}}=\left(-\tfrac{1}{2}\pi,0\right)^\top$ (\ie stable equilibrium point).
+Hence, in advance of the reference trajectory, the manipulator was initially positioned at ${\qd}^{\rm{origin}}=\left(-\tfrac{1}{2}\pi,0\right)^\top$, \ie stable equilibrium point.
 Then, a reference trajectory was applied to the manipulator to move from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ in 3 seconds, \ie $\mathcal{P}^5(t;{\qd}^{\rm{origin}},{\qd}_0,3)$, which is the initial and final points of the episode.
@@
 
-The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, (\ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.
+The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, \ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.
 
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Quantitative comparison of performances' $L_2$ norm.}
+    \caption{Quantitative\,comparison\,of\,performances'\,$L_2$\,norm.}
     \centering
@@
 The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
-This is because, (as wil be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
+This is because, (as will be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
 \KHCH{
@@
 }
-The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).
-Without consideration of the control input saturation, DDN became confused by the difference between its output (control input) and the saturated control input, which leads to the poor performance of (C$_3$).
+\MSRY{반영 중}
+The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) produced excessively large control inputs which hits the actuator limits, without considering the control input saturation.
+This may lead to the conclusion that CONAC without control input constraints outperformed the auxiliary system.
+However, since the CONAC adapts the weights to reduce the tracking error, \ie which is the only feedback signal, the CONAC increases the control input excessively to reduce the tracking error, which can not be regulated due to the actuator limits.
+In Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, the violations of the control input saturations grow larger in every saturated time interval.
+Moreover, this large violation occurs oscillations in the control input (adaptation),
+
+% The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).
+% Without consideration of the control input saturation, DDN became confused by the difference between its output (control input) and the saturated control input, which leads to the poor performance of (C$_3$).
 

### 2025-05-19 latexdiff.py

@@ -1,117 +1,0 @@
-"""
-latexdiff.py
-- COMMIT1: new commit hash.
-- COMMIT2: old commit hash.
-
-OUTPUT:
-- diff.pdf
-
-- Myeongseok Ryu
-- 2025.04.14
-"""
-
-import os
-import subprocess
-
-COMMIT1 = "6aeb18adc1837a672b27f840c0d8db9bda24ddea" # new
-COMMIT2 = "732664d84fa6e31b4a6167434ca7f8a5d4d41687" # old
-TEX_FILE_NAME = "{tex_file_name}"
-
-SAVE_DIR = "."
-
-def run_terminal_command(command):
-    print(f"$ {command}")
-    os.system(command)
-
-def compile_tex(file_name):
-    run_terminal_command("pdflatex -interaction=batchmode {file_name}")
-    run_terminal_command("bibtex {file_name[:-4]}.aux")
-    run_terminal_command("pdflatex -interaction=batchmode {file_name}")
-    run_terminal_command("pdflatex -interaction=batchmode {file_name}")
-
-def clean_up():
-    print("Cleaning up...")
-    run_terminal_command("rm tmp1.tex")
-    run_terminal_command("rm tmp2.tex")
-    run_terminal_command("rm tmp1.pdf")
-    run_terminal_command("rm tmp2.pdf")
-    run_terminal_command("rm diff.tex")
-    run_terminal_command("rm *.aux")
-    run_terminal_command("rm *.log")
-    run_terminal_command("rm *.out")
-    run_terminal_command("rm *.bbl")
-    run_terminal_command("rm *.blg")
-    run_terminal_command("rm *.run.xml")
-    run_terminal_command("rm *.toc")   
-    run_terminal_command("rm *.synctex.gz")
-    run_terminal_command("rm *.fdb_latexmk")
-    run_terminal_command("rm *.fls")
-    run_terminal_command("rm *.spl")
-    run_terminal_command("rm *.dvi")
-
-def main():
-    print(f"""  
-        *** LATEXDIFF ***
-        Myeonsgeok Ryu
-
-        INPUT OPTIONS:
-        - r: current working tree
-        - h: HEAD
-        - p: relatively previous
-        """)
-
-    # -----------------------------
-    # Get input arguments
-    # -----------------------------
-    tex_file_name = input(f"Enter the tex file name (default: {TEX_FILE_NAME}): ")
-
-    if tex_file_name == "":
[…]

### 2025-05-20 src/measurement/main_plotter.m
add new measurement

@@ -1,7 +1,7 @@
 clear
 
 %%
-SAVE_FLAG = 0;
+SAVE_FLAG = 1;
 POSITION_FLAG = 1; % it will plot fiugures in the same position
 TEX_CONVERT_FLAG = 0;
 gray = "#808080";
@@ -32,10 +32,15 @@ else
 end
 
 %% 
-ctrl1_name = "c1.trc"; 
-ctrl2_name = "c2.trc";
-ctrl3_name = "c3.trc"; 
-ctrl4_name = "c4.trc"; 
+% ctrl1_name = "c1.trc"; 
+% ctrl2_name = "c2.trc";
+% ctrl3_name = "c3.trc"; 
+% ctrl4_name = "c4.trc"; 
+
+ctrl1_name = "re_c1.trc"; 
+ctrl2_name = "re_c3.trc";
+ctrl3_name = "re_c4.trc"; 
+ctrl4_name = "re_c2.trc"; 
 
 data1 = trc2data(ctrl1_name, 1);
 data2 = trc2data(ctrl2_name, 2);

### 2025-05-25 manuscript.tex
add new measurement
peer review 1 finished; new video!

@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item For $\mm{A}\in\R^{n\times m}$, denotes the vectorization of $\mm A$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top$.
+    \item For $\mm{A}\in\R^{n\times m}$, denotes the vectorization of $\mm A$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top\in\R^{nm}$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
 NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
-Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations.
-SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}.
-Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations.
+SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
+However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa} and physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
 
@@
 These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. 
-Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.
+Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights by biasing the adaptation law toward the origin \cite{Ryu:2024aa}.
+This leaves room for improvement in terms of performance optimization.
+
+\hfill
 
@@
 This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
-In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.
+In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs \cite{Khalil:2002aa}.
 
@@
 In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
-However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+However, these approaches typically handle input bound constraints on a per-input basis, \ie applying bounds to each scalar control variable individually, and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+
+\hfill
 
@@
 Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
-Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.
+Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints.
 
 To overcome these limitations, constrained optimization offers a promising approach. 
-By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (\eg tracking error) subject to both weight norm and input constraints.
+By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function, \eg tracking error, subject to both weight and input constraints.
 Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.
@@
 However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation. 
-This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.
+This gap suggests that constrained optimization could be key to addressing both weight boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.
 
@@
 
-\KHCH{Abstract에 있는 것처럼 이 내용도 하나 추가해두죠.
-
-The controller’s stability is rigorously
-analyzed using Lyapunov theory, guaranteeing bounded
-tracking errors and DNN weights.}
+\MSRY{일단 제가 생각하는 기여를 모두 적었습니다.}
 
@@
     \item A constrained optimization-based neuro-adaptive controller (CONAC) is proposed, where the design of a deep neural network (DNN) is formulated as a constrained optimization problem.
-In this formulation, weight norm and convex input constraints are incorporated as inequality constraints, while minimizing a given objective function.
-    % \item A constrained optimization-based neuro-adaptive controller (CONAC) is developed using a DNN, where input constraints and the boundedness of DNN weights are formulated as inequality constraints within the adaptation process.
-    \item The adaptation laws for DNN weights in CONAC are systematically derived to solve the defined problem, using constrained optimization theory.
+In this formulation, weight and convex input constraints are incorporated as inequality constraints, while minimizing a given objective function.
+    \item Any convex input constraints can be applied to the proposed CONAC, including input bound constraints, and norm constraints.
+Moreover, the proposed CONAC can handle any combination of these constraints, which can be useful in practical applications where multiple constraints need to be satisfied simultaneously.
+    \item Since the proposed CONAC approximate the entire ideal control law with no prior knowledge of the system dynamics, the system identification process can be avoided, which is often difficult and time-consuming to implement in practice.
+    \item The adaptation laws for DNN weights in proposed CONAC are systematically derived to solve the defined problem, using constrained optimization theory.
 These laws guarantee convergence to the first-order optimality conditions, specifically the Karush–Kuhn–Tucker (KKT) conditions, as described in \cite[Chap.
@@
 12.1]{Nocedal:2006aa}.
-    % \item The weight adaptation laws in CONAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints.
-The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions defined in \cite[Chap.
-12 Thm.
-12.1]{Nocedal:2006aa}.
-    % \item The forward sensitivity method is applied in CONAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
-    %, enabling more precise real-time adaptation.
+    \item The proposed CONAC's stability is rigorously analyzed using Lyapunov theory, ensuring that the tracking error and DNN weights remain bounded.
+This analysis guarantees that the proposed CONAC can achieve stable adaptation online.
+    \item The proposed CONAC is implemented in real-time on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
+The experimental results validate the theoretical findings and show the practical applicability of the proposed controller.
 \end{itemize}
@@
 
-\KHCH{control direction과 sign of control input이 서로 다른 의미를 가지고 있지만 독자가 헷갈려할 수도 있을 것 같습니다. 이 부분 고민해주세요.}
 In \cite{Douratsos:2007aa,Saerens:1991aa}, the authors approximate $\pptfrac{\fe}{\rbu}$ by taking the sign of each entry, \ie
@@
 However, this approach is not applicable to \eqref{eq:sys:filtered}, where control directions are unknown.
-Instead, since the sign of the control input is known—owing to the positive definiteness of $\rbM^{-1}$ (see, Property \ref{prop:M})—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
+Instead, since the sign of the control input matrix is known—owing to the positive definiteness of $\rbM^{-1}$, see, Property \ref{prop:M}—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
 Consequently, the adaptation law in \eqref{eq:adap:th} becomes:
@@
 
-First, weight constraints are essential to prevent the weights from diverging during the adaptation process.
-The weight constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+First, weight norm constraints are essential to prevent the weights from diverging during the adaptation process.
+The weight norm constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
 \begin{equation}
@@
 Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, and \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights follows once the boundedness of $\estwth_k$ and $\fe$ is established.
-Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ is supposed to be active.
+Without loss of generality, weight norm constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ is supposed to be active.
 This assumption is justified because, even if $c_{\theta_i}$ is inactive, $\estwth$ is adapted to minimize the objective function $J(·)$ as long as the constraint is not violated.
@@
 
-\MSRY{Explain with active set, later}
 To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
@@
 The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
-For the weight constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ \color{red}increases sufficiently large\color{black} \MSRY{본래 infinitely였습니다만 무한까지 가는 것을 가정하지 않기 때문에 충분히 커질때로 바꿈} due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
+For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ \color{red}increases sufficiently large\color{black} \MSRY{본래 infinitely였습니다만 무한까지 가는 것을 가정하지 않기 때문에 충분히 커질때로 바꿈} due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
 The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
@@
 \end{equation}
-The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ remains positive unless the weight constraint $c_{\theta_k}$ is satisfied.
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ remains positive unless the weight norm constraint $c_{\theta_k}$ is satisfied.
 
@@
 
-To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
+To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link robotic manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
 The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
-The two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
+The two-link robotic manipulator actuated by two Cubemars AK10-90 servo motors. 
 The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
-The system dynamics of the two-link manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and are illustrated in Fig.~\ref{fig:robot:model}. 
-The estimated system parameters are provided in Table~\ref{table:system:params}.
+The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and are illustrated in Fig.~\ref{fig:robot:model}. 
+The measured and/or estimated system parameters are provided in Table~\ref{table:system:params}.
 
@@
     \centering
-    \subfloat[Two-link manipulator model.\MSRY{ADD inertia}]{
-        \includegraphics[width=0.75\linewidth]{src/figures/RobotModel.drawio.pdf}
+    \subfloat[Two-link robotic manipulator.\MSRY{ADD inertia}]{
+        \includegraphics[width=0.65\linewidth]{src/figures/RobotModel.drawio.pdf}
         \label{fig:robot:model}
@@
     }
-    \caption{Two-link manipulator model and control saturation function.}
+    \caption{Two-link robotic manipulator and control saturation function.}
     \label{fig:robot}
@@
     \renewcommand{\arraystretch}{1.3}
-    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
+    \caption{Two-link robotic manipulator's parameters.}
     \centering
@@
     \hline
-    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
-    \hline
-    \hline 
-    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
-    \hline
-    $l_p$  & Length & \multicolumn{2}{c}{0.2 (m)} \\  
-    \hline
-    ${l_c}_p$ & Center of mass & \multicolumn{2}{c}{0.139 (m)} \\
-    \hline
-    % $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
-    % \hline
-    % ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
-    % \hline
-    % ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
-    % \hline
-    $I_p$  & Inertia & \multicolumn{2}{c} {0.069 (kgm\textsuperscript{2})} \\
+    \textbf{Symbol} & \textbf{Description} & \textbf{Value} \\
+    \hline
+    \hline 
+    $m_1,m_2$ & Mass & 2.465 kg \\
+    \hline
+    $l_1,l_2$  & Length & 0.2 m \\  
+    \hline
+    ${l_c}_1,{l_c}_2$ & Center of mass & 0.139 m \\
+    \hline
+    $I_1,I_2$  & Inertia & 0.069 kgm\textsuperscript{2} \\
     \hline
@@
     }
-The corresponding control input constraints of \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, are defined in Appendix \ref{sec:appen:cstr} as input bound constraint \eqref{eq:cstr:input:norm} and nonlinear input norm constraint \eqref{eq:cstr:input:bound}, respectively.
+The corresponding control input constraints of \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, are mathematically defined in Appendix \ref{sec:appen:cstr} as input bound constraint \eqref{eq:cstr:input:norm} and nonlinear input norm constraint \eqref{eq:cstr:input:bound}, respectively.
 \MSRY{sets들과 제약조건을 이어주기 위하여 추가}
@@
 % ------------------------------------
+
 \hfill
+
 For a comparative study, we implemented 4 controllers.
@@
 % ------------------------------------
-\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large update rate of Lagrange Multipliers, $\beta_j,\forall j\in\mathcal{I}$}}
+\subsubsection*{Controller 1: \normalfont{(C$_1$)} \textit{CONAC with large update rate, $\beta_j,\forall j\in\mathcal{I}$, of Lagrange Multipliers}}
 
@@
 \end{equation}
-where $\overline\tau_2=-\underline{\tau}_2=3.5$ are the absolute bound of the second link actuator's torque, and $\overline\tau=11$ is the maximum feasible norm of the first and second torques.
+where $\overline\tau_2=-\underline{\tau}_2=3.5$, and $\overline\tau=11$.
 Hence, (C$_1$) is possible to use full capability of the actuator.
-The weight constraints $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ were also considered in the CONAC.
-As described in \eqref{eq:control:est}, the control input (torques) is equal to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
-
-The update rates of the Lagrange multipliers for weight constraints were set to $\beta_{\theta_i}=10^{-3},\ \forall i\in\{0,\cdots,k\}$, and ,for control input constraints, the update rates were set to large values such that $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$ to investigate the effect of the large values of update rates.
+The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ were also considered in the CONAC.
+As described in \eqref{eq:control:est}, the control input (torque) is equal to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
+
+The update rates of the Lagrange multipliers for weight norm constraints were set to $\beta_{\theta_i}=1,\ \forall i\in\{0,\cdots,k\}$, and ,for control input constraints, the update rates were set to large values such that $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$ to investigate the effect of the large values of update rates.
 
@@
 % ------------------------------------
-\subsubsection*{Controller 2: \normalfont{(C$_2$)} \textit{CONAC with small update rate of Lagrange Multipliers, $\beta_j,\forall j\in\mathcal{I}$}}
-
-As the second controller, the proposed CONAC was implemented with the same input bound constraint \eqref{eq:sim:cstr:CONAC} as (C$_1$), but with small update rate values such that $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.
+\subsubsection*{Controller 2: \normalfont{(C$_2$)} \textit{CONAC with small update rate, $\beta_j,\forall j\in\mathcal{I}$, of Lagrange Multipliers}}
+
+As the second controller, the proposed CONAC was implemented with the same input bound constraints as (C$_1$), but with $100$ times smaller update rate values such that $\beta_{\rbu}=0.1$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=1$.
 The remaining properties and parameters were the same as (C$_1$).
@@
 The third controller was the same as (C$_1$) and (C$_2$), but without the control input constraints, to emphasize the control input constraint handling capability of the proposed CONAC.
-In this case, the update rate of the Lagrange multipliers regarding the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, was set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated (see, \eqref{eq:adap:lbd}).
+In this case, the update rates of the Lagrange multipliers regarding the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, were set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated, \ie see, \eqref{eq:adap:lbd}.
 The remaining properties and parameters were the same as (C$_1$) and (C$_2$).
@@
 On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC with control input constraints by replacing them with the auxiliary system.
-The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state variables, and $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$ are user-designed matrices.
+The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$, with $\mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^2$ denotes the auxiliary state variables, and $\mm{A}_\zeta\in\R_{<0}^{2\times 2}$, and $\mm{B}_\zeta\in\R^{2\times 2}$ are user-designed matrices.
 The auxiliary state $\mv{\zeta}$ is affected by the overflow amount of the control input $\Delta\rbu$, whose entries are defined as $\Delta\tau_{i} = 
 \tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
-The auxiliary state are used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
-Consequently, the weights are adapted to reduce not only the tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.
-
-The matrices of the auxiliary system were set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed of the auxiliary system.
-Since, the auxiliary system only considers the saturation of each control input, \ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}, $\overline{\tau}_1$ was set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$).
-For simplicity, let say (C$_4$) was imposed with input bound constraint for the first link actuator, \ie $c_{\overline{\tau}_1}$ and $c_{\underline{\tau}_1}$.
-\MSRY{사실, 제약조건이 부여된 것은 아니기 떄문에 위와 같이 표현하였음}
+The auxiliary state were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
+Consequently, the weights were adapted to reduce not only the filtered tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.
+
+The matrices of the auxiliary system were set to $\mm{A}_\zeta=\mydiag\left((-10,-10)^\top\right)$ and $\mm{B}_\zeta=\mydiag\left((10^3,10^3)^\top\right)$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed of the auxiliary system.
+Since, the auxiliary system only considers the saturation of each control input, \ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}, $\overline{\tau}_1$ was set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$.
 
@@
 % ------------------------------------
-For all controllers ((C$_1$), (C$_2$), (C$_3$), and (C$_4$)), the DNN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+For all controllers, \ie (C$_1$), (C$_2$), (C$_3$), and (C$_4$), the DNN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{7}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
+All DNN architectures have two hidden layers with four nodes, \ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$ in \eqref{eq:DNN:architecture}, and the adaptation gain was set to $\alpha=0.2$.
+The filtering matrix $\mm{\Lambda}$ in \eqref{eq:err:filtered}, was set to $\mm{\Lambda}=\mydiag([5,15])$.
 The DNNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
-All DNN architectures have two hidden layers with four nodes, \ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$, and the adaptation gain was set to $\alpha=0.5$.
-The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
 The sampling rate of the controller was $250$ Hz considering the real-time implementation.
-The weight constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$.
-\MSRY{어차피 내부는 안걸리니까 그림 더 깔끔하게 다 6이라고 함} 
+The weight norm constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$.
 The control results were collected via CAN communication with PCAN USB  and recorded in a computer with a sampling rate of $250$ Hz.
@@
     \hline
-        &\bf{Description}&\bf{Input Constraint}\\
-    \hline
-    \hline
-        (C$_1$)&large $\beta_j$&$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
-    \hline
-        (C$_2$)&small $\beta_j$&$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
-    \hline
-        (C$_3$)&no $\rbu$ constraints&$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
-    \hline
-        (C$_4$)&aux. sys.&$\overline{\tau}_1=-\underline{\tau}_1=10.428,\overline{\tau_2}=-\underline{\tau_2}=3.5$\\
+        &\bf{Description}&\bf{Input Constraint Handling}\\
+    \hline
+    \hline
+        \multirow{2}{*}{(C$_1$)}&large&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
+        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+    \hline
+        \multirow{2}{*}{(C$_2$)}&small&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
+        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+    \hline
+        \multirow{2}{*}{(C$_3$)}&no input& \multirow{2}{*}{$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$} \\
+        & constraint &  \\
+    \hline
+        \multirow{2}{*}{(C$_4$)}&\multirow{2}{*}{auxiliary system} & $\overline{\tau}_1=-\underline{\tau}_1=10.428$ \\
+        &  & $\overline{\tau_2}=-\underline{\tau_2}=3.5$ \\    
     \hline
@@
 % Norm of error in Episode 1: 
-% C1 e1 ep1: 25.013
-% C1 e2 ep1: 22.651
+% C1 e1 ep1: 25.130
+% C1 e2 ep1: 25.016
 % C2 e1 ep1: 21.719
@@
 % C3 e1 ep1: 23.168
-% C3 e2 ep1: 13.062
+% C3 e2 ep1: 13.061
 % C4 e1 ep1: 24.195
@@
 % Norm of error in Episode 2: 
-% C1 e1 ep2: 7.513
-% C1 e2 ep2: 2.617
+% C1 e1 ep2: 7.066
+% C1 e2 ep2: 2.198
 % C2 e1 ep2: 8.021
@@
 % C3 e1 ep2: 8.408
-% C3 e2 ep2: 3.553
+% C3 e2 ep2: 3.554
 % C4 e1 ep2: 19.721
@@
 % Improvement in Episode 2: 
-% C1 e1: 0.700
-% C1 e2: 0.884
+% C1 e1: 0.719
+% C1 e2: 0.912
 % C2 e1: 0.631
@@
 % ------------------------------------
+
 \begin{table}[!t]
@@
 	\hline
-		$e_1\times10^{3}$ / rad & $25.013$ & $21.719$ & $23.168$ & $24.195$ \\
-	\hline
-        $e_2\times10^{3}$ / rad & $22.651$ & $10.530$ & $13.062$ & $12.927$ \\
+		$e_1\times10^{3}$ / rad & $25.130$ & $21.719$ & $23.168$ & $24.195$ \\ 
+	\hline
+        $e_2\times10^{3}$ / rad & $25.016$ & $10.530$ & $13.061$ & $12.927$ \\
 	\hline
@@
     \multirow{2}{*}{$e_1\times10^{3}$ / rad} 
-        & $7.513$ & $8.021$ & $8.408$ & $19.721$ \\
-        & ($-70.0\%$) & ($-63.1\%$) & ($-63.7\%$) & ($-18.5\%$) \\
+        & $7.066$ & $8.021$ & $8.408$ & $19.721$ \\
+        & ($-71.6\%$) & ($-63.1\%$) & ($-63.7\%$) & ($-18.5\%$) \\
     \hline
     \multirow{2}{*}{$e_2\times10^{3}$ / rad} 
-        & $2.617$ & $2.435$ & $3.553$ & $4.256$ \\
+        & $2.198$ & $2.435$ & $3.554$ & $4.256$ \\
         & ($-88.4\%$) & ($-76.9\%$) & ($-72.8\%$) & ($-67.1\%$) \\
@@
 The real-time implementation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
-Across the two episodes, all controllers enhanced their tracking performances about $70 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
+Across the two episodes, all controllers enhanced their tracking performances, \ie $71.6 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively.
 Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode.
-This results lead to the conclusion that the DNNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was unknown in advance.
-Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.
-
-In addition, it is notable that in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time intervals from $17.5$ s to $19.9$ for Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s for Episode $2$.
+This results lead to the conclusion that the DNNs in all controllers were able to learn the ideal control input $\rbu^*$ properly using the filtered error $\fe$, despite the fact that $\rbu^*$ was completely unknown in advance.
+Moreover, since the stable learning was achieved with the random weight initialization and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.
+
+Notably, in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time intervals from $17.5$ s to $19.9$ s for Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s for Episode $2$.
 This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
@@
 This is because, (as will be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
-\KHCH{
-    문단이 misleading 할 수 있습니다.
-C3가 C4보다는 낫다고 되어 있는데 마지막에는 C3가 poor 하다고 합니다. 명료한 결론으로 바꿔주세요.
-명확하지 않게 C4처럼 constraint를 고려하면 고려안하는 C3보다 더 안 좋아질 수 있다 등의 논리가 필요해보입니다.   
-}
-\MSRY{반영 중}
-The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) produced excessively large control inputs which hits the actuator limits, without considering the control input saturation.
-This may lead to the conclusion that CONAC without control input constraints outperformed the auxiliary system.
-However, since the CONAC adapts the weights to reduce the tracking error, \ie which is the only feedback signal, the CONAC increases the control input excessively to reduce the tracking error, which can not be regulated due to the actuator limits.
+The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) utilized more capability of the actuator than (C$_4$) without considering the control input saturation.
+One may conclude that (C$_3$) outperformed (C$_4$) since the tracking performance of (C$_3$) was better than (C$_4$), as shown in Table~\ref{tab:sim:L2}.
+However, since the CONAC adapts the weights to reduce the tracking error, \ie which is the only feedback signal, the CONAC increases the control input excessively large to reduce the tracking error, which can not be regulated due to the actuator limits.
 In Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, the violations of the control input saturations grow larger in every saturated time interval.
-Moreover, this large violation occurs oscillations in the control input (adaptation),
-
-% The tracking performance of (C$_3$) was also better than (C$_4$), but worse than (C$_1$) and (C$_2$), since the control input constraints were not considered in (C$_3$).
-% Without consideration of the control input saturation, DDN became confused by the difference between its output (control input) and the saturated control input, which leads to the poor performance of (C$_3$).
+Moreover, this large violation occurs oscillations when the control saturation is released as the reference trajectory is changed, since the weights are adapted to produce large control inputs.
 
@@
 	\caption{
-		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_1$.
-		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively (i.e., $\lambda_{j}' > \lambda_{j}''$).
+		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_2$.
+		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively, i.e., $\lambda_{j}' > \lambda_{j}''$.
 	}
@@
 \hfill
+
 \subsubsection{Constraint Handling} \label{sec:sim:constraint}
@@
 In this section, the constraint handling capability of all controllers are investigated.
-
-As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}, with $c_{\rbu},c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for (C$_1$), and (C$_2$), and $c_{\overline\tau_1},c_{\underline\tau_1},c_{\overline\tau_2}$, and $c_{\underline\tau_2}$ for (C$_4$), as the weights were adapted to reduce the constraint violations, using Lagrange multipliers $\lambda_j,\ \forall j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}$, and auxiliary state $\mv{\zeta}$, respectively.
-It is worth to note that the control input constraints were violated repeatedly, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
+As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}.
+For (C$_1$) and (C$_2$), the control input saturation was handled using the Lagrange multipliers and, for (C$_4$), the auxiliary system was used to handle the control input saturation.
+It is worth to note that the control input constraints were violated repeatedly after constraint handling, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
 
 Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $29.4$ s to $31.9$ s.
-This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$, instead of $c_{\rbu}$.
-In contrast, (C$_1$), and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$.
+This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$.
+In contrast, (C$_1$), and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$, defined in \eqref{eq:sat}, \ie see, Fig.~\ref{fig:robot:sat}.
+
+\hfill
 
@@
 The detail of the constraint handling in the time interval from $29.4$ s to $31.9$ s, is now investigated.
-First, for (C$_4$), the auxiliary state $\zeta_1$ generated by constraint violation of $c_{\overline\tau_1}$. \KHCH{FIg6c를 언급하며 설명되면 좋겠습니다}
-As the weights were adapted to reduce not only $\fe$ but also $\mv{\zeta}$, the constraint violation of $c_{\overline\tau_1}$ was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
-After the constraint was satisfied, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$.
+First, for (C$_4$), the auxiliary state $\zeta_1$ was generated by control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
+As the weights were adapted to reduce not only the filtered error $\fe$ but also the auxiliary state $\mv{\zeta}$, the control input saturation was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
+After the saturation was resolved, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as described in Fig.~\ref{fig:ctrl:result:scope:aux}.
 
 % beta + zeta
-For the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\estwth_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
+For the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_j\in\forall j\in\mathcal{I}$ adjusted the adaptation direction of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$ to reduce the constraint violation $c_j\in\forall j\in\mathcal{I}$, as $\lambda_j\in\forall j\in\mathcal{I}$ generated by the constraint violations.
 % comparison; big, small beta
-\KHCH{여기 아래 부터는, beta의 영향에 대해 설명하는데 lambda가 크고 작음만 언급됩니다. 명료하게 설명 수정해주세요.}
-For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for convex constraint $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
-With the bigger $\lambda_j$, the adaptation of $\estwth_1$ is more assertive than that with smaller $\lambda_j$.
-This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but this also causes oscillation in the adaptation process.
-In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_{\rbu}$ was satisfied and violated, respectively, in the discrete time implementation.
-Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
+The effect of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$ on the adaptation direction of the weights $\estwth_2$ is shown in Fig.~\ref{fig:lambda_effect} for a constraint $c_j,\ \forall j\in\mathcal{I}$, with two different amplitudes.
+It is noteworthy that the constraint $c_j$ which satisfies Assumptions \ref{assum:convex} and \ref{assum:LICQ}, is convex in $\estwth_2$-space, \ie see, Lemma. \ref{lem:convex:angle}.
+The bigger and smaller Lagrange multipliers can be interpreted as the case of (C$_1$) and (C$_2$), respectively, since the update rates of the Lagrange multipliers were set to $10^2$ times bigger for (C$_1$) than (C$_2$).
+This results in a fast growth of the Lagrange multipliers $\lambda_j$, when the constraint was violated, \ie see, \eqref{eq:adap:lbd}.
+With the bigger $\lambda_j'$, the adaptation of $\estwth_2$ is more assertive than that with smaller $\lambda_j''$.
+This leads to a faster satisfaction of the constraint $c_j$, but this also causes oscillation in the adaptation process.
+
+Hence, invoking above discussion, the real-time implementation results of (C$_1$) and (C$_2$) are compared in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}.
+In the figures, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and disappeared, which indicates that the constraint $c_{\rbu}$ was violated and satisfied, respectively, in the discrete time implementation.
+Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_2$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
 This allows the controller to show a smoother control input.
-\KHCH{흐름상 잘 이해되지 않습니다}
-However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt the weights with respect to the filtered error $\fe$.
 
@@
 
-Finally, the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,\cdots,2\}$ are investigated.
+Finally, the constraint handling of the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$ is investigated.
 The weight norm constraints were not activated except for the outer layer weights $c_{\theta_2}$ of (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}.
-This is because the weights of (C$_1$), (C$_2$), and (C$_4$) were suppressed by the control input constraints, while (C$_3$) was not.
-\MSRY{필요하다면 왜 제어입력 제약하는게 가중치 제약도 되는지 추가 가능}
-In addition, the inner and hidden layer weights constraints were not violated (\ie $\norm{\estwth_0},\norm{\estwth_1}$ were uniformly lower than $\norm{\estwth_2}$), since the backpropagated error was multiplied by the gradient of the activation function, which is limited from $-1$ to $1$, \ie see, \eqref{eq:gradient:phi}.
+This is because the weights of (C$_1$), (C$_2$), and (C$_4$) were implicitly suppressed by the control input constraints, while (C$_3$) was not.
+% , \ie by limiting the control input, the weight norms were also limited.
+% \MSRY{필요하다면 왜 제어입력 제약하는게 가중치 제약도 되는지 추가 가능}
+In addition, the inner and hidden layer weights constraints were not violated, \ie $\norm{\estwth_0},\norm{\estwth_1}$ were uniformly lower than $\norm{\estwth_2}$, since the backpropagated error was multiplied by the gradient of the activation function, which is limited from $-1$ to $1$, \ie see, \eqref{eq:gradient:phi}.
 
 \KHCH{반복해서 이 내용을 설명할 필요가 있을까요?}
+\MSRY{가중치 제약조건 만족에 대한 이야기가 없어서 추가했습니다.}
 The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
-In Fig.~\ref{fig:ctrl:result:scope:beta}, the Lagrange multipliers $\lambda_{\theta_2}$ were increased by the constraint violations, and the adaptation direction of the weights $\estwth_2$ was adjusted to reduce the constraint violations.
+In Fig.~\ref{fig:ctrl:result:scope:beta}, the Lagrange multipliers $\lambda_{\theta_2}$ were increased by the weight $\estwth_2$ exceeds the weight norm constraint $\overline\wth_2$, and the adaptation direction of the weights $\estwth_2$ was adjusted to resolve the violation of the constraint $c_{\theta_2}$.
 
@@
 \hfill
+
 \subsubsection{Satisfaction of Karsh-Kuhn-Tucker (KKT) conditions}
@@
 Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
-However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of active constraints were positive and inactive constraints were zero.
-
-\MSRY{이 부분도 IECON과 마찬가지로 이산으로 돌아감으로 바로 보여주기는 힘들 수 있을 것 같습니다. 실제로 보시면 많은 진동이 보여서 정상상태의 KKT를 주장할 수 있을지 의문입니다.}
+However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of the active constraints were positive and inactive constraints were zero.
+
 % reference 자체가 계속 움직이니까 엄밀하게는 steady state를 보장할 수 없습니다. rough 하게는 theta norm이 어느정도 수렴하므로 이 것을 기반으로 주장해볼 수도 있습니다. theta_dot이 평균적으로는 0에 가까운 것 같서요
@@
 \hfill
+
 \subsubsection{Effectiveness of CONAC in Real-time Applications}
 
-The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time measured using CPU clock ticks of the OpenCR1.0 board.
-The computational times are shown in Fig.~\ref{fig:ctrl:real:result:cmp:time} indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz.
-In addition, it is notable that the computational time decreased as the weights converged.
-\MSRY{삭제해야할수있음; C4는 그러하지 않기 때문}
+The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time using CPU clock ticks of the OpenCR1.0 board.
+The computational times shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz.
 

### 2025-05-26 presentation/presentation.tex
ppt minor update

--- 2025-04-22 presentation/presentation.tex
@@
-% https://www.overleaf.com/learn/latex/Beamer#Using_a_colortheme
+% https://www.overleaf.com/learn/latex/Beamer#Using_a_colorthemev
 
 % Inbuilt themes in beamer
-\documentclass[aspectratio=169]{beamer}
+\documentclass[8pt, aspectratio=169]{beamer}
 
-% Theme choice:
-\usetheme{Antibes}
-% \usecolortheme{beaver}
+\input{../template/macros/macros_general.tex}
+\input{../template/macros/macros_math.tex}
+\input{../template/symbols/symbols_NN.tex}
+\input{../template/symbols/symbols_robot.tex}
+
+% % Theme choice:
+% \usetheme{Antibes}
+% % \usecolortheme{beaver}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Use roboto Font (recommended)
+\usepackage[sfdefault]{roboto}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Use roboto Font (recommended)
+\usepackage[sfdefault]{roboto}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Define where theme files are located. ('/styles')
+\usepackage{styles/fluxmacros}
+\usefolder{styles}
+% Use Flux theme v0.1 beta
+% Available style: asphalt, blue, red, green, gray 
+\usetheme[style=blue]{flux}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Extra packages for the demo:
+\usepackage{booktabs}
+\usepackage{colortbl}
+\usepackage{ragged2e}
+\usepackage{schemabloc}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\usepackage{calc}
 
@@
 
+\AtBeginSubsection[]{%
+  \begin{frame}
+  \vfill
+  \centering
+    \insertsectionhead
+    \\
+    \large\textbf{\insertsubsectionhead}
+  \vfill
+  \end{frame}
+}
+
+\titlegraphic{logo_KAIST.png}
+
 \begin{document}
@@
 
-\begin{frame}{Introduction to Neuro–Adaptive Control}
+\begin{frame}{What is Neuro–Adaptive Control?}
 
-    \begin{block}{Standard Block}
-        This is a standard block.
+  \begin{block}{Neuro–Adaptive Control}
+      \begin{itemize}
+          \visible<+->{
+            \item \textbf{Neuro–adaptive control} is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques}.
+          }
+          \visible<+->{
+            \item It is used to handle uncertainties and nonlinearity in dynamic systems \cite{Arefinia:2020aa}. 
+          }
+      \end{itemize}
   \end{block}
-    \begin{alertblock}{Alert Message}
-        This block presents alert message.
-    \end{alertblock}
-    \begin{exampleblock}{An example of typesetting tool}
-        Example: MS Word, \LaTeX{}
-    \end{exampleblock}
+
+  \begin{figure}
+    \includegraphics[width=0.4\textwidth]{../fig/fig5.eps}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+  \end{figure}
+
+\end{frame}
+
+\begin{frame}{Effectiveness of Neuro–Adaptive Control}
 
@@
 
-\begin{frame}
+\begin{frame}{Inherent Challenges in Neuro–Adaptive Control}
+
+  Flux theme comes with three pre-defined block style collections.\\
+  % Native style (default) available as \verb+\setblockstyle{native}+\\[0.5cm]
+
+  \centering
+	\begin{minipage}[b]{0.5\textwidth}
+
+	  \begin{block}{Default}
+        Block content.
+      \end{block}
+
+      \begin{alertblock}{Alert}
+        Block content.
+      \end{alertblock}
+
+      \begin{exampleblock}{Example}
+        Block content.
+      \end{exampleblock}
+
+	\end{minipage}
+\end{frame}
+
+\begin{frame}{Literature Review}
+
+\end{frame}
+
+\subsection{Research Objectives}
+
+\begin{frame}{Research Objectives}
 
@@
 \section{Proposed Method}
-\subsection{Weight Norm Constraint}
-\begin{frame}{Weight Norm Constraint}
-    \begin{block}{Weight Norm Constraint}
+
+\subsection{Constrained Optimization Problem Formulation}
+
+\begin{frame}{Original Problem Formulation}
+  \large\textbf{Objectives}:
   \begin{itemize}
-            \item This is a list item.
-            \item This is another list item.
+    \item Minimize the tracking error by adapting the NN weights $\estwth$.
+    \item Guarantee the stability of the system and the NN weights $\estwth$.
   \end{itemize}
-    \end{block}
+
+  \begin{figure}
+    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+  \end{figure}
+
+  \small{
+    \textit{Notations}: 
+    $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
+  }
+
 \end{frame}
+
+\subsection{Adaptation Law Derivation}
+
+\subsection{Stability Analysis}
 
@@
 \subsection{Simulation Setup}
-\begin{frame}{Weight Norm Constraint}
-    \begin{block}{Weight Norm Constraint}
-        \begin{itemize}
-            \item This is a list item.
-            \item This is another list item.
-        \end{itemize}
-    \end{block}
+\begin{frame}{2-Link Robotic Manipulator}
+
 \end{frame}
@@
 \subsection{Simulation Results}
+
+\begin{frame}{Flux}{plots}
+	\begin{minipage}{0.56\textwidth}
+		\begin{figure}
+			\includegraphics[width=\textwidth]{assets/plot.png}
+		\end{figure}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.38\textwidth}
+		\begin{block}{Binary Softmax classifier}
+			\centering
+			$\sigma(\sum_i w_ix_i + b)$
+		\end{block}
+		\begin{exampleblock}{Loss function}
+			\centering\vspace*{0.1cm}
+			$L_i = -log(\frac{e^{f_{y_i}}}{\sum_j e^{f_j}})$\\[0.1cm]
+			cross entropy
+		\end{exampleblock}
+	\end{minipage}
+\end{frame}
+
+\begin{frame}{Flux}{tables}
+    \begin{table}
+      \caption{Largest cities in the world (source: Wikipedia)}
+      \begin{tabular}{@{} lr @{}}
+        \toprule
+        City & Population\\
+        \midrule
+        Mexico City & 20,116,842\\
+        Shanghai & 19,210,000\\
+        Peking & 15,796,450\\
+        Istanbul & 14,160,467\\
+        \bottomrule
+      \end{tabular}
+      \hspace*{1cm}
+          \setlength\extrarowheight{3pt}
+      \begin{tabular}{|lr|}
+        \hline
+        \rowcolor{primaryLight}\color{background}City & \color{background}Population\\
+        \hline
+        Mexico City & 20,116,842\\
+        Shanghai & 19,210,000\\
+        Peking & 15,796,450\\
+        Istanbul & 14,160,467\\
+        \hline
+      \end{tabular}
+  \end{table}
+\end{frame}
+
 \begin{frame}{Weight Norm Constraint}
-    \begin{block}{Weight Norm Constraint}
+  \begin{columns}[T,onlytextwidth]
+    \column{0.33\textwidth}
+      \textbf{Items}
       \begin{itemize}
-            \item This is a list item.
-            \item This is another list item.
+        \item Cats \item Dogs \item Birds
       \end{itemize}
-    \end{block}
+
+    \column{0.33\textwidth}
+      \textbf{Enumerations}
+      \begin{enumerate}
+        \item First \item Second \item Last
+      \end{enumerate}
+
+    \column{0.33\textwidth}
+      \textbf{Descriptions}
+      \begin{description}
+        \item[Apples] Yes \item[Oranges] No \item[Grappes] No
+      \end{description}
+  \end{columns}
+  \let\thefootnote\relax\footnote{Note the following demo slides are directly taken from metropolis theme. Copyright 2014 Matthias Vogelgesang.\\
+Give a look at https://github.com/matze/mtheme/tree/master/demo}
 \end{frame}
@@
 \subsection{Conclusion and Future Work}
+
 \begin{frame}{Conclusion}
-    \begin{block}{Weight Norm Constraint}
-        \begin{itemize}
-            \item This is a list item.
-            \item This is another list item.
-        \end{itemize}
-    \end{block}
+
 \end{frame}
@@
 
+\begin{frame}[allowframebreaks]{References}
+
+  \bibliography{../template/refs}
+  \bibliographystyle{ieeetr}
+
+\end{frame}
+
 \end{document}

### 2025-05-27 manuscript.tex
minor change

@@
 
-A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated. 
+A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN werights are updated. 
 Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
@@
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
+\MSRY{포화가 컨벡스하다는 가정을 추가했습니다.}
+In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
@@
 \begin{prop} 
-    The Coriolis/centripetal\MSRY{인용 책 그대로 적은 것입니다.} matrix $\rbVm$ can always be selected\MSRY{상동.} so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
+    The Coriolis/centripetal matrix $\rbVm$ can always be selected, so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
     \label{prop:skew}
@@
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).
-\MSRY{SAT은 좀더 명확히 하기 위해서 사용하였음; 그렇지 않으면 아래 실험 피규어를 통해 포화를 넘어선 제어가 입력된다고 생각할까봐 그렇습니다; ddt의 경우 수식과 통일하기 위함이 맞습니다.}}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
     \label{fig:ctrl:diagram}
@@
 where $\alpha\in\R_{>0}$ denotes the adaptation gain (learning rate) and $\beta_j\in\R_{>0}$ denotes the update rate of the Lagrange multipliers in $\mathcal I$, and the arguments of $L(\cdot)$ and $J(\cdot)$ are suppressed for brevity.
-% By selecting $\alpha_i\in\R_{>0},\ \forall i\in[1,\cdots,n]$, one can weight the importance of each component of the gradient of the objective function, allowing for a more tailored adaptation process.
 The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, due to \eqref{eq:adap:lbd:max}. 
@@
 \begin{remark}
-    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex\KHCH{앞에 convex라는 표현이 나오지 않았는데 확인부탁합니다.}\MSRY{컨벡스란 말이 없지만 practical하게 대부분의 포화 함수는 컨벡스라는 말을 의도하였습니다.} in practice including the origin.
+    Assumption \ref{assum:convex} is not restrictive, since, as aforementioned, the control input saturation is practically convex.
     Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
@@
 The convex function has a bounded derivative with respect to $\rbu$, since $\rbu$ is a bounded variable (\ie $\pptfrac{c_j}{\rbu}$ is bounded). 
-Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
+Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in\{k,\cdots,i+1\}$, are bounded. 
 This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
@@
 
-As a\MSRY{a?} result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative) can be obtained using Lemma \ref{lem:stable:set} as follows:
+As a result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative) can be obtained using Lemma \ref{lem:stable:set} as follows:
 \begin{equation}
@@
             \textstyle\sum_{
-                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
+                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
             }
@@
 The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
-For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ \color{red}increases sufficiently large\color{black} \MSRY{본래 infinitely였습니다만 무한까지 가는 것을 가정하지 않기 때문에 충분히 커질때로 바꿈} due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
+For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large, due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
 The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
-Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases sufficiently large \MSRY{위와 같은 이유로 변경}, leading to increase in ${\gamma}_2$.
+Similarly to $c_{\theta_k}$, when a control input constraint $c_j,\ \forall j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases sufficiently large, leading to increase in ${\gamma}_2$.
 It makes ${\gamma}_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
@@
 
-Since, the control input constraints are inactive, the saturation function $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and the constraint functions $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{\{i\in[0,\cdots,k\}}$ in \eqref{eq:lya2:dot} can be removed.
+Since, the control input constraints are inactive, the saturation function $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and the constraint functions $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ in \eqref{eq:lya2:dot} can be removed.
 Consider the Lyapunov function candidate $V_3:=V_1+V_2$, whose time derivative is given by:
@@
 표현이 조금 어색하거나 구어스러운 부분들이 있습니다.}
+\MSRY{빠른시일내에 수정 예정입니다.}
 
@@
 \end{subequations}
-These sets, \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, can be physically interpreted as the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.
-\KHCH{
-    (30a)의 의미를 다음과 같이 바꾸는게 명확하겠습니다. 
-    These sets, (30a) and (30b), can be physically interpreted as the current limitation imposed by the power source and the torque limitation of the second joint actuator, respectively.
-}
-\MSRY{
-    전압 제한이 곧 전류 제한인 것인가요?
-    전류 제한이라 하면 상태에 대한 제약조건이 부여된 것인가라는 오해가 생길가 걱정입니다.
-    }
+These sets, \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, can be physically interpreted as the current limitation imposed by the power source and the torque limitation of the second joint actuator, respectively.
 The corresponding control input constraints of \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, are mathematically defined in Appendix \ref{sec:appen:cstr} as input bound constraint \eqref{eq:cstr:input:norm} and nonlinear input norm constraint \eqref{eq:cstr:input:bound}, respectively.
@@
 
-The controller effectively incorporated both convex input constraints and weight norm constraints, ensuring that actuator limitations and neural network parameters\MSRY{Weight?} remained within predefined bounds.
+The controller effectively incorporated both convex input constraints and weight norm constraints, ensuring that actuator limitations and neural network weights remained within predefined bounds. 
 By embedding these constraints into the optimization process, CONAC ensured convergence of the weights in accordance with the Karush-Kuhn-Tucker (KKT) conditions, thereby achieving both stability and optimality.
@@
 Most physical systems have control input limits due to electrical and mechanical limitations.
-These are expressed as $\mv{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\mv{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
+These are expressed as $\mv{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in\{1,\cdots,n\}}$ and $\mv{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in\{1,\cdots,n\}}$, where
 \begin{equation}
@@
 with $\tau_{\overline \tau_i}\in\R_{>0}$ and $\tau_{\underline\tau_i}\in\R_{>0}$ representing the maximum and minimum control input bounds, respectively.
-% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
 The gradients of $\mv{c}_{\overline \tau}$ and $\mv{c}_{\underline\tau}$ with respect to $\estwth$ are given by

### 2025-05-28 presentation/presentation.tex
ppt update; animation;

@@
 
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Block options: Default, Alert, Example
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
 % % Theme choice:
@@
 % Use roboto Font (recommended)
-\usepackage[sfdefault]{roboto}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-% Use roboto Font (recommended)
-\usepackage[sfdefault]{roboto}
+% \usepackage[sfdefault]{roboto}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{calc}
+
+\usepackage{svg}
 
@@
 \logo{
-    \includegraphics[height=0.3cm]{logo_KAIST.png}
-    \hspace{.5cm}%
-    \includegraphics[height=0.3cm]{logo_KAIST.png}
+  \vspace{-.7cm}%
+  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
+  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
+  \hspace{.6cm}%
   }
@@
 
-\AtBeginSubsection[]{%
-  \begin{frame}
-  \vfill
-  \centering
-    \insertsectionhead
-    \\
-    \large\textbf{\insertsubsectionhead}
-  \vfill
-  \end{frame}
-}
+% \AtBeginSubsection[]{%
+%   \begin{frame}
+%   \vfill
+%   \centering
+%     \insertsectionhead
+%     \\
+%     \large\textbf{\insertsubsectionhead}
+%   \vfill
+%   \end{frame}
+% }
 
@@
 
-\begin{frame}{What is Neuro–Adaptive Control?}
+\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}
 
-  \begin{block}{Neuro–Adaptive Control}
+  \textbf{Neuro–Adaptive Control}
+  \small{
     \begin{itemize}
-          \visible<+->{
-            \item \textbf{Neuro–adaptive control} is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques}.
+      \item \textbf{Neuro–adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques} \cite{Farrell:2006aa}.
+      \item It is used to handle \textbf{uncertainties} and \textbf{nonlinearity} in dynamic systems. 
+    \end{itemize}
   }
-          \visible<+->{
-            \item It is used to handle uncertainties and nonlinearity in dynamic systems \cite{Arefinia:2020aa}. 
-          }
-      \end{itemize}
-  \end{block}
 
   \begin{figure}
-    \includegraphics[width=0.4\textwidth]{../fig/fig5.eps}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+    \includegraphics[width=0.55\textwidth]{figures/NAC.drawio.pdf}
   \end{figure}
@@
 
-\begin{frame}{Effectiveness of Neuro–Adaptive Control}
+\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}
+
+  \textbf{Advantages of Neuro-Adaptive Control}
+  \small{
+    \begin{itemize}
+      \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
+      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textbf{Lyapunov stability theory}.
+      \item \textbf{Online Learning Capability}: NAC adapts in \textbf{real-time} to new data with stability guarantees.
+      \item \textbf{Robustness}: NAC handles \textbf{uncertainties and disturbances} effectively with adaptive control techniques.
+    \end{itemize}
+  }
 
@@
 
-\subsection{Limitations of Neuro–Adaptive Control}
+\begin{frame}{\insertsubsectionhead}{Existing Challenges in NAC}
 
-\begin{frame}{Inherent Challenges in Neuro–Adaptive Control}
+  \textbf{Challenges}
+  \small{
+    \begin{itemize}
+      \item \textbf{Optimality}: In general, the adaptation laws are deriven with respect to the tracking error, which may not guarantee optimal performance.
+      \item \textbf{Unpredictable Amplitude of NN Weights}: 
+        \begin{itemize}
+          \item NN weights may diverge, leading to instability.
+          \item This can result in unpredictable behavior of the controller.
+        \end{itemize}
+      \item \textbf{Parameter Dependency}: 
+    \end{itemize}
+  }
+
+  \begin{figure}
+    \includegraphics[width=0.25\textwidth]{figures/KAIST-hi.png}
+  \end{figure}
+
+\end{frame}
+
+\subsection{Literature Review}
+
+\begin{frame}{\insertsubsectionhead}
+
+  In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.
+
+  \begin{enumerate}
+    \begin{columns}[T,onlytextwidth]
+        \column{0.49\textwidth}
+          \item \textbf{Projection Operator}
+
+          \begin{itemize}
+            \item Cats 
+            \item Dogs 
+            \item Birds
+          \end{itemize}
+
+        \column{0.49\textwidth}
+          \begin{figure}
+            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+      \end{columns}
+
+      \begin{columns}[T,onlytextwidth]
+        \column{0.49\textwidth}
+          \item \textbf{$\epsilon$-modification, and $\sigma$-modification}
+
+          \begin{itemize}
+            \item Cats 
+            \item Dogs 
+            \item Birds
+          \end{itemize}
+
+        \column{0.49\textwidth}
+          \begin{figure}
+            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+      \end{columns}
+  \end{enumerate}
+\end{frame}
+
+\subsection{Research Objectives}
+
+\begin{frame}{\insertsubsectionhead}
+
+  \textbf{Objective 1: Optimality}
+  \begin{itemize}
+    \item Formulate a constrained optimization problem to minimize the tracking error.
+    \item Guarantee the stability of the system and the NN weights.
+  \end{itemize}
+
+  \textbf{Objective 2: Stability}
+  \begin{itemize}
+    \item Derive an adaptation law that guarantees the stability of the system.
+    \item Ensure that the NN weights remain bounded during operation.
+  \end{itemize}
+
+  \textbf{Objective 3: Boundedness of }
+  \begin{itemize}
+    \item Ensure the controller is robust to uncertainties and disturbances.
+    \item Validate the proposed method through numerical simulations.
+  \end{itemize}
+
+\end{frame}
+
+\section{Proposed Method}
+
+\subsection{Problem Formulation}
+
+\begin{frame}{\insertsubsectionhead}{Original Control Problem}
+  \textbf{Objectives}:
+  \begin{itemize}
+    \item Minimize the tracking error by adapting the NN weights $\estwth$.
+    \item Guarantee the stability of the system and the NN weights $\estwth$.
+  \end{itemize}
+
+  \begin{figure}
+    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
+    % \includesvg{figures/problem.drawio}
+    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+  \end{figure}
+
+  \let\thefootnote\relax\footnote{
+    \textit{Notations}: 
+      $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
+      }
+
+\end{frame}
+
+\begin{frame}{\insertsubsectionhead}{Equvalent Constrained Optimization Problem}
+
+\end{frame}
+
+\begin{frame}{\insertsubsectionhead}{Inequality Constraint for Weight Boundedness}
+
+\end{frame}
+
+\subsection{Adaptation Law Derivation}
+
+\begin{frame}{\insertsubsectionhead}{Steepest Descent Method}
+
+\end{frame}
+\subsection{Stability Analysis}
+
+\begin{frame}{\insertsubsectionhead}{Lyapunov Stability Analysis}
+
+\end{frame}
+
+\section{Numerical Validation}
+
+\subsection{Simulation Setup}
+\begin{frame}{\insertsubsectionhead}{2-Link Robotic Manipulator}
+
+\end{frame}
+
+\subsection{Simulation Results}
+
+\begin{frame}{Representative Simulation Results}
+
+\end{frame}
+
+\begin{frame}{Box-and-Whisker Plots}
+
+  \begin{columns}
+    \column{0.5\textwidth}
+      \begin{figure}
+        \includegraphics[width=\textwidth]{figures/BoxWhisker.drawio.png}
+        \caption{Parameter dependencies of the proposed method.}
+      \end{figure}
+
+    \column{0.5\textwidth}
+      \begin{table}
+        \caption{Largest cities in the world (source: Wikipedia)}
+        \begin{tabular}{@{} lr @{}}
+          \toprule
+          City & Population\\
+          \midrule
+          Mexico City & 20,116,842\\
+          Shanghai & 19,210,000\\
+          Peking & 15,796,450\\
+          Istanbul & 14,160,467\\
+          \bottomrule
+        \end{tabular}
+    \end{table}
+
+  \end{columns}
+
+\end{frame}
+
+\begin{frame}{Parameter Dependencies}
+
+  \begin{columns}
+
+    \column{0.33\textwidth}
+      \begin{figure}      
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig9.eps}
+        \caption{Weight norms of NAC-L2}
+      \end{figure}
+
+    \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig10.eps}
+        \caption{Weight norms of NAC-eMod}
+      \end{figure}
+
+    \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig8.eps}
+        \caption{Weight norms of NAC-CO}
+      \end{figure}
+
+  \end{columns}
+
+  The weight norms of the proposed method (NAC-CO) are bounded, while ...
+
+\end{frame}
+
+\begin{frame}{Parameter Dependencies}
+
+  \begin{columns}
+
+    \column{0.33\textwidth}
+      \begin{figure}      
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig6.eps}
+        \caption{Tracking error of NAC-L2}
+      \end{figure}
+
+    \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig7.eps}
+        \caption{Tracking error of NAC-eMod}
+      \end{figure}
+
+    \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig5.eps}
+        \caption{Tracking error of NAC-CO}
+      \end{figure}
+
+  \end{columns}
+
+  The Tracking error ...
+
+\end{frame}
+
+\section{Conclusion}
+
+\subsection{Conclusion and Future Work}
+
+\begin{frame}{Conclusion}
 
@@
 
-\begin{frame}{Literature Review}
-
-\end{frame}
-
-\subsection{Research Objectives}
-
-\begin{frame}{Research Objectives}
-
-\end{frame}
-
-\section{Proposed Method}
-
-\subsection{Constrained Optimization Problem Formulation}
-
-\begin{frame}{Original Problem Formulation}
-  \large\textbf{Objectives}:
-  \begin{itemize}
-    \item Minimize the tracking error by adapting the NN weights $\estwth$.
-    \item Guarantee the stability of the system and the NN weights $\estwth$.
-  \end{itemize}
-
-  \begin{figure}
-    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
-  \end{figure}
-
-  \small{
-    \textit{Notations}: 
-    $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
-  }
-
-\end{frame}
-
-\subsection{Adaptation Law Derivation}
-
-\subsection{Stability Analysis}
-
-\section{Numerical Validation}
-
-\subsection{Simulation Setup}
-\begin{frame}{2-Link Robotic Manipulator}
-
-\end{frame}
-
-\subsection{Simulation Results}
-
-\begin{frame}{Flux}{plots}
-	\begin{minipage}{0.56\textwidth}
-		\begin{figure}
-			\includegraphics[width=\textwidth]{assets/plot.png}
-		\end{figure}
-	\end{minipage}
-	\hfill
-	\begin{minipage}{0.38\textwidth}
-		\begin{block}{Binary Softmax classifier}
-			\centering
-			$\sigma(\sum_i w_ix_i + b)$
-		\end{block}
-		\begin{exampleblock}{Loss function}
-			\centering\vspace*{0.1cm}
-			$L_i = -log(\frac{e^{f_{y_i}}}{\sum_j e^{f_j}})$\\[0.1cm]
-			cross entropy
-		\end{exampleblock}
-	\end{minipage}
-\end{frame}
-
-\begin{frame}{Flux}{tables}
-    \begin{table}
-      \caption{Largest cities in the world (source: Wikipedia)}
-      \begin{tabular}{@{} lr @{}}
-        \toprule
-        City & Population\\
-        \midrule
-        Mexico City & 20,116,842\\
-        Shanghai & 19,210,000\\
-        Peking & 15,796,450\\
-        Istanbul & 14,160,467\\
-        \bottomrule
-      \end{tabular}
-      \hspace*{1cm}
-          \setlength\extrarowheight{3pt}
-      \begin{tabular}{|lr|}
-        \hline
-        \rowcolor{primaryLight}\color{background}City & \color{background}Population\\
-        \hline
-        Mexico City & 20,116,842\\
-        Shanghai & 19,210,000\\
-        Peking & 15,796,450\\
-        Istanbul & 14,160,467\\
-        \hline
-      \end{tabular}
-  \end{table}
-\end{frame}
-
-\begin{frame}{Weight Norm Constraint}
-  \begin{columns}[T,onlytextwidth]
-    \column{0.33\textwidth}
-      \textbf{Items}
-      \begin{itemize}
-        \item Cats \item Dogs \item Birds
-      \end{itemize}
-
-    \column{0.33\textwidth}
-      \textbf{Enumerations}
-      \begin{enumerate}
-        \item First \item Second \item Last
-      \end{enumerate}
-
-    \column{0.33\textwidth}
-      \textbf{Descriptions}
-      \begin{description}
-        \item[Apples] Yes \item[Oranges] No \item[Grappes] No
-      \end{description}
-  \end{columns}
-  \let\thefootnote\relax\footnote{Note the following demo slides are directly taken from metropolis theme. Copyright 2014 Matthias Vogelgesang.\\
-Give a look at https://github.com/matze/mtheme/tree/master/demo}
-\end{frame}
-
-\section{Conclusion}
-
-\subsection{Conclusion and Future Work}
-
-\begin{frame}{Conclusion}
-
-\end{frame}
-
 \section{}

### 2025-05-28 presentation/presentation.tex
gif youtube test

@@
 \usepackage{svg}
+\usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
+\usepackage{multimedia}
+\usepackage{animate}
 
@@
     \begin{itemize}
-      \item \textbf{Optimality}: In general, the adaptation laws are deriven with respect to the tracking error, which may not guarantee optimal performance.
+      \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
       \item \textbf{Unpredictable Amplitude of NN Weights}: 
@@
 
+  % % \movie[width=3cm,height=2cm,poster]{}{overall.mp4}
+  % \begin{figure}
+  %   \centering
+  %   \href{https://youtu.be/U5uDbJQkGY8}{
+  %     \includegraphics[width=.1\textwidth]{figures/KAIST-hi.png}
+  %   }
+  % \end{figure}
+
+  % \animategraphics[loop,width=4cm]{gifs/overall-}
+  \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}
+
 \end{frame}

### 2025-05-30 manuscript.tex
bib update

@@
     \label{eq:cstr:input:norm:grad}
-\end{equation}
+\end{equation}0
 It should be noted that constraints \eqref{eq:cstr:input:bound} and \eqref{eq:cstr:input:norm} can be imposed simultaneously, as their gradients \eqref{eq:cstr:input:bound:grad} and \eqref{eq:cstr:input:norm:grad} are linearly independent, satisfying Assumption \ref{assum:LICQ}, \ie the LICQ condition.

### 2025-06-03 manuscript.tex
prof comment add

@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item For $\mm{A}\in\R^{n\times m}$, denotes the vectorization of $\mm A$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top\in\R^{nm}$.
+    \item For $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
 
-A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN werights are updated. 
+A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN weights are updated. 
 Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
@@
 
-\MSRY{일단 제가 생각하는 기여를 모두 적었습니다.}
-
 The main contributions of this study are listed as follows:
@@
 In this formulation, weight and convex input constraints are incorporated as inequality constraints, while minimizing a given objective function.
-    \item Any convex input constraints can be applied to the proposed CONAC, including input bound constraints, and norm constraints.
+    % \item Any convex input constraints can be applied to the proposed CONAC, including input bound constraints, and norm constraints.
 Moreover, the proposed CONAC can handle any combination of these constraints, which can be useful in practical applications where multiple constraints need to be satisfied simultaneously.
-    \item Since the proposed CONAC approximate the entire ideal control law with no prior knowledge of the system dynamics, the system identification process can be avoided, which is often difficult and time-consuming to implement in practice.
+    % \item Since the proposed CONAC approximate the entire ideal control law with no prior knowledge of the system dynamics, the system identification process can be avoided, which is often difficult and time-consuming to implement in practice.
     \item The adaptation laws for DNN weights in proposed CONAC are systematically derived to solve the defined problem, using constrained optimization theory.
@@
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
-\MSRY{포화가 컨벡스하다는 가정을 추가했습니다.}
 In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
@@
 The corresponding control input constraints of \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, are mathematically defined in Appendix \ref{sec:appen:cstr} as input bound constraint \eqref{eq:cstr:input:norm} and nonlinear input norm constraint \eqref{eq:cstr:input:bound}, respectively.
-\MSRY{sets들과 제약조건을 이어주기 위하여 추가}
 
@@
     \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/dhHong.jpg}}]{Donghwa Hong}
-    Donghwa Hong received his B.S.
+    received his B.S.
 degree in Physics and Engineering Physics from Yonsei University, Wonju, South Korea, in 2023.
@@
     \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/khChoi.jpg}}]{Kyunghwan Choi}
-    Kyunghwan Choi received his B.S., M.S., and Ph.D.
+    received his B.S., M.S., and Ph.D.
 degrees in Mechanical Engineering from KAIST, Daejeon, South Korea, in 2014, 2016, and 2020, respectively.

### 2025-06-05 manuscript.tex
applying comment

@@
-\documentclass[lettersize,journal]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 
@@
     \centering
-    \subfloat[Two-link robotic manipulator.\MSRY{ADD inertia}]{
+    \subfloat[Two-link robotic manipulator.]{
         \includegraphics[width=0.65\linewidth]{src/figures/RobotModel.drawio.pdf}
@@
 
-The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in both episodes, as shown in Table~\ref{tab:sim:L2}.
+The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in the second episodes, as shown in Table~\ref{tab:sim:L2}.
 This is because, (as will be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
 The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) utilized more capability of the actuator than (C$_4$) without considering the control input saturation.
+\KHCH{
+        여기부터 문단 끝날때까지의 표현이 명료하지 않습니다. C3의 tracking performance가 좋은 것은 지표상으로 명확히 맞는 말이기 때문에 마치 tracking performance가 실제로 좋은 것은 아니다라는 뉘앙스의 논리 전개가 적절치 않습니다.
+
+    Tracking performanc는 더 좋지만 과도한 control input을 사용하고, saturation이 지난 이후에는 진동 문제가 있다는 것만 명료하게 표현해주세요.
+}
 One may conclude that (C$_3$) outperformed (C$_4$) since the tracking performance of (C$_3$) was better than (C$_4$), as shown in Table~\ref{tab:sim:L2}.
-However, since the CONAC adapts the weights to reduce the tracking error, \ie which is the only feedback signal, the CONAC increases the control input excessively large to reduce the tracking error, which can not be regulated due to the actuator limits.
-In Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, the violations of the control input saturations grow larger in every saturated time interval.
+\KHCH{어색한 표현; 수정 요}\MSRY{필요없는 내용으로 판단하여 삭제했습니다.}
+However, during the episodes, (C$_3$) increases the control input excessively large to reduce the tracking error, even though it can not be regulated due to the actuator limits as shown in Fig.~\ref{fig:ctrl:result:tau:2} and Fig.~\ref{fig:ctrl:result:tau:norm}, \ie the violations of the control input saturations of (C$_3$) grow larger in every saturated time interval.
 Moreover, this large violation occurs oscillations when the control saturation is released as the reference trajectory is changed, since the weights are adapted to produce large control inputs.
@@
     \centering
-    \subfloat[Control input $\tau$ in time interval from $29.4$ s to $31.9$ s (bird's eye view).]{
+    \subfloat[Control input $\tau$ locus in time interval from $29.4$ s to $31.9$ s.]{
     % \subfloat[Auxiliary states $\mv{\zeta}$ of CONAC-AUX.]{
@@
 		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_2$.
-		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of bigger and smaller Lagrange multiplier, respectively, i.e., $\lambda_{j}' > \lambda_{j}''$.
+		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of large and small Lagrange multiplier, respectively, i.e., $\lambda_{j}' > \lambda_{j}''$.
 	}
@@
 For (C$_1$) and (C$_2$), the control input saturation was handled using the Lagrange multipliers and, for (C$_4$), the auxiliary system was used to handle the control input saturation.
-It is worth to note that the control input constraints were violated repeatedly after constraint handling, since the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
 
@@
 This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$.
-In contrast, (C$_1$), and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$, defined in \eqref{eq:sat}, \ie see, Fig.~\ref{fig:robot:sat}.
+In contrast, (C$_1$) and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$, defined in \eqref{eq:sat}, \ie see, Fig.~\ref{fig:robot:sat}.
 
@@
 As the weights were adapted to reduce not only the filtered error $\fe$ but also the auxiliary state $\mv{\zeta}$, the control input saturation was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
-After the saturation was resolved, the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as described in Fig.~\ref{fig:ctrl:result:scope:aux}.
+After the saturation was resolved at 31 seconds (see Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as described in Fig.~\ref{fig:ctrl:result:scope:aux}.
 
@@
 The effect of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$ on the adaptation direction of the weights $\estwth_2$ is shown in Fig.~\ref{fig:lambda_effect} for a constraint $c_j,\ \forall j\in\mathcal{I}$, with two different amplitudes.
-It is noteworthy that the constraint $c_j$ which satisfies Assumptions \ref{assum:convex} and \ref{assum:LICQ}, is convex in $\estwth_2$-space, \ie see, Lemma. \ref{lem:convex:angle}.
-The bigger and smaller Lagrange multipliers can be interpreted as the case of (C$_1$) and (C$_2$), respectively, since the update rates of the Lagrange multipliers were set to $10^2$ times bigger for (C$_1$) than (C$_2$).
+It is noteworthy that the constraint $c_j$ which satisfies Assumptions \ref{assum:convex} and \ref{assum:LICQ}, is convex in $\estwth_2$-space (see Lemma. \ref{lem:convex:angle}).
+The large and small Lagrange multipliers can be interpreted as the case of (C$_1$) and (C$_2$), respectively, since the update rates of the Lagrange multipliers were set to $10^2$ times larger for (C$_1$) than (C$_2$).
 This results in a fast growth of the Lagrange multipliers $\lambda_j$, when the constraint was violated, \ie see, \eqref{eq:adap:lbd}.
-With the bigger $\lambda_j'$, the adaptation of $\estwth_2$ is more assertive than that with smaller $\lambda_j''$.
+With the larger $\lambda_j'$, the adaptation of $\estwth_2$ is more assertive than that with smaller $\lambda_j''$.
 This leads to a faster satisfaction of the constraint $c_j$, but this also causes oscillation in the adaptation process.
@@
 In the figures, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and disappeared, which indicates that the constraint $c_{\rbu}$ was violated and satisfied, respectively, in the discrete time implementation.
-Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_2$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
-This allows the controller to show a smoother control input.
+Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_2$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and  positive Lagrange multiplier $\lambda_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}.
+This allows (C$_2$) to show a smoother control input.
 
@@
 
-\KHCH{반복해서 이 내용을 설명할 필요가 있을까요?}
-\MSRY{가중치 제약조건 만족에 대한 이야기가 없어서 추가했습니다.}
 The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
@@
 
+\KHCH{
+    이부분은 "worth to note"하지는 않아보입니다. 그리고 FIg 5에서 이 것을 확인하기도 어렵습니다. 굳이 이내용을 유지하려면 Fig 6에서 multiplier가 발생했다 사리지는 현상을 표현할 때 사용해주세요.
+}
+\MSRY{
+    부드럽게 제약조건만족이 안되는 것에 대한 변명(?)으로 포함하고 싶었습니다. 
+    그렇기에 제약조건 파트 제일 마직막으로 뺐습니다.
+}
+In addition, it is worth to note that the control input constraints were repeatedly violated even after the constraint handling, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
+This is because the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
+
 % ------------------------------------
@@
 Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
-However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of the active constraints were positive and inactive constraints were zero.
+However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of the active constraints were positive and those of inactive constraints were zero.
 
@@
 The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time using CPU clock ticks of the OpenCR1.0 board.
-The computational times shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz.
+The computational times shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz, since the computational time of all controllers was less than $4$ ms.
 

### 2025-06-07 presentation/presentation.tex
minor update

@@
 \title{
-    Imposing a Weight Norm Constraint for Neuro–Adaptive Control 
+    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
 } 
@@
 }
-\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}}
+\author{
+  \textbf{Myeongseok Ryu}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
+  }
 \date{\today}
@@
   \vspace{-.7cm}%
+  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
   \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
-  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
   \hspace{.6cm}%
@@
 
-\subsection{Introduction to Neuro–Adaptive Control}
+\subsection{Introduction to Neuro-Adaptive Control}
 
-\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}
+\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}
 
-  \textbf{Neuro–Adaptive Control}
+  \textbf{Neuro-Adaptive Control}
   \small{
     \begin{itemize}
-      \item \textbf{Neuro–adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques} \cite{Farrell:2006aa}.
-      \item It is used to handle \textbf{uncertainties} and \textbf{nonlinearity} in dynamic systems. 
+      \item \textbf{Neuro-adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control} \cite{Farrell:2006aa}.
+      \item Features of both \textbf{NNs} and \textbf{adaptive control} can be found in NAC.
     \end{itemize}
@@
   \begin{figure}
-    \includegraphics[width=0.55\textwidth]{figures/NAC.drawio.pdf}
+    \includegraphics[width=0.65\textwidth]{figures/NAC.drawio.pdf}
   \end{figure}
@@
 
-\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}
+\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}
 
@@
       \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
-      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textbf{Lyapunov stability theory}.
-      \item \textbf{Online Learning Capability}: NAC adapts in \textbf{real-time} to new data with stability guarantees.
-      \item \textbf{Robustness}: NAC handles \textbf{uncertainties and disturbances} effectively with adaptive control techniques.
+      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
+      \item \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
+      \item \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
     \end{itemize}
@@
       \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
-      \item \textbf{Unpredictable Amplitude of NN Weights}: 
+      \item \textbf{Unpredictable Amplitude of Control input}: 
         \begin{itemize}
-          \item NN weights may diverge, leading to instability.
-          \item This can result in unpredictable behavior of the controller.
+          \item The maximum amplitude of the NN weights is not predictable.
+          \item This can result in unpredictable amplitude of the control input, which may lead to control saturation.
         \end{itemize}
       \item \textbf{Parameter Dependency}: 
+      \begin{itemize}
+        \item The performance of the NAC is highly dependent on the choice of parameters, such as learning rate and NN architecture.
+      \end{itemize}
     \end{itemize}
@@
 \begin{frame}{\insertsubsectionhead}{2-Link Robotic Manipulator}
+
+  \begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/exp_set.drawio.png}
+    \caption{2-Link Robotic Manipulator}
+  \end{figure}
+
+  \let\thefootnote\relax\footnote{
+    \textit{Notations}: 
+      $\mv{q}$: Joint position, $\mv{\dot{q}}$: Joint velocity, $\mv{\tau}$: Control input, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector.
+  }
 

### 2025-06-07 manuscript.tex
improve with teacher

@@
 
-\KHCH{여기 아래부터는 글이 많아서 표현 수정을 하나씩 하지 못했습니다. 우선 아래에 있는 메모 반영해주시고, 최종적으로 chatGPT 등 통해서 표현 정리해주세요.
-표현이 조금 어색하거나 구어스러운 부분들이 있습니다.}
-\MSRY{빠른시일내에 수정 예정입니다.}
-
-However, since the DNN's weights are initialized randomly, large reference trajectories should be avoided to mitigate the effect of initial poor performance of the controller.
-Hence, in advance of the reference trajectory, the manipulator was initially positioned at ${\qd}^{\rm{origin}}=\left(-\tfrac{1}{2}\pi,0\right)^\top$, \ie stable equilibrium point.
-Then, a reference trajectory was applied to the manipulator to move from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ in 3 seconds, \ie $\mathcal{P}^5(t;{\qd}^{\rm{origin}},{\qd}_0,3)$, which is the initial and final points of the episode.
-After the manipulator reached ${\qd}_0$, the constant reference trajectory $\qd={\qd}_0$ was applied for 8 seconds to be steady and to avoid the effect of the transient response.
+However, due to the random initialization of the DNN weights, large reference trajectories should be avoided to reduce the impact of the controller's initial poor performance.
+Therefore, prior to applying the reference trajectory, the manipulator was first positioned at a stable equilibrium point, denoted as ${\qd}^{\rm{origin}} = \left(-\tfrac{1}{2}\pi, 0\right)^\top$.
+Subsequently, a trajectory $\mathcal{P}^5(t; {\qd}^{\rm{origin}}, {\qd}_0, 3)$ was used to move the manipulator from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ over a duration of 3 seconds, defining the start and end positions of each episode.
+Once the manipulator reached ${\qd}_0$, a constant reference trajectory $\qd = {\qd}_0$ was maintained for 8 seconds to allow the system to settle and eliminate the influence of transient dynamics.
 
@@
 % ------------------------------------
-The effectiveness of the proposed CONAC to handle the combination of the convex input constraints was demonstrated by defining the saturation function which projects the control input onto following convex set $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
+The effectiveness of the proposed CONAC in handling combined convex input constraints was demonstrated by introducing a saturation function that projects the control input onto the convex set $\Theta_{\mysat} :=\left\{ \Theta_{\mysat, {\tau_2}} \cap \Theta_{\mysat, {\rbu}} \right\}$, as illustrated in Fig.~\ref{fig:robot:sat}, where
 \begin{subequations}
     \begin{align}
+        \Theta_{\mysat, {\tau_2}}
+        :=&
+        \left\{
+            \tau_2
+            \mid
+            \vert{\tau_2}\vert \le 
+            3.5
+            % \overline\tau_2
+        \right\}
+        ,
+        \label{eq:sat:tau2}
+        \\    
         \Theta_{\mysat, {\rbu}}
@@
         \right\}
+        .
         \label{eq:sat:norm}
-        ,
-        \\
-        \Theta_{\mysat, {\tau_2}}
-        :=&
-        \left\{
-            \tau_2
-            \mid
-            \vert{\tau_2}\vert \le 
-            3.5
-            % \overline\tau_2
-        \right\}
-        .
-        \label{eq:sat:tau2}
     \end{align}
@@
 \end{subequations}
-These sets, \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, can be physically interpreted as the current limitation imposed by the power source and the torque limitation of the second joint actuator, respectively.
-The corresponding control input constraints of \eqref{eq:sat:norm} and \eqref{eq:sat:tau2}, are mathematically defined in Appendix \ref{sec:appen:cstr} as input bound constraint \eqref{eq:cstr:input:norm} and nonlinear input norm constraint \eqref{eq:cstr:input:bound}, respectively.
+
+The sets defined in \eqref{eq:sat:tau2} and \eqref{eq:sat:norm} can be physically interpreted as the current limit imposed by the torque limit of the second joint actuator and the power source, respectively.
+The corresponding control input constraints are mathematically described in Appendix~\ref{sec:appen:cstr} as the nonlinear input norm constraint \eqref{eq:cstr:input:bound} and the input bound constraint \eqref{eq:cstr:input:norm}, respectively.
 
@@
 
-For a comparative study, we implemented 4 controllers.
-The properties of the controllers are summarized in Table~\ref{table:controllers}.
+Four controllers were implemented for comparative analysis, with their properties summarized in Table~\ref{table:controllers}.
 
@@
 
-To handle the input saturation, the proposed CONAC was implemented with the input bound constraint \eqref{eq:cstr:input:bound} $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ for second link, and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
+To handle input saturation, the proposed CONAC was implemented with the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} for the second link, and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
 \begin{equation}
@@
 where $\overline\tau_2=-\underline{\tau}_2=3.5$, and $\overline\tau=11$.
-Hence, (C$_1$) is possible to use full capability of the actuator.
-The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ were also considered in the CONAC.
-As described in \eqref{eq:control:est}, the control input (torque) is equal to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
-
-The update rates of the Lagrange multipliers for weight norm constraints were set to $\beta_{\theta_i}=1,\ \forall i\in\{0,\cdots,k\}$, and ,for control input constraints, the update rates were set to large values such that $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$ to investigate the effect of the large values of update rates.
+Therefore, controller (C$1$) utilizes the full capability of the actuator.
+The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ defined in \eqref{eq:cstr:weight:ball}, were also incorporated into the CONAC framework.
+As described in \eqref{eq:control:est}, the control input (torque) corresponds to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
+
+The update rates of the Lagrange multipliers for the weight norm constraints were set to $\beta_{\theta_i}=1,\ \forall i\in\{0,\cdots,k\}$.
+For the control input constraints, the update rates were assigned large values: $\beta_{\rbu} = 10$ and $\beta_{\overline{\tau}2} = \beta{\underline{\tau}_2} = 10^2$, in order to investigate the effect of large update rates.
 
@@
 
-As the second controller, the proposed CONAC was implemented with the same input bound constraints as (C$_1$), but with $100$ times smaller update rate values such that $\beta_{\rbu}=0.1$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=1$.
-The remaining properties and parameters were the same as (C$_1$).
+As the second controller, the proposed CONAC was implemented with the same input bound constraints as (C$_1$), but with $100$ times smaller update rate values: $\beta_{\rbu}=0.1$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=1$.
+All other properties and parameters were kept identical to those of (C$_1$).
 
@@
 
-The third controller was the same as (C$_1$) and (C$_2$), but without the control input constraints, to emphasize the control input constraint handling capability of the proposed CONAC.
-In this case, the update rates of the Lagrange multipliers regarding the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, were set to $0$, so that $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ are not updated, \ie see, \eqref{eq:adap:lbd}.
-The remaining properties and parameters were the same as (C$_1$) and (C$_2$).
+The third controller was identical to (C$1$) and (C$2$), except that the control input constraints were removed to highlight the constraint handling capability of the proposed CONAC.
+In this case, the update rates of the Lagrange multipliers associated with the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, were set to zero, such that the corresponding multipliers $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ were not updated (see \eqref{eq:adap:lbd}).
+All other properties and parameters were kept the same as in (C$_1$) and (C$_2$).
 
@@
 
-On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed CONAC with control input constraints by replacing them with the auxiliary system.
-The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$, with $\mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^2$ denotes the auxiliary state variables, and $\mm{A}_\zeta\in\R_{<0}^{2\times 2}$, and $\mm{B}_\zeta\in\R^{2\times 2}$ are user-designed matrices.
-The auxiliary state $\mv{\zeta}$ is affected by the overflow amount of the control input $\Delta\rbu$, whose entries are defined as $\Delta\tau_{i} = 
-\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
-The auxiliary state were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.
-Consequently, the weights were adapted to reduce not only the filtered tracking error $\fe$ but also the auxiliary state $\mv{\zeta}$, minimizing the control input constraint saturation.
-
-The matrices of the auxiliary system were set to $\mm{A}_\zeta=\mydiag\left((-10,-10)^\top\right)$ and $\mm{B}_\zeta=\mydiag\left((10^3,10^3)^\top\right)$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed of the auxiliary system.
-Since, the auxiliary system only considers the saturation of each control input, \ie which is same as the input bound constraint \eqref{eq:cstr:input:bound}, $\overline{\tau}_1$ was set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, with respect to $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$, \ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$.
+As a baseline for comparison, the existing auxiliary system approach \cite{Esfandiari:2014aa, Karason:1994aa, Esfandiari:2015aa} was implemented in place of the proposed CONAC for handling control input constraints.
+The auxiliary system is defined by $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$, with initial condition $\mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^2$ represents the auxiliary state variables, and $\mm{A}_\zeta\in\R_{<0}^{2\times 2}$ and $\mm{B}_\zeta\in\R^{2\times 2}$ are user-designed matrices.
+The auxiliary state $\mv{\zeta}$ is driven by the overflow amount of the control input $\Delta\rbu$, where each element is defined as $\Delta\tau_{i} = \tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$..
+
+This auxiliary state was incorporated into the adaptation law \eqref{eq:adap:th:approx} by replacing the filtered tracking error $\fe$ with $\fe+\mv{\zeta}$.
+As a result, the weights were adapted to minimize both the filtered tracking error and the auxiliary state, thereby resolving the control input constraint saturation.
+
+The matrices for the auxiliary system were chosen as $\mm{A}_\zeta=\mydiag\left((-10,-10)^\top\right)$ and $\mm{B}_\zeta=\mydiag\left((10^3,10^3)^\top\right)$, reflecting a trade-off between sensitivity to input saturation and convergence speed of the auxiliary dynamics.
+Since the auxiliary system only accounts for individual input saturation—corresponding to the input bound constraint \eqref{eq:cstr:input:bound}—the upper limit for the first actuator torque, $\overline{\tau}_1$, was set to $10.428$ to approximately match the allowable control input norm $\overline{\tau}$, given $\overline{\tau}_2 = 3.5$ and $\overline{\tau} = 11$, satisfying $\overline{\tau}_1^2 + \overline{\tau}_2^2 = \overline{\tau}^2$.
 
@@
 % ------------------------------------
-For all controllers, \ie (C$_1$), (C$_2$), (C$_3$), and (C$_4$), the DNN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{7}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix.
-All DNN architectures have two hidden layers with four nodes, \ie $k=2$, and $l_0=6, l_1=4, l_2=4$, and $l_3=2$ in \eqref{eq:DNN:architecture}, and the adaptation gain was set to $\alpha=0.2$.
-The filtering matrix $\mm{\Lambda}$ in \eqref{eq:err:filtered}, was set to $\mm{\Lambda}=\mydiag([5,15])$.
-The DNNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
-The sampling rate of the controller was $250$ Hz considering the real-time implementation.
-The weight norm constraint parameters were selected as $\overline\wth_0=\overline\wth_1=\overline\wth_2=6$.
-The control results were collected via CAN communication with PCAN USB  and recorded in a computer with a sampling rate of $250$ Hz.
-
-The quantitative comparison of the tracking performance was evaluated using the $L_2$-norm of them, \ie $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the each episode duration time.
+For all controllers, \ie (C$_1$), (C$_2$), (C$_3$), and (C$_4$), the input vector to the DNN was defined as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{7}$, where the scalar $1$ was included to account for the bias term in the weight matrix.
+All DNNs shared the same architecture, consisting of two hidden layers with four nodes each, \ie $k=2$ and $l_0=6, l_1=4, l_2=4$, and $l_3=2$ in \eqref{eq:DNN:architecture}.
+The adaptation gain was set to $\alpha = 0.2$, and the filtering matrix in \eqref{eq:err:filtered} was chosen as $\mm{\Lambda}=\mydiag([5,15])$.
+The DNN weights were initialized using a uniform distribution in the range $[-0.1, 0.1]$, with the same random seed used across all experiments to ensure consistency.
+The controller sampling rate was set to $250$ Hz to support real-time implementation.
+Weight norm constraint parameters were selected as $\overline\theta_0=\overline\theta_1=\overline\theta_2=6$.
+
+Control results were collected via CAN communication using a PCAN-USB interface and recorded on a computer at a sampling rate of $250$ Hz.
+
+The tracking performance was quantitatively evaluated using the $L_2$-norm of the tracking error, defined as $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the duration of each episode.
 
@@
 
-The real-time implementation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
-Across the two episodes, all controllers enhanced their tracking performances, \ie $71.6 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$) in $L_2$ norm of $e_1$, and $88.4 \%$ for (C$_1$), $76.9 \%$ for (C$_2$), $72.8 \%$ for (C$_3$), and $67.1 \%$ for (C$_4$) in $L_2$ norm of $e_2$, respectively.
-Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode.
-This results lead to the conclusion that the DNNs in all controllers were able to learn the ideal control input $\rbu^*$ properly using the filtered error $\fe$, despite the fact that $\rbu^*$ was completely unknown in advance.
-Moreover, since the stable learning was achieved with the random weight initialization and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.
-
-Notably, in both episodes, all controllers failed to track the desired trajectory of $q_1$ in time intervals from $17.5$ s to $19.9$ s for Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s for Episode $2$.
-This is because the control inputs were saturated in the time intervals, as shown in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
-
-The tracking performances of CONAC with control input constraints, \ie (C$_1$), and (C$_2$), outperformed CONAC with the auxiliary system (C$_4$) in the second episodes, as shown in Table~\ref{tab:sim:L2}.
-This is because, (as will be discussed in Section \ref{sec:sim:constraint}) (C$_1$), and (C$_2$) were able to use the full capability of the actuator, while (C$_4$) was limited its first link actuator due to the feature of the auxiliary system.
-The tracking performance of (C$_3$) was also better than (C$_4$), but this is because (C$_3$) utilized more capability of the actuator than (C$_4$) without considering the control input saturation.
+The real-time implementation results are presented in Fig.\ref{fig:ctrl:result}, and the quantitative comparison of tracking performance is summarized in Table\ref{tab:sim:L2}.
+Across the two episodes, all controllers improved their tracking performance. 
+Specifically, the $L_2$-norm of $e_1$ was reduced by $71.6 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$); while the $L_2$-norm of $e_2$ was reduced by $88.4 \%$, $76.9 \%$, $72.8 \%$, and $67.1 \%$, respectively.
+Qualitatively, as illustrated in Fig.\ref{fig:ctrl:result:q1} and Fig.\ref{fig:ctrl:result:q2}, oscillations were suppressed during the second episode.
+These results indicate that the DNNs in all controllers successfully learned the ideal control input $\rbu^*$ using the filtered tracking error $\fe$, despite $\rbu^*$ being completely unknown a priori.
+Furthermore, the stable learning achieved under random weight initialization and without prior knowledge of the system demonstrates the effectiveness of the proposed CONAC in enabling online learning.
+
+Notably, in both episodes, all controllers failed to track the desired trajectory of $q_1$ during certain time intervals: from $17.5$ s to $19.9$ s in Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s in Episode $2$.
+This degradation in tracking performance is attributed to actuator saturation during those intervals, as observed in Fig.\ref{fig:ctrl:result:tau:1} and Fig.\ref{fig:ctrl:result:tau:norm}.
+
+The tracking performance of CONAC with control input constraints—\ie (C$_1$) and (C$_2$)—outperformed the auxiliary system-based controller (C$_4$) in the second episode, as shown in Table~\ref{tab:sim:L2}.
+This improvement is due to the fact that (C$_1$) and (C$_2$) were able to fully utilize the actuator's capabilities, whereas (C$_4$) was constrained by the auxiliary system's design, which limited the first joint actuator.
+While (C$_3$) also showed better performance than (C$_4$), this was primarily because it did not consider input saturation and thus used more of the actuator's capacity.
 \KHCH{
         여기부터 문단 끝날때까지의 표현이 명료하지 않습니다. C3의 tracking performance가 좋은 것은 지표상으로 명확히 맞는 말이기 때문에 마치 tracking performance가 실제로 좋은 것은 아니다라는 뉘앙스의 논리 전개가 적절치 않습니다.
-
     Tracking performanc는 더 좋지만 과도한 control input을 사용하고, saturation이 지난 이후에는 진동 문제가 있다는 것만 명료하게 표현해주세요.
@@
 	\caption{
-		The effect of Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{ \mv{\theta}}_2$.
-		The notation ($\cdot'$) and ($\cdot''$) represent two different cases of large and small Lagrange multiplier, respectively, i.e., $\lambda_{j}' > \lambda_{j}''$.
+        The effect of the Lagrange multiplier $\lambda_{j}$ on the adaptation direction of $\widehat{\mv{\theta}}_2$ is illustrated. 
+        The notations $(\cdot)'$ and $(\cdot)''$ denote two distinct cases corresponding to large and small values of the Lagrange multiplier, respectively, \ie $\lambda_{j}' > \lambda_{j}''$.
 	}
@@
 
-Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was not able to use the full capability of the actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:control} which shows the bird-eye view of the control input $\rbu$ in time interval from $29.4$ s to $31.9$ s.
-This is because, as aforementioned, the auxiliary system only considers saturation of each control input, and the maximum value of the first link's torque $\overline{\tau}_1$ was set to approximately match the maximum allowable norm of the control input $\overline\tau$.
-In contrast, (C$_1$) and (C$_2$) were able to use the full capability of the actuator with the combination of the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$, and the nonlinear input norm constraint $c_{\rbu}$ which is completely match the feasible domain of the control input $\Theta_{\mysat}$, defined in \eqref{eq:sat}, \ie see, Fig.~\ref{fig:robot:sat}.
+\KHCH{
+    여기에 각 제어기의 constraint를 표현해주는게 좋겠습니다. FIg6a만 보고 아래의 설명을 이해하기에는 리뷰어들에게 어려움이 있을 겁니다.
+}
+\MSRY{
+    아래의 설명을 보완하여 각 제어기의 constraint를 표현해주었습니다.
+}
+Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was unable to fully utilize the actuator's capability.
+As shown in Fig.~\ref{fig:ctrl:result:scope:control}, which illustrates the control input locus during the time interval from $29.4$ s to $31.9$ s, the control inputs of (C$_1$) and (C$_2$) were constrained by the combined convex input constraints, which precisely matched the feasible domain $\Theta_{\mysat}$ depicted in Fig.~\ref{fig:robot:sat}
+In contrast, (C$_4$)'s control input was restricted independently by each component-wise constraint, limiting its ability to explore the full admissible input space, owing to the decoupled formulation of the auxiliary system.
 
@@
 % zeta
-The detail of the constraint handling in the time interval from $29.4$ s to $31.9$ s, is now investigated.
-First, for (C$_4$), the auxiliary state $\zeta_1$ was generated by control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
-As the weights were adapted to reduce not only the filtered error $\fe$ but also the auxiliary state $\mv{\zeta}$, the control input saturation was reduced, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
-After the saturation was resolved at 31 seconds (see Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero, by the stable state matrix $\mm{A}_\zeta$ in the auxiliary system, \ie $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as described in Fig.~\ref{fig:ctrl:result:scope:aux}.
+The detail of the constraint handling during the time interval from $29.4$ s to $31.9$ s, is now investigated.
+For (C$_4$), the auxiliary state $\zeta_1$ was generated in response to the control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
+Since the weights were adapted to reduce both the filtered error $\fe$ and the auxiliary state $\mv{\zeta}$, the control input saturation was subsequently reduced, as evident in Fig.\ref{fig:ctrl:result:scope:control}.
+Once the saturation was resolved at approximately $31$ seconds (see, Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero due to the stable state matrix $\mm{A}_\zeta$ in the auxiliary dynamics, given by $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as shown again in Fig.~\ref{fig:ctrl:result:scope:aux}.
 
 % beta + zeta
-For the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_j\in\forall j\in\mathcal{I}$ adjusted the adaptation direction of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$ to reduce the constraint violation $c_j\in\forall j\in\mathcal{I}$, as $\lambda_j\in\forall j\in\mathcal{I}$ generated by the constraint violations.
+In the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_j\in\forall j\in\mathcal{I}$ directed the adaptation of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$, to reduce violations of the constraints $c_j$.
+The multipliers $\lambda_j$ were generated dynamically in response to constraint violations.
 % comparison; big, small beta
-The effect of the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal{I}$ on the adaptation direction of the weights $\estwth_2$ is shown in Fig.~\ref{fig:lambda_effect} for a constraint $c_j,\ \forall j\in\mathcal{I}$, with two different amplitudes.
-It is noteworthy that the constraint $c_j$ which satisfies Assumptions \ref{assum:convex} and \ref{assum:LICQ}, is convex in $\estwth_2$-space (see Lemma. \ref{lem:convex:angle}).
-The large and small Lagrange multipliers can be interpreted as the case of (C$_1$) and (C$_2$), respectively, since the update rates of the Lagrange multipliers were set to $10^2$ times larger for (C$_1$) than (C$_2$).
-This results in a fast growth of the Lagrange multipliers $\lambda_j$, when the constraint was violated, \ie see, \eqref{eq:adap:lbd}.
-With the larger $\lambda_j'$, the adaptation of $\estwth_2$ is more assertive than that with smaller $\lambda_j''$.
-This leads to a faster satisfaction of the constraint $c_j$, but this also causes oscillation in the adaptation process.
-
-Hence, invoking above discussion, the real-time implementation results of (C$_1$) and (C$_2$) are compared in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}.
-In the figures, $\lambda_{\rbu}$ of (C$_1$) repeatedly increased and disappeared, which indicates that the constraint $c_{\rbu}$ was violated and satisfied, respectively, in the discrete time implementation.
-Besides, with small $\lambda_{\rbu}$, the adaptation direction of $\estwth_2$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and  positive Lagrange multiplier $\lambda_{\rbu}$, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}.
-This allows (C$_2$) to show a smoother control input.
+The effect of Lagrange multiplier $\lambda_j$ on the adaptation direction of $\estwth_2$ is illustrated in Fig.~\ref{fig:lambda_effect}, where two different magnitudes of $\lambda_j$ are considered. 
+Notably, under Assumptions \ref{assum:convex} and \ref{assum:LICQ}, the constraint $c_j$ is convex in the $\estwth_2$-space (see, Lemma~\ref{lem:convex:angle}).
+Large and small Lagrange multipliers correspond to the configurations of (C$_1$) and (C$_2$), respectively, because the update rates in (C$_1$) were set $10^2$ times larger than those in (C$_2$).
+Consequently, in (C$_1$), $\lambda_j$ increases more rapidly in response to constraint violations (see, \eqref{eq:adap:lbd}). 
+This results in a more aggressive adaptation of $\estwth_2$, leading to faster constraint satisfaction—but at the cost of oscillatory behavior in the learning process.
+
+Following this reasoning, the real-time implementation results of (C$_1$) and (C$_2$) are compared in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}. 
+In these figures, $\lambda_{\rbu}$ for (C$_1$) repeatedly grows and resets, indicating recurring violations and satisfactions of the $c_{\rbu}$ constraint in discrete time.
+On the other hand, (C$_2$), with smaller $\lambda_{\rbu}$, updates $\estwth_2$ more conservatively. 
+This slower response leads to delayed constraint satisfaction, which is reflected by the persistent positive value of $\lambda_{\rbu}$ in Fig.\ref{fig:ctrl:result:scope:beta}. 
+However, this allows (C$_2$) to achieve smoother control input behavior, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
 
@@
 
-Finally, the constraint handling of the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$ is investigated.
-The weight norm constraints were not activated except for the outer layer weights $c_{\theta_2}$ of (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}.
-This is because the weights of (C$_1$), (C$_2$), and (C$_4$) were implicitly suppressed by the control input constraints, while (C$_3$) was not.
+Finally, the handling of the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$, is investigated. 
+Among all controllers, the weight norm constraint was only activated for the outer layer weights $c_{\theta_2}$ in (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}. 
+This is because the weights in (C$_1$), (C$_2$), and (C$_4$) were implicitly suppressed by the control input constraints, whereas (C$_3$) did not incorporate such constraints.
 % , \ie by limiting the control input, the weight norms were also limited.
 % \MSRY{필요하다면 왜 제어입력 제약하는게 가중치 제약도 되는지 추가 가능}
-In addition, the inner and hidden layer weights constraints were not violated, \ie $\norm{\estwth_0},\norm{\estwth_1}$ were uniformly lower than $\norm{\estwth_2}$, since the backpropagated error was multiplied by the gradient of the activation function, which is limited from $-1$ to $1$, \ie see, \eqref{eq:gradient:phi}.
-
-The details of the constraint handling process are shown in Fig.~\ref{fig:ctrl:result:scope}, as well.
-In Fig.~\ref{fig:ctrl:result:scope:beta}, the Lagrange multipliers $\lambda_{\theta_2}$ were increased by the weight $\estwth_2$ exceeds the weight norm constraint $\overline\wth_2$, and the adaptation direction of the weights $\estwth_2$ was adjusted to resolve the violation of the constraint $c_{\theta_2}$.
+Furthermore, the constraints on the inner and hidden layer weights were never violated; that is, $\norm{\estwth_0}$ and $\norm{\estwth_1}$ consistently remained below $\norm{\estwth_2}$. 
+This is attributed to the fact that the backpropagated error was scaled by the gradient of the activation function, which is bounded between $-1$ and $1$; see, \eqref{eq:gradient:phi}.
+
+Additional details on the constraint handling process are provided in Fig.~\ref{fig:ctrl:result:scope}. 
+In particular, Fig.~\ref{fig:ctrl:result:scope:beta} shows that the Lagrange multipliers $\lambda_{\theta_2}$ increased when $\estwth_2$ exceeded the prescribed norm constraint $\overline\theta_2$, prompting an adjustment in the adaptation direction of $\estwth_2$ to mitigate the violation of the constraint $c_{\theta_2}$.
 
@@
 }
-In addition, it is worth to note that the control input constraints were repeatedly violated even after the constraint handling, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
-This is because the controllers were implemented in discrete time with a low sampling rate of $250$ Hz.
+
+In addition, it is worth noting that the control input constraints were repeatedly violated even after the constraint handling mechanisms were applied, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
+This occurred because the controllers were implemented in discrete time with a relatively low sampling rate of $250$ Hz.
 
@@
 
-Since the proposed CONAC was implemented in discrete time, demonstration regarding the KKT conditions in steady state is not straightforward.
-However, as the weights and Lagrange multipliers were almost constant when the constraints were violated, the satisfaction of the KKT conditions can be implicitly shown, since the Lagrange multipliers of the active constraints were positive and those of inactive constraints were zero.
+Since the proposed CONAC was implemented in discrete time, a direct demonstration of the KKT conditions at steady state is not straightforward. 
+However, the near-constant values of the weights and Lagrange multipliers during constraint violation suggest an implicit satisfaction of the KKT conditions. 
+Specifically, the Lagrange multipliers corresponding to active constraints were positive, while those associated with inactive constraints remained zero.
 
@@
 
-The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time using CPU clock ticks of the OpenCR1.0 board.
-The computational times shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, indicates that the proposed CONAC can be implemented in real-time applications with a sampling rate of $250$ Hz, since the computational time of all controllers was less than $4$ ms.
+The effectiveness of the proposed CONAC in real-time applications was evaluated by measuring the computational time using CPU clock ticks on the OpenCR1.0 board. 
+As shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}, the computational times of all controllers remained below $4$ ms, demonstrating that the proposed CONAC is suitable for real-time implementation at a sampling rate of $250$ Hz.
 
@@
 
-This section introduces potential weight and input constraints that can be used in the proposed CONAC.
+This section introduces potential weight and input constraints that can be incorporated into the proposed CONAC framework.
 
@@
 
-Most physical systems have control input limits due to electrical and mechanical limitations.
+Most physical systems are subject to control input limitations due to inherent electrical and mechanical constraints.
 These are expressed as $\mv{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in\{1,\cdots,n\}}$ and $\mv{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in\{1,\cdots,n\}}$, where

### 2025-06-08 manuscript.tex
final touch for shJang

@@
 \thanks{
-    Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korean Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr and kh.choi@kaist.ac.kr).
+    Myeongseok Ryu and Kyunghwan Choi are with the Cho Chun Shik Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), Daejeon 34051, Korea (e-mail: dding\_98@kaist.ac.kr and kh.choi@kaist.ac.kr).
 
@@
 \begin{abstract}
-  This study presents a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems subject to weight norm and convex input constraints. 
+  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for uncertain Euler-Lagrange systems subject to weight and convex input constraints. 
   A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a constrained optimization framework.
-  The weight adaptation laws are formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
+  The adaptation law of DNN weights is formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
   The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and bounded DNN weights. 
@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item For $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  )^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
+    \item For $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=\left(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top)  \right)^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
 Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations.
-SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
+Conventionally, SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
 However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa} and physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
-
-A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN weights are updated. 
+\MSRY{CNN도 넣을까요? Dixon교수님네도 저희 preprint논문 인용하셨더라구요}
+
+A critical aspect of neuro-adaptive control is the NN weight adaptation law, which governs how NN weights are updated. 
 Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.
@@
 
-Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations. 
+Although both the existing methods for weight boundedness and input constraints have shown effectiveness, they come with significant limitations. 
 Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
-Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints.
+Moreover, auxiliary systems typically handle only simple forms of input constraints, such as individual input bound constraints, limiting their ability to address more complex, nonlinear constraints.
 
@@
 \begin{itemize}
-    \item A constrained optimization-based neuro-adaptive controller (CONAC) is proposed, where the design of a deep neural network (DNN) is formulated as a constrained optimization problem.
+    \item A constrained optimization-based neuro-adaptive control (CONAC) is proposed, where the control problem is formulated as a constrained optimization problem.
 In this formulation, weight and convex input constraints are incorporated as inequality constraints, while minimizing a given objective function.
@@
     % \item Since the proposed CONAC approximate the entire ideal control law with no prior knowledge of the system dynamics, the system identification process can be avoided, which is often difficult and time-consuming to implement in practice.
-    \item The adaptation laws for DNN weights in proposed CONAC are systematically derived to solve the defined problem, using constrained optimization theory.
+    \item The adaptation laws for DNN weights and Lagrange multipliers are systematically derived to solve the defined problem, using constrained optimization theory.
 These laws guarantee convergence to the first-order optimality conditions, specifically the Karush–Kuhn–Tucker (KKT) conditions, as described in \cite[Chap.
@@
     \item The proposed CONAC is implemented in real-time on a 2-DOF robotic manipulator, demonstrating its effectiveness in achieving accurate trajectory tracking while satisfying all imposed constraints.
-The experimental results validate the theoretical findings and show the practical applicability of the proposed controller.
+The experimental results validate the theoretical findings and show the practical applicability of the proposed CONAC.
 \end{itemize}
@@
 Section \ref{sec:Problem Formulation} presents the target system and control objective.
-Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
-In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
-Section \ref{sec:stability} analyzes the stability of the proposed controller.
-A real-time implementation of the proposed controller is presented in Section \ref{sec:sim}, where the proposed controller is applied to a 2-DOF robotic manipulator.
+Section \ref{sec:ctrl design} introduces the proposed CONAC and the architecture of DNN in the controller. 
+In Section \ref{sec:adap_laws}, the adaptation law is developed.
+Section \ref{sec:stability} analyzes the stability of the proposed CONAC.
+A real-time implementation of the proposed CONAC is presented in Section \ref{sec:sim}, where the proposed CONAC is applied to a 2-DOF robotic manipulator.
 Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
-The candidates of input constraints are presented in Appendix \ref{sec:appen:cstr}.
+The candidates of convex input constraints are presented in Appendix \ref{sec:appen:cstr}.
 
@@
 where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
-The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
+The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
@@
 \begin{prop}
-    The disturbance $\rbd$ is bounded, \ie $\norm{\rbd}\le \overline\tau_d$.
+    The disturbance $\rbd$ is bounded, \ie $\norm{\rbd}\le \overline\tau_d$, where $\overline\tau_d\in\R_{\ge0}$.
     \label{prop:dis_bound}
@@
 \begin{assum}
-    The desired trajectory $\qd(t)$ is assumed to be bounded, i.e., $\norm{\qd(t)}\le \overline{q}_d$ , and available for designing a bounded control input.
+    The desired trajectory $\qd(t)$ is assumed to be bounded, \ie $\norm{\qd(t)}\le \overline{q}_d\in\R_{>0}$ , and available for designing a bounded control input.
     \label{assum:feasible}
@@
 Section \ref{sec:sub:NAC} introduces the neuro-adaptive controller, followed by the DNN model in Section \ref{sec:sub:NN definition}. 
-The constrained optimization-based weight adaptation laws are presented in Section \ref{sec:adap_laws}.
+The constrained optimization-based weight adaptation law is presented in Section \ref{sec:adap_laws}.
 
@@
         \right)^2
-        -
+        +
         \tfrac{a_2^2}{4a_1}
@@
     \end{equation}
-    According to \eqref{eq:lem:lya:dot}, one can conclude that $\ddtt V$ is negative definite if $\norm{\mv{x}}\le\tfrac{a_2}{a_1}$ holds.
-    In other words, $\mv{x}$ remains within the bounded set $\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
+    According to \eqref{eq:lem:lya:dot}, one can conclude that $\ddtt V$ is negative definite if $\norm{\mv{x}}>\tfrac{a_2}{a_1}$ holds.
+    In other words, $\mv{x}$ remains within the bounded set $\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$, since $\ddtt V$ is negative definite when $\mv{x}$ is outside the set.
 \end{proof}
@@
 
-First, the filtered tracking error $\fe\in\R^n$ is defined as 
+First, a filtered tracking error $\fe\in\R^n$ is defined as 
 \begin{equation}
@@
 where $\mm{K}=\mm{K}^\top\in\R^{n\times n}_{>0}$ denotes an arbitrary unknown matrix and $
-    \mv f:= \mv f(\q,\dq,\qd,\dqd,\ddqd)
+    \mv f:= \mv F
+    \left(
+        \q,\dq,\qd,\dqd,\ddqd
+    \right)
     =
     \mm K \fe
-    +\rbM(-\ddqd+\mm\Lambda\ddtt{\mv e})
-    +
-    \rbVm(-\dqd+\mm\Lambda\mv e)
+    +\rbM
+    \left(
+        -\ddqd+\mm\Lambda\ddtt{\mv e}
+    \right)
+    +
+    \rbVm
+    \left(
+        -\dqd+\mm\Lambda\mv e
+    \right)
     -
@@
         =&
-        \fe^\top (
+        \fe^\top 
+        \left(
             -\rbVm \fe -\mm K \fe + \mv f
             -\rbd + \mysat(\rbu)
-        )
+        \right)
         \\
@@
         +
-        \fe^\top (
-            \mv f+\mysat(\rbu)
+        \fe^\top 
+        \left(
+            \mv f
             -\rbd
-        )
+            +\mysat(\rbu)
+        \right)
         \\
@@
 Let $\NN:=\NN({\q}_n;\wth): \R^{l_0+1}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where ${\q}_n\in\R^{l_0+1}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
-The architecture of $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}.
-According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an ideal weight vector $\idealwth$ over a compact subset $\Omega_{NN}\in\R^{l}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{NN}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
+The architecture of DNN $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}, later.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
 % Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
-In this study, $\idealwth$ is considered a locally optimal solution, rather than a global one.
+In this study, the ideal weight vector $\idealwth$ is considered a locally optimal solution, rather than a global one.
 
@@
 \end{align}
-where $\hat\NN:=\NN({\q}_n;\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
+where $\hat\NN:=\NN({\q}_n;\estwth)$, and  $\estwth\in\R^\Xi$ is the estimated weight vector for $\idealwth$.
 
@@
     +
-    \fe^\top (\mysat(\hat\NN)-\idealNN-\mv\epsilon)
+    \fe^\top 
+    \left(
+        -\idealNN
+        -\mv\epsilon
+        +\mysat(\hat\NN)
+    \right)
     .
@@
 \end{equation}
-Therefore, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$ (\ie $\hat\NN\to\idealNN$), neglecting the effect of input saturation.
+Therefore, one can conclude that the result of \eqref{eq:lya1:dot1} can be obtained by adapting $\estwth$ to $\idealwth$, \ie $\hat\NN\to\idealNN$, neglecting the effect of input saturation.
 Note that the control input saturation has not yet been considered in the derivation of the ideal control input; this will be addressed in the subsequent section.
@@
 The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
-Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$ (\ie $l_{k+1}=n$).
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$, \ie $l_{k+1}=n$.
 
@@
 These functions simplify stability analysis, since they are continuously differentiable and their outputs and gradients are bounded. 
-In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function (\ie $\sigma(x) = \tanh(x),\ \forall x\in\R$), which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}\le 1$.
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function, \ie $\sigma(x) = \tanh(x),\ \forall x\in\R$, which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}\le 1$.
 
 For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
-The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in \{0,\cdots,k\}$ as 
+The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i, \forall i\in \{0,\cdots,k\}$ as 
 \begin{equation}
@@
         \tfrac{1}{2} \fe^\top \fe
+        ,
         \\ \\
@@
 
-The real-time implementation results are presented in Fig.\ref{fig:ctrl:result}, and the quantitative comparison of tracking performance is summarized in Table\ref{tab:sim:L2}.
+The real-time implementation results are presented in Fig.~\ref{fig:ctrl:result}, and the quantitative comparison of tracking performance is summarized in Table~\ref{tab:sim:L2}.
 Across the two episodes, all controllers improved their tracking performance. 
 Specifically, the $L_2$-norm of $e_1$ was reduced by $71.6 \%$ for (C$_1$), $63.1 \%$ for (C$_2$), $63.7 \%$ for (C$_3$), and $18.5 \%$ for (C$_4$); while the $L_2$-norm of $e_2$ was reduced by $88.4 \%$, $76.9 \%$, $72.8 \%$, and $67.1 \%$, respectively.
-Qualitatively, as illustrated in Fig.\ref{fig:ctrl:result:q1} and Fig.\ref{fig:ctrl:result:q2}, oscillations were suppressed during the second episode.
+Qualitatively, as illustrated in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, oscillations were suppressed during the second episode.
 These results indicate that the DNNs in all controllers successfully learned the ideal control input $\rbu^*$ using the filtered tracking error $\fe$, despite $\rbu^*$ being completely unknown a priori.
@@
 Notably, in both episodes, all controllers failed to track the desired trajectory of $q_1$ during certain time intervals: from $17.5$ s to $19.9$ s in Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s in Episode $2$.
-This degradation in tracking performance is attributed to actuator saturation during those intervals, as observed in Fig.\ref{fig:ctrl:result:tau:1} and Fig.\ref{fig:ctrl:result:tau:norm}.
+This degradation in tracking performance is attributed to actuator saturation during those intervals, as observed in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
 
@@
 While (C$_3$) also showed better performance than (C$_4$), this was primarily because it did not consider input saturation and thus used more of the actuator's capacity.
+However, since (C$_3$) did not handle the control input saturation, it generated excessively large control efforts to minimize the tracking error, even though these efforts could not be realized due to actuator limits, as shown in Fig.~\ref{fig:ctrl:result:tau:2} and Fig.~\ref{fig:ctrl:result:tau:norm}.
+In addition, the magnitude of saturation violations for (C$_3$) increased during each interval where input constraints were active.
+Such large violations may lead to actuator damage or failure, posing a significant risk to the physical system.
+Moreover, once the control saturation was released—typically due to a change in the reference trajectory—these large violations resulted in oscillatory behavior, as the controller's weights had been adapted to produce excessively high control inputs.
 \KHCH{
@@
 }
-One may conclude that (C$_3$) outperformed (C$_4$) since the tracking performance of (C$_3$) was better than (C$_4$), as shown in Table~\ref{tab:sim:L2}.
-\KHCH{어색한 표현; 수정 요}\MSRY{필요없는 내용으로 판단하여 삭제했습니다.}
-However, during the episodes, (C$_3$) increases the control input excessively large to reduce the tracking error, even though it can not be regulated due to the actuator limits as shown in Fig.~\ref{fig:ctrl:result:tau:2} and Fig.~\ref{fig:ctrl:result:tau:norm}, \ie the violations of the control input saturations of (C$_3$) grow larger in every saturated time interval.
-Moreover, this large violation occurs oscillations when the control saturation is released as the reference trajectory is changed, since the weights are adapted to produce large control inputs.
 
@@
         \vfill
-    \subfloat[Lagrange multipliers $\lambda_j$  in time interval from $29.4$ s to $31.9$ s.]{
+    \subfloat[Lagrange multipliers $\lambda_j,\forall j\in\mathcal{I}$  in time interval from $29.4$ s to $31.9$ s.]{
         \includegraphics[width=\figSizeOneCol\linewidth]
@@
 For (C$_4$), the auxiliary state $\zeta_1$ was generated in response to the control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
-Since the weights were adapted to reduce both the filtered error $\fe$ and the auxiliary state $\mv{\zeta}$, the control input saturation was subsequently reduced, as evident in Fig.\ref{fig:ctrl:result:scope:control}.
+Since the weights were adapted to reduce both the filtered error $\fe$ and the auxiliary state $\mv{\zeta}$, the control input saturation was subsequently reduced, as evident in Fig.~\ref{fig:ctrl:result:scope:control}.
 Once the saturation was resolved at approximately $31$ seconds (see, Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero due to the stable state matrix $\mm{A}_\zeta$ in the auxiliary dynamics, given by $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as shown again in Fig.~\ref{fig:ctrl:result:scope:aux}.
@@
 On the other hand, (C$_2$), with smaller $\lambda_{\rbu}$, updates $\estwth_2$ more conservatively. 
-This slower response leads to delayed constraint satisfaction, which is reflected by the persistent positive value of $\lambda_{\rbu}$ in Fig.\ref{fig:ctrl:result:scope:beta}. 
+This slower response leads to delayed constraint satisfaction, which is reflected by the persistent positive value of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}. 
 However, this allows (C$_2$) to achieve smoother control input behavior, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.

### 2025-06-09 manuscript.tex
fix: correct typographical errors in manuscript.tex

@@
 However, this method cannot be realized, since we do not have the exact system dynamics, \ie $\rbM,\rbVm, \rbF$ and $ \rbG$.
-Additionally, the computational cost of the forward sensitivity method is high, as the number of DNN's weights are generally large.
+Additionally, the computational cost of the forward sensitivity method is high, as the number of DNN's weights is generally large.
 
@@
 
-\subsubsection{Satisfaction of Karsh-Kuhn-Tucker (KKT) conditions}
+\subsubsection{Satisfaction of Karush-Kuhn-Tucker (KKT) conditions}
 

### 2025-06-09 manuscript.tex
fix: update terminology and clarify equations in manuscript.tex

@@
 \begin{equation}
-    \rbM\ddq + \rbVm + \rbF + \rbG + \rbd
+    \rbM\ddq + \DHHO{\rbVm \dq}+ \rbF + \rbG + \rbd
     =
@@
 where $\q\in \R^n$ denotes the generalized coordinate, $\rbd$ represents the disturbance and $\rbu\in\R^n$ denotes the generalized control input. 
-The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
+The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, \DHHO{Coriolis/centrifugal matrix}, friction vector, and gravity vector, respectively.
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
@@
 \begin{prop} 
-    The Coriolis/centripetal matrix $\rbVm$ can always be selected, so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
+    The \DHHO{Coriolis/centrifugal matrix} $\rbVm$ can always be selected, so that the matrix $\ddtt{\rbM}-2\rbVm$ is skew-symmetric, \ie $\mv{x}^\top(\ddtt{\rbM}-2\rbVm)\mv{x}=0,\ \forall \mv{x}\in\R^n$.
     \label{prop:skew}
@@
 \begin{equation}
-    \fe := \ddtt{\mv e}-\mm\Lambda \mv e
+    \DHHO{\fe := \ddtt{\mv e}+\mm\Lambda \mv e}
     ,
@@
 \begin{equation}
+    \DHHO{ check:
    \rbM \ddtt\fe
@@
     -\rbd + \mysat(\rbu)
-    ,
+    ,}
     \label{eq:sys:filtered}
@@
     \begin{aligned}
+        \DHHO{ check}
         \ddtt{V}_1
@@
         +
-        \fe^\top (\mv f+\mysat(\rbu))
+        \fe^\top (\mv f+\mysat(\rbu))\\
         % \\
@@
         % \fe^\top (\mysat(\rbu)-\rbu^*)
-        .
     \end{aligned}
@@
     \hline
-    $I_1,I_2$  & Inertia & 0.069 kgm\textsuperscript{2} \\
+    $I_1,I_2$  & Inertia & 0.069 \DHHO{kg$\cdot$m\textsuperscript{2}} \\
     \hline
@@
 % ------------------------------------
-% Karsh-Kuhn-Tucker (KKT) conditions}
+% Karush-Kuhn-Tucker (KKT) conditions}
 % ------------------------------------
@@
 
-\subsubsection{Satisfaction of Karush-Kuhn-Tucker (KKT) conditions}
+\subsubsection{Satisfaction of \DHHO{Karush}-Kuhn-Tucker (KKT) conditions}
 

### 2025-06-09 presentation/presentation.tex
ppt update

@@
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-% Block options: Default, Alert, Example
+% Block options: block, alertblock, exampleblock
 % ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-\usepackage{calc}
-
-\usepackage{svg}
-\usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
-\usepackage{multimedia}
-\usepackage{animate}
+% \usepackage{calc}
+% \usepackage{svg}
+% \usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
+% \usepackage{multimedia}
+% \usepackage{animate}
 
@@
   }
-\date{\today}
-% \institute[short]{\inst{1} First \samelineand \inst{2} Second \samelineand \inst{3} Third}
-\newcommand{\samelineand}{\\}
+\date{2025-06-25}
 \institute{%
@@
 }
+\titlegraphic{assets/MIC_Lab_logo_white.png}
 % make institute font size smaller
@@
   \includegraphics[height=0.3cm]{assets/kaist_logo.png}
-  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
+  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
   \hspace{.6cm}%
@@
 % }
-
-\titlegraphic{logo_KAIST.png}
 
@@
 
+\begin{figure}
+  \label{fig:general_framework}
+  \includegraphics[width=0.65\textwidth]{figures/conv_nac.drawio.pdf}
+  \caption{General framework of neuro-adaptive control (NAC).}
+\end{figure}
+
 \end{frame}
@@
 
-\begin{frame}{\insertsubsectionhead}
+\begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}
 
@@
           \item \textbf{$\epsilon$-modification, and $\sigma$-modification}
+
+          \begin{itemize}
+            \item Cats 
+            \item Dogs 
+            \item Birds
+          \end{itemize}
+
+        \column{0.49\textwidth}
+          \begin{figure}
+            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+      \end{columns}
+  \end{enumerate}
+\end{frame}
+
+\subsection{Literature Review}
+
+\begin{frame}{\insertsubsectionhead}{Input Saturation}
+
+  The input saturation is generally handled using an auxiliary system.
+
+  \begin{enumerate}
+    \begin{columns}[T,onlytextwidth]
+        \column{0.49\textwidth}
+          \item \textbf{Auxiliary Systems}
+
+          \begin{itemize}
+            \item Cats 
+            \item Dogs 
+            \item Birds
+          \end{itemize}
+
+        \column{0.49\textwidth}
+          \begin{figure}
+            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+      \end{columns}
+
+      \begin{columns}[T,onlytextwidth]
+        \column{0.49\textwidth}
+          \item \textbf{Second?}
 
@@
 
-\subsection{Problem Formulation}
+\subsection{Architecture of the Proposed Method}
 
-\begin{frame}{\insertsubsectionhead}{Original Control Problem}
-  \textbf{Objectives}:
+\begin{frame}{\insertsubsectionhead}
+
+  \begin{columns}
+
+    \column{0.5\textwidth}
+
+      \textbf{Target 2-link Robotic Manipulator System}:
       \begin{itemize}
-    \item Minimize the tracking error by adapting the NN weights $\estwth$.
-    \item Guarantee the stability of the system and the NN weights $\estwth$.
+        \item Control input saturation function $\mysat(\cdot)$.
+        \item Desired trajectory $\mv{q}_d$ is given.
+      \end{itemize}
+        \begin{equation}
+          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
+          =
+          \mysat(\mv{\tau})
+        \end{equation}
+
+      \textbf{Control Input}:
+      \begin{itemize}
+        \item NN's output $\mv{\Phi}$ is used as the control input.
+        \item Consists of the estimated NN weights $\estwth$.
+      \end{itemize}
+      \begin{equation}
+        \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
+      \end{equation}
+
+      \textbf{Deep Neural Network (DNN)}:
+      \begin{itemize}
+        \item $k$ layers with $\estwth_i:=\myvec(\estwV_i)$.
+        \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
+        \begin{equation}
+          \mv{\Phi}(\mv{q}_n; \estwth)
+          :=
+          \begin{cases}
+              \estwV_i^\top \act_i(\estNN_{i-1}), 
+              &
+              i\in\{1,\dots ,k\},
+              \\
+              \estwV_0^\top {\q}_n,
+              &
+              i=0
+              ,
+          \end{cases}
+        \end{equation}
       \end{itemize}
 
+    \column{0.5\textwidth}
+
       \begin{figure}
-    \includegraphics[width=0.5\textwidth]{figures/problem.drawio.pdf}
-    % \includesvg{figures/problem.drawio}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+        \includegraphics[width=0.8\textwidth]{figures/Controller.drawio.pdf}
+        \caption{Architecture of the proposed method.}
       \end{figure}
+
+      \begin{figure}
+        \includegraphics[width=0.7\textwidth]{figures/DNN.drawio.pdf}
+        \caption{Architecture of the DNN.}
+      \end{figure}
+
+  \end{columns}
 
@@
       \textit{Notations}: 
-      $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{q}$: Joint position, $\estwth$: Estimated NN weights.
+        $\mv{q}\in\R^n$: Joint position, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\estwth$: Estimated NN weights.
+        $\estwth$: Estimated NN weights, $\mv{e}$: Tracking error, $\mv{\tau}_d$: Disturbance, $\mysat(\cdot)$: Saturation function.
       }
@@
 
-\begin{frame}{\insertsubsectionhead}{Equvalent Constrained Optimization Problem}
+\subsection{Problem Formulation}
+
+\begin{frame}{\insertsubsectionhead}{Optimization Problem}
+
+\begin{columns}
+
+  \column{0.45\textwidth}
+
+    \textbf{Optimization Problem Statement}:
+
+    \begin{itemize}
+      \item \textbf{Find} NN weights $\estwth$,
+      \item That \textbf{minimize} objective function $J(\cdot)$,
+        \begin{equation}
+          J(\mv{r}) := \frac{1}{2} \mv{r}^\top \mv{r}.
+        \end{equation}
+        \begin{itemize}
+          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is the filtered tracking error,
+        \end{itemize}
+      \item while satisfying the following \textbf{constraints}:
+        \begin{itemize}
+          \item Boundedness of the NN weights $\estwth$.
+          \item Saturation of the control input $\mv{\tau}$.
+        \end{itemize}
+    \end{itemize}
+
+  \column{0.5\textwidth}
+
+    \begin{block}{Considered Constraints}
+
+      \begin{itemize}
+        \item \textbf{Weight Boundedness}: 
+          \begin{equation}
+            c_{\theta_i}
+            :=
+            \norm{\estwth_i}^2 - \bar{\theta_i}^2 \le 0
+            , 
+            \forall i\in\{0,\ldots,k\}
+          \end{equation}
+
+        \item \textbf{Control Input Saturation}: 
+          \begin{itemize}
+            \item Input bound constraint:
+            \begin{equation}
+              c_{\overline{\tau}_i}
+              :=
+              \tau_i - \overline{\tau_i}
+              \le 
+              0
+              ,
+              c_{\underline{\tau}_i}
+              :=
+              \underline{\tau_i} - \tau_i
+              \le 
+              0
+            \end{equation}
+            \item Input norm constraint:
+            \begin{equation}
+              c_{\mv{\tau}}
+              :=
+              \norm{\mv{\tau}}^2 - \overline{\tau}^2
+              \le
+              0
+            \end{equation}
+        \end{itemize}
+      \end{itemize}
+
+    \end{block}
+
+  \end{columns}
+
+  \let\thefootnote\relax\footnote{
+    \textit{Notations}: 
+    $\Lambda\in\R_{>0}^{n\times n}$: filtering matrix
+  }
 
@@
 
-\begin{frame}{\insertsubsectionhead}{Inequality Constraint for Weight Boundedness}
+\begin{frame}{\insertsubsectionhead}{Optimization Problem}
+
+  \begin{columns}
+
+    \column{0.5\textwidth}
+
+      \centering
+      \begin{minipage}{0.9\textwidth}%
+        \begin{block}{Optimization Problem}%
+
+          \begin{equation}
+            \begin{matrix}
+              \min_{\estwth} J(\mv{r};\estwth)
+              \\\ \\
+              \text{s.t. } c_{j}(\estwth) 
+              \le 
+              0
+              ,
+              \forall j\in\mathcal{J}
+            \end{matrix}
+          \end{equation}
+
+        \end{block}
+      \end{minipage}
+
+    \column{0.5\textwidth}
+
+      \centering
+      \begin{minipage}{0.9\textwidth}%
+        \begin{block}{MinMax Problem}%
+
+          \begin{equation}
+            \begin{matrix}
+              \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{J}}} L(\cdot)
+              \\\ \\
+              \text{where }
+              L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{J}})
+              :=
+              J(\mv{r};\estwth)
+              +
+              \sum_{j\in\mathcal{J}} \lambda_j c_j(\estwth)
+            \end{matrix}
+          \end{equation}
+
+        \end{block}
+      \end{minipage}
+
+  \end{columns}
 
@@
 
-\begin{frame}{\insertsubsectionhead}{Steepest Descent Method}
+\begin{frame}{\insertsubsectionhead}{Steepest Descent/Ascent Method}
+
+  \begin{columns}
+
+    \column{0.5\textwidth}
+
+      \begin{minipage}{0.9\textwidth}%
+        For the min/max problem, the steepest descent/ascent method is used to derive the adaptation law.
+      \end{minipage}
+
+      \vspace{0.5cm}
+
+      \begin{minipage}{0.9\textwidth}%
+        \textbf{Steepest Descent Method for $\estwth$}:
+        \begin{equation}
+          \ddtt\estwth
+          =
+          -\alpha 
+          \pptfrac{L}{\estwth}
+        \end{equation}
+
+        \textbf{Steepest Ascent Method for $\lambda_j$}:
+        \begin{equation}
+          \ddtt\lambda_j = 
+        \end{equation}
+      \end{minipage}
+
+    \column{0.5\textwidth}
+
+      \centering
+        \begin{block}{Adaptation Law}%
+
+        \begin{subequations}
+            \begin{align}
+                    \ddt {{\estwth}}
+                    &
+                    =
+                    -\alpha 
+                    \ppfrac{L}{{\estwth}}
+                    =-\alpha 
+                    \left(
+                        \ppfrac{J}{{\estwth}}
+                        +
+                        \sum_{j\in\mathcal{I}}
+                        \lambda_j 
+                        \ppfrac{c_j}{\estwth}
+                    \right),
+                    \\
+                    \ddt\lambda_j
+                    & 
+                    = 
+                    \beta_j
+                    \ppfrac{L}{\lambda_j} 
+                    = 
+                    \beta_j c_j ,
+                    \quad\quad\quad\quad      \      
+                    \forall j\in\mathcal I,
+                    \\
+                    \lambda_j 
+                    & 
+                    = 
+                    \max(\lambda_j,0) ,
+            \end{align}
+        \end{subequations}
+
+        \end{block}
+
+  \end{columns}
 
 \end{frame}
+
 \subsection{Stability Analysis}
@@
 \begin{frame}{\insertsubsectionhead}{Lyapunov Stability Analysis}
+
+  \begin{block}{Theorem 1}
+    For the dynamical system described in (1), the neuro-adaptive controller in (2) with the weight adaptation laws in (12) ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2.
+This holds under the weight norm constraint (5).
+  \end{block}
+
+  \begin{exampleblock}{Assumption 1}
+    The constraint functions $c_j(\estwth),\forall j\in\mathcal{I}$, are convex in the $\tau$-space and satisfy $c_j(\estwth)\le0$ and $c_j(\idealwth)\le0$.
+  \end{exampleblock}
+
+  \begin{exampleblock}{Assumption 2}
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap. 12 Def. 12.1]{Nocedal:2006aa}.
+  \end{exampleblock}
+
+  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{}.
 
@@
   % \animategraphics[loop,width=4cm]{gifs/overall-}
-  \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}
+  % \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}
 
@@
 
-  Flux theme comes with three pre-defined block style collections.\\
-  % Native style (default) available as \verb+\setblockstyle{native}+\\[0.5cm]
+  \textbf{Summary of Contributions}
+  \begin{itemize}
+    \item Proposed a novel constrained optimization-based neuro-adaptive control (CONAC) method.
+    \item Adaptation laws are derived using constrained optimization method.
+    \item The proposed method guarantees the stability of the system and the boundedness of the NN weights.
+    \item Feasibility of the proposed method is validated through numerical simulations and real-time experiments.
+  \end{itemize}
 
-  \centering
-	\begin{minipage}[b]{0.5\textwidth}
+  \textbf{Future Work}
+  \begin{itemize}
+    \item Extend the proposed method to state constraints.
+    \item Enhance the robustness and flexibility of the proposed method for various systems.
+  \end{itemize}
 
-	  \begin{block}{Default}
-        Block content.
-      \end{block}
-
-      \begin{alertblock}{Alert}
-        Block content.
-      \end{alertblock}
-
-      \begin{exampleblock}{Example}
-        Block content.
-      \end{exampleblock}
-
-	\end{minipage}
 \end{frame}

### 2025-06-10 manuscript.tex
touch for dhHONG

@@
 \section{Real-Time Implementation and Validation}\label{sec:sim}
-
+\DHHO{이게 은근히 신경쓰이는데, VI.REAL-TIME IMPLEMENTATION AND VALIDATION이 적힌 부분이 최하단부 좌측에 있어서 실험 구현파트가 시작된지도 몰랐음. 우측 상단부에 오도록 하는게 좋을듯 싶음.}
 \subsection{Validation Setup}
@@
 \end{table}
-
+\DHHO{1.
+여기까지 읽었을 때, controller가 4개나 되다보니 'setup'이 너무 길어짐.
+가능할지는 모르겠지만, 도 subsection을 3개로 나눠서, A1.System or Harware Setup, A2.
+Reference Trajectory or Episode setup, A3.
+Controllers setup로 나누는게 좋을듯 싶음.
+Validation Setup이 너무 길다보니 한번에 읽기가 너무 힘듬.
+2.
+TABLEII가 사실 controller setup을 요약해주는 부분인데, 아예 페이지를 넘어가 버려서 한눈에 보기 어려움.
+개인적으로 TALBEII를 8page 상단 우측으로 옮겼으면 함.
+그러면 TABLEIII가 균형이 안 맞을거라는 의견이 있을 수도 있긴 한데, 오히려 TALBE.III 구조를 좀 바꾸면 좀더 보기 편할듯.
+Fig.5처럼 아예 좌우로 늘리고, 1열에 C1,C2,C3,C4를 나열하고, 2열 1행 Episode1, 3열 1행 Episode2 하면 오히려 fig.5와 매칭이 되어서 보기가 더 쉬울듯.}
 \subsection{Validation Results}

### 2025-06-10 presentation/presentation.tex
ppt final update for security check

@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\usepackage{multirow}
+
 % \usepackage{calc}
@@
 
-\logo{
-  \vspace{-.7cm}%
-  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
-  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
-  \hspace{.6cm}%
-  }
+% \logo{
+%   \vspace{-.7cm}%
+%   \includegraphics[height=0.3cm]{assets/kaist_logo.png}
+%   \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
+%   \hspace{.6cm}%
+%   }
 
@@
 
-  \begin{figure}
-    \includegraphics[width=0.25\textwidth]{figures/KAIST-hi.png}
-  \end{figure}
-
 \end{frame}
 
-\subsection{Literature Review}
+% \subsection{Literature Review}
 
-\begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}
+% \begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}
 
-  In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.
+%   In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.
 
-  \begin{enumerate}
-    \begin{columns}[T,onlytextwidth]
-        \column{0.49\textwidth}
-          \item \textbf{Projection Operator}
+%   \begin{enumerate}
+%     \begin{columns}[T,onlytextwidth]
+%         \column{0.49\textwidth}
+%           \item \textbf{Projection Operator}
 
-          \begin{itemize}
-            \item Cats 
-            \item Dogs 
-            \item Birds
-          \end{itemize}
+%           \begin{itemize}
+%             \item Cats 
+%             \item Dogs 
+%             \item Birds
+%           \end{itemize}
 
-        \column{0.49\textwidth}
-          \begin{figure}
-            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
-      \end{columns}
+%         \column{0.49\textwidth}
+%           \begin{figure}
+%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+%           \end{figure}
+%       \end{columns}
 
-      \begin{columns}[T,onlytextwidth]
-        \column{0.49\textwidth}
-          \item \textbf{$\epsilon$-modification, and $\sigma$-modification}
+%       \begin{columns}[T,onlytextwidth]
+%         \column{0.49\textwidth}
+%           \item \textbf{$\epsilon$-modification, and $\sigma$-modification}
 
-          \begin{itemize}
-            \item Cats 
-            \item Dogs 
-            \item Birds
-          \end{itemize}
+%           \begin{itemize}
+%             \item Cats 
+%             \item Dogs 
+%             \item Birds
+%           \end{itemize}
 
-        \column{0.49\textwidth}
-          \begin{figure}
-            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
-      \end{columns}
-  \end{enumerate}
-\end{frame}
+%         \column{0.49\textwidth}
+%           \begin{figure}
+%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+%           \end{figure}
+%       \end{columns}
+%   \end{enumerate}
+% \end{frame}
 
-\subsection{Literature Review}
+% \begin{frame}{\insertsubsectionhead}{Input Saturation}
 
-\begin{frame}{\insertsubsectionhead}{Input Saturation}
+%   The input saturation is generally handled using an auxiliary system.
 
-  The input saturation is generally handled using an auxiliary system.
+%   \begin{enumerate}
+%     \begin{columns}[T,onlytextwidth]
+%         \column{0.49\textwidth}
+%           \item \textbf{Auxiliary Systems}
 
-  \begin{enumerate}
-    \begin{columns}[T,onlytextwidth]
-        \column{0.49\textwidth}
-          \item \textbf{Auxiliary Systems}
+%           \begin{itemize}
+%             \item Cats 
+%             \item Dogs 
+%             \item Birds
+%           \end{itemize}
 
-          \begin{itemize}
-            \item Cats 
-            \item Dogs 
-            \item Birds
-          \end{itemize}
+%         \column{0.49\textwidth}
+%           \begin{figure}
+%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+%           \end{figure}
+%       \end{columns}
 
-        \column{0.49\textwidth}
-          \begin{figure}
-            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
-      \end{columns}
+%       \begin{columns}[T,onlytextwidth]
+%         \column{0.49\textwidth}
+%           \item \textbf{Second?}
 
-      \begin{columns}[T,onlytextwidth]
-        \column{0.49\textwidth}
-          \item \textbf{Second?}
+%           \begin{itemize}
+%             \item Cats 
+%             \item Dogs 
+%             \item Birds
+%           \end{itemize}
 
-          \begin{itemize}
-            \item Cats 
-            \item Dogs 
-            \item Birds
-          \end{itemize}
-
-        \column{0.49\textwidth}
-          \begin{figure}
-            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
-      \end{columns}
-  \end{enumerate}
-\end{frame}
+%         \column{0.49\textwidth}
+%           \begin{figure}
+%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+%           \end{figure}
+%       \end{columns}
+%   \end{enumerate}
+% \end{frame}
 
@@
 
-      \textbf{Target 2-link Robotic Manipulator System}:
+      \textbf{Target Two-link Robotic Manipulator System}:
       \begin{itemize}
@@
       \end{itemize}
-        \begin{equation}
+        \begin{equation}\label{eq:sys}
           \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
@@
       \end{itemize}
-      \begin{equation}
+      \begin{equation}\label{eq:input}
         \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
@@
         \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
-        \begin{equation}
+        \begin{equation}\label{eq:NN}
           \mv{\Phi}(\mv{q}_n; \estwth)
@@
       \item That \textbf{minimize} objective function $J(\cdot)$,
-        \begin{equation}
-          J(\mv{r}) := \frac{1}{2} \mv{r}^\top \mv{r}.
+        \begin{equation}\label{eq:obj}
+          J(\mv{r};\estwth)
+          := 
+          \frac{1}{2} \mv{r}^\top \mv{r}.
         \end{equation}
@@
       \begin{itemize}
-        \item \textbf{Weight Boundedness}: 
-          \begin{equation}
-            c_{\theta_i}
+        \item \textbf{Weight Boundedness for Each Layer}: 
+          \begin{equation}\label{eq:cstr:weight}
+            c_{\theta_i}(\estwth)
             :=
-            \norm{\estwth_i}^2 - \bar{\theta_i}^2 \le 0
+            \norm{\estwth_i}^2 - \overline{\theta_i}^2 \le 0
             , 
@@
 
-        \item \textbf{Control Input Saturation}: 
+        \item \textbf{Convex control Input Saturation}: 
           \begin{itemize}
             \item Input bound constraint:
-            \begin{equation}
-              c_{\overline{\tau}_i}
+            \begin{equation}\label{eq:cstr:input_bound}
+              c_{\overline{\tau}_i}(\estwth)
               :=
@@
               ,
-              c_{\underline{\tau}_i}
+              \quad
+              c_{\underline{\tau}_i}(\estwth)
               :=
@@
             \item Input norm constraint:
-            \begin{equation}
-              c_{\mv{\tau}}
+            \begin{equation}\label{eq:cstr:input_norm}
+              c_{\mv{\tau}}(\estwth)
               :=
@@
 
-  \begin{columns}
+  \textbf{Original Optimization Problem}
 
-    \column{0.5\textwidth}
+  \begin{itemize}
+    \item Constrained optimization problem to minimize the tracking error.
+    \item Inequality constraints $c_j(\estwth) \le 0$ for $j\in\mathcal{I}$.
+  \end{itemize}
 
-      \centering
-      \begin{minipage}{0.9\textwidth}%
-        \begin{block}{Optimization Problem}%
-
-          \begin{equation}
+    \begin{equation}\label{eq:opt_problem}
       \begin{matrix}
@@
         ,
-              \forall j\in\mathcal{J}
+        \forall j\in\mathcal{I}
       \end{matrix}
@@
 
-        \end{block}
-      \end{minipage}
+  \textbf{Define Lagrangian Function}
 
-    \column{0.5\textwidth}
-
-      \centering
-      \begin{minipage}{0.9\textwidth}%
-        \begin{block}{MinMax Problem}%
-
-          \begin{equation}
-            \begin{matrix}
-              \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{J}}} L(\cdot)
-              \\\ \\
-              \text{where }
-              L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{J}})
+  \begin{equation}\label{eq:lagrangian}
+      L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
       :=
@@
       +
-              \sum_{j\in\mathcal{J}} \lambda_j c_j(\estwth)
-            \end{matrix}
+      \sum_{j\in\mathcal{I}} \lambda_j c_j(\estwth)
   \end{equation}
 
-        \end{block}
-      \end{minipage}
+  \textbf{Dual Problem}
+  \begin{itemize}
+    \item The dual problem is to minimize the Lagrangian function with respect to the NN weights $\estwth$, while maximizing the Lagrange multipliers $\lambda_j$.
+    \item The Lagrange multipliers $\lambda_j$ are non-negative, \ie $\lambda_j \ge 0$.
+  \end{itemize}
 
-  \end{columns}
+  \begin{equation}\label{eq:dual_problem}
+    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
+    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
+  \end{equation}
 
@@
 
-\begin{frame}{\insertsubsectionhead}{Steepest Descent/Ascent Method}
+\begin{frame}{\insertsubsectionhead}{Gradient Descent/Ascent Method}
 
-  \begin{columns}
-
-    \column{0.5\textwidth}
-
-      \begin{minipage}{0.9\textwidth}%
-        For the min/max problem, the steepest descent/ascent method is used to derive the adaptation law.
-      \end{minipage}
-
-      \vspace{0.5cm}
-
-      \begin{minipage}{0.9\textwidth}%
-        \textbf{Steepest Descent Method for $\estwth$}:
+  For the dual problem, 
   \begin{equation}
-          \ddtt\estwth
-          =
-          -\alpha 
-          \pptfrac{L}{\estwth}
+    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
+    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
+    ,
   \end{equation}
-
-        \textbf{Steepest Ascent Method for $\lambda_j$}:
-        \begin{equation}
-          \ddtt\lambda_j = 
-        \end{equation}
-      \end{minipage}
-
-    \column{0.5\textwidth}
+  the first-order gradient descent/ascent method is used to derive the adaptation law.
 
   \centering
+  \begin{minipage}{0.6\textwidth}%
+
     \begin{block}{Adaptation Law}%
 
-        \begin{subequations}
-            \begin{align}
+    \textbf{Gradient Descent Method for $\estwth$}:
+    \begin{equation}\label{eq:adaptation_law:1}
       \ddt {{\estwth}}
-                    &
       =
@@
       \right),
-                    \\
+    \end{equation}
+
+    \textbf{Gradient Ascent Method for $\lambda_j, \forall j\in\mathcal I$}:
+    \begin{equation}\label{eq:adaptation_law:2}
       \ddt\lambda_j
-                    & 
       = 
@@
       \beta_j c_j ,
-                    \quad\quad\quad\quad      \      
-                    \forall j\in\mathcal I,
-                    \\
+    \end{equation}
+
+    For non-negativity of the Lagrange multipliers,
+    \begin{equation}\label{eq:adaptation_law:3}
       \lambda_j
-                    & 
-                    = 
-                    \max(\lambda_j,0) ,
-            \end{align}
-        \end{subequations}
+      \leftarrow
+      \max(\lambda_j,0)
+      .
+    \end{equation}
+
+    % \begin{subequations}
+    %     \begin{align}
+    %       \ddt {{\estwth}}
+    %       &
+    %       =
+    %       -\alpha 
+    %       \ppfrac{L}{{\estwth}}
+    %       =-\alpha 
+    %       \left(
+    %           \ppfrac{J}{{\estwth}}
+    %           +
+    %           \sum_{j\in\mathcal{I}}
+    %           \lambda_j 
+    %           \ppfrac{c_j}{\estwth}
+    %       \right),
+    %       \\
+    %       \ddt\lambda_j
+    %       & 
+    %       = 
+    %       \beta_j
+    %       \ppfrac{L}{\lambda_j} 
+    %       = 
+    %       \beta_j c_j ,
+    %       \quad\quad\quad\quad      \      
+    %       \forall j\in\mathcal I,
+    %       \\
+    %       \lambda_j
+    %       &
+    %       \leftarrow
+    %       \max(\lambda_j,0)
+    %     \end{align}
+    % \end{subequations}
 
     \end{block}
-
-  \end{columns}
-
+  \end{minipage}
 \end{frame}
@@
 
-  \begin{block}{Theorem 1}
-    For the dynamical system described in (1), the neuro-adaptive controller in (2) with the weight adaptation laws in (12) ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2.
-This holds under the weight norm constraint (5).
+  \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
+    For the dynamical system described in \eqref{eq:sys}, the neuro-adaptive controller in \eqref{eq:input} with the weight adaptation laws in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2.
+This holds under the weight norm constraint \eqref{eq:cstr:weight}.
   \end{block}
 
-  \begin{exampleblock}{Assumption 1}
+  \begin{exampleblock}{Assumption 1 (Convex Input Constraint)}
     The constraint functions $c_j(\estwth),\forall j\in\mathcal{I}$, are convex in the $\tau$-space and satisfy $c_j(\estwth)\le0$ and $c_j(\idealwth)\le0$.
@@
 
-  \begin{exampleblock}{Assumption 2}
+  \begin{exampleblock}{Assumption 2, Linear Independence Constraint Qualification (LICQ)}
     The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap. 12 Def. 12.1]{Nocedal:2006aa}.
@@
 
-  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{}.
+  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.
 
@@
 
-\section{Numerical Validation}
+\section{Experimental Validation}
 
 \subsection{Simulation Setup}
-\begin{frame}{\insertsubsectionhead}{2-Link Robotic Manipulator}
+
+\begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}
+
+    \begin{columns}
+
+      \column{.45\textwidth}
+
+        \textbf{Target System}:
+
+        \begin{equation*}
+          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
+          =
+          \mv{\tau}
+        \end{equation*}
 
@@
           \centering
-    \includegraphics[width=0.5\textwidth]{figures/exp_set.drawio.png}
-    \caption{2-Link Robotic Manipulator}
+          \includegraphics[width=.99\textwidth]{figures/RobotModel.drawio.png}
+          \caption{Two-link robotic manipulator model.}
         \end{figure}
 
-  \let\thefootnote\relax\footnote{
-    \textit{Notations}: 
-      $\mv{q}$: Joint position, $\mv{\dot{q}}$: Joint velocity, $\mv{\tau}$: Control input, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector.
-  }
+      \column{.55\textwidth}
+
+        \textbf{Desired Trajectory}:
+
+        \begin{equation}
+          \qd
+          =
+          \begin{bmatrix}
+              {q_d}_1\\
+              {q_d}_2
+          \end{bmatrix}
+          = 
+          \begin{bmatrix}
+              +\cos(
+                  \tfrac{\pi}{2}t
+              ) + 1 \\
+              -\cos(
+                  \tfrac{\pi}{2}t
+              ) - 1 
+          \end{bmatrix}
+          .
+      \end{equation}
+
+      \textbf{System Model Parameters}:
+
+      \begin{table}
+        \renewcommand{\arraystretch}{1.3}
+        \caption{System model parameters.}
+        \centering
+        \begin{tabular}{c m{5em} c c c }
+        \hline
+        \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
+        \hline
+        \hline 
+        $m_p$ & Mass & 23.902 kg & 3.88 kg \\
+        \hline
+        $l_p$  & Length & 0.45 m & 0.45 m \\
+        \hline
+        ${l_c}_p$ & COM & 0.091 m & 0.048 m \\
+        \hline
+        $b_p$   & Viscous coef. &  2.288 Nms & 0.172 Nms \\
+        \hline
+        ${f_c}_p$  & Friction coef. & 7.17 Nm & 1.734 Nm \\
+        \hline
+        \end{tabular}
+        \label{table: system parameters}
+      \end{table}
+
+    \end{columns}
+
+\end{frame}
+
+\begin{frame}{\insertsubsectionhead}{Controllers for Comparative Study}
+
+    \begin{itemize}
+      \item NAC-CO denotes the proposed controller based on constrained optimization.
+      \item For NAC-L2 and NAC-eMod, the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\tilde{\mv{z}}}\estwth$ ensures the boundedness of the NN weights
+    \end{itemize}
+
+    \begin{table}
+      \renewcommand{\arraystretch}{1.5}
+      % \caption{Controller Properties.}
+      \centering
+      \begin{tabular}{c m{20em} c c c }
+      \hline
+      \textbf{Name} & \textbf{Description} & \textbf{Adaptation Law} \\
+      \hline
+      \hline 
+        \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
+      $
+        \ddt\estwth = -\alpha \left(\ppfrac{L}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
+      $ 
+      \\
+        (proposed) & ($\beta_j$ determines $\lambda_j$ adaptation speed) &
+      $
+        \ddt\lambda_j = \beta_j c_j, \lambda_j \leftarrow \max(\lambda_j,0)
+      $
+      \\
+      \hline
+      \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization & \multirow{2}{*}
+      {$
+        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\lambda\estwth\right)
+      $}
+      \\
+        & ($\lambda\in\R_{>0}$ stabilizes $\estwth$ towards origin) &
+      \\
+      \hline
+      \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
+      {$
+        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\rho\norm{\tilde{\mv{z}}}\estwth\right)
+      $}
+      \\
+      & ($\rho$ stabilizes proportionally to the error $\tilde{\mv{z}}$) &
+      \\
+      \hline
+      \end{tabular}
+      \label{table:sys:param}
+    \end{table}
+
+    \centering
+    \begin{minipage}{0.75\textwidth}
+      \begin{block}{Simulation Objective}
+        By varying the parameters, \ie $\beta_j$, $\lambda$, and $\rho$, the parameter dependencies will be investigated.
+      \end{block}
+    \end{minipage}
 
@@
 
-\begin{frame}{Representative Simulation Results}
+% \begin{frame}{Representative Simulation Results}
 
@@
 
-\end{frame}
+% \end{frame}
 
-\begin{frame}{Box-and-Whisker Plots}
+\begin{frame}{\insertsubsectionhead}{Box-and-Whisker Plots}
 
   \begin{columns}
+    \column{0.55\textwidth}
+
+      \textbf{Parameter Dependencies Investigation}:
+
+      \begin{itemize}
+        \item The parameters ranged from 0.001 to 1 across 10 samples.
+        \item NAC-CO (proposed) shows the best performance and low variance.
+        \item NAC-L2 shows the worst performance with high variance.
+      \end{itemize}
+
     \column{0.5\textwidth}
+
       \begin{figure}
-        \includegraphics[width=\textwidth]{figures/BoxWhisker.drawio.png}
+        \includegraphics[width=.99\textwidth]{figures/BoxWhisker.drawio.png}
         \caption{Parameter dependencies of the proposed method.}
@@
 
-    \column{0.5\textwidth}
-      \begin{table}
-        \caption{Largest cities in the world (source: Wikipedia)}
-        \begin{tabular}{@{} lr @{}}
-          \toprule
-          City & Population\\
-          \midrule
-          Mexico City & 20,116,842\\
-          Shanghai & 19,210,000\\
-          Peking & 15,796,450\\
-          Istanbul & 14,160,467\\
-          \bottomrule
+  \end{columns}
+
+    \begin{table}[!t]
+      \renewcommand{\arraystretch}{1.1}
+      % \caption{Quantitative comparison of square root of tracking ISE.}
+      \centering
+      \begin{tabular}{c c c c }
+      \hline
+      & \textbf{NAC-L2}\!&\!\textbf{NAC-eMod}\!&\!\textbf{NAC-CO} (proposed) 
+      \\
+      \hline
+      \hline 
+        Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
+      \hline
+        Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
+      \hline
+        Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
+      \hline
       \end{tabular}
+      \label{table: error norm}
     \end{table}
 
-  \end{columns}
+    \let\thefootnote\relax\footnote{
+      Squared root of the tracking error ISE (Integral of Squared Error) is used, \ie $\sqrt{\int_0^T \norm{\mv{r}}^2\,\der t}$, where $T$ denotes a simulation termination time.
+    }
 
@@
 
-\begin{frame}{Parameter Dependencies}
+\begin{frame}{\insertsubsectionhead}{Weight Norms}
 
@@
     \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig8.eps}
+        \caption{Weight norms of NAC-CO}
+      \end{figure}
+
+    \column{0.33\textwidth}
+
       \begin{figure}      
@@
 
-    \column{0.33\textwidth}
-
-      \begin{figure}
-        \includegraphics[width=0.99\textwidth]{figures/ECC/fig8.eps}
-        \caption{Weight norms of NAC-CO}
-      \end{figure}
-
   \end{columns}
 
-  The weight norms of the proposed method (NAC-CO) are bounded, while ...
+  \begin{itemize}
+    \item NAC-CO (proposed) showed the weight norms are bounded under pre-defined constraint $\overline{\theta}=20$.
+    \item NAC-L2 and NAC-eMod showed the bounded weight norms, but they depended on the parameters $\lambda$ and $\rho$, respectively.
+    \item As the parameters $\lambda$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
+    \item In addition, NAC-CO tracked the desired trajectory with a smaller weight norm than NAC-L2 and NAC-eMod.
+  \end{itemize}
 
@@
 
-\begin{frame}{Parameter Dependencies}
+\begin{frame}{\insertsubsectionhead}{Tracking Performance}
 
@@
     \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig5.eps}
+        \caption{Tracking error of NAC-CO}
+      \end{figure}
+
+    \column{0.33\textwidth}
+
       \begin{figure}      
@@
 
-    \column{0.33\textwidth}
-
-      \begin{figure}
-        \includegraphics[width=0.99\textwidth]{figures/ECC/fig5.eps}
-        \caption{Tracking error of NAC-CO}
-      \end{figure}
-
   \end{columns}
 
-  The Tracking error ...
+  \begin{itemize}
+    \item NAC-CO (proposed) outperformed NAC-L2 and NAC-eMod in terms of tracking performance.
+    \item As the weights are biased towards the origin, the tracking performance of NAC-L2 and NAC-eMod deteriorated.
+  \end{itemize}
 
 \end{frame}
+
+% \subsection{Simulation Setup}
+
+% \begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}
+
+%     \begin{columns}
+
+%       \column{.55\textwidth}
+%         \begin{figure}
+%           \centering
+%           \includegraphics[width=.85\textwidth]{figures/RobotModel.drawio.png}
+%           \caption{Two-Link Robotic Manipulator}
+%         \end{figure}
+
+%       \column{.5\textwidth}
+
+%         \begin{table}[t]
+%             \renewcommand{\arraystretch}{1.3}
+%             \caption{Two-link robotic manipulator's parameters.}
+%             \centering
+%             \begin{tabular}{c m{9.5em} c c c }
+%             % \begin{tabular}{c c c c c}
+%             \hline
+%             \textbf{Symbol} & \textbf{Description} & \textbf{Value} \\
+%             \hline
+%             \hline 
+%             $m_1,m_2$ & Mass & 2.465 kg \\
+%             \hline
+%             $l_1,l_2$  & Length & 0.2 m \\  
+%             \hline
+%             ${l_c}_1,{l_c}_2$ & Center of mass & 0.139 m \\
+%             \hline
+%             $I_1,I_2$  & Inertia & 0.069 kgm\textsuperscript{2} \\
+%             \hline
+%             \end{tabular}
+%         \end{table}
+
+%     \end{columns}
+
+% \end{frame}
 
@@
 
-  \bibliography{../template/refs}
-  \bibliographystyle{ieeetr}
+  \bibliography{localRefs}
+  \bibliographystyle{IEEEtran}
 

### 2025-06-10 manuscript.tex
minor change

--- 2025-06-09 manuscript.tex
@@
 \begin{equation}
-    \rbM\ddq + \rbVm + \rbF + \rbG + \rbd
+    \rbM\ddq +\rbVm \dq+ \rbF + \rbG + \rbd
     =
@@
 \begin{equation}
-    \fe := \ddtt{\mv e}-\mm\Lambda \mv e
+    \fe := \ddtt{\mv e}+\mm\Lambda \mv e
     ,
@@
     \hline 
-    $m_1,m_2$ & Mass & 2.465 kg \\
-    \hline
-    $l_1,l_2$  & Length & 0.2 m \\  
-    \hline
-    ${l_c}_1,{l_c}_2$ & Center of mass & 0.139 m \\
-    \hline
-    $I_1,I_2$  & Inertia & 0.069 kgm\textsuperscript{2} \\
+    $m_1,m_2$ & Mass & 2.465 $\mathrm{kg}$ \\
+    \hline
+    $l_1,l_2$  & Length & 0.2 $\mathrm{m}$ \\  
+    \hline
+    ${l_c}_1,{l_c}_2$ & Center of mass & 0.139 $\mathrm{m}$ \\
+    \hline
+    $I_1,I_2$  & Inertia & 0.069 $\mathrm{kg\cdot m^{2}}$ \\
     \hline
@@
 Moreover, once the control saturation was released—typically due to a change in the reference trajectory—these large violations resulted in oscillatory behavior, as the controller's weights had been adapted to produce excessively high control inputs.
-\KHCH{
-        여기부터 문단 끝날때까지의 표현이 명료하지 않습니다. C3의 tracking performance가 좋은 것은 지표상으로 명확히 맞는 말이기 때문에 마치 tracking performance가 실제로 좋은 것은 아니다라는 뉘앙스의 논리 전개가 적절치 않습니다.
-    Tracking performanc는 더 좋지만 과도한 control input을 사용하고, saturation이 지난 이후에는 진동 문제가 있다는 것만 명료하게 표현해주세요.
-}
 
@@
 
-\KHCH{
-    여기에 각 제어기의 constraint를 표현해주는게 좋겠습니다. FIg6a만 보고 아래의 설명을 이해하기에는 리뷰어들에게 어려움이 있을 겁니다.
-}
-\MSRY{
-    아래의 설명을 보완하여 각 제어기의 constraint를 표현해주었습니다.
-}
 Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was unable to fully utilize the actuator's capability.

### 2025-06-12 manuscript.tex
complie test on windows; minor change

@@
 
-\begin{IEEEkeywords}
+\begin{IEEEkeywords}DV26H-64YTR-C9WFH-7A33V
     Neuro-adaptive control, constrained optimization, deep neural network, input constraint.
@@
     \mysat(\rbu)
+    ,
     \label{eq:sys1}
@@
         % \fe^\top (\mysat(\rbu)-\rbu^*)
+        .
     \end{aligned}
@@
     \in\R^{n \times \Xi}
+    ,
     \label{eq:gradient:phi}
@@
     % \le 0
+    ,
     \label{eq:cstr:weight:ball}
@@
     \pptfrac{\estNN}{\estwth_i}
+    ,
 \end{equation}
@@
             \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
-        }_{=:{\gamma}_1\in\R_{>0}}
+        }_{=:{\gamma}_1\in\R_{\ge0}}
         \norm{\fe}
@@
             \estwth_k^\top \pptfrac{c_j}{\estwth_k}
-        }_{=:{\gamma}_2<0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        }_{=:{\gamma}_2\in\R_{\le0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
         \\
@@
 The satisfaction of the constraints can be verified through the boundedness of $\estwth_k$.
-For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large, due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\estwth_k}^{1}$ shrinks to a point.
+For the weight norm constraint $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases sufficiently large, due to the constraint violation, $\estwth_k$ approaches to the origin, as the invariant set $\Theta_{\theta_k}^{1}$ shrinks to a point.
 The remaining control input constraints can be validated implicitly through the term ${\gamma}_2$ in \eqref{eq:lya2:dot}.
@@
 The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
-The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and are illustrated in Fig.~\ref{fig:robot:model}. 
+The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and is illustrated in Fig.~\ref{fig:robot:model}. 
 The measured and/or estimated system parameters are provided in Table~\ref{table:system:params}.
@@
 % ------------------------------------
-The desired trajectory $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, which satisfy the initial and final joint angles $\mv{x}_1$ and $\mv{x}_2$, as well as zero initial and final joint velocities.
+The desired trajectory $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, which satisfy the initial and final joint angles $\mv{x}_1\in\R^2$ and $\mv{x}_2\in\R^2$, as well as zero initial and final joint velocities.
 Here, $t_f$ denotes the duration of each segment.

### 2025-06-12 manuscript.tex
minor change

@@
 \begin{itemize}
+    \item $\R$ denotes the set of real numbers and $\R^n$ denotes the $n$-dimensional Euclidean space.
+    \item $(\cdot)^\top$ denotes the transpose of a vector or matrix.
     \item $\otimes$ denotes the Kronecker product \cite[Chap. 7 Def. 7.1.2]{Bernstein:2009aa}.
@@
 The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
+
 In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
@@
 where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
+The DNN $\NN({\q}_n;\wth)$ has $k+1$ layers, where the input layer is indexed by $i=0$, and the output layer is indexed by $i=k$.
+For instance, in Fig.~\ref{fig:DNN}, the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3$, and $l_3=2$ is illustrated.
+Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$, \ie $l_{k+1}=n$. 
+The weights $\wV_i,\forall i\in\{0,\cdots,k\}$ are initialized randomly using uniform distribution at the beginning of the control process.
+
 The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
-Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\rbu$, \ie $l_{k+1}=n$.
-
-One of the widely used activation functions for large DNNs is from the ReLU family \cite{Maas:2013aa}, which effectively avoids the gradient vanishing problem during error backpropagation. 
+In selecting the nonlinear function $\sigma(\cdot)$, the ReLU function \cite{Maas:2013aa} is one of the widely used functions for large DNNs, since it effectively avoids the gradient vanishing problem during error backpropagation.
 However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
@@
     \subfloat[Two-link robotic manipulator.]{
-        \includegraphics[width=0.65\linewidth]{src/figures/RobotModel.drawio.pdf}
+        \includegraphics[width=0.7\linewidth]{src/figures/RobotModel.drawio.pdf}
         \label{fig:robot:model}
@@
     \subfloat[Control input saturation function.]{
-        \includegraphics[width=0.55\linewidth]{src/figures/saturation.drawio.pdf}
+        \includegraphics[width=0.6\linewidth]{src/figures/saturation.drawio.pdf}
         \label{fig:robot:sat}
@@
 % Reference Trajectory
-% ------------------------------------
-The desired trajectory $\qd=\left({q_d}_1,{q_d}_2\right)^\top $ was generated using quintic (5$\textsuperscript{th}$-order) polynomial functions $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$, which satisfy the initial and final joint angles $\mv{x}_1\in\R^2$ and $\mv{x}_2\in\R^2$, as well as zero initial and final joint velocities.
-Here, $t_f$ denotes the duration of each segment.
-The desired (reference) trajectory is defined as follows:
+The desired (reference) trajectory is designed with $4$ segments as follows:
 \begin{equation}
@@
 \end{equation}
-where 
+where $\mathcal{P}^5(t;\mv{x}_1,\mv{x}_2,t_f)$ denotes a quintic (5$\textsuperscript{th}$-order) polynomial trajectory that moves the system from $\mv{x}_1\in\R^2$ to $\mv{x}_2\in\R^2$ in $t_f$ seconds, with zero initial and final velocities.
+The initial and final joint angles of the segments are defined as follows:
 $
@@
     \mv{q}_d^{(2)}:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top
-$, 
-and $t_f=3$ s, and the reference trajectory is illustrated in Fig.~\ref{fig:robot:model}.
+$, as illustrated in Fig.~\ref{fig:robot:model}.
+The time duration of the segment is defined as $t_f=3$ s.
 To demonstrate the learning capability of the DNN, the desired trajectory was applied twice. 
 The first and second repetitions of the reference trajectory are referred to as Episode $1$ and Episode $2$, respectively.
-
-However, due to the random initialization of the DNN weights, large reference trajectories should be avoided to reduce the impact of the controller's initial poor performance.
-Therefore, prior to applying the reference trajectory, the manipulator was first positioned at a stable equilibrium point, denoted as ${\qd}^{\rm{origin}} = \left(-\tfrac{1}{2}\pi, 0\right)^\top$.
-Subsequently, a trajectory $\mathcal{P}^5(t; {\qd}^{\rm{origin}}, {\qd}_0, 3)$ was used to move the manipulator from ${\qd}^{\rm{origin}}$ to ${\qd}_0$ over a duration of 3 seconds, defining the start and end positions of each episode.
-Once the manipulator reached ${\qd}_0$, a constant reference trajectory $\qd = {\qd}_0$ was maintained for 8 seconds to allow the system to settle and eliminate the influence of transient dynamics.
+% ------------------------------------
+
+However, due to the random initialization of the DNN weights, CONAC's initial performance is expected to be poor, leading to unstable behavior.
+Therefore, in order to avoid the instability caused by the initial poor performance of CONAC, a warm-up phase was introduced, prior to applying the reference trajectory.
+In the warm-up phase, the manipulator was initially positioned at a stable equilibrium point, denoted as ${\qd}^{\rm{origin}} = \left(-\tfrac{1}{2}\pi, 0\right)^\top$.
+Subsequently, a trajectory $\mathcal{P}^5(t; {\qd}^{\rm{origin}}, \mv{q}_d^{(0)})$ was used to move the manipulator from ${\qd}^{\rm{origin}}$ to $\mv{q}_d^{(0)}$ over a duration of 3 seconds.
+Once the manipulator reached $\mv{q}_d^{(0)}$, a constant reference trajectory $\qd = \mv{q}_d^{(0)}$ was maintained for 8 seconds to allow the system to settle and eliminate the influence of transient dynamics.
 
@@
 % ------------------------------------
-The effectiveness of the proposed CONAC in handling combined convex input constraints was demonstrated by introducing a saturation function that projects the control input onto the convex set $\Theta_{\mysat} :=\left\{ \Theta_{\mysat, {\tau_2}} \cap \Theta_{\mysat, {\rbu}} \right\}$, as illustrated in Fig.~\ref{fig:robot:sat}, where
+In the validation, we assume that the actuators are subject to a convex saturation function that projects the control input onto the convex set 
+$
+    \Theta_{\mysat} :=\left\{ \Theta_{\mysat, {\tau_2}} \cap \Theta_{\mysat, {\rbu}} \right\}
+$, as illustrated in Fig.~\ref{fig:robot:sat}, where
 \begin{subequations}
@@
 \end{subequations}
-
 The sets defined in \eqref{eq:sat:tau2} and \eqref{eq:sat:norm} can be physically interpreted as the current limit imposed by the torque limit of the second joint actuator and the power source, respectively.
-The corresponding control input constraints are mathematically described in Appendix~\ref{sec:appen:cstr} as the nonlinear input norm constraint \eqref{eq:cstr:input:bound} and the input bound constraint \eqref{eq:cstr:input:norm}, respectively.
+The corresponding control input constraints are mathematically described in Appendix~\ref{sec:appen:cstr} as the input bound constraint \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint \eqref{eq:cstr:input:norm}, respectively.
+
+% ------------------------------------
+% Controller Table
+% ------------------------------------
+\begin{table}[t]
+    \renewcommand{\arraystretch}{1.3}
+    \caption{Properties of the controllers}
+    \label{table:controller}
+    \centering
+    \begin{tabular}{c l l}
+    \hline
+        &\bf{Description}&\bf{Input Constraint Handling}\\
+    \hline
+    \hline
+        \multirow{2}{*}{(C$_1$)}&large&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
+        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+    \hline
+        \multirow{2}{*}{(C$_2$)}&small&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
+        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+    \hline
+        \multirow{2}{*}{(C$_3$)}&no input& \multirow{2}{*}{$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$} \\
+        & constraint &  \\
+    \hline
+        \multirow{2}{*}{(C$_4$)}&\multirow{2}{*}{auxiliary system} & $\overline{\tau}_1=-\underline{\tau}_1=10.428$ \\
+        &  & $\overline{\tau_2}=-\underline{\tau_2}=3.5$ \\    
+    \hline
+    \end{tabular}
+    \label{table:controllers}
+\end{table}
 
@@
 
-Four controllers were implemented for comparative analysis, with their properties summarized in Table~\ref{table:controllers}.
+For comparative analysis, four controllers were implemented, with their properties summarized in Table~\ref{table:controllers}.
 
@@
 Therefore, controller (C$1$) utilizes the full capability of the actuator.
-The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ defined in \eqref{eq:cstr:weight:ball}, were also incorporated into the CONAC framework.
+The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ defined in \eqref{eq:cstr:weight:ball}, were also incorporated into CONAC framework.
 As described in \eqref{eq:control:est}, the control input (torque) corresponds to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
@@
 The auxiliary system is defined by $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$, with initial condition $\mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^2$ represents the auxiliary state variables, and $\mm{A}_\zeta\in\R_{<0}^{2\times 2}$ and $\mm{B}_\zeta\in\R^{2\times 2}$ are user-designed matrices.
-The auxiliary state $\mv{\zeta}$ is driven by the overflow amount of the control input $\Delta\rbu$, where each element is defined as $\Delta\tau_{i} = \tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$..
+The auxiliary state $\mv{\zeta}$ is driven by the overflow amount of the control input $\Delta\rbu$, where each element is defined as $\Delta\tau_{i} = \tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
 
@@
 The tracking performance was quantitatively evaluated using the $L_2$-norm of the tracking error, defined as $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the duration of each episode.
-
-% ------------------------------------
-% Controller Table
-% ------------------------------------
-\begin{table}[t]
-    \renewcommand{\arraystretch}{1.3}
-    \caption{Properties of the controllers}
-    \label{table:controller}
-    \centering
-    \begin{tabular}{c l l}
-    \hline
-        &\bf{Description}&\bf{Input Constraint Handling}\\
-    \hline
-    \hline
-        \multirow{2}{*}{(C$_1$)}&large&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
-        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
-    \hline
-        \multirow{2}{*}{(C$_2$)}&small&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
-        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
-    \hline
-        \multirow{2}{*}{(C$_3$)}&no input& \multirow{2}{*}{$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$} \\
-        & constraint &  \\
-    \hline
-        \multirow{2}{*}{(C$_4$)}&\multirow{2}{*}{auxiliary system} & $\overline{\tau}_1=-\underline{\tau}_1=10.428$ \\
-        &  & $\overline{\tau_2}=-\underline{\tau_2}=3.5$ \\    
-    \hline
-    \end{tabular}
-    \label{table:controllers}
-\end{table}
 
@@
 
-The tracking performance of CONAC with control input constraints—\ie (C$_1$) and (C$_2$)—outperformed the auxiliary system-based controller (C$_4$) in the second episode, as shown in Table~\ref{tab:sim:L2}.
+The tracking performance of CONAC with control input constraints—\ie (C$_1$) and (C$_2$)—outperformed the auxiliary system-based CONAC (C$_4$) in the second episode, as shown in Table~\ref{tab:sim:L2}.
 This improvement is due to the fact that (C$_1$) and (C$_2$) were able to fully utilize the actuator's capabilities, whereas (C$_4$) was constrained by the auxiliary system's design, which limited the first joint actuator.
@@
 Such large violations may lead to actuator damage or failure, posing a significant risk to the physical system.
-Moreover, once the control saturation was released—typically due to a change in the reference trajectory—these large violations resulted in oscillatory behavior, as the controller's weights had been adapted to produce excessively high control inputs.
+Moreover, once the control saturation was released—typically due to a change in the reference trajectory—these large violations resulted in oscillatory behavior, as CONAC's weights had been adapted to produce excessively high control inputs.
 
@@
 This paper proposed a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems, addressing both weight norm and input constraints through a rigorous optimization framework.
-The stability of the proposed controller was analyzed via Lyapunov theory, demonstrating bounded tracking and estimation errors under real-time adaptation.
-
-The controller effectively incorporated both convex input constraints and weight norm constraints, ensuring that actuator limitations and neural network weights remained within predefined bounds. 
+The stability of the proposed CONAC was analyzed via Lyapunov theory, demonstrating bounded tracking and estimation errors under real-time adaptation.
+
+The proposed CONAC effectively incorporated both convex input constraints and weight norm constraints, ensuring that actuator limitations and neural network weights remained within predefined bounds. 
 By embedding these constraints into the optimization process, CONAC ensured convergence of the weights in accordance with the Karush-Kuhn-Tucker (KKT) conditions, thereby achieving both stability and optimality.
@@
 A real-time implementation validated the superior performance of CONAC compared to conventional methods. 
-The proposed controller successfully handled complex input constraints while rigorously managing weight norms, resulting in improved tracking accuracy and stable performance without significant oscillations.
+The proposed CONAC successfully handled complex input constraints while rigorously managing weight norms, resulting in improved tracking accuracy and stable performance without significant oscillations.
 
@@
     \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{\template/people/msRyu.jpg}}]{Myeongseok Ryu}
-    received the B.S.
-degree in mechanical engineering from Incheon National University, South Korea, in 2023, and the M.S.
-degree in mechanical engineering from Gwangju Institute of Science and Technology (GIST), South Korea, in 2025.
-    He is currently serving as a researcher at the Cho Chun Shik Graduate School of Mobility, Korea Advanced Institute of Science and Technology (KAIST), South Korea.
+    received the B.S. degree in Mechanical Engineering from Incheon National University, South Korea, in 2023, and the M.S. degree in Mechanical Engineering from GIST, South Korea, in 2025. 
+    He is currently serving as a researcher at the Cho Chun Shik Graduate School of Mobility at KAIST, South Korea.
     His research interests include adaptive control, neural-networks, and constrained optimization.

### 2025-06-13 manuscript.tex
review... for final step

@@
 \newcommand*{\figSizeOneCol}{0.98}
-
-% \addbibresource{\template/refs.bib}
 
@@
 
-\begin{IEEEkeywords}DV26H-64YTR-C9WFH-7A33V
+\begin{IEEEkeywords}
     Neuro-adaptive control, constrained optimization, deep neural network, input constraint.
@@
 \begin{itemize}
-    \item $\R$ denotes the set of real numbers and $\R^n$ denotes the $n$-dimensional Euclidean space.
+    \item := denotes ``is defined as" or ``is equal to".
+    \item $\R$ and $\R^{n\times m}$ denote the set of real numbers and $n\times m$ dimensional matrices, respectively, and $\R_{\ge0}:=[0,\infty)$ and $\R_{>0}:=(0,\infty)$.
     \item $(\cdot)^\top$ denotes the transpose of a vector or matrix.
-    \item $\otimes$ denotes the Kronecker product \cite[Chap. 7 Def. 7.1.2]{Bernstein:2009aa}.
+    \item $\norm{\cdot}$ and $\norm{\cdot}_F$ denote the Euclidean norm and Frobenius norm, respectively.
+    \item $\otimes$ denotes the Kronecker product \cite[Chap. 7, Def. 7.1.2]{Bernstein:2009aa}.
     \item A vector and a matrix are denoted by $\mv{x}=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ and $
@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item For $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=\left(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top) \right)^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
+    \item For the matrix $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=\left(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top) \right)^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
 
-More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
+More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Lewis:1998aa,Farrell:2006aa}. 
 NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
@@
 Conventionally, SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
-However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa} and physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.
-\MSRY{CNN도 넣을까요? Dixon교수님네도 저희 preprint논문 인용하셨더라구요}
+However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa}, physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, and convolutional NNs (CNNs) for learning historical sensor data \cite{Ryu:2024ac}, have further extended the capabilities of neuro-adaptive control systems.
+\MSRY{CNN도 넣었습니다.}
 
@@
 These laws guarantee convergence to the first-order optimality conditions, specifically the Karush–Kuhn–Tucker (KKT) conditions, as described in \cite[Chap.
-12 Thm.
+12, Thm.
 12.1]{Nocedal:2006aa}.
@@
 The terms $\rbM:=\rbM(\q)\in\R^{n\times n}$, $\rbVm:=\rbVm(\q,\dq)\in\R^{n\times n}$, $\rbF:=\rbF(\dq)\in\R^{n}$, and $\rbG:=\rbG(\q)\in\R^{n}$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction vector, and gravity vector, respectively.
-The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau$ denotes the maximum norm of control input.
+The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators such that $\norm{\mysat(\rbu)}\le \overline\tau$, where $\overline\tau\in\R_{>0}$ denotes the maximum norm of control input.
 
@@
 
-The Euler-Lagrange system \eqref{eq:sys1} satisfies several important physical properties, as presented in \cite[Chap. 3 Tab. 3.2.1]{Lewis:1998aa}. 
+The Euler-Lagrange system \eqref{eq:sys1} satisfies several important physical properties, as presented in \cite[Chap. 3, Tab. 3.2.1]{Lewis:1998aa}. 
 The key properties are introduced below:
@@
 
-The architecture of the proposed CONAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, and consists of a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN.
+The architecture of the proposed CONAC consists of a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN, as illustrated in Fig. \ref{fig:ctrl:diagram}.
 Before proceeding to the controller design, some mathematical preliminaries are revisited in Section \ref{sec:sub:math preliminaries}. 
@@
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
-    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CONAC).}
+    \caption{Architecture of the proposed constrained optimization-based neuro-adaptive controller (CONAC).}
     \label{fig:ctrl:diagram}
@@
 
-\begin{propsit}[see, {\cite[Chap. 7 Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
-	For matrix $\mm A\in\R^{n\times m}$ and vector $\mv b\in\mathbb R^n$, the following property holds:
+\begin{propsit}[see, {\cite[Chap. 7, Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
+	For a matrix $\mm A\in\R^{n\times m}$ and a vector $\mv b\in\mathbb R^n$, the following property holds:
 	\begin{equation}
@@
 \begin{lem} \label{lem:stable:set}
-    For Lyapunov function $V:=V(\mv{x})\ge0$ with $\mv{x}\in\R^n$, if the time derivative of $V$ is given by $\ddtt V\le -a_1 \mv{x}^\top \mv{x} + a_2 \mv{x}$ for some positive constants $a_1\in\R$ and $a_2\in\R$, then $\mv{x}$ is bounded as $\mv{x}\in\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
+    For a Lyapunov function $V:=V(\mv{x})\ge0$ with $\mv{x}\in\R^n$, if the time derivative of $V$ is given by $\ddtt V\le -a_1 \mv{x}^\top \mv{x} + a_2 \mv{x}$ for some positive constants $a_1\in\R_{>0}$ and $a_2\in\R_{>0}$, then $\mv{x}$ is bounded as $\mv{x}\in\{\mv{x}\mid\norm{\mv{x}}\le\tfrac{a_2}{a_1}\}$.
 \end{lem}
@@
 where $\mm{K}=\mm{K}^\top\in\R^{n\times n}_{>0}$ denotes an arbitrary unknown matrix and $
-    \mv f:= \mv F
+    \mv f:= \mv f
     \left(
@@
         +
-        \fe^\top (\mv f+\mysat(\rbu))\\
+        \fe^\top (\mv f+\mysat(\rbu))
         % \\
@@
 \end{equation} 
-Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped system uncertainty $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
-Hence, the ideal control input $\rbu^*$ is defined as $-\mv f$.
+Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}\le\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped system uncertainty $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
+Hence, the ideal control input $\rbu^*$ can be designed as $-\mv f$.
 However, $\rbu^*$ is not available in practice, since system dynamics encapsulated in $\mv f$ are unknown.
@@
 The architecture of DNN $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}, later.
-According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
-% Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \overline\wth<\infty$.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an bounded ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
+% Furthermore, the theorem states that the norm of $\idealwth$ is bounded such that $\norm{\idealwth}\le \overline\wth<\infty$.
 In this study, the ideal weight vector $\idealwth$ is considered a locally optimal solution, rather than a global one.
 
-Accordingly, the ideal control law $\rbu^*$ can be approximated by the DNN with the ideal weight vector $\idealNN:=\NN({\q}_n;\idealwth)$ as follows:
+Accordingly, the ideal control input $\rbu^*$ can be approximated by the DNN with the ideal weight vector $\idealNN:=\NN({\q}_n;\idealwth)$ as follows:
 \begin{align}
@@
 \end{align}
-where $\mv\epsilon\in\R^n$ is the approximation error vector, bounded by $\norm{\mv\epsilon}\le \bar{\epsilon}$.
-The control input $\rbu^*$ is estimated online by
+where $\mv\epsilon\in\R^n$ is the approximation error vector, bounded by $\norm{\mv\epsilon}\le \overline{\epsilon}$ for some $\overline{\epsilon}\in\R_{>0}$.
+The ideal control input $\rbu^*$ is estimated online by
 \begin{align}
@@
 \end{align}
-where $\hat\NN:=\NN({\q}_n;\estwth)$, and $\estwth\in\R^\Xi$ is the estimated weight vector for $\idealwth$.
+where $\hat\NN:=\NN({\q}_n;\estwth)$, and $\estwth\in\R^\Xi$ is the estimated weight vector for the ideal weight vector $\idealwth$.
 
@@
 \end{equation}
-where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer.
+where $\wV_i=[w_{ij}]_{i\in\{1,\cdots,l_i+1\},j\in\{1,\cdots,l_{i+1}\}}\in\R^{(l_i+1)\times l_{i+1}}$ and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represent the weight matrix and the activation function of the $i\textsuperscript{th}$ layer, respectively.
 The DNN $\NN({\q}_n;\wth)$ has $k+1$ layers, where the input layer is indexed by $i=0$, and the output layer is indexed by $i=k$.
@@
 
-The activation function is defined as $\act_i(\mv x)=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
+The activation function is defined as $\act_i(\mv x):=\left(\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1\right)^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices.
 In selecting the nonlinear function $\sigma(\cdot)$, the ReLU function \cite{Maas:2013aa} is one of the widely used functions for large DNNs, since it effectively avoids the gradient vanishing problem during error backpropagation.
-However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the activation function.
+However, for control applications, where relatively shallow DNNs are typically sufficient, and the gradient vanishing issue is less severe, the sigmoid function or the hyperbolic tangent function is commonly used as the nonlinear function $\sigma(\cdot)$.
 These functions simplify stability analysis, since they are continuously differentiable and their outputs and gradients are bounded. 
-In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the activation function, \ie $\sigma(x) = \tanh(x),\ \forall x\in\R$, which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}\le 1$.
-
-For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
+In this study, the hyperbolic tangent function $\tanh(\cdot)$ was selected as the nonlinear function, \ie $\sigma(x) = \tanh(x),\ \forall x\in\R$, which provides desirable boundedness with $\norm{\sigma(x)}<1$ and $\norm{\ddtfrac{\sigma(x)}{x}}\le 1$.
+
+For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i},\forall i\in\{0,\cdots,k\}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer.
 The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i, \forall i\in \{0,\cdots,k\}$ as 
@@
 \end{equation}
-where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. 
+where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights in the DNN.
+
 The gradient of $ \NN({\q}_n;\wth)$ with respect to $\wth$ can be obtained using Proposition \ref{propsit:kron} and the chain rule as follows:
@@
 In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
-Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \ddtfrac{\idealact_i}{\idealNN_{i-1}}$. 
-Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \ddtfrac{\estact_i}{\estNN_{i-1}}$.
+Additionally, let us define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \ddtfrac{\idealact_i}{\idealNN_{i-1}}$. 
+Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \ddtfrac{\estact_i}{\estNN_{i-1}}$.
 
@@
 \end{equation}
-where $J(\fe;\estwth):= \tfrac{1}{2} \fe^\top \fe$ is the objective function.
+where $J(\fe;\estwth)$ is the objective function.
 Inequality constraints $c_j:=c_j(\estwth),\ \forall j\in\mathcal{I}$, are imposed during the weight adaptation process to minimize the objective function, where $\mathcal I$ denotes the set of the imposed inequality constraints.
-Here, $\fe$ is considered a pre-defined data or static parameter for this optimization problem, so that the adaptation process does not consider the dynamics of $\fe$.
+% Here, $\fe$ is considered a pre-defined data or static parameter for this optimization problem, so that the adaptation process does not consider the dynamics of $\fe$.
 The Lagrangian function is defined as
@@
     + 
-    \sum_{j\in\mathcal I}
+    \textstyle\sum_{j\in\mathcal I}
     \lambda_{j}
@@
 \end{equation}
-where $\lambda_j$ denotes the Lagrange multiplier for each constraint.
-
-The adaptation laws for $\estwth$ and $[\lambda_j]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1} (\ie $\min_{\estwth} \max_{[\lambda_j]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda_j]_{j\in\mathcal I})$), as follows:
+where $\lambda_j,\forall j\in\mathcal{I}$ denotes the Lagrange multiplier for each constraint.
+
+The adaptation laws for $\estwth$ and $[\lambda_j]_{j\in\mathcal I}$ are derived to solve the dual problem of \eqref{eq:opt:problem1}, \ie $\min_{\estwth} \max_{[\lambda_j]_{j\in\mathcal I}}L(\fe,\estwth,[\lambda_j]_{j\in\mathcal I})$, as follows:
 \begin{subequations}
@@
 When a constraint $c_j$ becomes active, \ie $c_j > 0$, the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation, \ie see, \eqref{eq:adap:lbd}.
-Once the violation is resolved and the constraint is no longer active, \ie $c_j \le 0$, the multiplier decreases gradually until it returns to zero.
+Once the violation is resolved and the constraint is no longer active, \ie $c_j \le 0$, the Lagrange multiplier $\lambda_j$ decreases gradually until it returns to zero.
 Note that this adaption law is similar to the ALM in \cite{Nocedal:2006aa}, where the adaptation law for Lagrange multipliers is given by $\lambda_j\leftarrow \max\left(\lambda_j+\tfrac{c_j}{\mu},0\right)$, with $\mu\in\R_{>0}$ being the penalty parameter.
@@
 At steady state, where $\ddtt{\estwth}=0$ and $\ddtt\lambda_j=0$, the KKT conditions are satisfied, \ie $\pptfrac{L}{\estwth}=0$, $c_j \le 0$, $\lambda_j \ge 0$, and $\lambda_j c_j=0$.
-In other words, the proposed optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
+In other words, the proposed weight optimizer updates $\estwth$ and $\lambda_j$ in a way that satisfies the KKT conditions. 
 These conditions represent the first-order necessary conditions for optimality, guiding the updates toward candidates for a locally optimal point.
@@
 
-This section introduces essential constraints required to ensure the stability of the proposed CONAC, as well as candidate conditions for potential control input constraints.
-
-First, weight norm constraints are essential to prevent the weights from diverging during the adaptation process.
-The weight norm constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
+This section introduces essential constraints required to ensure the stability of the proposed CONAC, as well as conditions for potential control input constraints.
+
+First, weight norm constraints $\mv{c}_{\theta}(\estwth):= [c_{\theta_i}(\estwth)]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ defined in \eqref{eq:cstr:weight:ball}, are essential to prevent the weights from diverging during the adaptation process.
 \begin{equation}
@@
 \end{equation}
-with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$, and the arguments of $c_{\theta_i}(\cdot)$ are omitted for brevity.
-The gradient of $\mv{c}_\theta:=\mv c_{\theta}(\estwth)$ with respect to $\estwth$ is given by
+with $\overline\theta_i\in\R_{>0}$ denoting the maximum allowable norm for $\estwth_i$, and the arguments of $c_{\theta_i}(\cdot)$ are omitted for brevity.
+The gradient of $\mv{c}_\theta:=\mv c_{\theta}(\estwth)$ with respect to $\estwth$ can be obtained by accumulating the gradients of each layer as follows:
 \begin{equation}
@@
 \begin{assum}
-    The constraint functions $c_j(\estwth),\ \forall j\in\mathcal I$, are convex in the $\tau$-space and satisfy $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
+    The constraint function $c_j(\estwth)$ is convex in the $\tau$-space and satisfies $c_j(0) \le 0$ and $c_j(\idealwth)\le 0$.
     \label{assum:convex}
@@
 \begin{assum}
-    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12 Def.~12.1]{Nocedal:2006aa}.
+    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap.~12, Def.~12.1]{Nocedal:2006aa}.
     \label{assum:LICQ}
@@
 
-Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in\{0,\cdots,k\}}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
+Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in\{0,\cdots,k\}}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i, \forall i\in\{0,\cdots,k\}$.
 The following lemmas are introduced for the stability analysis.
@@
 
-Since $\rbu = \estNN$, using Proposition \ref{propsit:kron}, a linear mapping $\mm T(\cdot):\estwth_k\to\rbu$ that is independent of $\estwth_k$, can be derived using Proposition \ref{propsit:kron}:
+Since $\rbu = \estNN$, a linear mapping $\mm T(\cdot):\estwth_k\to\rbu$ that is independent of $\estwth_k$, can be derived using Proposition \ref{propsit:kron}:
 \begin{equation}\label{eq:linear:map}
@@
     If control input constraint $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
+    For instance, if $k=2$ and $i=0$, $\norm{\pptfrac{c_j}{\estwth_0}}$ is bounded, provided that $\norm{\estwth_2},\norm{\estwth_1}$ are bounded.
+    \MSRY{예시를 넣어봤는데 투머치 일까요?}
     \label{lem:cstr:grad:bound}
@@
     \pptfrac{c_j}{\rbu} 
+    \underbrace{
         \pptfrac{\rbu}{\estNN} 
+    }_{=\mm{I}_n}
     \pptfrac{\estNN}{\estwth_i}
-    ,
-\end{equation}
-where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
-From the linear mapping in \eqref{eq:linear:map}, $\rbu$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions.
-By Assumption \ref{assum:convex}, the function $c_j$ is convex in $\rbu$-space.
-The convex function has a bounded derivative with respect to $\rbu$, since $\rbu$ is a bounded variable (\ie $\pptfrac{c_j}{\rbu}$ is bounded). 
-Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in\{k,\cdots,i+1\}$, are bounded. 
+    = 
+    \pptfrac{c_j}{\rbu} 
+    \pptfrac{\estNN}{\estwth_i}
+    .
+\end{equation}
+The boundedness of the first term $\pptfrac{c_j}{\rbu}$ is guaranteed, if the input argument $\rbu$ is bounded owing to the convexity of $c_j$ by Assumption \ref{assum:convex}.
+In addition, the boundedness of $\rbu$ can be ensured by the boundedness of $\estwth_k$, since $\rbu=\estNN=(\mm I_{l_{k+1}}\otimes \estact_k^\top)\estwth_k$ and $\norm{\estact_k}$ is bounded due to the properties of the activation functions.
+The second term, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in\{k,\cdots,i+1\}$, are bounded. 
 This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
-Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$, is bounded, when $\estwth_i,\ \forall i\in \{k,\cdots,i+1\}$ are bounded.
+Consequently, the boundedness of $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ is depends on the boundedness of $\estwth_i,\ \forall i\in \{k,\cdots,i+1\}$.
 
@@
 
-The following theorem states that $\estwth$ and $\fe$ are bounded.
+The following theorem states that $\fe$ and $\estwth$ are bounded.
 
@@
     For the dynamical system described in \eqref{eq:sys1}, the neuro-adaptive controller in \eqref{eq:control:est} with the weight adaptation laws in \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
-    This holds under the weight norm constraint \eqref{eq:cstr:weight:ball}.
+    This holds under the weight norm constraints \eqref{eq:cstr:weight:ball}.
 \end{theorem}
@@
 % The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
-Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, and \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$, the boundedness of inner layers' weights follows once the boundedness of $\estwth_k$ and $\fe$ is established.
-Without loss of generality, weight norm constraint $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ is supposed to be active.
-This assumption is justified because, even if $c_{\theta_i}$ is inactive, $\estwth$ is adapted to minimize the objective function $J(·)$ as long as the constraint is not violated.
+Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, and \eqref{eq:DNN:architecture} and $\norm{\estact_k}<\infty$, 
+the boundedness of inner layers' weights will be established after proving the boundedness of $\fe$ and $\estwth_k$.
+In addition, without loss of generality, weight norm constraints $c_{\theta_i},\ \forall i\in\{0,\cdots,k\}$ are supposed to be active.
+This assumption is justified because, even if $c_{\theta_i}$ is inactive, $\estwth$ is adapted to minimize the objective function $J$ as long as the constraint is not violated.
 We consider two cases: (1) the control input is saturated, and (2) the control input is not saturated.
@@
 
-As a result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative) can be obtained using Lemma \ref{lem:stable:set} as follows:
+As a result of the time derivative of $V_1$ in \eqref{eq:lya1:dot2}, the invariant set $\Theta_{\fe}^{1}$ of $\fe$, \ie if $\fe$ leaves $\Theta_{\fe}^{1}$, $\ddtt V_1$ is negative, can be obtained using Lemma \ref{lem:stable:set} as follows:
 \begin{equation}
@@
             +
-            \bar{\theta}_k\sqrt{l_{k}+1}
-            +
-            \bar{\epsilon}
+            \overline{\theta}_k^*\sqrt{l_{k}+1}
+            +
+            \overline{\epsilon}
         }{
@@
 \end{equation}
-It is notable that the ideal DNN $\idealNN_k={\idealwV_k}^\top\idealact$ is bounded by $\bar{\theta}_k\sqrt{l_{k}+1}$, since $\norm{\idealwV_k}_F = \norm{\idealwth}_k \le \bar{\theta}_k$, and $\norm{\idealact_k}\le \sqrt{l_{k}+1}$.
+It is notable that the ideal DNN $\idealNN_k={\idealwV_k}^\top\idealact$ is bounded by $\overline{\theta}_k^*\sqrt{l_{k}+1}$.
+This is because, the ideal weight $\idealwth_k$ is bounded according to the universal approximation theorem in Section \ref{sec:sub:NAC} and Assumption \ref{assum:feasible} such that $\norm{\idealwth_k}\le\overline{\theta}_k^*$ for some positive constant $\overline{\theta}_k^*$.
+Hence, invoking $\norm{\idealwV_k}_F = \norm{\idealwth_k} \le \overline{\theta}_k^*$, and $\norm{\idealact_k}\le \sqrt{l_{k}+1}$, we have $\norm{\idealNN}\le \overline{\theta}_k^*\sqrt{l_{k}+1}$.
 
@@
         &
+        -
         \underbrace{
-            -
             \textstyle\sum_{
@@
             \estwth_k^\top \pptfrac{c_j}{\estwth_k}
-        }_{=:{\gamma}_2\in\R_{\le0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
+        }_{=:{\gamma}_2\in\R_{\ge0},\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
         \\
@@
                 +
-                \bar{\theta}_k\sqrt{l_{k}+1}
-                +
-                \bar{\epsilon}
+                \overline{\theta}^*_k\sqrt{l_{k}+1}
+                +
+                \overline{\epsilon}
             )
@@
 This drives $\estwth_k$ to the origin until the constraint is satisfied.
-By Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in the $\estwth_k$-space.
-
-Therefore, the boundedness of $\estwth_k$ and $\fe$ is guaranteed by the invariant sets $\Theta_{\fe}^{1}$ and $\Theta_{\theta_k}^{1}$, and the satisfactions of $c_j,\ \forall j\in\mathcal{I}$ is ensured.
+% By Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in the $\estwth_k$-space.
+
+Therefore, the boundedness of $\fe$ and $\estwth_k$ is guaranteed by the invariant sets $\Theta_{\fe}^{1}$ and $\Theta_{\theta_k}^{1}$, and the satisfactions of $c_j,\ \forall j\in\mathcal{I}$ is ensured.
 
@@
             +
-            \bar{\theta}_k\sqrt{l_{k}+1}
-            +
-            \bar{\epsilon}
+            \overline{\theta}^*_k\sqrt{l_{k}+1}
+            +
+            \overline{\epsilon}
         \right)
@@
             +
-            \bar{\theta}_k\sqrt{l_{k}+1}
-            +
-            \bar{\epsilon}
+            \overline{\theta}^*_k\sqrt{l_{k}+1}
+            +
+            \overline{\epsilon}
         }{
@@
 \end{equation}
-The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ remains positive unless the weight norm constraint $c_{\theta_k}$ is satisfied.
+The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta^*_k \}$, as $\lambda_{\theta_k}$ remains positive unless the weight norm constraint $c_{\theta_k}$ is satisfied.
 
@@
 
-The boundedness of the inner-layer weights and the satisfaction of their corresponding constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$, can be established recursively using \cite[Chap.~4 Thm.~1.9]{Desoer:2009aa}.
+The boundedness of the inner layer weights and the satisfaction of their corresponding constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in\{k-1,\cdots,0\}}$, can be established recursively using \cite[Chap.~4, Thm.~1.9]{Desoer:2009aa}.
 The dynamics of $\estwth_i,\ \forall i\in\{k-1,\cdots,0\}$, are represented as
@@
     .
-\end{equation}
-By Lemma \ref{lem:cstr:grad:bound} $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in\{k,\cdots,i+1\}$, are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
+    \label{eq:estwth:dyn}
+\end{equation}
+By Lemma \ref{lem:cstr:grad:bound} $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in\{k,\cdots,i+1\}$, are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded, \ie $\pptfrac{\estNN}{\estwth_i}, \fe, \pptfrac{c_j}{\estwth_i}$ are bounded and $\lambda_j$ does not diverge since the control input constraints will be satisfied before the divergence occurs.
 Therefore, starting from the $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).
+And the satisfaction of the weight norm constraints of inner weights can be verified as the Lagrange multipliers $\lambda_{\theta_i}$, $\forall i\in\{k-1,\cdots,0\}$, increase sufficiently large to stabilize the $\estwth_i$ dynamics \eqref{eq:estwth:dyn}, leading to the convergence of $\widehat{\mv{\theta}}_i$ toward the origin.
 
@@
 
-In conclusion, the filtered tracking error $\fe$ and the entire set of estimated weights $\estwth$ are bounded, and all imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
+In conclusion, the filtered tracking error $\fe$ and the weight estimate $\estwth$ are bounded, and all imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
 
@@
 The two-link robotic manipulator actuated by two Cubemars AK10-90 servo motors. 
-The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the corresponding servo via controller area network (CAN) communication.
+The servos were controlled using the OpenCR1.0 board which transmits the torque reference to the corresponding servo via controller area network (CAN) communication.
 The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and is illustrated in Fig.~\ref{fig:robot:model}. 
@@
 
-% \begin{table}[t]
-%     \renewcommand{\arraystretch}{1.3}
-%     \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
-%     \centering
-%     \begin{tabular}{c m{9.5em} c c c }
-%     % \begin{tabular}{c c c c c}
-%     \hline
-%     \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
-%     \hline
-%     \hline 
-%     $m_p$ & Mass & 2.465 (kg) & 2.465 (kg) \\
-%     \hline
-%     $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
-%     \hline
-%     ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
-%     \hline
-%     $b_p$   & Viscous friction coef. &  0.1 (Nms) & 0.1 (Nms) \\
-%     \hline
-%     ${f_c}_p$  & Coulomb friction coef. &  0.24 (Nm) & 0.24 (Nm) \\
-%     \hline
-%     ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
-%     \hline
-%     $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
-%     \hline
-%     \end{tabular}
-%     \label{table:system:params}
-% \end{table}
-
-% ------------------------------------
-% Reference Trajectory
-The desired (reference) trajectory is designed with $4$ segments as follows:
+% ------------------------------------
+% desired trajectory
+% ------------------------------------
+The desired trajectory is designed with $4$ segments as follows:
 \begin{equation}
@@
 To demonstrate the learning capability of the DNN, the desired trajectory was applied twice. 
-The first and second repetitions of the reference trajectory are referred to as Episode $1$ and Episode $2$, respectively.
+The first and second repetitions of the desired trajectory are referred to as Episode $1$ and Episode $2$, respectively.
 % ------------------------------------
@@
 However, due to the random initialization of the DNN weights, CONAC's initial performance is expected to be poor, leading to unstable behavior.
-Therefore, in order to avoid the instability caused by the initial poor performance of CONAC, a warm-up phase was introduced, prior to applying the reference trajectory.
+Therefore, in order to avoid the instability caused by the initial poor performance of CONAC, a warm-up phase was introduced, prior to applying the desired trajectory.
 In the warm-up phase, the manipulator was initially positioned at a stable equilibrium point, denoted as ${\qd}^{\rm{origin}} = \left(-\tfrac{1}{2}\pi, 0\right)^\top$.
 Subsequently, a trajectory $\mathcal{P}^5(t; {\qd}^{\rm{origin}}, \mv{q}_d^{(0)})$ was used to move the manipulator from ${\qd}^{\rm{origin}}$ to $\mv{q}_d^{(0)}$ over a duration of 3 seconds.
-Once the manipulator reached $\mv{q}_d^{(0)}$, a constant reference trajectory $\qd = \mv{q}_d^{(0)}$ was maintained for 8 seconds to allow the system to settle and eliminate the influence of transient dynamics.
+Once the manipulator reached $\mv{q}_d^{(0)}$, a constant desired trajectory $\qd = \mv{q}_d^{(0)}$ was maintained for 8 seconds to allow the system to settle and eliminate the influence of transient dynamics.
 
@@
 The sets defined in \eqref{eq:sat:tau2} and \eqref{eq:sat:norm} can be physically interpreted as the current limit imposed by the torque limit of the second joint actuator and the power source, respectively.
-The corresponding control input constraints are mathematically described in Appendix~\ref{sec:appen:cstr} as the input bound constraint \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint \eqref{eq:cstr:input:norm}, respectively.
+The corresponding control input constraints are mathematically described in Appendix~\ref{sec:appen:cstr} as the input bound constraint \eqref{eq:cstr:input:bound} and the input norm constraint \eqref{eq:cstr:input:norm}, respectively.
 
@@
 
-To handle input saturation, the proposed CONAC was implemented with the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} for the second link, and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
+To handle input saturation, the proposed CONAC was implemented with the input bound constraints $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} for the second link, and the input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
 \begin{equation}
@@
 The third controller was identical to (C$1$) and (C$2$), except that the control input constraints were removed to highlight the constraint handling capability of the proposed CONAC.
-In this case, the update rates of the Lagrange multipliers associated with the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, were set to zero, such that the corresponding multipliers $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ were not updated (see \eqref{eq:adap:lbd}).
+In this case, the update rates of the Lagrange multipliers associated with the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, were set to zero, such that the corresponding multipliers $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ were not updated, see, \eqref{eq:adap:lbd}.
 All other properties and parameters were kept the same as in (C$_1$) and (C$_2$).
@@
 This auxiliary state was incorporated into the adaptation law \eqref{eq:adap:th:approx} by replacing the filtered tracking error $\fe$ with $\fe+\mv{\zeta}$.
-As a result, the weights were adapted to minimize both the filtered tracking error and the auxiliary state, thereby resolving the control input constraint saturation.
-
-The matrices for the auxiliary system were chosen as $\mm{A}_\zeta=\mydiag\left((-10,-10)^\top\right)$ and $\mm{B}_\zeta=\mydiag\left((10^3,10^3)^\top\right)$, reflecting a trade-off between sensitivity to input saturation and convergence speed of the auxiliary dynamics.
-Since the auxiliary system only accounts for individual input saturation—corresponding to the input bound constraint \eqref{eq:cstr:input:bound}—the upper limit for the first actuator torque, $\overline{\tau}_1$, was set to $10.428$ to approximately match the allowable control input norm $\overline{\tau}$, given $\overline{\tau}_2 = 3.5$ and $\overline{\tau} = 11$, satisfying $\overline{\tau}_1^2 + \overline{\tau}_2^2 = \overline{\tau}^2$.
+As a result, the weights were adapted to minimize both the filtered tracking error and the auxiliary state, thereby resolving the control input saturation for each control input.
+
+The matrices for the auxiliary system were chosen as $\mm{A}_\zeta=\mydiag\left((-10,-10)^\top\right)$ and $\mm{B}_\zeta=\mydiag\left((10^3,10^3)^\top\right)$, reflecting a trade-off between sensitivity to input overflow and convergence speed of the auxiliary system dynamics.
+Since the auxiliary system only accounts for individual input saturation—corresponding to the input bound constraint \eqref{eq:cstr:input:bound}—the upper limit for the first actuator torque, $\overline{\tau}_1$ which is equal to $-\underline{\tau}_1$, was set to $10.428$ to approximately match the allowable control input norm $\overline{\tau}$, given $\overline{\tau}_2=-\underline{\tau}_2 = 3.5$ and $\overline{\tau} = 11$, satisfying $\overline{\tau}_1^2 + \overline{\tau}_2^2 = \overline{\tau}^2$.
 
@@
     \caption{
-    Real-time implementation results of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid}, and reference signal $\qd$ \protect\colorLine{red}{dashed}.
+    Real-time implementation results of (C$_1$) \protect\colorLine{blue}{solid}, (C$_2$) \protect\colorLine{cyan}{solid}, (C$_3$) \protect\colorLine{gray}{solid}, (C$_4$) \protect\colorLine{magenta}{solid}, and desired trajectory $\qd$ \protect\colorLine{red}{dashed}.
   }
@@
 These results indicate that the DNNs in all controllers successfully learned the ideal control input $\rbu^*$ using the filtered tracking error $\fe$, despite $\rbu^*$ being completely unknown a priori.
-Furthermore, the stable learning achieved under random weight initialization and without prior knowledge of the system demonstrates the effectiveness of the proposed CONAC in enabling online learning.
-
-Notably, in both episodes, all controllers failed to track the desired trajectory of $q_1$ during certain time intervals: from $17.5$ s to $19.9$ s in Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s in Episode $2$.
-This degradation in tracking performance is attributed to actuator saturation during those intervals, as observed in Fig.~\ref{fig:ctrl:result:tau:1} and Fig.~\ref{fig:ctrl:result:tau:norm}.
+Furthermore, the stable learning achieved under random weight initialization and no prior knowledge of the system, demonstrated the effectiveness of the proposed CONAC in enabling online learning capability.
+
+Notably, in both episodes, all controllers failed to track the desired trajectory of $q_1$ during certain time intervals: from $17.5$ s to $19.9$ s in Episode $1$, and from $23.5$ s to $25.9$ s and from $29.5$ s to $31.9$ s in Episode $2$, as shown in Fig.~\ref{fig:ctrl:result:q1}.
+This degradation in tracking performance is attributed to actuator saturation during those intervals, as observed in Fig.~\ref{fig:ctrl:result:tau:2} and Fig.~\ref{fig:ctrl:result:tau:norm}.
 
@@
 While (C$_3$) also showed better performance than (C$_4$), this was primarily because it did not consider input saturation and thus used more of the actuator's capacity.
-However, since (C$_3$) did not handle the control input saturation, it generated excessively large control efforts to minimize the tracking error, even though these efforts could not be realized due to actuator limits, as shown in Fig.~\ref{fig:ctrl:result:tau:2} and Fig.~\ref{fig:ctrl:result:tau:norm}.
+However, since (C$_3$) did not handle the control input saturation, it generated excessively large control efforts to minimize the tracking error, even though these efforts could not be realized due to actuator limits, as shown in Fig.~\ref{fig:ctrl:result:tau:1}–\ref{fig:ctrl:result:tau:norm}.
 In addition, the magnitude of saturation violations for (C$_3$) increased during each interval where input constraints were active.
 Such large violations may lead to actuator damage or failure, posing a significant risk to the physical system.
-Moreover, once the control saturation was released—typically due to a change in the reference trajectory—these large violations resulted in oscillatory behavior, as CONAC's weights had been adapted to produce excessively high control inputs.
+Moreover, once the control saturation was released—typically due to a change in the desired trajectory—these large violations resulted in oscillatory behavior, as CONAC's weights had been adapted to produce excessively high control inputs, as shown in Fig.~\ref{fig:ctrl:result:tau:1}–\ref{fig:ctrl:result:tau:norm}.
 
@@
 In this section, the constraint handling capability of all controllers are investigated.
-As shown in Fig.~\ref{fig:ctrl:result:tau:1}, Fig.~\ref{fig:ctrl:result:tau:2}, and Fig.~\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}.
-For (C$_1$) and (C$_2$), the control input saturation was handled using the Lagrange multipliers and, for (C$_4$), the auxiliary system was used to handle the control input saturation.
-
-Even though all controllers except (C$_3$) satisfied the input saturation, (C$_4$) was unable to fully utilize the actuator's capability.
-As shown in Fig.~\ref{fig:ctrl:result:scope:control}, which illustrates the control input locus during the time interval from $29.4$ s to $31.9$ s, the control inputs of (C$_1$) and (C$_2$) were constrained by the combined convex input constraints, which precisely matched the feasible domain $\Theta_{\mysat}$ depicted in Fig.~\ref{fig:robot:sat}
-In contrast, (C$_4$)'s control input was restricted independently by each component-wise constraint, limiting its ability to explore the full admissible input space, owing to the decoupled formulation of the auxiliary system.
-
-\hfill
+As shown in Fig.~\ref{fig:ctrl:result:tau:1}–\ref{fig:ctrl:result:tau:norm}, all controllers except (C$_3$) which did not consider the control input saturation, satisfied the control input saturation illustrated in Fig.~\ref{fig:robot:sat}.
+For (C$_1$) and (C$_2$), the control input saturation was handled using corresponding input constraints in the constrained optimization framework and, for (C$_4$), the auxiliary system was utilized, as summarized in Table~\ref{table:controllers}.
+
+To investigate the constraint handling process, the time interval from $29.4$ s to $31.9$ s was selected, during which the control input saturation was active for all controllers.
+In Fig.~\ref{fig:ctrl:result:scope}, the control input locus, the Lagrange multipliers, and the auxiliary states are illustrated during this time interval.
+The properties of the controllers can be observed in Fig.~\ref{fig:ctrl:result:scope:control}, where the control input locus of (C$_1$) and (C$_2$) fully explores the feasible domain of control input illustrated in Fig.~\ref{fig:robot:sat}, while (C$_3$) exceeds the input saturation limits, and (C$_4$) is limited in its first actuator input by the auxiliary system design.
+
+% beta
+The detail of the input constraint handling during the time interval from $29.4$ s to $31.9$ s, is now investigated.
+In the cases of (C$_1$) and (C$_2$), as the input constraints $c_j$ were activated, the corresponding Lagrange multipliers $\lambda_j$ were generated dynamically, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}.
+These Lagrange multipliers directed the adaptation of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$, to reduce violations of the constraints $c_j$, according to \eqref{eq:adap:th}.
+
+% comparison; big, small beta
+For more details, the growth effect of some convex input constraint's Lagrange multiplier $\lambda_j$ on the adaptation direction of $\estwth_2$ is illustrated in Fig.~\ref{fig:lambda_effect}, where two different magnitudes of $\lambda_j$ are considered.
+With this configuration, the difference between (C$_1$) and (C$_2$) can be investigated, \ie large and small update rate $\beta_j$, since, for instance, (C$_1$) with large update rate $\beta_j$ leads to a larger Lagrange multiplier $\lambda_j$ than (C$_2$) with small update rate, see, \eqref{eq:adap:lbd}.
+Notably, under Assumptions \ref{assum:convex} and \ref{assum:LICQ}, the constraint $c_j$ is convex in the $\estwth_2$-space, invoking Lemma~\ref{lem:convex:angle}.
+
+As illustrated in Fig.~\ref{fig:lambda_effect}, with large Lagrange multiplier $\lambda_j$, the adaptation direction of $\estwth_2$ is significantly influenced by the term $-\lambda_j\pptfrac{c_j}{\estwth_2}$ in \eqref{eq:adap:th}, which directs the weights toward satisfactory point of the constraint.
+Hence, this results in a more aggressive adjustment of the weights leading to faster constraint satisfaction—but at the cost of oscillatory behavior in the learning process.
+In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, the earlier reasoning can be observed, where (C$_1$) with large update rate $\beta_j$, satisfied the input constraint $c_{\overline{tau}_1}$ faster than (C$_2$) with repeatedly growing and resetting $\lambda_{\rbu}$.
+In contrast, with small $\lambda_j$, the adaptation direction of $\estwth_2$ is less influenced, leading to a more conservative adjustment of the weights adaptation.
+Consequently, the constraint satisfaction is achieved more smoothly, but potentially at the cost of slower satisfaction (convergence), as shown in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}.
 
 % zeta
-The detail of the constraint handling during the time interval from $29.4$ s to $31.9$ s, is now investigated.
-For (C$_4$), the auxiliary state $\zeta_1$ was generated in response to the control input saturation of the first link actuator, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
+For (C$_4$), the auxiliary state $\zeta_1$ was generated in response to the control input saturation of the first link actuator $\tau_1$, as shown in Fig.~\ref{fig:ctrl:result:scope:aux}.
 Since the weights were adapted to reduce both the filtered error $\fe$ and the auxiliary state $\mv{\zeta}$, the control input saturation was subsequently reduced, as evident in Fig.~\ref{fig:ctrl:result:scope:control}.
-Once the saturation was resolved at approximately $31$ seconds (see, Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero due to the stable state matrix $\mm{A}_\zeta$ in the auxiliary dynamics, given by $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as shown again in Fig.~\ref{fig:ctrl:result:scope:aux}.
-
-% beta + zeta
-In the cases of (C$_1$) and (C$_2$), the Lagrange multipliers $\lambda_j\in\forall j\in\mathcal{I}$ directed the adaptation of the weights $\estwth_i,\ \forall i\in\{0,1,2\}$, to reduce violations of the constraints $c_j$.
-The multipliers $\lambda_j$ were generated dynamically in response to constraint violations.
-% comparison; big, small beta
-The effect of Lagrange multiplier $\lambda_j$ on the adaptation direction of $\estwth_2$ is illustrated in Fig.~\ref{fig:lambda_effect}, where two different magnitudes of $\lambda_j$ are considered. 
-Notably, under Assumptions \ref{assum:convex} and \ref{assum:LICQ}, the constraint $c_j$ is convex in the $\estwth_2$-space (see, Lemma~\ref{lem:convex:angle}).
-Large and small Lagrange multipliers correspond to the configurations of (C$_1$) and (C$_2$), respectively, because the update rates in (C$_1$) were set $10^2$ times larger than those in (C$_2$).
-Consequently, in (C$_1$), $\lambda_j$ increases more rapidly in response to constraint violations (see, \eqref{eq:adap:lbd}). 
-This results in a more aggressive adaptation of $\estwth_2$, leading to faster constraint satisfaction—but at the cost of oscillatory behavior in the learning process.
-
-Following this reasoning, the real-time implementation results of (C$_1$) and (C$_2$) are compared in Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}. 
-In these figures, $\lambda_{\rbu}$ for (C$_1$) repeatedly grows and resets, indicating recurring violations and satisfactions of the $c_{\rbu}$ constraint in discrete time.
-On the other hand, (C$_2$), with smaller $\lambda_{\rbu}$, updates $\estwth_2$ more conservatively. 
-This slower response leads to delayed constraint satisfaction, which is reflected by the persistent positive value of $\lambda_{\rbu}$ in Fig.~\ref{fig:ctrl:result:scope:beta}. 
-However, this allows (C$_2$) to achieve smoother control input behavior, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
+Once the saturation was resolved at approximately $31$ s (see, Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero due to the stable state matrix $\mm{A}_\zeta$ in the auxiliary system dynamics, given by $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as shown again in Fig.~\ref{fig:ctrl:result:scope:aux}.
 
@@
 % \MSRY{필요하다면 왜 제어입력 제약하는게 가중치 제약도 되는지 추가 가능}
-Furthermore, the constraints on the inner and hidden layer weights were never violated; that is, $\norm{\estwth_0}$ and $\norm{\estwth_1}$ consistently remained below $\norm{\estwth_2}$. 
+Furthermore, the constraints on the inner and hidden layer weights were never violated; that is, $\norm{\estwth_0}$ and $\norm{\estwth_1}$ consistently remained below their limits.
 This is attributed to the fact that the backpropagated error was scaled by the gradient of the activation function, which is bounded between $-1$ and $1$; see, \eqref{eq:gradient:phi}.
@@
 
-\KHCH{
-    이부분은 "worth to note"하지는 않아보입니다. 그리고 FIg 5에서 이 것을 확인하기도 어렵습니다. 굳이 이내용을 유지하려면 Fig 6에서 multiplier가 발생했다 사리지는 현상을 표현할 때 사용해주세요.
-}
-\MSRY{
-    부드럽게 제약조건만족이 안되는 것에 대한 변명(?)으로 포함하고 싶었습니다. 
-    그렇기에 제약조건 파트 제일 마직막으로 뺐습니다.
-}
-
-In addition, it is worth noting that the control input constraints were repeatedly violated even after the constraint handling mechanisms were applied, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
-This occurred because the controllers were implemented in discrete time with a relatively low sampling rate of $250$ Hz.
+% In addition, it is worth noting that the control input constraints were repeatedly violated even after the constraint handling mechanisms were applied, as shown in Fig.~\ref{fig:ctrl:result:scope:control}.
+% This occurred because the controllers were implemented in discrete time with a relatively low sampling rate of $250$ Hz.
 
@@
     =
+    \tfrac{1}{2}\
+    \left(
         \norm{
@@
         \overline\tau^2
+    \right)
     ,
@@
     \!=\! 
-    \textstyle\sum_{i=1}^n 2\tau_{i} 
+    \textstyle\sum_{i=1}^n \tau_{i} 
     \left(
@@
     \label{eq:cstr:input:norm:grad}
-\end{equation}0
+\end{equation}
+
+\hfill
+
 It should be noted that constraints \eqref{eq:cstr:input:bound} and \eqref{eq:cstr:input:norm} can be imposed simultaneously, as their gradients \eqref{eq:cstr:input:bound:grad} and \eqref{eq:cstr:input:norm:grad} are linearly independent, satisfying Assumption \ref{assum:LICQ}, \ie the LICQ condition.

### 2025-06-13 src/measurement/animate.m

@@ -20,10 +20,10 @@ idleTime2 = 4;
 animation_end_t = T + idleTime1;
 
 PhaseList = {
-    "Idle 1",
+    "Warm-up",
     "Episode 1",
     "Episode 2",
-    "Idle 2"
+    "End"
 };
 
 %% 

### 2025-06-16 manuscript.tex
minor change

@@
 \begin{abstract}
-  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for uncertain Euler-Lagrange systems subject to weight and convex input constraints. 
+  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for \color{red}unkown\color{black} Euler-Lagrange systems subject to weight and convex input constraints. 
   A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a constrained optimization framework.
@@
 NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
-Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations.
-Conventionally, SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
+Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Lewis:1996aa,Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations.
+Conventionally, SHL and RBF NNs are often employed to approximate \color{red}unkown\color{black} system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
 However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa}, physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, and convolutional NNs (CNNs) for learning historical sensor data \cite{Ryu:2024ac}, have further extended the capabilities of neuro-adaptive control systems.
-\MSRY{CNN도 넣었습니다.}
 
@@
 The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
-The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
-This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
-In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs \cite{Khalil:2002aa}.
-
-To address input saturation, many studies introduced auxiliary systems. 
+% The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
+This issue is exacerbated in neuro-adaptive controllers that utilize NNs as additional control inputs to cancel out uncertain (unknown) system dynamics while conventional model-based control methods, \eg feedback linearization and backstepping, are employed.
+In the cases of feedback linearization and backstepping, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs \cite{Khalil:2002aa}.
+Moreover, if the control inputs are already saturated, the NNs are enforced to compensate for the saturated inputs.
+In other words, the conventional methods deteriorates the learning process by sabotaging the NN adaptation law, as the feedback error for learning is no longer directly related to the NNs' output.
+Hence, the input constraint should be handled in an unity adaptation framework \MSRY{Start from here!}
+
+To address this early discussed issue, many studies introduced auxiliary systems to handle input constraint in adaptation process. 
 These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
@@
 
+\hfill
+
+This study is extended from our preliminary work presented in \cite{Ryu:2024aa} where the inequality constraint for weight norm was imposed on the neuro-adaptive control design to establish the weight boundedness using constrained optimization framework.
+Similar to weight constraints in \cite{Ryu:2024aa}, control input constraints are also incorporated into the CONAC framework to address the convex input saturation problem as well.
+Furthermore, the applicability of the proposed CONAC is investigated in a real-time implementation on a 2-DOF robotic manipulator; while the referenced work was limited to the numerical simulation.
+
 \subsection{Organization}
@@
 
-We consider an uncertain Euler-Lagrange system modeled as
+We consider an \color{red}unkown\color{black} Euler-Lagrange system modeled as
 \begin{equation}
@@
 
-In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems, since the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
+In this study, the saturation function $\mysat(\cdot)$ is assumed to be convex, which is practically common in many engineering systems.
+This is because, the actuator limits are naturally convex, such as min/max torque limits, and bounds look like a box or ball in the input space.
 To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
@@
 The architecture of the proposed CONAC consists of a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN, as illustrated in Fig. \ref{fig:ctrl:diagram}.
+The algorithm of the proposed CONAC is given by Algorithm \ref{alg:CONAC}. 
 Before proceeding to the controller design, some mathematical preliminaries are revisited in Section \ref{sec:sub:math preliminaries}. 
@@
     \centering
-    \includegraphics[width=.99\linewidth]{src/figures/Controller.drawio.pdf}
+    \includegraphics[width=.999\linewidth]{src/figures/Controller.drawio.pdf}
     % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
@@
 
+\begin{algorithm}[!t]
+    \caption{Proposed CONAC Algorithm}\label{alg:CONAC}
+    \begin{algorithmic}[1]
+        \STATE \textbf{Initialize:} DNN weights $\estwth$ and Lagrange multipliers $\lambda_j$
+        \FOR{each sampling time}
+            \STATE Measure current state $\q,\dq$
+            \STATE Compute filtered error $\fe$ \eqref{eq:err:filtered}
+            \STATE Update DNN weights $\estwth$ using $\fe$ \eqref{eq:adap:th}
+            \STATE Update Lagrange multipliers $\lambda_j$ based on constraint function $c_j$ \eqref{eq:adap:lbd} and \eqref{eq:adap:lbd:max}
+            \STATE Compute control input $\rbu$ (DNN output) \eqref{eq:control:est} and \eqref{eq:DNN:architecture}
+            \STATE Apply control input $\rbu$ to the system \eqref{eq:sys1}
+        \ENDFOR
+    \end{algorithmic}
+\end{algorithm}
+
 \subsection{Mathematical Preliminaries}\label{sec:sub:math preliminaries}
@@
 
-\begin{propsit}[see, {\cite[Chap. 7, Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
+\begin{propsit}[see {\cite[Chap. 7, Prop. 7.1.9]{Bernstein:2009aa}}] \label{propsit:kron}
 	For a matrix $\mm A\in\R^{n\times m}$ and a vector $\mv b\in\mathbb R^n$, the following property holds:
@@
 
-First, a filtered tracking error $\fe\in\R^n$ is defined as 
+Given that the Euler-Lagrange system \eqref{eq:sys1} exhibits second-order dynamics, a filtered error $\fe\in\R^n$ is introduced to convert the system into a first-order system, as follows:
 \begin{equation}
@@
 The architecture of DNN $\NN({\q}_n;\wth)$ will be presented in Section \ref{sec:sub:NN definition}, later.
-According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an bounded ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
+According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN({\q}_n;\wth)$ can approximate a nonlinear function, denoted as $\mv g(\cdot)$, with an ideal weight vector $\idealwth\in\R^\Xi$ over a compact subset $\Omega_{n}\in\R^{l_0+1}$ to within $\epsilon$-accuracy, such that $\sup_{{\q}_n\in\Omega_{n}}\norm{ \NN({\q}_n;\idealwth) - \mv g(\cdot)} = \epsilon < \infty$.
 % Furthermore, the theorem states that the norm of $\idealwth$ is bounded such that $\norm{\idealwth}\le \overline\wth<\infty$.
-In this study, the ideal weight vector $\idealwth$ is considered a locally optimal solution, rather than a global one.
+In this study, the ideal weight vector $\idealwth$ is assumed to be bounded by Assumption \ref{assum:feasible} and \cite[Assum.
+1]{Lewis:1996aa}, and considered a locally optimal solution, rather than a global one.
 
@@
 
-The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented as follows:
+The DNN architecture $\NN({\q}_n;\wth) := \NN_k$ can be recursively represented from the $0\textsuperscript{th}$ input layer to the $k\textsuperscript{th}$ output layer, as follows:
 \begin{equation}
@@
 The Lagrange multipliers associated with inequality constraints are non-negative, \ie $\lambda_j\ge 0$, due to \eqref{eq:adap:lbd:max}. 
-When a constraint $c_j$ becomes active, \ie $c_j > 0$, the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation, \ie see, \eqref{eq:adap:lbd}.
+When a constraint $c_j$ becomes active, \ie $c_j > 0$, the corresponding Lagrange multiplier $\lambda_j$ increases to address the violation, \ie see \eqref{eq:adap:lbd}.
 Once the violation is resolved and the constraint is no longer active, \ie $c_j \le 0$, the Lagrange multiplier $\lambda_j$ decreases gradually until it returns to zero.
@@
 However, this approach is not applicable to \eqref{eq:sys:filtered}, where control directions are unknown.
-Instead, since the sign of the control input matrix is known—owing to the positive definiteness of $\rbM^{-1}$, see, Property \ref{prop:M}—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
+Instead, since the sign of the control input matrix is known—owing to the positive definiteness of $\rbM^{-1}$, see Property \ref{prop:M}—we approximate $\pptfrac{\fe}{\rbu}\approx \mm I_n$.
 Consequently, the adaptation law in \eqref{eq:adap:th} becomes:
@@
 
-%% ALGORITHM PART; Now omitted!
-% The proposed controller is implemented using Algorithm \ref{alg: alg1}.
-For implementation in the discrete-time domain, it is recommended to use a sufficiently small sampling time $T_s$.
-If a large $T_s$ is used, $\alpha$ and $\beta_j$ should satisfy the Armijo condition \cite[Chap.~3 eq.~(3.4)]{Nocedal:2006aa} to ensure that the objective function decreases.
-
-% \begin{algorithm}[!t]
-%     \caption{Weight Optimizer Implementation.}\label{alg: alg1}
-%     \begin{algorithmic}[1]
-%         \renewcommand{\algorithmicrequire}{\textbf{Input:}}
-%         \renewcommand{\algorithmicensure}{\textbf{Output:}}
-%         \REQUIRE $\xi$, $\estwth$, $\lambda_j$, $\eta$
-%         \ENSURE  $\estwth$, $\lambda_j$, $\eta$
-%         \STATE Set $\mathcal A \leftarrow \mathcal A\cup \{j\}$ for all $c_j\ge0$;
-%         \STATE Determine update matrix $\ddtt\eta$ using \eqref{eq. eta dynamics 1};
-%         \STATE Update $\eta\leftarrow \eta +\ddtt\eta\cdot T_s$; 
-%         \STATE Determine update directions $\ddtt{\estwth}$, $[\ddtt\lambda_j]_{j\in\mathcal A}$ using \eqref{eq. adaptation law th}, \eqref{eq. adaptation law L};
-%         \STATE Update weight vector $\estwth\leftarrow \estwth+\ddtt{\estwth}\cdot T_s$;
-%         \STATE Update multipliers $[\lambda_j]_{j\in\mathcal A}\leftarrow [\lambda_j]_{j\in\mathcal A}+[\ddtt\lambda_j]_{j\in\mathcal A}\cdot T_s$;
-%         \STATE $[\lambda_j]_{j\in\mathcal A}\leftarrow \max([\lambda_j]_{j\in\mathcal A}, 0)$;
-%         \STATE Set $\mathcal A \leftarrow \mathcal A - \{j\}$ for all $\lambda_j=0$;
-%         \STATE \textbf{RETURN};
-%     \end{algorithmic}
-%     \label{alg1}
-% \end{algorithm}
-
 \subsection{Essential and Potential Constraint Candidates}\label{sec:sub:cstr}
@@
     Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
-    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
+    This assumption will be used in the stability analysis (see Lemma \ref{lem:convex:angle}).
 \end{remark}
@@
 \begin{lem}
-    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} hold, then for each active constraint $c_j$, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive; that is $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
+    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} hold, then for each active constraint $c_j$, the angle between the output layer's weight vector $\estwth_k$ and $\pptfrac{c_j}{\estwth_k}$ is positive; that is $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
     \label{lem:convex:angle}
@@
 \end{equation}
-Therefore, the convexity of the input constraints in the $\rbu$-space (see, Assumption \ref{assum:convex}) is preserved in $\estwth_k$-space, implying
+Therefore, the convexity of the input constraints in the $\rbu$-space (see Assumption \ref{assum:convex}) is preserved in $\estwth_k$-space, implying
 that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
@@
     If control input constraint $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in\{k-1,\cdots, 0\}$, is bounded, provided the norms of $\estwth_i,\ \forall i\in\{k,\cdots, i+1\}$, remain bounded.
-    For instance, if $k=2$ and $i=0$, $\norm{\pptfrac{c_j}{\estwth_0}}$ is bounded, provided that $\norm{\estwth_2},\norm{\estwth_1}$ are bounded.
-    \MSRY{예시를 넣어봤는데 투머치 일까요?}
     \label{lem:cstr:grad:bound}
 \end{lem}
+
+For instance, if $k=3$ and $i=1$, $\norm{\pptfrac{c_j}{\estwth_1}}$ is bounded, provided that $\norm{\estwth_3},\norm{\estwth_2}$ are bounded.
 
@@
 % The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
-Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see, \eqref{eq:control:est}, and \eqref{eq:DNN:architecture} and $\norm{\estact_k}<\infty$, 
+Invoking the fact that the amplitude of the control input depends only on $\estwth_k$, \ie see \eqref{eq:control:est}, and \eqref{eq:DNN:architecture} and $\norm{\estact_k}<\infty$, 
 the boundedness of inner layers' weights will be established after proving the boundedness of $\fe$ and $\estwth_k$.
@@
 The servos were controlled using the OpenCR1.0 board which transmits the torque reference to the corresponding servo via controller area network (CAN) communication.
-The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1} and is illustrated in Fig.~\ref{fig:robot:model}. 
+The system dynamics of the two-link robotic manipulator can follow the Euler-Lagrange equation \eqref{eq:sys1}, where $\q$ denotes joint angles and $\rbu$ denotes the control input (joint torques), and is illustrated in Fig.~\ref{fig:robot:model}.
 The measured and/or estimated system parameters are provided in Table~\ref{table:system:params}.
@@
     \subfloat[Two-link robotic manipulator.]{
-        \includegraphics[width=0.7\linewidth]{src/figures/RobotModel.drawio.pdf}
+        \includegraphics[width=0.55\linewidth]{src/figures/RobotModel.drawio.pdf}
         \label{fig:robot:model}
@@
 $, as illustrated in Fig.~\ref{fig:robot:model}.
-The time duration of the segment is defined as $t_f=3$ s.
+The time duration of the segments is defined as $t_f=3$ s.
 To demonstrate the learning capability of the DNN, the desired trajectory was applied twice. 
@@
 In the warm-up phase, the manipulator was initially positioned at a stable equilibrium point, denoted as ${\qd}^{\rm{origin}} = \left(-\tfrac{1}{2}\pi, 0\right)^\top$.
-Subsequently, a trajectory $\mathcal{P}^5(t; {\qd}^{\rm{origin}}, \mv{q}_d^{(0)})$ was used to move the manipulator from ${\qd}^{\rm{origin}}$ to $\mv{q}_d^{(0)}$ over a duration of 3 seconds.
+Subsequently, a trajectory $\mathcal{P}^5(t; {\qd}^{\rm{origin}}, \mv{q}_d^{(0)},3)$ was used to move the manipulator from ${\qd}^{\rm{origin}}$ to $\mv{q}_d^{(0)}$ over a duration of 3 seconds.
 Once the manipulator reached $\mv{q}_d^{(0)}$, a constant desired trajectory $\qd = \mv{q}_d^{(0)}$ was maintained for 8 seconds to allow the system to settle and eliminate the influence of transient dynamics.
@@
     \hline
-        \multirow{2}{*}{(C$_1$)}&large&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
-        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
-    \hline
-        \multirow{2}{*}{(C$_2$)}&small&\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
-        &  update rate $\beta_j$ &\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
-    \hline
-        \multirow{2}{*}{(C$_3$)}&no input& \multirow{2}{*}{$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$} \\
+        \multirow{2}{*}{(C$_1$)}&large&\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+        &  update rate $\beta_j$ &\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
+    \hline
+        \multirow{2}{*}{(C$_2$)}&small&\eqref{eq:cstr:input:bound} $c_{\overline\tau_2}, c_{\underline\tau_2}$ with $\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
+        &  update rate $\beta_j$ &\eqref{eq:cstr:input:norm} $c_{\rbu}$ with $\overline{\tau}=11$ \\
+    \hline
+        \multirow{2}{*}{(C$_3$)}&no input& \multirow{2}{*}{$[\beta_j]_{j\in\{\overline{\tau}_2,\underline{\tau}_2,\rbu\}}=\mv{0}$} \\
         & constraint &  \\
@@
 % ------------------------------------
-% Controllers: CONAC 
+% Controllers: CONAC with large beta 
 % ------------------------------------
@@
 Therefore, controller (C$1$) utilizes the full capability of the actuator.
-The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ defined in \eqref{eq:cstr:weight:ball}, were also incorporated into CONAC framework.
+The weight norm constraints $c_{\theta_i}(\cdot),\ \forall i\in\{0,\cdots,k\}$ defined in \eqref{eq:cstr:weight:ball}, were also incorporated into CONAC framework with $\overline\theta_0=\overline\theta_1=\overline\theta_2=6$.
 As described in \eqref{eq:control:est}, the control input (torque) corresponds to the output of the DNN, and the adaptation law is defined in \eqref{eq:adaptation law}.
@@
 The update rates of the Lagrange multipliers for the weight norm constraints were set to $\beta_{\theta_i}=1,\ \forall i\in\{0,\cdots,k\}$.
-For the control input constraints, the update rates were assigned large values: $\beta_{\rbu} = 10$ and $\beta_{\overline{\tau}2} = \beta{\underline{\tau}_2} = 10^2$, in order to investigate the effect of large update rates.
+For the control input constraints, the update rates were assigned large values: $\beta_{\overline{\tau}2} = \beta{\underline{\tau}_2} = 10^2$ and $\beta_{\rbu} = 10$, in order to investigate the effect of large update rates.
 
@@
 
-As the second controller, the proposed CONAC was implemented with the same input bound constraints as (C$_1$), but with $100$ times smaller update rate values: $\beta_{\rbu}=0.1$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=1$.
+As the second controller, the proposed CONAC was implemented with the same input bound constraints as (C$_1$), but with $100$ times smaller update rate values: $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=1$ and $\beta_{\rbu}=0.1$.
 All other properties and parameters were kept identical to those of (C$_1$).
@@
 The third controller was identical to (C$1$) and (C$2$), except that the control input constraints were removed to highlight the constraint handling capability of the proposed CONAC.
-In this case, the update rates of the Lagrange multipliers associated with the control input constraints, \ie $\beta_{\rbu},\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2}$, were set to zero, such that the corresponding multipliers $[\lambda_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}$ were not updated, see, \eqref{eq:adap:lbd}.
+In this case, the update rates of the Lagrange multipliers associated with the control input constraints, \ie $\beta_{\overline{\tau}_2},\beta_{\underline{\tau}_2},\beta_{\rbu}$, were set to zero, such that the corresponding Lagrange multipliers $[\lambda_j]_{j\in\{\overline{\tau}_2,\underline{\tau}_2,\rbu\}}$ were not updated, see \eqref{eq:adap:lbd}.
 All other properties and parameters were kept the same as in (C$_1$) and (C$_2$).
@@
 All DNNs shared the same architecture, consisting of two hidden layers with four nodes each, \ie $k=2$ and $l_0=6, l_1=4, l_2=4$, and $l_3=2$ in \eqref{eq:DNN:architecture}.
-The adaptation gain was set to $\alpha = 0.2$, and the filtering matrix in \eqref{eq:err:filtered} was chosen as $\mm{\Lambda}=\mydiag([5,15])$.
-The DNN weights were initialized using a uniform distribution in the range $[-0.1, 0.1]$, with the same random seed used across all experiments to ensure consistency.
-The controller sampling rate was set to $250$ Hz to support real-time implementation.
-Weight norm constraint parameters were selected as $\overline\theta_0=\overline\theta_1=\overline\theta_2=6$.
-
-Control results were collected via CAN communication using a PCAN-USB interface and recorded on a computer at a sampling rate of $250$ Hz.
-
-The tracking performance was quantitatively evaluated using the $L_2$-norm of the tracking error, defined as $\sqrt{\int_0^T\norm{h}\,\der t}$, where $h\in\{e_1,e_2\}$ and $T\in\R_{>0}$ denotes the duration of each episode.
+The adaptation gain was set to $\alpha = 0.2$, and the filtering matrix in \eqref{eq:err:filtered} was chosen as $\mm{\Lambda}=\mydiag\left((5,15)^\top\right)$.
+To support real-time implementation, the controller operated at a sampling rate of $250$ Hz, with control results collected via CAN communication using a PCAN-USB interface and recorded on a computer at the same rate.
+
+The tracking performance was quantitatively evaluated using the $L_2$-norm of the each joint angle's tracking error, defined as $\sqrt{\int_0^T\norm{e_i(t)}\,\der t},\forall i\in\{1,2\}$, where $T\in\R_{>0}$ denotes the duration of each episode.
 
@@
   \centering
-    \subfloat[Tracking result of $q_1$.]{
+    \subfloat[Tracking result of $1$\textsuperscript{st} joint angle $q_1$.]{
     %   \includegraphics
@@
     \hfill
-    \subfloat[Tracking result of $q_2$.]{
+    \subfloat[Tracking result of $2$\textsuperscript{nd} joint angle $q_2$.]{
       \includegraphics[width=\figSizeTwoCol\linewidth]
@@
     \vfill
-      \subfloat[Control input $\tau_1$.]{
+      \subfloat[Control input $1$\textsuperscript{st} joint torque $\tau_1$.]{
         \includegraphics[width=\figSizeTwoCol\linewidth]
@@
     \hfill
-      \subfloat[Control input $\tau_2$.]{
+      \subfloat[Control input $2$\textsuperscript{nd} joint torque $\tau_2$.]{
         \includegraphics[width=\figSizeTwoCol\linewidth]
@@
         \vfill
-    \subfloat[Norm of control input $\rbu$.]{
+    \subfloat[Norm of control input (joint torque)$\rbu$.]{
         \includegraphics[width=\figSizeTwoCol\linewidth]
@@
     \hfill
-    \subfloat[Norm of weights ${\estwth}_i$.]{
+    \subfloat[Norm of DNN weights ${\estwth}_i$.]{
         % \includegraphics
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{
+	\includegraphics[width=0.7\linewidth]{
 		src/figures/lambda_effect.drawio.pdf
@@
 For more details, the growth effect of some convex input constraint's Lagrange multiplier $\lambda_j$ on the adaptation direction of $\estwth_2$ is illustrated in Fig.~\ref{fig:lambda_effect}, where two different magnitudes of $\lambda_j$ are considered.
-With this configuration, the difference between (C$_1$) and (C$_2$) can be investigated, \ie large and small update rate $\beta_j$, since, for instance, (C$_1$) with large update rate $\beta_j$ leads to a larger Lagrange multiplier $\lambda_j$ than (C$_2$) with small update rate, see, \eqref{eq:adap:lbd}.
-Notably, under Assumptions \ref{assum:convex} and \ref{assum:LICQ}, the constraint $c_j$ is convex in the $\estwth_2$-space, invoking Lemma~\ref{lem:convex:angle}.
+With this configuration, the difference between (C$_1$) and (C$_2$) can be investigated, as well, \ie large and small update rate $\beta_j$, since, for instance, (C$_1$) with large update rate $\beta_j$ leads to a larger Lagrange multiplier $\lambda_j$ than (C$_2$) with small update rate, see \eqref{eq:adap:lbd}.
+Notably, under Assumptions \ref{assum:convex} and \ref{assum:LICQ}, the constraint $c_j$ is convex in the $\estwth_2$-space, see Lemma~\ref{lem:convex:angle}.
 
@@
 Hence, this results in a more aggressive adjustment of the weights leading to faster constraint satisfaction—but at the cost of oscillatory behavior in the learning process.
-In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, the earlier reasoning can be observed, where (C$_1$) with large update rate $\beta_j$, satisfied the input constraint $c_{\overline{tau}_1}$ faster than (C$_2$) with repeatedly growing and resetting $\lambda_{\rbu}$.
+In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, the earlier reasoning can be observed, where (C$_1$) with large update rate $\beta_j$ satisfied the input constraint $c_{\overline{\tau}_1}$ faster than (C$_2$) with repeatedly growing and resetting $\lambda_{\rbu}$.
 In contrast, with small $\lambda_j$, the adaptation direction of $\estwth_2$ is less influenced, leading to a more conservative adjustment of the weights adaptation.
@@
 Since the weights were adapted to reduce both the filtered error $\fe$ and the auxiliary state $\mv{\zeta}$, the control input saturation was subsequently reduced, as evident in Fig.~\ref{fig:ctrl:result:scope:control}.
-Once the saturation was resolved at approximately $31$ s (see, Fig.~\ref{fig:ctrl:result:tau:norm}), the auxiliary state $\zeta_1$ converged to zero due to the stable state matrix $\mm{A}_\zeta$ in the auxiliary system dynamics, given by $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as shown again in Fig.~\ref{fig:ctrl:result:scope:aux}.
+Once the saturation was resolved at approximately $31$ s (see Fig.~\ref{fig:ctrl:result:scope:control}), the auxiliary state $\zeta_1$ converged to zero due to the stable state matrix $\mm{A}_\zeta$ in the auxiliary system dynamics, given by $\ddtt\mv{\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu$ with $\Delta\rbu=\mv{0}_{2\times1}$, as shown again in Fig.~\ref{fig:ctrl:result:scope:aux}.
 
@@
 Finally, the handling of the weight norm constraints $c_{\theta_i},\ \forall i\in\{0,1,2\}$, is investigated. 
-Among all controllers, the weight norm constraint was only activated for the outer layer weights $c_{\theta_2}$ in (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}. 
+Among all controllers, the weight norm constraint was only activated for the output layer weights $c_{\theta_2}$ in (C$_3$), as shown in Fig.~\ref{fig:ctrl:result:weight}. 
 This is because the weights in (C$_1$), (C$_2$), and (C$_4$) were implicitly suppressed by the control input constraints, whereas (C$_3$) did not incorporate such constraints.
@@
 Furthermore, the constraints on the inner and hidden layer weights were never violated; that is, $\norm{\estwth_0}$ and $\norm{\estwth_1}$ consistently remained below their limits.
-This is attributed to the fact that the backpropagated error was scaled by the gradient of the activation function, which is bounded between $-1$ and $1$; see, \eqref{eq:gradient:phi}.
-
-Additional details on the constraint handling process are provided in Fig.~\ref{fig:ctrl:result:scope}. 
-In particular, Fig.~\ref{fig:ctrl:result:scope:beta} shows that the Lagrange multipliers $\lambda_{\theta_2}$ increased when $\estwth_2$ exceeded the prescribed norm constraint $\overline\theta_2$, prompting an adjustment in the adaptation direction of $\estwth_2$ to mitigate the violation of the constraint $c_{\theta_2}$.
+This is attributed to the fact that the backpropagated error was scaled by the gradient of the activation function, which is bounded between $-1$ and $1$; see \eqref{eq:NN:grad}.
+
+Additional details on the constraint handling process are provided in Fig.~\ref{fig:ctrl:result:scope:beta}. 
+Similar to the case of the control input constraints, the Lagrange multipliers $\lambda_{\theta_2}$ increased when $\estwth_2$ exceeded the prescribed norm constraint 
+$\overline\theta_2$ at approximately $30.4$ s, as shown in Fig.~\ref{fig:ctrl:result:weight}, prompting an adjustment in the adaptation direction of $\estwth_2$ to mitigate the violation of the constraint $c_{\theta_2}$, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}.
 
@@
 Since the proposed CONAC was implemented in discrete time, a direct demonstration of the KKT conditions at steady state is not straightforward. 
-However, the near-constant values of the weights and Lagrange multipliers during constraint violation suggest an implicit satisfaction of the KKT conditions. 
+However, the near-constant values of the weights and Lagrange multipliers during constraint violation suggest an implicit satisfaction of the KKT conditions, as shown in Fig.~\ref{fig:ctrl:result:weight} and Fig.~\ref{fig:ctrl:result:scope:beta}.
 Specifically, the Lagrange multipliers corresponding to active constraints were positive, while those associated with inactive constraints remained zero.
@@
 
-This paper proposed a constrained optimization-based neuro-adaptive controller (CONAC) for uncertain Euler-Lagrange systems, addressing both weight norm and input constraints through a rigorous optimization framework.
-The stability of the proposed CONAC was analyzed via Lyapunov theory, demonstrating bounded tracking and estimation errors under real-time adaptation.
+This paper proposed a constrained optimization-based neuro-adaptive controller (CONAC) for \color{red}unkown\color{black} Euler-Lagrange systems, addressing both weight norm and input constraints through a rigorous optimization framework.
+The stability of the proposed CONAC was analyzed via Lyapunov theory, demonstrating bounded tracking and weight estimation errors under real-time adaptation.
 
@@
 
-This section introduces potential weight and input constraints that can be incorporated into the proposed CONAC framework.
+This section introduces potential input constraints that can be incorporated into the proposed CONAC framework.
 
@@
 \end{equation}
-with $\tau_{\overline \tau_i}\in\R_{>0}$ and $\tau_{\underline\tau_i}\in\R_{>0}$ representing the maximum and minimum control input bounds, respectively.
+with $\tau_{\overline \tau_i}\in\R$ and $\tau_{\underline\tau_i}\in\R$ representing the maximum and minimum control input bounds, respectively.
 The gradients of $\mv{c}_{\overline \tau}$ and $\mv{c}_{\underline\tau}$ with respect to $\estwth$ are given by
@@
 
-Consider the control input $\rbu$ as the torque of each actuator corresponding to its generalized coordinate. 
+Consider the control input $\rbu$ as the torque corresponding to its generalized coordinate. 
 Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations.

### 2025-06-16 manuscript.tex
peer review 3!

@@
 \begin{abstract}
-  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for \color{red}unkown\color{black} Euler-Lagrange systems subject to weight and convex input constraints. 
-  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a constrained optimization framework.
+  This study presents a constrained optimization-based neuro-adaptive control (CONAC) for unknown Euler-Lagrange systems subject to weight and convex input constraints. 
+  A deep neural network (DNN) is employed to approximate the ideal stabilizing control law while simultaneously learning the unknown system dynamics and addressing both types of constraints within a unified constrained optimization framework.
   The adaptation law of DNN weights is formulated to solve the defined constrained optimization problem, ensuring satisfaction of first-order optimality conditions at steady state.
@@
     \item := denotes ``is defined as" or ``is equal to".
-    \item $\R$ and $\R^{n\times m}$ denote the set of real numbers and $n\times m$ dimensional matrices, respectively, and $\R_{\ge0}:=[0,\infty)$ and $\R_{>0}:=(0,\infty)$.
+    \item $\R$, $\R^n$ and $\R^{n\times m}$ denote the set of real numbers, $n\times 1$ dimensional vectors and $n\times m$ dimensional matrices, respectively, and $\R_{\ge0}:=[0,\infty)$ and $\R_{>0}:=(0,\infty)$.
     \item $(\cdot)^\top$ denotes the transpose of a vector or matrix.
-    \item $\norm{\cdot}$ and $\norm{\cdot}_F$ denote the Euclidean norm and Frobenius norm, respectively.
+    \item $\norm{\cdot}$ and $\norm{\cdot}_F$ denote the Euclidean and Frobenius norm, respectively.
     \item $\otimes$ denotes the Kronecker product \cite[Chap. 7, Def. 7.1.2]{Bernstein:2009aa}.
@@
     \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
-    \item For the matrix $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=\left(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top) \right)^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
+    \item For the matrix $\mm{A}\in\R^{n\times m}$, $\myvec(\mm A):=(\myrow_1(\mm A^\top),\cdots,\myrow_m(\mm A^\top) )^\top\in\R^{nm}$ denotes the vectorization of $\mm A$.
     % \item $\mycol_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
@@
 These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
-To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.
-
-More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Lewis:1998aa,Farrell:2006aa}. 
+In worst cases, any prior knowledge of the system dynamics may not be available, making it challenging to design effective controllers.
+% To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.
+To address these challenges, adaptive control methods have been widely employed to ensure robust performance for uncertain (unknown) systems \cite{Ioannou:2006aa, Tao:2003aa}.
+
+More recently, neuro-adaptive control approaches have been introduced to approximate uncertain (unknown) system dynamics or entire control laws using neural networks (NNs) \cite{Lewis:1998aa,Farrell:2006aa}.
 NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
 Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) NNs \cite{Lewis:1996aa,Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) NNs \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep NNs (DNNs) \cite{Patil:2022aa} and their variations.
-Conventionally, SHL and RBF NNs are often employed to approximate \color{red}unkown\color{black} system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
+Conventionally, SHL and RBF NNs are often employed to approximate uncertain (unknown) system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}.
 However, since DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Griffis:2023aa}, physics-informed NNs (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, and convolutional NNs (CNNs) for learning historical sensor data \cite{Ryu:2024ac}, have further extended the capabilities of neuro-adaptive control systems.
@@
 The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
-% The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
-This issue is exacerbated in neuro-adaptive controllers that utilize NNs as additional control inputs to cancel out uncertain (unknown) system dynamics while conventional model-based control methods, \eg feedback linearization and backstepping, are employed.
-In the cases of feedback linearization and backstepping, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs \cite{Khalil:2002aa}.
-Moreover, if the control inputs are already saturated, the NNs are enforced to compensate for the saturated inputs.
-In other words, the conventional methods deteriorates the learning process by sabotaging the NN adaptation law, as the feedback error for learning is no longer directly related to the NNs' output.
-Hence, the input constraint should be handled in an unity adaptation framework \MSRY{Start from here!}
-
-To address this early discussed issue, many studies introduced auxiliary systems to handle input constraint in adaptation process. 
-These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
-For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly.
-This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.
-
-Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}.
-In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
+This issue is exacerbated in neuro-adaptive controllers that utilize NNs as additional control inputs to compensate for uncertain system dynamics, while model-based control methods—such as feedback linearization or backstepping—are employed.
+In such architectures, when the system model is inaccurate or the dynamics that the NN is intended to learn are already stabilizing, the model-based control inputs may produce excessively aggressive control inputs.
+This often lead to unnecessary saturation of the control inputs, as discussed in \cite{Khalil:2002aa}.
+
+To address the aforementioned issue, several approaches have been proposed in \cite{Gao:2006aa,Arefinia:2020aa,He:2016aa,Peng:2020aa,Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} to handle input constraints in neuro-adaptive control systems.
+Particularly, the auxiliary systems have been widely introduced.
+In \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}, the auxiliary states were generated whenever input saturation was detected, and these states were used as feedback terms in the control law to directly compensate for the effects of input saturation constraints.
+On the other hands, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, the auxiliary systems incorporated into the adaptation law by adding the auxiliary states to the feedback error for learning.
+This approach helped the NN reduce input saturation by indirectly regulating the auxiliary states, during the adaptation process.
+
 However, these approaches typically handle input bound constraints on a per-input basis, \ie applying bounds to each scalar control variable individually, and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.
+
+Moreover, from another perspective of learning, incorporating NNs with the conventional control methods by adding the NN output to the conventional control methods can disrupt the adaptation process of the NN.
+This is because the adaptation law relies on the feedback error, which becomes decoupled from the NN output due to the dominance of the conventional methods.
+In these cases, the NN is forced to counteract the conventional control inputs rather than learn the system dynamics directly.
+As a result, the NN's ability to learn and adapt is undermined.
+Therefore, it is recommended that input constraints be handled within a unified adaptation framework like \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, where both adaptation and constraint satisfaction are addressed simultaneously, without relying on the conventional control inputs.
 
@@
 Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
-Moreover, auxiliary systems typically handle only simple forms of input constraints, such as individual input bound constraints, limiting their ability to address more complex, nonlinear constraints.
+Auxiliary systems typically handle only simple forms of input constraints, such as individual input bound constraints, limiting their ability to address more complex, nonlinear constraints.
+Moreover, using conventional control methods in conjunction with NNs can disrupt the adaptation process.
 
 To overcome these limitations, constrained optimization offers a promising approach. 
-By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function, \eg tracking error, subject to both weight and input constraints.
+By formulating the neuro-adaptive control problem as an unified optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function, \eg tracking error, subject to both weight and input constraints, simultaneously.
 Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.
@@
 Moreover, the proposed CONAC can handle any combination of these constraints, which can be useful in practical applications where multiple constraints need to be satisfied simultaneously.
-    % \item Since the proposed CONAC approximate the entire ideal control law with no prior knowledge of the system dynamics, the system identification process can be avoided, which is often difficult and time-consuming to implement in practice.
+    \item Since the proposed CONAC approximate the entire ideal control law with no prior knowledge of the system dynamics, the system identification process for nominal conventional controller design can be avoided, which is often difficult and time-consuming to implement in practice.
     \item The adaptation laws for DNN weights and Lagrange multipliers are systematically derived to solve the defined problem, using constrained optimization theory.
@@
 This study is extended from our preliminary work presented in \cite{Ryu:2024aa} where the inequality constraint for weight norm was imposed on the neuro-adaptive control design to establish the weight boundedness using constrained optimization framework.
-Similar to weight constraints in \cite{Ryu:2024aa}, control input constraints are also incorporated into the CONAC framework to address the convex input saturation problem as well.
+Similar to weight constraints in \cite{Ryu:2024aa}, control input constraints are also incorporated into the constrained optimization framework to address the convex input saturation problem as well.
 Furthermore, the applicability of the proposed CONAC is investigated in a real-time implementation on a 2-DOF robotic manipulator; while the referenced work was limited to the numerical simulation.
@@
 
-We consider an \color{red}unkown\color{black} Euler-Lagrange system modeled as
+We consider an unknown Euler-Lagrange system modeled as
 \begin{equation}
@@
     \in\R^n
-$ denotes the lumped system uncertainty.
+$ denotes the lumped unknown system.
 % \color{red}
@@
 \end{equation} 
-Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}\le\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped system uncertainty $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
+Therefore, invoking Lemma \ref{lem:stable:set}, it can be concluded that the filtered error $\fe$ is exponentially stable, with $\lim_{t\to\infty}\norm{\fe}\le\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, provided that the lumped unknown system $\mv{f}$ can be perfectly cancelled by the control input $\rbu$, neglecting the effect of input saturation.
 Hence, the ideal control input $\rbu^*$ can be designed as $-\mv f$.
@@
 
-This paper proposed a constrained optimization-based neuro-adaptive controller (CONAC) for \color{red}unkown\color{black} Euler-Lagrange systems, addressing both weight norm and input constraints through a rigorous optimization framework.
+This paper proposed a constrained optimization-based neuro-adaptive controller (CONAC) for unknown Euler-Lagrange systems, addressing both weight norm and input constraints through a rigorous optimization framework.
 The stability of the proposed CONAC was analyzed via Lyapunov theory, demonstrating bounded tracking and weight estimation errors under real-time adaptation.

### 2025-06-17 presentation/presentation.tex
ppt update

@@
 % Inbuilt themes in beamer
-\documentclass[8pt, aspectratio=169]{beamer}
+\documentclass[8pt, aspectratio=169, handout]{beamer}
+% \documentclass[8pt, aspectratio=169]{beamer}
 
@@
 \usepackage{multirow}
-
-% \usepackage{calc}
-% \usepackage{svg}
-% \usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
-% \usepackage{multimedia}
-% \usepackage{animate}
+\usepackage{media9}
 
@@
 
-% \logo{
-%   \vspace{-.7cm}%
-%   \includegraphics[height=0.3cm]{assets/kaist_logo.png}
-%   \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
-%   \hspace{.6cm}%
-%   }
-
 \AtBeginSection[]{%
@@
 % Title page frame
-% \begin{frame}
 \titlepage
-% \end{frame}
 
@@
 
-% Lists frame
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Background and Contributions         ║
+% ╚═══════════════════════════════════════════════╝
 \section{Background and Contributions}
@@
     \begin{itemize}
-      \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
-      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
-      \item \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
-      \item \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
+      \item <+-> \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
+      \item <+-> \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
+      \item <+-> \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
+      \item <+-> \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
     \end{itemize}
@@
 
-  \textbf{Challenges}
-  \small{
+  \begin{enumerate}
+    \begin{columns}[T,onlytextwidth]
+        \column{0.49\textwidth}
+          \item \textbf{Weight Boundedness:}
+
           \begin{itemize}
-      \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
-      \item \textbf{Unpredictable Amplitude of Control input}: 
+            \item The NN weights can grow unbounded, leading to instability.
+            \item Unbounded weights can cause the NN to produce large control inputs, which may lead to following challenges.
+          \end{itemize}
+
+        \column{0.49\textwidth}
+          \centering
+          \begin{figure}
+            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
+            \caption{Unbounded NN weights.}
+          \end{figure}
+      \end{columns}
+
+      \begin{columns}[T,onlytextwidth]
+        \column{0.49\textwidth}
+          \item \textbf{Unpredictable Amplitude of Control Input:}
+
           \begin{itemize}
-          \item The maximum amplitude of the NN weights is not predictable.
-          \item This can result in unpredictable amplitude of the control input, which may lead to control saturation.
+            \item The NN outputs are unpredictable and not interpretable.
+            \item This feature and unbounded NN weights can lead to control input saturation.
           \end{itemize}
-      \item \textbf{Parameter Dependency}: 
-      \begin{itemize}
-        \item The performance of the NAC is highly dependent on the choice of parameters, such as learning rate and NN architecture.
-      \end{itemize}
-    \end{itemize}
-  }
+
+        \column{0.49\textwidth}
+          \centering
+          \begin{figure}
+            \includegraphics[width=0.8\textwidth]{figures/unpredictable.drawio.pdf}
+            \caption{Unpredictable amplitude of NN outputs.}
+          \end{figure}
+      \end{columns}
+  \end{enumerate}
 
@@
 
-% \subsection{Literature Review}
-
-% \begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}
-
-%   In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.
-
-%   \begin{enumerate}
-%     \begin{columns}[T,onlytextwidth]
-%         \column{0.49\textwidth}
-%           \item \textbf{Projection Operator}
-
-%           \begin{itemize}
-%             \item Cats 
-%             \item Dogs 
-%             \item Birds
-%           \end{itemize}
-
-%         \column{0.49\textwidth}
-%           \begin{figure}
-%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-%           \end{figure}
-%       \end{columns}
-
-%       \begin{columns}[T,onlytextwidth]
-%         \column{0.49\textwidth}
-%           \item \textbf{$\epsilon$-modification, and $\sigma$-modification}
-
-%           \begin{itemize}
-%             \item Cats 
-%             \item Dogs 
-%             \item Birds
-%           \end{itemize}
-
-%         \column{0.49\textwidth}
-%           \begin{figure}
-%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-%           \end{figure}
-%       \end{columns}
-%   \end{enumerate}
-% \end{frame}
-
-% \begin{frame}{\insertsubsectionhead}{Input Saturation}
-
-%   The input saturation is generally handled using an auxiliary system.
-
-%   \begin{enumerate}
-%     \begin{columns}[T,onlytextwidth]
-%         \column{0.49\textwidth}
-%           \item \textbf{Auxiliary Systems}
-
-%           \begin{itemize}
-%             \item Cats 
-%             \item Dogs 
-%             \item Birds
-%           \end{itemize}
-
-%         \column{0.49\textwidth}
-%           \begin{figure}
-%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-%           \end{figure}
-%       \end{columns}
-
-%       \begin{columns}[T,onlytextwidth]
-%         \column{0.49\textwidth}
-%           \item \textbf{Second?}
-
-%           \begin{itemize}
-%             \item Cats 
-%             \item Dogs 
-%             \item Birds
-%           \end{itemize}
-
-%         \column{0.49\textwidth}
-%           \begin{figure}
-%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-%           \end{figure}
-%       \end{columns}
-%   \end{enumerate}
-% \end{frame}
-
-\subsection{Research Objectives}
+\subsection{Literature Review}
 
@@
 
-  \textbf{Objective 1: Optimality}
+  \begin{enumerate}
+    \begin{columns}[T,onlytextwidth]
+        \column{0.65\textwidth}
+          \item \textbf{Projection Operator} \small{\textit{for weight boundednss}}
+
           \begin{itemize}
-    \item Formulate a constrained optimization problem to minimize the tracking error.
-    \item Guarantee the stability of the system and the NN weights.
+            \item Projects the NN weights onto a convex set.
+            \item Ensures that the weights remain within a predefined bound.
           \end{itemize}
 
-  \textbf{Objective 2: Stability}
+          \begin{equation}
+            \estwth \leftarrow \myproj_{\overline{\theta}}(\estwth)
+          \end{equation}
+
+        \column{0.35\textwidth}
+          \begin{figure}
+            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+      \end{columns}
+
+      \vspace{0.2cm}
+
+      \begin{columns}[T,onlytextwidth]
+        \column{0.65\textwidth}
+          \item \textbf{$\epsilon$-modification, and $\sigma$-modification} \small{\textit{for weight boundednss}}
+
           \begin{itemize}
-    \item Derive an adaptation law that guarantees the stability of the system.
-    \item Ensure that the NN weights remain bounded during operation.
+            \item Add a stabilizing term to adaptation law.
+            \item Invariance set of the NN weights can be ensured.
           \end{itemize}
 
-  \textbf{Objective 3: Boundedness of }
+          \begin{equation}
+            \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \rho \norm{\estwth}
+          \end{equation}
+
+        \column{0.35\textwidth}
+          \begin{figure}
+            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+
+      \end{columns}
+
+      \vspace{0.2cm}
+
+      \begin{columns}[T,onlytextwidth]
+        \column{0.65\textwidth}
+          \item \textbf{Additional Control Inputs} \small{\textit{for control saturation}}
+
           \begin{itemize}
-    \item Ensure the controller is robust to uncertainties and disturbances.
-    \item Validate the proposed method through numerical simulations.
+            \item Conventional controllers are used to address control input saturation. 
+                  \begin{itemize}
+                    \item Barrier Lyapunov function or auxiliary system-based control inputs.
+                  \end{itemize}
+            \item These methods do not guarantee the stability of the system.     
+          \end{itemize}
+
+        \column{0.35\textwidth}
+
+          \begin{figure}
+            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
+          \end{figure}
+
+      \end{columns}
+  \end{enumerate}
+\end{frame}
+
+\begin{frame}{\insertsubsectionhead}{Limitations of Existing Methods}
+
+  \textbf{Limitation 1: Lack of Optimality}
+  \begin{itemize}
+    \item The existing methods do not guarantee the optimality of the control input.
+    \item ...
+  \end{itemize}
+
+  \textbf{Limitation 2: Disruption of Learning Process by Additional Control Inputs}
+  \begin{itemize}
+    \item Feedback tracking error for learning is disrupted by additional control inputs.
+      \begin{itemize}
+        \item The feedback error does not reflect the error induced by the NN, directly.
+      \end{itemize}  
+    \item 
   \end{itemize}
@@
 
+\subsection{Contributions}
+
+\begin{frame}{\insertsubsectionhead}
+
+  \textbf{Contribution 1: Unified Optimization Framework} 
+  \begin{itemize}
+    \item 
+  \end{itemize}
+
+  \textbf{Contribution 2: Online Learning Capability (Stabiltiy Guarantees)}
+  \begin{itemize}
+    \item 
+  \end{itemize}
+
+  \textbf{Contribution 3: Weight and Control Input Constraint Handling}
+  \begin{itemize}
+    \item 
+  \end{itemize}
+
+\end{frame}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Proposed Method                      ║
+% ╚═══════════════════════════════════════════════╝
 \section{Proposed Method}
@@
 
-  For the dual problem, 
+  To solve the dual problem, 
   \begin{equation}
@@
 
+  \centering
+  \begin{minipage}{.9\textwidth}
+
     \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
@@
 
+  \end{minipage}
+
+  \vspace{.2cm}
+
   Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.
@@
 
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Experimental Validation              ║
+% ╚═══════════════════════════════════════════════╝
 \section{Experimental Validation}
@@
           =
-          \begin{bmatrix}
+          \begin{pmatrix}
               {q_d}_1\\
               {q_d}_2
-          \end{bmatrix}
+          \end{pmatrix}
           = 
-          \begin{bmatrix}
+          \begin{pmatrix}
               +\cos(
@@
               ) - 1 
-          \end{bmatrix}
+          \end{pmatrix}
           .
@@
 \subsection{Simulation Results}
-
-% \begin{frame}{Representative Simulation Results}
-
-  % % \movie[width=3cm,height=2cm,poster]{}{overall.mp4}
-  % \begin{figure}
-  %   \centering
-  %   \href{https://youtu.be/U5uDbJQkGY8}{
-  %     \includegraphics[width=.1\textwidth]{figures/KAIST-hi.png}
-  %   }
-  % \end{figure}
-
-  % \animategraphics[loop,width=4cm]{gifs/overall-}
-  % \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}
-
-% \end{frame}
 
@@
 
+% \begin{frame}{Representative Simulation Results}
+
+%   \centering
+%   \includemedia[
+%       width=0.96\linewidth,
+%       height=0.54\linewidth,
+%       activate=onclick,
+%       addresource=demonstration.mp4,
+%       flashvars={
+%          source=demonstration.mp4
+%         &autoPlay=true
+%         &loop=true
+%       }
+%     ]{}{VPlayer.swf}
+
+% \end{frame}
+
 % \subsection{Simulation Setup}
@@
 
+% ╔═══════════════════════════════════════════════╗ 
+% ║ Section: Conclusion and Future Work           ║
+% ╚═══════════════════════════════════════════════╝
 \section{Conclusion}

### 2025-06-17 src/main_ECC_plotter.m

@@ -403,11 +403,264 @@ ylim([0, max(cstr.V_max) * 1.25])
 
 if POSITION_FLAG
     set(gcf, 'Position',  default_size)
+end
+
+figure(13); clf % control input norm CoNAC
+
+t = ctrl_results.ctrl5_1.t;
+u_norm_1 = sqrt(ctrl_results.ctrl5_1.u_hist(1, :).^2 + ctrl_results.ctrl5_1.u_hist(2, :).^2);
+u_norm_2 = sqrt(ctrl_results.ctrl5_2.u_hist(1, :).^2 + ctrl_results.ctrl5_2.u_hist(2, :).^2);
+u_norm_3 = sqrt(ctrl_results.ctrl5_3.u_hist(1, :).^2 + ctrl_results.ctrl5_3.u_hist(2, :).^2);
+
+plot(t, u_norm_1, "color", c_list(1,:), "LineWidth", line_width, "LineStyle", "-", ...
+    "DisplayName", "$\beta_j=0.001$"); hold on
+plot(t, u_norm_2, "color", c_list(2,:), "LineWidth", line_width, "LineStyle", "-.", ...
+    "DisplayName", "$\beta_j=0.45$"); hold on
+plot(t, u_norm_3, "color", c_list(3,:), "LineWidth", line_width, "LineStyle", "--", ...
+    "DisplayName", "$\beta_j=1$"); hold on
+
+xlabel("$t\ (\rm s)$", "Interpreter", "latex")
+ylabel("$\Vert u \Vert$", "Interpreter","latex")
+set(gca, 'FontSize', font_size, 'FontName', 'Times New Roman')
+grid on
+ylim([0, 60])
+lgd = legend;
+lgd.Orientation = 'Vertical';
+lgd.Location = 'southwest';
+lgd.Interpreter = 'latex';
+lgd.FontSize = lgd_size;
+
+if POSITION_FLAG
+    set(gcf, 'Position',  default_size)
+end
+
+figure(14); clf % control input norm CM1
+t = ctrl_results.ctrl6_1.t;
+u_norm_1 = sqrt(ctrl_results.ctrl6_1.u_hist(1, :).^2 + ctrl_results.ctrl6_1.u_hist(2, :).^2);
+u_norm_2 = sqrt(ctrl_results.ctrl6_2.u_hist(1, :).^2 + ctrl_results.ctrl6_2.u_hist(2, :).^2);
[…]

### 2025-06-18 manuscript.tex
new video

@@
 Since the objective function depends on $\fe$ of a dynamic system, obtaining $\pptfrac{\fe}{\rbu}$ is not straightforward. 
-The recommended method to calculate the exact value of $\pptfrac{\fe}{\rbu}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
+The recommended method to calculate the exact value of $\pptfrac{\fe}{\rbu}$ is to use the forward sensitivity method \cite{Sengupta:2014aa,Ryu:2024aa} by simulating the sensitivity equation as follows:
 \begin{equation}
@@
         &
-        -\estwth_k^\top (
+        -\estwth_k^\top 
+        \left(
             (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
@@
             \lambda_{\theta_k}\estwth_k
-        )
+        \right)
         \\
@@
         +\fe^\top \estNN
-        +(
+        +
+        \left(
             \overline\tau_d+\norm{
@@
             }
-        )
+        \right)
         \norm{\fe}
@@
         =&
-        =
         +
@@
         =&
-        =
         -\begin{bmatrix}

### 2025-06-18 presentation/presentation.tex
ppt final peer review 1

@@
 % Inbuilt themes in beamer
-\documentclass[8pt, aspectratio=169, handout]{beamer}
-% \documentclass[8pt, aspectratio=169]{beamer}
+% \documentclass[8pt, aspectratio=169, handout]{beamer}
+\documentclass[8pt, aspectratio=169]{beamer}
+% \setbeamertemplate{caption}[numbered]
 
@@
 % Available style: asphalt, blue, red, green, gray 
-\usetheme[style=blue]{flux}
+\usetheme[style=dding]{flux}
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@
 
+% https://latexcolor.com % color list
+\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+\definecolor{awesome}{rgb}{1.0, 0.13, 0.32}
+\newcommand{\ctxt}[2]{\color{#1}{#2}\color{black} }
+% \newcommand{\ctxt}[2]{\color{#1}\mathbf{#2}\color{black} }
+
 % Title page details: 
@@
 \author{
-  \textbf{Myeongseok Ryu}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
+  \textbf{\ctxt{airforceblue}{Myeongseok Ryu}}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
   }
@@
         \inst{1}%
-        Department of Mechanical and Robotics Engineering\\
-        Gwangju Institute of Science and Technology
+        Mobility Intelligence and Control Laboratory (MIC Lab) \\
+        % Department of Mechanical and Robotics Engineering\\
+        % Gwangju Institute of Science and Technology
+        CCS Graduate School of Mobility \\
+        Korea Advanced Institute of Science and Technology (KAIST)
         \and
@@
         AI Graduate School\\
-        Gwangju Institute of Science and Technology
+        Gwangju Institute of Science and Technology (GIST)
   \end{minipage}
 }
+
+% \titlegraphic{assets/MIC_Lab_logo.png}
 \titlegraphic{assets/MIC_Lab_logo_white.png}
+
 % make institute font size smaller
@@
     \begin{itemize}
-      \item \textbf{Neuro-adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control} \cite{Farrell:2006aa}.
-      \item Features of both \textbf{NNs} and \textbf{adaptive control} can be found in NAC.
+      \item \textbf{Neuro-adaptive control} (NAC) is a control strategy that combines \ctxt{airforceblue}{neural networks (NNs) } with \ctxt{awesome}{adaptive control } \cite{Farrell:2006aa}.
+      \item Features of both \ctxt{airforceblue}{NNs } and \ctxt{awesome}{adaptive control } can be found in NAC.
     \end{itemize}
@@
     \begin{itemize}
-      \item <+-> \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
-      \item <+-> \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
-      \item <+-> \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
-      \item <+-> \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
+      \item <2-> \textbf{Adaptability}: NAC adapts \ctxt{airforceblue}{NN weights }to changing environments and system dynamics.
+      \item <3-> \textbf{Stability Guarantee}: The closed-loop stability is ensured using \ctxt{airforceblue}{Lyapunov stability theory}.
+      \item <4-> \textbf{Online Learning Capability}: NAC adapts in \ctxt{airforceblue}{real-time } to new data with stability guarantees.
+      \item <5-> \textbf{Robustness}: NAC handles \ctxt{airforceblue}{uncertainties and disturbances }effectively with adaptive control techniques.
     \end{itemize}
@@
 
-\begin{frame}{\insertsubsectionhead}{Existing Challenges in NAC}
+\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}
+
+  \textbf{Existing Challenges in NAC}
 
   \begin{enumerate}
+
+    \onslide<2->
+    {
+      \begin{columns}[T,onlytextwidth]
+
+        \column{0.49\textwidth}
+
+          \small{
+            \item \textbf{Weight Boundedness:}
+
+            \begin{itemize}
+              \item Generally, NN weights are adapted by \ctxt{airforceblue}{gradient descent method}.
+              \begin{itemize}
+                \item Objective function typically consists of the control error.
+              \end{itemize}
+              \item Hence, the NN weights can grow \ctxt{awesome}{unbounded}, leading to instability (also known as \textit{parameter drift}).
+              \item Unbounded weights can cause the NN to produce \ctxt{airforceblue}{large control inputs}, which may lead to following challenges.
+            \end{itemize}
+          }
+
+          \column{0.49\textwidth}
+            \centering
+
+              \begin{figure}
+                \includegraphics[width=0.7\textwidth]{figures/unbounded.drawio.pdf}
+                \caption{Divergence of NN weights even with convergent control error.}
+              \end{figure}
+        \end{columns}
+      }
+
+      \onslide<3->
+      {
         \begin{columns}[T,onlytextwidth]
           \column{0.49\textwidth}
-          \item \textbf{Weight Boundedness:}
-
-          \begin{itemize}
-            \item The NN weights can grow unbounded, leading to instability.
-            \item Unbounded weights can cause the NN to produce large control inputs, which may lead to following challenges.
-          \end{itemize}
-
-        \column{0.49\textwidth}
-          \centering
-          \begin{figure}
-            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
-            \caption{Unbounded NN weights.}
-          \end{figure}
-      \end{columns}
-
-      \begin{columns}[T,onlytextwidth]
-        \column{0.49\textwidth}
+
+          \small{
             \item \textbf{Unpredictable Amplitude of Control Input:}
@@
             \begin{itemize}
-            \item The NN outputs are unpredictable and not interpretable.
-            \item This feature and unbounded NN weights can lead to control input saturation.
-          \end{itemize}
+              \item Typical issue of control problem in physical systems.
+              \item The NN outputs are \ctxt{awesome}{unpredictable } and \ctxt{awesome}{not interpretable}.
+              \item These features—unbounded NN weights and unpredictable amplitudes—can lead to \ctxt{airforceblue}{input saturation}.
+            \end{itemize}
+          }
 
@@
         \end{columns}
+      }
+
   \end{enumerate}
@@
   \begin{enumerate}
-    \begin{columns}[T,onlytextwidth]
-        \column{0.65\textwidth}
+
+    \begin{columns}[T]
+
+        \column{0.33\textwidth}
           \item \textbf{Projection Operator} \small{\textit{for weight boundednss}}
 
+          \onslide<2->
+          {
             \begin{itemize}
               \item Projects the NN weights onto a convex set.
-            \item Ensures that the weights remain within a predefined bound.
+              \item Ensures that the weights \ctxt{airforceblue}{remain }within a predefined bound.
             \end{itemize}
@@
             \end{equation}
-
-        \column{0.35\textwidth}
-          \begin{figure}
-            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
+          }
+
+        \column{0.33\textwidth}
+          \item \textbf{$\sigma$-modification, and $\epsilon$-modification} \small{\textit{for weight boundednss}}
+
+          \onslide<3->
+          {
+            \begin{itemize}
+              \item Add a \ctxt{airforceblue}{stabilizing term }(\eg $ -\lambda \estwth $) to adaptation law.
+              \item Construct a \ctxt{airforceblue}{invariant set }of the NN weights.
+            \end{itemize}
+
+            \begin{equation}
+              \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \ctxt{awesome}{\lambda \estwth}
+            \end{equation}
+          }
+
+        \column{0.33\textwidth}
+          \item \textbf{Additional Control Inputs} \small{\textit{for control saturation}}
+
+          \onslide<4->
+          {
+            \begin{itemize}
+              \item \ctxt{airforceblue}{Conventional controllers }are used to address control input saturation. 
+                    \begin{itemize}
+                      \item Barrier Lyapunov function or auxiliary system-based control inputs.
+                    \end{itemize}
+              \item In general, \ctxt{awesome}{nominal models }are required.
+            \end{itemize}
+          }
+
       \end{columns}
 
-      \vspace{0.2cm}
-
-      \begin{columns}[T,onlytextwidth]
-        \column{0.65\textwidth}
-          \item \textbf{$\epsilon$-modification, and $\sigma$-modification} \small{\textit{for weight boundednss}}
-
-          \begin{itemize}
-            \item Add a stabilizing term to adaptation law.
-            \item Invariance set of the NN weights can be ensured.
-          \end{itemize}
-
-          \begin{equation}
-            \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \rho \norm{\estwth}
-          \end{equation}
-
-        \column{0.35\textwidth}
-          \begin{figure}
-            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
+  \end{enumerate}
+
+  \vspace{0.5cm}
+
+  \begin{columns}[T]
+
+      \column{0.33\textwidth}
+
+        \onslide<2->
+        {
+          \centering
+          \begin{figure}
+            \includegraphics[width=0.8\textwidth]{figures/existing_proj.drawio.pdf}
+            \caption{Projection of NN weights on a convex set.}
+          \end{figure}
+        }
+
+      \column{0.33\textwidth}
+
+        \onslide<3->
+        {
+          \centering
+          \begin{figure}
+            \includegraphics[width=0.8\textwidth]{figures/existing_modi.drawio.pdf}
+            \caption{Adaptation result with stabilizing function (\eg $\sigma$-modification).}
+          \end{figure}
+        }
+
+      \column{0.33\textwidth}
+
+        \onslide<4->
+        {
+          \centering
+          \begin{figure}
+            \includegraphics[width=0.999\textwidth]{figures/existing_conv.drawio.pdf}
+            \caption{Control input saturation handling with additional control inputs.}
+          \end{figure}
+        }
 
@@
 
-      \vspace{0.2cm}
-
-      \begin{columns}[T,onlytextwidth]
-        \column{0.65\textwidth}
-          \item \textbf{Additional Control Inputs} \small{\textit{for control saturation}}
-
-          \begin{itemize}
-            \item Conventional controllers are used to address control input saturation. 
-                  \begin{itemize}
-                    \item Barrier Lyapunov function or auxiliary system-based control inputs.
-                  \end{itemize}
-            \item These methods do not guarantee the stability of the system.     
-          \end{itemize}
-
-        \column{0.35\textwidth}
-
-          \begin{figure}
-            \includegraphics[width=0.3\textwidth]{figures/KAIST-hi.png}
-          \end{figure}
-
-      \end{columns}
-  \end{enumerate}
 \end{frame}
@@
 
+  \onslide<1->
+  {
     \textbf{Limitation 1: Lack of Optimality}
-  \begin{itemize}
-    \item The existing methods do not guarantee the optimality of the control input.
-    \item ...
-  \end{itemize}
-
+  }
+  \begin{itemize}
+    \item<2-> The existing methods do not guarantee the \ctxt{airforceblue}{optimality } of the control input.
+    \item<3-> Projection operator:
+    \begin{itemize}
+      \item The projection operator \ctxt{awesome}{simply projects } the NN weights onto a convex set, regardless of the imposed \ctxt{airforceblue}{constraints } (\eg weight boundedness or input saturation).
+      \item Moreover, if the convex set is conservatively defined, the weights may be limited to a \ctxt{awesome}{suboptimal region}.
+    \end{itemize}
+    \item<4-> $\sigma$- and $\epsilon$-modification:
+    \begin{itemize}
+      \item The stabilizing term \ctxt{awesome}{biases } the NN weights towards the origin.
+      \item Therefore, the weights converge toward a \ctxt{awesome}{suboptimal point}.
+    \end{itemize}
+  \end{itemize}
+
+  \onslide<1->
+  {
     \textbf{Limitation 2: Disruption of Learning Process by Additional Control Inputs}
-  \begin{itemize}
-    \item Feedback tracking error for learning is disrupted by additional control inputs.
-      \begin{itemize}
-        \item The feedback error does not reflect the error induced by the NN, directly.
-      \end{itemize}  
-    \item 
+  }
+  \begin{itemize}
+    \item<5-> Feedback tracking error for learning is \ctxt{awesome}{disrupted } by additional control inputs.
+      \begin{itemize}
+        \item The feedback error \ctxt{airforceblue}{does not reflect } the error induced by the NN, directly.
+        \item The additional control inputs may exceeds the \ctxt{awesome}{input saturation limits }, already.
+    \end{itemize}  
   \end{itemize}
@@
   \textbf{Contribution 1: Unified Optimization Framework} 
-  \begin{itemize}
-    \item 
-  \end{itemize}
-
-  \textbf{Contribution 2: Online Learning Capability (Stabiltiy Guarantees)}
-  \begin{itemize}
-    \item 
-  \end{itemize}
+  \onslide<2->
+  {
+    \begin{itemize}
+      \item Trajectory tracking and constraint handling are formulated as a \ctxt{airforceblue}{unified constrained optimization } problem.
+      \item The \ctxt{awesome}{conventional controllers } does not required.
+      \begin{itemize}
+        \item Nominal model knowledge is not required for the conventional controllers.
+      \end{itemize}
+    \end{itemize}
+  }
+
+  \textbf{Contribution 2: Online Learning Capability (Stability Guarantees)}
+  \onslide<3->
+  {
+    \begin{itemize}
+      \item Stability are rigorously proven using \ctxt{airforceblue}{Lyapunov stability theory}.
+      \item Hence, \ctxt{airforceblue}{online learning} with \ctxt{awesome}{no prior system knowledge } is possible.
+    \end{itemize}
+  }
 
   \textbf{Contribution 3: Weight and Control Input Constraint Handling}
-  \begin{itemize}
-    \item 
-  \end{itemize}
+  \onslide<4->
+  {
+    \begin{itemize}
+      \item Weight and control input \ctxt{awesome}{constraints } are \ctxt{airforceblue}{explicitly considered } in the optimization problem.
+      \item \ctxt{airforceblue}{Any combination } of convex input constraints can be handled.
+    \end{itemize}
+  }
 
@@
 
+    \onslide<2->
+    {
       \textbf{Target Two-link Robotic Manipulator System}:
-      \begin{itemize}
-        \item Control input saturation function $\mysat(\cdot)$.
+      \small{
+        \begin{itemize}
+          \item Control input \ctxt{awesome}{saturation function } $\mysat(\cdot)$.
           \item Desired trajectory $\mv{q}_d$ is given.
@@
           \end{equation}    
-
+      }
+    }
+
+    \onslide<3->
+    {
       \textbf{Control Input}:
-      \begin{itemize}
-        \item NN's output $\mv{\Phi}$ is used as the control input.
-        \item Consists of the estimated NN weights $\estwth$.
+      \small{
+        \begin{itemize}
+          \item NN's \ctxt{airforceblue}{output } $\mv{\Phi}$ is used as the control input.
+          \item Consists of the \ctxt{awesome}{estimated NN weights } $\estwth$.
         \end{itemize}
@@
         \end{equation}
-
+      }
+    }
+
+    \onslide<4->
+    {
       \textbf{Deep Neural Network (DNN)}:
-      \begin{itemize}
-        \item $k$ layers with $\estwth_i:=\myvec(\estwV_i)$.
+      \small{
+        \begin{itemize}
+          \item $k$ layers with weights $\estwth_i:=\myvec(\estwV_i)$.
           \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
@@
         \end{itemize}
+      }
+    }
 
@@
 
+    \onslide<4->
+    {
       \begin{figure}
@@
       \end{figure}
+    }
 
@@
       \textit{Notations}: 
-        $\mv{q}\in\R^n$: Joint position, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\estwth$: Estimated NN weights.
-        $\estwth$: Estimated NN weights, $\mv{e}$: Tracking error, $\mv{\tau}_d$: Disturbance, $\mysat(\cdot)$: Saturation function.
+        $\mv{q}\in\R^n$: Joint position, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector, $\mv{\tau}$: Control input, $\mv{\tau}_d$: Disturbance.
       }
@@
     \begin{itemize}
-      \item \textbf{Find} NN weights $\estwth$,
-      \item That \textbf{minimize} objective function $J(\cdot)$,
+      \item \ctxt{awesome}{Find } NN weights $\estwth$,
+      \item That \ctxt{airforceblue}{minimize } objective function $J(\cdot)$,
         \begin{equation}\label{eq:obj}
@@
         \begin{itemize}
-          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is the filtered tracking error,
-        \end{itemize}
-      \item while satisfying the following \textbf{constraints}:
-        \begin{itemize}
-          \item Boundedness of the NN weights $\estwth$.
-          \item Saturation of the control input $\mv{\tau}$.
+          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is \ctxt{awesome}{filtered tracking error},
+        \end{itemize}
+      \item while satisfying the following \ctxt{awesome}{constraints}:
+        \begin{itemize}
+          \item \ctxt{airforceblue}{Boundedness } of the NN weights $\estwth$.
+          \item \ctxt{airforceblue}{Saturation } of the control input $\mv{\tau}$.
         \end{itemize}
@@
 
+  \onslide<2->
+  {
     \begin{block}{Considered Constraints}
@@
           \begin{itemize}
-            \item Input bound constraint:
+            \item Input bound constraint \textit{for each control input}:
             \begin{equation}\label{eq:cstr:input_bound}
@@
     \end{block}
+  }
 
@@
 
+  \onslide<2->
+  {
     \textbf{Define Lagrangian Function}
@@
     \end{equation}
-
+  }
+
+  \onslide<3->
+  {
     \textbf{Dual Problem}
     \begin{itemize}
-    \item The dual problem is to minimize the Lagrangian function with respect to the NN weights $\estwth$, while maximizing the Lagrange multipliers $\lambda_j$.
+      \item The dual problem is to \ctxt{airforceblue}{minimize } the Lagrangian function with respect to the \ctxt{airforceblue}{NN weights } $\estwth$, while \ctxt{awesome}{maximizing } with respect to the \ctxt{awesome}{Lagrange multipliers } $\lambda_j$.
       \item The Lagrange multipliers $\lambda_j$ are non-negative, \ie $\lambda_j \ge 0$.
@@
     \end{equation}
+  }
 
@@
 
-    \textbf{Gradient Descent Method for $\estwth$}:
+    \onslide<2->
+    {
+      \textbf{Gradient \ctxt{airforceblue}{Descent } Method for weights $\estwth$}:
       \begin{equation}\label{eq:adaptation_law:1}
@@
       \end{equation}
-
-    \textbf{Gradient Ascent Method for $\lambda_j, \forall j\in\mathcal I$}:
+    }
+
+    \onslide<3->
+    {
+      \textbf{Gradient \ctxt{awesome}{Ascent } Method for Lagrange multipliers $\lambda_j, \forall j\in\mathcal I$}:
       \begin{equation}\label{eq:adaptation_law:2}
@@
       \end{equation}
-
+    }
+
+    \onslide<4->
+    {
       For non-negativity of the Lagrange multipliers,
@@
       \end{equation}
-
-    % \begin{subequations}
-    %     \begin{align}
-    %       \ddt {{\estwth}}
-    %       &
-    %       =
-    %       -\alpha 
-    %       \ppfrac{L}{{\estwth}}
-    %       =-\alpha 
-    %       \left(
-    %           \ppfrac{J}{{\estwth}}
-    %           +
-    %           \sum_{j\in\mathcal{I}}
-    %           \lambda_j 
-    %           \ppfrac{c_j}{\estwth}
-    %       \right),
-    %       \\
-    %       \ddt\lambda_j
-    %       & 
-    %       = 
-    %       \beta_j
-    %       \ppfrac{L}{\lambda_j} 
-    %       = 
-    %       \beta_j c_j ,
-    %       \quad\quad\quad\quad      \      
-    %       \forall j\in\mathcal I,
-    %       \\
-    %       \lambda_j
-    %       &
-    %       \leftarrow
-    %       \max(\lambda_j,0)
-    %     \end{align}
-    % \end{subequations}
+    }
 
@@
     \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
-      For the dynamical system described in \eqref{eq:sys}, the neuro-adaptive controller in \eqref{eq:input} with the weight adaptation laws in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2.
-This holds under the weight norm constraint \eqref{eq:cstr:weight}.
+      For the \ctxt{airforceblue}{dynamical system } described in \eqref{eq:sys}, the \ctxt{awesome}{neuro-adaptive controller } in \eqref{eq:input} with the \ctxt{airforceblue}{weight adaptation laws } in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the \ctxt{airforceblue}{boundedness } of the \ctxt{awesome}{filtered error } $\mv{r}$ and the \ctxt{awesome}{weight estimate } $\estwth$, under the control input constraints satisfying Assumption 1 and 2.
+This holds under the \ctxt{awesome}{weight norm constraint } \eqref{eq:cstr:weight}.
     \end{block}
@@
 
-  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.
+  Proof of Theorem 1 is \textbf{omitted } due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.
 
@@
 
+\begin{frame}{\insertsubsectionhead}{Controllers Setting}
+
+  \begin{itemize}
+    \item Only \ctxt{awesome}{weight norm constraint } is considered in this presentation (for \textbf{ECC}).
+    \item Input saturation constraints are not considered.
+  \end{itemize}
+
+  \centering
+  \begin{figure}
+    \includegraphics[width=0.8\textwidth]{figures/Controller.drawio.pdf}
+    \caption{Architecture of the controllers.}
+  \end{figure}
+
+\end{frame}
+
 \begin{frame}{\insertsubsectionhead}{Controllers for Comparative Study}
@@
     \begin{itemize}
-      \item NAC-CO denotes the proposed controller based on constrained optimization.
-      \item For NAC-L2 and NAC-eMod, the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\tilde{\mv{z}}}\estwth$ ensures the boundedness of the NN weights
+      \item NAC-CO denotes the proposed controller based on \ctxt{airforceblue}{constrained optimization }.
+      \item For NAC-L2 and NAC-eMod, the \ctxt{awesome}{stabilizing terms } $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$ ensures the weights boundedness, respectively.
     \end{itemize}
@@
       \hline 
+        \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization \tiny{(equal to $\sigma$-modification)} & \multirow{2}{*}
+        {$
+          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\lambda}\estwth\right)
+        $}
+        \\
+          & ($\ctxt{awesome}{\lambda}$ stabilizes $\estwth$ towards origin) &
+        \\
+      \hline
+        \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
+        {$
+          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\rho}\norm{\tilde{\mv{z}}}\estwth\right)
+        $}
+        \\
+        & ($\ctxt{awesome}{\rho}$ stabilizes proportionally to filtered error $\mv{r}$) &
+        \\
+      \hline
         \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
         $
-        \ddt\estwth = -\alpha \left(\ppfrac{L}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
+          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
         $ 
         \\
-        (proposed) & ($\beta_j$ determines $\lambda_j$ adaptation speed) &
+          (proposed) & ($\ctxt{awesome}{\beta_j}$ determines $\lambda_j$ adaptation speed) &
         $
-        \ddt\lambda_j = \beta_j c_j, \lambda_j \leftarrow \max(\lambda_j,0)
+          \ddt\lambda_j = \ctxt{awesome}{\beta_j} c_j$, and $\lambda_j \leftarrow \max(\lambda_j,0)
         $
-      \\
-      \hline
-      \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization & \multirow{2}{*}
-      {$
-        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\lambda\estwth\right)
-      $}
-      \\
-        & ($\lambda\in\R_{>0}$ stabilizes $\estwth$ towards origin) &
-      \\
-      \hline
-      \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
-      {$
-        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\rho\norm{\tilde{\mv{z}}}\estwth\right)
-      $}
-      \\
-      & ($\rho$ stabilizes proportionally to the error $\tilde{\mv{z}}$) &
         \\
@@
 
+    \onslide<2->
+    {
       \centering
@@
         \begin{block}{Simulation Objective}
-        By varying the parameters, \ie $\beta_j$, $\lambda$, and $\rho$, the parameter dependencies will be investigated.
+          By \ctxt{airforceblue}{varying the parameters }, \ie $\beta_j$, $\lambda$, and $\rho$, the parameter dependencies will be investigated.
         \end{block}
       \end{minipage}
+    }
 
@@
   \begin{columns}
-    \column{0.55\textwidth}
+    \column{0.6\textwidth}
 
@@
 
-      \begin{itemize}
-        \item The parameters ranged from 0.001 to 1 across 10 samples.
-        \item NAC-CO (proposed) shows the best performance and low variance.
-        \item NAC-L2 shows the worst performance with high variance.
-      \end{itemize}
-
-    \column{0.5\textwidth}
-
-      \begin{figure}
-        \includegraphics[width=.99\textwidth]{figures/BoxWhisker.drawio.png}
-        \caption{Parameter dependencies of the proposed method.}
+      \small
+      {
+        \begin{itemize}
+          \item<+-> The parameters ranged from $0.001$ to $1$ across 10 samples.
+          \item<+-> NAC-L2 shows the \ctxt{awesome}{worst performance } with high variance.
+          \item<+-> NAC-CO (proposed) shows the \ctxt{airforceblue}{best performance } and \ctxt{airforceblue}{lowest variance}.
+          \item<+-> This result is because, 
+            \begin{itemize}
+              \item<+-> NAC-L2 and NAC-eMod are \ctxt{airforceblue}{biased towards the origin}.
+$\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\lambda\estwth})$ (NAC-L2) or $+\ctxt{awesome}{\rho\norm{\mv{r}}\estwth}$ (NAC-eMod), proportionally to $\lambda$ and $\rho$, respectively.
+              % \item<+-> $\beta_j$ in NAC-CO (proposed) only determines the \ctxt{airforceblue}{update speed } of the Lagrange multipliers $\lambda_j$, \ie $\ddtt\lambda_j=\beta_j c_j$.
+              % \begin{itemize}
+                \item<+-> $\ctxt{awesome}{-\lambda_j\pptfrac{c_j}{\estwth}}$ in NAC-CO (proposed) (\ie $\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\lambda_j\pptfrac{c_j}{\estwth}})$) \ctxt{airforceblue}{disappears } when constraints are inactive (\ie $c_j<0$, and $\lambda=\beta_jc_j$ and $\lambda_j\leftarrow\max(\lambda_j,0)$).
+%
+              % \end{itemize}
+            \end{itemize}
+        \end{itemize}
+      }
+
+    \column{0.4\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=.89\textwidth]{figures/BoxWhisker.drawio.png}
+        \caption{Box-and-whisker plots of the tracking error ISE.}
       \end{figure}
@@
       \hline 
-        Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
-      \hline
-        Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
-      \hline
-        Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
+        Maximum & \ctxt{awesome}{$11.1753 \times\!10^{-3}$} & $0.5603 \times 10^{-3}$ & \ctxt{airforceblue}{$0.3439 \times 10^{-3}$}  \\
+      \hline
+        Median & \ctxt{awesome}{$0.5898\times\!10^{-3}$}  & $0.5519 \times 10^{-3}$ & \ctxt{airforceblue}{$0.3240 \times 10^{-3}$}  \\
+      \hline
+        Minimum & \ctxt{awesome}{$0.5434\times\!10^{-3}$}  & $0.5434 \times 10^{-3}$ & \ctxt{airforceblue}{$0.3235 \times 10^{-3}$}  \\
       \hline
@@
     \let\thefootnote\relax\footnote{
-      Squared root of the tracking error ISE (Integral of Squared Error) is used, \ie $\sqrt{\int_0^T \norm{\mv{r}}^2\,\der t}$, where $T$ denotes a simulation termination time.
+      Squared root of the tracking error ISE (Integral of Squared Error), \ie $\sqrt{\int_0^T \norm{\mv{r}}^2\,\der t}$, where $T$ denotes a simulation time.
     }
@@
   \begin{columns}
-
-    \column{0.33\textwidth}
-
-      \begin{figure}
-        \includegraphics[width=0.99\textwidth]{figures/ECC/fig8.eps}
-        \caption{Weight norms of NAC-CO}
-      \end{figure}
 
@@
 
+    \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig8.eps}
+        \caption{Weight norms of NAC-CO (proposed)}
+      \end{figure}
+
   \end{columns}
@@
   \begin{itemize}
-    \item NAC-CO (proposed) showed the weight norms are bounded under pre-defined constraint $\overline{\theta}=20$.
-    \item NAC-L2 and NAC-eMod showed the bounded weight norms, but they depended on the parameters $\lambda$ and $\rho$, respectively.
-    \item As the parameters $\lambda$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
-    \item In addition, NAC-CO tracked the desired trajectory with a smaller weight norm than NAC-L2 and NAC-eMod.
+    \item<+-> NAC-CO (proposed) showed the \ctxt{airforceblue}{weight norms } are bounded \ctxt{awesome}{under pre-defined constraint } $\overline{\theta}=20$.
+    \item<+-> NAC-L2 and NAC-eMod showed the bounded weight norms, but they \ctxt{awesome}{depended } on the parameters $\lambda$ and $\rho$, respectively.
+    % \item<+-> As the parameters $\lambda$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
+    \item<+-> In other words, NAC-CO tracked the desired trajectory with a \ctxt{airforceblue}{smaller weight } norm than NAC-L2 and NAC-eMod.
   \end{itemize}
@@
   \begin{columns}
-
-    \column{0.33\textwidth}
-
-      \begin{figure}
-        \includegraphics[width=0.99\textwidth]{figures/ECC/fig5.eps}
-        \caption{Tracking error of NAC-CO}
-      \end{figure}
 
@@
 
+    \column{0.33\textwidth}
+
+      \begin{figure}
+        \includegraphics[width=0.99\textwidth]{figures/ECC/fig5.eps}
+        \caption{Tracking error of NAC-CO (proposed)}
+      \end{figure}
+
   \end{columns}
@@
   \begin{itemize}
-    \item NAC-CO (proposed) outperformed NAC-L2 and NAC-eMod in terms of tracking performance.
-    \item As the weights are biased towards the origin, the tracking performance of NAC-L2 and NAC-eMod deteriorated.
-  \end{itemize}
-
-\end{frame}
-
-% \begin{frame}{Representative Simulation Results}
-
-%   \centering
-%   \includemedia[
-%       width=0.96\linewidth,
-%       height=0.54\linewidth,
-%       activate=onclick,
-%       addresource=demonstration.mp4,
-%       flashvars={
-%          source=demonstration.mp4
-%         &autoPlay=true
-%         &loop=true
-%       }
-%     ]{}{VPlayer.swf}
-
-% \end{frame}
-
-% \subsection{Simulation Setup}
-
-% \begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}
-
-%     \begin{columns}
-
-%       \column{.55\textwidth}
-%         \begin{figure}
-%           \centering
-%           \includegraphics[width=.85\textwidth]{figures/RobotModel.drawio.png}
-%           \caption{Two-Link Robotic Manipulator}
-%         \end{figure}
-
-%       \column{.5\textwidth}
-
-%         \begin{table}[t]
-%             \renewcommand{\arraystretch}{1.3}
-%             \caption{Two-link robotic manipulator's parameters.}
-%             \centering
-%             \begin{tabular}{c m{9.5em} c c c }
-%             % \begin{tabular}{c c c c c}
-%             \hline
-%             \textbf{Symbol} & \textbf{Description} & \textbf{Value} \\
-%             \hline
-%             \hline 
-%             $m_1,m_2$ & Mass & 2.465 kg \\
-%             \hline
-%             $l_1,l_2$  & Length & 0.2 m \\  
-%             \hline
-%             ${l_c}_1,{l_c}_2$ & Center of mass & 0.139 m \\
-%             \hline
-%             $I_1,I_2$  & Inertia & 0.069 kgm\textsuperscript{2} \\
-%             \hline
-%             \end{tabular}
-%         \end{table}
-
-%     \end{columns}
-
-% \end{frame}
+    \item NAC-CO (proposed) \ctxt{airforceblue}{outperformed } NAC-L2 and NAC-eMod in terms of \ctxt{awesome}{tracking performance}.
+    \item As the weights are \ctxt{awesome}{biased }towards the origin proportionally to the parameters $\lambda$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward \ctxt{airforceblue}{suboptimal points}.
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Real-time Implementation Result}
+
+  \begin{itemize}
+    \item This video demonstrates:
+    \begin{itemize}
+      \item \ctxt{airforceblue}{Applicability }of the proposed method to real-time control (under 4 ms sampling time).
+      \item \ctxt{awesome}{Convex input constraints } handling.
+    \end{itemize}
+  \end{itemize}
+
+  \centering
+  \includemedia[
+      width=0.64\linewidth,
+      height=0.36\linewidth,
+      activate=onclick,
+      addresource=animation.mp4,
+      flashvars={
+        source=animation.mp4
+        &autoPlay=true
+        &loop=true
+      }
+    ]{}{VPlayer.swf}
+
+\end{frame}
 
@@
     \item Proposed a novel constrained optimization-based neuro-adaptive control (CONAC) method.
-    \item Adaptation laws are derived using constrained optimization method.
-    \item The proposed method guarantees the stability of the system and the boundedness of the NN weights.
-    \item Feasibility of the proposed method is validated through numerical simulations and real-time experiments.
+    \item Adaptation laws are derived using \ctxt{airforceblue}{constrained optimization method}.
+    \item The proposed method guarantees the \ctxt{awesome}{stability }of the system and the boundedness of the NN weights.
+    \item Feasibility of the proposed method is validated through numerical simulations.
   \end{itemize}
@@
   \begin{itemize}
-    \item Extend the proposed method to state constraints.
-    \item Enhance the robustness and flexibility of the proposed method for various systems.
+    \item Extend the proposed method to \ctxt{airforceblue}{state constraints}.
+    \item Enhance the \ctxt{awesome}{robustness }and \ctxt{awesome}{flexibility }of the proposed method for \ctxt{airforceblue}{various systems}.
   \end{itemize}

### 2025-06-19 presentation/presentation.tex
adding notes

@@
-% https://www.overleaf.com/learn/latex/Beamer#Using_a_colorthemev
-
-% Inbuilt themes in beamer
-% \documentclass[8pt, aspectratio=169, handout]{beamer}
-\documentclass[8pt, aspectratio=169]{beamer}
+\documentclass[8pt, aspectratio=169, handout]{beamer}
+% \documentclass[8pt, aspectratio=169]{beamer}
+
+% For figure numbering
 % \setbeamertemplate{caption}[numbered]
 
+% Slide show note
+% \setbeameroption{hide notes}
+% \setbeameroption{show only notes}
+\setbeameroption{show notes on second screen}
+
+% MIC Lab template
 \input{../template/macros/macros_general.tex}
@@
 
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 % Block options: block, alertblock, exampleblock
-% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
-% % Theme choice:
-% \usetheme{Antibes}
-% % \usecolortheme{beaver}
+
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@
 % Use Flux theme v0.1 beta
-% Available style: asphalt, blue, red, green, gray 
+% Available style: asphalt, blue, red, green, gray, dding (custom)
 \usetheme[style=dding]{flux}
@@
 \usepackage{schemabloc}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
 \usepackage{multirow}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% for video
 \usepackage{media9}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% colors
 % https://latexcolor.com % color list
@@
 \definecolor{awesome}{rgb}{1.0, 0.13, 0.32}
-\newcommand{\ctxt}[2]{\color{#1}{#2}\color{black} }
-% \newcommand{\ctxt}[2]{\color{#1}\mathbf{#2}\color{black} }
-
+\newcommand{\ctxt}[2]{\color{#1}{#2}\color{black}}
+% \newcommand{\mtxt}[2]{\color{#1}\mathbf{#2}\color{black} }
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 % Title page details: 
@@
 }
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+% Global settings
 
@@
 % }
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 % Title page frame
@@
 \end{frame}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}
@@
 \end{frame} 
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item adaptive controls adapts their parameters in real-time to systems.
+  \begin{itemize}
+    \item Hence, they can handle uncertainties and disturbances.
+  \end{itemize}
+  \item Like adaptive control, NAC adapts its NN weights, as well.
+  \item Hence, it has both features of NN and adaptive control.
+}
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item The features are...
+  \begin{itemize}
+    \item It can adapts its weights to change environments.
+    \item And the stability is ensured in the sense of Lyapunov.
+    \item So, it has online learning capability.
+    \item In addition, with various methods from adaptive control, NAC can be more robust than naive NN-based control methods.
+  \end{itemize}
+}
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item However, there are some challenges in NAC.
+  \item The first challenge is weight boundedness.
+  \begin{itemize}
+    \item If the NNs are used for control naively, the boundedness of NN weights is not ensured.
+    \item Despite the convergence of the control error, the NN weights can diverge like parameter drift.
+    \item This divergence leads to the following issue.
+  \end{itemize}
+  \item Second one is the NN's output can be excessively large control inputs.
+  \begin{itemize}
+    \item This is because, the output of NN is not interpretable and unpredictable.
+    \item So, the input saturation problem can occur by them.
+  \end{itemize}
+}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Background and Contributions         ║
+% ║   - Subsection: Literature Review             ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Literature Review}
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}
@@
 
-  \vspace{0.5cm}
+  % \vspace{0.5cm}
 
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item To address these issues, several methods have been introduced.
+  \item For weight boundedness, the projection operator and modification methods are used.
+  \begin{itemize}
+    \item they ensures the weight boundedness by projects onto a convex set or adding a stabilizing term.
+    \item Hence, the the boundedness of NN weights can 
+  \end{itemize}
+  \item For control input saturation, additional control inputs are used.
+  \begin{itemize}
+    \item Conventionally, auxiliary system-based control inputs or, more recently, barrier Lyapunov function-based control inputs are used.
+    \item For this, the nominal model knowledge is required.
+    \item These makes the control design more complicated, but, have shown the effectiveness of the control input saturation handling.
+  \end{itemize}
+}
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Limitations of Existing Methods}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item the limitations of the existing methods can be summarized as follows.
+  \item Most of methods does not consider the optimality when the constraints are active.
+  \item 
+}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Background and Contributions         ║
+% ║   - Subsection: Contributions                 ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Contributions}
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}
@@
 % ╚═══════════════════════════════════════════════╝
+
 \section{Proposed Method}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Optimization Problem}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Gradient Descent/Ascent Method}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Lyapunov Stability Analysis}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Controllers Setting}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Controllers for Comparative Study}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Box-and-Whisker Plots}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Weight Norms}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Tracking Performance}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{Real-time Implementation Result}
@@
 
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{Conclusion}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \section{}
@@
 \end{frame}
-
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}[allowframebreaks]{References}

### 2025-06-20 presentation/presentation.tex
end adding notes

@@
-\documentclass[8pt, aspectratio=169, handout]{beamer}
-% \documentclass[8pt, aspectratio=169]{beamer}
-
-% For figure numbering
-% \setbeamertemplate{caption}[numbered]
-
-% Slide show note
-% \setbeameroption{hide notes}
-% \setbeameroption{show only notes}
-\setbeameroption{show notes on second screen}
+% \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show notes on second screen}
+% \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show only notes}
+\documentclass[8pt, aspectratio=169]{beamer}
 
@@
 % ╚═══════════════════════════════════════════════╝
+
 \section{Background and Contributions}
@@
           \small{
-            \item \textbf{Unpredictable Amplitude of Control Input:}
+            \item \textbf{Control Saturation} \textit{(unpredictable amplitude of NN outputs)}:
 
@@
     \item If the NNs are used for control naively, the boundedness of NN weights is not ensured.
-    \item Despite the convergence of the control error, the NN weights can diverge like parameter drift.
+    \item For instance, despite the convergence of the control error, the NN weights can diverge like parameter drift.
     \item This divergence leads to the following issue.
@@
     \item they ensures the weight boundedness by projects onto a convex set or adding a stabilizing term.
-    \item Hence, the the boundedness of NN weights can 
+    \item Hence, the the boundedness of NN weights can be easily ensured.
   \end{itemize}
@@
   \item Most of methods does not consider the optimality when the constraints are active.
-  \item 
+  \begin{itemize}
+    \item Because, they only consider the boundedness of the weights or the control input saturation using additional operators or terms.
+  \end{itemize}
+  \item Using additional terms can lead to disruption of learning process.
+  \item It is, because, as the NN learns with respect to the feedback error, once the additional control inputs are applied, the feedback error does not reflect the error induced by the NN, directly.
+  \item Moreover, the additional control inputs may exceed the input limits, already.
+  \item Therefore, in the worst case, the NN may be forced to compensate for the additional terms.
 }
@@
 
+\note[enumerate]
+{
+  \item So, here are the contributions of this work.
+  \item We, first, formulated a unified optimization framework for trajectory tracking and constraint handling.
+  \item Hence, we do not need the additional operators or conventional controllers, which may need the nominal model knowledge.
+  \item Second, we rigorously proved the stability of the proposed method using Lyapunov stability theory.
+  \item It means, that the proposed method can learn online without any prior system knowledge with stability guarantees.
+  \item Finally, as we explicitly consider the weight and control input constraints in the optimization problem, we can handle any combination of convex input constraints and weight constraint.
+}
+
 % ╔═══════════════════════════════════════════════╗
@@
 
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Proposed Method                      ║
+% ║   - Subsection: Architecture of the Proposed Method
+% ╚═══════════════════════════════════════════════╝
 \subsection{Architecture of the Proposed Method}
@@
 
+\note[enumerate]{
+  \item The proposed method consists of a DNN and weight optimizer, inside.
+  \item Let's start with the system.
+  \begin{itemize}
+    \item The system is a two-link robotic manipulator system, which is controlled by the control input $\mv{\tau}$.
+    \item The control input is saturated by the saturation function $\mysat(\cdot)$.
+    \item The desired trajectory $\mv{q}_d$ is given.
+  \end{itemize}
+  \item The control input is purely decided by the DNN, so the output of the DNN is the control input.
+  \item And, the DNN is defined like \eqref{eq:NN}, with $k$ layers and weights, and $\tanh(\cdot)$ as the activation function.
+}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Proposed Method                      ║
+% ║   - Subsection: Problem Formulation           ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Problem Formulation}
@@
 \end{frame}
-
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\note[enumerate]
+{
+  \item The control problem can be represented as a constrained optimization problem.
+  \begin{itemize}
+    \item That is, 
+    \item We need to find NN weights ...
+  \end{itemize}
+  \item To explicitly consider the constraints, we define the constraint functions as follows, for weight boundedness and convex control input saturation of each control input and norm of the control input.
+}
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{frame}{\insertsubsectionhead}{Optimization Problem}
@@
 
+\note[enumerate]
+{
+  \item Then using the constraint functions, we can formulate the constrained optimization problem as in \eqref{eq:opt_problem}.
+  \item And, we can define the Lagrangian function as in \eqref{eq:lagrangian}.
+  \item So, the dual problem can be formulated as in \eqref{eq:dual_problem}.
+  \item It means, that we can find the optimal solution by minimizing the Lagrangian function with respect to the NN weights, while maximizing it with respect to the Lagrange multipliers.
+}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Proposed Method                      ║
+% ║   - Subsection: Adaptation Law Derivation     ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Adaptation Law Derivation}
@@
       \begin{equation}\label{eq:adaptation_law:1}
-        \ddt {{\estwth}}
+        \ddtt {
+          \ctxt{airforceblue}{\estwth}
+          }
         =
         -\alpha 
-        \ppfrac{L}{{\estwth}}
+        \pptfrac{L}{\ctxt{airforceblue}{\estwth}}
         =-\alpha 
         \left(
-            \ppfrac{J}{{\estwth}}
+            \pptfrac{J}{\ctxt{airforceblue}{\estwth}}
             +
-            \sum_{j\in\mathcal{I}}
-            \lambda_j 
-            \ppfrac{c_j}{\estwth}
+            \textstyle\sum_{j\in\mathcal{I}}
+            \ctxt{awesome}{\lambda_j}
+            \pptfrac{c_j}{\ctxt{airforceblue}{\estwth}}
         \right),
@@
       \begin{equation}\label{eq:adaptation_law:2}
-        \ddt\lambda_j
+        \ddtt\ctxt{awesome}{\lambda_j}
         = 
         \beta_j
-        \ppfrac{L}{\lambda_j} 
+        \pptfrac{L}{\ctxt{awesome}{\lambda_j}} 
         = 
@@
       \begin{equation}\label{eq:adaptation_law:3}
-        \lambda_j
+        \ctxt{awesome}{\lambda_j}
         \leftarrow
-        \max(\lambda_j,0)
+        \max(\ctxt{awesome}{\lambda_j},0)
         .
@@
   \end{minipage}
-\end{frame}
-%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
-
+
+  \let\thefootnote\relax\footnote{
+    $\alpha$: adaptation gain (learning rate), $\beta_j$: update rate of the Lagrange multipliers.
+  }
+
+\end{frame}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item To solve this problem, we employed the first-order gradient descent/ascent method.
+  \item For minimizing the Lagrangian function with respect to the NN weights, the gradient descent method is used.
+  \begin{itemize}
+    \item We have a adaptation gain $\alpha$ to control the learning rate.
+  \end{itemize}
+  \item For maximizing the Lagrangian function with respect to the Lagrange multipliers, the gradient ascent method is used.
+  \begin{itemize}
+    \item We have an update rate $\beta_j$ for each Lagrange multiplier.
+  \end{itemize}
+  \item Finally, the max operator is used to ensure the non-negativity of the Lagrange multipliers.
+  \item Therefore, according to the adaptation law, when the constraints are active, the Lagrange multipliers are updated to be positive.
+  \item And, the NN weights are updated to minimize the constraint violation while minimizing the tracking error.
+  \item After the constraints are satisfied, \it negative, the Lagrange multipliers are updated to zero, and the NN weights are updated to minimize the tracking error only.
+}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Proposed Method                      ║
+% ║   - Subsection: Stability Analysis            ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Stability Analysis}
@@
 
+\note[enumerate]
+{
+  \item The stability of the proposed methods is proven using Lyapunov stability theory.
+  \item The requirements for the stability are as follows.
+  \item First, the weight norm constraints should be imposed.
+  \item And, two assumptions for convex input constraints and LICQ conditions should be satisfied.
+  \item The proof is omitted, but the detailed proof can be found in the reference \cite{Ryu:2025aa}.
+}
+
 % ╔═══════════════════════════════════════════════╗
@@
 % ╚═══════════════════════════════════════════════╝
+
 \section{Experimental Validation}
 
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Experimental Validation              ║
+% ║   - Subsection: Simulation Setup              ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Simulation Setup}
@@
 
+\note[enumerate]
+{
+  \item For validation, we simulated a two-link robotic manipulator system.
+  \item A simple cosine trajectory is given as the desired trajectory.
+}
+
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@
     \item Input saturation constraints are not considered.
+    \item For simplicity, \ctxt{airforceblue}{single hidden layer NN} is used.
   \end{itemize}
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item For this conference paper, we only considered the weight norm constraint.
+  \item So, please ignore the input saturation.
+}
 
@@
         {$
-          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\rho}\norm{\tilde{\mv{z}}}\estwth\right)
+          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\rho}\norm{\tilde{\mv{r}}}\estwth\right)
         $}
@@
 
+\note[enumerate]
+{
+  \item For comparative study, we used two existing methods: L2-regularization (NAC-L2) and $\epsilon$-modification (NAC-eMod).
+  \item Please, note that the L2-regularization is equal to the $\sigma$-modification.
+  \item In summary, the NAC-L2 and NAC-eMod use the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$, respectively, to ensure the boundedness of the weights.
+  \item While the NAC-CO is the proposed method, which uses the Lagrange multipliers $\lambda_j$ to ensure the boundedness of the weights.
+  \item The simulation is mainly conducted to investigate dependencies of the crucial parameters, \ie $\beta_j$, $\lambda$, and $\rho$.
+}
+
+% ╔═══════════════════════════════════════════════╗
+% ║ Section: Experimental Validation              ║
+% ║   - Subsection: Simulation Results            ║
+% ╚═══════════════════════════════════════════════╝
 \subsection{Simulation Results}
@@
 
+\note[enumerate]
+{
+  \item The parameters were varied from $0.001$ to $1$ across 10 samples.
+  \item The box-and-whisker plots show the distribution of the tracking error ISE (Integral of Squared Error).
+  \item The NAC-L2 shows the worst performance with high variance, while the NAC-CO (proposed) shows the best performance with the lowest variance.
+  \item The reason is that the NAC-L2 and NAC-eMod are biased towards the origin, especially, proportionally to the parameters $\lambda$ and $\rho$, respectively.
+  \item On the other hand, the term that biases the weights towards the origin in NAC-CO, is removed when the constraints are inactive, \ie $c_j<0$.
+  \item Therefore, the NAC-CO can track the desired trajectory without being biased, when the constraints are inactive.
+}
+
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@
 
+\note[enumerate]
+{
+  \item In this slide, the weight norms are shown.
+  \item We can see that the NAC-CO's weights are bounded under the pre-defined constraint $\overline{\theta}=20$.
+  \item The other two methods shows larger weight norms, and biased weights towards the origin, which may lead to suboptimal performance.
+  \item Moreover, the dependencies also can be seen, as the distribution of the weight norms of NAC-L2 and NAC-eMod are wider than that of NAC-CO.
+}
+
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+\note[enumerate]
+{
+  \item The tracking performance of the three methods are shown.
+  \item The NAC-CO (proposed) outperformed the other two methods in terms of tracking performance.
+  \item As the weights are biased towards the origin proportionally to the parameters $\lambda$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward suboptimal points.
+}
 
@@
 
+\note[enumerate]
+{
+  \item And, until the last slice, we have shown the conference paper's results.
+  \item In this slide, we show the recent result with real-time implementation.
+  \item The video demonstrates the applicability of the proposed method to real-time control, under 4 ms sampling time.
+  \item And, the convex input constraints are handled, here.
+}
+
 % ╔═══════════════════════════════════════════════╗ 
@@
 % ╚═══════════════════════════════════════════════╝
+
 \section{Conclusion}
@@
 %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
 \section{}

### 2025-06-20 presentation/presentation.tex
after rehearser ; prof cmt added

@@
-% \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show notes on second screen}
+\documentclass[8pt, aspectratio=169, handout]{beamer} 
+% \documentclass[8pt, aspectratio=169, handout, draft]{beamer} 
 % \documentclass[8pt, aspectratio=169, handout]{beamer} \setbeameroption{show only notes}
-\documentclass[8pt, aspectratio=169]{beamer}
+% \documentclass[8pt, aspectratio=169]{beamer}
 
@@
             \begin{itemize}
-              \item Add a \ctxt{airforceblue}{stabilizing term }(\eg $ -\lambda \estwth $) to adaptation law.
+              \item Add a \ctxt{airforceblue}{stabilizing term }(\eg $ -\sigma \estwth $) to adaptation law.
               \item Construct a \ctxt{airforceblue}{invariant set }of the NN weights.
@@
             \begin{equation}
-              \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \ctxt{awesome}{\lambda \estwth}
+              \ddtt{\estwth} \leftarrow \ddtt{\estwth} - \ctxt{awesome}{\sigma \estwth}
             \end{equation}
@@
 
-  \textbf{Contribution 1: Unified Optimization Framework} 
+  \textbf{Contribution 1: Constrained Unified Optimization Framework} 
   \onslide<2->
@@
         \begin{itemize}
-          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is \ctxt{awesome}{filtered tracking error},
+          \item where $\mv{r} := \ddt\mv{e} + \sigma\mv{e}$ is \ctxt{awesome}{filtered tracking error},
         \end{itemize}
@@
     \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
-      For the \ctxt{airforceblue}{dynamical system } described in \eqref{eq:sys}, the \ctxt{awesome}{neuro-adaptive controller } in \eqref{eq:input} with the \ctxt{airforceblue}{weight adaptation laws } in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the \ctxt{airforceblue}{boundedness } of the \ctxt{awesome}{filtered error } $\mv{r}$ and the \ctxt{awesome}{weight estimate } $\estwth$, under the control input constraints satisfying Assumption 1 and 2.
+      For the \ctxt{airforceblue}{dynamical system } described in \eqref{eq:sys}, the \ctxt{awesome}{neuro-adaptive controller } in \eqref{eq:input} with the \ctxt{airforceblue}{weight adaptation laws } in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the \ctxt{airforceblue}{boundedness } of the \ctxt{awesome}{filtered error } $\mv{r}$ and the \ctxt{awesome}{weight estimate } $\estwth$, under the \ctxt{airforceblue}{control input constraints} satisfying Assumption 1 and 2.
 This holds under the \ctxt{awesome}{weight norm constraint } \eqref{eq:cstr:weight}.
@@
   \begin{itemize}
-    \item Only \ctxt{awesome}{weight norm constraint } is considered in this presentation (for \textbf{ECC}).
+    \item Only \ctxt{awesome}{weight norm constraint } is considered in this presentation (for \textbf{†his Conference paper}).
     \item Input saturation constraints are not considered.
@@
       \item NAC-CO denotes the proposed controller based on \ctxt{airforceblue}{constrained optimization }.
-      \item For NAC-L2 and NAC-eMod, the \ctxt{awesome}{stabilizing terms } $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$ ensures the weights boundedness, respectively.
+      \item For NAC-L2 and NAC-eMod, the \ctxt{awesome}{stabilizing terms } $-\sigma\estwth$ and $\rho\norm{\mv{r}}\estwth$ ensures the weights boundedness, respectively.
     \end{itemize}
@@
         {$
-          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\lambda}\estwth\right)
+          \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\ctxt{awesome}{\sigma}\estwth\right)
         $}
         \\
-          & ($\ctxt{awesome}{\lambda}$ stabilizes $\estwth$ towards origin) &
+          & ($\ctxt{awesome}{\sigma}$ stabilizes $\estwth$ towards origin) &
         \\
@@
         \begin{block}{Simulation Objective}
-          By \ctxt{airforceblue}{varying the parameters }, \ie $\beta_j$, $\lambda$, and $\rho$, the parameter dependencies will be investigated.
+          By \ctxt{airforceblue}{varying the parameters }, \ie $\beta_j$, $\sigma$, and $\rho$, the parameter dependencies will be investigated.
         \end{block}
@@
   \item Please, note that the L2-regularization is equal to the $\sigma$-modification.
-  \item In summary, the NAC-L2 and NAC-eMod use the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\mv{r}}\estwth$, respectively, to ensure the boundedness of the weights.
+  \item In summary, the NAC-L2 and NAC-eMod use the stabilizing terms $-\sigma\estwth$ and $\rho\norm{\mv{r}}\estwth$, respectively, to ensure the boundedness of the weights.
   \item While the NAC-CO is the proposed method, which uses the Lagrange multipliers $\lambda_j$ to ensure the boundedness of the weights.
-  \item The simulation is mainly conducted to investigate dependencies of the crucial parameters, \ie $\beta_j$, $\lambda$, and $\rho$.
+  \item The simulation is mainly conducted to investigate dependencies of the crucial parameters, \ie $\beta_j$, $\sigma$, and $\rho$.
 }
@@
               \item<+-> NAC-L2 and NAC-eMod are \ctxt{airforceblue}{biased towards the origin}.
-$\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\lambda\estwth})$ (NAC-L2) or $+\ctxt{awesome}{\rho\norm{\mv{r}}\estwth}$ (NAC-eMod), proportionally to $\lambda$ and $\rho$, respectively.
+$\ddtt\estwth=-\alpha(\pptfrac{J}{\estwth}+\ctxt{awesome}{\sigma\estwth})$ (NAC-L2) or $+\ctxt{awesome}{\rho\norm{\mv{r}}\estwth}$ (NAC-eMod), proportionally to $\sigma$ and $\rho$, respectively.
               % \item<+-> $\beta_j$ in NAC-CO (proposed) only determines the \ctxt{airforceblue}{update speed } of the Lagrange multipliers $\lambda_j$, \ie $\ddtt\lambda_j=\beta_j c_j$.
@@
   \item The NAC-L2 shows the worst performance with high variance, while the NAC-CO (proposed) shows the best performance with the lowest variance.
-  \item The reason is that the NAC-L2 and NAC-eMod are biased towards the origin, especially, proportionally to the parameters $\lambda$ and $\rho$, respectively.
+  \item The reason is that the NAC-L2 and NAC-eMod are biased towards the origin, especially, proportionally to the parameters $\sigma$ and $\rho$, respectively.
   \item On the other hand, the term that biases the weights towards the origin in NAC-CO, is removed when the constraints are inactive, \ie $c_j<0$.
@@
     \item<+-> NAC-CO (proposed) showed the \ctxt{airforceblue}{weight norms } are bounded \ctxt{awesome}{under pre-defined constraint } $\overline{\theta}=20$.
-    \item<+-> NAC-L2 and NAC-eMod showed the bounded weight norms, but they \ctxt{awesome}{depended } on the parameters $\lambda$ and $\rho$, respectively.
-    % \item<+-> As the parameters $\lambda$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
+    \item<+-> NAC-L2 and NAC-eMod showed the bounded weight norms, but they \ctxt{awesome}{depended } on the parameters $\sigma$ and $\rho$, respectively.
+    % \item<+-> As the parameters $\sigma$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
     \item<+-> In other words, NAC-CO tracked the desired trajectory with a \ctxt{airforceblue}{smaller weight } norm than NAC-L2 and NAC-eMod.
@@
     \item NAC-CO (proposed) \ctxt{airforceblue}{outperformed } NAC-L2 and NAC-eMod in terms of \ctxt{awesome}{tracking performance}.
-    \item As the weights are \ctxt{awesome}{biased }towards the origin proportionally to the parameters $\lambda$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward \ctxt{airforceblue}{suboptimal points}.
+    \item As the weights are \ctxt{awesome}{biased }towards the origin proportionally to the parameters $\sigma$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward \ctxt{airforceblue}{suboptimal points}.
   \end{itemize}
@@
   \item The NAC-CO (proposed) outperformed the other two methods in terms of tracking performance.
-  \item As the weights are biased towards the origin proportionally to the parameters $\lambda$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward suboptimal points.
+  \item As the weights are biased towards the origin proportionally to the parameters $\sigma$ and $\rho$ in NAC-L2 and NAC-eMod, respectively, the tracking performance of NAC-L2 and NAC-eMod deteriorated, as approaching toward suboptimal points.
 }
@@
       activate=onclick,
-      addresource=animation.mp4,
+      addresource=assets/animation.mp4,
       flashvars={
-        source=animation.mp4
+        source=assets/animation.mp4
         &autoPlay=true
@@
   \begin{itemize}
-    \item Proposed a novel constrained optimization-based neuro-adaptive control (CONAC) method.
+    \item Proposed a constrained optimization-based neuro-adaptive control method.
     \item Adaptation laws are derived using \ctxt{airforceblue}{constrained optimization method}.

### 2025-06-20 src/main_ECC_plotter_for_pres.m

@@ -1,0 +1,676 @@
+clear
+clc
+
+%%
+FIGURE_PLOT = 1;
+% SAVE_FLAG = 1;
+SAVE_FLAG = 1;
+POSITION_FLAG = 1; % it will plot fiugures in the same position
+
+font_size = 18;
+line_width = 2;
+lgd_size = 18;
+default_size = [100, 100, 560, 200];
+
+% ERROR DATA LOAD
+CoNAC_Pi = load("sim_result/CoNAC_var.mat");
+CoNAC_Pi = CoNAC_Pi.Pi_list;    
+
+CM2_Pi = load("sim_result/CM2_var.mat");
+CM2_Pi = CM2_Pi.Pi_list;    
+
+CM1_Pi = load("sim_result/CM1_var.mat");
+CM1_Pi = CM1_Pi.Pi_list;    
+
+% figure(1);clf %check CoNAC
+% tl = tiledlayout(2,1);
+
+% nexttile
+% plot(CoNAC_Pi(1,:), CoNAC_Pi(2,:), 'r', 'LineWidth', 2); hold on
+% nexttile
+% plot(CoNAC_Pi(1,:), CoNAC_Pi(3,:), 'r', 'LineWidth', 2); hold on
+
+% figure(2);clf % check CM1
+% tl = tiledlayout(2,1);
+
+% nexttile
+% plot(CM1_Pi(1,:), CM1_Pi(2,:), 'r', 'LineWidth', 2); hold on
+% nexttile
+% plot(CM1_Pi(1,:), CM1_Pi(3,:), 'r', 'LineWidth', 2); hold on
+
+% figure(3);clf % check CM2
+% tl = tiledlayout(2,1);
+
+% nexttile
+% plot(CM2_Pi(1,:), CM2_Pi(2,:), 'r', 'LineWidth', 2); hold on
+% nexttile
+% plot(CM2_Pi(1,:), CM2_Pi(3,:), 'r', 'LineWidth', 2); hold on
+
+figure(3); clf % box-whisker plot
+
+CoNAC_Pi = sqrt(sum(CoNAC_Pi(2:3,:).^2, 1));
+CM1_Pi = sqrt(sum(CM1_Pi(2:3,:).^2, 1));
+CM2_Pi = sqrt(sum(CM2_Pi(2:3,:).^2, 1));
+
+Pi_list = [CM1_Pi; CM2_Pi; CoNAC_Pi];
[…]
